### 2022-03-07 acyclicFacets/draft/latticePipeDreams.tex
draft from 5 years ago, with some additional comments

\documentclass{amsart}

\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap, a4wide, pdflscape, multido, xargs, colortbl, multicol, multirow, calc, shuffle}
\hypersetup{colorlinks=true, citecolor=PineGreen, linkcolor=PineGreen}
%\usepackage[all]{xy}
\usepackage{tikz}\usetikzlibrary{trees,snakes,shapes,arrows,matrix,calc}
\usepackage{comment}
\usepackage{etex}
%\reserveinserts{50}
\graphicspath{{figures/}}
\makeatletter
\def\input@path{{figures/}}
\makeatother

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{The lattice of acyclic pipe dreams}

\author[N.~Bergeron]{Nantel Bergeron} 
\address[N.~Bergeron]{Department of Mathematics and Statistics, York University, Toronto}
\email{bergeron@mathstat.yorku.ca}
\urladdr{http://www.math.yorku.ca/bergeron/}

\author[N.~Cartier]{No\'emie Cartier} 
\address[N.~Cartier]{LRI, Université Paris Saclay}
\email{noemie.cartier@lri.fr}

\author[C.~Ceballos]{Cesar Ceballos}
\address[C.~Ceballos]{Institute of Geometry, Technische Universit\"at Graz}
\email{cesar.ceballos@tugraz.at}
\urladdr{http://www.geometrie.tugraz.at/ceballos/}

\author[V.~Pilaud]{Vincent Pilaud}
\address[V.~Pilaud]{CNRS \& LIX, \'Ecole Polytechnique, Palaiseau}
\email{vincent.pilaud@lix.polytechnique.fr}
\urladdr{http://www.lix.polytechnique.fr/~pilaud/}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% theorems
\newtheorem{theorem}{Theorem}%[section]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{conjecture}[theorem]{Conjecture}

\theoremstyle{definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{question}[theorem]{Question}

% newcommands
% math special letters
\newcommand{\R}{\mathbb{R}} % reals
\newcommand{\N}{\mathbb{N}} % naturals
\newcommand{\Z}{\mathbb{Z}} % integers
\newcommand{\I}{\mathbb{I}} % set of integers
\newcommand{\C}{\mathbb{C}} % set of summands

% math commands
\newcommand{\set}[2]{\left\{ #1 \;\middle|\; #2 \right\}} % set notation
\newcommand{\bigset}[2]{\big\{ #1 \;|\; #2 \big\}} % big set notation
\newcommand{\biggset}[2]{\bigg\{ #1 \;\bigg|\; #2 \bigg\}} % big set notation
\newcommand{\multiset}[2]{\left\{\!\!\left\{ #1 \;\middle|\; #2 \right\}\!\!\right\}} % multiset notation
\newcommand{\bigmultiset}[2]{\big\{\!\!\big\{ #1 \;|\; #2 \big\}\!\!\big\}} % big multiset notation
\newcommand{\ssm}{\smallsetminus} % small set minus
\newcommand{\dotprod}[2]{\langle #1 | #2 \rangle} % dot product
\newcommand{\symdif}{\triangle} % symmetric difference
\newcommand{\one}{{1\!\!1}} % the all one vector
\newcommand{\eqdef}{\mbox{\,\raisebox{0.2ex}{\scriptsize\ensuremath{\mathrm:}}\ensuremath{=}\,}} % :=
\newcommand{\defeq}{\mbox{~\ensuremath{=}\raisebox{0.2ex}{\scriptsize\ensuremath{\mathrm:}} }} % =:
\newcommand{\polar}{^\diamond} % polar
\newcommand{\simplex}{\triangle} % simplex

% operators
\DeclareMathOperator{\conv}{conv} % convex hull
\DeclareMathOperator{\cone}{cone} % cone hull
\DeclareMathOperator{\arr}{Arr} % arrangements
\DeclareMathOperator{\inv}{inv} % inversion set

% others
\newcommand{\fix}[1]{{\bf FIXME: }#1} % emphasis of a problem to FIX
\newcommand{\fref}[1]{Figure~\ref{#1}} % reference figures
\newcommand{\ie}{\textit{i.e.}~} % id est
\newcommand{\eg}{\textit{e.g.}~} % exempli gratia
\newcommand{\Eg}{\textit{E.g.}~} % exempli gratia
\newcommand{\aka}{\textit{aka.}~} % also known as
\newcommand{\viceversa}{\textit{vice versa}} % vice versa
\newcommand{\ordinal}{\textsuperscript{th}} % th for ordinals
\newcommand{\ex}[1]{^{\textrm{ex#1}}} % example
\newcommand{\para}[1]{\medskip\noindent\textbf{#1~---}} % paragraph
\newcommand{\subpara}[1]{\smallskip\noindent\textit{#1.}} % paragraph
\definecolor{PineGreen}{RGB}{2,120,120} % pinegreen color
\definecolor{darkgreen}{RGB}{57,181,74} % darkgreen color
\renewcommand{\b}[1]{{\color{blue} #1}} % blue
\renewcommand{\r}[1]{{\color{red} #1}} % red
\newcommand{\g}[1]{{\color{darkgreen} #1}} % green
\newcommand{\defn}[1]{\textbf{\textsf{\color{PineGreen} #1}}} % emphasis of a definition
\usepackage{todonotes}
\newcommand{\nantel}[1]{\todo[color=red!30]{#1 \\ \hfill --- N.}}
\newcommand{\cesar}[1]{\todo[color=orange!30]{#1 \\ \hfill --- C.}}
\newcommand{\noemie}[1]{\todo[color=green!30]{#1 \\ \hfill --- N.}}
\newcommand{\vincent}[1]{\todo[color=blue!30]{#1 \\ \hfill --- V.}}

% permutations
\newcommand{\fS}{\mathfrak{S}} % symmetric group
\newcommand{\gdproduct}{\bullet} % global descent product
\newcommand{\gdshuffle}{\shuffle_\gdproduct} % global descent shuffle product
\newcommand{\gddeconcat}{\coproduct_\gdproduct} % global descent deconcatenation coproduct
\newcommand{\HS}{{\bk\fS}} % Hopf Algebra of permutations
\newcommand{\shiftedShuffle}{\,\bar\shuffle\,} % shifted shuffle
\newcommand{\convolution}{\star} % convolution

% pipe dreams
\input{pipeDreamsTikz}
% cross
%\newcommand{\cross}[1][black]{\raisebox{.1cm}{\pipeDreamMonoColor{#1}{black}{c}}}
\newcommand{\cross}[1][black]{\raisebox{-.15cm}{\includegraphics[scale=.9]{cross}}}
\newcommand{\crossBiColor}[2]{\raisebox{.1cm}{\pipeDreamBiColor{#1}{#2}{black}{c/l/r}}}
\newcommand{\NScross}[1][black]{\raisebox{-.15cm}{\includegraphics[scale=.9]{NScross}}}
\newcommand{\WEcross}[1][black]{\raisebox{-.15cm}{\includegraphics[scale=.9]{WEcross}}}
% elbow
%\newcommand{\elbow}[1][black]{\raisebox{.1cm}{\pipeDreamMonoColor{#1}{black}{e}}}
\newcommand{\elbow}[1][black]{\raisebox{-.15cm}{\includegraphics[scale=.9]{elbow}}}
\newcommand{\elbowBiColor}[2]{\raisebox{.1cm}{\pipeDreamBiColor{#1}{#2}{black}{e/l/r}}}
%\newcommand{\SEelbow}[1][black]{\raisebox{.1cm}{\pipeDreamBiColor{white}{#1}{black}{e/l/r}}}
\newcommand{\SEelbow}[1][black]{\raisebox{-.15cm}{\includegraphics[scale=.9]{SEelbow}}}
%\newcommand{\WNelbow}[1][black]{\raisebox{.1cm}{\pipeDreamBiColor{#1}{white}{black}{e/l/r}}}
\newcommand{\WNelbow}[1][black]{\raisebox{-.15cm}{\includegraphics[scale=.9]{WNelbow}}}
\newcommand{\waving}{\mathsf{wav}}%{\raisebox{-.2cm}{\begin{tikzpicture}[scale=1]\pipeDreamBiColor{.2}{(0,0)}{black}{white}{{t/r/l},{t/l/l},{t/l/r}}\end{tikzpicture}}}
\newcommand{\transpose}{\mathsf{transp}}
\newcommand{\pipeDreams}{\Pi} % set of pipe dreams
\newcommand{\HP}{{\bk\pipeDreams}} % Hopf Algebra of pipe dreams
\newcommand{\reversingPipeDreams}{\Omega} % reversing pipe dreams
\newcommand{\contact}{^\#} % contact graph
\newcommand{\se}{\textsc{se}} % south-east
\newcommand{\nw}{\textsc{nw}} % north-west
\newcommand{\insertion}[2]{\mathsf{ins}(#1,#2)} % insertion of permutation #1 in pipe dreams with permutation #2
\newcommand{\duality}{^\star} % duality pipe dreams - triangulations
\newcommand{\acyclicPipeDreams}{\Sigma} % acyclic pipe dreams
\newcommand{\wo}{w_\circ} % longest element
\newcommand{\subwordComplex}{\mathcal{SC}} % subword complex
\newcommand{\Roots}{\mathrm{R}} % root configuration
\newcommand{\linearExtensions}{\mathcal{L}} % linear extensions
\newcommand{\noninversions}[2]{\mathsf{ninv}(#1,#2)} % non-inversions
\newcommand{\acyclicOrientations}{\Omega} % set of pipe dreams
\newcommand{\recoils}[2]{\mathsf{rec}(#1,#2)} % recoil scheme of a pipe dream
\newcommand{\canopy}[1]{\mathsf{can}(#1)} % canopy of a pipe dream

% lattices
\newcommand{\meet}{\wedge} % meet
\newcommand{\join}{\vee} % join
\newcommand{\less}{\vartriangleleft} % smaller WOIP
\newcommand{\more}{\vartriangleright} % larger WOIP
\newcommand{\contactLess}[1]{\less_{#1}} % smaller contact graph
\newcommand{\contactMore}[1]{\more_{#1}} % larger contact graph
\newcommand{\projDown}{\pi_\downarrow} % Down projection
\newcommand{\projUp}{\pi^\uparrow} % Down projection

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{abstract}
We show that for any permutation~$\omega$, the increasing flip graph on acyclic pipe dreams with permutation~$\omega$ is a lattice quotient of the interval~$[e,\omega]$ of the weak order.
\end{abstract}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The purpose of this note is to show that for any permutation~$\omega$, the increasing flip graph on acyclic pipe dreams with permutation~$\omega$ is a lattice quotient of the interval~$[e,\omega]$ of the weak order. It motivates Conjecture~\ref{conj:Coxeter} which is the long-term perspective of this work. The approach and proofs developed here are direct adaptations from~\cite[Sect.~1]{Pilaud-BrickAlgebra}.

\section{Preliminaries}
\label{sec:preliminaries}

% Let $\fS_n$ denote the set of permutations of~$[n] \eqdef \{1,2,\ldots,n\}$, and let~$\fS \eqdef \bigsqcup_{n \ge 0} \fS_n$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Pipe dreams}
\label{subsec:pipeDreams}

A \defn{pipe dream}~$P$ is a filling of a triangular shape with crosses~\cross{} and elbows~\elbow{} so that all pipes entering on the left side exit on the top side. We only consider \defn{reduced} pipe dreams, where two pipes have at most one intersection. We label the pipes with~$1, 2, \dots, n$ in the order of their entry points from top to bottom. We denote by~$\omega_P \in \fS_n$ the order of the exit points of the non-zero pipes of~$P$ from left to right. In other words, the pipe entering at row~$i$ exits at column~$\omega^{-1}_P(i)$. For a fixed permutation~$\omega \in \fS_n$, we denote by~$\pipeDreams(\omega)$ the set of reduced pipe dreams~$P$ such that~$\omega_P = \omega$.
% We let~$\pipeDreams_n \eqdef \bigsqcup_{\omega \in \fS_n} \pipeDreams(\omega)$ and~$\pipeDreams \eqdef \bigsqcup_{n \in \N} \pipeDreams_n$.

\begin{figure}[ht]
	\centerline{
		%\input{pipeDreams}
		\includegraphics[scale=.9]{pipeDreams}
	}
	\caption{Two pipe dreams of~$\pipeDreams(1365724)$ connected by a flip (exchanging an elbow with the crossing on the two red pipes~$3$ and~$4$).}
	\label{fig:pipeDreams}
\end{figure}

Two pipe dreams are related by a \defn{flip} if they define the same permutation of the pipes and only differ by the position of a cross and an elbow. An elbow~$e$ in a pipe dream~$P$ is \defn{flippable} if the two pipes passing through elbow~$e$ have a crossing~$c$, and the flip exchanges the elbow~$e$ with the cross~$c$. See \fref{fig:pipeDreams}. The flip is \defn{increasing} if the elbow~$e$ is weakly south-west of the crossing~$c$. For example, the flip of \fref{fig:pipeDreams} is increasing from left to right.

The \defn{contact graph} of a pipe dream~$P$ is the directed graph~$P\contact$ with one node for each pipe of~$P$ and one arc for each elbow of~$P$ connecting the north-west path to the south-east path of the elbow\footnote{We have reversed the usual orientation conventions to suit better our purposes, in particular in Section~\ref{subsec:insertionAlgorithm}.}. We see equivalently the contact graph~$P\contact$ as a graph on the pipes of~$P$ or on the integers~$[n]$. We say that a pipe dream~$P$ is \defn{acyclic} if its contact graph~$P\contact$ is (no oriented cycle). We then denote by~$\contactLess{P}$ the transitive closure of the contact graph of~$P$. For~$\omega \in \fS_n$, we denote by~$\acyclicPipeDreams(\omega)$ the set of acyclic pipe dreams of~$\pipeDreams(\omega)$.
% We let~$\acyclicPipeDreams_n \eqdef \bigsqcup_{\omega \in \fS_n} \acyclicPipeDreams(\omega)$ and~$\acyclicPipeDreams \eqdef \bigsqcup_{n \in \N} \acyclicPipeDreams_n$.
%\vincent{Add contact graphs to \fref{fig:pipeDreams}.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Reversing pipe dreams}
\label{subsec:reversingPipeDreams}

We say that a pipe dream~$P \in \pipeDreams_n$ is \defn{reversing} if it fixes the first pipe and reverses the order of the remaining pipes, \ie if~$\omega_P = [1, n, n-1, \dots, 2]$ (in one-line notation). We denote by~$\reversingPipeDreams_n$ the reversing pipe dreams of~$\pipeDreams_n$. As observed by different authors~\cite{Woo, PilaudPocchiola, Pilaud-these, Stump}, the pipe dreams of~$\reversingPipeDreams_n$ belong to the Catalan family. \fref{fig:bijection} illustrates explicit bijections between the pipe dreams of~$\reversingPipeDreams_n$, the binary trees on $n$ vertices, and the triangulations of a convex $(n+2)$-gon.

\begin{figure}[h]
	\centerline{\includegraphics[scale=1.3]{dualiteTriangulation}}
	\caption{The bijection between reversing pipe dreams (left), binary trees (middle) and triangulations (right).}
	\label{fig:bijection}
\end{figure}

More precisely, the map which sends an elbow in row~$i$ and column~$j$ of the triangular shape to the diagonal~$[i,n+1-j]$ of the~$(n+2)$-gon provides the following correspondence:
\begin{center}
\begin{tabular}{r@{$\quad\longleftrightarrow\quad$}l}
pipe dream~$P \in \reversingPipeDreams_n$ & triangulation~$P\duality$ of the $(n+2)$-gon, \\
$i$th pipe of~$P$ & $i$th triangle of~$P\duality$ (with central vertex~$i$), \\
elbows of~$P$ & diagonals of~$P\duality$, \\
crosses of~$P$ & common bisectors between triangles of~$P\duality$, \\
contact graph of~$P$ & dual binary tree of~$P\duality$, \\
elbow flips in~$P$ & diagonal flips in~$P\duality$.
\end{tabular}
\end{center}

\begin{remark}
All reversing pipe dreams are acyclic. Indeed, there contact graphs are (oriented) binary trees, which are certainly acyclic.
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Subword complexes}
\label{subsec:subwordComplexes}

Pipe dreams are a very particular family of the family of subword complexes. Consider a Coxeter system~$(W,S)$, where~$W$ is a finite Coxeter group and~$S$ is the set of simple reflections of~$W$. We denote by~$e$ (resp.~$\wo$) the identity (resp.~longest element) of~$W$. Let~$Q \eqdef q_1 \dots q_m \in S^*$ be a word on the alphabet formed by the simple generators of~$W$ and~$w \in W$. The \defn{subword complex}~$\subwordComplex(Q,w)$ is the simplicial complex whose ground set~$[m]$ are the positions in~$Q$ and whose facets are the complements of the reduced expressions for~$w$ in~$Q$.

It is known that~$\subwordComplex(Q,w)$ is either a ball or a sphere, in particular it is a pseudomanifold (with or without boundary). The flip graph of~$\subwordComplex(Q,w)$ is the graph whose vertices are the facets of~$\subwordComplex(Q,w)$ and whose edges are the ridges of~$\subwordComplex(Q,w)$. If~$F,F'$ are two adjacent facets with~$F \ssm \{p\} = F' \ssm \{p'\}$, we say that the flip is \defn{increasing} when~$p < p'$. The increasing flip graph was studied in particular in~\cite{PilaudStump-ELlabelings}. It is known to be acyclic, and its transitive closure is an EL-shellable poset (see~\cite{PilaudStump-ELlabelings} for the precise definition and references).

There is also a notion of acyclicity for subword complexes. It is based on the notion of \defn{root configuration}~$\Roots(F)$ of a facet~$F$ of~$\subwordComplex(Q,w)$. We skip the details and refer to~\cite{CeballosLabbeStump, PilaudStump-brickPolytope} for details. The facet~$F$ is \defn{acyclic} if its root configuration is pointed (meaning that it generates a pointed cone).

\begin{example}
Consider the symmetric group~$\fS_{n+1}$ generated by the set of simple transpositions $\set{\tau_i}{i \in [n]}$ where~$\tau_i \eqdef (i \; i+1)$.
For a permutation~$\omega \in \fS_{n+1}$, the pipe dreams of~$\pipeDreams(\omega)$ correspond to the facets of the subword complex~$\subwordComplex(Q,\omega)$ with~$Q = \tau_1, \tau_2, \dots, \tau_n, \tau_1, \tau_2, \dots, \tau_{n-1}, \dots, \tau_1, \tau_2, \tau_1$. % The notions of flips, increasing flips and acyclic pipe dreams transpose in the world of subword complexes.
\end{example}

\begin{example}
For any Coxeter group~$W$ and any Coxeter element~$c \in W$ (a product of all generators of~$S$ in a given arbitrary order), let~$\wo(c)$ denote the $c$-sorting word of~$\wo$ (see \cite{Reading-CambrianLattices} for details). Extending the observation of Section~\ref{subsec:reversingPipeDreams}, it was shown in~\cite{CeballosLabbeStump} that the subword complex~$\subwordComplex(c\wo(c), \wo)$ is isomorphic to the cluster complex of type~$W$. In particular, the increasing flip graph is the Hasse diagram of the $c$-Cambrian lattice of~\cite{Reading-CambrianLattices}.
\end{example}

In contrast to the previous example, consider the word~$Q = \tau_1 \tau_2 \tau_3 \tau_2 \tau_1 \tau_2 \tau_3 \tau_2 \tau_1$ on the simple generators of the symmetric group~$\fS_4$ and the subword complex~$\subwordComplex(Q,\wo)$. Note that all facets in this subword complex are acyclic. It is shown in~\cite[Rem.~5.12]{PilaudStump-brickPolytope} that its increasing flip poset is not a lattice. This shows that neither the increasing flip poset, nor the acyclic increasing flip poset are lattices in general, even in type~$A$. In this note, we investigate the case of acyclic pipe~dreams.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Elementary properties of pipe dreams}
\label{subsec:elementaryProperties}

We gather in this section some elementary properties of pipe dreams needed later.

\begin{lemma}
\label{lem:horiVertCrossings}
For any pipe dream~$P \in \pipeDreams(\omega)$, the pipe~$j$ of~$P$ (which enters at row~$j$ and exits at column~$\omega^{-1}(j)$) crosses
\begin{itemize}
\item vertically the pipes~$i$ such that~$i < j$ while~$\omega^{-1}(i) > \omega^{-1}(j)$,
\item horizontally the pipes~$k$ such that~$j < k$ while~$\omega^{-1}(j) > \omega^{-1}(k)$.
\end{itemize}
\end{lemma}

\begin{proof}
For~$i < j$, if~$\omega^{-1}(i) > \omega^{-1}(j)$, then the pipes~$i$ and~$j$ have to cross exactly once, while if~$\omega^{-1}(i) < \omega^{-1}(j)$ the pipes~$i$ and~$j$ cannot cross. The same argument applies for~${k > j}$.
\end{proof}

\begin{lemma}
\label{lem:countingElbows}
For any pipe dream~$P \in \pipeDreams(\omega)$, the pipe~$j$ (which enters at row~$j$ and exits at column~$\omega^{-1}(j)$) has precisely
\begin{itemize}
\item $\noninversions{\omega}{j}$ many \se{} elbows\!\SEelbow{}
\item $1+\noninversions{\omega}{j}$ many \nw{} elbows~\WNelbow{}
\item $j-1-\noninversions{\omega}{j}$ vertical crossings~\NScross
\item $\omega^{-1}(j)-1-\noninversions{\omega}{j}$ horizontal crossings~\WEcross
\end{itemize}
where~$\noninversions{\omega}{j} \eqdef |\set{i \in [n]}{i < j \text{ and } \omega^{-1}(i) < \omega^{-1}(j)}|$.
\end{lemma}

\begin{proof}
Pipe~$j$ enters at row~$j$ and exits at column~$\omega^{-1}(j)$, so that it passes through~$j+\omega^{-1}(j)-1$ grid points. By Lemma~\ref{lem:horiVertCrossings}, it has~$|\set{i \in [n]}{i < j \text{ and } \omega^{-1}(i) > \omega^{-1}(j)}| = j-1-\noninversions{\omega}{j}$ vertical crossings and~$|\set{k \in [n]}{j < k \text{ and } \omega^{-1}(j) > \omega^{-1}(k)}| = \omega^{-1}(j)-1-\noninversions{\omega}{j}$ horizontal crossings. The~$1+2\,\noninversions{\omega}{j}$ remaining grid points along the pipe~$j$ are thus alternating north-west elbows and south-east elbows.
\end{proof}

\begin{lemma}
\label{lem:characterizationPipeDreams}
A collection~$P$ of~$n$ pipes pairwise disjoint except at crossing and elbows and such that for each~$j \in [n]$, the pipe~$j$ enters at row~$j$, exits at column~$\omega^{-1}(j)$, and has~$\noninversions{\omega}{j}$ \se{} elbows is a pipe dream of~$\pipeDreams(\omega)$.
\end{lemma}

\begin{proof}
The argument is similar to the previous lemma. Observe first that the pipe~$j$ must cross the paths~$i$ such that~$i < j$ and~$\omega^{-1}(i) > \omega^{-1}(j)$ and the paths~$k$ such that~$j < k$ and~$\omega^{-1}(j) > \omega^{-1}(k)$. Moreover, it has~$\noninversions{\omega}{j}$ \se{} elbows and thus~$1+\noninversions{\omega}{j}$ \nw{} elbows. This already exhausts all~$j+\omega^{-1}(j)-1$ grid points of~$j$. Therefore, the pipe~$j$ can only cross at most once any other pipe.
\end{proof}

\begin{lemma}
\label{lem:rectangle}
Let~$P$ be a pipe dream and~$p,q$ be pipes of~$P$. If there is a elbow of~$p$ weakly north-west of a elbow~$q$, then~$p \contactLess{} q$ (\ie there is an oriented path from~$p$ to~$q$ in the contact graph~$P\contact$ of~$P$).
\end{lemma}

\begin{proof}
Let~$x$ (reps.~$y$) be the location of a elbow of~$p$ (resp.~$q$) such that~$x$ is weakly north-west of~$y$. We proceed by induction on the grid distance from~$x$ to~$y$. If they coincide, then~$p$ and~$q$ share a elbow, so that there is an edge from~$p$ to~$q$ in~$P\contact$. Otherwise, let~$r$ be the pipe of~$P$ with a south-east elbow at~$x$ ($r$ is either the pipe~$p$ itself, or there is an edge from~$p$ to~$r$ in~$P\contact$) and~$s$ be the pipe of~$P$ with a north-west elbow at~$y$ ($s$ is either the pipe~$q$ itself, or there is an edge from~$s$ to~$q$ in~$P\contact$). Let~$R$ be the axis-parallel rectangle with elbows~$x$ and~$y$. Since~$r$ and~$s$ cross at most once, at least one of them has an additional elbow along the sides of~$R$. Assume for instance that~$r$ has an elbow at~$x'$. Then~$x'$ is still weakly northwest of~$y$ and $x',y$ are strictly closer than~$x,y$. By induction, there is a path from~$r$ to~$s$ in~$P\contact$, and thus a path form~$p$ to~$q$.
\end{proof}

Note that the reciprocal assertion of Lemma~\ref{lem:rectangle} is false.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Three equivalent partitions}
\label{sec:partitions}

Remember that the \defn{weak order} on~$\fS_n$ is defined as the inclusion order of inversions, where an inversion of~$\pi \in \fS_n$ is a pair of values~$i, j \in \N$ such that~$i < j$ while~$\pi^{-1}(i) > \pi^{-1}(j)$. Fix a permutation~$\omega \in \fS_n$, and let~$[e, \omega] \eqdef \set{\pi \in \fS_n}{\pi \le \omega}$ denote the weak order interval between the identity~$e$ and~$\omega$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Linear extensions of contact graphs}
\label{subsec:linearExtensions}

Consider an acyclic pipe dream~$P$. Recall that we denote by~$\contactLess{P}$ the transitive closure of the contact graph~$P\contact$ of~$P$. We denote by~$\linearExtensions(P)$ the set of linear extensions of~$P\contact$ (\ie $\pi \in \linearExtensions(P)$ if and only if~$\pi^{-1}(i) < \pi^{-1}(j)$ for all~$i \to j$ in~$P\contact$). We often say abusively that the permutations of~$\linearExtensions(P)$ are linear extensions of~$P$. In this section, we prove certain structural properties of~$\linearExtensions(P)$. The following definitions of weak order intervals and weak order interval posets are connected in the Proposition~\ref{prop:WOIP} proved by A.~Bjorner and M.~Wachs~\cite{BjornerWachs}, see also~\cite{ChatelPilaudPons}.

\begin{definition}
\label{def:WOIP}
A \defn{weak order interval (WOI)} is a subset~$[\tau, \tau']$ of~$\fS_n$ consisting of all permutations~$\sigma \in \fS_n$ such that~$\tau \le \sigma \le \tau'$ in weak order. A \defn{weak order interval poset (WOIP)} is a poset~$\less$ on~$[n]$ such that for all~$a < b < c$,
\[
a \less c \implies a \less b \text{ or } b \less c 
\qquad\text{and}\qquad
a \more c \implies a \more b \text{ or } b \more c.
\]
\end{definition}

\begin{proposition}[\protect{\cite[Thm.~6.8]{BjornerWachs}}]
\label{prop:WOIP}
The WOIs are the sets of linear extensions of WOIPs:
\begin{enumerate}[(i)]
\item the WOI~$[\tau, \tau']$ is the set of linear extensions of the WOIP obtained as the transitive closure of the relations~$i \less j$ for all non coinversions~$i,j$ of~$\tau$ and~$i \more j$ for all coinversions~$i,j$~of~$\tau'$;
\item the linear extensions of a WOIP~$\less$ is the WOI~$[\tau,\tau']$, where~$\tau$ and~$\tau'$ are respectively the greedy and antigreedy linear extensions of~$\less$.
\end{enumerate}
\end{proposition}

We use this characterization to prove the following statement.

\begin{proposition}
\label{prop:intervals}
For any pipe dream~$P \in \acyclicPipeDreams(\omega)$, the set~$\linearExtensions(P)$ is an interval of the weak order.
\end{proposition}

\begin{proof}
We just need to show that the poset~$\contactLess{P}$ satisfies the WOIP condition.
Consider~$a < b < c$ such that~$a \contactLess{P} c$. If~$\omega^{-1}(a) < \omega^{-1}(b)$, we know from Lemma~\ref{lem:rectangle} that~$a \contactLess{P} b$. Similarly, if~$\omega^{-1}(b) < \omega^{-1}(c)$, we have~$b \contactLess{P} c$. We can therefore assume that~$\omega^{-1}(a) > \omega^{-1}(b) > \omega^{-1}(c)$. Assume moreover that~$a \contactLess{T} c$. Decompose the triangular shape into three regions: the region~$A$ of all points located south-west of the first elbow of the pipe~$b$ of~$P$, the region~$B$ of all points located north-west or south-east of an elbow of the pipe~$b$ of~$P$, and the region~$C$ of all points located north-east of the last elbow of the pipe~$b$ of~$P$. Since~$a \contactLess{T} c$, there is a path~$\pi$ form the entering point of the pipe~$a$ of~$P$ to the exiting point of the pipe~$c$ of~$P$ which travels along the pipes and the elbows of~$P$. Since~$a < b < c$, the path~$\pi$ starts in region~$A$ and ends in region~$C$, so that it necessarily passes from region~$A$ to region~$C$. Since the north-east corner of~$A$ is located south-west of the south-west corner of~$C$, this forces an elbow~$e$ of~$\pi$ to lie in region~$B$. Lemma~\ref{lem:rectangle} then ensures that either~$a \contactLess{T} b$ (if~$e$ is above the pipe~$b$), or~$b \contactLess{T} c$ (if~$e$ is below the pipe~$b$). The proof is similar if~$a \contactMore{T} c$.
\end{proof}

In the next two statements, we show that the sets~$\linearExtensions(P)$ partition an interval of the weak order.

\begin{lemma}
\label{lem:interval}
For any linear extension~$\pi$ of a pipe dream~$P \in \pipeDreams(\omega)$, we have~$\pi \le \omega$ in weak order.
\end{lemma}

\begin{proof}
Consider a non-inversion of~$\omega$, \ie~$(i,j) \in [n]^2$ such that~$i < j$ and~$\omega^{-1}(i) < \omega^{-1}(j)$. Since~$i < j$ and~$\omega^{-1}(i) < \omega^{-1}(j)$, the pipes~$i$ and~$j$ do not cross. Therefore, the path~$j$ passes south-east of any elbow of the path~$i$. This shows that~$i \contactLess{P} j$ by Lemma~\ref{lem:rectangle}. Therefore, $\pi^{-1}(i) < \pi^{-1}(j)$ for any linear extension~$\pi$ of~$P$. In other words, $(i,j)$ is also a non-inversion of~$\pi$. We conclude that all linear extensions \mbox{of~$P$ are smaller than~$\omega$ in weak order}.
\end{proof}

\begin{proposition}
\label{prop:partition}
The collection~$\set{\linearExtensions(P)}{P \in \acyclicPipeDreams(\omega)}$ forms a partition of the interval~$[e,\omega]$ of the weak order.
\end{proposition}

\begin{proof}
\vincent{There are other methods to prove this without using the sweeping algorithm... We will actually do this for arbitrary subword complexes.}
By Lemma~\ref{lem:interval}, all linear extensions belong to the interval~$[e,\omega]$.

We now show that~$\linearExtensions(P) \cap \linearExtensions(P') = \varnothing$ for any two distinct acyclic pipe dreams~$P, P' \in \pipeDreams(\omega)$. For this, we show that we can reconstructing a pipe~$P$ knowing a linear extension~$\pi \in \linearExtensions(P)$. For this, we sweep the pipe dream in any perturbation of the \nw{} direction (meaning that we sweep the grid in any order such that each point is swept before all points weakly \nw of~$p$). When we sweep a vertex~$v$ of the grid, we see a pipe~$p$ arriving horizontally at~$v$ and a pipe~$q$ arriving vertically at~$v$. If~$p > q$, then $p$ and~$q$ already crossed before, so we have no choice but imposing an elbow at~$v$. If~$p < q$, there are three situations:
\begin{itemize}
\item if~$\pi^{-1}(p) > \pi^{-1}(q)$ then~$p$ and~$q$ cannot touch (otherwise $\pi$ would not be a linear extension of~$P$), so that we have no choice but imposing a crossing~at~$v$,
\item if~$\omega^{-1}(p) < \omega^{-1}(q)$, then~$p$ and~$q$ cannot cross (otherwise~$P$ would not be a pipe dream of~$\pipeDreams(\omega)$), so that we have no choice but imposing a contact at~$v$,
\item if~$\pi^{-1}(p) < \pi^{-1}(q)$ and~$\omega^{-1}(p) > \omega^{-1}(q)$, then we have again two situations;
	\begin{itemize}
	\item If $q$ needs to go straight north, then we have no choice but imposing a crossing at~$v$,
	\item Otherwise, we have no choice but imposing an elbow at~$v$. Indeed, if there is a crossing at~$v$, then Lemma~\ref{lem:rectangle} ensures that~$q$ will be below~$p$ in~$P\contact$, so that~$\pi$ would not be a linear extension of~$P$.
	\end{itemize}
\end{itemize}

%Several arguments could be invoked, as for example the insertion algorithm discussed in Section~\ref{subsec:insertionAlgorithm}. We prefer here to recall from~\cite{PilaudPocchiola} that one can reconstruct a pipe dream~$P$ by sweeping the triangular shape in any slight perturbation of the north-east direction. When we sweep a vertex~$v$ of the grid, we see a pipe~$p$ arriving horizontally at~$v$ and a pipe~$q$ arriving vertically at~$v$. If~$p > q$, then $p$ and~$q$ already crossed before, so we have no choice but imposing an elbow at~$v$. If~$p < q$, there are two situations:
%\begin{itemize}
%\item if~$p \not\contactLess{P} q$ then~$p$ and~$q$ cannot touch, so that we have no choice but imposing a crossing~at~$v$,
%\item if~$\omega^{-1}(p) < \omega^{-1}(q)$, then~$p$ and~$q$ cannot cross, so that we have no choice but imposing a contact at~$v$,
%\item if~$p \contactLess{P} q$ and~$\omega^{-1}(p) > \omega^{-1}(q)$, then we have again two situations;
%	\begin{itemize}
%	\item If $q$ needs to go straight north, then we have no choice but imposing a crossing at~$v$,
%	\item Otherwise, we have no choice but imposing an elbow at~$v$. \qedhere
%	\end{itemize}
%\end{itemize}

To conclude the proof, we need to show that any permutation of~$[e,\omega]$ is a linear extension of some pipe dream~$P \in \acyclicPipeDreams(\omega)$. This is done using an insertion algorithm presented next.
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Insertion algorithm}
\label{subsec:insertionAlgorithm}

We now define a surjective map from the permutations of~$[e, \omega]$ to the pipe dreams of~$\acyclicPipeDreams(\omega)$. This map, adapted from~\cite{Pilaud-BrickAlgebra}, is obtained by an insertion process similar to the insertion in binary search trees. 
%To properly describe this insertion algorithm, we introduce additional notations.
We now describe this insertion algorithm, which is illustrated in \fref{fig:insertionAlgorithm}.

Consider a given permutation~$\pi \eqdef \pi(1) \dots \pi(n)$ (written in one-line notation) in~$[e, \omega]$. We start from the empty triangular shape and insert the pipes~$\pi(1), \dots, \pi(n)$ one by one in the order of the permutation~$\pi$ as \nw{} as possible. In other words, at step~$t$, we consider the set~$X_t$ of free \nw{} elbows in the rectangle~$[\pi(t)] \times [\omega^{-1}(\pi(t))]$. The pipe inserted at step~$t$ then starts in row~$\pi(t)$, ends in column~$\omega^{-1}(\pi(t))$, covers each elbow of~$X_t$ with a \se{} elbow, and adds just one new free \nw{} elbow in between any two consecutive elbows of~$X_t$. We denote the resulting pipe dream by~$\insertion{\pi}{\omega}$. See \fref{fig:insertionAlgorithm}.

\begin{figure}[b]
	\centerline{
		\includegraphics[scale=.9]{insertion}
	}
	\caption{The insertion~$\insertion{513264}{561324}$.}
	\label{fig:insertionAlgorithm}
\end{figure}

We need to argue that this algorithm indeed creates a pipe dream of~$\acyclicPipeDreams(\omega)$. To see it, we observe that the following invariant is maintained throughout the algorithm.

\begin{lemma}
\label{lem:rectangleInsertionAlgorithm}
At each step~$t$ of the insertion algorithm, we have
\[
|X_t| = \big| \bigset{s < t}{\pi(s) < \pi(t) \text{ and } \omega^{-1}\big( \pi(s) \big) < \omega^{-1}\big( \pi(t) \big)} \big|.
\]
\vincent{Note that this is independent of~$\pi$... This can be seen from Lemma~\ref{lem:interval}.}
\end{lemma}

\begin{proof}
Fix~$t \in [n]$. At the beginning of the algorithm, there is no \se{} elbow in the rectangle~$R_t \eqdef [\pi(t)] \times [\omega^{-1}(\pi(t))]$. At each step~$s < t$, we have inserted a new pipe~$\pi(s)$ which enters at~$\pi(s)$ and exits at~$\omega^{-1}\big( \pi(s) \big)$. We conclude by considering the four possible cases:
\begin{itemize}
\item If~$\pi(s) < \pi(t)$ and~$\omega^{-1}\big( \pi(s) \big) < \omega^{-1}\big( \pi(t) \big)$, then the pipe~$\pi(s)$ is completely contained in the rectangle~$R_t$. Since the pipe~$\pi(s)$ has one more \nw{} elbow than \se{} elbow, its insertion creates a new free \nw{} elbow in the rectangle~$R_t$.
\item If~$\pi(s) < \pi(t)$ and~$\omega^{-1}\big( \pi(s) \big) > \omega^{-1}\big( \pi(t) \big)$, then the pipe~$\pi(s)$ enters and exits the rectangle~$R_t$ with an horizontal step, so that it has as many \nw{} and \se{} elbows in~$R_t$, and its insertion does not modify the number of free \nw{} elbows in the rectangle~$R_t$.
\item If~$\pi(s) > \pi(t)$ and~$\omega^{-1}\big( \pi(s) \big) < \omega^{-1}\big( \pi(t) \big)$, then the pipe~$\pi(s)$ enters and exits the rectangle~$R_t$ with a vertical step, so that it has as many \nw{} and \se{} elbows in~$R_t$, and its insertion does not modify the number of free \nw{} elbows in the rectangle~$R_t$.
\item If~$\pi(s) > \pi(t)$ and~$\omega^{-1}\big( \pi(s) \big) > \omega^{-1}\big( \pi(t) \big)$, then setting~$i = \pi(t)$ and~$j = \pi(s)$, we have~$i < j$ and~$\pi^{-1}(i) > \pi^{-1}(j)$ while~$\omega^{-1}(i) < \omega^{-1}(j)$, which contradicts our assumption that~$\pi \not< \omega$ in weak order. \qedhere
\end{itemize}
\end{proof}

\begin{corollary}
For any~$\pi \le \omega$, the insertion algorithm creates a pipe dream~$\insertion{\pi}{\omega}$ of~$\pipeDreams(\omega)$.
\end{corollary}

\begin{proof}
The algorithm constructs a collection~$P$ of $n$ pairwise disjoint pipes except at crossings and elbows. For each~$t \in [n]$, the pipe~$\pi(t)$ enters at~$\pi(t)$, exits at~$\omega^{-1}\big( \pi(t) \big)$, and has 
\[
\big| \bigset{s < t}{\pi(s) < \pi(t) \text{ and } \omega^{-1}\big( \pi(s) \big) < \omega^{-1}\big( \pi(t) \big)} \big| = \noninversions(\omega, \pi(t))
\]
many $\se$ elbows by Lemma~\ref{lem:rectangleInsertionAlgorithm} and since~$\pi < \omega$ in weak order. We thus conclude the proof by a direct application of Lemma~\ref{lem:characterizationPipeDreams}.
\vincent{Maybe we should argue that the pipes remain in the triangle.}
\end{proof}

\begin{proposition}
\label{prop:fibersInsertion}
For any pipe dream~$P \in \acyclicPipeDreams(\omega)$,  the permutations~$\pi \le \omega$ such that~$\insertion{\pi}{\omega} = P$ are precisely the linear extensions of the contact graph~$P\contact$ of~$P$. In particular, $\insertion{\cdot}{\omega}$ is a surjection from~$[e, \omega]$ to~$\acyclicPipeDreams(\omega)$.
\end{proposition}

\begin{proof}
By construction of the insertion algorithm, all \se{} elbows of the pipe~$\pi(t)$ inserted at step~$t$ are in contact with \nw{} elbows of pipes~$\pi(s)$ inserted at steps~$s < t$. In other words, all edges in the contact graph of~$\insertion{\pi}{\omega}$ are of the form~$\pi(s) \to \pi(t)$ for some~$s < t$. It follows that the permutation~$\pi$ is a linear extension of~$\insertion{\pi}{\omega}$. Reciprocally, consider a linear extension~$\pi$ of a pipe dream~$P$. Then~$\insertion{\pi}{\omega}$ and~$P$ have a common linear extension~$\pi$, so that~$\insertion{\pi}{\omega} = P$ by Proposition~\ref{prop:partition}.
\end{proof}

In other words, the sets~$\set{\linearExtensions(P)}{P \in \acyclicPipeDreams(\omega)}$ are the fibers of the surjective insertion map~$\insertion{\cdot}{\omega}$. Note that this concludes the proof of the surjectivity left open in Proposition~\ref{prop:partition}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Pipe dream congruence}
\label{subsec:pipeDreamCongruence}

We now characterize the sets of linear extensions of pipe dreams in terms of a rewriting rule. We write the permutations of~$\fS_n$ as words in one-line notation.

\begin{definition}
\label{def:congruence}
For any permutation~$\omega \in \fS_n$, the \defn{pipe dream congruence} is the equivalence relation~$\equiv_\omega$ on the interval~$[e,\omega]$ of the weak order defined as the transitive closure of the rewriting rule~$U ac V \equiv_\omega U ca V$ if and only if
\[
|\set{b \in U}{a < b < c \text{ and } \omega^{-1}(a) > \omega^{-1}(b) > \omega^{-1}(c)}| \ge |\set{b < a}{\omega^{-1}(b) < \omega^{-1}(c)}|,
\]
\vincent{Note that $b \in U$ on the right hand side by Lemma~\ref{lem:interval}.}
where~$a, b, c$ are elements of~$[n]$ while~$U, V$ are (possibly empty) words on~$[n]$. The letters~$b \in U$ such that~$a < b < c$ while~$\omega^{-1}(a) > \omega^{-1}(b) > \omega^{-1}(c)$ are called \defn{pipe dream congruence witnesses} for the exchange of~$a$ and~$c$.
\vincent{Another option to write this is $d \ge u$ where $d \eqdef \set{b \in U}{b > a}$ and~$u \eqdef \set{b \in U}{\omega^{-1}(b) < \omega^{-1}(c)}$. Or $dr \ge \ell u$ where $dr \eqdef \set{b \in U}{b > a \text{ and } \omega^{-1}(b) > \omega^{-1}(c)}$ and~$\ell u \eqdef \set{b \in U}{b < a \text{ and } \omega^{-1}(b) < \omega^{-1}(c)}$.}
\end{definition}

\begin{proposition}
\label{prop:congruence}
For any~$\pi, \pi' \in [e,\omega]$, we have~${\pi \equiv_\omega \pi' \!\iff\! \insertion{\pi}{\omega} = \insertion{\pi'}{\omega} \!\iff\! \pi}$~and~$\pi'$ are linear extensions of a same pipe dream.
\end{proposition}

\begin{proof}
By Proposition~\ref{prop:fibersInsertion}, each fiber of~$\insertion{\cdot}{\omega}$ gathers the linear extensions of a pipe dream of~$\pipeDreams(\omega)$. Since the set of linear extensions of a poset is connected by simple transpositions, we just need to show that~$\pi \equiv_\omega \pi' \!\iff\! \insertion{\pi}{\omega} = \insertion{\pi'}{\omega}$ for any two permutations~$\pi = UacV$ and~$\pi' = UcaV$ of~$[e,\omega]$ which differ by the inversion of two consecutive values.

Let~$t = \pi^{-1}(a) = \pi'{-1}(c)$. At step~$t$ of the algorithm presented in the previous section, we have inserted the word~$U$. At that moment, let~$X_t$ (resp.~$X'_t$, resp~$Y_t$) denote the set of free \nw{} elbows in the rectangle~$[a] \times [\omega^{-1}(a)]$ (resp.~$[c] \times [\omega^{-1}(c)]$, resp.~$[a] \times [\omega^{-1}(c)]$). Applying the same argument as in Lemma~\ref{lem:rectangleInsertionAlgorithm}, we have
\begin{gather*}
|Y_t| = \max\big( |\set{b \in U}{b < a \text{ and } \omega^{-1}(b) < \omega^{-1}(c)}| \hspace{5cm} \\ \hspace{5cm} - |\set{b \in U}{a < b < c \text{ and } \omega^{-1}(a) > \omega^{-1}(b) > \omega^{-1}(c)}|, 0\big).
\end{gather*}
It follows that~$U ac V \equiv_\omega U ca V \iff |Y_t| = 0$. However, $Y_t = 0$ if and only if all elbows of~$X_t$ are in~$[a] \times [\omega^{-1}(c), \omega^{-1}(a)]$ and all elbows of~$X'_t$ are in~$[a,c] \times [\omega^{-1}(c)]$. The latter is equivalent to the fact that the insertion of~$a$ and~$c$ commute. We conclude that
\[
U ac V \equiv_\omega U ca V \iff \insertion{UacV}{\omega} = \insertion{UcaV}{\omega},
\]
which concludes the proof since the set of linear extensions of a poset is connected by simple transpositions.
\end{proof}

\begin{proposition}
\label{prop:patternAvoiding}
The minimal (resp.~maximal) permutations in the partition
\(
{[e,\omega] = \bigsqcup_{P \in \acyclicPipeDreams(\omega)} \linearExtensions(P)}
\)
are the permutations avoiding the patterns~$b_1 - \cdots - b_k - ca$ (resp.~$b_1 - \cdots - b_k - ac$) where $k = |\set{b < a}{\omega^{-1}(b) < \omega^{-1}(c)}|$.
\end{proposition}

\begin{proof}
This is an immediate consequence of Proposition~\ref{prop:congruence}: a permutation~$\pi$ is minimal (resp.~maximal) in its $\equiv_\omega$-congruence class if and only if it contains no consecutive exchangeable entries~$ca$ (resp.~$ac$) with~$a < c$.
\end{proof}

To sum up, there are three equivalent ways to partition the interval~$[e,\omega]$ of the weak order:
\vincent{In fact, we should write 4 different ways, the last one being the sweeping algorithm.}
\begin{itemize}
\item by the sets of linear extensions~$\linearExtensions(P)$ of all pipe dreams of~$\acyclicPipeDreams(\omega)$,
\item by the fibers of the insertion map~$\insertion{\cdot}{\omega}$,
\item by the classes of the pipe dream congruence~$\equiv_\omega$.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Lattice of acyclic pipe dreams}
\label{sec:latticeAcyclicPipeDreams}

Based on the result of the previous section, we now show that the pipe dream congruence~$\equiv_\omega$ is a lattice congruence of the interval~$[e,\omega]$ of weak order for any~$\omega \in \fS_n$. We extend the proof of~\cite{Pilaud-BrickAlgebra} which treated the particular case of~$\omega = [1, \dots, k, n-k, \dots, k+1, n-k+1, \dots, n]$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Lattice congruences and lattice quotients}
\label{subsec:latticeCongruences}

We first remind the reader with the definition of these congruences and refer to~\cite{Reading-LatticeCongruences, Reading-CambrianLattices} for further details.

An \defn{order congruence} is an equivalence relation~$\equiv$ on a poset~$P$ such that:
\begin{enumerate}[(i)]
\item Every equivalence class under~$\equiv$ is an interval of~$P$.
\item The projection~$\projDown : P \to P$ (resp.~$\projUp : P \to P$), which maps an element of~$P$ to the minimal (resp.~maximal) element of its equivalence class, is order preserving.
\end{enumerate}
The \defn{quotient}~$P/{\equiv}$ is a poset on the equivalence classes of~$\equiv$, where the order relation is defined by~$X \le Y$ in~$P/{\equiv}$ iff there exists representatives~$x \in X$ and~$y \in Y$ such that~$x \le y$ in~$P$. The quotient~$P/{\equiv}$ is isomorphic to the subposet of~$P$ induced by~$\projDown(P)$ (or equivalently by~$\projUp(P)$).

If moreover~$P$ is a finite lattice, then~$\equiv$ is a automatically \defn{lattice congruence}, meaning that it is compatible with meets and joins: for any~$x \equiv x'$ and~$y \equiv y'$, we have~$x \meet y \equiv x' \meet y'$ and~$x \join y \equiv x' \join y'$. The poset quotient~$P/{\equiv}$ then inherits a lattice structure where the meet~$X \meet Y$ (resp.~the join~$X \join Y$) of two congruence classes~$X$ and~$Y$ is the congruence classe of~$x \meet y$ (resp.~of~$x \join y$) for arbitrary representatives~$x \in X$ and~$y \in Y$.

%Lattice quotient of the weak order.
%Connection to the increasing flip poset.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{The pipe dream congruence is a lattice congruence}
\label{subsec:proofCongruence}

We are now ready to prove the main statement of this note. Recall that an interval in a lattice is itself a lattice, so that the weak order on~$[e,\omega]$ has a lattice structure.

\begin{theorem}
For any permutation~$\omega \in \fS_n$, the pipe dream congruence~$\equiv_\omega$ is a lattice congruence of the interval~$[e,\omega]$ of the weak order.
\end{theorem}

\begin{proof}
We already observed in Proposition~\ref{prop:intervals} that the $\equiv_\omega$-congruence classes are intervals of the weak order. We therefore just need to show that~$\tau < \tau'$ implies~$\min(C) < \min(C')$ and $\max(C) < \max(C')$ for any two permutations~$\tau, \tau' \in [e,\omega]$ from distinct $\equiv_\omega$-congruence classes~$C,C'$. We only prove the result for the maximums, the proof for the minimums being similar. We first observe that we can assume that~$\tau' = \tau s_i$ for some simple transposition~${s_i = (i \;\, i+1)}$ which is not a descent of~$\tau$. The proof then works by induction on the weak order distance between~$\tau$ and~$\max(C)$. If~$\tau = \max(C)$, the result is immediate as~$\max(C) = \tau < \tau' \le \max(C')$. Otherwise, consider a permutation~$\sigma$ in~$C$ covering~$\tau$ in weak order. We write~$\sigma = \tau s_j$, and $s_j$ is not a descent of~$\tau$. We now distinguish four cases, according to the relative positions of~$i$ and~$j$:
\begin{enumerate}[(1)]
\item If~$i > j+1$, we have~$\tau = UabVcdW$, $\tau' = UabVdcW$ and~$\sigma = UbaVcdW$ for some letters~$a < b$ with~$\omega^{-1}(a) > \omega^{-1}(b)$, some letters~$c < d$ with~$\omega^{-1}(c) > \omega^{-1}(d)$ and some words~$U,V,W$. Define~$\sigma' \eqdef \tau s_i s_j = \tau' s_j = \sigma s_i = UbaVdcW$. Since~$\tau \equiv_\omega \sigma$, there exist $k = |\set{u < a}{\omega^{-1}(u) < \omega^{-1}(b)}|$ $\equiv_\omega$-congruence witnesses~$u_1, \dots, u_k$ in the word~$U$, with~$a < u_\ell < b$ and~$\omega^{-1}(a) > \omega^{-1}(u_\ell) > \omega^{-1}(c)$ for all~$\ell \in [k]$. These letters are also $\equiv_\omega$-congruence witnesses for the equivalence~$\tau' \equiv_\omega \sigma'$. Moreover, $\sigma < \sigma'$ since~$c < d$.
\item If~$i = j+1$, we have~$\tau = UabcW$, $\tau' = UacbW$ and~$\sigma = UbacW$ for some letters~${a < b < c}$ with~$\omega^{-1}(a) > \omega^{-1}(b) > \omega^{-1}(c)$ (since~$\tau < \omega$ in weak order by asumption) and some words~$U,W$. Define~$\sigma' \eqdef \tau s_i s_j s_i = \tau' s_j s_i = \sigma s_i s_j = UcbaW$. Since~$\tau \equiv_\omega \sigma$, there exist $k = |\set{u < a}{\omega^{-1}(u) < \omega^{-1}(b)}|$ $\equiv_\omega$-congruence witnesses~$u_1, \dots, u_k$ in the word~$U$, with ${a < u_\ell < b}$ and~$\omega^{-1}(a) > \omega^{-1}(u_\ell) > \omega^{-1}(c)$ for all~$\ell \in [k]$. Since~$b < c$ and~$\omega^{-1}(b) > \omega^{-1}(c)$, these letters are also $\equiv_\omega$-congruence witnesses for the equivalences~${\tau' \equiv_\omega \tau' s_j \equiv_\omega \tau' s_j s_i = \sigma'}$. (Moreover, note that there are indeed enough witnesses for the equivalence~$\tau' \equiv_\omega \tau' s_j$ since ${k = |\set{u < a}{\omega^{-1}(u) < \omega^{-1}(b)}| \ge |\set{u < a}{\omega^{-1}(u) < \omega^{-1}(c)}|}$). Finally, since~$a < b < c$, we have~$\sigma < \sigma'$.
\item If~$i = j-1$, we proceed similarly as in Situation~(2).
\item If~$i < j-1$, we proceed similarly as in Situation~(1).
\end{enumerate}
In all cases, we have~$\tau \equiv_\omega \sigma < \sigma' \equiv_\omega \tau'$. Since~$\sigma$ is closer to~$\max(C)$ than~$\tau$, we obtain that ${\max(C) < \max(C')}$ by induction hypothesis.
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Lattice of acyclic pipe dreams}
\label{subsec:proofCongruence}

Finally, we need to show that the lattice quotient~$[e,\omega]/\equiv_\omega$ is isomorphic to the increasing flip poset on~$\acyclicPipeDreams(\omega)$. This is the purpose of the following statement.

\begin{proposition}
For any pipe dreams~$P, P' \in \acyclicPipeDreams(\omega)$, the following assertions are equivalent:
\begin{enumerate}[(i)]
\item $P < P'$ in the increasing flip poset on~$\acyclicPipeDreams(\omega)$,
\item there exist linear extensions~$\pi$ of~$P$ and~$\pi'$ of~$P'$ such that~$\pi < \pi'$ in weak order,
\item the minimal (resp.~max) linear extensions~$\pi$ of~$P$ and~$\pi'$ of~$P$ satisfy~$\pi < \pi'$ in weak order.
\end{enumerate}
\end{proposition}

\begin{proof}
Consider two distinct acyclic pipe dreams~$P, P' \in \acyclicPipeDreams(\omega)$ and their $\equiv_\omega$-congruence~classes~$C, C'$. If there exist representatives~$\pi = UijV \in C$ and~$\pi' = UjiV \in C'$ which are adjacent in weak order, then~$P = \insertion{\pi}{\omega}$ and~$P' = \insertion{\pi'}{\omega}$ differ by the flip of the first/last elbow between the pipes~$i$ and~$j$, by definition of the map~$\insertion{\cdot}{\omega}$. Conversely, if~$P$ and~$P'$ differ by the flip of the first/last elbow between the pipes~$i$ and~$j$, then $i$ and~$j$ are connected in the contact graph~$P\contact$, so that there exists a linear extension~$\pi = UijV$ of~$P\contact$ where~$i$ and~$j$ are consecutive. Let~$\pi' = UjiV$ be the permutation obtained by the switch of~$i$ and~$j$ in~$\pi$. By definition of the map~$\insertion{\cdot}{\omega}$, the pipe dream~$\insertion{\pi'}{\omega}$ is obtained by flipping the first elbow between the pipes~$i$ and~$j$ in~$\insertion{\pi}{\omega}$. The representatives~$\pi \in C$ and~$\pi' \in C'$ are thus adjacent in weak order. This proves that~$\insertion{\cdot}{\omega}$~induces an isomorphism from the quotient lattice of the interval~$[e,\omega]$ of the weak order by the $\equiv_\omega$-congruence to the increasing flip order on acyclic pipe dreams of~$\acyclicPipeDreams(\omega)$. In turn, since the $\equiv_\omega$-congruence is a lattice congruence, this quotient lattice is isomorphic to the subposet of the weak order induced by the minimal (resp.~maximal) elements of the classes. See~\cite{Reading-LatticeCongruences, Reading-CambrianLattices} for further details on quotient lattices.
\vincent{I am not sure anymore that this proof is correct. At least this could require more explanations.}
\end{proof}

\begin{corollary}
For any permutation~$\omega \in \fS_n$, the increasing flip poset on~$\acyclicPipeDreams(\omega)$ is a lattice.
\end{corollary}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Canopy}
\label{sec:canopy}

Recall that the \defn{canopy} of a binary tree~$T$ with~$n$ internal nodes is the sign sequence~${\canopy{T} \in \{{-},{+}\}^{n-1}}$ defined by~$\canopy{T}_i = {-}$ if the $(i+1)$st leaf of~$T$ is a left leaf and~$\canopy{T}_i = {+}$ if the $(i+1)$st leaf of~$T$ is a right leaf. Equivalently, $\canopy{T}_i = -$ if the node~$i$ of~$T$ is above the node~$i+1$ of~$T$ and~$\canopy{T}_i = +$ otherwise. This map was already used by J.-L.~Loday in~\cite{LodayRonco, Loday}, but the name ``canopy'' was coined by X.~Viennot~\cite{Viennot}.
% The binary search tree insertion map and the canopy map factorize the recoil map: $\surjectionBrickZono[] \circ \surjectionPermBrick[] = \surjectionPermZono[]$. This combinatorial fact can also be understood on the geometry of the normal fans of the permutahedron, the associahedron and the cube, see Section~\ref{subsec:normalFans}.

Before introducing the canopy, let us define the $\omega$-recoils. For this, consider the graph~$G(\omega)$ with vertex set~$[n]$ and edge set
\[
\bigset{ij}{i < j \text{ and } j-i \le |\set{k < i}{\omega^{-1}(k) < \omega^{-1}(j)}|}.
\]
Let~$\acyclicOrientations(\omega)$ denote the set of acyclic orientations of~$G(\omega)$.

\begin{definition}
The \defn{$\omega$-recoil scheme} of a permutation~$\pi \in [e,\omega]$ is the orientation~${\recoils{\pi}{\omega} \in \acyclicOrientations(\omega)}$ where for all~$i < j \in [n]$ such that~$j-i \le |\set{k < i}{\omega^{-1}(k) < \omega^{-1}(j)}|$, the edge~$ij$ is oriented~$i \to j$ if~$\pi^{-1}(i) < \pi^{-1}(j)$ and~$j \to i$ if~$\pi^{-1}(j) < \pi^{-1}(i)$. We call \defn{$\omega$-recoil map} the map~$\recoils{\cdot}{\omega} : [e,\omega] \to \acyclicOrientations(\omega)$.
\end{definition}

\begin{remark}
The fiber of an acyclic orientation~$O \in \acyclicOrientations(\omega)$ under the $\omega$-recoil map~$\recoils{\cdot}{\omega}$ are the linear extensions of~$O$ in~$[e,\omega]$.
\end{remark}

We now define a generalization of the canopy map for pipe dreams in~$\acyclicPipeDreams(\omega)$. To ensure that Definition~\ref{def:canopy} is valid, we need the following simple observation on comparisons of ``close'' pipes in a pipe dream.

\begin{lemma}
\label{lem:canopy}
If~$i < j$ satisfy~$j-i \le |\set{k < i}{\omega^{-1}(k) < \omega^{-1}(j)}|$, then the pipes~$i$ and~$j$ in any acyclic pipe dream~$P \in \acyclicPipeDreams(\omega)$ are comparable~for~$\contactLess{P}$.
\end{lemma}

\begin{proof}
If pipes~$i$ and~$j$ were incomparable in~$\contactLess{P}$, there would be two $\equiv_\omega$-congruent permutations~$UijV \equiv_\omega UjiV$. However, the assumption contradicts the definition of the $\equiv_\omega$-conguence in Definition~\ref{def:congruence}.
\end{proof}

\begin{definition}
\label{def:canopy}
The \defn{canopy} of a pipe dream~$P \in \acyclicPipeDreams(\omega)$ is the orientation~$\canopy{P} \in \acyclicOrientations(\omega)$ where for all~$i < j \in [n]$ such that~$j-i \le |\set{k < i}{\omega^{-1}(k) < \omega^{-1}(j)}$, the edge~$ij$ is oriented~$i \to j$ if~$i \contactLess{P} j$ and~$j \to i$ if~$j \contactLess{P} i$. It indeed defines an acyclic orientation of~$G(\omega)$ by Lemma~\ref{lem:canopy}. We call \defn{canopy} the map~$\canopy{\cdot}: \acyclicPipeDreams(\omega) \to \acyclicOrientations(\omega)$.
\end{definition}

\begin{proposition}
\label{prop:latticeHomomorphisms}
The maps~$\recoils{\cdot}{\omega}$, $\insertion{\cdot}{\omega}$, and~$\canopy{\cdot}$ define the following commutative diagram of lattice homomorphisms:
\[
\begin{tikzpicture}
  \matrix (m) [matrix of math nodes,row sep=1.2em,column sep=5em,minimum width=2em]
  {
     [e,\omega]  	&								& \acyclicOrientations(\omega)	\\
					& \acyclicPipeDreams(\omega) 	&								\\
  };
  \path[->] (m-1-1) edge node [above] {$\recoils{\cdot}{\omega}$} (m-1-3);
  \path[->>] (m-1-1) edge node [below] {$\insertion{\cdot}{\omega}\qquad$} (m-2-2.west);
  \path[->] (m-2-2.east) edge node [below] {$\quad\canopy{\cdot}$} (m-1-3);
\end{tikzpicture}
\]
\end{proposition}

\begin{proof}
Consider a permutation~$\pi$ and let~$i < j \in [n]$ be such that~$j-i \le |\set{k < i}{\omega^{-1}(k) < \omega^{-1}(j)}$. Assume that the edge~$ij$ is oriented from~$i$ to~$j$. Then~$\pi^{-1}(i) < \pi^{-1}(j)$, thus the pipe~$i$ is inserted before the pipe~$j$ in~$\insertion{\pi}{\omega}$, so that~$i \contactLess{\insertion{\pi}{\omega}} j$ and there is also an arc from~$i$ to~$j$ in~$\canopy{\insertion{\pi}{\omega}}$.
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Future work}
\label{sec:futureWork}

\subsection{Sortability and alignement}

We should describe the minimum (or maximum) of the congruence classes of~$\equiv_\omega$ by
\begin{itemize}
\item a pattern avoiding condition, see Proposition~\ref{prop:patternAvoiding}.
\item ``$\omega$-sortability'', see~\cite{Reading-sortableElements}.
\item ``$\omega$-alignement'', see~\cite{Reading-sortableElements}.
\end{itemize}

\subsection{Other Coxeter groups}

\vincent{This part is not up-to-date.  We have new (hopefully correct) conjectures.}
All the arguments presented above should extend to type A Cambrian pipe dreams... This means that we consider the increasing flip poset of the type~$A$ subword complex~$\subwordComplex(\wo(c),\omega)$ for any Coxeter element~$c$ and any permutation~$\omega$ of~$\fS_n$. Similar arguments where already developed in~\cite{Pilaud-BrickAlgebra} for the particular case of the permutation
\[
\omega = [1, \dots, k, n-k, n-k-1, \dots, k+2, k+1, n-k+1, \dots, n].
\]
More generally, we can consider the following conjecture.

\begin{conjecture}
\label{conj:Coxeter}
For any finite Coxeter group~$W$, any Coxeter element~$c$ of~$W$, and any element~$w \in W$, the increasing flip poset on the acyclic facets of the subword complex~$\subwordComplex(\wo(c),w)$ is a lattice quotient of the interval~$[e,w]$ of the weak order on~$W$.
\end{conjecture}

Let's be a little more precise here: for an acyclic facet~$F$ of the subword complex~$\subwordComplex(\wo(c),w)$, one can consider the set~$\set{\pi \in W}{\R_{\ge 0} \pi(\Delta) \supseteq \R_{\ge 0} \Roots(F)}$, \ie the elements of~$W$ whose dual Coxeter chamber belongs to the cone generated by the root configuration of~$F$. I hope that this defines a lattice congruence of~$[e,w]$.

We should actually consider the lattice properties of the acyclic facets of~$\subwordComplex(c^k\wo(c),w)$ for any~$k$ and any~$w$. In type~$A$, this is the same as any subword complex~$\subwordComplex(c^k\wo(c),w)$ can be embedded in a bigger~$\subwordComplex(\wo(c'),w')$. In other types however it is a more general question.

\subsection{Hopf algebra}

Define an equivalence relation~$\equiv$ on intervals~$[\pi,\omega]$ of the weak order by~$[\pi,\omega] \equiv [\pi',\omega'] \iff \omega = \omega' \text{ and } \pi \equiv_\omega \pi'$. Essentially, we proved that the collection of all acyclic pipe dreams is in bijection with the equivalence classes of~$\equiv$. Now is there a Hopf algebra on intervals of the weak order such that the equivalence relation~$\equiv$ gives a subalgebra?
\vincent{I believe that this part should disappear.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliographystyle{alpha}
\bibliography{latticePipeDreams}
\label{sec:biblio}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

### 2022-08-25 acyclicFacets/draft/latticePipeDreams.tex
Fixing my email and web address (just making simple commit to be registered)
Added Section 6 about subword complexes

@@
 \usepackage{etex}
+\usepackage{ulem} % to strike through a word
+
 %\reserveinserts{50}
@@
 \address[N.~Bergeron]{Department of Mathematics and Statistics, York University, Toronto}
-\email{bergeron@mathstat.yorku.ca}
-\urladdr{http://www.math.yorku.ca/bergeron/}
+\email{bergeron@yorku.ca}
+\urladdr{http://bergeron.mathstats.yorku.ca}
 
@@
 % theorems
-\newtheorem{theorem}{Theorem}%[section]
+\newtheorem{theorem}{Theorem}[section]
 \newtheorem{corollary}[theorem]{Corollary}
@@
 \newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{conjecture}[theorem]{Conjecture}
+
+\theoremstyle{definition}
 \newtheorem{definition}[theorem]{Definition}
-\newtheorem{conjecture}[theorem]{Conjecture}
-
-\theoremstyle{definition}
 \newtheorem{example}[theorem]{Example}
@@
 \DeclareMathOperator{\arr}{Arr} % arrangements
-\DeclareMathOperator{\inv}{inv} % inversion set
+\DeclareMathOperator{\Inv}{Inv} % inversion set
+\DeclareMathOperator{\Ninv}{Ninv} % non-inversion set
+\DeclareMathOperator{\DemazureProduct}{Dem} % non-inversion set
 
@@
 \newcommand{\nantel}[1]{\todo[color=red!30]{#1 \\ \hfill --- N.}}
-\newcommand{\cesar}[1]{\todo[color=orange!30]{#1 \\ \hfill --- C.}}
+\newcommand{\cesar}[1]{\todo[color=orange!30,inline]{#1 \\ \hfill --- C.}}
+\newcommand{\cesarm}[1]{\todo[color=orange!30]{#1 \\ \hfill --- C.}}
 \newcommand{\noemie}[1]{\todo[color=green!30]{#1 \\ \hfill --- N.}}
@@
 \newcommand{\acyclicPipeDreams}{\Sigma} % acyclic pipe dreams
-\newcommand{\wo}{w_\circ} % longest element
-\newcommand{\subwordComplex}{\mathcal{SC}} % subword complex
-\newcommand{\Roots}{\mathrm{R}} % root configuration
 \newcommand{\linearExtensions}{\mathcal{L}} % linear extensions
@@
 \newcommand{\canopy}[1]{\mathsf{can}(#1)} % canopy of a pipe dream
+
+% Subword complexes
+
+\newcommand{\wo}{w_\circ} % longest element
+\newcommand{\subwordComplex}{\mathcal{SC}} % subword complex
+\newcommand{\Roots}{\mathrm{R}} % root configuration
+\newcommand{\rootFunction}[2]{\mathrm{r}_{#1}(#2)} % root function
+\newcommand{\subwordFacets}{\mathcal{F}} % subword complex
+\newcommand{\subwordAcyclicFacets}{\mathcal{F}^{ac}} % subword complex
+\newcommand{\greedyFacet}{I^{\overleftarrow{gr}}} % greedy facet
+\newcommand{\antiGreedyFacet}{I^{\overrightarrow{gr}}} % antigreedy facet
+\newcommand{\sweepingAlgorithm}{\mathrm{sweep}} % sweeping algorithm
 
@@
 
-\begin{theorem}
+\begin{theorem}\label{thm_pipe_latticecongruence}
 For any permutation~$\omega \in \fS_n$, the pipe dream congruence~$\equiv_\omega$ is a lattice congruence of the interval~$[e,\omega]$ of the weak order.
@@
 
-\begin{corollary}
-For any permutation~$\omega \in \fS_n$, the increasing flip poset on~$\acyclicPipeDreams(\omega)$ is a lattice.
+\begin{corollary}\label{cor_acyclicpipedreams_lattice}
+For any permutation~$\omega \in \fS_n$:
+\begin{enumerate}
+\item The increasing flip poset on~$\acyclicPipeDreams(\omega)$ is isomorphic to the lattice quotient~$[e,\omega]/\equiv_\omega$.
+\item The increasing flip poset on~$\acyclicPipeDreams(\omega)$ is a lattice.
+\end{enumerate}
 \end{corollary}
@@
 
+\newpage
+\section{Subword complexes}
+The objective of this section is to partially extend the results about the lattice structure of acyclic pipe dreams, presented in Section~\ref{sec:latticeAcyclicPipeDreams}, to the wider context of subword complexes of finite type.
+Before doing so, we recall some preliminaries about finite Coxeter groups and subword complexes.
+We refer to~\cite{bjorner_coxeterGroups_2005,humphreys_reflectionGroups_1990} for more details on Coxeter groups.
+
+\subsection{Finite coxeter groups} 
+%a~\cesar{To do:\\
+%Coxeter groups of finite type, root systems, weak order, Bruhat order, inversions, non-inversions. 
+%}
+We consider a \defn{finite root system} $\Phi=\Phi^+\cup \Phi^-$ in an $n$-dimensional euclidian space $V$, with \defn{simple roots} $\Delta=\{\alpha_1,\dots,\alpha_n\} \subseteq \Phi^+$. 
+The reflections along the hyperplanes orthogonal to the roots in $\Phi$ generate a finite Coxeter group $W$.  
+This group is generated by the simple transpositions $S=\{s_1,\dots ,s_n\}$, where $s_i$ is the reflection along the hyperplane orthogonal to the simple root $\alpha_i$.
+We also denote by $\alpha_s$ the simple root associated to $s\in S$.
+Throughout this paper, we only consider Coxeter groups which are finite.
+They are classified in terms of Dynkin diagrams, and arise from finite root systems, see~\cite{humphreys_reflectionGroups_1990}.
+
+Abstractly, the \defn{Coxeter group} $W$ is the group generated by a collection $S=\{s_1,\dots, s_n\}$ which satisfies the relations $(s_is_j)^{m_{ij}}=1$, where $m_{ii}=1$ and $m_{ij}\geq 2$ for~$i\neq j$.
+The pair $(W,S)$ is called a \defn{Coxeter system}.
+The \defn{length} $\ell(w)$ of an element $w\in W$ is the smallest~$\ell$ such that it can be written of the form $w=w_1w_2\dots w_\ell$ where $w_i\in S$.
+A \defn{reduced expression} of~$w$ is an expression of minimal length.
+We denote by $\wo$ the \defn{unique longest} element in $W$.
+
+For a finite Coxeter $W$ associated to a root system $\Phi$, the length $\ell(w)$ can be geometrically interpreted as the cardinality of the \defn{inversion set} $\Inv(w)$ of $w$, which is defined as
+\begin{align}\label{def_inversionset}
+\Inv(w) := \Phi^+ \cap w(\Phi^-). 
+\end{align}
+Indeed, this set can be written as 
+\begin{align}\label{def_inversionset2}
+\Inv(w) := \{
+\alpha_{w_1}, w_1(\alpha_{w_2}),\dots , w_1w_2\dots w_{\ell-1}(\alpha_{w_\ell})
+\}
+\end{align}
+for any reduced expression $w=w_1w_2\dots w_\ell$ of $w$.
+
+The \defn{non-inversion set} $\Ninv (w)$ of $w$ is defined as
+\begin{align}
+\Ninv(w) &:= \Phi^+ \cap w(\Phi^+) \label{def_noninversionset} \\
+& =\Inv(w\wo)
+\end{align}
+
+In particular, 
+\begin{align}
+\Phi^+=\Inv(w) \sqcup \Ninv (w).
+\end{align}
+
+The \defn{weak order} on $W$ is the partial order $\leq$ defined by $u \leq w$ if there exists $v \in W$ such that $uv = w$ and $\ell(u) + \ell(v) = \ell(w)$.
+In other words, the element $w$ has a reduced expression with a prefix which is a reduced expression of $u$.
+Equivalently, the weak order corresponds to the inclusion order on inversion sets, that is $u \leq w$ if and only if $\Inv(u) \subseteq \Inv(w)$.
+This order defines a lattice structure on the elements of W.
+The minimal element is the identity $e \in W$ and the maximal element is $\wo$.
+
+\subsection{Subword complexes}
+%~\cesar{To do:\\
+%subword complexes, flips, greedy facets, \sout{root function, root configuration, acyclic facets}. 
+%}
+
+Motivated by their study of Gröbner geometry of Schubert varieties~\cite{KnutsonMiller-GroebnerGeometry}, Knutson and Miller~\cite{knutson_subword_2004} introduced a remarkable family of simplicial complexes in the context of Coxeter groups.
+
+Let $(W,S)$ be a Coxeter system of finite type, $Q=(q_1,\dots,q_m)$ be a word in the generators $S$, and $w\in W$ be an element of the group. 
+For $J\subseteq [r]$, we denote by $Q_J$ the subword of~$Q$ consisting of the letters with positions in $J$. 
+The \defn{subword complex} $\subwordComplex(Q,w)$ is the simplicial complex whose facets are subsets $I\subseteq [m]$ such that $Q_{[m]\setminus I}$ is a reduced expression for $w$. 
+We denote the \defn{set of facets} of $\subwordComplex(Q,w)$ by $\subwordFacets(Q,w)$.
+
+Two facets $I,J\in\subwordComplex(Q,w)$ are said to be connected by a \defn{flip} if they differ one element:
+\[J=I\smallsetminus \{i\} \cup\{j\}\]
+for some $i\in I$ and $j\in J$ with $i\neq j$. If $i<j$, the flip from $I$ to $J$ is called an \defn{increasing flip}.
+
+The increasing flip graph on facets of the subword complex is an acyclic graph which has a unique source and a unique sink~\cite{pilaud_greedy_2012,pilaud_el_labelling_2013}.
+These two special facets are called the \defn{greedy facet} $\greedyFacet$ and the \defn{antigreedy facet} $\antiGreedyFacet$.
+They are the lexicographically smallest and largest facets of $\subwordComplex(Q,\pi)$, respectively.
+
+The poset on the set of facets induced by increasing flips is called the \defn{increasing flip poset}.
+
+\begin{definition}[{\cite{CeballosLabbeStump}}]
+    The \defn{root function} $\rootFunction{I}{\cdot}:[m]\rightarrow \Phi$ associated to a facet $I$ is the map from positions in the word $Q$ to roots defined by 
+    \[
+    \rootFunction{I}{k} := \prod Q_{[k-1]\smallsetminus I}(\alpha_{q_k}).
+    \]
+    The \defn{root configuration} is the set $\Roots(I)=\set{\rootFunction{I}{i}}{i\in I}$. 
+    The facet $I$ is called \defn{acyclic} if $\cone \Roots(I)$ is a pointed cone. 
+    We denote the \defn{set of acyclic facets} by $\subwordAcyclicFacets(Q,w)$. 
+\end{definition}
+The root function is a useful and well established tool in the study of subword complexes. For instance, they can be used to fully understand flips. 
+\begin{lemma}[{\cite{CeballosLabbeStump,knutson_subword_2004}}]
+\label{lem_rootfunction_flips}
+Let $I$ be a facet of the subword complex~$\subwordComplex(Q,w)$. The following hold:
+\begin{enumerate}
+    \item $i \in I$ is flippable if and only if $|\rootFunction{I}{i}|\in \Inv(w)$.
+    \item If $i \in I$ is flippable, it can be flipped to the unique $j\in [m]\smallsetminus I$ such that $\rootFunction{I}{j}=|\rootFunction{I}{i}|$. 
+    The flip is increasing ($i<j$) when $\rootFunction{I}{i}\in \Phi^+$ and decreasing ($i>j$) when $\rootFunction{I}{i}\in \Phi^-$. \label{lem_rootfunction_flips2}
+    \item If $I'=I\smallsetminus \{i\}\cap \{i'\}$ is a facet obtained from $I$ by flipping $i$ to $i'$ with $i<i'$, then
+    \begin{equation}\label{eq_rootfunction_flip}
+         \rootFunction{I'}{k} = 
+  \begin{cases}
+    s_\beta(\rootFunction{I}{k}), & \text{for } i < k \leq i' \\
+    \rootFunction{I}{k}, & \text{otherwise}
+  \end{cases}
+    \end{equation}
+    where $\beta=\rootFunction{I}{i}$ and $s_\beta\in W$ is the reflection orthogonal to the root $\beta$.
+    \item $i \in I$ is not flippable if and only if $\rootFunction{I}{i}\in \Ninv(w)$.
+\end{enumerate}
+\end{lemma}
+
+\subsection{Linear extensions of facets}
+
+\begin{definition}
+Let $\subwordComplex(Q,w)$ be a non-empty subword complex and $I\in \subwordComplex(Q,w)$ be a facet. 
+An element $\pi\in W$ is called a \defn{linear extension} of $I$ if the root configuration $\Roots(I)\subseteq \pi(\Phi^+)$.
+The \defn{set of linear extensions} of $I$ is denoted by
+\begin{align}
+\linearExtensions(I)=
+\set{\pi\in W}{\Roots(I)\subseteq \pi(\Phi^+)}.    
+\end{align}
+\end{definition}
+
+\begin{lemma}
+\label{lem_acyclic_nonempty}
+$\linearExtensions(I)\neq \emptyset$ if and only if $I$ is acyclic.
+\end{lemma}
+\begin{proof}
+Let $\Phi=\Phi^+\sqcup\Phi^-$ be the root system associated to $W$. 
+A known result for root systems of finite type states that any other choice of a positive root system $\Phi^+$ for $\Phi$ is of the form $\widetilde \Phi^+=\pi(\Phi^+)$ for some $w\in W$. 
+Since any pointed cone is contained in some $\widetilde \Phi^+$, then 
+\[
+\begin{array}{rcl}
+I \text{ is acyclic}  & \longleftrightarrow  &  \cone \Roots(I) \text{ is pointed} \\
+  & \longleftrightarrow  & \cone \Roots(I)\subseteq \pi(\Phi^+) \text{ for some } \pi\in W \\
+  & \longleftrightarrow  &  \Roots(I)\subseteq \pi(\Phi^+) \text{ for some } \pi\in W \\
+  & \longleftrightarrow  &  \linearExtensions(I) \neq \emptyset 
+\end{array}
+\]
+\end{proof}
+
+\begin{lemma}
+\label{lem_pi_phiplus_inv_ninv}
+The following holds,
+\[
+\pi(\Phi^+)=-\Inv(\pi)\sqcup \Ninv(\pi).
+\]
+\end{lemma}
+\begin{proof}
+This is straight forward from the definition of inversions and non-inversion of $\pi$. In fact, multiplying Equation~\eqref{def_inversionset} by $-1$ we deduce $\pi(\Phi^+)\cap \Phi^-=-\Inv(\pi)$. 
+Furthermore,  
+$\pi(\Phi^+)\cap \Phi^+=\Ninv(\pi)$ by Equation~\eqref{def_noninversionset}.
+\end{proof}
+
+The following lemma regards linear extensions of the greedy and antigreedy facets.
+
+\begin{lemma}\label{lem_linearext_greedyfacets}
+    Let $\greedyFacet$ and $\antiGreedyFacet$ be the greedy and antigreedy facets of $\subwordComplex(Q,w)$, respectively. Then 
+    \begin{enumerate}
+        \item $e\in \linearExtensions(\greedyFacet)$. 
+        \item $w \in \linearExtensions(\antiGreedyFacet)$.
+        \item If $e\in \linearExtensions(I)$ then $I=\greedyFacet$.
+    \end{enumerate}
+\end{lemma}
+\begin{proof}
+    Let $e\in W$ be the minimal element of the week order. 
+    The greedy facet $\greedyFacet$ is the unique facet for which every flip (if any) is increasing.
+By Lemma~\ref{lem_rootfunction_flips}~\eqref{lem_rootfunction_flips2}, this implies that $\greedyFacet$ is the unique facet $I$ such that $\Roots(I)\subseteq \Phi^+ = e(\Phi^+)$.
+This proves parts (1) and (3) of the Lemma.
+
+    For part (2) we need to analyze the possibilities for the set $\Roots(\antiGreedyFacet)$.
+By Lemma~\ref{lem_rootfunction_flips}~\eqref{lem_rootfunction_flips2}, if $i\in \antiGreedyFacet$ is flippable then $\rootFunction{\antiGreedyFacet}{i}\in -\Inv(w)$.
+Furthermore, if $i\in \antiGreedyFacet$ is not flippable then $\rootFunction{\antiGreedyFacet}{i}\in \Ninv(w)$.
+Therefore, $\Roots(\antiGreedyFacet)\subseteq w(\Phi^+)=-\Inv(w)\sqcup \Ninv(w)$.
+\end{proof}
+
+\begin{remark}
+The concept of linear extensions of acyclic facets of subword complexes are a natural generalization of linear extensions of contact graphs of acyclic pipe dreams that we introduced in Section~\ref{subsec:linearExtensions}.
+Indeed ...
+\cesar{make this connection crystal clear...}
+\end{remark}
+
+\subsection{Two fundamental theorems about linear extensions}
+In this section, we present our two main results about linear extensions for subword complexes, Theorem~\ref{thm_subword_linearextensions_A} and Theorem~\ref{thm_subword_linearextensions_B}.
+
+We say that a subset $A$ of the weak order is a \defn{lower set} if $a<b$ and $b\in A$ implies $a\in A$. 
+We say that $A$ is \defn{closed by intervals} if $a,b\in A$ implies that $[a,b]\in A$, where $[a,b]=\{c: a \leq c\leq b\}$.
+
+\begin{theorem}\label{thm_subword_linearextensions_A}
+Let~$\subwordComplex(Q,w)$ be a non-empty subword complex. The following hold:
+\begin{enumerate}
+\item  $\bigcup_{I\in\subwordFacets(Q,w)} \linearExtensions(I)$ is a lower set of the weak order. 
+\label{thmA_item1}
+\hfill (lower set)
+\item $[e,w] \subseteq \bigcup_{I\in\subwordFacets(Q,w)} \linearExtensions(I)$ 
+\label{thmA_item2}
+\hfill (containment)
+\item If $I_1\neq I_2$ then $\linearExtensions(I_1)\cap \linearExtensions(I_2)=\emptyset$. 
+\label{thmA_item3}
+\hfill (partition)
+\item The set $\linearExtensions(I)$ is closed by intervals. 
+\label{thmA_item4}
+\hfill (interval closed) 
+\end{enumerate}
+\end{theorem}
+
+\begin{remark}\label{rem_thmA}
+Before proving this theorem, we would like to make the following remarks about items~\eqref{thmA_item2} and~\eqref{thmA_item4}.
+\begin{enumerate}
+  \setcounter{enumi}{1}
+\item There are cases where $[e,w] \neq \bigcup_{I\in\subwordFacets(Q,w)}$. \cesarm{add discussion}
+\begin{figure}[h]
+\includegraphics[width=0.52\textwidth]{interval_not_contained1} \quad
+\includegraphics[width=0.43\textwidth]{interval_not_contained2}
+\end{figure}
+  \setcounter{enumi}{3}
+\item $\linearExtensions(I)$ is not an interval in general. See for instance the example~\cite[Figure~9]{PilaudStump-brickPolytope}. 
+In that figure, the elements of the week order $\mathfrak{S}_4$ that are linear extensions of the same acyclic facet of a given subword complex are grouped together.
+Some of the groups in the figure are not intervals.
+\\
+\end{enumerate}
+\end{remark}
+
+\begin{proof}[Proof of Theorem~\ref{thm_subword_linearextensions_A}]
+We will prove the items of the theorem one by one.
+
+Proof of \eqref{thmA_item1}:
+Let $\pi\in \linearExtensions(I)$ for some facet $I$.
+We need to show that if $\pi'<\pi$ then there exist another facet $I'$ such that $\pi'\in \linearExtensions(I')$. 
+It is enough to show this when $\pi=\pi' s$ for some $s\in S$ such that $\ell(\pi'
+)<\ell(\pi)$.
+
+By definition, $\pi\in \linearExtensions(I)$ if and only if $\Roots(I)\subseteq \pi(\Phi^+)$. Now, 
+\[
+\pi(\Phi^+)= -\Inv(\pi)\sqcup \Ninv(\pi)
+\]  
+and 
+\begin{align*}
+    \Inv(\pi') &=\Inv(\pi)\smallsetminus \{\beta\} \\
+    \Ninv(\pi') &= \Ninv(\pi) \cup \{\beta\}
+\end{align*}
+for $\beta=\pi'(\alpha_s)$. 
+Therefore,
+\begin{align*}
+    \pi'(\Phi^+) = \pi(\Phi^+) \smallsetminus \{-\beta\} \cup \{\beta\}.
+\end{align*}
+
+\begin{center}
+\begin{tikzpicture}
+\coordinate (a) at (0,0);
+\coordinate (b) at (0:2);
+\coordinate (c) at (60:2);
+\coordinate (d) at (120:2);
+\coordinate (e) at (180:2);
+\draw (b) node[right] {$\beta$};
+\draw (e) node[left] {$-\beta$};
+%
+\path[fill=green!20] (0,0) --  (60:2) arc(60:180:2) -- cycle;
+%
+\draw[-stealth,dashed] (a) -- (b);
+\draw[-stealth] (a) -- (c);
+% \draw[-stealth] (a) -- (d);
+\draw[-stealth] (a) -- (e);
+\node at (120:1) {$\pi(\Phi^+)$};
+\end{tikzpicture} 
+%
+\qquad
+%
+\begin{tikzpicture}
+\coordinate (a) at (0,0);
+\coordinate (b) at (0:2);
+\coordinate (c) at (60:2);
+\coordinate (d) at (120:2);
+\coordinate (e) at (180:2);
+\draw (b) node[right] {$\beta$};
+\draw (e) node[left] {$-\beta$};
+%
+\path[fill=green!20] (0,0) -- (0:2) arc(0:120:2)  -- cycle;
+%
+\draw[-stealth] (a) -- (b);
+% \draw[-stealth] (a) -- (c);
+\draw[-stealth] (a) -- (d);
+\draw[-stealth,dashed] (a) -- (e);
+\node at (60:1) {$\pi'(\Phi^+)$};
+\end{tikzpicture} 
+\end{center}
+%
+Note that the reflection $s_\beta=\pi's\pi'^{-1}$ orthogonal to the root $\beta$ transforms $\pi(\Phi^+)$ and $\pi'(\Phi^+)$ into each other:
+\[
+s_\beta(\pi(\Phi^+))=\pi'(\Phi^+).
+\]
+Since $s_\beta(\beta)= -\beta$, then $s_\beta$ preserves the set 
+\[
+\pi(\Phi^+)\smallsetminus \{-\beta\}=
+\pi'(\Phi^+)\smallsetminus \{\beta\}=
+\pi(\Phi^+)\cap \pi'(\Phi^+). 
+\]
+This observation will be useful to prove the statement in the second of the following two cases.
+
+\medskip
+{\bf Case 1}: $-\beta \notin \Roots(I)$.
+
+In this case, 
+$\Roots(I)\subseteq \pi(\Phi^+) \smallsetminus \{-\beta\} \subseteq \pi'(\Phi^+)$.
+Taking $I'=I$, we have 
+$\pi'\in \linearExtensions(I')$ 
+as wanted.
+
+\medskip
+{\bf Case 2}: $-\beta \in \Roots(I)$.
+
+In this case, we need to remove $-\beta$ from the root configuration.
+We will achieve this by flipping the position of the last $-\beta$ in $I$ to create a new facet $I'$.
+This position is indeed flippable as we will argue now.
+
+Given a facet $I$ of a subword complex~$\subwordComplex(Q,w)$ and a positive root $\beta\in \Phi^+$, the restriction of the list of roots 
+\[
+\rootFunction{I}{1}, \rootFunction{I}{2}, \dots , \rootFunction{I}{m}.
+\]
+to the set $\{\beta,-\beta\}$ is of the form
+\[
+\begin{array}{cccc}
+  \beta, \dots , & \beta &, -\beta, \dots, &-\beta.\\
+     & i && j
+\end{array}
+\]
+The sequence of $-\beta$'s could in principle be empty and so does the sequence of $\beta$'s.
+But if there is a $-\beta$ in this list, then there should be at least one $\beta$ preceding it.
+The position $i$ of the last $\beta$ is used in the reduced expression of $w$ in the complement of $I$, that is $i\notin I$.
+The positions of the other $\beta$'s and $-\beta$'s all belong to~$I$, and can all be flipped to $i$ (see Lemma~\ref{lem_rootfunction_flips}~\eqref{lem_rootfunction_flips2}).
+In particular, the position $j$ of the last $-\beta$ belongs to $I$, and it can be flipped to $i$ creating a new facet $I'=I\smallsetminus \{j\} \cap \{i\}$.
+
+Now, since $\beta\notin \pi(\Phi^+)$.
+There must be only one $\beta$ in the list.
+Otherwise, there would be at least one $\beta$ whose position belongs to the facet $I$.
+This would imply that $\beta\in \Roots(I)$ and $\pi$ would not be a linear extension of $I$, which is a contradiction.
+So, our restricted list corresponding to $I$ looks like
+\begin{equation}
+\begin{array}{ccc}
+  \beta &, -\beta, \dots, &-\beta.\\
+      i && j
+\end{array}    
+\end{equation}
+Flipping $j$ to $i$ creates the new facet $I'=I\smallsetminus \{j\} \cap \{i\}$ whose corresponding restricted list looks like
+\begin{equation}
+\begin{array}{ccc}
+  \beta &, \beta, \dots, &\beta.\\
+      i && j
+\end{array}    
+\end{equation}
+Indeed, Equation~\eqref{eq_rootfunction_flip} describes how the root function is modified after a flip.
+For a position $k$ satisfying $i<k\leq j$, we have $\rootFunction{I'}{k}=s_\beta (\rootFunction{I}{k})$; otherwise we have $\rootFunction{I'}{k}=\rootFunction{I}{k}$.
+Then, all $-\beta$'s get transformed into $\beta$'s.
+
+Moreover, since the reflection $s_\beta$ preserves the set 
+$$\pi'(\Phi^+)\smallsetminus \{\beta\} =
+\pi(\Phi^+)\smallsetminus \{-\beta\} =
+\pi(\Phi^+) \cap \pi'(\Phi^+).
+$$
+then $\Roots(I')\subseteq \pi'(\Phi^+)$. 
+Thus, $\pi'\in \linearExtensions(I')$ as desired.
+
+Proof of~\eqref{thmA_item2}: 
+By part \eqref{thmA_item1}, the union of all linear extensions of facets is a lower set.
+So, we just need to show that $w$ belongs to this set.
+This follows from $w\in \linearExtensions(\antiGreedyFacet)$, which was proven in    Lemma~\ref{lem_linearext_greedyfacets}.
+
+Proof of~\eqref{thmA_item3}: 
+We will show that if there is an element $\pi\in \linearExtensions(I_1)\cap \linearExtensions(I_2)$ then $I_1= I_2$. 
+We already showed this for $\pi=e$ in Lemma~\ref{lem_linearext_greedyfacets}.
+
+Let $I_1, I_2$ be two facets such that $e\neq \pi \in \linearExtensions(I_1)\cap \linearExtensions(I_2)$.
+As in the proof of part \eqref{thmA_item1}, let $\pi'=\pi s$ for some $s\in S$ such that $\ell(\pi')<\ell(\pi)$, and let $I_1',I_2'$ be the corresponding facets obtained using the same steps of the proof.
+These new facets satisfy $\pi'\in \linearExtensions(I_1')\cap \linearExtensions(I_2')$.
+
+We claim that $I_1=I_2$ if and only if $I_1'=I_2'$. 
+The forward direction is clear.
+For the reverse direction we analyze the two cases if the proof of part \eqref{thmA_item1}.
+Note that in Case~1, the resulting facet~$I'$ obtained from $I$ satisfies $\beta\notin \Roots(I')$, while in Case 2 we have $\beta \in \Roots(I')$.
+Therefore, if $I_1'=I_2'$ then both $I_1$ and $I_2$ fall into Case 1 or both into Case 2. 
+If both fall into Case 1, then $I_1'=I_1$ and $I_2'=I_2$ and so $I_1=I_2$ as desired. 
+If both fall into Case 2, then we just need to flip back the performed flip to obtain $I_1=I_2$.
+
+Now we need to show that $I_1=I_2$.
+We proceed by contradiction.
+If $I_1\neq I_2$, then $I_1'\neq I_2'$ and $\pi'\in \linearExtensions(I_1')\cap \linearExtensions(I_2')$.
+We can continue going down in the week order until reaching the minimal element $e$.
+The resulting two facets are different and their linear extensions contain $e$.
+This is a contradiction to Lemma~\ref{lem_linearext_greedyfacets}.
+
+Proof of~\eqref{thmA_item4}: 
+Let $\pi_1,\pi_2\in \linearExtensions(I)$ and assume $\pi_1<\pi_2$. We need to show that if $\pi_1\leq \pi \leq \pi_2$ then~$\pi \in \linearExtensions(I)$. 
+By definition of linear extensions and Lemma~\ref{lem_pi_phiplus_inv_ninv} we have
+\[
+\Roots(I) \subseteq \pi_i(\Phi^+)=-\Inv(\pi_i)\sqcup \Ninv(\pi_i)
+\]
+for $i=1,2$. 
+Restricting to the set of negative and positive roots, respectively, we deduce
+\[
+\Roots(I)\cap \Phi^- \subseteq -\Inv(\pi_1) \subseteq -\Inv(\pi) \qquad 
+\Roots(I)\cap \Phi^+ \subseteq \Ninv(\pi_2)  \subseteq \Ninv(\pi)
+\]
+Therefore
+\[
+\Roots(I) \subseteq \pi(\Phi^+)=-\Inv(\pi)\sqcup \Ninv(\pi)
+\]
+and so $\pi\in \linearExtensions(I)$.
+\end{proof}
+
+For simplicity, we denote by 
+\[
+\linearExtensions(Q,w) = \bigcup_{I\in\subwordFacets(Q,w)} \linearExtensions(I)
+\]
+the \defn{set of linear extensions of all facets} of $\subwordComplex(Q,w)$.
+Since $\linearExtensions(I)\neq \emptyset$ if and only if $I$ is acyclic (Lemma~\ref{lem_acyclic_nonempty}), we have the following straight forward corollary. 
+\begin{corollary}\label{cor_linearextensions_partition}
+The following holds:    
+\begin{align}
+    \linearExtensions(Q,w) =
+    \bigsqcup_{I\in\subwordAcyclicFacets(Q,w)} \linearExtensions(I).
+\end{align}
+\end{corollary}
+
+As pointed out in Remark~\ref{rem_thmA}, there are subword complexes for which $[e,w] \neq \bigcup_{I\in\subwordFacets(Q,w)}$.
+Our second fundamental theorem describes a large family of cases where equality holds.
+
+\begin{theorem}\label{thm_subword_linearextensions_B}
+
+Let $\subwordComplex(Q,w)$ be a non-empty subword complex such that the word $Q$ contains a reduced expression of $\wo$.
+The linear extensions of acyclic facets of $\subwordComplex(Q,w)$ form a partition of the interval $[e,w]$:
+\begin{align}
+    [e,w] =
+    \bigsqcup_{I\in\subwordAcyclicFacets(Q,w)} \linearExtensions(I).
+\end{align}
+\end{theorem}
+
+The proof of this theorem is based on the following proposition, which follows from~\cite[Theorem~3.1 and Corollary 3.3]{jahn_bruhat_2021}.
+
+\begin{proposition}[{\cite{jahn_bruhat_2021}}]\label{prop_jahnStump_intersection}
+    Let $\subwordComplex(Q,w)$ be a non-empty subword complex such that the word $Q$ contains a reduced expression of $\wo$. Then 
+    \[
+\left(
+\bigcap_{I\in \subwordFacets(Q,\pi)} \cone \Roots(I) 
+\right)
+\cap \Phi
+= 
+\Ninv(w).
+    \]
+\end{proposition}
+\begin{proof}
+    We include a short proof here for self containment. We refer to~\cite{jahn_bruhat_2021} for the description of the notation $C^+(w,\cdot)$. 
+    By~\cite[Theorem~3.1]{jahn_bruhat_2021} we have
+    \[
+\bigcap_{I\in \subwordFacets(Q,\pi)} \cone \Roots(I) =
+C^+(w,\DemazureProduct(Q)).
+    \]
+    The word $Q$ contains a reduced expression of $\wo$ if and only if $\DemazureProduct(Q)=\wo$. Furthermore, by~\cite[Corollary~3.3]{jahn_bruhat_2021} we have
+    \[
+C^+(w,\wo)\cap \Phi
+= \Inv(w \wo) = \Ninv(w).
+    \]    
+\end{proof}
+
+\begin{proof}[Proof of Theorem~\ref{thm_subword_linearextensions_B}]
+Assume $\pi\in \linearExtensions(I)$. 
+We want to show that $\pi<w$. 
+By Proposition~\ref{prop_jahnStump_intersection} we have 
+\[
+\Ninv(w) 
+\subseteq \cone \Roots(I) 
+\subseteq \cone \pi(\Phi^+).
+\]
+Therefore
+\[
+\Ninv(w) 
+\subseteq \cone \pi(\Phi^+) \cap \Phi^+ 
+= \Ninv(\pi).
+\]
+Thus $\pi \leq w$ as desired.
+\end{proof}
+
+\subsection{The sweeping algorithm}
+
+Given a linear extension $\pi \in \linearExtensions(Q,w)$, one natural question is whether we can recover the unique acyclic facet $I$ such that $\pi \in \linearExtensions(I)$.
+We can recover this facet via a sweeping algorithm which we now introduce. 
+The algorithm outcomes a facet for every element~$\pi \in W$, and this will be the desired facet for each $\pi \in \linearExtensions(Q,w)$.
+
+\[
+\begin{tabular}{cccc}
+$\sweepingAlgorithm$ : & $W$  &$\longrightarrow$ &$\subwordFacets(Q,w)$\\
+    & $\pi$ & $\longrightarrow$ & $\sweepingAlgorithm(Q,w,\pi)$
+\end{tabular}
+\]
+
+We start by setting $I^0=\emptyset$ to be the empty set. 
+Then we scan the word $Q=(q_1,\dots ,q_m)$ from left to right.
+At position $j\in [m]$ we produce a new set $I^j$ obtained from the previous one $I^{j-1}$ by either adding $j$ or not, according to certain rules.
+We let $Q^j=Q_{[j]\smallsetminus I^j}$ and denote by
+    \[
+    \rootFunction{I^j}{k} = \prod Q_{[k-1]\smallsetminus I^j}(\alpha_{q_k}).
+    \]
+the partial root function for $k\leq j$.   
+The rules are the following:
+
+\begin{enumerate}
+    \item If $\rootFunction{I^j}{j}\in \Ninv(w)$ then let 
+    \[
+    I^j=I^{j-1}\cup\{j\}.
+    \] 
+    \label{sweeping_case1}
+    \item If $\rootFunction{I^j}{j}\in \Inv(w) \cap \Inv (\pi)$ then let 
+    \[
+    I^j=I^{j-1}. 
+    \]
+    \label{sweeping_case2}
+    \item If $\rootFunction{I^j}{j}\in \Inv(w) \cap \Ninv (\pi)$ then we consider two cases: 
+    \label{sweeping_case3} 
+    \begin{enumerate}
+        \item If $Q_{[m]\smallsetminus I^{j-1}\smallsetminus \{j\}}$ contains a reduced expression of $w$ with prefix $Q^{j-1}$ then let 
+        \[
+        I^j=I^{j-1}\cup \{j\}. 
+        \]        
+        \label{sweeping_case3a}
+        \item If not let 
+        \[
+        I^j=I^{j-1}.
+        \]
+        \label{sweeping_case3b}
+    \end{enumerate}
+    \item If $\rootFunction{I^j}{j}\in -\Inv(w)$ then let
+    \[
+    I^j=I^{j-1}\cup \{j\}.
+    \]
+    \label{sweeping_case4}
+\end{enumerate}
+
+We denote by \defn{$\sweepingAlgorithm(Q,w,\pi)$} the resulting set $I^m$ obtained at the last step of the algorithm.
+
+Roughly speaking, the goal of the algorithm is to insert a reduced expression of $w$ in $Q$ by sweeping the word from left to right, while deciding whether we use a letter or not by looking at the root $\beta=\rootFunction{I^j}{j}$ that it produces.
+If $\beta \in \Ninv(w)$ then it can not be used (Case~\eqref{sweeping_case1}), otherwise we would not have a reduced expression for $w$. 
+If $\beta \in \Inv(w)$ then we take it when $\beta \in \Inv(\pi)$ (Case~\eqref{sweeping_case2}), or delay it as much as possible when $\beta \in \Ninv(\pi)$ (Case~\eqref{sweeping_case3}). 
+If $\beta \in -\Inv(w)$ we can simply not take it (Case~\eqref{sweeping_case4}).
+
+\begin{proposition}
+\label{prop_sweeping1}
+    Let $\subwordComplex(Q,w)$ be a non-empty subword complex.
+    For every $\pi \in W$, the set $\sweepingAlgorithm(Q,w,\pi)$ is a facet of $\subwordComplex(Q,w)$.
+\end{proposition}
+
+\begin{proof}
+    Let $I^j$ and $Q^j=Q_{[j]\smallsetminus I^j}$ be as defined in the sweeping algorithm for $\pi$.  
+    The proposition follows by applying the following claim for $j=m$. 
+    \smallskip
+
+    {\bf Claim}: $Q^j$ is a reduced expression which is the prefix of a reduced expression of $w$ in $Q_{[m]\smallsetminus I^j}$.
+
+    \smallskip
+    We prove the claim by induction on $j$.
+
+    For $j=0$, $Q^0$ is the empty word which is reduced by definition. 
+    Furthermore, $Q_{[m]\smallsetminus I^0 }=Q$ contains a reduced expression of $w$ because the subword complex is non-empty. The empty word is a prefix of this reduced expression.
+
+    Now assume that the claim holds for $j-1$ and prove it for $j$. 
+    Note that 
+    \begin{equation}
+         Q^j = 
+  \begin{cases}
+    Q^{j-1}, & \text{if } I^j=I^{j-1}\cup \{j\} \\
+    Q^{j-1}\circ (q_j), & \text{if } I^j=I^{j-1}
+  \end{cases}
+    \end{equation}    
+    We analyze the different cases of the sweeping algorithm.
+    \begin{enumerate}
+    \item If $\rootFunction{I^j}{j}\in \Ninv(w)$ then 
+    $Q^j=Q^{j-1}$, which is reduced by induction hypothesis. 
+    Moreover, it is a prefix of a reduced expression of $w$ in $Q_{[m]\smallsetminus I^{j-1}}$.
+    Since $\rootFunction{I^j}{j}\in \Ninv(w)$, this reduced expression can not use the letter $q_j$; so, it is a reduced expression of $w$ in $Q_{[m]\smallsetminus I^{j}}$ as desired.
+    \item If $\rootFunction{I^j}{j}\in \Inv(w) \cap \Inv (\pi)$ then $Q^j= Q^{j-1}\circ (q_j)$, which is a reduced expression because~$Q^{j-1}$ is reduced and $\rootFunction{I^j}{j}\in \Inv(w)$.
+
+    Now let $\widetilde Q$ be a subword of $Q_{[m]\smallsetminus I^{j-1}}=Q_{[m]\smallsetminus I^{j}}$ which is a reduced expression of $w$ with prefix $Q^{j-1}$, and let $\widetilde I$ be the corresponding facet.
+
+    If $j\notin \widetilde I$, then $q_j$ is used in $\widetilde Q$ and we are done because $\widetilde Q$ has $Q^j$ as a prefix.
+
+    If $j\in \widetilde I$, then we can flip it to a position $j'>j$ (by Lemma~\ref{lem_rootfunction_flips}~\eqref{lem_rootfunction_flips2}), creating a new reduced expression $\widetilde Q'$ of $w$ which uses $q_j$, and thus has $Q^j$ as a prefix.
+
+    \item[(3)(a)] If $\rootFunction{I^j}{j}\in \Inv(w) \cap \Ninv (\pi)$ and $Q_{[m]\smallsetminus I^{j-1}\smallsetminus \{j\}}$ contains a reduced expression of $w$ with prefix $Q^{j-1}$, then $Q^j=Q^{j-1}$.
+    Therefore, $Q^j$ is reduced and it is a prefix of a reduced expression of $w$ in 
+    $Q_{[m]\smallsetminus I^{j-1}\smallsetminus \{j\}}=Q_{[m]\smallsetminus I^j}$.
+
+    \item[(3)(b)] In this case, $\rootFunction{I^j}{j}\in \Inv(w) \cap \Ninv (\pi)$ but $Q^j= Q^{j-1}\circ (q_j)$. The proof is similar to the proof of (2).
+
+    \item[(4)] If $\rootFunction{I^j}{j}\in -\Inv(w)$ then $Q^j=Q^{j-1}$. The argument is similar to that of part (1). 
+    \end{enumerate}
+
+Finally, we need to argue that any position $j$ falls into one of these cases. 
+The root $\rootFunction{I^j}{j}\in \Phi^+ \sqcup \Phi^-$ and we know that
+\[
+\Phi^+ = \Inv(w) \sqcup \Ninv(w) \qquad \qquad
+\Phi^- = -\Inv(w) \sqcup -\Ninv(w)  
+\]
+The positive roots are covered by the cases (1),(2), and (3). 
+The negative roots in $-\Inv(w)$ are covered in case (4). 
+Since we are inserting a reduced expression of $w$ in $Q$, the case $-\Ninv(w)$ never occurs.  
+\end{proof}
+
+The following proposition shows that for every linear extension $\pi \in \linearExtensions(Q,w)$, the sweeping algorithm recovers the unique acyclic facet $I$ such that $\pi \in \linearExtensions(I)$.
+
+\begin{proposition}
+\label{prop_sweeping2}
+    If $\pi\in \linearExtensions(I)$ for some facet $I\in \subwordComplex(Q,w)$, then 
+    \[
+I = \sweepingAlgorithm(Q,w,\pi).
+    \]
+\end{proposition}
+
+Our proof is based on the following lemma.
+
+\begin{lemma}\label{lem_negativeroot}
+    Let $I_1,I_2\in \subwordComplex(Q,w)$ be two different facets, and $j\in [m]$ be the first position where they differ. Without loss of generality assume 
+    \[
+I_2\cap [j] = I_1\cap [j] \smallsetminus \{j\}
+    \]
+with $j\in I_1$. Let $\beta=\rootFunction{I_1}{j}=\rootFunction{I_2}{j}$, then 
+\[
+-\beta \in \cone \Roots(I_2).
+\]
+\end{lemma}
+
+\begin{proof}
+    ~\cesar{Noemie: can you please write the proof of this Lemma?
+I do not remember the details at the moment, but the proof is based on the paper of Jahn--Stump that we discussed during your visit in Graz.}
+\end{proof}
+
+\begin{proof}[Proof of Proposition~\ref{prop_sweeping2}]
+Assume $\pi \in \linearExtensions(I)$ and let $I^j=I\cap [j]$. 
+We will show that the partial root function $\rootFunction{I^j}{\cdot}$ agrees with the decisions taken in the sweeping algorithm. Indeed, we will see that those decisions are forced.
+
+Recall that
+
+\begin{center}
+\begin{tabular}{ccl}
+    $\pi \in \linearExtensions(I)$ & $\longleftrightarrow$ & $R(I)\subseteq \pi(\Phi^+)$\\
+     & $\longleftrightarrow$ & $\cone R(I)\subseteq \pi(\Phi^+)$
+\end{tabular}    
+\end{center}
+and 
+\[
+\pi(\Phi^+) = -\Inv(\pi) \sqcup \Ninv(\pi).
+\]
+We analyze the possible cases in the sweeping algorithm.
+
+\begin{enumerate}
+    \item If $\rootFunction{I^j}{j}\in \Ninv(w)$ then clearly $j\in I$ is forced. Otherwise $Q_{[m]\smallsetminus I}$ would not be a reduced expression of $w$.
+    \item If $\rootFunction{I^j}{j}\in \Inv(w) \cap \Inv (\pi)$ then $j\notin I$ is forced. 
+    Otherwise we would have an inversion of $\pi$ in the root configuration, which contradicts $\pi \in \linearExtensions(I)$.
+    \item[(3)(a)] If $\rootFunction{I^j}{j}\in \Inv(w) \cap \Ninv (\pi)$ and $Q_{[m]\smallsetminus I^{j-1}\smallsetminus \{j\}}$ contains a reduced expression of $w$ with prefix $Q^{j-1}$ then $j\in I^j$ is forced.
+
+    We argue this by contradiction. 
+    Assume $j\notin I^j$ ($j\notin I$).
+Let $I_1=\sweepingAlgorithm(Q,w,\pi)$ and $I_2=I$.
+Applying Lemma~\ref{lem_negativeroot}, we deduce that $\beta=\rootFunction{I^j}{j}=\rootFunction{I}{j}$ satisfies
+    \[
+    -\beta \in \cone \Roots(I).
+    \]
+    But $\beta \in \Ninv(\pi)$. This contradicts $\pi\in \linearExtensions(I)$.
+    \item[(3)(b)]  If $\rootFunction{I^j}{j}\in \Inv(w) \cap \Ninv (\pi)$ and $Q_{[m]\smallsetminus I^{j-1}\smallsetminus \{j\}}$ does not contain a reduced expression of $w$ with prefix $Q^{j-1}$ then $j\notin I^j$ is forced.
+Otherwise, the complement of $I$ would not be a reduced expression of $w$.
+    \item[(4)] If $\rootFunction{I^j}{j}\in -\Inv(w)$ then $j\in I^j$ is clearly forced. Otherwise, the complement of $I$ would not be a reduced expression.
+\end{enumerate}
+\end{proof}
+
+\begin{remark}
+    Although the sweeping algorithm produces a facet $I=\sweepingAlgorithm(Q,w,\pi)$ for every~$w\in W$, in some cases we have $\pi \notin \linearExtensions(I)$. 
+    This happens because of Case~\eqref{sweeping_case1}, when a non-inversion~$\beta\in \Ninv(w)$ of $w$ is added to the root configuration $\Roots(I)$, such that~$\beta \notin \Ninv(\pi)$.
+This is only potentially possible when $\pi \notin [e,w]$.
+\end{remark}
+
+\subsection{The subword complex congruence conjecture}\cesarm{To do: meet to discuss about this section? put it in final form...}
+By Corollary~\ref{cor_linearextensions_partition}, the set $\linearExtensions(Q,w)$ of linear extensions of all facets of $\subwordComplex(Q,w)$ can be written as
+\begin{align*}
+    \linearExtensions(Q,w) =
+    \bigsqcup_{I\in\subwordAcyclicFacets(Q,w)} \linearExtensions(I).
+\end{align*}
+This partition determines a natural equivalence relation on the set $\linearExtensions(Q,w)$.
+
+\begin{definition}
+For a non-empty subword complex $\subwordComplex(Q,w)$, the \defn{subword complex congruence} is the equivalence relation~$\equiv_{Q,w}$ on the set $\linearExtensions(Q,w)\subseteq W$ of linear extensions  of all facets of $\subwordComplex(Q,w)$ determined by $\pi \equiv_{Q,w} \pi'$ if and only if $\pi$ and $\pi'$ are linear extensions of the same facet.
+\end{definition}
+
+By Theorem~\ref{thm_subword_linearextensions_B}, if $Q$ contains a reduced expression for $\wo$, this gives an equivalence relation on the interval $[e,w]$ of the week order. 
+We say that a word $Q$ is \defn{alternating} if all non-commuting pairs $s, t\in S$ alternate within $Q$.
+The following conjecture is supported by extensive computer computations.\cesarm{Noemie: in which cases did you check this conjecture? Type $A_n$ for n=???, B,C,D,....?}
+
+\begin{conjecture}
+Let $Q$ be an alternating word which contains a reduced expression for $\wo$.
+For any~$w\in W$, the subword complex congruence~$\equiv_{Q,w}$ is a lattice congruence of the interval~$[e,w]$ of the weak order.
+\end{conjecture}
+\cesarm{Do we have more conjectures or questions to be included here?}
+
+\begin{remark}\label{rem_acyclicflipposet_not_latticequotient}
+In analogy to the case of pipe dreams in Section~\ref{subsec:proofCongruence}, one might expect that the quotient~$[e,\omega]/\equiv_{Q,w}$ is isomorphic to the restriction of the increasing flip poset of $\subwordComplex(Q,w)$ to the set of acyclic facets.
+But this is not the case as shown in Example~\ref{ex_acyclicflip_not_weakorder_related}.
+\end{remark}
+
+\begin{example}\label{ex_acyclicflip_not_weakorder_related}
+    Let $W=S_3$ be the symmetric group generated by simple transpositions $S=\{s_1,s_2\}$ with $s_i=(i, i+1 )$.
+Let $Q=(s_1,s_2,s_1,s_2,s_1,s_2)$ and $w=\wo=s_1s_2s_1=s_2s_1s_2$.
+The subword complex $\subwordComplex(Q,w)$ has eight facets, six of which are acyclic.
+    All the fibers of $\equiv_{Q,w}$ are singletons and the lattice quotient~$[e,\omega]/\equiv_{Q,w}$ coincides with the weak order of type $A_2$.
+On the other hand there are two facets, $I_1=\{1,3,4\}$ and $I_2=\{3,4,6\}$, which are connected by a flip but whose corresponding elements $\pi_1$ and $\pi_2$ are not related in weak order.
+    \cesar{To do: Double check and expand this example in detail. Add figure.}
+\end{example}
+
+As we have seen in Corollary~\ref{cor_acyclicpipedreams_lattice}, the increasing flip poset of acyclic pipe dreams of any permutation $w$ is a lattice, because it is isomorphic to the lattice quotient~$[e,\omega]/\equiv_\omega$.
+This motivates the following open question for subword complexes.
+
+\begin{question}
+Let $\subwordComplex(Q,w)$ be a non-empty subword complex. Is the restriction of the increasing flip poset of $\subwordComplex(Q,w)$ to the set of acyclic facets a lattice?    
+\end{question}
+
+As pointed out in Remark~\ref{rem_acyclicflipposet_not_latticequotient},  we can not expect~$[e,\omega]/\equiv_{Q,w}$ to be isomorphic to the restriction of the increasing flip poset of $\subwordComplex(Q,w)$ to the set of acyclic facets.
+Example~\ref{ex_acyclicflip_not_weakorder_related} shows that there are flips between acyclic facets that are not detected by the week order.
+One could expect that there is a natural restriction to a special class of flips that behave nicer, meaning that all of them are identified by the quotient~$[e,\omega]/\equiv_{Q,w}$.
+In our Example~\ref{ex_acyclicflip_not_weakorder_related},
+the generalized Chute moves from~\cite{rubey_maximal_2012} do the job, because the flip that is not detected by the week order is exactly the one flip which is not Chute.
+The Chute lattice conjecture~\cite[Conjecture~2.8]{rubey_maximal_2012} might be an indication that this is the right direction to look at.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \bibliographystyle{alpha}

### 2022-10-13 acyclicFacets/draft/latticePipeDreams.tex
Rewrite Sections 1 and 2

@@
 \usepackage{etex}
-\usepackage{ulem} % to strike through a word
+\usepackage{ulem}\normalem % to strike through a word
+\usepackage[noabbrev,capitalise]{cleveref}
 
@@
 \newcommand{\fix}[1]{{\bf FIXME: }#1} % emphasis of a problem to FIX
-\newcommand{\fref}[1]{Figure~\ref{#1}} % reference figures
 \newcommand{\ie}{\textit{i.e.}~} % id est
@@
 \newcommand{\ex}[1]{^{\textrm{ex#1}}} % example
-\newcommand{\para}[1]{\medskip\noindent\textbf{#1~---}} % paragraph
+\newcommand{\para}[1]{\medskip\noindent\textbf{#1}} % paragraph
 \newcommand{\subpara}[1]{\smallskip\noindent\textit{#1.}} % paragraph
@@
 \newcommand{\contact}{^\#} % contact graph
-\newcommand{\se}{\textsc{se}} % south-east
-\newcommand{\nw}{\textsc{nw}} % north-west
+\newcommand{\se}{\textsc{se}} % southeast
+\newcommand{\nw}{\textsc{nw}} % northwest
 \newcommand{\insertion}[2]{\mathsf{ins}(#1,#2)} % insertion of permutation #1 in pipe dreams with permutation #2
@@
 \newcommand{\canopy}[1]{\mathsf{can}(#1)} % canopy of a pipe dream
+\newcommand{\greedyPipeDream}{P^{\overleftarrow{gr}}} % greedy facet
+\newcommand{\antiGreedyPipeDream}{P^{\overrightarrow{gr}}} % antigreedy facet
 
 % Subword complexes
-
 \newcommand{\wo}{w_\circ} % longest element
@@
 We show that for any permutation~$\omega$, the increasing flip graph on acyclic pipe dreams with permutation~$\omega$ is a lattice quotient of the interval~$[e,\omega]$ of the weak order.
+We then discuss conjectural generalizations of this result to acyclic facets of subword complexes on arbitrary finite Coxeter groups.
 \end{abstract}
@@
 The purpose of this note is to show that for any permutation~$\omega$, the increasing flip graph on acyclic pipe dreams with permutation~$\omega$ is a lattice quotient of the interval~$[e,\omega]$ of the weak order.
-It motivates Conjecture~\ref{conj:Coxeter} which is the long-term perspective of this work.
+It motivates \cref{conj:Coxeter} which is the long-term perspective of this work.
 The approach and proofs developed here are direct adaptations from~\cite[Sect.~1]{Pilaud-BrickAlgebra}.
-
-\section{Preliminaries}
+\vincent{Include an introduction}
+\vincent{cite \cite{BergeronBilley,KnutsonMiller-subwordComplex}}
+
+\section{Preliminaries on pipe dreams}
 \label{sec:preliminaries}
@@
 We label the pipes with~$1, 2, \dots, n$ in the order of their entry points from top to bottom.
-We denote by~$\omega_P \in \fS_n$ the order of the exit points of the non-zero pipes of~$P$ from left to right.
+We denote by~$\omega_P \in \fS_n$ the order of the exit points of the pipes of~$P$ from left to right.
 In other words, the pipe entering at row~$i$ exits at column~$\omega^{-1}_P(i)$.
@@
 An elbow~$e$ in a pipe dream~$P$ is \defn{flippable} if the two pipes passing through elbow~$e$ have a crossing~$c$, and the flip exchanges the elbow~$e$ with the cross~$c$.
-See \fref{fig:pipeDreams}.
-The flip is \defn{increasing} if the elbow~$e$ is weakly south-west of the crossing~$c$.
-For example, the flip of \fref{fig:pipeDreams} is increasing from left to right.
-
-The \defn{contact graph} of a pipe dream~$P$ is the directed graph~$P\contact$ with one node for each pipe of~$P$ and one arc for each elbow of~$P$ connecting the north-west path to the south-east path of the elbow\footnote{We have reversed the usual orientation conventions to suit better our purposes, in particular in Section~\ref{subsec:insertionAlgorithm}.}.
+See \cref{fig:pipeDreams}.
+The flip is \defn{increasing} if the elbow~$e$ is weakly southwest of the crossing~$c$.
+For example, the flip of \cref{fig:pipeDreams} is increasing from left to right.
+%
+The \defn{increasing flip graph} is the graph of increasing flips on~$\pipeDreams(\omega)$.
+It is clearly a directed acyclic graph, and it has a unique source and a unique sink \cite{PilaudPocchiola}, called the \defn{greedy} and \defn{antigreedy} pipe dreams, and denoted~$\greedyPipeDream$ and~$\antiGreedyPipeDream$.
+\vincent{In \cite{PilaudStump-ELlabeling}, these are called positive and negative greedy facets. Also the notations are different...}
+
+The \defn{contact graph} of a pipe dream~$P$ is the directed graph~$P\contact$ with one node for each pipe of~$P$ and one arc for each elbow of~$P$ connecting the northwest pipe to the southeast pipe of the elbow\footnote{We have reversed the usual orientation conventions of \cite{PilaudSantos-brickPolytope, PilaudPocchiola, Pilaud-BrickAlgebra} to suit better our purposes, in particular in \cref{subsec:insertionAlgorithm}.}.
 We see equivalently the contact graph~$P\contact$ as a graph on the pipes of~$P$ or on the integers~$[n]$.
@@
 % We let~$\acyclicPipeDreams_n \eqdef \bigsqcup_{\omega \in \fS_n} \acyclicPipeDreams(\omega)$ and~$\acyclicPipeDreams \eqdef \bigsqcup_{n \in \N} \acyclicPipeDreams_n$.
-%\vincent{Add contact graphs to \fref{fig:pipeDreams}.}
+%\vincent{Add contact graphs to \cref{fig:pipeDreams}.}
 
@@
 As observed by different authors~\cite{Woo, PilaudPocchiola, Pilaud-these, Stump}, the pipe dreams of~$\reversingPipeDreams_n$ belong to the Catalan family.
-\fref{fig:bijection} illustrates explicit bijections between the pipe dreams of~$\reversingPipeDreams_n$, the binary trees on $n$ vertices, and the triangulations of a convex $(n+2)$-gon.
+\cref{fig:bijection} illustrates explicit bijections between the pipe dreams of~$\reversingPipeDreams_n$, the binary trees on $n$ vertices, and the triangulations of a convex $(n+2)$-gon.
+\vincent{figure starts with pipe $0$}
 
@@
 \begin{remark}
-All reversing pipe dreams are acyclic. Indeed, there contact graphs are (oriented) binary trees, which are certainly acyclic.
+All reversing pipe dreams are acyclic.
+Indeed, there contact graphs are (oriented) binary trees, which are certainly acyclic.
 \end{remark}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Subword complexes}
-\label{subsec:subwordComplexes}
-
-Pipe dreams are a very particular family of the family of subword complexes.
-Consider a Coxeter system~$(W,S)$, where~$W$ is a finite Coxeter group and~$S$ is the set of simple reflections of~$W$.
-We denote by~$e$ (resp.~$\wo$) the identity (resp.~longest element) of~$W$.
-Let~$Q \eqdef q_1 \dots q_m \in S^*$ be a word on the alphabet formed by the simple generators of~$W$ and~$w \in W$.
-The \defn{subword complex}~$\subwordComplex(Q,w)$ is the simplicial complex whose ground set~$[m]$ are the positions in~$Q$ and whose facets are the complements of the reduced expressions for~$w$ in~$Q$.
-
-It is known that~$\subwordComplex(Q,w)$ is either a ball or a sphere, in particular it is a pseudomanifold (with or without boundary).
-The flip graph of~$\subwordComplex(Q,w)$ is the graph whose vertices are the facets of~$\subwordComplex(Q,w)$ and whose edges are the ridges of~$\subwordComplex(Q,w)$.
-If~$F,F'$ are two adjacent facets with~$F \ssm \{p\} = F' \ssm \{p'\}$, we say that the flip is \defn{increasing} when~$p < p'$.
-The increasing flip graph was studied in particular in~\cite{PilaudStump-ELlabelings}.
-It is known to be acyclic, and its transitive closure is an EL-shellable poset (see~\cite{PilaudStump-ELlabelings} for the precise definition and references).
-
-There is also a notion of acyclicity for subword complexes.
-It is based on the notion of \defn{root configuration}~$\Roots(F)$ of a facet~$F$ of~$\subwordComplex(Q,w)$.
-We skip the details and refer to~\cite{CeballosLabbeStump, PilaudStump-brickPolytope} for details.
-The facet~$F$ is \defn{acyclic} if its root configuration is pointed (meaning that it generates a pointed cone).
-
-\begin{example}
-Consider the symmetric group~$\fS_{n+1}$ generated by the set of simple transpositions $\set{\tau_i}{i \in [n]}$ where~$\tau_i \eqdef (i \; i+1)$.
-For a permutation~$\omega \in \fS_{n+1}$, the pipe dreams of~$\pipeDreams(\omega)$ correspond to the facets of the subword complex~$\subwordComplex(Q,\omega)$ with~$Q = \tau_1, \tau_2, \dots, \tau_n, \tau_1, \tau_2, \dots, \tau_{n-1}, \dots, \tau_1, \tau_2, \tau_1$.
-% The notions of flips, increasing flips and acyclic pipe dreams transpose in the world of subword complexes.
-\end{example}
-
-\begin{example}
-For any Coxeter group~$W$ and any Coxeter element~$c \in W$ (a product of all generators of~$S$ in a given arbitrary order), let~$\wo(c)$ denote the $c$-sorting word of~$\wo$ (see \cite{Reading-CambrianLattices} for details).
-Extending the observation of Section~\ref{subsec:reversingPipeDreams}, it was shown in~\cite{CeballosLabbeStump} that the subword complex~$\subwordComplex(c\wo(c), \wo)$ is isomorphic to the cluster complex of type~$W$.
-In particular, the increasing flip graph is the Hasse diagram of the $c$-Cambrian lattice of~\cite{Reading-CambrianLattices}.
-\end{example}
-
-In contrast to the previous example, consider the word~$Q = \tau_1 \tau_2 \tau_3 \tau_2 \tau_1 \tau_2 \tau_3 \tau_2 \tau_1$ on the simple generators of the symmetric group~$\fS_4$ and the subword complex~$\subwordComplex(Q,\wo)$.
-Note that all facets in this subword complex are acyclic.
-It is shown in~\cite[Rem.~5.12]{PilaudStump-brickPolytope} that its increasing flip poset is not a lattice.
-This shows that neither the increasing flip poset, nor the acyclic increasing flip poset are lattices in general, even in type~$A$.
-In this note, we investigate the case of acyclic pipe~dreams.
 
@@
 We gather in this section some elementary properties of pipe dreams needed later.
+\vincent{Not sure we use all these. At least say that they are just technical points.}
 
@@
 \begin{itemize}
-\item $\noninversions{\omega}{j}$ many \se{} elbows\!\SEelbow{}
-\item $1+\noninversions{\omega}{j}$ many \nw{} elbows~\WNelbow{}
+\item $\noninversions{\omega}{j}$ many southeast elbows\!\SEelbow{}
+\item $1+\noninversions{\omega}{j}$ many northwest elbows~\WNelbow{}
 \item $j-1-\noninversions{\omega}{j}$ vertical crossings~\NScross
@@
 \end{itemize}
-where~$\noninversions{\omega}{j} \eqdef |\set{i \in [n]}{i < j \text{ and } \omega^{-1}(i) < \omega^{-1}(j)}|$.
+where~$\noninversions{\omega}{j} \eqdef \#\set{i \in [n]}{i < j \text{ and } \omega^{-1}(i) < \omega^{-1}(j)}$.
 \end{lemma}
@@
 Pipe~$j$ enters at row~$j$ and exits at column~$\omega^{-1}(j)$, so that it passes through~$j+\omega^{-1}(j)-1$ grid points.
-By Lemma~\ref{lem:horiVertCrossings}, it has~$|\set{i \in [n]}{i < j \text{ and } \omega^{-1}(i) > \omega^{-1}(j)}| = j-1-\noninversions{\omega}{j}$ vertical crossings and~$|\set{k \in [n]}{j < k \text{ and } \omega^{-1}(j) > \omega^{-1}(k)}| = \omega^{-1}(j)-1-\noninversions{\omega}{j}$ horizontal crossings.
-The~$1+2\,\noninversions{\omega}{j}$ remaining grid points along the pipe~$j$ are thus alternating north-west elbows and south-east elbows.
+By \cref{lem:horiVertCrossings}, it has~$\#\set{i \in [n]}{i < j \text{ and } \omega^{-1}(i) > \omega^{-1}(j)} = j-1-\noninversions{\omega}{j}$ vertical crossings and~$\#\set{k \in [n]}{j < k \text{ and } \omega^{-1}(j) > \omega^{-1}(k)} = \omega^{-1}(j)-1-\noninversions{\omega}{j}$ horizontal crossings.
+The~$1+2\,\noninversions{\omega}{j}$ remaining grid points along the pipe~$j$ are thus alternating northwest elbows and southeast elbows.
 \end{proof}
@@
 \label{lem:characterizationPipeDreams}
-A collection~$P$ of~$n$ pipes pairwise disjoint except at crossing and elbows and such that for each~$j \in [n]$, the pipe~$j$ enters at row~$j$, exits at column~$\omega^{-1}(j)$, and has~$\noninversions{\omega}{j}$ \se{} elbows is a pipe dream of~$\pipeDreams(\omega)$.
+A collection~$P$ of~$n$ pipes pairwise disjoint except at crossing and elbows and such that for each~$j \in [n]$, the pipe~$j$ enters at row~$j$, exits at column~$\omega^{-1}(j)$, and has~$\noninversions{\omega}{j}$ southeast elbows is a pipe dream of~$\pipeDreams(\omega)$.
 \end{lemma}
@@
 Observe first that the pipe~$j$ must cross the paths~$i$ such that~$i < j$ and~$\omega^{-1}(i) > \omega^{-1}(j)$ and the paths~$k$ such that~$j < k$ and~$\omega^{-1}(j) > \omega^{-1}(k)$.
-Moreover, it has~$\noninversions{\omega}{j}$ \se{} elbows and thus~$1+\noninversions{\omega}{j}$ \nw{} elbows.
+Moreover, it has~$\noninversions{\omega}{j}$ southeast elbows and thus~$1+\noninversions{\omega}{j}$ northwest elbows.
 This already exhausts all~$j+\omega^{-1}(j)-1$ grid points of~$j$.
@@
 \label{lem:rectangle}
-Let~$P$ be a pipe dream and~$p,q$ be pipes of~$P$.
-If there is a elbow of~$p$ weakly north-west of a elbow~$q$, then~$p \contactLess{} q$ (\ie there is an oriented path from~$p$ to~$q$ in the contact graph~$P\contact$ of~$P$).
+Let~$P$ be a pipe dream and~$i,j$ be pipes of~$P$.
+If there is an elbow of pipe~$i$ weakly northwest of an elbow of pipe~$j$, then~$i \contactLess{P} j$.
 \end{lemma}
@@
 \begin{proof}
-Let~$x$ (reps.~$y$) be the location of a elbow of~$p$ (resp.~$q$) such that~$x$ is weakly north-west of~$y$.
+Let~$x$ (resp.~$y$) be the location of an elbow of pipe~$i$ (resp.~$j$) such that~$x$ is weakly northwest of~$y$.
 We proceed by induction on the grid distance from~$x$ to~$y$.
-If they coincide, then~$p$ and~$q$ share a elbow, so that there is an edge from~$p$ to~$q$ in~$P\contact$.
-Otherwise, let~$r$ be the pipe of~$P$ with a south-east elbow at~$x$ ($r$ is either the pipe~$p$ itself, or there is an edge from~$p$ to~$r$ in~$P\contact$) and~$s$ be the pipe of~$P$ with a north-west elbow at~$y$ ($s$ is either the pipe~$q$ itself, or there is an edge from~$s$ to~$q$ in~$P\contact$).
+If they coincide, then pipes~$i$ and~$j$ share an elbow, so that there is an edge from~$i$ to~$j$ in~$P\contact$.
+Otherwise, let~$k$ be the pipe of~$P$ with a southeast elbow at~$x$ ($k$ is either the pipe~$i$ itself, or there is an edge from~$i$ to~$k$ in~$P\contact$) and~$\ell$ be the pipe of~$P$ with a northwest elbow at~$y$ ($\ell$ is either the pipe~$j$ itself, or there is an edge from~$\ell$ to~$j$ in~$P\contact$).
 Let~$R$ be the axis-parallel rectangle with elbows~$x$ and~$y$.
-Since~$r$ and~$s$ cross at most once, at least one of them has an additional elbow along the sides of~$R$.
-Assume for instance that~$r$ has an elbow at~$x'$.
+Since pipes~$k$ and~$\ell$ cross at most once, at least one of them has an additional elbow along the sides of~$R$.
+Assume for instance that~$k$ has an elbow at~$x'$.
 Then~$x'$ is still weakly northwest of~$y$ and $x',y$ are strictly closer than~$x,y$.
-By induction, there is a path from~$r$ to~$s$ in~$P\contact$, and thus a path form~$p$ to~$q$.
-\end{proof}
-
-Note that the reciprocal assertion of Lemma~\ref{lem:rectangle} is false.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Three equivalent partitions}
-\label{sec:partitions}
-
-Remember that the \defn{weak order} on~$\fS_n$ is defined as the inclusion order of inversions, where an inversion of~$\pi \in \fS_n$ is a pair of values~$i, j \in \N$ such that~$i < j$ while~$\pi^{-1}(i) > \pi^{-1}(j)$.
-Fix a permutation~$\omega \in \fS_n$, and let~$[e, \omega] \eqdef \set{\pi \in \fS_n}{\pi \le \omega}$ denote the weak order interval between the identity~$e$ and~$\omega$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Linear extensions of contact graphs}
+By induction, there is a directed path from~$k$ to~$\ell$ in~$P\contact$, and thus a path directed form~$i$ to~$j$.
+\end{proof}
+
+Note that the reciprocal assertion of \cref{lem:rectangle} is false.
+We conclude by two consequences of \cref{lem:rectangle}.
+
+\begin{lemma}
+\label{lem:consequenceRectangle1}
+If~$i < j$ and~$\omega^{-1}(i) < \omega^{-1}(j)$, then $i \contactLess{P} j$ for any~$P \in \pipeDreams(\omega)$.
+\end{lemma}
+
+\begin{proof}
+If~$i < j$ and~$\omega^{-1}(i) < \omega^{-1}(j)$, then the pipes~$i$ and~$j$ do not cross.
+Consider an elbow~$e$ of the pipe~$i$.
+Since the pipe~$j$ passes southeast of~$e$, it has an elbow southeast of~$e$.
+We conclude that~$i \contactLess{P} j$ by \cref{lem:rectangle}.
+\end{proof}
+
+\begin{lemma}
+\label{lem:consequenceRectangle2}
+Let~$P$ be a pipe dream and let~$i,j,k$ be three pipes of~$P$ such that~$\min(i,k) < j$ and~$\min(\omega^{-1}(i), \omega^{-1}(k)) < \omega^{-1}(j)$.
+If~$i \to k$ in~$P\contact$, then either~$i \contactLess{P} j \contactMore{P} k$ or~$i \contactMore{P} j \contactLess{P} k$.
+\vincent{not sure we really use this version}
+\end{lemma}
+
+\begin{proof}
+Let~$e$ denote the contact of~$i$ and~$k$ in~$P$.
+Decompose the triangular shape into three regions: the region~$A$ of all points located southwest of~$e$, the region~$B$ of all points located northwest or southeast of~$e$, and the region~$C$ of all points located northeast of~$e$.
+Since~$\min(i,k) < j$ and~$\min(\omega^{-1}(i), \omega^{-1}(k)) < \omega^{-1}(j)$, the pipe~$j$ starts in region~$A$ and ends in region~$C$.
+Hence, the pipe~$j$ has an elbow~$f$ in region~$B$.
+We thus obtain that~$i \contactLess{P} j \contactMore{P} k$ if this $f$ is southeast of~$e$, and that~$i \contactMore{P} j \contactLess{P} k$ if $f$ is northwest of~$e$.
+\end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Lattice of acyclic pipe dreams}
+\label{sec:latticeAcyclicPipeDreams}
+
+\vincent{Mention here and throughout the classical sylvester example}
+
+The \defn{weak order} on the permutations of~$[n]$ is defined as the inclusion order of inversion sets, where an inversion of a permutation~$\pi$ is a pair of values~$i, j \in [n]$ such that~$i < j$ while~${\pi^{-1}(i) > \pi^{-1}(j)}$.
+The cover relations in the weak order correspond to switching pairs of consecutive values in permutations.
+The weak order is known to be a lattice \cite{GuilbaudRosenstiehl,Bjorner}.
+For two permutations~$\sigma < \tau$, we denote by~$[\sigma, \tau]$ the weak order interval between~$\sigma$ and~$\tau$, which is again a lattice.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Linear extensions of pipe dreams}
 \label{subsec:linearExtensions}
 
-Consider an acyclic pipe dream~$P$.
-Recall that we denote by~$\contactLess{P}$ the transitive closure of the contact graph~$P\contact$ of~$P$.
-We denote by~$\linearExtensions(P)$ the set of linear extensions of~$P\contact$ (\ie $\pi \in \linearExtensions(P)$ if and only if~$\pi^{-1}(i) < \pi^{-1}(j)$ for all~$i \to j$ in~$P\contact$).
-We often say abusively that the permutations of~$\linearExtensions(P)$ are linear extensions of~$P$.
-In this section, we prove certain structural properties of~$\linearExtensions(P)$.
-The following definitions of weak order intervals and weak order interval posets are connected in the Proposition~\ref{prop:WOIP} proved by A.~Bjorner and M.~Wachs~\cite{BjornerWachs}, see also~\cite{ChatelPilaudPons}.
-
-\begin{definition}
-\label{def:WOIP}
-A \defn{weak order interval (WOI)} is a subset~$[\tau, \tau']$ of~$\fS_n$ consisting of all permutations~$\sigma \in \fS_n$ such that~$\tau \le \sigma \le \tau'$ in weak order.
-A \defn{weak order interval poset (WOIP)} is a poset~$\less$ on~$[n]$ such that for all~$a < b < c$,
-\[
-a \less c \implies a \less b \text{ or } b \less c 
-\qquad\text{and}\qquad
-a \more c \implies a \more b \text{ or } b \more c.
-\]
-\end{definition}
-
-\begin{proposition}[\protect{\cite[Thm.~6.8]{BjornerWachs}}]
-\label{prop:WOIP}
-The WOIs are the sets of linear extensions of WOIPs:
+%Recall that a \defn{linear extension} of a binary relation~$\less$ on~$[n]$ is a permutation~$\pi \in \fS_n$ such that~$i \less j$ implies $\pi^{-1}(i) < \pi^{-1}(j)$.
+%We denote by~$\linearExtensions(\less)$ the set of linear extensions of~$\less$.
+%Consider an acyclic pipe dream~$P$, and recall that we denote by~$\contactLess{P}$ the transitive closure of the contact graph~$P\contact$ of~$P$.
+%We denote by~$\linearExtensions(P)$ the set of linear extensions of~$\contactLess{P}$, and we say abusively that the permutations of~$\linearExtensions(P)$ are linear extensions of~$P$.
+%In other words, $\pi \in \linearExtensions(P)$ if and only if~$\pi^{-1}(i) < \pi^{-1}(j)$ for all arcs~$i \to j$ in~$P\contact$.
+We say that a permutation~$\pi$ is a \defn{linear extension} of a pipe dream~$P \in \pipeDreams(\omega)$ if~$\pi^{-1}(i) < \pi^{-1}(j)$ for every arc~$i \to j$ in~$P\contact$ (we should say linear extension of~$\contactLess{P}$, but prefer to simplify notation).
+We denote by~$\linearExtensions(P)$ the set of linear extensions of~$P$.
+%For a pipe dream~$P \in \pipeDreams(\omega)$, we denote by~$\linearExtensions(P)$ the set of \defn{linear extensions} of~$P$, \ie the permutations~$\pi$ of~$[n]$ such that~$\pi^{-1}(i) < \pi^{-1}(j)$ for every arc~$i \to j$ in~$P\contact$.
+In this section, we prove the following structural property of~$\linearExtensions(P)$.
+
+\begin{theorem}
+\label{thm:partitionPipeDreams}
+The set~$\set{\linearExtensions(P)}{P \in \acyclicPipeDreams(\omega)}$ partitions the weak order interval~$[e,\omega]$.
+\end{theorem}
+
+We will see in \cref{sec:algorithms} different algorithms to compute the pipe dream~$P \in \acyclicPipeDreams(\omega)$ of which a given permutation~$\pi \in [e,\omega]$ is a linear extension.
+These algorithms are however not needed for the proof of \cref{thm:partitionPipeDreams}, which we break into the next three elementary lemmas.
+
+\begin{lemma}
+\label{lem:lowerSetPipeDreams}
+If~$\pi \eqdef UjiV$ covers $\pi' \eqdef UijV$ in weak order, and ${\pi \in \linearExtensions(P)}$ for some~${P \in \acyclicPipeDreams(\omega)}$,~then
+\begin{itemize}
+\item if~$P\contact$ has no arc~$j \to i$, then~$\pi' \in \linearExtensions(P)$,
+\item otherwise, $\pi' \in \linearExtensions(P')$ where~$P'$ denotes the pipe dream obtained from~$P$ by flipping the furthest northeast contact between pipes~$i$ and~$j$ in~$P$.
+\end{itemize}
+\end{lemma}
+
+\begin{proof}
+The first point is obvious.
+For the second point, observe that the flip of the furthest contact just reverses all arcs~$j \to i$ and exchanges~$i$ and~$j$ at some extremities of the arcs of the contact graph.
+\end{proof}
+
+\begin{lemma}
+\label{lem:partition}
+If~$\pi \le \omega$ in weak order, then~$\pi$ a linear extension of a unique pipe dream~$P \in \acyclicPipeDreams(\omega)$.
+\end{lemma}
+
+\begin{proof}
+Consider the greedy and antigreedy pipe dreams~$\greedyPipeDream$ and~$\antiGreedyPipeDream$ of \cite{PilaudPocchiola}.
+For any contact between the pipes~$i$ and~$j$ in~$\greedyPipeDream$, with~$i < j$, we have
+\begin{itemize}
+\item if the pipes~$i$ and~$j$ never cross, then~$\omega^{-1}(i) < \omega^{-1}(j)$,
+\item if the pipes~$i$ and~$j$ cross, then~$\omega^{-1}(i) > \omega^{-1}(j)$ and the contact in~$\greedyPipeDream$ must be from~$i$ to~$j$ (since all flips in~$\greedyPipeDream$ are increasing by definition).
+\end{itemize}
+We conclude that~$e \in \linearExtensions(\greedyPipeDream)$.
+Conversely, if~$e \in \linearExtensions(P)$, all arcs of~$P\contact$ are increasing, so that all flips in~$P$ are increasing.
+We conclude that~$\greedyPipeDream$ is the unique pipe dream with~$e \in \linearExtensions(\greedyPipeDream)$.
+Similar arguments show that~$\antiGreedyPipeDream$ is the unique pipe dream with~$\omega \in \linearExtensions(\antiGreedyPipeDream)$.
+The result thus follows from~\cref{lem:lowerSetPipeDreams}, since it shows that the existence (resp.~uniqueness) of a pipe dream~$P$ such that~$\pi \in \linearExtensions(P)$ is preserved when going down (resp.~up) in weak order.
+\end{proof}
+
+\begin{lemma}
+\label{lem:interval}
+If~$\pi$ is a linear extension of a pipe dream~$P \in \acyclicPipeDreams(\omega)$, then~$\pi \le \omega$ in weak order.
+\end{lemma}
+
+\begin{proof}
+For any~$i < j$ with~$\omega^{-1}(i) < \omega^{-1}(j)$, the pipes~$i$ and~$j$ do not cross.
+Hence, the pipe~$j$ passes southeast of every elbow of the pipe~$i$.
+This shows that~$i \contactLess{P} j$ by \cref{lem:rectangle}, thus ${\pi^{-1}(i) < \pi^{-1}(j)}$.
+In other words, any non-inversion of~$\omega$ is a non-inversion of~$\pi$, so that~${\pi < \omega}$.
+\end{proof}
+
+\begin{proof}[Proof of \cref{thm:partitionPipeDreams}]
+Direct consequence of \cref{lem:partition,lem:interval}.
+\end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Pipe dream congruence}
+\label{subsec:pipeDreamCongruence}
+
+A \defn{congruence} of a lattice~$(L, \le, \meet, \join)$ is an equivalence relation~$\equiv$ on~$L$ which respects meets and joins: $x \equiv x'$ and~$y \equiv y'$ implies $x \meet y \equiv x' \meet y'$ and~$x \join y \equiv x' \join y'$.
+We will use the following classical characterization of lattice congruences.
+
+\begin{proposition}
+\label{prop:characterizationCongruences}
+An equivalence relation~$\equiv$ on a lattice~$L$ is a congruence if and only if
 \begin{enumerate}[(i)]
-\item the WOI~$[\tau, \tau']$ is the set of linear extensions of the WOIP obtained as the transitive closure of the relations~$i \less j$ for all non coinversions~$i,j$ of~$\tau$ and~$i \more j$ for all coinversions~$i,j$~of~$\tau'$;
-\item the linear extensions of a WOIP~$\less$ is the WOI~$[\tau,\tau']$, where~$\tau$ and~$\tau'$ are respectively the greedy and antigreedy linear extensions of~$\less$.
+\item every equivalence class of~$\equiv$ is an interval of~$L$,
+\item the projections~$\projDown : L \to L$ and~$\projUp : L \to L$, which maps an element of~$L$ to the minimal and maximal elements of its equivalence class respectively, are order preserving.
 \end{enumerate}
@@
 
-We use this characterization to prove the following statement.
+We call \defn{pipe dream congruence} the equivalence relation~$\equiv_\omega$ on the weak order interval~$[e,\omega]$, whose equivalence classes are the sets of linear extensions of the pipe dreams of~$\acyclicPipeDreams(\omega)$.
+This indeed defines an equivalence relation by \cref{thm:partitionPipeDreams}.
+In this section, we prove the following statement.
+
+\begin{theorem}
+\label{thm:pipeDreamCongruence}
+The pipe dream congruence~$\equiv_\omega$ is a congruence of the weak order interval~$[e,\omega]$.
+\end{theorem}
+
+We prove this statement by checking both conditions of \cref{prop:characterizationCongruences}.
+For the first condition, we need the following classical characterization of weak order intervals, see \cite{BjornerWachs} or~\cite{ChatelPilaudPons}.
+
+\begin{proposition}[{\cite[Thm.~6.8]{BjornerWachs}}]
+\label{prop:WOIP}
+The set~$\linearExtensions(\less)$ of linear extensions of a poset~$\less$ on~$[n]$ forms an interval~$I$ of the weak order if and only if for every~$i < j < k$,
+\[
+i \less k \implies i \less j \text{ or } j \less k
+\qquad\text{and}\qquad
+i \more k \implies i \more j \text{ or } j \more k.
+\]
+Moreover, the inversions of~$\min(I)$ are the pairs~$i,j \in [n]$ with $i < j$ and $i \more j$, and the non-inversions of~$\max(I)$ are the pairs~$i,j \in [n]$ with $i < j$ and $i \less j$.
+\vincent{Not sure I want to use that last sentence later.}
+\end{proposition}
 
@@
 \begin{proof}
-We just need to show that the poset~$\contactLess{P}$ satisfies the WOIP condition.
-Consider~$a < b < c$ such that~$a \contactLess{P} c$.
-If~$\omega^{-1}(a) < \omega^{-1}(b)$, we know from Lemma~\ref{lem:rectangle} that~$a \contactLess{P} b$.
-Similarly, if~$\omega^{-1}(b) < \omega^{-1}(c)$, we have~$b \contactLess{P} c$.
-We can therefore assume that~$\omega^{-1}(a) > \omega^{-1}(b) > \omega^{-1}(c)$.
-Assume moreover that~$a \contactLess{T} c$.
-Decompose the triangular shape into three regions: the region~$A$ of all points located south-west of the first elbow of the pipe~$b$ of~$P$, the region~$B$ of all points located north-west or south-east of an elbow of the pipe~$b$ of~$P$, and the region~$C$ of all points located north-east of the last elbow of the pipe~$b$ of~$P$.
-Since~$a \contactLess{T} c$, there is a path~$\pi$ form the entering point of the pipe~$a$ of~$P$ to the exiting point of the pipe~$c$ of~$P$ which travels along the pipes and the elbows of~$P$.
-Since~$a < b < c$, the path~$\pi$ starts in region~$A$ and ends in region~$C$, so that it necessarily passes from region~$A$ to region~$C$.
-Since the north-east corner of~$A$ is located south-west of the south-west corner of~$C$, this forces an elbow~$e$ of~$\pi$ to lie in region~$B$.
-Lemma~\ref{lem:rectangle} then ensures that either~$a \contactLess{T} b$ (if~$e$ is above the pipe~$b$), or~$b \contactLess{T} c$ (if~$e$ is below the pipe~$b$).
-The proof is similar if~$a \contactMore{T} c$.
-\end{proof}
-
-In the next two statements, we show that the sets~$\linearExtensions(P)$ partition an interval of the weak order.
+We just need to show that the poset~$\contactLess{P}$ (given by the transitive closure of~$P\contact$) satisfies the conditions of \cref{prop:WOIP}.
+Consider~$i < j < k$ such that~$i \contactLess{P} k$.
+If~$\omega^{-1}(i) < \omega^{-1}(j)$, then~$i \contactLess{P} j$ by \cref{lem:consequenceRectangle1}.
+Similarly, if~$\omega^{-1}(j) < \omega^{-1}(k)$, then~$j \contactLess{P} k$ by \cref{lem:consequenceRectangle1}.
+We can therefore assume that~$\omega^{-1}(i) > \omega^{-1}(j) > \omega^{-1}(k)$.
+Decompose the triangular shape into three regions: the region~$A$ of all points located northeast of the last elbow of the pipe~$j$ of~$P$, the region~$B$ of all points located northwest or southeast of an elbow of the pipe~$j$ of~$P$, and the region~$C$ of all points located southwest of the first elbow of the pipe~$j$ of~$P$.
+Since~$i \contactLess{P} k$, there is a path~$\pi$ form the exiting point of the pipe~$i$ of~$P$ to the entering point of the pipe~$j$ of~$P$ which travels along the pipes of~$P$, possibly jumping from the northwest pipe to the southeast pipe of an elbow it encounters.
+Since~$i < j$ and~$\omega^{-1}(j) > \omega^{-1}(k)$, the path~$\pi$ starts in region~$A$ and ends in region~$C$, so that it necessarily passes from region~$A$ to region~$C$.
+Since the southwest corner of~$A$ is located northeast of the northeast corner of~$C$, this forces an elbow~$e$ of~$\pi$ to lie in region~$B$.
+\cref{lem:rectangle} then ensures that either~$i \contactLess{P} j$ (if~$e$ is above the pipe~$j$), or~$j \contactLess{P} k$ (if~$e$ is below the pipe~$j$).
+The proof is similar if~$i \contactMore{P} k$.
+\end{proof}
+
+\begin{proposition}
+\label{prop:orderPreserving}
+Let $\sigma, \sigma'$ be two permutations of~$[e, \omega]$ and~$C, C'$ denote their $\equiv_\omega$-congruence classes.
+Then $\sigma \le \sigma'$ implies~$\min(C) \le \min(C')$ and $\max(C) \le \max(C')$ in weak order.
+\end{proposition}
+
+\begin{proof}
+We prove the statement for the maximums, the proof for the minimums is symmetrical.
+Observe first that we can assume that~$\sigma$ is covered by~$\sigma'$ in weak order, so that we write~${\sigma' = \sigma s_p}$ for some simple transposition~$s_p \eqdef (p \; p+1)$.
+The proof now works by induction on the weak order distance between~$\sigma$ and~$\max(C)$.
+If~$\sigma = \max(C)$, the result is immediate as~${\max(C) = \sigma < \sigma' \le \max(C')}$.
+Otherwise, $\sigma$ is covered by a permutation~$\tau$ in the class~$C$, and we write~$\tau = \sigma s_q$ for some simple transposition~$s_q \eqdef (q \; q+1)$.
+Let~$P,P' \in \acyclicPipeDreams(\omega)$ be such that~$C = \linearExtensions(P)$ and~$C' = \linearExtensions(P')$.
+We now distinguish five cases, according to the relative positions of~$p$ and~$q$:
+\begin{enumerate}[(1)]
+\item If~$p > q+1$, then~$\sigma = UijVk\ell W$, $\sigma' = UijV\ell kW$ and~$\tau = UjiVk\ell W$ for some~$i < j$~and~${k < \ell}$.
+Define~$\tau' \eqdef \sigma s_p s_q = \sigma s_q s_p = UjiV\ell kW$.
+By \cref{lem:lowerSetPipeDreams}, there is no arc~$i \to j$ in~$P\contact$ (since~$\sigma$ and~$\tau$ both belong to~$C$), and~$P\contact$ and~$P'{}\contact$ can only differ by arcs incident~to~$k$~or~$\ell$.
+Hence, there is no arc~$i \to j$ in~$P'{}\contact$.
+We thus obtain again by \cref{lem:lowerSetPipeDreams} that~$\tau' \in \linearExtensions(P') = C'$.
+\item If~$p = q+1$, then~$\sigma = UijkV$, $\sigma' = UikjV$ and~$\tau = UjikV$ for some~$i < j < k$.
+Define~$\tau' \eqdef \sigma s_p s_q s_p = \sigma s_q s_p s_q = UkjiV$.
+Since~$\sigma \in \linearExtensions(P)$, we have~$i \not\contactMore{P} j$ and~$j \not\contactMore{P} k$, so that there is no arc~$i \to k$ in~$P\contact$ by \cref{lem:consequenceRectangle2}.
+By \cref{lem:lowerSetPipeDreams}, there is no arc~$i \to j$ in~$P\contact$, and~$P\contact$ and~$P'{}\contact$ can only differ by arcs incident to~$j$ or~$k$.
+We thus obtain that there is no arc~$i \to j$ nor~$i \to k$ in~$P'{}\contact$.
+Consequently, again by \cref{lem:lowerSetPipeDreams}, both~$\sigma' s_q$ and~$\tau' = \sigma' s_q s_p$ belong to~$\linearExtensions(P') = C'$.
+\item If~$p = q$, then~$\sigma' = \tau$ is in~$C$, so that~$C = C'$ and there is nothing to prove.
+\item If~$p = q-1$, we proceed similarly as in Situation~(2).
+\item If~$p < q-1$, we proceed similarly as in Situation~(1).
+\end{enumerate}
+In all cases, we found~$\tau' > \tau$ with~$\tau' \in C'$.
+Since~$\tau < \tau'$ with~$\tau \in C$ and~$\tau' \in C'$, and since~$\tau$ is closer to~$\max(C)$ than~$\sigma$, we obtain that ${\max(C) < \max(C')}$ by induction hypothesis.
+\end{proof}
+
+\begin{proof}[Proof of \cref{thm:pipeDreamCongruence}]
+Follows from \cref{prop:characterizationCongruences}, whose conditions are guaranteed by \cref{prop:intervals,prop:orderPreserving}.
+\end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Pipe dream quotient}
+\label{subsec:}
+
+For a congruence~$\equiv$ of a lattice~$L$, the \defn{lattice quotient}~$L/{\equiv}$ is the lattice on the classes of~$\equiv$ where for any two congruence classes~$X$ and~$Y$, 
+\begin{itemize}
+\item $X \le Y$ in~$L/{\equiv}$ if and only if there exist representatives~$x \in X$ and~$y \in Y$ such that~$x \le y$ in~$L$, or equivalently $\min(X) \le \min(Y)$, or equivalently $\max(X) \le \max(Y)$,
+\item $X \meet Y$ (resp.~$X \join Y$) is the congruence classe of~$x \meet y$ (resp.~of~$x \join y$) for arbitrary representatives~$x \in X$ and~$y \in Y$.
+\end{itemize}
+In this section, we prove the following statement.
+
+\begin{theorem}
+\label{thm:pipeDreamQuotient}
+The lattice quotient~$[e,\omega]/{\equiv_\omega}$ is isomorphic to the increasing flip poset on~$\acyclicPipeDreams(\omega)$.
+\end{theorem}
+
+To prove this result, we need the following auxiliary statement.
 
 \begin{lemma}
-\label{lem:interval}
-For any linear extension~$\pi$ of a pipe dream~$P \in \pipeDreams(\omega)$, we have~$\pi \le \omega$ in weak order.
+\label{lem:flippable}
+Consider two acyclic pipe dreams~$P,P' \in \acyclicPipeDreams(\omega)$ connected by the flip of an elbow between their pipes~$i$ and~$j$.
+Then any directed path in~$P\contact$ or~$P'{}\contact$ between~$i$ and~$j$ is an arc.
 \end{lemma}
@@
 \begin{proof}
-Consider a non-inversion of~$\omega$, \ie~$(i,j) \in [n]^2$ such that~$i < j$ and~$\omega^{-1}(i) < \omega^{-1}(j)$.
-Since~$i < j$ and~$\omega^{-1}(i) < \omega^{-1}(j)$, the pipes~$i$ and~$j$ do not cross.
-Therefore, the path~$j$ passes south-east of any elbow of the path~$i$.
-This shows that~$i \contactLess{P} j$ by Lemma~\ref{lem:rectangle}.
-Therefore, $\pi^{-1}(i) < \pi^{-1}(j)$ for any linear extension~$\pi$ of~$P$.
-In other words, $(i,j)$ is also a non-inversion of~$\pi$.
-We conclude that all linear extensions \mbox{of~$P$ are smaller than~$\omega$ in weak order}.
-\end{proof}
+Say that~$i < j$ while~$\omega^{-1}(i) > \omega^{-1}(j)$ and that~$i \to j$ is an arc of~$P\contact$ while~$j \to i$ is an arc of~$P'{}\contact$.
+Since $P\contact$ is acyclic, there is no path from~$j$ to~$i$ in~$P\contact$.
+Assume by means of contradiction that there is a path~$i \to k_1 \to \dots \to k_p \to j$ in~$P\contact$ with~$p \ge 1$.
+Since the arcs of~$P'{}\contact$ are the arcs of~$P\contact$ where only extremities~$i$ and~$j$ can be changed, $P'{}\contact$ contains the path~$k_1 \to \dots \to k_p$ and at least one of the arcs~$i \to k_1$ or~$j \to k_1$, and at least one of the arcs~$k_p \to j$ or~$k_p \to i$.
+Consequently, since~$P'{}\contact$ contains the arc~$j \to i$ and is acyclic, it must contain the path~$j \to k_1 \to \dots \to k_p \to i$.
+We thus obtained that~$i \contactLess{P} k_1 \contactLess{P} j$ while~$i \contactMore{P'} k_1 \contactMore{P'} j$, and~$k_1$ has a contact with~$i$ in~$P$ and with~$j$ in~$P'$.
+
+Consider now the elbow~$e$ of~$P$ which is a crossing in~$P'$ and the elbow~$e'$ of~$P'$ which is a crossing of~$P$.
+Let~$R$ the rectangle with corners~$e$ and~$e'$.
+Since~$k_1$ has a contact with~$i$ in~$P$ and with~$j$ in~$P'$, it must pass inside~$R$.
+Since~$i \contactLess{P} k_1 \contactLess{P} j$ and~$i \contactMore{P'} k_1 \contactMore{P'} j$, the pipe~$k$ has no elbow located northwest or southeast of~$e$ or~$e'$, hence no elbow located north, south, west or east of~$R$.
+We thus obtain that~$k$ must be straight before it reaches~$R$, and after it leaves~$R$.
+Hence $k_1 < i < j$ and~$\omega^{-1}(k_1) > \omega^{-1}(j) > \omega^{-1}(i)$.
+By \cref{lem:consequenceRectangle1}, this contradicts~$k_1 \contactLess{P} j$~and~$i \contactMore{P'} k_1$.
+\end{proof}
+
+\begin{proof}[Proof of \cref{thm:pipeDreamQuotient}]
+It suffices to prove that the following conditions are equivalent for two distinct pipe dreams~$P,P' \in \acyclicPipeDreams(\omega)$:
+\begin{enumerate}[(i)]
+\item $P$ covers~$P'$ in the increasing flip poset on~$\acyclicPipeDreams(\omega)$,
+\item there exist linear extensions~$\pi$ of~$P$ and~$\pi'$ of~$P'$ such that~$\pi$ covers~$\pi'$ in weak order.
+\end{enumerate}
+\para{(ii) $\Rightarrow$ (i)}
+Follows from \cref{lem:lowerSetPipeDreams}.
+
+\para{(i) $\Rightarrow$ (ii)}
+Assume that~$P$ covers~$P'$ in the increasing flip poset.
+Let~$i < j$ be the two pipes involved in the flip between~$P$ and~$P'$.
+Hence, $j \to i$ is an arc of~$P$ while~$i \to j$ is an arc of~$P'$.
+By \cref{lem:flippable}, there is no directed path from~$j$ to~$i$ in~$P$ besides the arcs~$j \to i$ (there might be more than one such arc).
+Hence, there exists a linear extension~$\pi$ of~$P$ where~$j$ and~$i$ are consecutive.
+Write~$\pi \eqdef UjiV$ and define~$\pi' \eqdef UijV$.
+Since~$j \to i$ is an arc of~$P$, $\pi'$ is not a linear extension of~$P$.
+Hence, by \cref{lem:lowerSetPipeDreams}, $\pi'$ is a linear extension of~$P'$.
+\end{proof}
+
+Let us conclude by providing more equivalent characterizations of the increasing flip lattice lattice on~$\acyclicPipeDreams(\omega)$.
 
 \begin{proposition}
-\label{prop:partition}
-The collection~$\set{\linearExtensions(P)}{P \in \acyclicPipeDreams(\omega)}$ forms a partition of the interval~$[e,\omega]$ of the weak order.
+For any pipe dreams~$P, P' \in \acyclicPipeDreams(\omega)$, the following assertions are equivalent:
+\begin{enumerate}[(i)]
+\item $P < P'$ in the increasing flip poset on~$\acyclicPipeDreams(\omega)$,
+\item there exist linear extensions~$\pi$ of~$P$ and~$\pi'$ of~$P'$ such that~$\pi < \pi'$ in weak order,
+\item the minimal (resp.~max) linear extensions~$\pi$ of~$P$ and~$\pi'$ of~$P$ satisfy~$\pi < \pi'$ in weak order.
+\item there is no~$i < j$ such that~$i \contactMore{P} j$ and~$i \contactLess{P'} j$,
+\item for all~$i < j$, if~$i \contactMore{P} j$, then~$j \contactMore{P'} i$,
+\item for all~$i < j$, if~$i \contactLess{P'} j$, then~$i \contactLess{P} j$,
+\end{enumerate}
 \end{proposition}
@@
 \begin{proof}
-\vincent{There are other methods to prove this without using the sweeping algorithm... We will actually do this for arbitrary subword complexes.}
-By Lemma~\ref{lem:interval}, all linear extensions belong to the interval~$[e,\omega]$.
-
+We already proved that (i) $\Leftrightarrow$ (ii).
+\vincent{todo}
+\end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Three algorithms}
+\label{sec:algorithms}
+
+\vincent{This section is in progress}
+In this section, we describe three algorithms to decide whether two permutations are equivalent for the pipe dream congruence~$\equiv_\omega$.
+
+%To sum up, there are three equivalent ways to partition the interval~$[e,\omega]$ of the weak order:
+%\begin{itemize}
+%\item by the sets of linear extensions~$\linearExtensions(P)$ of all pipe dreams of~$\acyclicPipeDreams(\omega)$,
+%\item by the fibers of the sweeping algorithm, \vincent{choose notation}
+%\item by the fibers of the insertion map~$\insertion{\cdot}{\omega}$,
+%\item by the classes of the pipe dream congruence~$\equiv_\omega$.
+%\end{itemize}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Sweeping algorithm}
+\label{subsec:sweepingAlgorithm}
+
+\vincent{adapt the following}
 We now show that~$\linearExtensions(P) \cap \linearExtensions(P') = \varnothing$ for any two distinct acyclic pipe dreams~$P, P' \in \pipeDreams(\omega)$.
 For this, we show that we can reconstructing a pipe~$P$ knowing a linear extension~$\pi \in \linearExtensions(P)$.
-For this, we sweep the pipe dream in any perturbation of the \nw{} direction (meaning that we sweep the grid in any order such that each point is swept before all points weakly \nw of~$p$).
+For this, we sweep the pipe dream in any perturbation of the northwest direction (meaning that we sweep the grid in any order such that each point is swept before all points weakly northwest of~$p$).
 When we sweep a vertex~$v$ of the grid, we see a pipe~$p$ arriving horizontally at~$v$ and a pipe~$q$ arriving vertically at~$v$.
@@
 	\item Otherwise, we have no choice but imposing an elbow at~$v$.
-Indeed, if there is a crossing at~$v$, then Lemma~\ref{lem:rectangle} ensures that~$q$ will be below~$p$ in~$P\contact$, so that~$\pi$ would not be a linear extension of~$P$.
+Indeed, if there is a crossing at~$v$, then \cref{lem:rectangle} ensures that~$q$ will be below~$p$ in~$P\contact$, so that~$\pi$ would not be a linear extension of~$P$.
 	\end{itemize}
 \end{itemize}
-
-%Several arguments could be invoked, as for example the insertion algorithm discussed in Section~\ref{subsec:insertionAlgorithm}.
-We prefer here to recall from~\cite{PilaudPocchiola} that one can reconstruct a pipe dream~$P$ by sweeping the triangular shape in any slight perturbation of the north-east direction.
-When we sweep a vertex~$v$ of the grid, we see a pipe~$p$ arriving horizontally at~$v$ and a pipe~$q$ arriving vertically at~$v$.
-If~$p > q$, then $p$ and~$q$ already crossed before, so we have no choice but imposing an elbow at~$v$.
-If~$p < q$, there are two situations:
-%\begin{itemize}
-%\item if~$p \not\contactLess{P} q$ then~$p$ and~$q$ cannot touch, so that we have no choice but imposing a crossing~at~$v$,
-%\item if~$\omega^{-1}(p) < \omega^{-1}(q)$, then~$p$ and~$q$ cannot cross, so that we have no choice but imposing a contact at~$v$,
-%\item if~$p \contactLess{P} q$ and~$\omega^{-1}(p) > \omega^{-1}(q)$, then we have again two situations;
-%	\begin{itemize}
-%	\item If $q$ needs to go straight north, then we have no choice but imposing a crossing at~$v$,
-%	\item Otherwise, we have no choice but imposing an elbow at~$v$. \qedhere
-%	\end{itemize}
-%\end{itemize}
-
-To conclude the proof, we need to show that any permutation of~$[e,\omega]$ is a linear extension of some pipe dream~$P \in \acyclicPipeDreams(\omega)$.
-This is done using an insertion algorithm presented next.
-\end{proof}
 
@@
 %To properly describe this insertion algorithm, we introduce additional notations.
-We now describe this insertion algorithm, which is illustrated in \fref{fig:insertionAlgorithm}.
+We now describe this insertion algorithm, which is illustrated in \cref{fig:insertionAlgorithm}.
 
 Consider a given permutation~$\pi \eqdef \pi(1) \dots \pi(n)$ (written in one-line notation) in~$[e, \omega]$.
-We start from the empty triangular shape and insert the pipes~$\pi(1), \dots, \pi(n)$ one by one in the order of the permutation~$\pi$ as \nw{} as possible.
-In other words, at step~$t$, we consider the set~$X_t$ of free \nw{} elbows in the rectangle~$[\pi(t)] \times [\omega^{-1}(\pi(t))]$.
-The pipe inserted at step~$t$ then starts in row~$\pi(t)$, ends in column~$\omega^{-1}(\pi(t))$, covers each elbow of~$X_t$ with a \se{} elbow, and adds just one new free \nw{} elbow in between any two consecutive elbows of~$X_t$.
+We start from the empty triangular shape and insert the pipes~$\pi(1), \dots, \pi(n)$ one by one in the order of the permutation~$\pi$ as northwest as possible.
+In other words, at step~$t$, we consider the set~$X_t$ of free northwest elbows in the rectangle~$[\pi(t)] \times [\omega^{-1}(\pi(t))]$.
+The pipe inserted at step~$t$ then starts in row~$\pi(t)$, ends in column~$\omega^{-1}(\pi(t))$, covers each elbow of~$X_t$ with a southeast elbow, and adds just one new free northwest elbow in between any two consecutive elbows of~$X_t$.
 We denote the resulting pipe dream by~$\insertion{\pi}{\omega}$.
-See \fref{fig:insertionAlgorithm}.
+See \cref{fig:insertionAlgorithm}.
 
@@
 
-We need to argue that this algorithm indeed creates a pipe dream of~$\acyclicPipeDreams(\omega)$. To see it, we observe that the following invariant is maintained throughout the algorithm.
+We need to argue that this algorithm indeed creates a pipe dream of~$\acyclicPipeDreams(\omega)$.
+To see it, we observe that the following invariant is maintained throughout the algorithm.
 
@@
 \[
-|X_t| = \big| \bigset{s < t}{\pi(s) < \pi(t) \text{ and } \omega^{-1}\big( \pi(s) \big) < \omega^{-1}\big( \pi(t) \big)} \big|.
-\]
-\vincent{Note that this is independent of~$\pi$... This can be seen from Lemma~\ref{lem:interval}.}
+\#X_t = \# \bigset{s < t}{\pi(s) < \pi(t) \text{ and } \omega^{-1}\big( \pi(s) \big) < \omega^{-1}\big( \pi(t) \big)}.
+\]
+\vincent{Note that this is independent of~$\pi$... This can be seen from \cref{lem:interval}.}
 \end{lemma}
@@
 Fix~$t \in [n]$.
-At the beginning of the algorithm, there is no \se{} elbow in the rectangle~$R_t \eqdef [\pi(t)] \times [\omega^{-1}(\pi(t))]$.
+At the beginning of the algorithm, there is no southeast elbow in the rectangle~$R_t \eqdef [\pi(t)] \times [\omega^{-1}(\pi(t))]$.
 At each step~$s < t$, we have inserted a new pipe~$\pi(s)$ which enters at~$\pi(s)$ and exits at~$\omega^{-1}\big( \pi(s) \big)$.
@@
 \item If~$\pi(s) < \pi(t)$ and~$\omega^{-1}\big( \pi(s) \big) < \omega^{-1}\big( \pi(t) \big)$, then the pipe~$\pi(s)$ is completely contained in the rectangle~$R_t$.
-Since the pipe~$\pi(s)$ has one more \nw{} elbow than \se{} elbow, its insertion creates a new free \nw{} elbow in the rectangle~$R_t$.
-\item If~$\pi(s) < \pi(t)$ and~$\omega^{-1}\big( \pi(s) \big) > \omega^{-1}\big( \pi(t) \big)$, then the pipe~$\pi(s)$ enters and exits the rectangle~$R_t$ with an horizontal step, so that it has as many \nw{} and \se{} elbows in~$R_t$, and its insertion does not modify the number of free \nw{} elbows in the rectangle~$R_t$.
-\item If~$\pi(s) > \pi(t)$ and~$\omega^{-1}\big( \pi(s) \big) < \omega^{-1}\big( \pi(t) \big)$, then the pipe~$\pi(s)$ enters and exits the rectangle~$R_t$ with a vertical step, so that it has as many \nw{} and \se{} elbows in~$R_t$, and its insertion does not modify the number of free \nw{} elbows in the rectangle~$R_t$.
+Since the pipe~$\pi(s)$ has one more northwest elbow than southeast elbow, its insertion creates a new free northwest elbow in the rectangle~$R_t$.
+\item If~$\pi(s) < \pi(t)$ and~$\omega^{-1}\big( \pi(s) \big) > \omega^{-1}\big( \pi(t) \big)$, then the pipe~$\pi(s)$ enters and exits the rectangle~$R_t$ with an horizontal step, so that it has as many northwest and southeast elbows in~$R_t$, and its insertion does not modify the number of free northwest elbows in the rectangle~$R_t$.
+\item If~$\pi(s) > \pi(t)$ and~$\omega^{-1}\big( \pi(s) \big) < \omega^{-1}\big( \pi(t) \big)$, then the pipe~$\pi(s)$ enters and exits the rectangle~$R_t$ with a vertical step, so that it has as many northwest and southeast elbows in~$R_t$, and its insertion does not modify the number of free northwest elbows in the rectangle~$R_t$.
 \item If~$\pi(s) > \pi(t)$ and~$\omega^{-1}\big( \pi(s) \big) > \omega^{-1}\big( \pi(t) \big)$, then setting~$i = \pi(t)$ and~$j = \pi(s)$, we have~$i < j$ and~$\pi^{-1}(i) > \pi^{-1}(j)$ while~$\omega^{-1}(i) < \omega^{-1}(j)$, which contradicts our assumption that~$\pi \not< \omega$ in weak order.
@@
 \[
-\big| \bigset{s < t}{\pi(s) < \pi(t) \text{ and } \omega^{-1}\big( \pi(s) \big) < \omega^{-1}\big( \pi(t) \big)} \big| = \noninversions(\omega, \pi(t))
-\]
-many $\se$ elbows by Lemma~\ref{lem:rectangleInsertionAlgorithm} and since~$\pi < \omega$ in weak order.
-We thus conclude the proof by a direct application of Lemma~\ref{lem:characterizationPipeDreams}.
+\# \bigset{s < t}{\pi(s) < \pi(t) \text{ and } \omega^{-1}\big( \pi(s) \big) < \omega^{-1}\big( \pi(t) \big)} = \noninversions(\omega, \pi(t))
+\]
+many $\se$ elbows by \cref{lem:rectangleInsertionAlgorithm} and since~$\pi < \omega$ in weak order.
+We thus conclude the proof by a direct application of \cref{lem:characterizationPipeDreams}.
 \vincent{Maybe we should argue that the pipes remain in the triangle.}
@@
 \begin{proof}
-By construction of the insertion algorithm, all \se{} elbows of the pipe~$\pi(t)$ inserted at step~$t$ are in contact with \nw{} elbows of pipes~$\pi(s)$ inserted at steps~$s < t$.
+By construction of the insertion algorithm, all southeast elbows of the pipe~$\pi(t)$ inserted at step~$t$ are in contact with northwest elbows of pipes~$\pi(s)$ inserted at steps~$s < t$.
 In other words, all edges in the contact graph of~$\insertion{\pi}{\omega}$ are of the form~$\pi(s) \to \pi(t)$ for some~$s < t$.
@@
 Reciprocally, consider a linear extension~$\pi$ of a pipe dream~$P$.
-Then~$\insertion{\pi}{\omega}$ and~$P$ have a common linear extension~$\pi$, so that~$\insertion{\pi}{\omega} = P$ by Proposition~\ref{prop:partition}.
+Then~$\insertion{\pi}{\omega}$ and~$P$ have a common linear extension~$\pi$, so that~$\insertion{\pi}{\omega} = P$ by \cref{prop:partition}.
 \end{proof}
@@
 In other words, the sets~$\set{\linearExtensions(P)}{P \in \acyclicPipeDreams(\omega)}$ are the fibers of the surjective insertion map~$\insertion{\cdot}{\omega}$.
-Note that this concludes the proof of the surjectivity left open in Proposition~\ref{prop:partition}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Pipe dream congruence}
-\label{subsec:pipeDreamCongruence}
-
-We now characterize the sets of linear extensions of pipe dreams in terms of a rewriting rule. We write the permutations of~$\fS_n$ as words in one-line notation.
+Note that this concludes the proof of the surjectivity left open in \cref{prop:partition}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Rewriting algorithm}
+\label{subsec:rewritingAlgorithm}
+
+We now characterize the sets of linear extensions of pipe dreams in terms of a rewriting rule.
+We write the permutations of~$\fS_n$ as words in one-line notation.
 
@@
 \[
-|\set{b \in U}{a < b < c \text{ and } \omega^{-1}(a) > \omega^{-1}(b) > \omega^{-1}(c)}| \ge |\set{b < a}{\omega^{-1}(b) < \omega^{-1}(c)}|,
-\]
-\vincent{Note that $b \in U$ on the right hand side by Lemma~\ref{lem:interval}.}
+\#\set{b \in U}{a < b < c \text{ and } \omega^{-1}(a) > \omega^{-1}(b) > \omega^{-1}(c)} \ge \#\set{b < a}{\omega^{-1}(b) < \omega^{-1}(c)},
+\]
+\vincent{Note that $b \in U$ on the right hand side by \cref{lem:interval}.}
 where~$a, b, c$ are elements of~$[n]$ while~$U, V$ are (possibly empty) words on~$[n]$.
@@
 \begin{proof}
-By Proposition~\ref{prop:fibersInsertion}, each fiber of~$\insertion{\cdot}{\omega}$ gathers the linear extensions of a pipe dream of~$\pipeDreams(\omega)$.
+By \cref{prop:fibersInsertion}, each fiber of~$\insertion{\cdot}{\omega}$ gathers the linear extensions of a pipe dream of~$\pipeDreams(\omega)$.
 Since the set of linear extensions of a poset is connected by simple transpositions, we just need to show that~$\pi \equiv_\omega \pi' \!\iff\!
@@
 At step~$t$ of the algorithm presented in the previous section, we have inserted the word~$U$.
-At that moment, let~$X_t$ (resp.~$X'_t$, resp~$Y_t$) denote the set of free \nw{} elbows in the rectangle~$[a] \times [\omega^{-1}(a)]$ (resp.~$[c] \times [\omega^{-1}(c)]$, resp.~$[a] \times [\omega^{-1}(c)]$).
-Applying the same argument as in Lemma~\ref{lem:rectangleInsertionAlgorithm}, we have
+At that moment, let~$X_t$ (resp.~$X'_t$, resp~$Y_t$) denote the set of free northwest elbows in the rectangle~$[a] \times [\omega^{-1}(a)]$ (resp.~$[c] \times [\omega^{-1}(c)]$, resp.~$[a] \times [\omega^{-1}(c)]$).
+Applying the same argument as in \cref{lem:rectangleInsertionAlgorithm}, we have
 \begin{gather*}
-|Y_t| = \max\big( |\set{b \in U}{b < a \text{ and } \omega^{-1}(b) < \omega^{-1}(c)}| \hspace{5cm} \\ \hspace{5cm} - |\set{b \in U}{a < b < c \text{ and } \omega^{-1}(a) > \omega^{-1}(b) > \omega^{-1}(c)}|, 0\big).
+\# Y_t = \max\big( \#\set{b \in U}{b < a \text{ and } \omega^{-1}(b) < \omega^{-1}(c)} \hspace{5cm} \\ \hspace{5cm} - \; \#\set{b \in U}{a < b < c \text{ and } \omega^{-1}(a) > \omega^{-1}(b) > \omega^{-1}(c)}, 0\big).
 \end{gather*}
-It follows that~$U ac V \equiv_\omega U ca V \iff |Y_t| = 0$.
+It follows that~$U ac V \equiv_\omega U ca V \iff \# Y_t = 0$.
 However, $Y_t = 0$ if and only if all elbows of~$X_t$ are in~$[a] \times [\omega^{-1}(c), \omega^{-1}(a)]$ and all elbows of~$X'_t$ are in~$[a,c] \times [\omega^{-1}(c)]$.
@@
 \)
-are the permutations avoiding the patterns~$b_1 - \cdots - b_k - ca$ (resp.~$b_1 - \cdots - b_k - ac$) where $k = |\set{b < a}{\omega^{-1}(b) < \omega^{-1}(c)}|$.
+are the permutations avoiding the patterns~$b_1 - \cdots - b_k - ca$ (resp.~$b_1 - \cdots - b_k - ac$) where $k = \#\set{b < a}{\omega^{-1}(b) < \omega^{-1}(c)}$.
 \end{proposition}
@@
 \begin{proof}
-This is an immediate consequence of Proposition~\ref{prop:congruence}: a permutation~$\pi$ is minimal (resp.~maximal) in its $\equiv_\omega$-congruence class if and only if it contains no consecutive exchangeable entries~$ca$ (resp.~$ac$) with~$a < c$.
-\end{proof}
-
-To sum up, there are three equivalent ways to partition the interval~$[e,\omega]$ of the weak order:
-\vincent{In fact, we should write 4 different ways, the last one being the sweeping algorithm.}
-\begin{itemize}
-\item by the sets of linear extensions~$\linearExtensions(P)$ of all pipe dreams of~$\acyclicPipeDreams(\omega)$,
-\item by the fibers of the insertion map~$\insertion{\cdot}{\omega}$,
-\item by the classes of the pipe dream congruence~$\equiv_\omega$.
-\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Lattice of acyclic pipe dreams}
-\label{sec:latticeAcyclicPipeDreams}
-
-Based on the result of the previous section, we now show that the pipe dream congruence~$\equiv_\omega$ is a lattice congruence of the interval~$[e,\omega]$ of weak order for any~$\omega \in \fS_n$.
-We extend the proof of~\cite{Pilaud-BrickAlgebra} which treated the particular case of~$\omega = [1, \dots, k, n-k, \dots, k+1, n-k+1, \dots, n]$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Lattice congruences and lattice quotients}
-\label{subsec:latticeCongruences}
-
-We first remind the reader with the definition of these congruences and refer to~\cite{Reading-LatticeCongruences, Reading-CambrianLattices} for further details.
-
-An \defn{order congruence} is an equivalence relation~$\equiv$ on a poset~$P$ such that:
-\begin{enumerate}[(i)]
-\item Every equivalence class under~$\equiv$ is an interval of~$P$.
-\item The projection~$\projDown : P \to P$ (resp.~$\projUp : P \to P$), which maps an element of~$P$ to the minimal (resp.~maximal) element of its equivalence class, is order preserving.
-\end{enumerate}
-The \defn{quotient}~$P/{\equiv}$ is a poset on the equivalence classes of~$\equiv$, where the order relation is defined by~$X \le Y$ in~$P/{\equiv}$ iff there exists representatives~$x \in X$ and~$y \in Y$ such that~$x \le y$ in~$P$.
-The quotient~$P/{\equiv}$ is isomorphic to the subposet of~$P$ induced by~$\projDown(P)$ (or equivalently by~$\projUp(P)$).
-
-If moreover~$P$ is a finite lattice, then~$\equiv$ is a automatically \defn{lattice congruence}, meaning that it is compatible with meets and joins: for any~$x \equiv x'$ and~$y \equiv y'$, we have~$x \meet y \equiv x' \meet y'$ and~$x \join y \equiv x' \join y'$.
-The poset quotient~$P/{\equiv}$ then inherits a lattice structure where the meet~$X \meet Y$ (resp.~the join~$X \join Y$) of two congruence classes~$X$ and~$Y$ is the congruence classe of~$x \meet y$ (resp.~of~$x \join y$) for arbitrary representatives~$x \in X$ and~$y \in Y$.
-
-%Lattice quotient of the weak order.
-%Connection to the increasing flip poset.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{The pipe dream congruence is a lattice congruence}
-\label{subsec:proofCongruence}
-
-We are now ready to prove the main statement of this note. Recall that an interval in a lattice is itself a lattice, so that the weak order on~$[e,\omega]$ has a lattice structure.
-
-\begin{theorem}\label{thm_pipe_latticecongruence}
-For any permutation~$\omega \in \fS_n$, the pipe dream congruence~$\equiv_\omega$ is a lattice congruence of the interval~$[e,\omega]$ of the weak order.
-\end{theorem}
-
-\begin{proof}
-We already observed in Proposition~\ref{prop:intervals} that the $\equiv_\omega$-congruence classes are intervals of the weak order.
-We therefore just need to show that~$\tau < \tau'$ implies~$\min(C) < \min(C')$ and $\max(C) < \max(C')$ for any two permutations~$\tau, \tau' \in [e,\omega]$ from distinct $\equiv_\omega$-congruence classes~$C,C'$.
-We only prove the result for the maximums, the proof for the minimums being similar.
-We first observe that we can assume that~$\tau' = \tau s_i$ for some simple transposition~${s_i = (i \;\, i+1)}$ which is not a descent of~$\tau$.
-The proof then works by induction on the weak order distance between~$\tau$ and~$\max(C)$.
-If~$\tau = \max(C)$, the result is immediate as~$\max(C) = \tau < \tau' \le \max(C')$.
-Otherwise, consider a permutation~$\sigma$ in~$C$ covering~$\tau$ in weak order.
-We write~$\sigma = \tau s_j$, and $s_j$ is not a descent of~$\tau$.
-We now distinguish four cases, according to the relative positions of~$i$ and~$j$:
-\begin{enumerate}[(1)]
-\item If~$i > j+1$, we have~$\tau = UabVcdW$, $\tau' = UabVdcW$ and~$\sigma = UbaVcdW$ for some letters~$a < b$ with~$\omega^{-1}(a) > \omega^{-1}(b)$, some letters~$c < d$ with~$\omega^{-1}(c) > \omega^{-1}(d)$ and some words~$U,V,W$.
-Define~$\sigma' \eqdef \tau s_i s_j = \tau' s_j = \sigma s_i = UbaVdcW$.
-Since~$\tau \equiv_\omega \sigma$, there exist $k = |\set{u < a}{\omega^{-1}(u) < \omega^{-1}(b)}|$ $\equiv_\omega$-congruence witnesses~$u_1, \dots, u_k$ in the word~$U$, with~$a < u_\ell < b$ and~$\omega^{-1}(a) > \omega^{-1}(u_\ell) > \omega^{-1}(c)$ for all~$\ell \in [k]$.
-These letters are also $\equiv_\omega$-congruence witnesses for the equivalence~$\tau' \equiv_\omega \sigma'$.
-Moreover, $\sigma < \sigma'$ since~$c < d$.
-\item If~$i = j+1$, we have~$\tau = UabcW$, $\tau' = UacbW$ and~$\sigma = UbacW$ for some letters~${a < b < c}$ with~$\omega^{-1}(a) > \omega^{-1}(b) > \omega^{-1}(c)$ (since~$\tau < \omega$ in weak order by asumption) and some words~$U,W$.
-Define~$\sigma' \eqdef \tau s_i s_j s_i = \tau' s_j s_i = \sigma s_i s_j = UcbaW$.
-Since~$\tau \equiv_\omega \sigma$, there exist $k = |\set{u < a}{\omega^{-1}(u) < \omega^{-1}(b)}|$ $\equiv_\omega$-congruence witnesses~$u_1, \dots, u_k$ in the word~$U$, with ${a < u_\ell < b}$ and~$\omega^{-1}(a) > \omega^{-1}(u_\ell) > \omega^{-1}(c)$ for all~$\ell \in [k]$.
-Since~$b < c$ and~$\omega^{-1}(b) > \omega^{-1}(c)$, these letters are also $\equiv_\omega$-congruence witnesses for the equivalences~${\tau' \equiv_\omega \tau' s_j \equiv_\omega \tau' s_j s_i = \sigma'}$.
-(Moreover, note that there are indeed enough witnesses for the equivalence~$\tau' \equiv_\omega \tau' s_j$ since ${k = |\set{u < a}{\omega^{-1}(u) < \omega^{-1}(b)}| \ge |\set{u < a}{\omega^{-1}(u) < \omega^{-1}(c)}|}$).
-Finally, since~$a < b < c$, we have~$\sigma < \sigma'$.
-\item If~$i = j-1$, we proceed similarly as in Situation~(2).
-\item If~$i < j-1$, we proceed similarly as in Situation~(1).
-\end{enumerate}
-In all cases, we have~$\tau \equiv_\omega \sigma < \sigma' \equiv_\omega \tau'$. Since~$\sigma$ is closer to~$\max(C)$ than~$\tau$, we obtain that ${\max(C) < \max(C')}$ by induction hypothesis.
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Lattice of acyclic pipe dreams}
-\label{subsec:proofCongruence}
-
-Finally, we need to show that the lattice quotient~$[e,\omega]/\equiv_\omega$ is isomorphic to the increasing flip poset on~$\acyclicPipeDreams(\omega)$.
-This is the purpose of the following statement.
-
-\begin{proposition}
-For any pipe dreams~$P, P' \in \acyclicPipeDreams(\omega)$, the following assertions are equivalent:
-\begin{enumerate}[(i)]
-\item $P < P'$ in the increasing flip poset on~$\acyclicPipeDreams(\omega)$,
-\item there exist linear extensions~$\pi$ of~$P$ and~$\pi'$ of~$P'$ such that~$\pi < \pi'$ in weak order,
-\item the minimal (resp.~max) linear extensions~$\pi$ of~$P$ and~$\pi'$ of~$P$ satisfy~$\pi < \pi'$ in weak order.
-\end{enumerate}
-\end{proposition}
-
-\begin{proof}
-Consider two distinct acyclic pipe dreams~$P, P' \in \acyclicPipeDreams(\omega)$ and their $\equiv_\omega$-congruence~classes~$C, C'$.
-If there exist representatives~$\pi = UijV \in C$ and~$\pi' = UjiV \in C'$ which are adjacent in weak order, then~$P = \insertion{\pi}{\omega}$ and~$P' = \insertion{\pi'}{\omega}$ differ by the flip of the first/last elbow between the pipes~$i$ and~$j$, by definition of the map~$\insertion{\cdot}{\omega}$.
-Conversely, if~$P$ and~$P'$ differ by the flip of the first/last elbow between the pipes~$i$ and~$j$, then $i$ and~$j$ are connected in the contact graph~$P\contact$, so that there exists a linear extension~$\pi = UijV$ of~$P\contact$ where~$i$ and~$j$ are consecutive.
-Let~$\pi' = UjiV$ be the permutation obtained by the switch of~$i$ and~$j$ in~$\pi$.
-By definition of the map~$\insertion{\cdot}{\omega}$, the pipe dream~$\insertion{\pi'}{\omega}$ is obtained by flipping the first elbow between the pipes~$i$ and~$j$ in~$\insertion{\pi}{\omega}$.
-The representatives~$\pi \in C$ and~$\pi' \in C'$ are thus adjacent in weak order.
-This proves that~$\insertion{\cdot}{\omega}$~induces an isomorphism from the quotient lattice of the interval~$[e,\omega]$ of the weak order by the $\equiv_\omega$-congruence to the increasing flip order on acyclic pipe dreams of~$\acyclicPipeDreams(\omega)$.
-In turn, since the $\equiv_\omega$-congruence is a lattice congruence, this quotient lattice is isomorphic to the subposet of the weak order induced by the minimal (resp.~maximal) elements of the classes.
-See~\cite{Reading-LatticeCongruences, Reading-CambrianLattices} for further details on quotient lattices.
-\vincent{I am not sure anymore that this proof is correct. At least this could require more explanations.}
-\end{proof}
-
-\begin{corollary}\label{cor_acyclicpipedreams_lattice}
-For any permutation~$\omega \in \fS_n$:
-\begin{enumerate}
-\item The increasing flip poset on~$\acyclicPipeDreams(\omega)$ is isomorphic to the lattice quotient~$[e,\omega]/\equiv_\omega$.
-\item The increasing flip poset on~$\acyclicPipeDreams(\omega)$ is a lattice.
-\end{enumerate}
-\end{corollary}
+This is an immediate consequence of \cref{prop:congruence}: a permutation~$\pi$ is minimal (resp.~maximal) in its $\equiv_\omega$-congruence class if and only if it contains no consecutive exchangeable entries~$ca$ (resp.~$ac$) with~$a < c$.
+\end{proof}
 
@@
 % The binary search tree insertion map and the canopy map factorize the recoil map: $\surjectionBrickZono[] \circ \surjectionPermBrick[] = \surjectionPermZono[]$.
-This combinatorial fact can also be understood on the geometry of the normal fans of the permutahedron, the associahedron and the cube, see Section~\ref{subsec:normalFans}.
-
-Before introducing the canopy, let us define the $\omega$-recoils. For this, consider the graph~$G(\omega)$ with vertex set~$[n]$ and edge set
-\[
-\bigset{ij}{i < j \text{ and } j-i \le |\set{k < i}{\omega^{-1}(k) < \omega^{-1}(j)}|}.
+This combinatorial fact can also be understood on the geometry of the normal fans of the permutahedron, the associahedron and the cube, see \cref{subsec:normalFans}.
+
+Before introducing the canopy, let us define the $\omega$-recoils.
+For this, consider the graph~$G(\omega)$ with vertex set~$[n]$ and edge set
+\[
+\bigset{ij}{i < j \text{ and } j-i \le \#\set{k < i}{\omega^{-1}(k) < \omega^{-1}(j)}}.
 \]
@@
 \begin{definition}
-The \defn{$\omega$-recoil scheme} of a permutation~$\pi \in [e,\omega]$ is the orientation~${\recoils{\pi}{\omega} \in \acyclicOrientations(\omega)}$ where for all~$i < j \in [n]$ such that~$j-i \le |\set{k < i}{\omega^{-1}(k) < \omega^{-1}(j)}|$, the edge~$ij$ is oriented~$i \to j$ if~$\pi^{-1}(i) < \pi^{-1}(j)$ and~$j \to i$ if~$\pi^{-1}(j) < \pi^{-1}(i)$.
+The \defn{$\omega$-recoil scheme} of a permutation~$\pi \in [e,\omega]$ is the orientation~${\recoils{\pi}{\omega} \in \acyclicOrientations(\omega)}$ where for all~$i < j \in [n]$ such that~$j-i \le \#\set{k < i}{\omega^{-1}(k) < \omega^{-1}(j)}$, the edge~$ij$ is oriented~$i \to j$ if~$\pi^{-1}(i) < \pi^{-1}(j)$ and~$j \to i$ if~$\pi^{-1}(j) < \pi^{-1}(i)$.
 We call \defn{$\omega$-recoil map} the map~$\recoils{\cdot}{\omega} : [e,\omega] \to \acyclicOrientations(\omega)$.
@@
 We now define a generalization of the canopy map for pipe dreams in~$\acyclicPipeDreams(\omega)$.
-To ensure that Definition~\ref{def:canopy} is valid, we need the following simple observation on comparisons of ``close'' pipes in a pipe dream.
+To ensure that \cref{def:canopy} is valid, we need the following simple observation on comparisons of ``close'' pipes in a pipe dream.
 
@@
 \label{lem:canopy}
-If~$i < j$ satisfy~$j-i \le |\set{k < i}{\omega^{-1}(k) < \omega^{-1}(j)}|$, then the pipes~$i$ and~$j$ in any acyclic pipe dream~$P \in \acyclicPipeDreams(\omega)$ are comparable~for~$\contactLess{P}$.
+If~$i < j$ satisfy~$j-i \le \#\set{k < i}{\omega^{-1}(k) < \omega^{-1}(j)}$, then the pipes~$i$ and~$j$ in any acyclic pipe dream~$P \in \acyclicPipeDreams(\omega)$ are comparable~for~$\contactLess{P}$.
 \end{lemma}
@@
 If pipes~$i$ and~$j$ were incomparable in~$\contactLess{P}$, there would be two $\equiv_\omega$-congruent permutations~$UijV \equiv_\omega UjiV$.
-However, the assumption contradicts the definition of the $\equiv_\omega$-conguence in Definition~\ref{def:congruence}.
+However, the assumption contradicts the definition of the $\equiv_\omega$-conguence in \cref{def:congruence}.
 \end{proof}
@@
 \label{def:canopy}
-The \defn{canopy} of a pipe dream~$P \in \acyclicPipeDreams(\omega)$ is the orientation~$\canopy{P} \in \acyclicOrientations(\omega)$ where for all~$i < j \in [n]$ such that~$j-i \le |\set{k < i}{\omega^{-1}(k) < \omega^{-1}(j)}$, the edge~$ij$ is oriented~$i \to j$ if~$i \contactLess{P} j$ and~$j \to i$ if~$j \contactLess{P} i$.
-It indeed defines an acyclic orientation of~$G(\omega)$ by Lemma~\ref{lem:canopy}.
+The \defn{canopy} of a pipe dream~$P \in \acyclicPipeDreams(\omega)$ is the orientation~$\canopy{P} \in \acyclicOrientations(\omega)$ where for all~$i < j \in [n]$ such that~$j-i \le \#\set{k < i}{\omega^{-1}(k) < \omega^{-1}(j)}$, the edge~$ij$ is oriented~$i \to j$ if~$i \contactLess{P} j$ and~$j \to i$ if~$j \contactLess{P} i$.
+It indeed defines an acyclic orientation of~$G(\omega)$ by \cref{lem:canopy}.
 We call \defn{canopy} the map~$\canopy{\cdot}: \acyclicPipeDreams(\omega) \to \acyclicOrientations(\omega)$.
@@
 \begin{proof}
-Consider a permutation~$\pi$ and let~$i < j \in [n]$ be such that~$j-i \le |\set{k < i}{\omega^{-1}(k) < \omega^{-1}(j)}$.
+Consider a permutation~$\pi$ and let~$i < j \in [n]$ be such that~$j-i \le \#\set{k < i}{\omega^{-1}(k) < \omega^{-1}(j)}$.
 Assume that the edge~$ij$ is oriented from~$i$ to~$j$.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{Sortability and alignement}
@@
 \begin{itemize}
-\item a pattern avoiding condition, see Proposition~\ref{prop:patternAvoiding}.
+\item a pattern avoiding condition, see \cref{prop:patternAvoiding}.
 \item ``$\omega$-sortability'', see~\cite{Reading-sortableElements}.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{Hopf algebra}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Subword complexes}
+\label{subsec:subwordComplexes}
+
+Pipe dreams are a very particular family of the family of subword complexes.
+Consider a Coxeter system~$(W,S)$, where~$W$ is a finite Coxeter group and~$S$ is the set of simple reflections of~$W$.
+We denote by~$e$ (resp.~$\wo$) the identity (resp.~longest element) of~$W$.
+Let~$Q \eqdef q_1 \dots q_m \in S^*$ be a word on the alphabet formed by the simple generators of~$W$ and~$w \in W$.
+The \defn{subword complex}~$\subwordComplex(Q,w)$ is the simplicial complex whose ground set~$[m]$ are the positions in~$Q$ and whose facets are the complements of the reduced expressions for~$w$ in~$Q$.
+
+It is known that~$\subwordComplex(Q,w)$ is either a ball or a sphere, in particular it is a pseudomanifold (with or without boundary).
+The flip graph of~$\subwordComplex(Q,w)$ is the graph whose vertices are the facets of~$\subwordComplex(Q,w)$ and whose edges are the ridges of~$\subwordComplex(Q,w)$.
+If~$F,F'$ are two adjacent facets with~$F \ssm \{p\} = F' \ssm \{p'\}$, we say that the flip is \defn{increasing} when~$p < p'$.
+The increasing flip graph was studied in particular in~\cite{PilaudStump-ELlabelings}.
+It is known to be acyclic, and its transitive closure is an EL-shellable poset (see~\cite{PilaudStump-ELlabelings} for the precise definition and references).
+
+There is also a notion of acyclicity for subword complexes.
+It is based on the notion of \defn{root configuration}~$\Roots(F)$ of a facet~$F$ of~$\subwordComplex(Q,w)$.
+We skip the details and refer to~\cite{CeballosLabbeStump, PilaudStump-brickPolytope} for details.
+The facet~$F$ is \defn{acyclic} if its root configuration is pointed (meaning that it generates a pointed cone).
+
+\begin{example}
+Consider the symmetric group~$\fS_{n+1}$ generated by the set of simple transpositions $\set{\tau_i}{i \in [n]}$ where~$\tau_i \eqdef (i \; i+1)$.
+For a permutation~$\omega \in \fS_{n+1}$, the pipe dreams of~$\pipeDreams(\omega)$ correspond to the facets of the subword complex~$\subwordComplex(Q,\omega)$ with~$Q = \tau_1, \tau_2, \dots, \tau_n, \tau_1, \tau_2, \dots, \tau_{n-1}, \dots, \tau_1, \tau_2, \tau_1$.
+% The notions of flips, increasing flips and acyclic pipe dreams transpose in the world of subword complexes.
+\end{example}
+
+\begin{example}
+For any Coxeter group~$W$ and any Coxeter element~$c \in W$ (a product of all generators of~$S$ in a given arbitrary order), let~$\wo(c)$ denote the $c$-sorting word of~$\wo$ (see \cite{Reading-CambrianLattices} for details).
+Extending the observation of \cref{subsec:reversingPipeDreams}, it was shown in~\cite{CeballosLabbeStump} that the subword complex~$\subwordComplex(c\wo(c), \wo)$ is isomorphic to the cluster complex of type~$W$.
+In particular, the increasing flip graph is the Hasse diagram of the $c$-Cambrian lattice of~\cite{Reading-CambrianLattices}.
+\end{example}
+
+In contrast to the previous example, consider the word~$Q = \tau_1 \tau_2 \tau_3 \tau_2 \tau_1 \tau_2 \tau_3 \tau_2 \tau_1$ on the simple generators of the symmetric group~$\fS_4$ and the subword complex~$\subwordComplex(Q,\wo)$.
+Note that all facets in this subword complex are acyclic.
+It is shown in~\cite[Rem.~5.12]{PilaudStump-brickPolytope} that its increasing flip poset is not a lattice.
+This shows that neither the increasing flip poset, nor the acyclic increasing flip poset are lattices in general, even in type~$A$.
+In this note, we investigate the case of acyclic pipe~dreams.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Subword complexes}
-The objective of this section is to partially extend the results about the lattice structure of acyclic pipe dreams, presented in Section~\ref{sec:latticeAcyclicPipeDreams}, to the wider context of subword complexes of finite type.
+
+The objective of this section is to partially extend the results about the lattice structure of acyclic pipe dreams, presented in \cref{sec:latticeAcyclicPipeDreams}, to the wider context of subword complexes of finite type.
 Before doing so, we recall some preliminaries about finite Coxeter groups and subword complexes.
-We refer to~\cite{bjorner_coxeterGroups_2005,humphreys_reflectionGroups_1990} for more details on Coxeter groups.
+We refer to~\cite{BjornerBrenti, Humphreys} for more details on Coxeter groups.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 Throughout this paper, we only consider Coxeter groups which are finite.
-They are classified in terms of Dynkin diagrams, and arise from finite root systems, see~\cite{humphreys_reflectionGroups_1990}.
+They are classified in terms of Dynkin diagrams, and arise from finite root systems, see~\cite{Humphreys}.
 
@@
 \begin{align}\label{def_inversionset}
-\Inv(w) := \Phi^+ \cap w(\Phi^-). 
+\Inv(w) \eqdef \Phi^+ \cap w(\Phi^-).
 \end{align}
@@
 \begin{align}\label{def_inversionset2}
-\Inv(w) := \{
-\alpha_{w_1}, w_1(\alpha_{w_2}),\dots , w_1w_2\dots w_{\ell-1}(\alpha_{w_\ell})
-\}
+\Inv(w) \eqdef \{\alpha_{w_1}, w_1(\alpha_{w_2}),\dots , w_1w_2\dots w_{\ell-1}(\alpha_{w_\ell})\}
 \end{align}
@@
 \begin{align}
-\Ninv(w) &:= \Phi^+ \cap w(\Phi^+) \label{def_noninversionset} \\
+\Ninv(w) & \eqdef \Phi^+ \cap w(\Phi^+) \label{def_noninversionset} \\
 & =\Inv(w\wo)
@@
 
-Motivated by their study of Gröbner geometry of Schubert varieties~\cite{KnutsonMiller-GroebnerGeometry}, Knutson and Miller~\cite{knutson_subword_2004} introduced a remarkable family of simplicial complexes in the context of Coxeter groups.
+Motivated by their study of Gröbner geometry of Schubert varieties~\cite{KnutsonMiller-GroebnerGeometry}, Knutson and Miller~\cite{KnutsonMiller-subwordComplex} introduced a remarkable family of simplicial complexes in the context of Coxeter groups.
 
@@
 \[J=I\smallsetminus \{i\} \cup\{j\}\]
-for some $i\in I$ and $j\in J$ with $i\neq j$. If $i<j$, the flip from $I$ to $J$ is called an \defn{increasing flip}.
-
-The increasing flip graph on facets of the subword complex is an acyclic graph which has a unique source and a unique sink~\cite{pilaud_greedy_2012,pilaud_el_labelling_2013}.
+for some $i\in I$ and $j\in J$ with $i\neq j$.
+If $i<j$, the flip from $I$ to $J$ is called an \defn{increasing flip}.
+
+The increasing flip graph on facets of the subword complex is an acyclic graph which has a unique source and a unique sink~\cite{Pilaud-greedyFlipTree, PilaudStump-ELlabelings}.
 These two special facets are called the \defn{greedy facet} $\greedyFacet$ and the \defn{antigreedy facet} $\antiGreedyFacet$.
@@
     \[
-    \rootFunction{I}{k} := \prod Q_{[k-1]\smallsetminus I}(\alpha_{q_k}).
+    \rootFunction{I}{k} \eqdef \prod Q_{[k-1]\smallsetminus I}(\alpha_{q_k}).
     \]
@@
 \end{definition}
-The root function is a useful and well established tool in the study of subword complexes. For instance, they can be used to fully understand flips. 
-\begin{lemma}[{\cite{CeballosLabbeStump,knutson_subword_2004}}]
+
+The root function is a useful and well established tool in the study of subword complexes.
+For instance, they can be used to fully understand flips.
+
+\begin{lemma}[{\cite{CeballosLabbeStump, KnutsonMiller-subwordComplex}}]
 \label{lem_rootfunction_flips}
-Let $I$ be a facet of the subword complex~$\subwordComplex(Q,w)$. The following hold:
+Let $I$ be a facet of the subword complex~$\subwordComplex(Q,w)$.
+The following hold:
 \begin{enumerate}
-    \item $i \in I$ is flippable if and only if $|\rootFunction{I}{i}|\in \Inv(w)$.
-    \item If $i \in I$ is flippable, it can be flipped to the unique $j\in [m]\smallsetminus I$ such that $\rootFunction{I}{j}=|\rootFunction{I}{i}|$. 
-    The flip is increasing ($i<j$) when $\rootFunction{I}{i}\in \Phi^+$ and decreasing ($i>j$) when $\rootFunction{I}{i}\in \Phi^-$. \label{lem_rootfunction_flips2}
+    \item $i \in I$ is flippable if and only if $\pm \rootFunction{I}{i} \in \Inv(w)$.
+    \item If $i \in I$ is flippable, it can be flipped to the unique $j\in [m]\smallsetminus I$ such that $\rootFunction{I}{j} = \pm\rootFunction{I}{i}$.
+    The flip is increasing ($i<j$) when $\rootFunction{I}{i}\in \Phi^+$ and decreasing ($i>j$) when $\rootFunction{I}{i}\in \Phi^-$.\label{lem_rootfunction_flips2}
     \item If $I'=I\smallsetminus \{i\}\cap \{i'\}$ is a facet obtained from $I$ by flipping $i$ to $i'$ with $i<i'$, then
@@
 \label{lem_acyclic_nonempty}
-$\linearExtensions(I)\neq \emptyset$ if and only if $I$ is acyclic.
+$\linearExtensions(I)\neq \varnothing$ if and only if $I$ is acyclic.
 \end{lemma}
@@
   & \longleftrightarrow  &  \Roots(I)\subseteq \pi(\Phi^+) \text{ for some } \pi\in W \\
-  & \longleftrightarrow  &  \linearExtensions(I) \neq \emptyset 
+  & \longleftrightarrow  &  \linearExtensions(I) \neq \varnothing 
 \end{array}
@@
 \end{lemma}
-\begin{proof}
-This is straight forward from the definition of inversions and non-inversion of $\pi$. In fact, multiplying Equation~\eqref{def_inversionset} by $-1$ we deduce $\pi(\Phi^+)\cap \Phi^-=-\Inv(\pi)$. 
+
+\begin{proof}
+This is straight forward from the definition of inversions and non-inversion of $\pi$.
+In fact, multiplying Equation~\eqref{def_inversionset} by $-1$ we deduce $\pi(\Phi^+)\cap \Phi^-=-\Inv(\pi)$.
 Furthermore,  
@@
 \begin{lemma}\label{lem_linearext_greedyfacets}
-    Let $\greedyFacet$ and $\antiGreedyFacet$ be the greedy and antigreedy facets of $\subwordComplex(Q,w)$, respectively. Then 
+    Let $\greedyFacet$ and $\antiGreedyFacet$ be the greedy and antigreedy facets of $\subwordComplex(Q,w)$, respectively.
+Then 
     \begin{enumerate}
@@
     The greedy facet $\greedyFacet$ is the unique facet for which every flip (if any) is increasing.
-By Lemma~\ref{lem_rootfunction_flips}~\eqref{lem_rootfunction_flips2}, this implies that $\greedyFacet$ is the unique facet $I$ such that $\Roots(I)\subseteq \Phi^+ = e(\Phi^+)$.
+By \cref{lem_rootfunction_flips}~\eqref{lem_rootfunction_flips2}, this implies that $\greedyFacet$ is the unique facet $I$ such that $\Roots(I)\subseteq \Phi^+ = e(\Phi^+)$.
 This proves parts (1) and (3) of the Lemma.
@@
     For part (2) we need to analyze the possibilities for the set $\Roots(\antiGreedyFacet)$.
-By Lemma~\ref{lem_rootfunction_flips}~\eqref{lem_rootfunction_flips2}, if $i\in \antiGreedyFacet$ is flippable then $\rootFunction{\antiGreedyFacet}{i}\in -\Inv(w)$.
+ By \cref{lem_rootfunction_flips}~\eqref{lem_rootfunction_flips2}, if $i\in \antiGreedyFacet$ is flippable then $\rootFunction{\antiGreedyFacet}{i}\in -\Inv(w)$.
 Furthermore, if $i\in \antiGreedyFacet$ is not flippable then $\rootFunction{\antiGreedyFacet}{i}\in \Ninv(w)$.
@@
 \begin{remark}
-The concept of linear extensions of acyclic facets of subword complexes are a natural generalization of linear extensions of contact graphs of acyclic pipe dreams that we introduced in Section~\ref{subsec:linearExtensions}.
+The concept of linear extensions of acyclic facets of subword complexes are a natural generalization of linear extensions of contact graphs of acyclic pipe dreams that we introduced in \cref{subsec:linearExtensions}.
 Indeed ... 
@@
 \subsection{Two fundamental theorems about linear extensions}
-In this section, we present our two main results about linear extensions for subword complexes, Theorem~\ref{thm_subword_linearextensions_A} and Theorem~\ref{thm_subword_linearextensions_B}.
+In this section, we present our two main results about linear extensions for subword complexes, \cref{thm_subword_linearextensions_A} and \cref{thm_subword_linearextensions_B}.
 
@@
 We say that $A$ is \defn{closed by intervals} if $a,b\in A$ implies that $[a,b]\in A$, where $[a,b]=\{c: a \leq c\leq b\}$.
+\vincent{I usually say ``order-convex''}
 
 \begin{theorem}\label{thm_subword_linearextensions_A}
-Let~$\subwordComplex(Q,w)$ be a non-empty subword complex. The following hold:
+Let~$\subwordComplex(Q,w)$ be a non-empty subword complex.
+The following hold:
 \begin{enumerate}
@@
 \hfill (containment)
-\item If $I_1\neq I_2$ then $\linearExtensions(I_1)\cap \linearExtensions(I_2)=\emptyset$. 
+\item If $I_1\neq I_2$ then $\linearExtensions(I_1)\cap \linearExtensions(I_2)=\varnothing$.
 \label{thmA_item3}
@@
 \end{enumerate}
+\vincent{Replace ``containement'' by ``cover'' and ``partition'' by ``disjoint''?}
 \end{theorem}
@@
 
-\begin{proof}[Proof of Theorem~\ref{thm_subword_linearextensions_A}]
 We will prove the items of the theorem one by one.
 
-Proof of \eqref{thmA_item1}:
+\begin{proof}[Proof of \cref{thm_subword_linearextensions_A} \eqref{thmA_item1}]
 Let $\pi\in \linearExtensions(I)$ for some facet $I$.
 We need to show that if $\pi'<\pi$ then there exist another facet $I'$ such that $\pi'\in \linearExtensions(I')$.
-It is enough to show this when $\pi=\pi' s$ for some $s\in S$ such that $\ell(\pi'
-)<\ell(\pi)$.
-
-By definition, $\pi\in \linearExtensions(I)$ if and only if $\Roots(I)\subseteq \pi(\Phi^+)$. Now, 
+It is enough to show this when $\pi=\pi' s$ for some $s\in S$ such that $\ell(\pi')<\ell(\pi)$.
+
+By definition, $\pi\in \linearExtensions(I)$ if and only if $\Roots(I)\subseteq \pi(\Phi^+)$.
+Now, 
 \[
@@
 The position $i$ of the last $\beta$ is used in the reduced expression of $w$ in the complement of $I$, that is $i\notin I$.
-The positions of the other $\beta$'s and $-\beta$'s all belong to~$I$, and can all be flipped to $i$ (see Lemma~\ref{lem_rootfunction_flips}~\eqref{lem_rootfunction_flips2}).
+The positions of the other $\beta$'s and $-\beta$'s all belong to~$I$, and can all be flipped to $i$ (see \cref{lem_rootfunction_flips}~\eqref{lem_rootfunction_flips2}).   
 In particular, the position $j$ of the last $-\beta$ belongs to $I$, and it can be flipped to $i$ creating a new facet $I'=I\smallsetminus \{j\} \cap \{i\}$.
@@
 Thus, $\pi'\in \linearExtensions(I')$ as desired.
-
-Proof of~\eqref{thmA_item2}: 
+\end{proof}
+
+\begin{proof}[Proof of \cref{thm_subword_linearextensions_A}~\eqref{thmA_item2}]
 By part \eqref{thmA_item1}, the union of all linear extensions of facets is a lower set.
 So, we just need to show that $w$ belongs to this set.
-This follows from $w\in \linearExtensions(\antiGreedyFacet)$, which was proven in    Lemma~\ref{lem_linearext_greedyfacets}.
-
-Proof of~\eqref{thmA_item3}: 
+This follows from $w\in \linearExtensions(\antiGreedyFacet)$, which was proven in \cref{lem_linearext_greedyfacets}.
+\end{proof}
+
+\begin{proof}[Proof of \cref{thm_subword_linearextensions_A}~\eqref{thmA_item3}]
 We will show that if there is an element $\pi\in \linearExtensions(I_1)\cap \linearExtensions(I_2)$ then $I_1= I_2$.
-We already showed this for $\pi=e$ in Lemma~\ref{lem_linearext_greedyfacets}.
+We already showed this for $\pi=e$ in \cref{lem_linearext_greedyfacets}.
 
@@
 The resulting two facets are different and their linear extensions contain $e$.
-This is a contradiction to Lemma~\ref{lem_linearext_greedyfacets}.
-
-Proof of~\eqref{thmA_item4}: 
-Let $\pi_1,\pi_2\in \linearExtensions(I)$ and assume $\pi_1<\pi_2$. We need to show that if $\pi_1\leq \pi \leq \pi_2$ then~$\pi \in \linearExtensions(I)$. 
-By definition of linear extensions and Lemma~\ref{lem_pi_phiplus_inv_ninv} we have
+This is a contradiction to \cref{lem_linearext_greedyfacets}.  
+\vincent{This paragraph is not needed. Say it better in the first paragraph of the proof of (3).}
+\end{proof}
+
+\begin{proof}[Proof of \cref{thm_subword_linearextensions_A}~\eqref{thmA_item4}]
+Let $\pi_1,\pi_2\in \linearExtensions(I)$ and assume $\pi_1<\pi_2$.
+We need to show that if $\pi_1\leq \pi \leq \pi_2$ then~$\pi \in \linearExtensions(I)$.
+By definition of linear extensions and \cref{lem_pi_phiplus_inv_ninv} we have
 \[
@@
 the \defn{set of linear extensions of all facets} of $\subwordComplex(Q,w)$.
-Since $\linearExtensions(I)\neq \emptyset$ if and only if $I$ is acyclic (Lemma~\ref{lem_acyclic_nonempty}), we have the following straight forward corollary. 
+Since $\linearExtensions(I)\neq \varnothing$ if and only if $I$ is acyclic (\cref{lem_acyclic_nonempty}), we have the following straight forward corollary.
+
 \begin{corollary}\label{cor_linearextensions_partition}
@@
 
-As pointed out in Remark~\ref{rem_thmA}, there are subword complexes for which $[e,w] \neq \bigcup_{I\in\subwordFacets(Q,w)}$.
+As pointed out in \cref{rem_thmA}, there are subword complexes for which $[e,w] \neq \bigcup_{I\in\subwordFacets(Q,w)}$.
 Our second fundamental theorem describes a large family of cases where equality holds.
@@
 
-The proof of this theorem is based on the following proposition, which follows from~\cite[Theorem~3.1 and Corollary 3.3]{jahn_bruhat_2021}.
-
-\begin{proposition}[{\cite{jahn_bruhat_2021}}]\label{prop_jahnStump_intersection}
-    Let $\subwordComplex(Q,w)$ be a non-empty subword complex such that the word $Q$ contains a reduced expression of $\wo$. Then 
+The proof of this theorem is based on the following proposition, which follows from~\cite[Theorem~3.1 and Corollary 3.3]{JahnStump}.
+
+\begin{proposition}[{\cite{JahnStump}}]\label{prop_jahnStump_intersection}
+    Let $\subwordComplex(Q,w)$ be a non-empty subword complex such that the word $Q$ contains a reduced expression of $\wo$.
+Then 
     \[
@@
 \begin{proof}
-    We include a short proof here for self containment. We refer to~\cite{jahn_bruhat_2021} for the description of the notation $C^+(w,\cdot)$. 
-    By~\cite[Theorem~3.1]{jahn_bruhat_2021} we have
+    We include a short proof here for self containment.
+We refer to~\cite{JahnStump} for the description of the notation $C^+(w,\cdot)$.
+    By~\cite[Theorem~3.1]{JahnStump} we have
     \[
@@
     \]
-    The word $Q$ contains a reduced expression of $\wo$ if and only if $\DemazureProduct(Q)=\wo$. Furthermore, by~\cite[Corollary~3.3]{jahn_bruhat_2021} we have
+    The word $Q$ contains a reduced expression of $\wo$ if and only if $\DemazureProduct(Q)=\wo$.
+Furthermore, by~\cite[Corollary~3.3]{JahnStump} we have
     \[
@@
 
-\begin{proof}[Proof of Theorem~\ref{thm_subword_linearextensions_B}]
+\begin{proof}[Proof of \cref{thm_subword_linearextensions_B}]
 Assume $\pi\in \linearExtensions(I)$.
 We want to show that $\pi<w$.
-By Proposition~\ref{prop_jahnStump_intersection} we have 
+By \cref{prop_jahnStump_intersection} we have 
 \[
@@
 
-We start by setting $I^0=\emptyset$ to be the empty set. 
+We start by setting $I^0=\varnothing$ to be the empty set.
 Then we scan the word $Q=(q_1,\dots ,q_m)$ from left to right.
@@
     For $j=0$, $Q^0$ is the empty word which is reduced by definition.
-    Furthermore, $Q_{[m]\smallsetminus I^0 }=Q$ contains a reduced expression of $w$ because the subword complex is non-empty. The empty word is a prefix of this reduced expression.
+    Furthermore, $Q_{[m]\smallsetminus I^0 }=Q$ contains a reduced expression of $w$ because the subword complex is non-empty.
+The empty word is a prefix of this reduced expression.
 
@@
 
-    If $j\in \widetilde I$, then we can flip it to a position $j'>j$ (by Lemma~\ref{lem_rootfunction_flips}~\eqref{lem_rootfunction_flips2}), creating a new reduced expression $\widetilde Q'$ of $w$ which uses $q_j$, and thus has $Q^j$ as a prefix.
+    If $j\in \widetilde I$, then we can flip it to a position $j'>j$ (by \cref{lem_rootfunction_flips}~\eqref{lem_rootfunction_flips2}), creating a new reduced expression $\widetilde Q'$ of $w$ which uses $q_j$, and thus has $Q^j$ as a prefix.
 
@@
 \begin{lemma}\label{lem_negativeroot}
-    Let $I_1,I_2\in \subwordComplex(Q,w)$ be two different facets, and $j\in [m]$ be the first position where they differ. Without loss of generality assume 
+    Let $I_1,I_2\in \subwordComplex(Q,w)$ be two different facets, and $j\in [m]$ be the first position where they differ.
+    Without loss of generality assume 
     \[
@@
     \]
-with $j\in I_1$. Let $\beta=\rootFunction{I_1}{j}=\rootFunction{I_2}{j}$, then 
+with $j\in I_1$.
+Let $\beta=\rootFunction{I_1}{j}=\rootFunction{I_2}{j}$, then 
 \[
@@
 
-\begin{proof}[Proof of Proposition~\ref{prop_sweeping2}]
+\begin{proof}[Proof of \cref{prop_sweeping2}]
 Assume $\pi \in \linearExtensions(I)$ and let $I^j=I\cap [j]$.
-We will show that the partial root function $\rootFunction{I^j}{\cdot}$ agrees with the decisions taken in the sweeping algorithm. Indeed, we will see that those decisions are forced.
+We will show that the partial root function $\rootFunction{I^j}{\cdot}$ agrees with the decisions taken in the sweeping algorithm.
+Indeed, we will see that those decisions are forced.
 
@@
     We argue this by contradiction. 
-    Assume $j\notin I^j$ ($j\notin I$).
-Let $I_1=\sweepingAlgorithm(Q,w,\pi)$ and $I_2=I$.
-Applying Lemma~\ref{lem_negativeroot}, we deduce that $\beta=\rootFunction{I^j}{j}=\rootFunction{I}{j}$ satisfies
+    Assume $j\notin I^j$ ($j\notin I$). Let $I_1=\sweepingAlgorithm(Q,w,\pi)$ and $I_2=I$. Applying \cref{lem_negativeroot}, we deduce that $\beta=\rootFunction{I^j}{j}=\rootFunction{I}{j}$ satisfies 
     \[
@@
 \subsection{The subword complex congruence conjecture}\cesarm{To do: meet to discuss about this section? put it in final form...}
-By Corollary~\ref{cor_linearextensions_partition}, the set $\linearExtensions(Q,w)$ of linear extensions of all facets of $\subwordComplex(Q,w)$ can be written as
+By \cref{cor_linearextensions_partition}, the set $\linearExtensions(Q,w)$ of linear extensions of all facets of $\subwordComplex(Q,w)$ can be written as
 \begin{align*}
@@
 
-By Theorem~\ref{thm_subword_linearextensions_B}, if $Q$ contains a reduced expression for $\wo$, this gives an equivalence relation on the interval $[e,w]$ of the week order. 
+By \cref{thm_subword_linearextensions_B}, if $Q$ contains a reduced expression for $\wo$, this gives an equivalence relation on the interval $[e,w]$ of the week order.
 We say that a word $Q$ is \defn{alternating} if all non-commuting pairs $s, t\in S$ alternate within $Q$.
@@
 \begin{remark}\label{rem_acyclicflipposet_not_latticequotient}
-In analogy to the case of pipe dreams in Section~\ref{subsec:proofCongruence}, one might expect that the quotient~$[e,\omega]/\equiv_{Q,w}$ is isomorphic to the restriction of the increasing flip poset of $\subwordComplex(Q,w)$ to the set of acyclic facets.
-But this is not the case as shown in Example~\ref{ex_acyclicflip_not_weakorder_related}.
+In analogy to the case of pipe dreams in \cref{subsec:proofCongruence}, one might expect that the quotient~$[e,\omega]/\equiv_{Q,w}$ is isomorphic to the restriction of the increasing flip poset of $\subwordComplex(Q,w)$ to the set of acyclic facets.
+But this is not the case as shown in \cref{ex_acyclicflip_not_weakorder_related}.     
 \end{remark}
@@
 
-As we have seen in Corollary~\ref{cor_acyclicpipedreams_lattice}, the increasing flip poset of acyclic pipe dreams of any permutation $w$ is a lattice, because it is isomorphic to the lattice quotient~$[e,\omega]/\equiv_\omega$.
+As we have seen in \cref{cor_acyclicpipedreams_lattice}, the increasing flip poset of acyclic pipe dreams of any permutation $w$ is a lattice, because it is isomorphic to the lattice quotient~$[e,\omega]/\equiv_\omega$.
 This motivates the following open question for subword complexes.
@@
 \begin{question}
-Let $\subwordComplex(Q,w)$ be a non-empty subword complex. Is the restriction of the increasing flip poset of $\subwordComplex(Q,w)$ to the set of acyclic facets a lattice?    
+Let $\subwordComplex(Q,w)$ be a non-empty subword complex.
+Is the restriction of the increasing flip poset of $\subwordComplex(Q,w)$ to the set of acyclic facets a lattice?    
 \end{question}
 
-As pointed out in Remark~\ref{rem_acyclicflipposet_not_latticequotient},  we can not expect~$[e,\omega]/\equiv_{Q,w}$ to be isomorphic to the restriction of the increasing flip poset of $\subwordComplex(Q,w)$ to the set of acyclic facets.
-Example~\ref{ex_acyclicflip_not_weakorder_related} shows that there are flips between acyclic facets that are not detected by the week order.
+As pointed out in \cref{rem_acyclicflipposet_not_latticequotient},  we can not expect~$[e,\omega]/\equiv_{Q,w}$ to be isomorphic to the restriction of the increasing flip poset of $\subwordComplex(Q,w)$ to the set of acyclic facets.
+\cref{ex_acyclicflip_not_weakorder_related} shows that there are flips between acyclic facets that are not detected by the week order.
 One could expect that there is a natural restriction to a special class of flips that behave nicer, meaning that all of them are identified by the quotient~$[e,\omega]/\equiv_{Q,w}$.
-In our Example~\ref{ex_acyclicflip_not_weakorder_related},
-the generalized Chute moves from~\cite{rubey_maximal_2012} do the job, because the flip that is not detected by the week order is exactly the one flip which is not Chute.
-The Chute lattice conjecture~\cite[Conjecture~2.8]{rubey_maximal_2012} might be an indication that this is the right direction to look at.
+In our \cref{ex_acyclicflip_not_weakorder_related}, the generalized Chute moves from~\cite{Rubey} do the job, because the flip that is not detected by the week order is exactly the one flip which is not Chute.
+The Chute lattice conjecture~\cite[Conjecture~2.8]{Rubey} might be an indication that this is the right direction to look at.
 

### 2022-10-13 acyclicFacets/draft/latticePipeDreams.tex
Proof for Cesar

--- 2022-08-25 acyclicFacets/draft/latticePipeDreams.tex
@@
 I do not remember the details at the moment, but the proof is based on the paper of Jahn--Stump that we discussed during your visit in Graz.}
+
+For the purpose of this proof, let us write~$\leqslant_B$ the strong Bruhat order, defined by~$x \leqslant_B y \iff$ a reduced expression of~$y$ has a reduced expression of~$x$ as a subword, and~$x \less_B y$ the covers of this order.
+We note that for any word~$Q$ and any~$x\in W$, we can find a reduced expression of~$x$ as a subword of~$Q$ if and only if~$x \leqslant_B Dem(Q)$ the demazure product of~$Q$.
+
+Let us write~$w = uv$ with~$u$ the prefix of~$w$ defined by~$I_1$ and~$I_2$ on~$Q$ until index~$j-1$ and~$v$ the suffix of~$w$ defined by the same facets from index~$j$ and onward.
+Let us also write~$s$ the~$j^{\text{th}}$ letter of~$Q$ and~$\alpha$ the simple root associated with~$s$.
+We note that~$\beta = \rootFunction{I_1}{j} = u(\alpha)$.
+
+Let us call~$Q'$ the suffix of~$Q$ starting at index~$j+1$.
+Since~$j \notin I_2$, we note that~$sv \less_B v$ and the restriction of~$I_2$ to~$Q'$ is a facet of~$\subwordComplex(Q', sv)$.
+However, since~$j \in I_1$, the restriction of~$I_1$ to~$Q'$ is a facet of~$\subwordComplex(Q', v)$.
+Therefore, we know that~$v \leqslant_B Dem(Q')$.
+
+We can now apply \cite{jahn_bruhat_2021, proposition 3.14} to~$I'_2$ the restriction of~$I_2$ to~$Q'$, which tells us that~$\mathcal{E}^+(sv, Dem(Q)) \subseteq \cone \Roots(I'_2)$.
+Since~$sv \less_B v \leqslant Dem(Q)$, then~$\alpha \in \mathcal{E}^+(sv, Dem(Q))$ and so~$\alpha \in \cone \Roots(I'_2)$.
+
+Going back to~$I_2$, we know that~$us(\Roots(I'_2)) \subseteq \Roots(I_2)$ and so~$us(\alpha) = -u(\alpha) = -\beta \in \cone \Roots(I_2)$.
 \end{proof}

### 2022-10-17 acyclicFacets/draft/latticePipeDreams.tex
cleaning Section 2

--- 2022-10-13 acyclicFacets/draft/latticePipeDreams.tex
@@
 
+The \defn{weak order} on the permutations of~$[n]$ is defined as the inclusion order of inversion sets, where an inversion of a permutation~$\pi$ is a pair of values~$i, j \in [n]$ such that~$i < j$ while~${\pi^{-1}(i) > \pi^{-1}(j)}$.
+The cover relations in the weak order correspond to switching pairs of consecutive values in permutations.
+The weak order is known to be a lattice \cite{GuilbaudRosenstiehl,Bjorner}.
+For two permutations~$\sigma < \tau$, we denote by~$[\sigma, \tau]$ the weak order interval between~$\sigma$ and~$\tau$, which is again a lattice.
+
 \section{Preliminaries on pipe dreams}
@@
 \vincent{In \cite{PilaudStump-ELlabeling}, these are called positive and negative greedy facets. Also the notations are different...}
+The \defn{increasing flip poset} is the reflexive and transitive closure of the increasing flip graph on~$\pipeDreams(\omega)$.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Reversing pipe dreams}
-\label{subsec:reversingPipeDreams}
-
-We say that a pipe dream~$P \in \pipeDreams_n$ is \defn{reversing} if it fixes the first pipe and reverses the order of the remaining pipes, \ie if~$\omega_P = [1, n, n-1, \dots, 2]$ (in one-line notation).
-We denote by~$\reversingPipeDreams_n$ the reversing pipe dreams of~$\pipeDreams_n$.
-As observed by different authors~\cite{Woo, PilaudPocchiola, Pilaud-these, Stump}, the pipe dreams of~$\reversingPipeDreams_n$ belong to the Catalan family.
-\cref{fig:bijection} illustrates explicit bijections between the pipe dreams of~$\reversingPipeDreams_n$, the binary trees on $n$ vertices, and the triangulations of a convex $(n+2)$-gon.
-\vincent{figure starts with pipe $0$}
-
-\begin{figure}[h]
+\begin{example}
+\label{exm:Tamari1}
+We say that a pipe dream is \defn{reversing} if it fixes the first and last pipes and reverses the order of the remaining pipes.
+In this case, it is natural to label the pipes from~$0$ to~$n+1$, so that the permutation of the pipes is~$\rho_n \eqdef [0, n, n-1, \dots, 2, 1, n+1]$.
+% We denote by~$\reversingPipeDreams_n$ the reversing pipe dreams of~$\pipeDreams_n$.
+As observed in~\cite{Woo, PilaudPocchiola, Pilaud-these, Stump}, the family of reversing pipe dreams belong to the Catalan families.
+\cref{fig:bijection} illustrates explicit bijections between reversing pipe dreams of~$\pipeDreams(\rho_n)$, binary trees with $n$ internal nodes, and the triangulations of a convex $(n+2)$-gon.
+More precisely, the map which sends an elbow in row~$i$ and column~$j$ of the triangular shape to the diagonal~$[i,n+1-j]$ of the~$(n+2)$-gon provides the following correspondence: \\[.3cm]
+\centerline{
+\begin{tabular}{r@{$\quad\longleftrightarrow\quad$}l}
+pipe dream~$P \in \reversingPipeDreams_n$ & triangulation~$P\duality$ of the $(n+2)$-gon, \\
+pipe $i$ of~$P$ & triangle $i\duality$ of~$P\duality$ (with central vertex~$i$), \\
+elbow between pipes~$i$ and~$j$ of~$P$ & common side of triangles~$i\duality$ and~$j\duality$ of~$P\duality$, \\
+cross between pipes~$i$ and~$j$ of~$P$ & common bisector between triangles~$i\duality$ and~$j\duality$ of~$P\duality$, \\
+contact graph of~$P$ & dual binary tree of~$P\duality$, \\
+elbow flips in~$P$ & diagonal flips in~$P\duality$. \\
+%increasing flip poset & Tamari lattice.
+\end{tabular}} \\[.3cm]
+%
+\begin{figure}
 	\centerline{\includegraphics[scale=1.3]{dualiteTriangulation}}
@@
 \end{figure}
-
-More precisely, the map which sends an elbow in row~$i$ and column~$j$ of the triangular shape to the diagonal~$[i,n+1-j]$ of the~$(n+2)$-gon provides the following correspondence:
-\begin{center}
-\begin{tabular}{r@{$\quad\longleftrightarrow\quad$}l}
-pipe dream~$P \in \reversingPipeDreams_n$ & triangulation~$P\duality$ of the $(n+2)$-gon, \\
-$i$th pipe of~$P$ & $i$th triangle of~$P\duality$ (with central vertex~$i$), \\
-elbows of~$P$ & diagonals of~$P\duality$, \\
-crosses of~$P$ & common bisectors between triangles of~$P\duality$, \\
-contact graph of~$P$ & dual binary tree of~$P\duality$, \\
-elbow flips in~$P$ & diagonal flips in~$P\duality$.
-\end{tabular}
-\end{center}
-
-\begin{remark}
-All reversing pipe dreams are acyclic.
-Indeed, there contact graphs are (oriented) binary trees, which are certainly acyclic.
-\end{remark}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Elementary properties of pipe dreams}
-\label{subsec:elementaryProperties}
-
-We gather in this section some elementary properties of pipe dreams needed later.
-\vincent{Not sure we use all these. At least say that they are just technical points.}
+%
+As a consequence, this map sends the increasing flip poset on reversing pipe dreams to the \defn{Tamari lattice} on binary trees.
+This lattice is defined as the transitive closure of right rotations on binary trees, and is obtained as the quotient of the weak order by the \defn{sylvester congruence}.
+\vincent{Not sure where we want that...}
+An important point here is that all reversing pipe dreams are acyclic, since there contact graphs are (oriented) binary trees.
+\end{example}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Crossing and contact properties}
+\label{subsec:crossingsContacts}
+
+We now gather some elementary properties of crossings and contacts that will be needed later to construct pipe dreams from permutations.
+For a pipe dream~$P \in \pipeDreams(\omega)$, we call pipe~$j$ the pipe which enters at row~$j$ and exits at column~$\omega^{-1}(j)$.
 
@@
 \label{lem:horiVertCrossings}
-For any pipe dream~$P \in \pipeDreams(\omega)$, the pipe~$j$ of~$P$ (which enters at row~$j$ and exits at column~$\omega^{-1}(j)$) crosses
+For any pipe dream~$P \in \pipeDreams(\omega)$, the pipe~$j$ of~$P$ crosses precisely
 \begin{itemize}
@@
 \begin{proof}
-For~$i < j$, if~$\omega^{-1}(i) > \omega^{-1}(j)$, then the pipes~$i$ and~$j$ have to cross exactly once, while if~$\omega^{-1}(i) < \omega^{-1}(j)$ the pipes~$i$ and~$j$ cannot cross.
+For~$i < j$, if~$\omega^{-1}(i) > \omega^{-1}(j)$, then the pipes~$i$ and~$j$ have to cross exactly once (and $j$ must be the vertical pipe at that crossing), while if~$\omega^{-1}(i) < \omega^{-1}(j)$ the pipes~$i$ and~$j$ cannot cross.
 The same argument applies for~${k > j}$.
@@
 \label{lem:countingElbows}
-For any pipe dream~$P \in \pipeDreams(\omega)$, the pipe~$j$ (which enters at row~$j$ and exits at column~$\omega^{-1}(j)$) has precisely
+For any pipe dream~$P \in \pipeDreams(\omega)$, the pipe~$j$ has precisely
 \begin{itemize}
@@
 \end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Contact graph properties}
+\label{subsec:contactGraph}
+
+We now state a simple observation about the poset~$\contactLess{P}$, and two of its consequences, that will play essential roles in the proofs in \cref{sec:latticeAcyclicPipeDreams}.
 
@@
 Note that the reciprocal assertion of \cref{lem:rectangle} is false.
-We conclude by two consequences of \cref{lem:rectangle}.
+We conclude this section by two consequences of \cref{lem:rectangle}.
 
@@
 \label{lem:consequenceRectangle2}
-Let~$P$ be a pipe dream and let~$i,j,k$ be three pipes of~$P$ such that~$\min(i,k) < j$ and~$\min(\omega^{-1}(i), \omega^{-1}(k)) < \omega^{-1}(j)$.
+Let~$P$ be a pipe dream and let~$i,j,k$ be three pipes of~$P$ such that~$i < j < k$ and~$\omega^{-1}(i) > \omega^{-1}(j) > \omega^{-1}(k)$.
 If~$i \to k$ in~$P\contact$, then either~$i \contactLess{P} j \contactMore{P} k$ or~$i \contactMore{P} j \contactLess{P} k$.
-\vincent{not sure we really use this version}
 \end{lemma}
@@
 \begin{proof}
-Let~$e$ denote the contact of~$i$ and~$k$ in~$P$.
+Let~$e$ denote the contact of pipes~$i$ and~$k$ in~$P$.
 Decompose the triangular shape into three regions: the region~$A$ of all points located southwest of~$e$, the region~$B$ of all points located northwest or southeast of~$e$, and the region~$C$ of all points located northeast of~$e$.
-Since~$\min(i,k) < j$ and~$\min(\omega^{-1}(i), \omega^{-1}(k)) < \omega^{-1}(j)$, the pipe~$j$ starts in region~$A$ and ends in region~$C$.
+Since~$i < j$ and~$\omega^{-1}(j) > \omega^{-1}(k)$, the pipe~$j$ starts in region~$A$ and ends in region~$C$.
 Hence, the pipe~$j$ has an elbow~$f$ in region~$B$.
@@
 
+%\begin{lemma}
+%\label{lem:consequenceRectangle2}
+%Let~$P$ be a pipe dream and let~$i,j,k$ be three pipes of~$P$ such that~$\min(i,k) < j$ and~$\min(\omega^{-1}(i), \omega^{-1}(k)) < \omega^{-1}(j)$.
+%If~$i \to k$ in~$P\contact$, then either~$i \contactLess{P} j \contactMore{P} k$ or~$i \contactMore{P} j \contactLess{P} k$.
+%\vincent{not sure we really use this extended version}
+%\end{lemma}
+%
+%\begin{proof}
+%Let~$e$ denote the contact of pipes~$i$ and~$k$ in~$P$.
+%Decompose the triangular shape into three regions: the region~$A$ of all points located southwest of~$e$, the region~$B$ of all points located northwest or southeast of~$e$, and the region~$C$ of all points located northeast of~$e$.
+%Since~$\min(i,k) < j$ and~$\min(\omega^{-1}(i), \omega^{-1}(k)) < \omega^{-1}(j)$, the pipe~$j$ starts in region~$A$ and ends in region~$C$.
+%Hence, the pipe~$j$ has an elbow~$f$ in region~$B$.
+%We thus obtain that~$i \contactLess{P} j \contactMore{P} k$ if this $f$ is southeast of~$e$, and that~$i \contactMore{P} j \contactLess{P} k$ if $f$ is northwest of~$e$.
+%\end{proof}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\vincent{Mention here and throughout the classical sylvester example}
-
-The \defn{weak order} on the permutations of~$[n]$ is defined as the inclusion order of inversion sets, where an inversion of a permutation~$\pi$ is a pair of values~$i, j \in [n]$ such that~$i < j$ while~${\pi^{-1}(i) > \pi^{-1}(j)}$.
-The cover relations in the weak order correspond to switching pairs of consecutive values in permutations.
-The weak order is known to be a lattice \cite{GuilbaudRosenstiehl,Bjorner}.
-For two permutations~$\sigma < \tau$, we denote by~$[\sigma, \tau]$ the weak order interval between~$\sigma$ and~$\tau$, which is again a lattice.
+As already mentioned, the increasing flip poset on reversing pipe dreams is isomorphic to the Tamari lattice, which is a well known lattice quotient of the weak order.
+In this section, we extend this result to any permutation~$\omega$, by proving that the transitive closure of the increasing flip graph on acyclic pipe dreams of~$\acyclicPipeDreams(\omega)$ is the Hasse diagram of a lattice quotient of the weak order interval~$[e,\omega]$.
 
@@
 
-We will see in \cref{sec:algorithms} different algorithms to compute the pipe dream~$P \in \acyclicPipeDreams(\omega)$ of which a given permutation~$\pi \in [e,\omega]$ is a linear extension.
-These algorithms are however not needed for the proof of \cref{thm:partitionPipeDreams}, which we break into the next three elementary lemmas.
+\begin{example}
+\label{exm:Tamari2}
+Following \cref{exm:Tamari1}, observe that the permutations of~$\{0, 1, \dots, n, n+1\}$ below $\rho_n$ are precisely the permutations of the form~$[0, \pi, n+1]$ for some~$\pi \in \fS_n$.
+It is well-known that any permutation~$\pi \in \fS_n$ is a linear extension of a unique binary tree.
+This binary tree can be obtained by inserting~$\pi$ from right to left in a binary search tree.
+Hence any permutation of~$\{0, 1, \dots, n, n+1\}$ below~$\rho_n$ is a linear extension of a unique reversing pipe dream on~$n+2$ pipes.
+For instance, the pipe dream of \cref{fig:bijection} has linear extensions~$0421356$, $0423156$, $0421536$, $0423516$, $0425136$, $0425316$, $0452136$, $0452316$.
+\end{example}
+
+We will see in \cref{sec:algorithms} insertion algorithms to compute the pipe dream~$P \in \acyclicPipeDreams(\omega)$ of which a given permutation~$\pi \in [e,\omega]$ is a linear extension, for any permutation~$\omega$.
+These algorithms are however not needed for the proof of \cref{thm:partitionPipeDreams}, which we break into the following three lemmas.
 
@@
 
-We prove this statement by checking both conditions of \cref{prop:characterizationCongruences}.
+\begin{example}
+\label{exm:Tamari3}
+Following \cref{exm:Tamari1,exm:Tamari2}, observe that the congruence~$\equiv_{\rho_n}$ on the permutations of~$\{0, 1, \dots, n, n+1\}$ below~$\rho_n$ corresponds to the sylvester congruence on~$\fS_n$.
+The classes of this congruence are the sets of linear extensions of the binary trees (considered as posets, labeled in inorder, and oriented towards their roots).
+It can also be defined by the classical rewriting rule~$UikVjW \equiv UkiVjW$ for~$i < j < k$.
+\end{example}
+
+We will discuss in \cref{subsec:rewritingAlgorithm} rewriting rules for the pipe dream congruence~$\equiv_\omega$, for any permutation~$\omega$.
+This rewriting rule is however not needed for the proof of \cref{thm:pipeDreamCongruence}.
+We prove it by checking both conditions of \cref{prop:characterizationCongruences}.
 For the first condition, we need the following classical characterization of weak order intervals, see \cite{BjornerWachs} or~\cite{ChatelPilaudPons}.
@@
 Moreover, the inversions of~$\min(I)$ are the pairs~$i,j \in [n]$ with $i < j$ and $i \more j$, and the non-inversions of~$\max(I)$ are the pairs~$i,j \in [n]$ with $i < j$ and $i \less j$.
-\vincent{Not sure I want to use that last sentence later.}
 \end{proposition}
@@
 \end{itemize}
-In this section, we prove the following statement.
+In this section, we aim at the following statement.
 
@@
 \label{thm:pipeDreamQuotient}
-The lattice quotient~$[e,\omega]/{\equiv_\omega}$ is isomorphic to the increasing flip poset on~$\acyclicPipeDreams(\omega)$.
+The increasing flip graph on~$\acyclicPipeDreams(\omega)$ is isomorphic to the Hasse diagram of the lattice quotient~$[e,\omega]/{\equiv_\omega}$.
 \end{theorem}
 
-To prove this result, we need the following auxiliary statement.
+\begin{example}
+\label{exm:Tamari4}
+Following \cref{exm:Tamari1,exm:Tamari2,exm:Tamari3}, observe that the increasing flip poset on reversing pipe dreams is isomorphic to the Tamari lattice, which is the quotient of the weak order by the sylvester congruence.
+\end{example}
+
+\begin{remark}
+\label{rem:pipeDreamQuotient}
+The increasing flip poset on~$\pipeDreams(\omega)$ is the transitive closure of the increasing flip graph on~$\pipeDreams(\omega)$.
+Observe that the two natural ways to restrict to the acyclic pipe dreams of~$\acyclicPipeDreams(\omega)$ (restrict either the flip graph or the flip poset) do not coincide in general.
+Namely, the transitive closure of the subgraph of the increasing flip graph induced by~$\acyclicPipeDreams(\omega)$ may have strictly less relations than the subposet of the increasing flip poset induced by~$\acyclicPipeDreams(\omega)$.
+\cref{fig:counterExampleRestrictionIncreasingFlipPoset} illustrates two acyclic pipe dreams of~$\acyclicPipeDreams(126543)$ connected by a sequence of increasing flips in~$\pipeDreams(126543)$ but by no sequence of increasing flips in~$\acyclicPipeDreams(126543)$.
+%	* type A5,
+%	* Q = [1, 2, 3, 4, 5, 1, 2, 3, 4, 1, 2, 3, 1, 2, 1] 
+%	* w = [1, 2, 3, 1, 2, 1]
+%	* flips: 
+%	(0, 2, 3, 4, 5, 6, 7, 8, 12)
+%	(2, 3, 4, 5, 6, 7, 8, 10, 12) 
+%	(3, 4, 5, 6, 7, 8, 10, 11, 12)
+%	(3, 4, 5, 7, 8, 10, 11, 12, 14)
+
+\begin{figure}[ht]
+	\centerline{\includegraphics[scale=1.3]{counterExampleRestrictionIncreasingFlipPoset}}
+	\caption{Two acyclic pipe dreams~$\acyclicPipeDreams(126543)$ connected by a sequence of increasing flips in~$\pipeDreams(126543)$ but by no sequence of increasing flips in~$\acyclicPipeDreams(126543)$.}
+	\label{fig:counterExampleRestrictionIncreasingFlipPoset}
+\end{figure}
+\end{remark}
+
+To prove \cref{thm:pipeDreamQuotient}, we need the following auxiliary statement.
 
@@
 Consequently, since~$P'{}\contact$ contains the arc~$j \to i$ and is acyclic, it must contain the path~$j \to k_1 \to \dots \to k_p \to i$.
-We thus obtained that~$i \contactLess{P} k_1 \contactLess{P} j$ while~$i \contactMore{P'} k_1 \contactMore{P'} j$, and~$k_1$ has a contact with~$i$ in~$P$ and with~$j$ in~$P'$.
-
-Consider now the elbow~$e$ of~$P$ which is a crossing in~$P'$ and the elbow~$e'$ of~$P'$ which is a crossing of~$P$.
-Let~$R$ the rectangle with corners~$e$ and~$e'$.
+We thus obtained that~$i \contactLess{P} k_1 \contactLess{P} j$ while~$i \contactMore{P'} k_1 \contactMore{P'} j$, and~$k_1$ has a contact with~$i$ in~$P$ that becomes a contact with~$j$ in~$P'$.
+
+Consider now the contact~$c$ of~$P$ which is a crossing in~$P'$ and the contact~$c'$ of~$P'$ which is a crossing of~$P$.
+Let~$R$ the rectangle with corners~$c$ and~$c'$.
 Since~$k_1$ has a contact with~$i$ in~$P$ and with~$j$ in~$P'$, it must pass inside~$R$.
-Since~$i \contactLess{P} k_1 \contactLess{P} j$ and~$i \contactMore{P'} k_1 \contactMore{P'} j$, the pipe~$k$ has no elbow located northwest or southeast of~$e$ or~$e'$, hence no elbow located north, south, west or east of~$R$.
+Since~$i \contactLess{P} k_1 \contactLess{P} j$ and~$i \contactMore{P'} k_1 \contactMore{P'} j$, the pipe~$k$ has no elbow located northwest or southeast of~$c$ or~$c'$, hence no elbow located north, south, west or east of~$R$.
 We thus obtain that~$k$ must be straight before it reaches~$R$, and after it leaves~$R$.
 Hence $k_1 < i < j$ and~$\omega^{-1}(k_1) > \omega^{-1}(j) > \omega^{-1}(i)$.
-By \cref{lem:consequenceRectangle1}, this contradicts~$k_1 \contactLess{P} j$~and~$i \contactMore{P'} k_1$.
+By \cref{lem:consequenceRectangle1}, this contradicts~$i \contactLess{P} k_1$~and~$k_1 \contactMore{P'} j$.
 \end{proof}
@@
 \begin{proof}[Proof of \cref{thm:pipeDreamQuotient}]
-It suffices to prove that the following conditions are equivalent for two distinct pipe dreams~$P,P' \in \acyclicPipeDreams(\omega)$:
+We need to prove that the following conditions are equivalent for two distinct pipe dreams~$P,P' \in \acyclicPipeDreams(\omega)$:
 \begin{enumerate}[(i)]
-\item $P$ covers~$P'$ in the increasing flip poset on~$\acyclicPipeDreams(\omega)$,
-\item there exist linear extensions~$\pi$ of~$P$ and~$\pi'$ of~$P'$ such that~$\pi$ covers~$\pi'$ in weak order.
+\item there is an increasing flip from $P$ to~$P'$,
+\item there exist linear extensions~$\pi$ of~$P$ and~$\pi'$ of~$P'$ such that~$\pi'$ covers~$\pi$ in weak order.
 \end{enumerate}
-\para{(ii) $\Rightarrow$ (i)}
-Follows from \cref{lem:lowerSetPipeDreams}.
-
-\para{(i) $\Rightarrow$ (ii)}
-Assume that~$P$ covers~$P'$ in the increasing flip poset.
-Let~$i < j$ be the two pipes involved in the flip between~$P$ and~$P'$.
-Hence, $j \to i$ is an arc of~$P$ while~$i \to j$ is an arc of~$P'$.
-By \cref{lem:flippable}, there is no directed path from~$j$ to~$i$ in~$P$ besides the arcs~$j \to i$ (there might be more than one such arc).
-Hence, there exists a linear extension~$\pi$ of~$P$ where~$j$ and~$i$ are consecutive.
-Write~$\pi \eqdef UjiV$ and define~$\pi' \eqdef UijV$.
-Since~$j \to i$ is an arc of~$P$, $\pi'$ is not a linear extension of~$P$.
+\cref{lem:lowerSetPipeDreams,thm:partitionPipeDreams} directly imply that (ii) $\Rightarrow$ (i).
+For (i) $\Rightarrow$ (ii), let~$i < j$ be the two pipes involved in the flip between~$P$ and~$P'$.
+Hence, $i \to j$ is an arc of~$P\contact$ while~$j \to i$ is an arc of~$P'{}\contact$.
+By \cref{lem:flippable}, there is no directed path from~$i$ to~$j$ in~$P\contact$ besides the arcs~$i \to j$ (there might be more than one such arc).
+Hence, there exists a linear extension~$\pi$ of~$P$ where~$i$ and~$j$ are consecutive.
+Write~$\pi \eqdef UijV$ and define~$\pi' \eqdef UjiV$.
+Since~$i \to j$ is an arc of~$P\contact$, $\pi'$ is not a linear extension of~$P$.
 Hence, by \cref{lem:lowerSetPipeDreams}, $\pi'$ is a linear extension of~$P'$.
@@
 \begin{enumerate}[(i)]
-\item $P < P'$ in the increasing flip poset on~$\acyclicPipeDreams(\omega)$,
+\item there is a path from $P$ to~$P'$ in the increasing flip graph on~$\acyclicPipeDreams(\omega)$,
 \item there exist linear extensions~$\pi$ of~$P$ and~$\pi'$ of~$P'$ such that~$\pi < \pi'$ in weak order,
@@
 \begin{proof}
-We already proved that (i) $\Leftrightarrow$ (ii).
-\vincent{todo}
+We already proved the equivalence (i) $\Leftrightarrow$ (ii) in \cref{thm:pipeDreamQuotient}.
+The equivalence (ii) $\Leftrightarrow$ (iii) is valid for any lattice quotient.
+The equivalences (iii) $\Leftrightarrow$ (iv) $\Leftrightarrow$ (v) $\Leftrightarrow$ (vi) follow from the descriptions of \cref{prop:WOIP} for the inversions of the minimum and the non-inversions of the maximum of a weak order interval.
 \end{proof}
@@
 
+\vincent{Explain with the example of the sylvester congruence}
+
 \begin{definition}
@@
 \end{proof}
+
+\vincent{I want to think about congruences of the interval $[e,\omega]$ in general.}
 

### 2022-10-17 acyclicFacets/draft/latticePipeDreams.tex
start algorithms

@@
 \newcommand{\WEcross}[1][black]{\raisebox{-.15cm}{\includegraphics[scale=.9]{WEcross}}}
-% elbow
+% elbows
 %\newcommand{\elbow}[1][black]{\raisebox{.1cm}{\pipeDreamMonoColor{#1}{black}{e}}}
@@
 
-A \defn{pipe dream}~$P$ is a filling of a triangular shape with crosses~\cross{} and elbows~\elbow{} so that all pipes entering on the left side exit on the top side.
-We only consider \defn{reduced} pipe dreams, where two pipes have at most one intersection.
+A \defn{pipe dream}~$P$ is a filling of a triangular shape with crossings~\cross{} and contacts~\elbow{} so that all pipes entering on the left side exit on the top side.
+We only consider \defn{reduced} pipe dreams, where two pipes have at most one crossing.
 We label the pipes with~$1, 2, \dots, n$ in the order of their entry points from top to bottom.
@@
 	}
-	\caption{Two pipe dreams of~$\pipeDreams(1365724)$ connected by a flip (exchanging an elbow with the crossing on the two red pipes~$3$ and~$4$).}
+	\caption{Two pipe dreams of~$\pipeDreams(1365724)$ connected by a flip (exchanging a contact with the crossing on the two red pipes~$3$ and~$4$).}
 	\label{fig:pipeDreams}
@@
 
-Two pipe dreams are related by a \defn{flip} if they define the same permutation of the pipes and only differ by the position of a cross and an elbow.
-An elbow~$e$ in a pipe dream~$P$ is \defn{flippable} if the two pipes passing through elbow~$e$ have a crossing~$c$, and the flip exchanges the elbow~$e$ with the cross~$c$.
-See \cref{fig:pipeDreams}.
-The flip is \defn{increasing} if the elbow~$e$ is weakly southwest of the crossing~$c$.
-For example, the flip of \cref{fig:pipeDreams} is increasing from left to right.
+%Two pipe dreams are related by a \defn{flip} if they only differ by the position of a crossing and a contact (in particular, they define the same permutation).
+A contact~$c$ is \defn{flippable} if the two pipes passing through contact~$c$ have a crossing~$x$.
+The \defn{flip} exchanges the contact~$c$ with the crossing~$x$.
+%See \cref{fig:pipeDreams}.
+The flip is \defn{increasing} if the contact~$c$ is weakly southwest of the crossing~$x$.
+For example, \cref{fig:pipeDreams} illustrates an increasing from the left pipe dream to the right pipe dream.
 %
@@
 
-The \defn{contact graph} of a pipe dream~$P$ is the directed graph~$P\contact$ with one node for each pipe of~$P$ and one arc for each elbow of~$P$ connecting the northwest pipe to the southeast pipe of the elbow\footnote{We have reversed the usual orientation conventions of \cite{PilaudSantos-brickPolytope, PilaudPocchiola, Pilaud-BrickAlgebra} to suit better our purposes, in particular in \cref{subsec:insertionAlgorithm}.}.
+The \defn{contact graph} of a pipe dream~$P$ is the directed graph~$P\contact$ with one node for each pipe of~$P$ and one arc for each contact of~$P$ connecting the northwest pipe to the southeast pipe of the contact\footnote{We have reversed the usual orientation conventions of \cite{PilaudSantos-brickPolytope, PilaudPocchiola, Pilaud-BrickAlgebra} to suit better our purposes, in particular in \cref{subsec:insertionAlgorithm}.}.
 We see equivalently the contact graph~$P\contact$ as a graph on the pipes of~$P$ or on the integers~$[n]$.
-We say that a pipe dream~$P$ is \defn{acyclic} if its contact graph~$P\contact$ is (no oriented cycle).
+We say that a pipe dream~$P$ is \defn{acyclic} if its contact graph~$P\contact$ is acyclic (no oriented cycle).
 We then denote by~$\contactLess{P}$ the transitive closure of the contact graph of~$P$.
@@
 \cref{fig:bijection} illustrates explicit bijections between reversing pipe dreams of~$\pipeDreams(\rho_n)$, binary trees with $n$ internal nodes, and the triangulations of a convex $(n+2)$-gon.
-More precisely, the map which sends an elbow in row~$i$ and column~$j$ of the triangular shape to the diagonal~$[i,n+1-j]$ of the~$(n+2)$-gon provides the following correspondence: \\[.3cm]
+More precisely, the map which sends a contact in row~$i$ and column~$j$ of the triangular shape to the diagonal~$[i,n+1-j]$ of the~$(n+2)$-gon provides the following correspondence: \\[.3cm]
 \centerline{
@@
 pipe $i$ of~$P$ & triangle $i\duality$ of~$P\duality$ (with central vertex~$i$), \\
-elbow between pipes~$i$ and~$j$ of~$P$ & common side of triangles~$i\duality$ and~$j\duality$ of~$P\duality$, \\
-cross between pipes~$i$ and~$j$ of~$P$ & common bisector between triangles~$i\duality$ and~$j\duality$ of~$P\duality$, \\
+contact between pipes~$i$ and~$j$ of~$P$ & common side of triangles~$i\duality$ and~$j\duality$ of~$P\duality$, \\
+crossing between pipes~$i$ and~$j$ of~$P$ & common bisector of triangles~$i\duality$ and~$j\duality$ of~$P\duality$, \\
 contact graph of~$P$ & dual binary tree of~$P\duality$, \\
-elbow flips in~$P$ & diagonal flips in~$P\duality$. \\
+contact flips in~$P$ & diagonal flips in~$P\duality$. \\
 %increasing flip poset & Tamari lattice.
@@
 \label{lem:characterizationPipeDreams}
-A collection~$P$ of~$n$ pipes pairwise disjoint except at crossing and elbows and such that for each~$j \in [n]$, the pipe~$j$ enters at row~$j$, exits at column~$\omega^{-1}(j)$, and has~$\noninversions{\omega}{j}$ southeast elbows is a pipe dream of~$\pipeDreams(\omega)$.
+A collection~$P$ of~$n$ pipes pairwise disjoint except at crossing and contacts and such that for each~$j \in [n]$, the pipe~$j$ enters at row~$j$, exits at column~$\omega^{-1}(j)$, and has~$\noninversions{\omega}{j}$ southeast contacts is a pipe dream of~$\pipeDreams(\omega)$.
 \end{lemma}
@@
 We proceed by induction on the grid distance from~$x$ to~$y$.
-If they coincide, then pipes~$i$ and~$j$ share an elbow, so that there is an edge from~$i$ to~$j$ in~$P\contact$.
+If they coincide, then pipes~$i$ and~$j$ share a contact, so that there is an edge from~$i$ to~$j$ in~$P\contact$.
 Otherwise, let~$k$ be the pipe of~$P$ with a southeast elbow at~$x$ ($k$ is either the pipe~$i$ itself, or there is an edge from~$i$ to~$k$ in~$P\contact$) and~$\ell$ be the pipe of~$P$ with a northwest elbow at~$y$ ($\ell$ is either the pipe~$j$ itself, or there is an edge from~$\ell$ to~$j$ in~$P\contact$).
-Let~$R$ be the axis-parallel rectangle with elbows~$x$ and~$y$.
+Let~$R$ be the axis-parallel rectangle with corners~$x$ and~$y$.
 Since pipes~$k$ and~$\ell$ cross at most once, at least one of them has an additional elbow along the sides of~$R$.
@@
 \begin{proof}
-Let~$e$ denote the contact of pipes~$i$ and~$k$ in~$P$.
-Decompose the triangular shape into three regions: the region~$A$ of all points located southwest of~$e$, the region~$B$ of all points located northwest or southeast of~$e$, and the region~$C$ of all points located northeast of~$e$.
+Let~$c$ denote the contact of pipes~$i$ and~$k$ in~$P$.
+Decompose the triangular shape into three regions: the region~$A$ of all points located southwest of~$c$, the region~$B$ of all points located northwest or southeast of~$c$, and the region~$C$ of all points located northeast of~$c$.
 Since~$i < j$ and~$\omega^{-1}(j) > \omega^{-1}(k)$, the pipe~$j$ starts in region~$A$ and ends in region~$C$.
-Hence, the pipe~$j$ has an elbow~$f$ in region~$B$.
-We thus obtain that~$i \contactLess{P} j \contactMore{P} k$ if this $f$ is southeast of~$e$, and that~$i \contactMore{P} j \contactLess{P} k$ if $f$ is northwest of~$e$.
+Hence, the pipe~$j$ has an elbow~$e$ in region~$B$.
+We thus obtain that~$i \contactLess{P} j \contactMore{P} k$ if this $e$ is southeast of~$c$, and that~$i \contactMore{P} j \contactLess{P} k$ if $e$ is northwest of~$c$.
 \end{proof}
@@
 %Since~$\min(i,k) < j$ and~$\min(\omega^{-1}(i), \omega^{-1}(k)) < \omega^{-1}(j)$, the pipe~$j$ starts in region~$A$ and ends in region~$C$.
-%Hence, the pipe~$j$ has an elbow~$f$ in region~$B$.
+%Hence, the pipe~$j$ has a contact~$f$ in region~$B$.
 %We thus obtain that~$i \contactLess{P} j \contactMore{P} k$ if this $f$ is southeast of~$e$, and that~$i \contactMore{P} j \contactLess{P} k$ if $f$ is northwest of~$e$.
@@
 \begin{proof}
-For any~$i < j$ with~$\omega^{-1}(i) < \omega^{-1}(j)$, the pipes~$i$ and~$j$ do not cross.
-Hence, the pipe~$j$ passes southeast of every elbow of the pipe~$i$.
-This shows that~$i \contactLess{P} j$ by \cref{lem:rectangle}, thus ${\pi^{-1}(i) < \pi^{-1}(j)}$.
-In other words, any non-inversion of~$\omega$ is a non-inversion of~$\pi$, so that~${\pi < \omega}$.
+For any~$i < j$ with~$\omega^{-1}(i) < \omega^{-1}(j)$, we have~$i \contactLess{P} j$ by \cref{lem:consequenceRectangle1}, thus ${\pi^{-1}(i) < \pi^{-1}(j)}$ since~$\pi \in \linearExtensions(P)$.
+In other words, any non-inversion of~$\omega$ is a non-inversion of~$\pi$, so that~${\pi \le \omega}$.
 \end{proof}
@@
 \begin{proof}
-We just need to show that the poset~$\contactLess{P}$ (given by the transitive closure of~$P\contact$) satisfies the conditions of \cref{prop:WOIP}.
+We just need to show that the poset~$\contactLess{P}$ satisfies the conditions of \cref{prop:WOIP}.
 Consider~$i < j < k$ such that~$i \contactLess{P} k$.
@@
 Similarly, if~$\omega^{-1}(j) < \omega^{-1}(k)$, then~$j \contactLess{P} k$ by \cref{lem:consequenceRectangle1}.
-We can therefore assume that~$\omega^{-1}(i) > \omega^{-1}(j) > \omega^{-1}(k)$.
+We can thus assume that~${\omega^{-1}(i) > \omega^{-1}(j) > \omega^{-1}(k)}$.
 Decompose the triangular shape into three regions: the region~$A$ of all points located northeast of the last elbow of the pipe~$j$ of~$P$, the region~$B$ of all points located northwest or southeast of an elbow of the pipe~$j$ of~$P$, and the region~$C$ of all points located southwest of the first elbow of the pipe~$j$ of~$P$.
-Since~$i \contactLess{P} k$, there is a path~$\pi$ form the exiting point of the pipe~$i$ of~$P$ to the entering point of the pipe~$j$ of~$P$ which travels along the pipes of~$P$, possibly jumping from the northwest pipe to the southeast pipe of an elbow it encounters.
+Since~$i \contactLess{P} k$, there is a path~$\pi$ form the exiting point of the pipe~$i$ of~$P$ to the entering point of the pipe~$j$ of~$P$ which travels along the pipes of~$P$, possibly jumping from the northwest pipe to the southeast pipe of a contact it encounters.
 Since~$i < j$ and~$\omega^{-1}(j) > \omega^{-1}(k)$, the path~$\pi$ starts in region~$A$ and ends in region~$C$, so that it necessarily passes from region~$A$ to region~$C$.
@@
 \label{lem:flippable}
-Consider two acyclic pipe dreams~$P,P' \in \acyclicPipeDreams(\omega)$ connected by the flip of an elbow between their pipes~$i$ and~$j$.
+Consider two acyclic pipe dreams~$P,P' \in \acyclicPipeDreams(\omega)$ connected by the flip of a contact between their pipes~$i$ and~$j$.
 Then any directed path in~$P\contact$ or~$P'{}\contact$ between~$i$ and~$j$ is an arc.
@@
 \vincent{This section is in progress}
-In this section, we describe three algorithms to decide whether two permutations are equivalent for the pipe dream congruence~$\equiv_\omega$.
+In this section, we describe three algorithms to decide whether two permutations~$\pi$ and~$\pi'$ are equivalent for the pipe dream congruence~$\equiv_\omega$.
+The first two algorithms actually construct the unique pipe dream~$P \in \acyclicPipeDreams(\omega)$ of which~$\pi$ is a linear extension, while the last algorithm uses a rewriting technique.
 
@@
 
-\vincent{adapt the following}
-We now show that~$\linearExtensions(P) \cap \linearExtensions(P') = \varnothing$ for any two distinct acyclic pipe dreams~$P, P' \in \pipeDreams(\omega)$.
-For this, we show that we can reconstructing a pipe~$P$ knowing a linear extension~$\pi \in \linearExtensions(P)$.
-For this, we sweep the pipe dream in any perturbation of the northwest direction (meaning that we sweep the grid in any order such that each point is swept before all points weakly northwest of~$p$).
-When we sweep a vertex~$v$ of the grid, we see a pipe~$p$ arriving horizontally at~$v$ and a pipe~$q$ arriving vertically at~$v$.
-If~$p > q$, then $p$ and~$q$ already crossed before, so we have no choice but imposing an elbow at~$v$.
-If~$p < q$, there are three situations:
+Our first algorithm is a \defn{sweeping algorithm} that constructs the unique pipe dream~$P \in \acyclicPipeDreams(\omega)$ of which~$\pi$ is a linear extension.
+It is inspired by the algorithm to compute greedy pipe dreams~\cite{PilaudPocchiola, PilaudStump-ELlabelings}.
+Extensions of this algorithm will be discussed in \cref{..}. \vincent{todo. Was this algorithm explicitly somewhere before? We should cite Jahn-Stump later in the paper.}
+
+\begin{proposition}
+\label{prop:sweepingAlgorithm}
+For any permutations~$\pi,\omega \in \fS_n$ such that~$\pi < \omega$ in weak order, the unique pipe dream~$P \in \acyclicPipeDreams(\omega)$ such that~$\pi \in \linearExtensions(P)$ can be constructed by sweeping the triangular shape in any perturbation of the northwest direction and inserting a crossing when sweeping a vertex~$v$ of the grid where pipe~$i$ arrives horizontally and pipe~$j$ arrives vertically if and only if
 \begin{itemize}
-\item if~$\pi^{-1}(p) > \pi^{-1}(q)$ then~$p$ and~$q$ cannot touch (otherwise $\pi$ would not be a linear extension of~$P$), so that we have no choice but imposing a crossing~at~$v$,
-\item if~$\omega^{-1}(p) < \omega^{-1}(q)$, then~$p$ and~$q$ cannot cross (otherwise~$P$ would not be a pipe dream of~$\pipeDreams(\omega)$), so that we have no choice but imposing a contact at~$v$,
-\item if~$\pi^{-1}(p) < \pi^{-1}(q)$ and~$\omega^{-1}(p) > \omega^{-1}(q)$, then we have again two situations;
+\item $i < j$ and~$\omega^{-1}(i) > \omega^{-1}(j)$, and 
+\item $\pi^{-1}(i) > \pi^{-1}(j)$ or vertex~$v$ lies in column~$\omega^{-1}(j)$.
+\end{itemize}
+See \cref{fig:sweepingAlgorithm}.
+\vincent{todo}
+
+\begin{figure}
+%	\centerline{\includegraphics[scale=.9]{sweeping}}
+	\caption{Sweeping algorithm for the permutations~$\pi = 513264$ and~$\omega = 561324$.}
+	\label{fig:sweepingAlgorithm}
+\end{figure}
+
+\end{proposition}
+
+\begin{proof}
+When we sweep vertex~$v$ where pipe~$i$ arrives horizontally and pipe~$j$ arrives vertically,
 \begin{itemize}
-	\item If $q$ needs to go straight north, then we have no choice but imposing a crossing at~$v$,
-	\item Otherwise, we have no choice but imposing an elbow at~$v$.
-Indeed, if there is a crossing at~$v$, then \cref{lem:rectangle} ensures that~$q$ will be below~$p$ in~$P\contact$, so that~$\pi$ would not be a linear extension of~$P$.
+\item we have no choice but imposing a contact at~$v$ if~$i > j$ (since pipes $i$ and~$j$ already crossed before) or~$\omega^{-1}(i) < \omega^{-1}(j)$ (since pipes~$i$ and~$j$ do not cross at all),
+\item if~$i < j$ and~$\omega^{-1}(i) > \omega^{-1}(j)$, then
+\begin{itemize}
+\item if~$\pi^{-1}(i) > \pi^{-1}(j)$ then pipes~$i$ and~$j$ cannot touch (otherwise $\pi$ would not be a linear extension of~$P$), so that we have no choice but imposing a crossing~at~$v$,
+\item if~$\pi^{-1}(p) < \pi^{-1}(q)$ then
+	\begin{itemize}
+	\item if $v$ lies in column~$\omega^{-1}(j)$, then pipe $j$ needs to go straight north, and we have no choice but imposing a crossing at~$v$,
+	\item otherwise, we have no choice but imposing a contact at~$v$ (otherwise \cref{lem:rectangle} ensures that~$j \contactLess{P} i$, so that~$\pi$ would not be a linear extension of~$P$).
+	\qedhere
 	\end{itemize}
 \end{itemize}
+\end{itemize}
+\end{proof}
 
@@
 
-We now define a surjective map from the permutations of~$[e, \omega]$ to the pipe dreams of~$\acyclicPipeDreams(\omega)$.
-This map, adapted from~\cite{Pilaud-BrickAlgebra}, is obtained by an insertion process similar to the insertion in binary search trees.
-%To properly describe this insertion algorithm, we introduce additional notations.
-We now describe this insertion algorithm, which is illustrated in \cref{fig:insertionAlgorithm}.
-
-Consider a given permutation~$\pi \eqdef \pi(1) \dots \pi(n)$ (written in one-line notation) in~$[e, \omega]$.
-We start from the empty triangular shape and insert the pipes~$\pi(1), \dots, \pi(n)$ one by one in the order of the permutation~$\pi$ as northwest as possible.
-In other words, at step~$t$, we consider the set~$X_t$ of free northwest elbows in the rectangle~$[\pi(t)] \times [\omega^{-1}(\pi(t))]$.
-The pipe inserted at step~$t$ then starts in row~$\pi(t)$, ends in column~$\omega^{-1}(\pi(t))$, covers each elbow of~$X_t$ with a southeast elbow, and adds just one new free northwest elbow in between any two consecutive elbows of~$X_t$.
-We denote the resulting pipe dream by~$\insertion{\pi}{\omega}$.
+Our second algorithm is an \defn{insertion algorithm} that constructs the unique pipe dream~$P \in \acyclicPipeDreams(\omega)$ of which~$\pi$ is a linear extension.
+It is inspired from~\cite{Pilaud-BrickAlgebra} and is similar to the insertion in binary search trees.
+
+\begin{proposition}
+\label{prop:insertionAlgorithm}
+For any permutations~$\pi,\omega \in \fS_n$ such that~$\pi < \omega$ in weak order, the unique pipe dream~$P \in \acyclicPipeDreams(\omega)$ such that~$\pi \in \linearExtensions(P)$ can be constructed starting from the empty triangular shape and inserting the pipes~$\pi(1), \dots, \pi(n)$ one by one in the order of the permutation~$\pi$ as northwest as possible.
+More precisely, at step~$t$, we consider the set~$X_t$ of free southeast elbows in the rectangle~$[\pi(t)] \times [\omega^{-1}(\pi(t))]$, and we insert a pipe starting at row~$\pi(t)$, ending at column~$\omega^{-1}(\pi(t))$, covering each elbow of~$X_t$, and adding a new free southeast elbow in between any two consecutive elbows of~$X_t$
 See \cref{fig:insertionAlgorithm}.
 
-\begin{figure}[b]
-	\centerline{
-		\includegraphics[scale=.9]{insertion}
-	}
-	\caption{The insertion~$\insertion{513264}{561324}$.}
+\begin{figure}
+	\centerline{\includegraphics[scale=.9]{insertion}}
+	\caption{Insertion algorithm for the permutations~$\pi = 513264$ and~$\omega = 561324$.}
 	\label{fig:insertionAlgorithm}
 \end{figure}
-
+\end{proposition}
+
+\vincent{I am still working below this line.}
 We need to argue that this algorithm indeed creates a pipe dream of~$\acyclicPipeDreams(\omega)$.
@@
 Fix~$t \in [n]$.
-At the beginning of the algorithm, there is no southeast elbow in the rectangle~$R_t \eqdef [\pi(t)] \times [\omega^{-1}(\pi(t))]$.
+At the beginning of the algorithm, there is no southeast contact in the rectangle~$R_t \eqdef [\pi(t)] \times [\omega^{-1}(\pi(t))]$.
 At each step~$s < t$, we have inserted a new pipe~$\pi(s)$ which enters at~$\pi(s)$ and exits at~$\omega^{-1}\big( \pi(s) \big)$.
@@
 \item If~$\pi(s) < \pi(t)$ and~$\omega^{-1}\big( \pi(s) \big) < \omega^{-1}\big( \pi(t) \big)$, then the pipe~$\pi(s)$ is completely contained in the rectangle~$R_t$.
-Since the pipe~$\pi(s)$ has one more northwest elbow than southeast elbow, its insertion creates a new free northwest elbow in the rectangle~$R_t$.
-\item If~$\pi(s) < \pi(t)$ and~$\omega^{-1}\big( \pi(s) \big) > \omega^{-1}\big( \pi(t) \big)$, then the pipe~$\pi(s)$ enters and exits the rectangle~$R_t$ with an horizontal step, so that it has as many northwest and southeast elbows in~$R_t$, and its insertion does not modify the number of free northwest elbows in the rectangle~$R_t$.
-\item If~$\pi(s) > \pi(t)$ and~$\omega^{-1}\big( \pi(s) \big) < \omega^{-1}\big( \pi(t) \big)$, then the pipe~$\pi(s)$ enters and exits the rectangle~$R_t$ with a vertical step, so that it has as many northwest and southeast elbows in~$R_t$, and its insertion does not modify the number of free northwest elbows in the rectangle~$R_t$.
+Since the pipe~$\pi(s)$ has one more northwest contact than southeast contact, its insertion creates a new free northwest contact in the rectangle~$R_t$.
+\item If~$\pi(s) < \pi(t)$ and~$\omega^{-1}\big( \pi(s) \big) > \omega^{-1}\big( \pi(t) \big)$, then the pipe~$\pi(s)$ enters and exits the rectangle~$R_t$ with an horizontal step, so that it has as many northwest and southeast contacts in~$R_t$, and its insertion does not modify the number of free northwest contacts in the rectangle~$R_t$.
+\item If~$\pi(s) > \pi(t)$ and~$\omega^{-1}\big( \pi(s) \big) < \omega^{-1}\big( \pi(t) \big)$, then the pipe~$\pi(s)$ enters and exits the rectangle~$R_t$ with a vertical step, so that it has as many northwest and southeast contacts in~$R_t$, and its insertion does not modify the number of free northwest contacts in the rectangle~$R_t$.
 \item If~$\pi(s) > \pi(t)$ and~$\omega^{-1}\big( \pi(s) \big) > \omega^{-1}\big( \pi(t) \big)$, then setting~$i = \pi(t)$ and~$j = \pi(s)$, we have~$i < j$ and~$\pi^{-1}(i) > \pi^{-1}(j)$ while~$\omega^{-1}(i) < \omega^{-1}(j)$, which contradicts our assumption that~$\pi \not< \omega$ in weak order.
@@
 \begin{proof}
-The algorithm constructs a collection~$P$ of $n$ pairwise disjoint pipes except at crossings and elbows.
+The algorithm constructs a collection~$P$ of $n$ pairwise disjoint pipes except at crossings and contacts.
 For each~$t \in [n]$, the pipe~$\pi(t)$ enters at~$\pi(t)$, exits at~$\omega^{-1}\big( \pi(t) \big)$, and has 
@@
 \]
-many $\se$ elbows by \cref{lem:rectangleInsertionAlgorithm} and since~$\pi < \omega$ in weak order.
+many $\se$ contacts by \cref{lem:rectangleInsertionAlgorithm} and since~$\pi < \omega$ in weak order.
 We thus conclude the proof by a direct application of \cref{lem:characterizationPipeDreams}.
@@
 \begin{proof}
-By construction of the insertion algorithm, all southeast elbows of the pipe~$\pi(t)$ inserted at step~$t$ are in contact with northwest elbows of pipes~$\pi(s)$ inserted at steps~$s < t$.
+By construction of the insertion algorithm, all southeast contacts of the pipe~$\pi(t)$ inserted at step~$t$ are in contact with northwest contacts of pipes~$\pi(s)$ inserted at steps~$s < t$.
 In other words, all edges in the contact graph of~$\insertion{\pi}{\omega}$ are of the form~$\pi(s) \to \pi(t)$ for some~$s < t$.
@@
 At step~$t$ of the algorithm presented in the previous section, we have inserted the word~$U$.
-At that moment, let~$X_t$ (resp.~$X'_t$, resp~$Y_t$) denote the set of free northwest elbows in the rectangle~$[a] \times [\omega^{-1}(a)]$ (resp.~$[c] \times [\omega^{-1}(c)]$, resp.~$[a] \times [\omega^{-1}(c)]$).
+At that moment, let~$X_t$ (resp.~$X'_t$, resp~$Y_t$) denote the set of free northwest contacts in the rectangle~$[a] \times [\omega^{-1}(a)]$ (resp.~$[c] \times [\omega^{-1}(c)]$, resp.~$[a] \times [\omega^{-1}(c)]$).
 Applying the same argument as in \cref{lem:rectangleInsertionAlgorithm}, we have
@@
 It follows that~$U ac V \equiv_\omega U ca V \iff \# Y_t = 0$.
-However, $Y_t = 0$ if and only if all elbows of~$X_t$ are in~$[a] \times [\omega^{-1}(c), \omega^{-1}(a)]$ and all elbows of~$X'_t$ are in~$[a,c] \times [\omega^{-1}(c)]$.
+However, $Y_t = 0$ if and only if all contacts of~$X_t$ are in~$[a] \times [\omega^{-1}(c), \omega^{-1}(a)]$ and all contacts of~$X'_t$ are in~$[a,c] \times [\omega^{-1}(c)]$.
 The latter is equivalent to the fact that the insertion of~$a$ and~$c$ commute.

### 2022-11-29 acyclicFacets/draft/latticePipeDreams.tex
minor changes

--- 2022-10-17 acyclicFacets/draft/latticePipeDreams.tex
@@
 The flip is \defn{increasing} if the contact~$c$ is weakly southwest of the crossing~$x$.
-For example, \cref{fig:pipeDreams} illustrates an increasing from the left pipe dream to the right pipe dream.
+For example, \cref{fig:pipeDreams} illustrates an increasing flip from the left pipe dream to the right pipe dream.
 %
@@
 \cref{fig:counterExampleRestrictionIncreasingFlipPoset} illustrates two acyclic pipe dreams of~$\acyclicPipeDreams(126543)$ connected by a sequence of increasing flips in~$\pipeDreams(126543)$ but by no sequence of increasing flips in~$\acyclicPipeDreams(126543)$.
+This example is minimal.
 %	* type A5,
@@
 See \cref{fig:sweepingAlgorithm}.
-\vincent{todo}
-
+%
 \begin{figure}
-%	\centerline{\includegraphics[scale=.9]{sweeping}}
+	\centerline{\includegraphics[scale=.9]{sweeping}}
 	\caption{Sweeping algorithm for the permutations~$\pi = 513264$ and~$\omega = 561324$.}
@@
 For any permutations~$\pi,\omega \in \fS_n$ such that~$\pi < \omega$ in weak order, the unique pipe dream~$P \in \acyclicPipeDreams(\omega)$ such that~$\pi \in \linearExtensions(P)$ can be constructed starting from the empty triangular shape and inserting the pipes~$\pi(1), \dots, \pi(n)$ one by one in the order of the permutation~$\pi$ as northwest as possible.
-More precisely, at step~$t$, we consider the set~$X_t$ of free southeast elbows in the rectangle~$[\pi(t)] \times [\omega^{-1}(\pi(t))]$, and we insert a pipe starting at row~$\pi(t)$, ending at column~$\omega^{-1}(\pi(t))$, covering each elbow of~$X_t$, and adding a new free southeast elbow in between any two consecutive elbows of~$X_t$
+More precisely, at step~$t$, we insert a pipe starting at row~$\pi(t)$, ending at column~$\omega^{-1}(\pi(t))$, and whose northeast elbows are precisely covering the free southeast elbows in the rectangle~$[\pi(t)] \times [\omega^{-1}(\pi(t))]$.
+%More precisely, at step~$t$, we consider the set~$X_t$ of free southeast elbows in the rectangle~$[\pi(t)] \times [\omega^{-1}(\pi(t))]$, and we insert a pipe starting at row~$\pi(t)$, ending at column~$\omega^{-1}(\pi(t))$, and whose northeast elbows are precisely covering the elbows of~$X_t$, and adding a new free southeast elbow in between any two consecutive elbows of~$X_t$
 See \cref{fig:insertionAlgorithm}.
@@
 \label{lem:rectangleInsertionAlgorithm}
-At each step~$t$ of the insertion algorithm, we have
-\[
-\#X_t = \# \bigset{s < t}{\pi(s) < \pi(t) \text{ and } \omega^{-1}\big( \pi(s) \big) < \omega^{-1}\big( \pi(t) \big)}.
+At each step~$t$ of the insertion algorithm, the number of free southeast elbows in the rectangle~$[\pi(t)] \times [\omega^{-1}(\pi(t))]$ is
+\[
+\# \bigset{s < t}{\pi(s) < \pi(t) \text{ and } \omega^{-1}\big( \pi(s) \big) < \omega^{-1}\big( \pi(t) \big)}.
 \]

### 2023-01-11 acyclicFacets/draft/latticePipeDreams.tex
insertion algorithms completed

--- 2022-11-29 acyclicFacets/draft/latticePipeDreams.tex
@@
 It is clearly a directed acyclic graph, and it has a unique source and a unique sink \cite{PilaudPocchiola}, called the \defn{greedy} and \defn{antigreedy} pipe dreams, and denoted~$\greedyPipeDream$ and~$\antiGreedyPipeDream$.
-\vincent{In \cite{PilaudStump-ELlabeling}, these are called positive and negative greedy facets. Also the notations are different...}
+\vincent{In \cite{PilaudStump-ELlabelings}, these are called positive and negative greedy facets. Also the notations are different...}
 The \defn{increasing flip poset} is the reflexive and transitive closure of the increasing flip graph on~$\pipeDreams(\omega)$.
@@
 % We denote by~$\reversingPipeDreams_n$ the reversing pipe dreams of~$\pipeDreams_n$.
-As observed in~\cite{Woo, PilaudPocchiola, Pilaud-these, Stump}, the family of reversing pipe dreams belong to the Catalan families.
+As observed in~\cite{Woo, PilaudPocchiola, Pilaud-these, Stump}, the family of reversing pipe dreams belong to the Catalan families, meaning that it is counted by the famous Catalan numbers.
 \cref{fig:bijection} illustrates explicit bijections between reversing pipe dreams of~$\pipeDreams(\rho_n)$, binary trees with $n$ internal nodes, and the triangulations of a convex $(n+2)$-gon.
@@
 
-We now gather some elementary properties of crossings and contacts that will be needed later to construct pipe dreams from permutations.
+We now gather some elementary properties of crossings and contacts in pipe dreams that will be needed later to construct pipe dreams from permutations.
 For a pipe dream~$P \in \pipeDreams(\omega)$, we call pipe~$j$ the pipe which enters at row~$j$ and exits at column~$\omega^{-1}(j)$.
@@
 In this section, we extend this result to any permutation~$\omega$, by proving that the transitive closure of the increasing flip graph on acyclic pipe dreams of~$\acyclicPipeDreams(\omega)$ is the Hasse diagram of a lattice quotient of the weak order interval~$[e,\omega]$.
+This section goes straight to the proof of this property, and leaves alternative perspectives on this quotient to \cref{sec:furtherTopics}.
 
@@
 
-We will see in \cref{sec:algorithms} insertion algorithms to compute the pipe dream~$P \in \acyclicPipeDreams(\omega)$ of which a given permutation~$\pi \in [e,\omega]$ is a linear extension, for any permutation~$\omega$.
+We will see in \cref{sec:furtherTopics} insertion algorithms to compute the pipe dream~$P \in \acyclicPipeDreams(\omega)$ of which a given permutation~$\pi \in [e,\omega]$ is a linear extension, for any permutation~$\omega$.
 These algorithms are however not needed for the proof of \cref{thm:partitionPipeDreams}, which we break into the following three lemmas.
@@
 \label{lem:partition}
-If~$\pi \le \omega$ in weak order, then~$\pi$ a linear extension of a unique pipe dream~$P \in \acyclicPipeDreams(\omega)$.
+If~$\pi \le \omega$ in weak order, then~$\pi$ is a linear extension of a unique pipe dream~$P \in \acyclicPipeDreams(\omega)$.
 \end{lemma}
@@
 A \defn{congruence} of a lattice~$(L, \le, \meet, \join)$ is an equivalence relation~$\equiv$ on~$L$ which respects meets and joins: $x \equiv x'$ and~$y \equiv y'$ implies $x \meet y \equiv x' \meet y'$ and~$x \join y \equiv x' \join y'$.
-We will use the following classical characterization of lattice congruences.
+We will use the following classical characterization of lattice congruences, see~\cite{Reading-PosetRegionsChapter}.
 
@@
 
-We will discuss in \cref{subsec:rewritingAlgorithm} rewriting rules for the pipe dream congruence~$\equiv_\omega$, for any permutation~$\omega$.
-This rewriting rule is however not needed for the proof of \cref{thm:pipeDreamCongruence}.
+We will discuss in \cref{subsec:rewritingRule} rewriting rules for the pipe dream congruence~$\equiv_\omega$, for any permutation~$\omega$.
+These rewriting rules are however not needed for the proof of \cref{thm:pipeDreamCongruence}.
 We prove it by checking both conditions of \cref{prop:characterizationCongruences}.
@@
 Since the southwest corner of~$A$ is located northeast of the northeast corner of~$C$, this forces an elbow~$e$ of~$\pi$ to lie in region~$B$.
-\cref{lem:rectangle} then ensures that either~$i \contactLess{P} j$ (if~$e$ is above the pipe~$j$), or~$j \contactLess{P} k$ (if~$e$ is below the pipe~$j$).
+\cref{lem:rectangle} then ensures that either~$i \contactLess{P} j$ (if~$e$ is north of pipe~$j$), or~$j \contactLess{P} k$ (if~$e$ is south of pipe~$j$).
 The proof is similar if~$i \contactMore{P} k$.
@@
 
-\section{Three algorithms}
-\label{sec:algorithms}
-
-\vincent{This section is in progress}
-In this section, we describe three algorithms to decide whether two permutations~$\pi$ and~$\pi'$ are equivalent for the pipe dream congruence~$\equiv_\omega$.
-The first two algorithms actually construct the unique pipe dream~$P \in \acyclicPipeDreams(\omega)$ of which~$\pi$ is a linear extension, while the last algorithm uses a rewriting technique.
+\section{Further topics}
+\label{sec:furtherTopics}
+
+In this section, we discuss four further topics on the pipe dream congruence.
+In \cref{subsec:sweepingAlgorithm,subsec:insertionAlgorithm}, we describe two algorithms to construct the unique pipe dream~$P \in \acyclicPipeDreams(\omega)$ of which a given permutation~$\pi$ is a linear extension.
+In \cref{subsec:rewritingRule}, we describe the pipe dream congruence~$\equiv_\omega$ as the transitive closure of a rewriting rule on permutations of~$[e, \omega]$.
+Finally, in \cref{subsec:canopy}, we describe the natural coarsening of the pipe dream congruence~$\equiv_\omega$ by the recoil congruence~$\simeq_\omega$.
 
@@
 
-Our first algorithm is a \defn{sweeping algorithm} that constructs the unique pipe dream~$P \in \acyclicPipeDreams(\omega)$ of which~$\pi$ is a linear extension.
-It is inspired by the algorithm to compute greedy pipe dreams~\cite{PilaudPocchiola, PilaudStump-ELlabelings}.
+Our first algorithm to construct the unique pipe dream~$P \in \acyclicPipeDreams(\omega)$ with~$\pi \in \linearExtensions(P)$ is a \defn{sweeping algorithm}, inspired by the algorithm to compute greedy pipe dreams~\cite{PilaudPocchiola, PilaudStump-ELlabelings}.
 Extensions of this algorithm will be discussed in \cref{..}. \vincent{todo. Was this algorithm explicitly somewhere before? We should cite Jahn-Stump later in the paper.}
@@
 \label{prop:sweepingAlgorithm}
-For any permutations~$\pi,\omega \in \fS_n$ such that~$\pi < \omega$ in weak order, the unique pipe dream~$P \in \acyclicPipeDreams(\omega)$ such that~$\pi \in \linearExtensions(P)$ can be constructed by sweeping the triangular shape in any perturbation of the northwest direction and inserting a crossing when sweeping a vertex~$v$ of the grid where pipe~$i$ arrives horizontally and pipe~$j$ arrives vertically if and only if
+For any permutations~$\pi,\omega \in \fS_n$ such that~$\pi < \omega$ in weak order, the unique pipe dream~$P \in \acyclicPipeDreams(\omega)$ such that~$\pi \in \linearExtensions(P)$ can be constructed by sweeping the triangular shape in any perturbation of the northwest direction and placing a crossing when sweeping a vertex~$v$ of the grid where pipe~$i$ arrives horizontally and pipe~$j$ arrives vertically if and only if
 \begin{itemize}
@@
 	\centerline{\includegraphics[scale=.9]{sweeping}}
-	\caption{Sweeping algorithm for the permutations~$\pi = 513264$ and~$\omega = 561324$.}
+	\caption{Sweeping algorithm for the permutations~$\pi = 513264$ and~$\omega = 561324$.} % See details in \cref{exm:sweepingAlgorithm}.}
 	\label{fig:sweepingAlgorithm}
 \end{figure}
-
 \end{proposition}
 
-\begin{proof}
+\begin{example}
+\label{exm:sweepingAlgorithm}
+\cref{fig:sweepingAlgorithm} illustrates the sweeping algorithm for the permutations~${\pi = 513264}$ and~${\omega = 561324}$.
+The algorithm has 15 steps, but we have grouped together steps $2$ to $9$ (second arrow) and steps $12$ to $13$ (fifth arrow) as they have the same justification.
+We place contacts in steps $1$, $10$, $12$, $13$ and~$15$ since~$\omega^{-1}(i) < \omega^{-1}(j)$, and in step~$14$ since~$i > j$.
+We place crossings in steps $2$ to $9$ since~$i < j$, $\omega^{-1}(i) > \omega^{-1}(j)$ and we are in the column~$\omega^{-1}(j)$, and in step $11$ since~$i < j$, $\omega^{-1}(i) > \omega^{-1}(j)$ and~$\pi^{-1}(i) > \pi^{-1}(j)$.
+\end{example}
+
+\begin{proof}[Proof of \cref{prop:sweepingAlgorithm}]
 When we sweep vertex~$v$ where pipe~$i$ arrives horizontally and pipe~$j$ arrives vertically,
@@
 
-Our second algorithm is an \defn{insertion algorithm} that constructs the unique pipe dream~$P \in \acyclicPipeDreams(\omega)$ of which~$\pi$ is a linear extension.
-It is inspired from~\cite{Pilaud-BrickAlgebra} and is similar to the insertion in binary search trees.
+Our second algorithm to construct the unique pipe dream~$P \in \acyclicPipeDreams(\omega)$ with~$\pi \in \linearExtensions(P)$ is an \defn{insertion algorithm} inspired from~\cite{Pilaud-BrickAlgebra} and similar to the insertion in binary search trees.
+
+We call \defn{staircase} of length~$k$ a sequence~$e_1, \dots, e_k$ of southeast elbows such that~$e_i$ is located strictly southwest of~$e_{i+1}$ for each~$i \in [k-1]$.
+In other words, $r_1 > \dots > r_k$ and~$c_1 < \dots < c_k$ where~$e_i$ is located in row~$r_i$ and column~$c_i$.
+For~$j \in [n]$ such that~$j > r_1$ and~$c_k < \omega^{-1}(j)$, there is a unique pipe which enters at row~$j$, exits at column~$\omega^{-1}(j)$, and whose northeast elbows are precisely covering the southeast elbows~$e_1, \dots, e_k$.
+Namely, it has a northeast elbow at row~$r_i$ and column~$c_i$ for each~$i \in [k]$, and a southeast elbow at row~$r_{i-1}$ and column~$c_i$ for each~$i \in [k+1]$, where by convention~$r_0 \eqdef j$ and~$c_{k+1} \eqdef \omega^{-1}(j)$.
 
@@
 For any permutations~$\pi,\omega \in \fS_n$ such that~$\pi < \omega$ in weak order, the unique pipe dream~$P \in \acyclicPipeDreams(\omega)$ such that~$\pi \in \linearExtensions(P)$ can be constructed starting from the empty triangular shape and inserting the pipes~$\pi(1), \dots, \pi(n)$ one by one in the order of the permutation~$\pi$ as northwest as possible.
-More precisely, at step~$t$, we insert a pipe starting at row~$\pi(t)$, ending at column~$\omega^{-1}(\pi(t))$, and whose northeast elbows are precisely covering the free southeast elbows in the rectangle~$[\pi(t)] \times [\omega^{-1}(\pi(t))]$.
+More precisely, at step~$t$, we insert a pipe starting at row~$\pi(t)$, ending at column~$\omega^{-1}(\pi(t))$, and whose northeast elbows are precisely covering the staircase of currently free southeast elbows in the rectangle~$[\pi(t)] \times [\omega^{-1}(\pi(t))]$.
 %More precisely, at step~$t$, we consider the set~$X_t$ of free southeast elbows in the rectangle~$[\pi(t)] \times [\omega^{-1}(\pi(t))]$, and we insert a pipe starting at row~$\pi(t)$, ending at column~$\omega^{-1}(\pi(t))$, and whose northeast elbows are precisely covering the elbows of~$X_t$, and adding a new free southeast elbow in between any two consecutive elbows of~$X_t$
@@
 
-\vincent{I am still working below this line.}
-We need to argue that this algorithm indeed creates a pipe dream of~$\acyclicPipeDreams(\omega)$.
-To see it, we observe that the following invariant is maintained throughout the algorithm.
+\begin{example}
+\label{exm:insertionAlgorithm}
+\cref{fig:insertionAlgorithm} illustrates the insertion algorithm for the permutations~${\pi = 513264}$ and~${\omega = 561324}$.
+For instance, when inserting the (green) pipe~$4$ in the last step, the currently free southeast elbows are the first southeast elbow of the (blue) pipe~$3$ and the two southeast elbows of the (purple) pipe~$2$.
+\end{example}
+
+We need to argue that this algorithm indeed creates a pipe dream of~$\pipeDreams(\omega)$.
+To see it, we observe that the following two invariants are maintained throughout the algorithm.
+We call \defn{hook} of a southeast elbow~$e$ the union of the horizontal segment west of~$e$ and the vertical segment north of~$e$.
+
+\begin{lemma}
+\label{lem:disjointPipesInsertionAlgorithm}
+At any time during the insertion algorithm, the support of the pipes already inserted is precisely the union of the hooks of the currently free southeast elbows.
+\end{lemma}
+
+\begin{proof}
+Immediate by induction, as the support of a pipe is precisely the union of the hooks of its southeast elbows minus the union of the pipes of its northeast elbows.
+\end{proof}
+
+\begin{corollary}
+\label{coro:disjointPipesInsertionAlgorithm}
+The pipes constructed by the insertion algorithm are disjoint, except at crossings and contacts.
+\end{corollary}
 
@@
 \label{lem:rectangleInsertionAlgorithm}
-At each step~$t$ of the insertion algorithm, the number of free southeast elbows in the rectangle~$[\pi(t)] \times [\omega^{-1}(\pi(t))]$ is
-\[
-\# \bigset{s < t}{\pi(s) < \pi(t) \text{ and } \omega^{-1}\big( \pi(s) \big) < \omega^{-1}\big( \pi(t) \big)}.
-\]
-\vincent{Note that this is independent of~$\pi$... This can be seen from \cref{lem:interval}.}
+For any~$1 \le t \le r \le n$, the free southeast elbows in the rectangle~$[\pi(r)] \times [\omega^{-1}(\pi(r))]$ just before step~$t$ of the insertion algorithm form a staircase of length
+\[
+{\# \bigset{s < t}{\pi(s) < \pi(r) \text{ and } \omega^{-1}(\pi(s)) < \omega^{-1}(\pi(r))}}.
+\]
 \end{lemma}
@@
 \begin{proof}
-Fix~$t \in [n]$.
-At the beginning of the algorithm, there is no southeast contact in the rectangle~$R_t \eqdef [\pi(t)] \times [\omega^{-1}(\pi(t))]$.
-At each step~$s < t$, we have inserted a new pipe~$\pi(s)$ which enters at~$\pi(s)$ and exits at~$\omega^{-1}\big( \pi(s) \big)$.
-We conclude by considering the four possible cases:
+Denote by~$R$ the rectangle~$[\pi(r)] \times [\omega^{-1}(\pi(r))]$.
+The proof works by induction on~$t$.
+Before step~$1$, there is no southeast elbow in~$R$.
+Assume now that just before step~$t$, the free southeast elbows in~$R$ form a staircase~$e_1, \dots, e_k$ with~$k = \# \bigset{{s < t}}{{\pi(s) < \pi(r)} \text{ and } {\omega^{-1}(\pi(s)) < \omega^{-1}(\pi(r))}}$.
+At step~$t$, we insert a new pipe~$\pi(t)$ which enters at~$\pi(t)$ and exits at~$\omega^{-1}(\pi(t))$.
+Let~${0 \le i < j \le k+1}$ be such that~$e_{i+1}, \dots, e_{j-1}$ are the northwest elbows of pipe~$\pi(t)$ in~$R$, and let~$e'_1, \dots, e'_\ell$ be the southeast elbows of pipe~$\pi(t)$ in~$R$.
+Hence, the free southeast elbows in~$R$ after step~$t$ form the sequence~$e_1, \dots, e_i, e'_1, \dots, e'_\ell, e_j, \dots, e_k$.
+We thus just need to see that
 \begin{itemize}
-\item If~$\pi(s) < \pi(t)$ and~$\omega^{-1}\big( \pi(s) \big) < \omega^{-1}\big( \pi(t) \big)$, then the pipe~$\pi(s)$ is completely contained in the rectangle~$R_t$.
-Since the pipe~$\pi(s)$ has one more northwest contact than southeast contact, its insertion creates a new free northwest contact in the rectangle~$R_t$.
-\item If~$\pi(s) < \pi(t)$ and~$\omega^{-1}\big( \pi(s) \big) > \omega^{-1}\big( \pi(t) \big)$, then the pipe~$\pi(s)$ enters and exits the rectangle~$R_t$ with an horizontal step, so that it has as many northwest and southeast contacts in~$R_t$, and its insertion does not modify the number of free northwest contacts in the rectangle~$R_t$.
-\item If~$\pi(s) > \pi(t)$ and~$\omega^{-1}\big( \pi(s) \big) < \omega^{-1}\big( \pi(t) \big)$, then the pipe~$\pi(s)$ enters and exits the rectangle~$R_t$ with a vertical step, so that it has as many northwest and southeast contacts in~$R_t$, and its insertion does not modify the number of free northwest contacts in the rectangle~$R_t$.
-\item If~$\pi(s) > \pi(t)$ and~$\omega^{-1}\big( \pi(s) \big) > \omega^{-1}\big( \pi(t) \big)$, then setting~$i = \pi(t)$ and~$j = \pi(s)$, we have~$i < j$ and~$\pi^{-1}(i) > \pi^{-1}(j)$ while~$\omega^{-1}(i) < \omega^{-1}(j)$, which contradicts our assumption that~$\pi \not< \omega$ in weak order.
+\item $e_i$ is southwest of~$e'_1$ and~$e'_\ell$ is southwest of~$e_j$,
+\item $\ell = j-i$ if~$\pi(s) < \pi(t)$ and~$\omega^{-1}(\pi(s)) > \omega^{-1}(\pi(t))$, and $\ell = j-i-1$ otherwise.
+\end{itemize}
+This immediately follows considering the four possible cases:
+\begin{itemize}
+\item If~$\pi(t) < \pi(r)$ and~$\omega^{-1}(\pi(t)) < \omega^{-1}(\pi(r))$, then the pipe~$\pi(t)$ is completely contained in~$R$, hence it has one more northwest elbow than southeast elbow in~$R$.
+\item If~$\pi(s) < \pi(t)$ and~$\omega^{-1}(\pi(s)) > \omega^{-1}(\pi(t))$, then the pipe~$\pi(s)$ enters and exits~$R$ with an horizontal step, hence it has as many northwest and southeast elbows in~$R$.
+\item If~$\pi(s) > \pi(t)$ and~$\omega^{-1}(\pi(s)) < \omega^{-1}(\pi(t))$, then the pipe~$\pi(s)$ enters and exits~$R$ with a vertical step, hence it has as many northwest and southeast elbows in~$R$.
+\item If~$\pi(s) > \pi(t)$ and~$\omega^{-1}(\pi(s)) > \omega^{-1}(\pi(t))$, then setting~$i \eqdef \pi(t)$ and~$j \eqdef \pi(s)$, we have~${i < j}$ and~$\pi^{-1}(i) > \pi^{-1}(j)$ while~$\omega^{-1}(i) < \omega^{-1}(j)$, which contradicts our assumption that~$\pi < \omega$ in weak order.
 \qedhere
@@
 
+We now derive two properties of the insertion algorithm from \cref{lem:rectangleInsertionAlgorithm}.
+Recall that we denote by~$\noninversions{\omega}{j} \eqdef \#\set{i \in [n]}{i < j \text{ and } \omega^{-1}(i) < \omega^{-1}(j)}$ the number of non-inversions of~$j$ in a permutation~$\omega$.
+
 \begin{corollary}
-For any~$\pi \le \omega$, the insertion algorithm creates a pipe dream~$\insertion{\pi}{\omega}$ of~$\pipeDreams(\omega)$.
+\label{coro:rectangleInsertionAlgorithm1}
+For any~$t \in [n]$, the free southeast elbows in the rectangle~$[\pi(t)] \times [\omega^{-1}(\pi(t))]$ just before step~$t$ of the insertion algorithm form a staircase of length~$\noninversions{\omega}{\pi(t)}$.
 \end{corollary}
@@
 \begin{proof}
-The algorithm constructs a collection~$P$ of $n$ pairwise disjoint pipes except at crossings and contacts.
-For each~$t \in [n]$, the pipe~$\pi(t)$ enters at~$\pi(t)$, exits at~$\omega^{-1}\big( \pi(t) \big)$, and has 
-\[
-\# \bigset{s < t}{\pi(s) < \pi(t) \text{ and } \omega^{-1}\big( \pi(s) \big) < \omega^{-1}\big( \pi(t) \big)} = \noninversions(\omega, \pi(t))
-\]
-many $\se$ contacts by \cref{lem:rectangleInsertionAlgorithm} and since~$\pi < \omega$ in weak order.
-We thus conclude the proof by a direct application of \cref{lem:characterizationPipeDreams}.
-\vincent{Maybe we should argue that the pipes remain in the triangle.}
-\end{proof}
+%Fix~$t \in [n]$.
+Observe first that if there is~$s > t$ such that~$\pi(s) < \pi(t)$ and~$\omega^{-1}(\pi(s)) < \omega^{-1}(\pi(t))$, then setting~$i \eqdef \pi(s)$ and~$j \eqdef \pi(t)$, we have~$i < j$ and~$\pi^{-1}(i) > \pi^{-1}(j)$ while~$\omega^{-1}(i) < \omega^{-1}(j)$, which contradicts our assumption that~$\pi < \omega$ in weak order.
+Hence, we obtain that
+\[
+\noninversions{\omega}{\pi(t)} = \# \bigset{s < t}{\pi(s) < \pi(t) \text{ and } \omega^{-1}(\pi(s)) < \omega^{-1}(\pi(t))}.
+\]
+Hence, the result follows from~\cref{lem:rectangleInsertionAlgorithm} applied to~$t = r$.
+\end{proof}
+
+\begin{corollary}
+\label{coro:rectangleInsertionAlgorithm2}
+All pipes of constructed by the insertion algorithm remain in the triangular shape.
+\end{corollary}
+
+\begin{proof}
+Let~$1 \le i \le j \le n$.
+Note that
+\[
+j - \noninversions{\omega}{j} = \#\set{i \in [n]}{i < j \text{ and } \omega^{-1}(i) > \omega^{-1}(j)} + 1 \le n - \omega^{-1}(j) + 1,
+\]
+so that~$\omega^{-1}(j) - \noninversions{\omega}{j} + j \ge n + 1$.
+By~\cref{lem:rectangleInsertionAlgorithm}, the pipe~$j$ has~$\noninversions{\omega}{j}$ southeast elbows in total, at most~$j-i-1$ of which are strictly south of row~$i$, so that at least~$\noninversions{\omega}{j} - j + i$ of which are strictly north of row~$i$.
+Hence, the eastmost point of pipe~$j$ in row~$i$ is at most in column~$\omega^{-1}(j) - \noninversions{\omega}{j} + j - i \le n - i + 1$.
+We conclude that pipe~$j$ indeed remains in the triangular shape.
+\end{proof}
+
+%\begin{corollary}
+%For any~$\pi \le \omega$, the insertion algorithm creates a pipe dream of~$\pipeDreams(\omega)$.
+%\end{corollary}
+
+\begin{proof}[Proof of \cref{prop:insertionAlgorithm}]
+The insertion algorithm constructs a collection~$P$ of $n$ pipes in the triangular shape (by \cref{coro:rectangleInsertionAlgorithm2}), which are pairwise disjoint except at crossings and contacts (by \cref{coro:disjointPipesInsertionAlgorithm}).
+For each~$t \in [n]$, the pipe~$\pi(t)$ enters at row~$\pi(t)$, exits at column~$\omega^{-1}(\pi(t))$, and has~$\noninversions{\omega}{\pi(t)}$ many southeast contacts (by \cref{coro:rectangleInsertionAlgorithm1}).
+We thus conclude that~$P$ is a pipe dream of~$\pipeDreams(\omega)$ by a direct application of \cref{lem:characterizationPipeDreams}.
+
+By construction, all southeast contacts of the pipe~$\pi(t)$ inserted at step~$t$ are in contact with northwest contacts of pipes~$\pi(s)$ inserted at steps~$s < t$.
+In other words, all edges in the contact graph of~$\insertion{\pi}{\omega}$ are of the form~$\pi(s) \to \pi(t)$ for some~$s < t$.
+It follows that the permutation~$\pi$ is a linear extension of the pipe dream~$P$.
+\end{proof}
+
+%\begin{proposition}
+%\label{prop:fibersInsertion}
+%For any pipe dream~$P \in \acyclicPipeDreams(\omega)$,  the permutations~$\pi \le \omega$ such that~$\insertion{\pi}{\omega} = P$ are precisely the linear extensions of the contact graph~$P\contact$ of~$P$.
+%In particular, $\insertion{\cdot}{\omega}$ is a surjection from~$[e, \omega]$ to~$\acyclicPipeDreams(\omega)$.
+%\end{proposition}
+%
+%\begin{proof}
+%By construction of the insertion algorithm, all southeast contacts of the pipe~$\pi(t)$ inserted at step~$t$ are in contact with northwest contacts of pipes~$\pi(s)$ inserted at steps~$s < t$.
+%In other words, all edges in the contact graph of~$\insertion{\pi}{\omega}$ are of the form~$\pi(s) \to \pi(t)$ for some~$s < t$.
+%It follows that the permutation~$\pi$ is a linear extension of~$\insertion{\pi}{\omega}$.
+%Reciprocally, consider a linear extension~$\pi$ of a pipe dream~$P$.
+%Then~$\insertion{\pi}{\omega}$ and~$P$ have a common linear extension~$\pi$, so that~$\insertion{\pi}{\omega} = P$ by \cref{prop:partition}.
+%\end{proof}
+%
+%In other words, the sets~$\set{\linearExtensions(P)}{P \in \acyclicPipeDreams(\omega)}$ are the fibers of the surjective insertion map~$\insertion{\cdot}{\omega}$.
+%Note that this concludes the proof of the surjectivity left open in \cref{prop:partition}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Rewriting rule}
+\label{subsec:rewritingRule}
+
+\vincent{I am still working below this line.}
+
+Recall from \cref{exm:Tamari3} that the sylvester congruence can be defined as the transitive closure of the classical rewriting rule~$UikVjW \equiv UkiVjW$ for~$i < j < k$ (as usual, we write the permutations of~$\fS_n$ as words in one-line notation).
+We now describe a similar rewriting rule for the pipe dream congruence~$\equiv_\omega$.
 
 \begin{proposition}
-\label{prop:fibersInsertion}
-For any pipe dream~$P \in \acyclicPipeDreams(\omega)$,  the permutations~$\pi \le \omega$ such that~$\insertion{\pi}{\omega} = P$ are precisely the linear extensions of the contact graph~$P\contact$ of~$P$.
-In particular, $\insertion{\cdot}{\omega}$ is a surjection from~$[e, \omega]$ to~$\acyclicPipeDreams(\omega)$.
+\label{prop:rewritingRule}
+On the interval~$[e,\omega]$ of the weak order, the pipe dream congruence~$\equiv_\omega$ coincides with the transitive closure of the rewriting rule~$U ik V \equiv_\omega U ki V$ where~$i < k$ are elements of~$[n]$ while~$U, V$ are (possibly empty) words on~$[n]$ such that
+\[
+\#\set{j \in U}{i < j < k \text{ and } \omega^{-1}(i) > \omega^{-1}(j) > \omega^{-1}(k)} \ge \#\set{j \in U}{j < i \text{ and } \omega^{-1}(j) < \omega^{-1}(k)}.
+%\#\set{j \in U}{i < j < k \text{ and } \omega^{-1}(i) > \omega^{-1}(j) > \omega^{-1}(k)} \ge \#\set{j < i}{\omega^{-1}(j) < \omega^{-1}(k)},
+\]
+\vincent{Note that $b \in U$ on the right hand side by \cref{lem:interval}.}
+% The letters~$j \in U$ such that~$i < j < k$ while~$\omega^{-1}(i) > \omega^{-1}(j) > \omega^{-1}(k)$ are called \defn{pipe dream congruence witnesses} for the exchange of~$i$ and~$k$.
+%\vincent{Another option to write this is $d \ge u$ where $d \eqdef \set{b \in U}{b > a}$ and~$u \eqdef \set{b \in U}{\omega^{-1}(b) < \omega^{-1}(c)}$.
+%Or $dr \ge \ell u$ where $dr \eqdef \set{b \in U}{b > a \text{ and } \omega^{-1}(b) > \omega^{-1}(c)}$ and~$\ell u \eqdef \set{b \in U}{b < a \text{ and } \omega^{-1}(b) < \omega^{-1}(c)}$.}
 \end{proposition}
-
-\begin{proof}
-By construction of the insertion algorithm, all southeast contacts of the pipe~$\pi(t)$ inserted at step~$t$ are in contact with northwest contacts of pipes~$\pi(s)$ inserted at steps~$s < t$.
-In other words, all edges in the contact graph of~$\insertion{\pi}{\omega}$ are of the form~$\pi(s) \to \pi(t)$ for some~$s < t$.
-It follows that the permutation~$\pi$ is a linear extension of~$\insertion{\pi}{\omega}$.
-Reciprocally, consider a linear extension~$\pi$ of a pipe dream~$P$.
-Then~$\insertion{\pi}{\omega}$ and~$P$ have a common linear extension~$\pi$, so that~$\insertion{\pi}{\omega} = P$ by \cref{prop:partition}.
-\end{proof}
-
-In other words, the sets~$\set{\linearExtensions(P)}{P \in \acyclicPipeDreams(\omega)}$ are the fibers of the surjective insertion map~$\insertion{\cdot}{\omega}$.
-Note that this concludes the proof of the surjectivity left open in \cref{prop:partition}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Rewriting algorithm}
-\label{subsec:rewritingAlgorithm}
-
-We now characterize the sets of linear extensions of pipe dreams in terms of a rewriting rule.
-We write the permutations of~$\fS_n$ as words in one-line notation.
-
-\vincent{Explain with the example of the sylvester congruence}
-
-\begin{definition}
-\label{def:congruence}
-For any permutation~$\omega \in \fS_n$, the \defn{pipe dream congruence} is the equivalence relation~$\equiv_\omega$ on the interval~$[e,\omega]$ of the weak order defined as the transitive closure of the rewriting rule~$U ac V \equiv_\omega U ca V$ if and only if
-\[
-\#\set{b \in U}{a < b < c \text{ and } \omega^{-1}(a) > \omega^{-1}(b) > \omega^{-1}(c)} \ge \#\set{b < a}{\omega^{-1}(b) < \omega^{-1}(c)},
-\]
-\vincent{Note that $b \in U$ on the right hand side by \cref{lem:interval}.}
-where~$a, b, c$ are elements of~$[n]$ while~$U, V$ are (possibly empty) words on~$[n]$.
-The letters~$b \in U$ such that~$a < b < c$ while~$\omega^{-1}(a) > \omega^{-1}(b) > \omega^{-1}(c)$ are called \defn{pipe dream congruence witnesses} for the exchange of~$a$ and~$c$.
-\vincent{Another option to write this is $d \ge u$ where $d \eqdef \set{b \in U}{b > a}$ and~$u \eqdef \set{b \in U}{\omega^{-1}(b) < \omega^{-1}(c)}$.
-Or $dr \ge \ell u$ where $dr \eqdef \set{b \in U}{b > a \text{ and } \omega^{-1}(b) > \omega^{-1}(c)}$ and~$\ell u \eqdef \set{b \in U}{b < a \text{ and } \omega^{-1}(b) < \omega^{-1}(c)}$.}
-\end{definition}
 

### 2023-01-11 acyclicFacets/draft/latticePipeDreams.tex
section 3 completed

@@
 \newtheorem{question}[theorem]{Question}
+\newtheorem{notation}[theorem]{Notation}
 
@@
 \newcommand{\nw}{\textsc{nw}} % northwest
-\newcommand{\insertion}[2]{\mathsf{ins}(#1,#2)} % insertion of permutation #1 in pipe dreams with permutation #2
 \newcommand{\duality}{^\star} % duality pipe dreams - triangulations
@@
 \newcommand{\acyclicOrientations}{\Omega} % set of pipe dreams
+\newcommand{\insertion}[2]{\mathsf{pd}(#1,#2)} % insertion of permutation #1 in pipe dreams with permutation #2
 \newcommand{\recoils}[2]{\mathsf{rec}(#1,#2)} % recoil scheme of a pipe dream
@@
 
+\begin{notation}
+For~$\pi \in [e, \omega]$, we denote by~$\insertion{\pi}{\omega}$ the pipe dream of~$\acyclicPipeDreams(\omega)$ such that~${\pi \in \linearExtensions(\insertion{\pi}{\omega})}$.
+\end{notation}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-We call \defn{pipe dream congruence} the equivalence relation~$\equiv_\omega$ on the weak order interval~$[e,\omega]$, whose equivalence classes are the sets of linear extensions of the pipe dreams of~$\acyclicPipeDreams(\omega)$.
+We call \defn{pipe dream congruence} the equivalence relation~$\equiv_\omega$ on the weak order interval~$[e,\omega]$ whose equivalence classes are the sets of linear extensions of the pipe dreams of~$\acyclicPipeDreams(\omega)$.
+In other words, $\pi \equiv_\omega \pi'$ if and only if~$\insertion{\pi}{\omega} = \insertion{\pi'}{\omega}$.
 This indeed defines an equivalence relation by \cref{thm:partitionPipeDreams}.
@@
 The classes of this congruence are the sets of linear extensions of the binary trees (considered as posets, labeled in inorder, and oriented towards their roots).
-It can also be defined by the classical rewriting rule~$UikVjW \equiv UkiVjW$ for~$i < j < k$.
+It can also be defined by the classical rewriting rule~$UjVikW \equiv UjVkiW$ where~$i < j < k$ are elements of~$[n]$ while~$U, V, W$ are (possibly empty) words on~$[n]$.
 \end{example}
@@
 In this section, we discuss four further topics on the pipe dream congruence.
-In \cref{subsec:sweepingAlgorithm,subsec:insertionAlgorithm}, we describe two algorithms to construct the unique pipe dream~$P \in \acyclicPipeDreams(\omega)$ of which a given permutation~$\pi$ is a linear extension.
+In \cref{subsec:sweepingAlgorithm,subsec:insertionAlgorithm}, we describe two algorithms to construct the pipe dream~$\insertion{\pi}{\omega}$ of~$\acyclicPipeDreams(\omega)$ of which a given permutation~$\pi$ is a linear extension.
 In \cref{subsec:rewritingRule}, we describe the pipe dream congruence~$\equiv_\omega$ as the transitive closure of a rewriting rule on permutations of~$[e, \omega]$.
-Finally, in \cref{subsec:canopy}, we describe the natural coarsening of the pipe dream congruence~$\equiv_\omega$ by the recoil congruence~$\simeq_\omega$.
+Finally, in \cref{subsec:canopy}, we describe the natural coarsening of the pipe dream congruence~$\equiv_\omega$ by the recoil congruence~$\cong_\omega$.
 
@@
 
-Our first algorithm to construct the unique pipe dream~$P \in \acyclicPipeDreams(\omega)$ with~$\pi \in \linearExtensions(P)$ is a \defn{sweeping algorithm}, inspired by the algorithm to compute greedy pipe dreams~\cite{PilaudPocchiola, PilaudStump-ELlabelings}.
+Our first algorithm to construct~$\insertion{\pi}{\omega}$ is a \defn{sweeping algorithm}, inspired by the algorithm to compute greedy pipe dreams~\cite{PilaudPocchiola, PilaudStump-ELlabelings}.
 Extensions of this algorithm will be discussed in \cref{..}. \vincent{todo. Was this algorithm explicitly somewhere before? We should cite Jahn-Stump later in the paper.}
@@
 
-Our second algorithm to construct the unique pipe dream~$P \in \acyclicPipeDreams(\omega)$ with~$\pi \in \linearExtensions(P)$ is an \defn{insertion algorithm} inspired from~\cite{Pilaud-BrickAlgebra} and similar to the insertion in binary search trees.
+Our second algorithm to construct~$\insertion{\pi}{\omega}$ is an \defn{insertion algorithm} inspired from~\cite{Pilaud-BrickAlgebra} and similar to the insertion in binary search trees.
 
@@
 \label{lem:rectangleInsertionAlgorithm}
-For any~$1 \le t \le r \le n$, the free southeast elbows in the rectangle~$[\pi(r)] \times [\omega^{-1}(\pi(r))]$ just before step~$t$ of the insertion algorithm form a staircase of length
-\[
-{\# \bigset{s < t}{\pi(s) < \pi(r) \text{ and } \omega^{-1}(\pi(s)) < \omega^{-1}(\pi(r))}}.
+For any~$t, r, c \in [n]$, the free southeast elbows in the rectangle~$[r] \times [c]$ just before step~$t$ of the insertion algorithm form a staircase of length
+\[
+\# \set{s < t}{\pi(s) \le r \text{ and } \omega^{-1}(\pi(s)) \le c} - \# \set{s < t}{\pi(s) > r \text{ and } \omega^{-1}(\pi(s)) > c}.
 \]
@@
 \begin{proof}
-Denote by~$R$ the rectangle~$[\pi(r)] \times [\omega^{-1}(\pi(r))]$.
+Denote by~$R$ the rectangle~$[r] \times [c]$.
 The proof works by induction on~$t$.
 Before step~$1$, there is no southeast elbow in~$R$.
-Assume now that just before step~$t$, the free southeast elbows in~$R$ form a staircase~$e_1, \dots, e_k$ with~$k = \# \bigset{{s < t}}{{\pi(s) < \pi(r)} \text{ and } {\omega^{-1}(\pi(s)) < \omega^{-1}(\pi(r))}}$.
+Assume now that just before step~$t$, the free southeast elbows in~$R$ form a staircase~$e_1, \dots, e_k$ with~$k$ given by the formula of the statement.
 At step~$t$, we insert a new pipe~$\pi(t)$ which enters at~$\pi(t)$ and exits at~$\omega^{-1}(\pi(t))$.
@@
 Hence, the free southeast elbows in~$R$ after step~$t$ form the sequence~$e_1, \dots, e_i, e'_1, \dots, e'_\ell, e_j, \dots, e_k$.
-We thus just need to see that
-\begin{itemize}
-\item $e_i$ is southwest of~$e'_1$ and~$e'_\ell$ is southwest of~$e_j$,
-\item $\ell = j-i$ if~$\pi(s) < \pi(t)$ and~$\omega^{-1}(\pi(s)) > \omega^{-1}(\pi(t))$, and $\ell = j-i-1$ otherwise.
-\end{itemize}
-This immediately follows considering the four possible cases:
-\begin{itemize}
-\item If~$\pi(t) < \pi(r)$ and~$\omega^{-1}(\pi(t)) < \omega^{-1}(\pi(r))$, then the pipe~$\pi(t)$ is completely contained in~$R$, hence it has one more northwest elbow than southeast elbow in~$R$.
-\item If~$\pi(s) < \pi(t)$ and~$\omega^{-1}(\pi(s)) > \omega^{-1}(\pi(t))$, then the pipe~$\pi(s)$ enters and exits~$R$ with an horizontal step, hence it has as many northwest and southeast elbows in~$R$.
-\item If~$\pi(s) > \pi(t)$ and~$\omega^{-1}(\pi(s)) < \omega^{-1}(\pi(t))$, then the pipe~$\pi(s)$ enters and exits~$R$ with a vertical step, hence it has as many northwest and southeast elbows in~$R$.
-\item If~$\pi(s) > \pi(t)$ and~$\omega^{-1}(\pi(s)) > \omega^{-1}(\pi(t))$, then setting~$i \eqdef \pi(t)$ and~$j \eqdef \pi(s)$, we have~${i < j}$ and~$\pi^{-1}(i) > \pi^{-1}(j)$ while~$\omega^{-1}(i) < \omega^{-1}(j)$, which contradicts our assumption that~$\pi < \omega$ in weak order.
+We thus just need to see that $e_i$ is southwest of~$e'_1$ and~$e'_\ell$ is southwest of~$e_j$, and that
+\[
+\ell = \begin{cases} j-i  & \text{if } \pi(s) \le r \text{ and } \omega^{-1}(\pi(s)) \le c, \\  j-i-2  & \text{if } \pi(s) > r \text{ and } \omega^{-1}(\pi(s)) > c, \\  j-i-1 & \text{otherwise.} \end{cases}
+\]
+Since the northwest and southeast elbows alternate along pipe~$\pi(t)$, this follows from the fact that the pipe~$\pi(t)$ enters~$R$ with an horizontal step if~$\pi(t) \le r$ and with a vertical step if~$\pi(s) > r$, and exits~$R$ with a vertical step if~$\omega^{-1}(\pi(t)) \le c$ and with an horizontal step if~$\omega^{-1}(\pi(s)) > c$.
+%setting~$i \eqdef \pi(t)$ and~$j \eqdef \pi(s)$, we have~${i < j}$ and~$\pi^{-1}(i) > \pi^{-1}(j)$ while~$\omega^{-1}(i) < \omega^{-1}(j)$, which contradicts our assumption that~$\pi < \omega$.
 \qedhere
-\end{itemize}
 \end{proof}
@@
 \begin{proof}
-%Fix~$t \in [n]$.
-Observe first that if there is~$s > t$ such that~$\pi(s) < \pi(t)$ and~$\omega^{-1}(\pi(s)) < \omega^{-1}(\pi(t))$, then setting~$i \eqdef \pi(s)$ and~$j \eqdef \pi(t)$, we have~$i < j$ and~$\pi^{-1}(i) > \pi^{-1}(j)$ while~$\omega^{-1}(i) < \omega^{-1}(j)$, which contradicts our assumption that~$\pi < \omega$ in weak order.
-Hence, we obtain that
-\[
-\noninversions{\omega}{\pi(t)} = \# \bigset{s < t}{\pi(s) < \pi(t) \text{ and } \omega^{-1}(\pi(s)) < \omega^{-1}(\pi(t))}.
-\]
-Hence, the result follows from~\cref{lem:rectangleInsertionAlgorithm} applied to~$t = r$.
+Observe first that if there if~$r < s$ such that~$\pi(r) > \pi(s)$ and~$\omega^{-1}(\pi(r)) > \omega^{-1}(\pi(s))$, then setting~$i \eqdef \pi(s)$ and~$j \eqdef \pi(r)$, we have~${i < j}$ and~$\pi^{-1}(i) > \pi^{-1}(j)$ while~$\omega^{-1}(i) < \omega^{-1}(j)$, which contradicts our assumption that~$\pi < \omega$.
+This implies that
+\begin{align*}
+\# \set{s < t}{\pi(s) < \pi(t) \text{ and } \omega^{-1}(\pi(s)) < \omega^{-1}(\pi(t))} & = \noninversions{\omega}{\pi(t)} \\
+\text{and}\qquad \# \set{s < t}{\pi(s) > \pi(t) \text{ and } \omega^{-1}(\pi(s)) > \omega^{-1}(\pi(t))} & = 0.
+\end{align*}
+Hence, the result follows from~\cref{lem:rectangleInsertionAlgorithm} applied to the parameters~$t, \pi(t), \omega^{-1}(\pi(t))$.
 \end{proof}
@@
 
-%\begin{corollary}
-%For any~$\pi \le \omega$, the insertion algorithm creates a pipe dream of~$\pipeDreams(\omega)$.
-%\end{corollary}
-
 \begin{proof}[Proof of \cref{prop:insertionAlgorithm}]
@@
 
-%\begin{proposition}
-%\label{prop:fibersInsertion}
-%For any pipe dream~$P \in \acyclicPipeDreams(\omega)$,  the permutations~$\pi \le \omega$ such that~$\insertion{\pi}{\omega} = P$ are precisely the linear extensions of the contact graph~$P\contact$ of~$P$.
-%In particular, $\insertion{\cdot}{\omega}$ is a surjection from~$[e, \omega]$ to~$\acyclicPipeDreams(\omega)$.
-%\end{proposition}
-%
-%\begin{proof}
-%By construction of the insertion algorithm, all southeast contacts of the pipe~$\pi(t)$ inserted at step~$t$ are in contact with northwest contacts of pipes~$\pi(s)$ inserted at steps~$s < t$.
-%In other words, all edges in the contact graph of~$\insertion{\pi}{\omega}$ are of the form~$\pi(s) \to \pi(t)$ for some~$s < t$.
-%It follows that the permutation~$\pi$ is a linear extension of~$\insertion{\pi}{\omega}$.
-%Reciprocally, consider a linear extension~$\pi$ of a pipe dream~$P$.
-%Then~$\insertion{\pi}{\omega}$ and~$P$ have a common linear extension~$\pi$, so that~$\insertion{\pi}{\omega} = P$ by \cref{prop:partition}.
-%\end{proof}
-%
-%In other words, the sets~$\set{\linearExtensions(P)}{P \in \acyclicPipeDreams(\omega)}$ are the fibers of the surjective insertion map~$\insertion{\cdot}{\omega}$.
-%Note that this concludes the proof of the surjectivity left open in \cref{prop:partition}.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\vincent{I am still working below this line.}
-
-Recall from \cref{exm:Tamari3} that the sylvester congruence can be defined as the transitive closure of the classical rewriting rule~$UikVjW \equiv UkiVjW$ for~$i < j < k$ (as usual, we write the permutations of~$\fS_n$ as words in one-line notation).
+Recall from \cref{exm:Tamari3} that the sylvester congruence can be defined as the transitive closure of the classical rewriting rule~$UjVikW \equiv UjVkiW$ where~$i < j < k$ are elements of~$[n]$ while~$U, V, W$ are (possibly empty) words on~$[n]$ (as usual, we write the permutations of~$\fS_n$ as words in one-line notation).
 We now describe a similar rewriting rule for the pipe dream congruence~$\equiv_\omega$.
@@
 \label{prop:rewritingRule}
-On the interval~$[e,\omega]$ of the weak order, the pipe dream congruence~$\equiv_\omega$ coincides with the transitive closure of the rewriting rule~$U ik V \equiv_\omega U ki V$ where~$i < k$ are elements of~$[n]$ while~$U, V$ are (possibly empty) words on~$[n]$ such that
-\[
-\#\set{j \in U}{i < j < k \text{ and } \omega^{-1}(i) > \omega^{-1}(j) > \omega^{-1}(k)} \ge \#\set{j \in U}{j < i \text{ and } \omega^{-1}(j) < \omega^{-1}(k)}.
-%\#\set{j \in U}{i < j < k \text{ and } \omega^{-1}(i) > \omega^{-1}(j) > \omega^{-1}(k)} \ge \#\set{j < i}{\omega^{-1}(j) < \omega^{-1}(k)},
-\]
-\vincent{Note that $b \in U$ on the right hand side by \cref{lem:interval}.}
-% The letters~$j \in U$ such that~$i < j < k$ while~$\omega^{-1}(i) > \omega^{-1}(j) > \omega^{-1}(k)$ are called \defn{pipe dream congruence witnesses} for the exchange of~$i$ and~$k$.
-%\vincent{Another option to write this is $d \ge u$ where $d \eqdef \set{b \in U}{b > a}$ and~$u \eqdef \set{b \in U}{\omega^{-1}(b) < \omega^{-1}(c)}$.
-%Or $dr \ge \ell u$ where $dr \eqdef \set{b \in U}{b > a \text{ and } \omega^{-1}(b) > \omega^{-1}(c)}$ and~$\ell u \eqdef \set{b \in U}{b < a \text{ and } \omega^{-1}(b) < \omega^{-1}(c)}$.}
+On the interval~$[e,\omega]$ of the weak order, the pipe dream congruence~$\equiv_\omega$ coincides with the transitive closure of the rewriting rule~$U ij V \equiv_\omega U ji V$ where~$1 \le i < j \le n$ are elements of~$[n]$ while~$U, V$ are (possibly empty) words on~$[n]$ such that
+\[
+\# \set{k \in U}{k > i} \ge \# \set{k \in U}{\omega^{-1}(k) < \omega^{-1}(j)}.
+\]
 \end{proposition}
 
-\begin{proposition}
-\label{prop:congruence}
-For any~$\pi, \pi' \in [e,\omega]$, we have~${\pi \equiv_\omega \pi' \!\iff\! \insertion{\pi}{\omega} = \insertion{\pi'}{\omega} \!\iff\! \pi}$~and~$\pi'$ are linear extensions of a same pipe dream.
-\end{proposition}
-
-\begin{proof}
-By \cref{prop:fibersInsertion}, each fiber of~$\insertion{\cdot}{\omega}$ gathers the linear extensions of a pipe dream of~$\pipeDreams(\omega)$.
-Since the set of linear extensions of a poset is connected by simple transpositions, we just need to show that~$\pi \equiv_\omega \pi' \!\iff\!
-\insertion{\pi}{\omega} = \insertion{\pi'}{\omega}$ for any two permutations~$\pi = UacV$ and~$\pi' = UcaV$ of~$[e,\omega]$ which differ by the inversion of two consecutive values.
-
-Let~$t = \pi^{-1}(a) = \pi'{-1}(c)$.
-At step~$t$ of the algorithm presented in the previous section, we have inserted the word~$U$.
-At that moment, let~$X_t$ (resp.~$X'_t$, resp~$Y_t$) denote the set of free northwest contacts in the rectangle~$[a] \times [\omega^{-1}(a)]$ (resp.~$[c] \times [\omega^{-1}(c)]$, resp.~$[a] \times [\omega^{-1}(c)]$).
-Applying the same argument as in \cref{lem:rectangleInsertionAlgorithm}, we have
-\begin{gather*}
-\# Y_t = \max\big( \#\set{b \in U}{b < a \text{ and } \omega^{-1}(b) < \omega^{-1}(c)} \hspace{5cm} \\ \hspace{5cm} - \; \#\set{b \in U}{a < b < c \text{ and } \omega^{-1}(a) > \omega^{-1}(b) > \omega^{-1}(c)}, 0\big).
-\end{gather*}
-It follows that~$U ac V \equiv_\omega U ca V \iff \# Y_t = 0$.
-However, $Y_t = 0$ if and only if all contacts of~$X_t$ are in~$[a] \times [\omega^{-1}(c), \omega^{-1}(a)]$ and all contacts of~$X'_t$ are in~$[a,c] \times [\omega^{-1}(c)]$.
-The latter is equivalent to the fact that the insertion of~$a$ and~$c$ commute.
-We conclude that
-\[
-U ac V \equiv_\omega U ca V \iff \insertion{UacV}{\omega} = \insertion{UcaV}{\omega},
-\]
-which concludes the proof since the set of linear extensions of a poset is connected by simple transpositions.
-\end{proof}
-
-\begin{proposition}
-\label{prop:patternAvoiding}
-The minimal (resp.~maximal) permutations in the partition
-\(
-{[e,\omega] = \bigsqcup_{P \in \acyclicPipeDreams(\omega)} \linearExtensions(P)}
-\)
-are the permutations avoiding the patterns~$b_1 - \cdots - b_k - ca$ (resp.~$b_1 - \cdots - b_k - ac$) where $k = \#\set{b < a}{\omega^{-1}(b) < \omega^{-1}(c)}$.
-\end{proposition}
-
-\begin{proof}
-This is an immediate consequence of \cref{prop:congruence}: a permutation~$\pi$ is minimal (resp.~maximal) in its $\equiv_\omega$-congruence class if and only if it contains no consecutive exchangeable entries~$ca$ (resp.~$ac$) with~$a < c$.
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Canopy}
-\label{sec:canopy}
-
+\begin{proof}
+As they are linear extensions of posets, the congruence classes of $\equiv_\omega$ are connected by simple transpositions.
+We thus just need to show that any two permutations~$\pi \eqdef UijV$ and~$\pi' \eqdef UjiV$ of~$[e, \omega]$ which differ by the inversion of two consecutive values are equivalent for~$\equiv_\omega$ if and only if~$\# \set{k \in U}{k > i} \ge \# \set{k \in U}{\omega^{-1}(k) < \omega^{-1}(j)}$.
+Moreover, by \cref{prop:insertionAlgorithm}, $\pi \equiv_\omega \pi'$ if and only if they are sent to the same pipe dream by the insertion algorithm.
+Let~$t \eqdef \pi^{-1}(i) = \pi'^{-1}(j)$.
+Before step~$t$ of the insertion algorithm, we insert the word~$U$ both for~$\pi$ and for~$\pi'$.
+The insertion of~$i$ and~$j$ then commute if and only if there is no currently free elbow in the rectangle~$[i] \times [\omega^{-1}(j)]$.
+By \cref{lem:rectangleInsertionAlgorithm} applied to the parameters~$t, i, \omega^{-1}(j)$, this is equivalent to
+\[
+\# \set{s < t}{\pi(s) \le i \text{ and } \omega^{-1}(\pi(s)) \le \omega^{-1}(j)} \le \# \set{s < t}{\pi(s) > i \text{ and } \omega^{-1}(\pi(s)) > \omega^{-1}(j)}.
+\]
+or written differently,
+\[
+\# \set{k \in U}{k < i \text{ and } \omega^{-1}(k) < \omega^{-1}(j)} \le \# \set{k \in U}{k > i \text{ and } \omega^{-1}(k) > \omega^{-1}(j)}.
+\]
+(note that  to replace large by strict inequalities in the first set, we used that~$k \ne i$ and ${\omega^{-1}(k) \ne \omega^{-1}(j)}$ since~$i,j \notin U$ while~$k \in U$).
+Finally, observe that adding~$\# \set{k \in U}{k > i \text{ and } \omega^{-1}(k) < \omega^{-1}(j)}$ from both side, we obtain the equivalent condition
+\[
+\# \set{k \in U}{\omega^{-1}(k) < \omega^{-1}(j)} \le \# \set{k \in U}{k > i}.
+\qedhere
+\]
+\end{proof}
+
+\begin{remark}
+\label{rem:rewritingRule}
+Observe from the proof that the condition of \cref{prop:rewritingRule} is equivalent to
+\[
+\# \set{k \in U}{k < i \text{ and } \omega^{-1}(k) < \omega^{-1}(j)} \le \# \set{k \in U}{k > i \text{ and } \omega^{-1}(k) > \omega^{-1}(j)}.
+\]
+Observe moreover that since~$\pi \le \omega$ and~$i < j$, we have
+\begin{align*}
+\set{k \in U}{k < i \text{ and } \omega^{-1}(k) < \omega^{-1}(j)} & = \set{k \in [i]}{\omega^{-1}(k) < \omega^{-1}(j)} \qquad \text{and}\\
+\set{k \in U}{k > i \text{ and } \omega^{-1}(k) > \omega^{-1}(j)} & = \set{k \in [n]}{i < k < j \text{ and } \omega^{-1}(i) > \omega^{-1}(k) > \omega^{-1}(j)}.
+\end{align*}
+\end{remark}
+
+We close this section by two immediate consequences of \cref{prop:rewritingRule,rem:rewritingRule}.
+
+\begin{corollary}
+\label{coro:patternAvoiding}
+A permutation is minimal (resp.~maximal) in its pipe dream congruence class if and only if it avoids the patters~$k_1 - \cdots - k_p - ji$ (resp.~$k_1 - \cdots - k_p - ij$) where~$k_q > i$ and~$\omega^{-1}(k_q) > \omega^{-1}(j)$ for~$q \in [p]$ and~$p = \# \set{k \in [i]}{\omega^{-1}(k) < \omega^{-1}(j)}$.
+\end{corollary}
+
+\begin{proof}
+This is an immediate consequence of \cref{prop:rewritingRule}: a permutation~$\pi$ is minimal (resp.~maximal) in its $\equiv_\omega$-congruence class if and only if it contains no consecutive exchangeable entries~$ji$ (resp.~$ij$) with~$i < j$.
+\end{proof}
+
+\begin{corollary}
+\label{coro:canopy}
+If~$1 \le i < j \le n$ and~$j-i \le \#\set{k \in [i]}{\omega^{-1}(k) < \omega^{-1}(j)}$, then the pipes~$i$ and~$j$ are comparable for $\contactLess{P}$ in any acyclic pipe dream~$P \in \acyclicPipeDreams(\omega)$.
+\end{corollary}
+
+\begin{proof}
+If pipes~$i$ and~$j$ were incomparable in~$\contactLess{P}$, there would be two permutations~$UijV \equiv_\omega UjiV$.
+However, $j-i \le \#\set{k \in [i]}{\omega^{-1}(k) < \omega^{-1}(j)}$ implies that the condition of \cref{prop:rewritingRule} cannot hold, by \cref{rem:rewritingRule}
+\end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Recoils and canopy}
+\label{subsec:canopy}
+
+To conclude, we generalize the notion of recoils of permutations and of canopy of a binary trees to show a natural commutative diagram of lattice homomorphisms.
+We start with the easy generalization of recoils of a permutation.
+
+\begin{definition}
+\label{def:recoils}
+Consider the graph~$G(\omega)$ with vertex set~$[n]$ and edge set
+\[
+\set{ik}{i < j \text{ and } j-i \le \#\set{k \in [i]}{\omega^{-1}(k) < \omega^{-1}(j)}}.
+\]
+Let~$\acyclicOrientations(\omega)$ denote the set of acyclic orientations of~$G(\omega)$.
+The \defn{$\omega$-recoil congruence} is the equivalence relation on the weak order interval~$[e, \omega]$ whose equivalence classes are the sets of linear extensions of the acyclic orientations of~$G(\omega)$.
+The \defn{$\omega$-recoils} of a permutation~$\pi \in [e,\omega]$ is the acyclic orientation~${\recoils{\pi}{\omega} \in \acyclicOrientations(\omega)}$ such that~$\pi$ is a linear extension of~$\recoils{\pi}{\omega}$.
+\end{definition}
+
+We now generalize the canopy of a binary tree.
 Recall that the \defn{canopy} of a binary tree~$T$ with~$n$ internal nodes is the sign sequence~${\canopy{T} \in \{{-},{+}\}^{n-1}}$ defined by~$\canopy{T}_i = {-}$ if the $(i+1)$st leaf of~$T$ is a left leaf and~$\canopy{T}_i = {+}$ if the $(i+1)$st leaf of~$T$ is a right leaf.
@@
 This map was already used by J.-L.~Loday in~\cite{LodayRonco, Loday}, but the name ``canopy'' was coined by X.~Viennot~\cite{Viennot}.
-% The binary search tree insertion map and the canopy map factorize the recoil map: $\surjectionBrickZono[] \circ \surjectionPermBrick[] = \surjectionPermZono[]$.
-This combinatorial fact can also be understood on the geometry of the normal fans of the permutahedron, the associahedron and the cube, see \cref{subsec:normalFans}.
-
-Before introducing the canopy, let us define the $\omega$-recoils.
-For this, consider the graph~$G(\omega)$ with vertex set~$[n]$ and edge set
-\[
-\bigset{ij}{i < j \text{ and } j-i \le \#\set{k < i}{\omega^{-1}(k) < \omega^{-1}(j)}}.
-\]
-Let~$\acyclicOrientations(\omega)$ denote the set of acyclic orientations of~$G(\omega)$.
-
-\begin{definition}
-The \defn{$\omega$-recoil scheme} of a permutation~$\pi \in [e,\omega]$ is the orientation~${\recoils{\pi}{\omega} \in \acyclicOrientations(\omega)}$ where for all~$i < j \in [n]$ such that~$j-i \le \#\set{k < i}{\omega^{-1}(k) < \omega^{-1}(j)}$, the edge~$ij$ is oriented~$i \to j$ if~$\pi^{-1}(i) < \pi^{-1}(j)$ and~$j \to i$ if~$\pi^{-1}(j) < \pi^{-1}(i)$.
-We call \defn{$\omega$-recoil map} the map~$\recoils{\cdot}{\omega} : [e,\omega] \to \acyclicOrientations(\omega)$.
-\end{definition}
-
-\begin{remark}
-The fiber of an acyclic orientation~$O \in \acyclicOrientations(\omega)$ under the $\omega$-recoil map~$\recoils{\cdot}{\omega}$ are the linear extensions of~$O$ in~$[e,\omega]$.
-\end{remark}
-
-We now define a generalization of the canopy map for pipe dreams in~$\acyclicPipeDreams(\omega)$.
-To ensure that \cref{def:canopy} is valid, we need the following simple observation on comparisons of ``close'' pipes in a pipe dream.
-
-\begin{lemma}
-\label{lem:canopy}
-If~$i < j$ satisfy~$j-i \le \#\set{k < i}{\omega^{-1}(k) < \omega^{-1}(j)}$, then the pipes~$i$ and~$j$ in any acyclic pipe dream~$P \in \acyclicPipeDreams(\omega)$ are comparable~for~$\contactLess{P}$.
-\end{lemma}
-
-\begin{proof}
-If pipes~$i$ and~$j$ were incomparable in~$\contactLess{P}$, there would be two $\equiv_\omega$-congruent permutations~$UijV \equiv_\omega UjiV$.
-However, the assumption contradicts the definition of the $\equiv_\omega$-conguence in \cref{def:congruence}.
-\end{proof}
+We now define a generalization of the canopy map for pipe dreams in~$\acyclicPipeDreams(\omega)$, using \cref{coro:canopy}.
 
@@
 \label{def:canopy}
-The \defn{canopy} of a pipe dream~$P \in \acyclicPipeDreams(\omega)$ is the orientation~$\canopy{P} \in \acyclicOrientations(\omega)$ where for all~$i < j \in [n]$ such that~$j-i \le \#\set{k < i}{\omega^{-1}(k) < \omega^{-1}(j)}$, the edge~$ij$ is oriented~$i \to j$ if~$i \contactLess{P} j$ and~$j \to i$ if~$j \contactLess{P} i$.
-It indeed defines an acyclic orientation of~$G(\omega)$ by \cref{lem:canopy}.
-We call \defn{canopy} the map~$\canopy{\cdot}: \acyclicPipeDreams(\omega) \to \acyclicOrientations(\omega)$.
+The \defn{canopy} of a pipe dream~$P \in \acyclicPipeDreams(\omega)$ is the orientation~$\canopy{P} \in \acyclicOrientations(\omega)$ where each edge~$ij$ is oriented~$i \to j$ if~$i \contactLess{P} j$ and~$j \to i$ if~$j \contactLess{P} i$.
 \end{definition}
@@
 \end{proof}
-
-\vincent{I want to think about congruences of the interval $[e,\omega]$ in general.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Future work}
-\label{sec:futureWork}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Sortability and alignement}
-
-We should describe the minimum (or maximum) of the congruence classes of~$\equiv_\omega$ by
-\begin{itemize}
-\item a pattern avoiding condition, see \cref{prop:patternAvoiding}.
-\item ``$\omega$-sortability'', see~\cite{Reading-sortableElements}.
-\item ``$\omega$-alignement'', see~\cite{Reading-sortableElements}.
-\end{itemize}
-
-\subsection{Other Coxeter groups}
-
-\vincent{This part is not up-to-date.  We have new (hopefully correct) conjectures.}
-All the arguments presented above should extend to type A Cambrian pipe dreams...
-This means that we consider the increasing flip poset of the type~$A$ subword complex~$\subwordComplex(\wo(c),\omega)$ for any Coxeter element~$c$ and any permutation~$\omega$ of~$\fS_n$.
-Similar arguments where already developed in~\cite{Pilaud-BrickAlgebra} for the particular case of the permutation
-\[
-\omega = [1, \dots, k, n-k, n-k-1, \dots, k+2, k+1, n-k+1, \dots, n].
-\]
-More generally, we can consider the following conjecture.
-
-\begin{conjecture}
-\label{conj:Coxeter}
-For any finite Coxeter group~$W$, any Coxeter element~$c$ of~$W$, and any element~$w \in W$, the increasing flip poset on the acyclic facets of the subword complex~$\subwordComplex(\wo(c),w)$ is a lattice quotient of the interval~$[e,w]$ of the weak order on~$W$.
-\end{conjecture}
-
-Let's be a little more precise here: for an acyclic facet~$F$ of the subword complex~$\subwordComplex(\wo(c),w)$, one can consider the set~$\set{\pi \in W}{\R_{\ge 0} \pi(\Delta) \supseteq \R_{\ge 0} \Roots(F)}$, \ie the elements of~$W$ whose dual Coxeter chamber belongs to the cone generated by the root configuration of~$F$.
-I hope that this defines a lattice congruence of~$[e,w]$.
-
-We should actually consider the lattice properties of the acyclic facets of~$\subwordComplex(c^k\wo(c),w)$ for any~$k$ and any~$w$.
-In type~$A$, this is the same as any subword complex~$\subwordComplex(c^k\wo(c),w)$ can be embedded in a bigger~$\subwordComplex(\wo(c'),w')$.
-In other types however it is a more general question.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Hopf algebra}
-
-Define an equivalence relation~$\equiv$ on intervals~$[\pi,\omega]$ of the weak order by~$[\pi,\omega] \equiv [\pi',\omega'] \iff \omega = \omega' \text{ and } \pi \equiv_\omega \pi'$.
-Essentially, we proved that the collection of all acyclic pipe dreams is in bijection with the equivalence classes of~$\equiv$.
-Now is there a Hopf algebra on intervals of the weak order such that the equivalence relation~$\equiv$ gives a subalgebra?
-\vincent{I believe that this part should disappear.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Subword complexes}
-\label{subsec:subwordComplexes}
-
-Pipe dreams are a very particular family of the family of subword complexes.
-Consider a Coxeter system~$(W,S)$, where~$W$ is a finite Coxeter group and~$S$ is the set of simple reflections of~$W$.
-We denote by~$e$ (resp.~$\wo$) the identity (resp.~longest element) of~$W$.
-Let~$Q \eqdef q_1 \dots q_m \in S^*$ be a word on the alphabet formed by the simple generators of~$W$ and~$w \in W$.
-The \defn{subword complex}~$\subwordComplex(Q,w)$ is the simplicial complex whose ground set~$[m]$ are the positions in~$Q$ and whose facets are the complements of the reduced expressions for~$w$ in~$Q$.
-
-It is known that~$\subwordComplex(Q,w)$ is either a ball or a sphere, in particular it is a pseudomanifold (with or without boundary).
-The flip graph of~$\subwordComplex(Q,w)$ is the graph whose vertices are the facets of~$\subwordComplex(Q,w)$ and whose edges are the ridges of~$\subwordComplex(Q,w)$.
-If~$F,F'$ are two adjacent facets with~$F \ssm \{p\} = F' \ssm \{p'\}$, we say that the flip is \defn{increasing} when~$p < p'$.
-The increasing flip graph was studied in particular in~\cite{PilaudStump-ELlabelings}.
-It is known to be acyclic, and its transitive closure is an EL-shellable poset (see~\cite{PilaudStump-ELlabelings} for the precise definition and references).
-
-There is also a notion of acyclicity for subword complexes.
-It is based on the notion of \defn{root configuration}~$\Roots(F)$ of a facet~$F$ of~$\subwordComplex(Q,w)$.
-We skip the details and refer to~\cite{CeballosLabbeStump, PilaudStump-brickPolytope} for details.
-The facet~$F$ is \defn{acyclic} if its root configuration is pointed (meaning that it generates a pointed cone).
-
-\begin{example}
-Consider the symmetric group~$\fS_{n+1}$ generated by the set of simple transpositions $\set{\tau_i}{i \in [n]}$ where~$\tau_i \eqdef (i \; i+1)$.
-For a permutation~$\omega \in \fS_{n+1}$, the pipe dreams of~$\pipeDreams(\omega)$ correspond to the facets of the subword complex~$\subwordComplex(Q,\omega)$ with~$Q = \tau_1, \tau_2, \dots, \tau_n, \tau_1, \tau_2, \dots, \tau_{n-1}, \dots, \tau_1, \tau_2, \tau_1$.
-% The notions of flips, increasing flips and acyclic pipe dreams transpose in the world of subword complexes.
-\end{example}
-
-\begin{example}
-For any Coxeter group~$W$ and any Coxeter element~$c \in W$ (a product of all generators of~$S$ in a given arbitrary order), let~$\wo(c)$ denote the $c$-sorting word of~$\wo$ (see \cite{Reading-CambrianLattices} for details).
-Extending the observation of \cref{subsec:reversingPipeDreams}, it was shown in~\cite{CeballosLabbeStump} that the subword complex~$\subwordComplex(c\wo(c), \wo)$ is isomorphic to the cluster complex of type~$W$.
-In particular, the increasing flip graph is the Hasse diagram of the $c$-Cambrian lattice of~\cite{Reading-CambrianLattices}.
-\end{example}
-
-In contrast to the previous example, consider the word~$Q = \tau_1 \tau_2 \tau_3 \tau_2 \tau_1 \tau_2 \tau_3 \tau_2 \tau_1$ on the simple generators of the symmetric group~$\fS_4$ and the subword complex~$\subwordComplex(Q,\wo)$.
-Note that all facets in this subword complex are acyclic.
-It is shown in~\cite[Rem.~5.12]{PilaudStump-brickPolytope} that its increasing flip poset is not a lattice.
-This shows that neither the increasing flip poset, nor the acyclic increasing flip poset are lattices in general, even in type~$A$.
-In this note, we investigate the case of acyclic pipe~dreams.
 

### 2023-01-11 acyclicFacets/draft/latticePipeDreams.tex
a basic introduction

@@
 % theorems
+\newtheorem*{theorem*}{Theorem}
 \newtheorem{theorem}{Theorem}[section]
@@
 \begin{abstract}
-We show that for any permutation~$\omega$, the increasing flip graph on acyclic pipe dreams with permutation~$\omega$ is a lattice quotient of the interval~$[e,\omega]$ of the weak order.
+We show that for any permutation~$\omega$, the increasing flip graph on acyclic pipe dreams with exiting permutation~$\omega$ is a lattice quotient of the interval~$[e,\omega]$ of the weak order.
 We then discuss conjectural generalizations of this result to acyclic facets of subword complexes on arbitrary finite Coxeter groups.
@@
 
+\vspace*{.2cm}
 \maketitle
@@
 
-The purpose of this note is to show that for any permutation~$\omega$, the increasing flip graph on acyclic pipe dreams with permutation~$\omega$ is a lattice quotient of the interval~$[e,\omega]$ of the weak order.
-It motivates \cref{conj:Coxeter} which is the long-term perspective of this work.
-The approach and proofs developed here are direct adaptations from~\cite[Sect.~1]{Pilaud-BrickAlgebra}.
-\vincent{Include an introduction}
-\vincent{cite \cite{BergeronBilley,KnutsonMiller-subwordComplex}}
-
-The \defn{weak order} on the permutations of~$[n]$ is defined as the inclusion order of inversion sets, where an inversion of a permutation~$\pi$ is a pair of values~$i, j \in [n]$ such that~$i < j$ while~${\pi^{-1}(i) > \pi^{-1}(j)}$.
-The cover relations in the weak order correspond to switching pairs of consecutive values in permutations.
-The weak order is known to be a lattice \cite{GuilbaudRosenstiehl,Bjorner}.
-For two permutations~$\sigma < \tau$, we denote by~$[\sigma, \tau]$ the weak order interval between~$\sigma$ and~$\tau$, which is again a lattice.
+The weak order is the lattice on permutations of~$[n]$ whose cover relations correspond to switching pairs of consecutive values in permutations.
+The Tamari lattice is the lattice on binary trees with~$n$ internal nodes whose cover relations correspond to right rotations in binary trees.
+The Tamari lattice is known to be the lattice quotient of the weak order by the sylvester congruence, defined as the equivalence relation on permutations of~$[n]$ whose equivalence classes are the sets of linear extensions of binary trees (labeled in inorder and oriented towards their leaves).
+
+This paper develops a similar framework for acyclic pipe dreams.
+Pipe dreams were introduced by N.~Bergeron and S.~Billey in~\cite{BergeronBilley} to compute Schubert polynomials and later revisited in the context of Gr\"obner geometry by A.~Knutson and E.~Miller~\cite{KnutsonMiller-GroebnerGeometry}, who coined the name \emph{pipe dreams}.
+They have important connections and applications to various areas related to Schubert calculus and Schubert varieties~\cite{LascouxSchutzenberger-PolynomesSchubert, LascouxSchutzenberger-SchubertLittlewoudRichardson}.
+A pipe dream is an arrangement of pipes in the triangular shape, each entering along the vertical side and exiting along the horizontal side.
+They are grouped according to their exiting permutation, given by the order in which the pipes appear along the horizontal axis.
+The pipes in a pipe dream have some crossings and some contacts, and the contact graph records all contacts of a pipe dream.
+A flip in a pipe dream exchanges a contact between with a crossing between two pipes, and the flip is increasing when the contact is southeast of the crossing involved in the flip.
+The acyclic pipe dreams are the pipe dreams with an acyclic contact graph, and they naturally appear in the study of brick polytopes~\cite{PilaudSantos-brickPolytope}.
+A brief recollection on pipe dreams is given in \cref{sec:preliminaries}.
+
+In the core \cref{sec:latticeAcyclicPipeDreams} of this paper, we show that for any permutation~$\omega$,
+\begin{itemize}
+\item the sets of linear extensions of the acyclic pipe dreams with exiting permutation~$\omega$ form a partition of the interval~$[e,\omega]$ of the weak order (\cref{subsec:linearExtensions}),
+\item the equivalence relation defined by this partition is a lattice congruence of~$[e, \omega]$, that we call the pipe dream congruence (\cref{subsec:pipeDreamCongruence}),
+\item the Hasse diagram of the corresponding lattice quotient is the increasing flip graph on acyclic pipe dreams with exiting permutation~$\omega$ (\cref{subsec:pipeDreamQuotient}).
+\end{itemize}
+In summary, we obtain the following statement.
+
+\begin{theorem*}
+For any permutation~$\omega$, the increasing flip graph on acyclic pipe dreams with exiting permutation~$\omega$ is the Hasse diagram of the lattice quotient of the interval~$[e,\omega]$ of the weak order by the pipe dream congruence of~$\omega$.
+\end{theorem*}
+
+Note that we recover the connection between the weak order and the Tamari lattice by the sylvester congruence for a well-chosen exiting permutation~$\omega$.
+
+We then explore in \cref{sec:furtherTopics} some natural further topics.
+We describe two algorithms to compute the unique acyclic pipe dream whose linear extensions contain a given permutation generalizing the binary tree insertion map on permutations (\cref{subsec:sweepingAlgorithm,subsec:insertionAlgorithm}), we describe the pipe dream congruence as the transitive closure of a local rewriting rule generalizing that of the sylvester congruence (\cref{subsec:rewritingRule}), and we describe a natural commutative diagram of lattice morphism generalizing the connection between the recoil map and the binary tree insertion map on permutations and the canopy on binary trees (\cref{subsec:canopy}).
+
+Finally, we discuss in \cref{sec:subwordComplexes} a conjectural extension of our results to subword complexes in finite Coxeter groups~\cite{KnutsonMiller-subwordComplex}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \subsection{Pipe dream quotient}
-\label{subsec:}
+\label{subsec:pipeDreamQuotient}
 
@@
 \section{Subword complexes}
-
-The objective of this section is to partially extend the results about the lattice structure of acyclic pipe dreams, presented in \cref{sec:latticeAcyclicPipeDreams}, to the wider context of subword complexes of finite type.
+\label{sec:subwordComplexes}
+
+The objective of this section is to partially extend the results about the lattice structure of acyclic pipe dreams, presented in \cref{sec:latticeAcyclicPipeDreams}, to the wider context of subword complexes in finite Coxeter groups.
 Before doing so, we recall some preliminaries about finite Coxeter groups and subword complexes.
@@
 
-Two facets $I,J\in\subwordComplex(Q,w)$ are said to be connected by a \defn{flip} if they differ one element:
+Two facets $I,J \in \subwordFacets(Q,w)$ are said to be connected by a \defn{flip} if they differ one element:
 \[J=I\smallsetminus \{i\} \cup\{j\}\]

### 2023-01-18 acyclicFacets/draft/latticePipeDreams.tex
minor modifs
modifications subword complexes

@@
-\documentclass{amsart}
+\documentclass[reqno]{amsart}
 
@@
 \newcommand{\fS}{\mathfrak{S}} % symmetric group
-\newcommand{\gdproduct}{\bullet} % global descent product
-\newcommand{\gdshuffle}{\shuffle_\gdproduct} % global descent shuffle product
-\newcommand{\gddeconcat}{\coproduct_\gdproduct} % global descent deconcatenation coproduct
-\newcommand{\HS}{{\bk\fS}} % Hopf Algebra of permutations
-\newcommand{\shiftedShuffle}{\,\bar\shuffle\,} % shifted shuffle
-\newcommand{\convolution}{\star} % convolution
+\newcommand{\fR}{\mathfrak{R}} % subset symmetric group
 
@@
 \newcommand{\pipeDreams}{\Pi} % set of pipe dreams
-\newcommand{\HP}{{\bk\pipeDreams}} % Hopf Algebra of pipe dreams
 \newcommand{\reversingPipeDreams}{\Omega} % reversing pipe dreams
@@
 % Subword complexes
-\newcommand{\wo}{w_\circ} % longest element
+\newcommand{\wo}{\omega_\circ} % longest element
 \newcommand{\subwordComplex}{\mathcal{SC}} % subword complex
@@
 \newcommand{\subwordFacets}{\mathcal{F}} % subword complex
-\newcommand{\subwordAcyclicFacets}{\mathcal{F}^{ac}} % subword complex
+\newcommand{\subwordAcyclicFacets}{\mathcal{F}^\mathrm{ac}} % subword complex
 \newcommand{\greedyFacet}{I^{\overleftarrow{gr}}} % greedy facet
 \newcommand{\antiGreedyFacet}{I^{\overrightarrow{gr}}} % antigreedy facet
-\newcommand{\sweepingAlgorithm}{\mathrm{sweep}} % sweeping algorithm
+\newcommand{\sweepingAlgorithm}{\mathsf{sweep}} % sweeping algorithm
 
@@
 Finally, we discuss in \cref{sec:subwordComplexes} a conjectural extension of our results to subword complexes in finite Coxeter groups~\cite{KnutsonMiller-subwordComplex}.
+
+\begin{conjecture}
+For any sorting and alternating word~$Q$ and any~$\omega \in W$, the
+
+the subword complex congruence~$\equiv_{Q,\omega}$ is a lattice congruence of the interval~$[e,\omega]$ of the weak order.
+\end{conjecture}
 
@@
 
-As already mentioned, the increasing flip poset on reversing pipe dreams is isomorphic to the Tamari lattice, which is a well known lattice quotient of the weak order.
-In this section, we extend this result to any permutation~$\omega$, by proving that the transitive closure of the increasing flip graph on acyclic pipe dreams of~$\acyclicPipeDreams(\omega)$ is the Hasse diagram of a lattice quotient of the weak order interval~$[e,\omega]$.
+As already mentioned, the increasing flip poset on reversing pipe dreams is isomorphic to the Tamari lattice, which is a lattice quotient of the weak order.
+In this section, we extend this result to any permutation~$\omega$ by showing that the sets of linear extensions of pipe dreams of~$\acyclicPipeDreams(\omega)$ partition the interval~$[e,w]$ (\cref{subsec:linearExtensions}), that this partition actually defines a lattice congruence of the weak order on~$[e,w]$ (\cref{subsec:pipeDreamCongruence}), and that the Hasse diagram of the quotient by this congruence is the increasing flip graph on acyclic pipe dreams of~$\acyclicPipeDreams(\omega)$ (\cref{subsec:pipeDreamQuotient}).
 This section goes straight to the proof of this property, and leaves alternative perspectives on this quotient to \cref{sec:furtherTopics}.
@@
 \label{subsec:linearExtensions}
+
+The main characters in this section are the following sets of permutations.
 
@@
 %In other words, $\pi \in \linearExtensions(P)$ if and only if~$\pi^{-1}(i) < \pi^{-1}(j)$ for all arcs~$i \to j$ in~$P\contact$.
+
+\begin{definition}
+\label{def:linearExtensions}
 We say that a permutation~$\pi$ is a \defn{linear extension} of a pipe dream~$P \in \pipeDreams(\omega)$ if~$\pi^{-1}(i) < \pi^{-1}(j)$ for every arc~$i \to j$ in~$P\contact$ (we should say linear extension of~$\contactLess{P}$, but prefer to simplify notation).
@@
 %For a pipe dream~$P \in \pipeDreams(\omega)$, we denote by~$\linearExtensions(P)$ the set of \defn{linear extensions} of~$P$, \ie the permutations~$\pi$ of~$[n]$ such that~$\pi^{-1}(i) < \pi^{-1}(j)$ for every arc~$i \to j$ in~$P\contact$.
+\end{definition}
+
 In this section, we prove the following structural property of~$\linearExtensions(P)$.
@@
 
-We will see in \cref{sec:furtherTopics} insertion algorithms to compute the pipe dream~$P \in \acyclicPipeDreams(\omega)$ of which a given permutation~$\pi \in [e,\omega]$ is a linear extension, for any permutation~$\omega$.
+We will see in \cref{sec:furtherTopics} insertion algorithms to compute the pipe dream~$P \in \acyclicPipeDreams(\omega)$ such that~$\pi \in \linearExtensions(P)$ for given permutations~$\pi < \omega$.
 These algorithms are however not needed for the proof of \cref{thm:partitionPipeDreams}, which we break into the following three lemmas.
@@
 
-We call \defn{pipe dream congruence} the equivalence relation~$\equiv_\omega$ on the weak order interval~$[e,\omega]$ whose equivalence classes are the sets of linear extensions of the pipe dreams of~$\acyclicPipeDreams(\omega)$.
+We now focus on the following congruence.
+
+\begin{definition}
+\label{def:pipeDreamCongruence}
+The \defn{pipe dream congruence} is the equivalence relation~$\equiv_\omega$ on the weak order interval~$[e,\omega]$ whose equivalence classes are the sets~$\linearExtensions(P)$ of linear extensions of the pipe dreams~$P$ of~$\acyclicPipeDreams(\omega)$.
 In other words, $\pi \equiv_\omega \pi'$ if and only if~$\insertion{\pi}{\omega} = \insertion{\pi'}{\omega}$.
-This indeed defines an equivalence relation by \cref{thm:partitionPipeDreams}.
-In this section, we prove the following statement.
+\end{definition}
+
+Note that the pipe dream congruence indeed defines an equivalence relation by \cref{thm:partitionPipeDreams}.
+In this section, we prove that it is a lattice congruence.
 
@@
 In this section, we discuss four further topics on the pipe dream congruence.
-In \cref{subsec:sweepingAlgorithm,subsec:insertionAlgorithm}, we describe two algorithms to construct the pipe dream~$\insertion{\pi}{\omega}$ of~$\acyclicPipeDreams(\omega)$ of which a given permutation~$\pi$ is a linear extension.
-In \cref{subsec:rewritingRule}, we describe the pipe dream congruence~$\equiv_\omega$ as the transitive closure of a rewriting rule on permutations of~$[e, \omega]$.
-Finally, in \cref{subsec:canopy}, we describe the natural coarsening of the pipe dream congruence~$\equiv_\omega$ by the recoil congruence~$\cong_\omega$.
+We first describe two algorithms to construct the pipe dream~$\insertion{\pi}{\omega}$ of~$\acyclicPipeDreams(\omega)$ of which a given permutation~$\pi$ is a linear extension (\cref{subsec:sweepingAlgorithm,subsec:insertionAlgorithm}).
+We then describe the pipe dream congruence~$\equiv_\omega$ as the transitive closure of a rewriting rule on permutations of~$[e, \omega]$ (\cref{subsec:rewritingRule}).
+Finally, we describe the natural coarsening of the pipe dream congruence~$\equiv_\omega$ by the recoil congruence~$\cong_\omega$ (\cref{subsec:canopy}).
 
@@
 See \cref{fig:sweepingAlgorithm}.
-%
-\begin{figure}
-	\centerline{\includegraphics[scale=.9]{sweeping}}
-	\caption{Sweeping algorithm for the permutations~$\pi = 513264$ and~$\omega = 561324$.} % See details in \cref{exm:sweepingAlgorithm}.}
-	\label{fig:sweepingAlgorithm}
-\end{figure}
 \end{proposition}
@@
 We place crossings in steps $2$ to $9$ since~$i < j$, $\omega^{-1}(i) > \omega^{-1}(j)$ and we are in the column~$\omega^{-1}(j)$, and in step $11$ since~$i < j$, $\omega^{-1}(i) > \omega^{-1}(j)$ and~$\pi^{-1}(i) > \pi^{-1}(j)$.
+%
+\begin{figure}[h]
+	\centerline{\includegraphics[scale=.9]{sweeping}}
+	\caption{Sweeping algorithm for the permutations~$\pi = 513264$ and~$\omega = 561324$.} % See details in \cref{exm:sweepingAlgorithm}.}
+	\label{fig:sweepingAlgorithm}
+\end{figure}
 \end{example}
@@
 See \cref{fig:insertionAlgorithm}.
-
-\begin{figure}
+\end{proposition}
+
+\begin{example}
+\label{exm:insertionAlgorithm}
+\cref{fig:insertionAlgorithm} illustrates the insertion algorithm for the permutations~${\pi = 513264}$ and~${\omega = 561324}$.
+For instance, when inserting the (green) pipe~$4$ in the last step, the currently free southeast elbows are the first southeast elbow of the (blue) pipe~$3$ and the two southeast elbows of the (purple) pipe~$2$.
+%
+\begin{figure}[t]
 	\centerline{\includegraphics[scale=.9]{insertion}}
@@
 \end{figure}
-\end{proposition}
-
-\begin{example}
-\label{exm:insertionAlgorithm}
-\cref{fig:insertionAlgorithm} illustrates the insertion algorithm for the permutations~${\pi = 513264}$ and~${\omega = 561324}$.
-For instance, when inserting the (green) pipe~$4$ in the last step, the currently free southeast elbows are the first southeast elbow of the (blue) pipe~$3$ and the two southeast elbows of the (purple) pipe~$2$.
 \end{example}
@@
 
-\newpage
 \section{Subword complexes}
@@
 
-The objective of this section is to partially extend the results about the lattice structure of acyclic pipe dreams, presented in \cref{sec:latticeAcyclicPipeDreams}, to the wider context of subword complexes in finite Coxeter groups.
-Before doing so, we recall some preliminaries about finite Coxeter groups and subword complexes.
-We refer to~\cite{BjornerBrenti, Humphreys} for more details on Coxeter groups.
+The objective of this section is to partially extend our results about the lattice structure of acyclic pipe dreams (\cref{sec:latticeAcyclicPipeDreams}) to the wider context of subword complexes in finite Coxeter groups.
+We start with some basic preliminaries on finite Coxeter groups (\cref{subsec:finiteCoxeterGroups}) and subword complexes (\cref{subsec:subwordComplexes}).
+We then define linear extensions of facets of subword complexes (\cref{subsec:linearExtensionsFacets}) and present two theorems (\cref{subsec:twoTheorems}) and two conjectures (\cref{subsec:twoConjectures}) about them.
+To conclude, we present a sweeping algorithm to construct the facet with a given linear extension (\cref{subsec:sweepingAlgorithmSubwordComplexes})
 
@@
 \subsection{Finite coxeter groups} 
-%a~\cesar{To do:\\
-%Coxeter groups of finite type, root systems, weak order, Bruhat order, inversions, non-inversions. 
-%}
-We consider a \defn{finite root system} $\Phi=\Phi^+\cup \Phi^-$ in an $n$-dimensional euclidian space $V$, with \defn{simple roots} $\Delta=\{\alpha_1,\dots,\alpha_n\} \subseteq \Phi^+$.
-The reflections along the hyperplanes orthogonal to the roots in $\Phi$ generate a finite Coxeter group $W$. 
-This group is generated by the simple transpositions $S=\{s_1,\dots ,s_n\}$, where $s_i$ is the reflection along the hyperplane orthogonal to the simple root $\alpha_i$.
-We also denote by $\alpha_s$ the simple root associated to $s\in S$.
-Throughout this paper, we only consider Coxeter groups which are finite.
-They are classified in terms of Dynkin diagrams, and arise from finite root systems, see~\cite{Humphreys}.
-
-Abstractly, the \defn{Coxeter group} $W$ is the group generated by a collection $S=\{s_1,\dots, s_n\}$ which satisfies the relations $(s_is_j)^{m_{ij}}=1$, where $m_{ii}=1$ and $m_{ij}\geq 2$ for~$i\neq j$.
-The pair $(W,S)$ is called a \defn{Coxeter system}.
-The \defn{length} $\ell(w)$ of an element $w\in W$ is the smallest~$\ell$ such that it can be written of the form $w=w_1w_2\dots w_\ell$ where $w_i\in S$.
-A \defn{reduced expression} of~$w$ is an expression of minimal length.
-We denote by $\wo$ the \defn{unique longest} element in $W$.
-
-For a finite Coxeter $W$ associated to a root system $\Phi$, the length $\ell(w)$ can be geometrically interpreted as the cardinality of the \defn{inversion set} $\Inv(w)$ of $w$, which is defined as
-\begin{align}\label{def_inversionset}
-\Inv(w) \eqdef \Phi^+ \cap w(\Phi^-).
-\end{align}
-Indeed, this set can be written as 
-\begin{align}\label{def_inversionset2}
-\Inv(w) \eqdef \{\alpha_{w_1}, w_1(\alpha_{w_2}),\dots , w_1w_2\dots w_{\ell-1}(\alpha_{w_\ell})\}
-\end{align}
-for any reduced expression $w=w_1w_2\dots w_\ell$ of $w$.
-
-The \defn{non-inversion set} $\Ninv (w)$ of $w$ is defined as
-\begin{align}
-\Ninv(w) & \eqdef \Phi^+ \cap w(\Phi^+) \label{def_noninversionset} \\
-& =\Inv(w\wo)
-\end{align}
-
-In particular, 
-\begin{align}
-\Phi^+=\Inv(w) \sqcup \Ninv (w).
-\end{align}
-
-The \defn{weak order} on $W$ is the partial order $\leq$ defined by $u \leq w$ if there exists $v \in W$ such that $uv = w$ and $\ell(u) + \ell(v) = \ell(w)$.
-In other words, the element $w$ has a reduced expression with a prefix which is a reduced expression of $u$.
-Equivalently, the weak order corresponds to the inclusion order on inversion sets, that is $u \leq w$ if and only if $\Inv(u) \subseteq \Inv(w)$.
-This order defines a lattice structure on the elements of W.
-The minimal element is the identity $e \in W$ and the maximal element is $\wo$.
+\label{subsec:finiteCoxeterGroups}
+
+We refer to~\cite{BjornerBrenti, Humphreys} for detailed references on Coxeter groups. 
+We consider a \defn{finite root system} $\Phi$ with \defn{positive roots}~$\Phi^+$, \defn{negative roots}~$\Phi^+-$, and \defn{simple roots} $\Delta \subseteq \Phi^+$.
+The reflections along the hyperplanes orthogonal to the roots in $\Phi$ generate a \defn{finite Coxeter group} $W$.
+We denote by~$s_\alpha \in W$ the reflection orthogonal to a root~$\alpha \in \Phi$, and by~$\alpha_s \in \Phi^+$ the positive root orthogonal to a reflection~$s \in W$.
+The group~$W$ is actually generated by the simple reflections~$S = \set{s_\alpha}{\alpha \in \Delta}$, and the pair~$(W,S)$ is a \defn{finite Coxeter system}.
+Finite root systems and finite Coxeter systems are classified in terms of Dynkin diagrams, see~\cite{Humphreys}.
+
+The \defn{inversion set}~$\Inv(\omega)$ and the \defn{non-inversion set}~$\Ninv(\omega)$ of an element~$\omega \in W$ are
+\[
+\Inv(\omega) \eqdef \Phi^+ \cap \omega(\Phi^-)
+\qquad\text{and}\qquad
+\Ninv(\omega) \eqdef \Phi^+ \cap \omega(\Phi^+).
+\]
+Note that
+\[
+\Phi^+ = \Inv(\omega) \sqcup \Ninv(\omega)
+\qquad\text{and}\qquad
+\omega(\Phi^+) = -\Inv(\omega) \sqcup \Ninv(\omega).
+\]
+
+A \defn{reduced expression} of~$\omega$ is a product~$s_1 s_2 \dots s_\ell = \omega$ of simple reflections~$s_i \in S$ such that~$\ell$ is minimal.
+This minimal~$\ell$ is the \defn{length} $\ell(\omega)$ of~$\omega$.
+The length of~$\omega$ coincides with the size of its inversion set~$\Inv(\omega)$ since $\Inv(\omega) \eqdef \{\alpha_{s_1}, s_1(\alpha_{s_2}), s_1s_2(\alpha_{s_3}), \dots, s_1s_2 \dots s_{\ell-1}(\alpha_{s_\ell})\}$.
+
+The \defn{weak order} on $W$ is the partial order $\le$ defined by $\sigma \leq \omega$ if there exists $\tau \in W$ such that $\sigma\tau = \omega$ and $\ell(\sigma) + \ell(\tau) = \ell(\omega)$.
+In other words, the element $\omega$ has a reduced expression with a prefix which is a reduced expression of $\sigma$.
+Equivalently, the weak order corresponds to the inclusion order on inversion sets, that is $\sigma \leq \omega$ if and only if $\Inv(\sigma) \subseteq \Inv(\omega)$.
+This order defines a lattice structure on the elements of~$W$.
+The minimal element is the identity $e \in W$ and the maximal element is the \defn{unique longest element} $\wo$ of~$W$.
+Note that~$\Inv(e) = \varnothing = \Ninv(\wo)$ and~$\Ninv(e) = \Phi^+ = \Inv(\wo)$, so that~$\ell(e) = 0$ while~$\ell(\wo) = |\Phi^+|$.
+% Note also that~$\Ninv(\omega) =\Inv(\omega\wo)$.
+
+\begin{example}
+\vincent{todo}
+Type A
+\end{example}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \subsection{Subword complexes}
-%~\cesar{To do:\\
-%subword complexes, flips, greedy facets, \sout{root function, root configuration, acyclic facets}. 
-%}
-
-Motivated by their study of Gröbner geometry of Schubert varieties~\cite{KnutsonMiller-GroebnerGeometry}, Knutson and Miller~\cite{KnutsonMiller-subwordComplex} introduced a remarkable family of simplicial complexes in the context of Coxeter groups.
-
-Let $(W,S)$ be a Coxeter system of finite type, $Q=(q_1,\dots,q_m)$ be a word in the generators $S$, and $w\in W$ be an element of the group.
+\label{subsec:subwordComplexes}
+
+Motivated by their study of Gröbner geometry of Schubert varieties~\cite{KnutsonMiller-GroebnerGeometry}, A.~Knutson and E.~Miller introduced in~\cite{KnutsonMiller-subwordComplex} the following remarkable family of simplicial complexes in the context of Coxeter groups.
+
+Let $(W,S)$ be a finite Coxeter system, $Q=(q_1,\dots,q_m)$ be a word in the simple reflections $S$, and $\omega \in W$ be an element of the group.
 For $J\subseteq [r]$, we denote by $Q_J$ the subword of~$Q$ consisting of the letters with positions in $J$.
-The \defn{subword complex} $\subwordComplex(Q,w)$ is the simplicial complex whose facets are subsets $I\subseteq [m]$ such that $Q_{[m]\setminus I}$ is a reduced expression for $w$.
-We denote the \defn{set of facets} of $\subwordComplex(Q,w)$ by $\subwordFacets(Q,w)$.
-
-Two facets $I,J \in \subwordFacets(Q,w)$ are said to be connected by a \defn{flip} if they differ one element:
-\[J=I\smallsetminus \{i\} \cup\{j\}\]
-for some $i\in I$ and $j\in J$ with $i\neq j$.
-If $i<j$, the flip from $I$ to $J$ is called an \defn{increasing flip}.
-
-The increasing flip graph on facets of the subword complex is an acyclic graph which has a unique source and a unique sink~\cite{Pilaud-greedyFlipTree, PilaudStump-ELlabelings}.
+The \defn{subword complex} $\subwordComplex(Q,\omega)$ is the simplicial complex whose facets are subsets $I\subseteq [m]$ such that $Q_{[m]\setminus I}$ is a reduced expression for $\omega$.
+We denote by $\subwordFacets(Q,\omega)$ the set of facets of $\subwordComplex(Q,\omega)$.
+
+Two facets $I,J \in \subwordFacets(Q,\omega)$ are connected by a \defn{flip} if they differ one element: $I \ssm \{i\} = J \ssm \{j\}$ for some $i\in I$ and $j\in J$ with $i \ne j$.
+The flip from $I$ to $J$ is called \defn{increasing} if~$i < j$, and \defn{decreasing} otherwise.
+The \defn{increasing flip graph} on the facets of the subword complex is an acyclic graph which has a unique source and a unique sink~\cite{Pilaud-greedyFlipTree, PilaudStump-ELlabelings}.
 These two special facets are called the \defn{greedy facet} $\greedyFacet$ and the \defn{antigreedy facet} $\antiGreedyFacet$.
 They are the lexicographically smallest and largest facets of $\subwordComplex(Q,\pi)$, respectively.
-
-The poset on the set of facets induced by increasing flips is called the \defn{increasing flip poset}.
-
-\begin{definition}[{\cite{CeballosLabbeStump}}]
-    The \defn{root function} $\rootFunction{I}{\cdot}:[m]\rightarrow \Phi$ associated to a facet $I$ is the map from positions in the word $Q$ to roots defined by 
+The \defn{increasing flip poset} is the transitive closure of the increasing flip graph.
+
+An important tool to study subword complexes are the root functions introduced in~\cite{CeballosLabbeStump}.
+For a facet $I$ of~$\subwordComplex(Q,\omega)$, the \defn{root function} $\rootFunction{I}{\cdot}:[m]\rightarrow \Phi$ sends a position~$k$ in the word $Q$ to the root~$ \rootFunction{I}{k}$ defined by
 \[
@@
 The facet $I$ is called \defn{acyclic} if $\cone \Roots(I)$ is a pointed cone.
-    We denote the \defn{set of acyclic facets} by $\subwordAcyclicFacets(Q,w)$.
-\end{definition}
-
-The root function is a useful and well established tool in the study of subword complexes.
-For instance, they can be used to fully understand flips.
+We denote by $\subwordAcyclicFacets(Q,\omega)$ the set of acyclic facets of the subword complex~$\subwordComplex(Q,\omega)$.
+We will use the following statement that enables to perform flips using the root function.
 
 \begin{lemma}[{\cite{CeballosLabbeStump, KnutsonMiller-subwordComplex}}]
-\label{lem_rootfunction_flips}
-Let $I$ be a facet of the subword complex~$\subwordComplex(Q,w)$.
-The following hold:
+\label{lem:rootFunctionFlips}
+Let $I$ be a facet of the subword complex~$\subwordComplex(Q,\omega)$.
+Then
 \begin{enumerate}
-    \item $i \in I$ is flippable if and only if $\pm \rootFunction{I}{i} \in \Inv(w)$.
+\item $i \in I$ is flippable if and only if $\pm \rootFunction{I}{i} \in \Inv(\omega)$.
 \item If $i \in I$ is flippable, it can be flipped to the unique $j\in [m]\smallsetminus I$ such that $\rootFunction{I}{j} = \pm\rootFunction{I}{i}$.
-    The flip is increasing ($i<j$) when $\rootFunction{I}{i}\in \Phi^+$ and decreasing ($i>j$) when $\rootFunction{I}{i}\in \Phi^-$.\label{lem_rootfunction_flips2}
+The flip is increasing ($i<j$) when $\rootFunction{I}{i}\in \Phi^+$ and decreasing ($i>j$) when $\rootFunction{I}{i}\in \Phi^-$.
+\label{lem:rootFunctionFlips2}
 \item If $I'=I\smallsetminus \{i\}\cap \{i'\}$ is a facet obtained from $I$ by flipping $i$ to $i'$ with $i<i'$, then
-    \begin{equation}\label{eq_rootfunction_flip}
+\[
 \rootFunction{I'}{k} = 
@@
 \end{cases}
-    \end{equation}
+\]
 where $\beta=\rootFunction{I}{i}$ and $s_\beta\in W$ is the reflection orthogonal to the root $\beta$.
-    \item $i \in I$ is not flippable if and only if $\rootFunction{I}{i}\in \Ninv(w)$.
+\label{lem:rootFunctionFlips3}
+\item $i \in I$ is not flippable if and only if $\rootFunction{I}{i}\in \Ninv(\omega)$.
 \end{enumerate}
@@
 
+\begin{example}
+\vincent{todo}
+Connection root configuration --- contact graph.
+\end{example}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{Linear extensions of facets}
+\label{subsec:linearExtensionsFacets}
+
+We now introduce the analogue of \cref{def:linearExtensions} for subword complexes.
+\vincent{Is linear extension a good term? Should we say $W$-extension?}.
 
 \begin{definition}
-Let $\subwordComplex(Q,w)$ be a non-empty subword complex and $I\in \subwordComplex(Q,w)$ be a facet.
-An element $\pi\in W$ is called a \defn{linear extension} of $I$ if the root configuration $\Roots(I)\subseteq \pi(\Phi^+)$.
-The \defn{set of linear extensions} of $I$ is denoted by
-\begin{align}
-\linearExtensions(I)=
-\set{\pi\in W}{\Roots(I)\subseteq \pi(\Phi^+)}.   
-\end{align}
+\label{def:linearExtensionsSubwordComplexes}
+Let $\subwordComplex(Q,\omega)$ be a non-empty subword complex and $I\in \subwordComplex(Q,\omega)$ be a facet.
+A \defn{linear extension} of $I$ is an element $\pi \in W$ such that~$\Roots(I) \subseteq \pi(\Phi^+)$.
+We denote by~$\linearExtensions(I)$ the set of linear extensions of $I$, and by
+\[
+\linearExtensions(Q,\omega) \eqdef \bigcup_{I\in\subwordFacets(Q,\omega)} \linearExtensions(I)
+\]
+the set of linear extensions of all facets of~$\subwordComplex(Q,\omega)$.
 \end{definition}
@@
 \begin{lemma}
-\label{lem_acyclic_nonempty}
-$\linearExtensions(I)\neq \varnothing$ if and only if $I$ is acyclic.
+\label{lem:linearExtensionsAcyclic}
+A facet~$I$ is acyclic if and only if~$\linearExtensions(I)\neq \varnothing$.
 \end{lemma}
-\begin{proof}
-Let $\Phi=\Phi^+\sqcup\Phi^-$ be the root system associated to $W$.
-A known result for root systems of finite type states that any other choice of a positive root system $\Phi^+$ for $\Phi$ is of the form $\widetilde \Phi^+=\pi(\Phi^+)$ for some $w\in W$.
-Since any pointed cone is contained in some $\widetilde \Phi^+$, then 
+
+\begin{proof}
+%Let $\Phi = \Phi^+ \sqcup \Phi^-$ be the root system associated to $W$.
+A classical result for finite root systems states that for any generic linear halfspace~$H^+$ the intersection~$\Phi \cap H^+$ is of the form $\pi(\Phi^+)$ for some $\pi \in W$.
+Since any pointed cone is contained in some generic linear halfspace, we obtain
 \[
@@
   & \longleftrightarrow  &  \linearExtensions(I) \neq \varnothing 
+  \qedhere
 \end{array}
@@
 
+The following lemma regards linear extensions of the greedy and antigreedy facets.
+
 \begin{lemma}
-\label{lem_pi_phiplus_inv_ninv}
-The following holds,
-\[
-\pi(\Phi^+)=-\Inv(\pi)\sqcup \Ninv(\pi).
-\]
-\end{lemma}
-
-\begin{proof}
-This is straight forward from the definition of inversions and non-inversion of $\pi$.
-In fact, multiplying Equation~\eqref{def_inversionset} by $-1$ we deduce $\pi(\Phi^+)\cap \Phi^-=-\Inv(\pi)$.
-Furthermore,  
-$\pi(\Phi^+)\cap \Phi^+=\Ninv(\pi)$ by Equation~\eqref{def_noninversionset}.
-\end{proof}
-
-The following lemma regards linear extensions of the greedy and antigreedy facets.
-
-\begin{lemma}\label{lem_linearext_greedyfacets}
-    Let $\greedyFacet$ and $\antiGreedyFacet$ be the greedy and antigreedy facets of $\subwordComplex(Q,w)$, respectively.
+\label{lem:linearExtensionsGreedyFacets}
+Let $\greedyFacet$ and $\antiGreedyFacet$ be the greedy and antigreedy facets of $\subwordComplex(Q,\omega)$, respectively.
 Then 
@@
 \item $e\in \linearExtensions(\greedyFacet)$.
-        \item $w \in \linearExtensions(\antiGreedyFacet)$.
+\item $\omega \in \linearExtensions(\antiGreedyFacet)$.
 \item If $e\in \linearExtensions(I)$ then $I=\greedyFacet$.
@@
 \end{lemma}
-\begin{proof}
-    Let $e\in W$ be the minimal element of the week order.
+
+\begin{proof}
 The greedy facet $\greedyFacet$ is the unique facet for which every flip (if any) is increasing.
-By \cref{lem_rootfunction_flips}~\eqref{lem_rootfunction_flips2}, this implies that $\greedyFacet$ is the unique facet $I$ such that $\Roots(I)\subseteq \Phi^+ = e(\Phi^+)$.
+By \cref{lem:rootFunctionFlips}~\eqref{lem:rootFunctionFlips2}, this implies that $\greedyFacet$ is the unique facet $I$ such that $\Roots(I)\subseteq \Phi^+ = e(\Phi^+)$.
 This proves parts (1) and (3) of the Lemma.
@@
 For part (2) we need to analyze the possibilities for the set $\Roots(\antiGreedyFacet)$.
- By \cref{lem_rootfunction_flips}~\eqref{lem_rootfunction_flips2}, if $i\in \antiGreedyFacet$ is flippable then $\rootFunction{\antiGreedyFacet}{i}\in -\Inv(w)$.
-Furthermore, if $i\in \antiGreedyFacet$ is not flippable then $\rootFunction{\antiGreedyFacet}{i}\in \Ninv(w)$.
-Therefore, $\Roots(\antiGreedyFacet)\subseteq w(\Phi^+)=-\Inv(w)\sqcup \Ninv(w)$.
-\end{proof}
+By \cref{lem:rootFunctionFlips}~\eqref{lem:rootFunctionFlips2}, if $i\in \antiGreedyFacet$ is flippable then $\rootFunction{\antiGreedyFacet}{i}\in -\Inv(\omega)$.
+Furthermore, if $i\in \antiGreedyFacet$ is not flippable then $\rootFunction{\antiGreedyFacet}{i}\in \Ninv(\omega)$.
+Therefore, $\Roots(\antiGreedyFacet)\subseteq \omega(\Phi^+)=-\Inv(\omega)\sqcup \Ninv(\omega)$.
+\end{proof}
+
+\begin{example}
+%The concept of linear extensions of acyclic facets of subword complexes are a natural generalization of linear extensions of contact graphs of acyclic pipe dreams that we introduced in \cref{subsec:linearExtensions}.
+Connection linear extensions of contact graphs.
+\end{example}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Two theorems on linear extensions of facets}
+\label{subsec:twoTheorems}
+
+In this section, we present our two main results about linear extensions for subword complexes (\cref{thm:linearExtensionsPartitionSubwordComplexA,thm:linearExtensionsPartitionSubwordComplexB}), extending the results of \cref{subsec:linearExtensions}.
+
+A subset $\fR$ of the weak order is 
+\begin{itemize}
+\item a \defn{lower set} if $\sigma < \tau$ and $\tau \in \fR$ implies~$\sigma \in \fR$,
+\item \defn{order convex} if $\sigma < \tau < \rho$ and~$\sigma, \rho \in \fR$ implies~$\tau \in \R$.
+\end{itemize}
+
+\begin{theorem}
+\label{thm:linearExtensionsPartitionSubwordComplexA}
+Let~$\subwordComplex(Q,\omega)$ be a non-empty subword complex.
+Then
+\begin{enumerate}
+\item For any facet~$I$ of~$\subwordComplex(Q,\omega)$ set $\linearExtensions(I)$ is order convex.
+\label{item:convex}
+\hfill (convex) 
+\item  $\linearExtensions(Q,\omega)$ is a lower set of the weak order.
+\label{item:lowerSet}
+\hfill (lower set)
+\item $[e,\omega] \subseteq \linearExtensions(Q,\omega).$
+\label{item:cover}
+\hfill (cover)
+\item If $I_1\neq I_2$ then $\linearExtensions(I_1)\cap \linearExtensions(I_2)=\varnothing$.
+\label{item:partition}
+\hfill (partition)
+\end{enumerate}
+\end{theorem}
 
 \begin{remark}
-The concept of linear extensions of acyclic facets of subword complexes are a natural generalization of linear extensions of contact graphs of acyclic pipe dreams that we introduced in \cref{subsec:linearExtensions}.
-Indeed ... 
-\cesar{make this connection crystal clear...}
-\end{remark}
-
-\subsection{Two fundamental theorems about linear extensions}
-In this section, we present our two main results about linear extensions for subword complexes, \cref{thm_subword_linearextensions_A} and \cref{thm_subword_linearextensions_B}.
-
-We say that a subset $A$ of the weak order is a \defn{lower set} if $a<b$ and $b\in A$ implies $a\in A$.
-We say that $A$ is \defn{closed by intervals} if $a,b\in A$ implies that $[a,b]\in A$, where $[a,b]=\{c: a \leq c\leq b\}$.
-\vincent{I usually say ``order-convex''}
-
-\begin{theorem}\label{thm_subword_linearextensions_A}
-Let~$\subwordComplex(Q,w)$ be a non-empty subword complex.
-The following hold:
-\begin{enumerate}
-\item  $\bigcup_{I\in\subwordFacets(Q,w)} \linearExtensions(I)$ is a lower set of the weak order.
-\label{thmA_item1}
-\hfill (lower set)
-\item $[e,w] \subseteq \bigcup_{I\in\subwordFacets(Q,w)} \linearExtensions(I)$ 
-\label{thmA_item2}
-\hfill (containment)
-\item If $I_1\neq I_2$ then $\linearExtensions(I_1)\cap \linearExtensions(I_2)=\varnothing$.
-\label{thmA_item3}
-\hfill (partition)
-\item The set $\linearExtensions(I)$ is closed by intervals.
-\label{thmA_item4}
-\hfill (interval closed) 
-\end{enumerate}
-\vincent{Replace ``containement'' by ``cover'' and ``partition'' by ``disjoint''?}
-\end{theorem}
-
-\begin{remark}\label{rem_thmA}
-Before proving this theorem, we would like to make the following remarks about items~\eqref{thmA_item2} and~\eqref{thmA_item4}.
+\label{rem:linearExtensionsPartitionSubwordComplexA}
+Before proving this theorem, we would like to make the following remarks about items~\eqref{item:cover} and~\eqref{item:convex}.
 \begin{enumerate}
 \setcounter{enumi}{1}
-\item There are cases where $[e,w] \neq \bigcup_{I\in\subwordFacets(Q,w)}$. \cesarm{add discussion}
+\item There are cases where $[e,\omega] \ne \linearExtensions(Q,\omega)$. \cesarm{add discussion}
+%
 \begin{figure}[h]
@@
 \end{figure}
+%
 \setcounter{enumi}{3}
@@
 
-We will prove the items of the theorem one by one.
-
-\begin{proof}[Proof of \cref{thm_subword_linearextensions_A} \eqref{thmA_item1}]
-Let $\pi\in \linearExtensions(I)$ for some facet $I$.
-We need to show that if $\pi'<\pi$ then there exist another facet $I'$ such that $\pi'\in \linearExtensions(I')$.
-It is enough to show this when $\pi=\pi' s$ for some $s\in S$ such that $\ell(\pi')<\ell(\pi)$.
-
-By definition, $\pi\in \linearExtensions(I)$ if and only if $\Roots(I)\subseteq \pi(\Phi^+)$.
+We will now prove the four points of \cref{thm:linearExtensionsPartitionSubwordComplexA} one by one.
+
+\begin{proof}[Proof of \cref{thm:linearExtensionsPartitionSubwordComplexA}~\eqref{item:convex}]
+Let $\sigma < \tau < \rho$ be such that~$\sigma, \rho \in \linearExtensions(I)$.
+By definition of linear extensions, we have
+\[
+\Roots(I) \subseteq \sigma(\Phi^+)=-\Inv(\sigma) \sqcup \Ninv(\sigma)
+\quad\text{and}\quad
+\Roots(I) \subseteq \rho(\Phi^+)=-\Inv(\rho) \sqcup \Ninv(\rho).
+\]
+Restricting to the set of negative and positive roots, respectively, we deduce
+\[
+\Roots(I) \cap \Phi^- \subseteq -\Inv(\sigma) \subseteq -\Inv(\tau) \qquad 
+\Roots(I) \cap \Phi^+ \subseteq \Ninv(\rho)  \subseteq \Ninv(\tau)
+\]
+since~$\sigma < \tau < \rho$. Therefore
+\[
+\Roots(I) \subseteq -\Inv(\tau) \sqcup \Ninv(\tau) = \tau(\Phi^+)
+\]
+and so $\tau \in \linearExtensions(I)$.
+\end{proof}
+
+\begin{proof}[Proof of \cref{thm:linearExtensionsPartitionSubwordComplexA} \eqref{item:lowerSet}]
+Let $\pi \in \linearExtensions(I)$ for some facet $I$.
+We need to show that if $\pi' < \pi$ then there exist another facet $I'$ such that $\pi' \in \linearExtensions(I')$.
+It is enough to show this when $\pi = \pi's$ for some descent~$s$ of~$\pi$ (\ie some $s\in S$ such that $\ell(\pi') < \ell(\pi)$).
+
+By definition, $\pi \in \linearExtensions(I)$ if and only if $\Roots(I) \subseteq \pi(\Phi^+)$.
 Now,
@@
 and 
-\begin{align*}
-    \Inv(\pi') &=\Inv(\pi)\smallsetminus \{\beta\} \\
-    \Ninv(\pi') &= \Ninv(\pi) \cup \{\beta\}
-\end{align*}
+\[
+\Inv(\pi') =\Inv(\pi) \smallsetminus \{\beta\}
+\qquad\text{and}\qquad
+\Ninv(\pi') = \Ninv(\pi) \cup \{\beta\}
+\]
 for $\beta=\pi'(\alpha_s)$.
@@
 \[
-\pi(\Phi^+)\smallsetminus \{-\beta\}=
-\pi'(\Phi^+)\smallsetminus \{\beta\}=
-\pi(\Phi^+)\cap \pi'(\Phi^+).
+\pi(\Phi^+) \smallsetminus \{-\beta\} = \pi'(\Phi^+) \smallsetminus \{\beta\} = \pi(\Phi^+) \cap \pi'(\Phi^+).
 \]
 This observation will be useful to prove the statement in the second of the following two cases.
+\vincent{I believe we could shorten all this discussion. Also the picture is not really useful.}
 
 \medskip
-{\bf Case 1}: $-\beta \notin \Roots(I)$.
+\paragraph{\bf Case 1:} $-\beta \notin \Roots(I)$.
 
@@
 \medskip
-{\bf Case 2}: $-\beta \in \Roots(I)$.
+\paragraph{\bf Case 2:} $-\beta \in \Roots(I)$.
 
@@
 
-Given a facet $I$ of a subword complex~$\subwordComplex(Q,w)$ and a positive root $\beta\in \Phi^+$, the restriction of the list of roots 
+Given a facet $I$ of a subword complex~$\subwordComplex(Q,\omega)$ and a positive root $\beta\in \Phi^+$, the restriction of the list of roots 
 \[
@@
 But if there is a $-\beta$ in this list, then there should be at least one $\beta$ preceding it.
-The position $i$ of the last $\beta$ is used in the reduced expression of $w$ in the complement of $I$, that is $i\notin I$.
-The positions of the other $\beta$'s and $-\beta$'s all belong to~$I$, and can all be flipped to $i$ (see \cref{lem_rootfunction_flips}~\eqref{lem_rootfunction_flips2}).   
+The position $i$ of the last $\beta$ is used in the reduced expression of $\omega$ in the complement of $I$, that is $i\notin I$.
+The positions of the other $\beta$'s and $-\beta$'s all belong to~$I$, and can all be flipped to $i$ (see \cref{lem:rootFunctionFlips}~\eqref{lem:rootFunctionFlips2}).   
 In particular, the position $j$ of the last $-\beta$ belongs to $I$, and it can be flipped to $i$ creating a new facet $I'=I\smallsetminus \{j\} \cap \{i\}$.
@@
 \end{equation}
-Flipping $j$ to $i$ creates the new facet $I'=I\smallsetminus \{j\} \cap \{i\}$ whose corresponding restricted list looks like
+By  \cref{lem:rootFunctionFlips}~\eqref{lem:rootFunctionFlips3}, we obtain that flipping $j$ to $i$ creates the new facet $I' = I \smallsetminus \{j\} \cap \{i\}$ whose corresponding restricted list looks like
 \begin{equation}
@@
 \end{equation}
-Indeed, Equation~\eqref{eq_rootfunction_flip} describes how the root function is modified after a flip.
-For a position $k$ satisfying $i<k\leq j$, we have $\rootFunction{I'}{k}=s_\beta (\rootFunction{I}{k})$; otherwise we have $\rootFunction{I'}{k}=\rootFunction{I}{k}$.
-Then, all $-\beta$'s get transformed into $\beta$'s.
 
 Moreover, since the reflection $s_\beta$ preserves the set 
-$$\pi'(\Phi^+)\smallsetminus \{\beta\} =
-\pi(\Phi^+)\smallsetminus \{-\beta\} =
-\pi(\Phi^+) \cap \pi'(\Phi^+).
-$$
-then $\Roots(I')\subseteq \pi'(\Phi^+)$.
+\[
+\pi'(\Phi^+) \smallsetminus \{\beta\} = \pi(\Phi^+) \smallsetminus \{-\beta\} = \pi(\Phi^+) \cap \pi'(\Phi^+).
+\]
+then $\Roots(I') \subseteq \pi'(\Phi^+)$.
 Thus, $\pi'\in \linearExtensions(I')$ as desired.
@@
 
-\begin{proof}[Proof of \cref{thm_subword_linearextensions_A}~\eqref{thmA_item2}]
-By part \eqref{thmA_item1}, the union of all linear extensions of facets is a lower set.
-So, we just need to show that $w$ belongs to this set.
-This follows from $w\in \linearExtensions(\antiGreedyFacet)$, which was proven in \cref{lem_linearext_greedyfacets}.
-\end{proof}
-
-\begin{proof}[Proof of \cref{thm_subword_linearextensions_A}~\eqref{thmA_item3}]
-We will show that if there is an element $\pi\in \linearExtensions(I_1)\cap \linearExtensions(I_2)$ then $I_1= I_2$.
-We already showed this for $\pi=e$ in \cref{lem_linearext_greedyfacets}.
-
-Let $I_1, I_2$ be two facets such that $e\neq \pi \in \linearExtensions(I_1)\cap \linearExtensions(I_2)$.
-As in the proof of part \eqref{thmA_item1}, let $\pi'=\pi s$ for some $s\in S$ such that $\ell(\pi')<\ell(\pi)$, and let $I_1',I_2'$ be the corresponding facets obtained using the same steps of the proof.
-These new facets satisfy $\pi'\in \linearExtensions(I_1')\cap \linearExtensions(I_2')$.
-
-We claim that $I_1=I_2$ if and only if $I_1'=I_2'$.
-The forward direction is clear.
-For the reverse direction we analyze the two cases if the proof of part \eqref{thmA_item1}.
+\begin{proof}[Proof of \cref{thm:linearExtensionsPartitionSubwordComplexA}~\eqref{item:cover}]
+By part \eqref{item:lowerSet}, the union of all linear extensions of facets is a lower set.
+So, we just need to show that $\omega$ belongs to this set.
+This follows from $\omega\in \linearExtensions(\antiGreedyFacet)$, which was proven in \cref{lem:linearExtensionsGreedyFacets}.
+\end{proof}
+
+\begin{proof}[Proof of \cref{thm:linearExtensionsPartitionSubwordComplexA}~\eqref{item:partition}]
+We show that if there is two facets~$I_1, I_2$ of~$\subwordComplex(Q, \omega)$ and an element~$\pi \in W$ such that $\pi \in \linearExtensions(I_1) \cap \linearExtensions(I_2)$ then~$I_1= I_2$.
+The proof works by induction on the length~$\ell(\pi)$ of~$\pi$.
+We already showed this for $\pi = e$ in \cref{lem:linearExtensionsGreedyFacets}.
+
+Let $I_1, I_2$ be two facets such that $e \neq \pi \in \linearExtensions(I_1)\cap \linearExtensions(I_2)$.
+As in the proof of part \eqref{item:lowerSet}, let $\pi'=\pi s$ for some $s\in S$ such that $\ell(\pi')<\ell(\pi)$, and let $I_1',I_2'$ be the corresponding facets obtained using the same steps of the proof.
+These new facets satisfy $\pi' \in \linearExtensions(I_1')\cap \linearExtensions(I_2')$, so that~$I_1' = I_2'$ by induction.
+
+We now claim that it implies that~$I_1 = I_2$.
+We analyze the two cases if the proof of part \eqref{item:lowerSet}.
 Note that in Case~1, the resulting facet~$I'$ obtained from $I$ satisfies $\beta\notin \Roots(I')$, while in Case 2 we have $\beta \in \Roots(I')$. 
-Therefore, if $I_1'=I_2'$ then both $I_1$ and $I_2$ fall into Case 1 or both into Case 2.
+As $I_1' = I_2'$, this shows that $I_1$ and $I_2$ fall either both into Case 1 or both into Case 2.
 If both fall into Case 1, then $I_1'=I_1$ and $I_2'=I_2$ and so $I_1=I_2$ as desired.
 If both fall into Case 2, then we just need to flip back the performed flip to obtain $I_1=I_2$.
-
-Now we need to show that $I_1=I_2$.
-We proceed by contradiction.
-If $I_1\neq I_2$, then $I_1'\neq I_2'$ and $\pi'\in \linearExtensions(I_1')\cap \linearExtensions(I_2')$.
-We can continue going down in the week order until reaching the minimal element $e$.
-The resulting two facets are different and their linear extensions contain $e$.
-This is a contradiction to \cref{lem_linearext_greedyfacets}.  
-\vincent{This paragraph is not needed. Say it better in the first paragraph of the proof of (3).}
-\end{proof}
-
-\begin{proof}[Proof of \cref{thm_subword_linearextensions_A}~\eqref{thmA_item4}]
-Let $\pi_1,\pi_2\in \linearExtensions(I)$ and assume $\pi_1<\pi_2$.
-We need to show that if $\pi_1\leq \pi \leq \pi_2$ then~$\pi \in \linearExtensions(I)$.
-By definition of linear extensions and \cref{lem_pi_phiplus_inv_ninv} we have
-\[
-\Roots(I) \subseteq \pi_i(\Phi^+)=-\Inv(\pi_i)\sqcup \Ninv(\pi_i)
-\]
-for $i=1,2$.
-Restricting to the set of negative and positive roots, respectively, we deduce
-\[
-\Roots(I)\cap \Phi^- \subseteq -\Inv(\pi_1) \subseteq -\Inv(\pi) \qquad 
-\Roots(I)\cap \Phi^+ \subseteq \Ninv(\pi_2)  \subseteq \Ninv(\pi)
-\]
-Therefore
-\[
-\Roots(I) \subseteq \pi(\Phi^+)=-\Inv(\pi)\sqcup \Ninv(\pi)
-\]
-and so $\pi\in \linearExtensions(I)$.
-\end{proof}
-
-For simplicity, we denote by 
-\[
-\linearExtensions(Q,w) = \bigcup_{I\in\subwordFacets(Q,w)} \linearExtensions(I)
-\]
-the \defn{set of linear extensions of all facets} of $\subwordComplex(Q,w)$.
-Since $\linearExtensions(I)\neq \varnothing$ if and only if $I$ is acyclic (\cref{lem_acyclic_nonempty}), we have the following straight forward corollary.
-
-\begin{corollary}\label{cor_linearextensions_partition}
-The following holds:    
-\begin{align}
-    \linearExtensions(Q,w) =
-    \bigsqcup_{I\in\subwordAcyclicFacets(Q,w)} \linearExtensions(I).
-\end{align}
+\end{proof}
+
+Since $\linearExtensions(I)\neq \varnothing$ if and only if $I$ is acyclic by \cref{lem:linearExtensionsAcyclic}, we have the following straight forward corollary.
+
+\begin{corollary}\label{coro:linearExtensionsPartitionSubwordComplexes}
+For any word~$Q$ and element~$\omega$,
+\[
+\linearExtensions(Q,\omega) = \bigsqcup_{I\in\subwordAcyclicFacets(Q,\omega)} \linearExtensions(I).
+\]
 \end{corollary}
 
-As pointed out in \cref{rem_thmA}, there are subword complexes for which $[e,w] \neq \bigcup_{I\in\subwordFacets(Q,w)}$.
+As pointed out in \cref{rem:linearExtensionsPartitionSubwordComplexA}, there are subword complexes for which $[e,\omega] \neq \linearExtensions(Q,\omega)$.
 Our second fundamental theorem describes a large family of cases where equality holds.
-
-\begin{theorem}\label{thm_subword_linearextensions_B}
-
-Let $\subwordComplex(Q,w)$ be a non-empty subword complex such that the word $Q$ contains a reduced expression of $\wo$.
-The linear extensions of acyclic facets of $\subwordComplex(Q,w)$ form a partition of the interval $[e,w]$:
-\begin{align}
-    [e,w] =
-    \bigsqcup_{I\in\subwordAcyclicFacets(Q,w)} \linearExtensions(I).
-\end{align}
+We say that a word~$Q$ is \defn{sorting} if it contains a reduced expression of $\wo$.
+Equivalently~$Q$ contains a reduced expression for any element~$w \in W$.
+Still equivalently, $\DemazureProduct(Q) = \wo$ where~$\DemazureProduct(Q)$ denotes the \defn{Demazure product} of~$Q$, defined by~$\DemazureProduct(\varepsilon) = e$ and~$\DemazureProduct(Qs) = \max(\DemazureProduct(Q), \DemazureProduct(Q)s)$ (where the $\max$ is in weak order).
+
+\begin{theorem}
+\label{thm:linearExtensionsPartitionSubwordComplexB}
+If the word $Q$ is sorting, then the linear extensions of acyclic facets of $\subwordComplex(Q,\omega)$ form a partition of the interval $[e,\omega]$, that is
+\[
+[e,\omega] = \bigsqcup_{I\in\subwordAcyclicFacets(Q,\omega)} \linearExtensions(I).
+\]
 \end{theorem}
 
-The proof of this theorem is based on the following proposition, which follows from~\cite[Theorem~3.1 and Corollary 3.3]{JahnStump}.
+The proof is based on the following statement, which follows from~\cite[Thm.~3.1 \& Coro.~3.3]{JahnStump}.
 
 \begin{proposition}[{\cite{JahnStump}}]\label{prop_jahnStump_intersection}
-    Let $\subwordComplex(Q,w)$ be a non-empty subword complex such that the word $Q$ contains a reduced expression of $\wo$.
-Then 
-    \[
-\left(
-\bigcap_{I\in \subwordFacets(Q,\pi)} \cone \Roots(I) 
-\right)
-\cap \Phi
-= 
-\Ninv(w).
+If the word $Q$ is sorting, then 
+\[
+\Big( \bigcap_{I\in \subwordFacets(Q,\omega)} \cone \Roots(I) \Big) \cap \Phi^+ = \Ninv(\omega).
 \]
 \end{proposition}
+
 \begin{proof}
 We include a short proof here for self containment.
-We refer to~\cite{JahnStump} for the description of the notation $C^+(w,\cdot)$.
+We refer to~\cite{JahnStump} for the description of the notation $C^+(\omega,\cdot)$.
 By~\cite[Theorem~3.1]{JahnStump} we have
 \[
-\bigcap_{I\in \subwordFacets(Q,\pi)} \cone \Roots(I) =
-C^+(w,\DemazureProduct(Q)).
+\bigcap_{I\in \subwordFacets(Q,\pi)} \cone \Roots(I) = C^+(\omega,\DemazureProduct(Q)).
 \]
@@
 \[
-C^+(w,\wo)\cap \Phi
-= \Inv(w \wo) = \Ninv(w).
-    \]    
-\end{proof}
-
-\begin{proof}[Proof of \cref{thm_subword_linearextensions_B}]
-Assume $\pi\in \linearExtensions(I)$.
-We want to show that $\pi<w$.
-By \cref{prop_jahnStump_intersection} we have 
-\[
-\Ninv(w) 
-\subseteq \cone \Roots(I) 
-\subseteq \cone \pi(\Phi^+).
-\]
-Therefore
-\[
-\Ninv(w) 
-\subseteq \cone \pi(\Phi^+) \cap \Phi^+ 
-= \Ninv(\pi).
-\]
-Thus $\pi \leq w$ as desired.
-\end{proof}
+C^+(\omega,\wo)\cap \Phi^+ = \Inv(\omega \wo) = \Ninv(\omega).
+\qedhere
+\]
+\end{proof}
+
+\begin{proof}[Proof of \cref{thm:linearExtensionsPartitionSubwordComplexB}]
+If $\pi \in \linearExtensions(I)$ for some facet~$I$ of~$\subwordComplex(Q, \omega)$, then by \cref{prop_jahnStump_intersection} we have 
+\[
+\Ninv(\omega) \subseteq \cone \Roots(I) \cap \Phi^+ \subseteq \cone \pi(\Phi^+) \cap \Phi^+  = \Ninv(\pi).
+\]
+Thus $\pi \le \omega$ as desired.
+\end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Two conjectures on linear extensions of facets}
+\label{subsec:twoConjectures}
+
+In this section, we present two conjectural generalizations of the results of \cref{subsec:pipeDreamCongruence,subsec:pipeDreamQuotient}.
+We first introduce the analogue of \cref{def:pipeDreamCongruence} for subword complexes.
+
+\begin{definition}
+\label{def:pipeDreamCongruenceSubwordComplexes}
+For a non-empty subword complex $\subwordComplex(Q,\omega)$, the \defn{subword complex congruence} is the equivalence relation~$\equiv_{Q,\omega}$ on the set~$\linearExtensions(Q,\omega) \eqdef \sqcup_{I \in \subwordAcyclicFacets(Q, \omega)} \linearExtensions(I)$  whose equivalence classes are the sets~$\linearExtensions(I)$ of linear extensions of the acyclic facets~$I$ of~$\subwordComplex(Q, \omega)$.
+In other words, $\pi \equiv_{Q,\omega} \pi'$ if and only if $\pi$ and $\pi'$ are linear extensions of the same facet.  
+\end{definition}
+
+Note that the subword complex congruence indeed defines an equivalence relation by \cref{coro:linearExtensionsPartitionSubwordComplexes}.
+However, it is in general not a lattice congruence for two obvious reasons:
+\begin{itemize}
+\item while~$\linearExtensions(Q,\omega)$ is a lower set of the weak order containing~$[e, \omega]$ by \cref{thm:linearExtensionsPartitionSubwordComplexA}, it does not necessarily have a maximal element, hence it is not necessarily a lattice,
+\item while the sets~$\linearExtensions(I)$ are always order convex in the weak order by \cref{thm:linearExtensionsPartitionSubwordComplexA}~\eqref{item:convex}, they are not necessarily intervals in the weak order by \cref{rem:linearExtensionsPartitionSubwordComplexA}.
+\end{itemize}
+These two issues can however be bypassed with additional assumptions on the word~$Q$.
+Recall that a word~$Q$ is
+\begin{itemize}
+\item \defn{sorting} if it contains a reduced expression of $\wo$ (see just before \cref{thm:linearExtensionsPartitionSubwordComplexB}),
+\item \defn{alternating} if all non-commuting pairs $s, t\in S$ alternate within $Q$ (see \cite{PilaudSantos-brickPolytope, CeballosLabbeStump}).
+\end{itemize}
+By \cref{thm:linearExtensionsPartitionSubwordComplexB}, $\linearExtensions(Q,\omega) = [e, \omega]$ if $Q$ is sorting.
+
+\begin{conjecture}
+If the word~$Q$ is sorting and alternating, then for any~$\omega \in W$, the subword complex congruence~$\equiv_{Q,\omega}$ is a lattice congruence of the interval~$[e,\omega]$ of the weak order.
+\end{conjecture}
+
+This conjecture holds in type~$A_n$: our specific proof of~\cref{thm:pipeDreamCongruence} can be extended to arbitrary sorting and alternating words in type~$A_n$ as shown in~\cite{Cartier}.
+It is also supported by extensive computer experiments: we verified it in types...
+\cesarm{Noemie: in which cases did you check this conjecture? Type $A_n$ for n=???, B,C,D,....?}
+
+\vincent{I am working below this line}
+
+\cesarm{To do: meet to discuss about this section? put it in final form...}
+
+cesarm{Do we have more conjectures or questions to be included here?}
+
+\begin{remark}\label{rem_acyclicflipposet_not_latticequotient}
+In analogy to the case of pipe dreams in \cref{subsec:proofCongruence}, one might expect that the quotient~$[e,\omega]/\equiv_{Q,\omega}$ is isomorphic to the restriction of the increasing flip poset of $\subwordComplex(Q,\omega)$ to the set of acyclic facets.
+But this is not the case as shown in \cref{ex_acyclicflip_not_weakorder_related}.     
+\end{remark}
+
+\begin{example}\label{ex_acyclicflip_not_weakorder_related}
+    Let $W=S_3$ be the symmetric group generated by simple transpositions $S=\{s_1,s_2\}$ with $s_i=(i, i+1 )$.
+Let $Q=(s_1,s_2,s_1,s_2,s_1,s_2)$ and $\omega=\wo=s_1s_2s_1=s_2s_1s_2$.
+The subword complex $\subwordComplex(Q,\omega)$ has eight facets, six of which are acyclic.
+    All the fibers of $\equiv_{Q,\omega}$ are singletons and the lattice quotient~$[e,\omega]/\equiv_{Q,\omega}$ coincides with the weak order of type $A_2$.
+    On the other hand there are two facets, $I_1=\{1,3,4\}$ and $I_2=\{3,4,6\}$, which are connected by a flip but whose corresponding elements $\pi_1$ and $\pi_2$ are not related in weak order.
+    \cesar{To do: Double check and expand this example in detail. Add figure.}
+\end{example}
+
+As we have seen in \cref{cor_acyclicpipedreams_lattice}, the increasing flip poset of acyclic pipe dreams of any permutation $\omega$ is a lattice, because it is isomorphic to the lattice quotient~$[e,\omega]/\equiv_\omega$.
+This motivates the following open question for subword complexes.
+
+\begin{question}
+Let $\subwordComplex(Q,\omega)$ be a non-empty subword complex.
+Is the restriction of the increasing flip poset of $\subwordComplex(Q,\omega)$ to the set of acyclic facets a lattice?    
+\end{question}
+
+As pointed out in \cref{rem_acyclicflipposet_not_latticequotient},  we can not expect~$[e,\omega]/\equiv_{Q,\omega}$ to be isomorphic to the restriction of the increasing flip poset of $\subwordComplex(Q,\omega)$ to the set of acyclic facets.
+\cref{ex_acyclicflip_not_weakorder_related} shows that there are flips between acyclic facets that are not detected by the week order.
+One could expect that there is a natural restriction to a special class of flips that behave nicer, meaning that all of them are identified by the quotient~$[e,\omega]/\equiv_{Q,\omega}$.
+In our \cref{ex_acyclicflip_not_weakorder_related}, the generalized Chute moves from~\cite{Rubey} do the job, because the flip that is not detected by the week order is exactly the one flip which is not Chute.
+The Chute lattice conjecture~\cite[Conjecture~2.8]{Rubey} might be an indication that this is the right direction to look at.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \subsection{The sweeping algorithm}
-
-Given a linear extension $\pi \in \linearExtensions(Q,w)$, one natural question is whether we can recover the unique acyclic facet $I$ such that $\pi \in \linearExtensions(I)$.
+\label{subsec:sweepingAlgorithmSubwordComplexes}
+
+Given a linear extension $\pi \in \linearExtensions(Q,\omega)$, one natural question is whether we can recover the unique acyclic facet $I$ such that $\pi \in \linearExtensions(I)$.
 We can recover this facet via a sweeping algorithm which we now introduce.
-The algorithm outcomes a facet for every element~$\pi \in W$, and this will be the desired facet for each $\pi \in \linearExtensions(Q,w)$.
+The algorithm outcomes a facet for every element~$\pi \in W$, and this will be the desired facet for each $\pi \in \linearExtensions(Q,\omega)$.
 
@@
 \begin{tabular}{cccc}
-$\sweepingAlgorithm$ : & $W$  &$\longrightarrow$ &$\subwordFacets(Q,w)$\\
-    & $\pi$ & $\longrightarrow$ & $\sweepingAlgorithm(Q,w,\pi)$
+$\sweepingAlgorithm$ : & $W$  &$\longrightarrow$ &$\subwordFacets(Q,\omega)$\\
+    & $\pi$ & $\longrightarrow$ & $\sweepingAlgorithm(Q,\omega,\pi)$
 \end{tabular}
@@
 \begin{enumerate}
-    \item If $\rootFunction{I^j}{j}\in \Ninv(w)$ then let 
+    \item If $\rootFunction{I^j}{j}\in \Ninv(\omega)$ then let 
     \[
@@
     \label{sweeping_case1}
-    \item If $\rootFunction{I^j}{j}\in \Inv(w) \cap \Inv (\pi)$ then let 
+    \item If $\rootFunction{I^j}{j}\in \Inv(\omega) \cap \Inv (\pi)$ then let 
     \[
@@
     \label{sweeping_case2}
-    \item If $\rootFunction{I^j}{j}\in \Inv(w) \cap \Ninv (\pi)$ then we consider two cases: 
+    \item If $\rootFunction{I^j}{j}\in \Inv(\omega) \cap \Ninv (\pi)$ then we consider two cases: 
     \label{sweeping_case3} 
     \begin{enumerate}
-        \item If $Q_{[m]\smallsetminus I^{j-1}\smallsetminus \{j\}}$ contains a reduced expression of $w$ with prefix $Q^{j-1}$ then let 
+        \item If $Q_{[m]\smallsetminus I^{j-1}\smallsetminus \{j\}}$ contains a reduced expression of $\omega$ with prefix $Q^{j-1}$ then let 
         \[
@@
     \end{enumerate}
-    \item If $\rootFunction{I^j}{j}\in -\Inv(w)$ then let
+    \item If $\rootFunction{I^j}{j}\in -\Inv(\omega)$ then let
     \[
@@
 
-We denote by \defn{$\sweepingAlgorithm(Q,w,\pi)$} the resulting set $I^m$ obtained at the last step of the algorithm.
-
-Roughly speaking, the goal of the algorithm is to insert a reduced expression of $w$ in $Q$ by sweeping the word from left to right, while deciding whether we use a letter or not by looking at the root $\beta=\rootFunction{I^j}{j}$ that it produces.
-If $\beta \in \Ninv(w)$ then it can not be used (Case~\eqref{sweeping_case1}), otherwise we would not have a reduced expression for $w$.
-If $\beta \in \Inv(w)$ then we take it when $\beta \in \Inv(\pi)$ (Case~\eqref{sweeping_case2}), or delay it as much as possible when $\beta \in \Ninv(\pi)$ (Case~\eqref{sweeping_case3}).
-If $\beta \in -\Inv(w)$ we can simply not take it (Case~\eqref{sweeping_case4}).
+We denote by \defn{$\sweepingAlgorithm(Q,\omega,\pi)$} the resulting set $I^m$ obtained at the last step of the algorithm.
+
+Roughly speaking, the goal of the algorithm is to insert a reduced expression of $\omega$ in $Q$ by sweeping the word from left to right, while deciding whether we use a letter or not by looking at the root $\beta=\rootFunction{I^j}{j}$ that it produces.
+If $\beta \in \Ninv(\omega)$ then it can not be used (Case~\eqref{sweeping_case1}), otherwise we would not have a reduced expression for $\omega$.
+If $\beta \in \Inv(\omega)$ then we take it when $\beta \in \Inv(\pi)$ (Case~\eqref{sweeping_case2}), or delay it as much as possible when $\beta \in \Ninv(\pi)$ (Case~\eqref{sweeping_case3}).
+If $\beta \in -\Inv(\omega)$ we can simply not take it (Case~\eqref{sweeping_case4}).
 
@@
 \label{prop_sweeping1}
-    Let $\subwordComplex(Q,w)$ be a non-empty subword complex.
-    For every $\pi \in W$, the set $\sweepingAlgorithm(Q,w,\pi)$ is a facet of $\subwordComplex(Q,w)$.
+    Let $\subwordComplex(Q,\omega)$ be a non-empty subword complex.
+    For every $\pi \in W$, the set $\sweepingAlgorithm(Q,\omega,\pi)$ is a facet of $\subwordComplex(Q,\omega)$.
 \end{proposition}
@@
 
-    {\bf Claim}: $Q^j$ is a reduced expression which is the prefix of a reduced expression of $w$ in $Q_{[m]\smallsetminus I^j}$.
+    {\bf Claim}: $Q^j$ is a reduced expression which is the prefix of a reduced expression of $\omega$ in $Q_{[m]\smallsetminus I^j}$.
 
@@
     For $j=0$, $Q^0$ is the empty word which is reduced by definition.
-    Furthermore, $Q_{[m]\smallsetminus I^0 }=Q$ contains a reduced expression of $w$ because the subword complex is non-empty.
+    Furthermore, $Q_{[m]\smallsetminus I^0 }=Q$ contains a reduced expression of $\omega$ because the subword complex is non-empty.
 The empty word is a prefix of this reduced expression.
@@
     \begin{enumerate}
-    \item If $\rootFunction{I^j}{j}\in \Ninv(w)$ then 
+    \item If $\rootFunction{I^j}{j}\in \Ninv(\omega)$ then 
     $Q^j=Q^{j-1}$, which is reduced by induction hypothesis.
-    Moreover, it is a prefix of a reduced expression of $w$ in $Q_{[m]\smallsetminus I^{j-1}}$.
-    Since $\rootFunction{I^j}{j}\in \Ninv(w)$, this reduced expression can not use the letter $q_j$; so, it is a reduced expression of $w$ in $Q_{[m]\smallsetminus I^{j}}$ as desired.
-    \item If $\rootFunction{I^j}{j}\in \Inv(w) \cap \Inv (\pi)$ then $Q^j= Q^{j-1}\circ (q_j)$, which is a reduced expression because~$Q^{j-1}$ is reduced and $\rootFunction{I^j}{j}\in \Inv(w)$.
-
-    Now let $\widetilde Q$ be a subword of $Q_{[m]\smallsetminus I^{j-1}}=Q_{[m]\smallsetminus I^{j}}$ which is a reduced expression of $w$ with prefix $Q^{j-1}$, and let $\widetilde I$ be the corresponding facet.
+    Moreover, it is a prefix of a reduced expression of $\omega$ in $Q_{[m]\smallsetminus I^{j-1}}$.
+    Since $\rootFunction{I^j}{j}\in \Ninv(\omega)$, this reduced expression can not use the letter $q_j$; so, it is a reduced expression of $\omega$ in $Q_{[m]\smallsetminus I^{j}}$ as desired.
+    \item If $\rootFunction{I^j}{j}\in \Inv(\omega) \cap \Inv (\pi)$ then $Q^j= Q^{j-1}\circ (q_j)$, which is a reduced expression because~$Q^{j-1}$ is reduced and $\rootFunction{I^j}{j}\in \Inv(\omega)$.
+
+    Now let $\widetilde Q$ be a subword of $Q_{[m]\smallsetminus I^{j-1}}=Q_{[m]\smallsetminus I^{j}}$ which is a reduced expression of $\omega$ with prefix $Q^{j-1}$, and let $\widetilde I$ be the corresponding facet.
 
@@
 
-    If $j\in \widetilde I$, then we can flip it to a position $j'>j$ (by \cref{lem_rootfunction_flips}~\eqref{lem_rootfunction_flips2}), creating a new reduced expression $\widetilde Q'$ of $w$ which uses $q_j$, and thus has $Q^j$ as a prefix.
-
-    \item[(3)(a)] If $\rootFunction{I^j}{j}\in \Inv(w) \cap \Ninv (\pi)$ and $Q_{[m]\smallsetminus I^{j-1}\smallsetminus \{j\}}$ contains a reduced expression of $w$ with prefix $Q^{j-1}$, then $Q^j=Q^{j-1}$.
-    Therefore, $Q^j$ is reduced and it is a prefix of a reduced expression of $w$ in 
+    If $j\in \widetilde I$, then we can flip it to a position $j'>j$ (by \cref{lem:rootFunctionFlips}~\eqref{lem:rootFunctionFlips2}), creating a new reduced expression $\widetilde Q'$ of $\omega$ which uses $q_j$, and thus has $Q^j$ as a prefix.
+
+    \item[(3)(a)] If $\rootFunction{I^j}{j}\in \Inv(\omega) \cap \Ninv (\pi)$ and $Q_{[m]\smallsetminus I^{j-1}\smallsetminus \{j\}}$ contains a reduced expression of $\omega$ with prefix $Q^{j-1}$, then $Q^j=Q^{j-1}$.
+    Therefore, $Q^j$ is reduced and it is a prefix of a reduced expression of $\omega$ in 
     $Q_{[m]\smallsetminus I^{j-1}\smallsetminus \{j\}}=Q_{[m]\smallsetminus I^j}$.
 
-    \item[(3)(b)] In this case, $\rootFunction{I^j}{j}\in \Inv(w) \cap \Ninv (\pi)$ but $Q^j= Q^{j-1}\circ (q_j)$. The proof is similar to the proof of (2).
-
-    \item[(4)] If $\rootFunction{I^j}{j}\in -\Inv(w)$ then $Q^j=Q^{j-1}$. The argument is similar to that of part (1).
+    \item[(3)(b)] In this case, $\rootFunction{I^j}{j}\in \Inv(\omega) \cap \Ninv (\pi)$ but $Q^j= Q^{j-1}\circ (q_j)$. The proof is similar to the proof of (2).
+
+    \item[(4)] If $\rootFunction{I^j}{j}\in -\Inv(\omega)$ then $Q^j=Q^{j-1}$. The argument is similar to that of part (1).
     \end{enumerate}
@@
 \[
-\Phi^+ = \Inv(w) \sqcup \Ninv(w) \qquad \qquad
-\Phi^- = -\Inv(w) \sqcup -\Ninv(w)  
+\Phi^+ = \Inv(\omega) \sqcup \Ninv(\omega) \qquad \qquad
+\Phi^- = -\Inv(\omega) \sqcup -\Ninv(\omega)  
 \]
 The positive roots are covered by the cases (1),(2), and (3).
-The negative roots in $-\Inv(w)$ are covered in case (4).
-Since we are inserting a reduced expression of $w$ in $Q$, the case $-\Ninv(w)$ never occurs. 
-\end{proof}
-
-The following proposition shows that for every linear extension $\pi \in \linearExtensions(Q,w)$, the sweeping algorithm recovers the unique acyclic facet $I$ such that $\pi \in \linearExtensions(I)$.
+The negative roots in $-\Inv(\omega)$ are covered in case (4).
+Since we are inserting a reduced expression of $\omega$ in $Q$, the case $-\Ninv(\omega)$ never occurs. 
+\end{proof}
+
+The following proposition shows that for every linear extension $\pi \in \linearExtensions(Q,\omega)$, the sweeping algorithm recovers the unique acyclic facet $I$ such that $\pi \in \linearExtensions(I)$.
 
@@
 \label{prop_sweeping2}
-    If $\pi\in \linearExtensions(I)$ for some facet $I\in \subwordComplex(Q,w)$, then 
-    \[
-I = \sweepingAlgorithm(Q,w,\pi).
+    If $\pi\in \linearExtensions(I)$ for some facet $I\in \subwordComplex(Q,\omega)$, then 
+    \[
+I = \sweepingAlgorithm(Q,\omega,\pi).
     \]
@@
 \begin{lemma}\label{lem_negativeroot}
-    Let $I_1,I_2\in \subwordComplex(Q,w)$ be two different facets, and $j\in [m]$ be the first position where they differ.
+    Let $I_1,I_2\in \subwordComplex(Q,\omega)$ be two different facets, and $j\in [m]$ be the first position where they differ.
     Without loss of generality assume 
@@
 \begin{enumerate}
-    \item If $\rootFunction{I^j}{j}\in \Ninv(w)$ then clearly $j\in I$ is forced. Otherwise $Q_{[m]\smallsetminus I}$ would not be a reduced expression of $w$.
-    \item If $\rootFunction{I^j}{j}\in \Inv(w) \cap \Inv (\pi)$ then $j\notin I$ is forced. 
+    \item If $\rootFunction{I^j}{j}\in \Ninv(\omega)$ then clearly $j\in I$ is forced. Otherwise $Q_{[m]\smallsetminus I}$ would not be a reduced expression of $\omega$.
+    \item If $\rootFunction{I^j}{j}\in \Inv(\omega) \cap \Inv (\pi)$ then $j\notin I$ is forced. 
     Otherwise we would have an inversion of $\pi$ in the root configuration, which contradicts $\pi \in \linearExtensions(I)$.
-    \item[(3)(a)] If $\rootFunction{I^j}{j}\in \Inv(w) \cap \Ninv (\pi)$ and $Q_{[m]\smallsetminus I^{j-1}\smallsetminus \{j\}}$ contains a reduced expression of $w$ with prefix $Q^{j-1}$ then $j\in I^j$ is forced.
+    \item[(3)(a)] If $\rootFunction{I^j}{j}\in \Inv(\omega) \cap \Ninv (\pi)$ and $Q_{[m]\smallsetminus I^{j-1}\smallsetminus \{j\}}$ contains a reduced expression of $\omega$ with prefix $Q^{j-1}$ then $j\in I^j$ is forced.
 
     We argue this by contradiction. 
-    Assume $j\notin I^j$ ($j\notin I$). Let $I_1=\sweepingAlgorithm(Q,w,\pi)$ and $I_2=I$. Applying \cref{lem_negativeroot}, we deduce that $\beta=\rootFunction{I^j}{j}=\rootFunction{I}{j}$ satisfies 
+    Assume $j\notin I^j$ ($j\notin I$).
+Let $I_1=\sweepingAlgorithm(Q,\omega,\pi)$ and $I_2=I$.
+Applying \cref{lem_negativeroot}, we deduce that $\beta=\rootFunction{I^j}{j}=\rootFunction{I}{j}$ satisfies
     \[
@@
     But $\beta \in \Ninv(\pi)$. This contradicts $\pi\in \linearExtensions(I)$.
-    \item[(3)(b)]  If $\rootFunction{I^j}{j}\in \Inv(w) \cap \Ninv (\pi)$ and $Q_{[m]\smallsetminus I^{j-1}\smallsetminus \{j\}}$ does not contain a reduced expression of $w$ with prefix $Q^{j-1}$ then $j\notin I^j$ is forced.
-Otherwise, the complement of $I$ would not be a reduced expression of $w$.
-    \item[(4)] If $\rootFunction{I^j}{j}\in -\Inv(w)$ then $j\in I^j$ is clearly forced. Otherwise, the complement of $I$ would not be a reduced expression.
+    \item[(3)(b)]  If $\rootFunction{I^j}{j}\in \Inv(\omega) \cap \Ninv (\pi)$ and $Q_{[m]\smallsetminus I^{j-1}\smallsetminus \{j\}}$ does not contain a reduced expression of $\omega$ with prefix $Q^{j-1}$ then $j\notin I^j$ is forced.
+Otherwise, the complement of $I$ would not be a reduced expression of $\omega$.
+    \item[(4)] If $\rootFunction{I^j}{j}\in -\Inv(\omega)$ then $j\in I^j$ is clearly forced. Otherwise, the complement of $I$ would not be a reduced expression.
 \end{enumerate}
@@
 \begin{remark}
-    Although the sweeping algorithm produces a facet $I=\sweepingAlgorithm(Q,w,\pi)$ for every~$w\in W$, in some cases we have $\pi \notin \linearExtensions(I)$. 
-    This happens because of Case~\eqref{sweeping_case1}, when a non-inversion~$\beta\in \Ninv(w)$ of $w$ is added to the root configuration $\Roots(I)$, such that~$\beta \notin \Ninv(\pi)$.
-This is only potentially possible when $\pi \notin [e,w]$.
+    Although the sweeping algorithm produces a facet $I=\sweepingAlgorithm(Q,\omega,\pi)$ for every~$\omega\in W$, in some cases we have $\pi \notin \linearExtensions(I)$. 
+    This happens because of Case~\eqref{sweeping_case1}, when a non-inversion~$\beta\in \Ninv(\omega)$ of $\omega$ is added to the root configuration $\Roots(I)$, such that~$\beta \notin \Ninv(\pi)$.
+This is only potentially possible when $\pi \notin [e,\omega]$.
 \end{remark}
-
-\subsection{The subword complex congruence conjecture}\cesarm{To do: meet to discuss about this section? put it in final form...}
-By \cref{cor_linearextensions_partition}, the set $\linearExtensions(Q,w)$ of linear extensions of all facets of $\subwordComplex(Q,w)$ can be written as
-\begin{align*}
-    \linearExtensions(Q,w) =
-    \bigsqcup_{I\in\subwordAcyclicFacets(Q,w)} \linearExtensions(I).
-\end{align*}
-This partition determines a natural equivalence relation on the set $\linearExtensions(Q,w)$.
-
-\begin{definition}
-For a non-empty subword complex $\subwordComplex(Q,w)$, the \defn{subword complex congruence} is the equivalence relation~$\equiv_{Q,w}$ on the set $\linearExtensions(Q,w)\subseteq W$ of linear extensions  of all facets of $\subwordComplex(Q,w)$ determined by $\pi \equiv_{Q,w} \pi'$ if and only if $\pi$ and $\pi'$ are linear extensions of the same facet.
-\end{definition}
-
-By \cref{thm_subword_linearextensions_B}, if $Q$ contains a reduced expression for $\wo$, this gives an equivalence relation on the interval $[e,w]$ of the week order.
-We say that a word $Q$ is \defn{alternating} if all non-commuting pairs $s, t\in S$ alternate within $Q$.
-The following conjecture is supported by extensive computer computations.\cesarm{Noemie: in which cases did you check this conjecture? Type $A_n$ for n=???, B,C,D,....?}
-
-\begin{conjecture}
-Let $Q$ be an alternating word which contains a reduced expression for $\wo$.
-For any~$w\in W$, the subword complex congruence~$\equiv_{Q,w}$ is a lattice congruence of the interval~$[e,w]$ of the weak order.
-\end{conjecture}
-\cesarm{Do we have more conjectures or questions to be included here?}
-
-\begin{remark}\label{rem_acyclicflipposet_not_latticequotient}
-In analogy to the case of pipe dreams in \cref{subsec:proofCongruence}, one might expect that the quotient~$[e,\omega]/\equiv_{Q,w}$ is isomorphic to the restriction of the increasing flip poset of $\subwordComplex(Q,w)$ to the set of acyclic facets.
-But this is not the case as shown in \cref{ex_acyclicflip_not_weakorder_related}.     
-\end{remark}
-
-\begin{example}\label{ex_acyclicflip_not_weakorder_related}
-    Let $W=S_3$ be the symmetric group generated by simple transpositions $S=\{s_1,s_2\}$ with $s_i=(i, i+1 )$.
-Let $Q=(s_1,s_2,s_1,s_2,s_1,s_2)$ and $w=\wo=s_1s_2s_1=s_2s_1s_2$.
-The subword complex $\subwordComplex(Q,w)$ has eight facets, six of which are acyclic.
-    All the fibers of $\equiv_{Q,w}$ are singletons and the lattice quotient~$[e,\omega]/\equiv_{Q,w}$ coincides with the weak order of type $A_2$.
-    On the other hand there are two facets, $I_1=\{1,3,4\}$ and $I_2=\{3,4,6\}$, which are connected by a flip but whose corresponding elements $\pi_1$ and $\pi_2$ are not related in weak order.
-    \cesar{To do: Double check and expand this example in detail. Add figure.}
-\end{example}
-
-As we have seen in \cref{cor_acyclicpipedreams_lattice}, the increasing flip poset of acyclic pipe dreams of any permutation $w$ is a lattice, because it is isomorphic to the lattice quotient~$[e,\omega]/\equiv_\omega$.
-This motivates the following open question for subword complexes.
-
-\begin{question}
-Let $\subwordComplex(Q,w)$ be a non-empty subword complex.
-Is the restriction of the increasing flip poset of $\subwordComplex(Q,w)$ to the set of acyclic facets a lattice?    
-\end{question}
-
-As pointed out in \cref{rem_acyclicflipposet_not_latticequotient},  we can not expect~$[e,\omega]/\equiv_{Q,w}$ to be isomorphic to the restriction of the increasing flip poset of $\subwordComplex(Q,w)$ to the set of acyclic facets.
-\cref{ex_acyclicflip_not_weakorder_related} shows that there are flips between acyclic facets that are not detected by the week order.
-One could expect that there is a natural restriction to a special class of flips that behave nicer, meaning that all of them are identified by the quotient~$[e,\omega]/\equiv_{Q,w}$.
-In our \cref{ex_acyclicflip_not_weakorder_related}, the generalized Chute moves from~\cite{Rubey} do the job, because the flip that is not detected by the week order is exactly the one flip which is not Chute.
-The Chute lattice conjecture~\cite[Conjecture~2.8]{Rubey} might be an indication that this is the right direction to look at.
 

### 2023-01-18 acyclicFacets/draft/latticePipeDreams.tex
modifications conjectures

--- 2023-01-18 acyclicFacets/draft/latticePipeDreams.tex
@@
 \newtheorem{lemma}[theorem]{Lemma}
+\newtheorem*{conjecture*}{Conjecture}
 \newtheorem{conjecture}[theorem]{Conjecture}
+\crefname{conjecture}{Conjecture}{Conjectures}
 
@@
 \newcommand{\linearExtensions}{\mathcal{L}} % linear extensions
+\newcommand{\strictLinearExtensions}{\mathcal{L}^\star} % strict linear extensions
 \newcommand{\noninversions}[2]{\mathsf{ninv}(#1,#2)} % non-inversions
@@
 \newcommand{\subwordFacets}{\mathcal{F}} % subword complex
-\newcommand{\subwordAcyclicFacets}{\mathcal{F}^\mathrm{ac}} % subword complex
+\newcommand{\subwordAcyclicFacets}{\mathcal{F}^\bullet} % subword complex
+\newcommand{\subwordStrictAcyclicFacets}{\mathcal{F}^\star} % subword complex
 \newcommand{\greedyFacet}{I^{\overleftarrow{gr}}} % greedy facet
@@
 \newcommand{\sweepingAlgorithm}{\mathsf{sweep}} % sweeping algorithm
+\newcommand{\brickPolyhedron}{\mathsf{Brick}} % brick polyhedron
 
@@
 \item the equivalence relation defined by this partition is a lattice congruence of~$[e, \omega]$, that we call the pipe dream congruence (\cref{subsec:pipeDreamCongruence}),
-\item the Hasse diagram of the corresponding lattice quotient is the increasing flip graph on acyclic pipe dreams with exiting permutation~$\omega$ (\cref{subsec:pipeDreamQuotient}).
+\item the Hasse diagram of the corresponding lattice quotient is isomorphic to the increasing flip graph on acyclic pipe dreams with exiting permutation~$\omega$ (\cref{subsec:pipeDreamQuotient}).
 \end{itemize}
@@
 \begin{theorem*}
-For any permutation~$\omega$, the increasing flip graph on acyclic pipe dreams with exiting permutation~$\omega$ is the Hasse diagram of the lattice quotient of the interval~$[e,\omega]$ of the weak order by the pipe dream congruence of~$\omega$.
+For any permutation~$\omega$, the Hasse diagram of the lattice quotient of the interval~$[e,\omega]$ of the weak order by the pipe dream congruence of~$\omega$ is isomorphic to the increasing flip graph on acyclic pipe dreams with exiting permutation~$\omega$.
 \end{theorem*}
@@
 
-\begin{conjecture}
+\begin{conjecture*}
 For any sorting and alternating word~$Q$ and any~$\omega \in W$, the
@@
 the subword complex congruence~$\equiv_{Q,\omega}$ is a lattice congruence of the interval~$[e,\omega]$ of the weak order.
-\end{conjecture}
+\end{conjecture*}
 
@@
 \label{thm:pipeDreamQuotient}
-The increasing flip graph on~$\acyclicPipeDreams(\omega)$ is isomorphic to the Hasse diagram of the lattice quotient~$[e,\omega]/{\equiv_\omega}$.
+The Hasse diagram of the lattice quotient~$[e,\omega]/{\equiv_\omega}$ is isomorphic to the increasing flip graph on~$\acyclicPipeDreams(\omega)$.
 \end{theorem}
@@
 \[
-\rootFunction{I}{k} \eqdef \prod Q_{[k-1]\smallsetminus I}(\alpha_{q_k}).
+\rootFunction{I}{k} \eqdef \prod Q_{[k-1]\ssm I}(\alpha_{q_k}).
 \]
@@
 \item $i \in I$ is flippable if and only if $\pm \rootFunction{I}{i} \in \Inv(\omega)$.
-\item If $i \in I$ is flippable, it can be flipped to the unique $j\in [m]\smallsetminus I$ such that $\rootFunction{I}{j} = \pm\rootFunction{I}{i}$.
+\item If $i \in I$ is flippable, it can be flipped to the unique $j\in [m]\ssm I$ such that $\rootFunction{I}{j} = \pm\rootFunction{I}{i}$.
 The flip is increasing ($i<j$) when $\rootFunction{I}{i}\in \Phi^+$ and decreasing ($i>j$) when $\rootFunction{I}{i}\in \Phi^-$.
 \label{lem:rootFunctionFlips2}
-\item If $I'=I\smallsetminus \{i\}\cap \{i'\}$ is a facet obtained from $I$ by flipping $i$ to $i'$ with $i<i'$, then
-\[
-\rootFunction{I'}{k} = 
+\item If $I$ and $J$ are two facets related by a flip, with $I \ssm \{i\} = J \ssm  \{j\}$ and $i < j$, then
+\[
+\rootFunction{J}{k} = 
 \begin{cases}
-s_\beta(\rootFunction{I}{k}), & \text{for } i < k \leq i' \\
+s_\beta(\rootFunction{I}{k}), & \text{for } i < k \leq j \\
 \rootFunction{I}{k}, & \text{otherwise}
@@
 \]
-where $\beta=\rootFunction{I}{i}$ and $s_\beta\in W$ is the reflection orthogonal to the root $\beta$.
+where $\beta \eqdef \rootFunction{I}{i}$ and $s_\beta\in W$ is the reflection orthogonal to the root $\beta$.
 \label{lem:rootFunctionFlips3}
@@
 \[
-\Inv(\pi') =\Inv(\pi) \smallsetminus \{\beta\}
+\Inv(\pi') =\Inv(\pi) \ssm \{\beta\}
 \qquad\text{and}\qquad
@@
 \begin{align*}
-    \pi'(\Phi^+) = \pi(\Phi^+) \smallsetminus \{-\beta\} \cup \{\beta\}.
+    \pi'(\Phi^+) = \pi(\Phi^+) \ssm \{-\beta\} \cup \{\beta\}.
 \end{align*}
@@
 \[
-\pi(\Phi^+) \smallsetminus \{-\beta\} = \pi'(\Phi^+) \smallsetminus \{\beta\} = \pi(\Phi^+) \cap \pi'(\Phi^+).
+\pi(\Phi^+) \ssm \{-\beta\} = \pi'(\Phi^+) \ssm \{\beta\} = \pi(\Phi^+) \cap \pi'(\Phi^+).
 \]
@@
 In this case, 
-$\Roots(I)\subseteq \pi(\Phi^+) \smallsetminus \{-\beta\} \subseteq \pi'(\Phi^+)$.
+$\Roots(I)\subseteq \pi(\Phi^+) \ssm \{-\beta\} \subseteq \pi'(\Phi^+)$.
 Taking $I'=I$, we have 
@@
 The positions of the other $\beta$'s and $-\beta$'s all belong to~$I$, and can all be flipped to $i$ (see \cref{lem:rootFunctionFlips}~\eqref{lem:rootFunctionFlips2}).   
-In particular, the position $j$ of the last $-\beta$ belongs to $I$, and it can be flipped to $i$ creating a new facet $I'=I\smallsetminus \{j\} \cap \{i\}$.
+In particular, the position $j$ of the last $-\beta$ belongs to $I$, and it can be flipped to $i$ creating a new facet $I'=I\ssm \{j\} \cap \{i\}$.
 
@@
 \end{equation}
-By  \cref{lem:rootFunctionFlips}~\eqref{lem:rootFunctionFlips3}, we obtain that flipping $j$ to $i$ creates the new facet $I' = I \smallsetminus \{j\} \cap \{i\}$ whose corresponding restricted list looks like
+By  \cref{lem:rootFunctionFlips}~\eqref{lem:rootFunctionFlips3}, we obtain that flipping $j$ to $i$ creates the new facet $I' = I \ssm \{j\} \cap \{i\}$ whose corresponding restricted list looks like
 \begin{equation}
@@
 \[
-\pi'(\Phi^+) \smallsetminus \{\beta\} = \pi(\Phi^+) \smallsetminus \{-\beta\} = \pi(\Phi^+) \cap \pi'(\Phi^+).
+\pi'(\Phi^+) \ssm \{\beta\} = \pi(\Phi^+) \ssm \{-\beta\} = \pi(\Phi^+) \cap \pi'(\Phi^+).
 \]
@@
 
-Since $\linearExtensions(I)\neq \varnothing$ if and only if $I$ is acyclic by \cref{lem:linearExtensionsAcyclic}, we have the following straight forward corollary.
-
-\begin{corollary}\label{coro:linearExtensionsPartitionSubwordComplexes}
+Since $\linearExtensions(I)\neq \varnothing$ if and only if $I$ is acyclic by \cref{lem:linearExtensionsAcyclic}, and~$\linearExtensions(I) \ne \linearExtensions(J)$ for~$I \ne J$ by \cref{thm:linearExtensionsPartitionSubwordComplexA}~\eqref{item:partition}, we have the following straight forward corollary.
+
+\begin{corollary}
+\label{coro:linearExtensionsPartitionSubwordComplexes}
 For any word~$Q$ and element~$\omega$,
@@
 
-\begin{proposition}[{\cite{JahnStump}}]\label{prop_jahnStump_intersection}
+\begin{proposition}[{\cite{JahnStump}}]
+\label{prop:intersectionRootConfigurations}
 If the word $Q$ is sorting, then 
@@
 \begin{proof}[Proof of \cref{thm:linearExtensionsPartitionSubwordComplexB}]
-If $\pi \in \linearExtensions(I)$ for some facet~$I$ of~$\subwordComplex(Q, \omega)$, then by \cref{prop_jahnStump_intersection} we have 
+If $\pi \in \linearExtensions(I)$ for some facet~$I$ of~$\subwordComplex(Q, \omega)$, then by \cref{prop:intersectionRootConfigurations} we have 
 \[
@@
 In this section, we present two conjectural generalizations of the results of \cref{subsec:pipeDreamCongruence,subsec:pipeDreamQuotient}.
-We first introduce the analogue of \cref{def:pipeDreamCongruence} for subword complexes.
+By \cref{coro:linearExtensionsPartitionSubwordComplexes}, we have
+\[
+\linearExtensions(Q,\omega) = \bigsqcup_{I \in \subwordAcyclicFacets(Q, \omega)} \linearExtensions(I)
+\]
+which naturally defines an equivalence relation on~$\linearExtensions(Q,\omega)$.
+However, this equivalence relation is in general not a lattice congruence for two obvious reasons:
+\begin{enumerate}[(i)]
+\item while~$\linearExtensions(Q,\omega)$ is a lower set of the weak order containing~$[e, \omega]$ by \cref{thm:linearExtensionsPartitionSubwordComplexA}, it does not always coincides with~$[e, \omega]$ by \cref{rem:linearExtensionsPartitionSubwordComplexA}, and in fact it does not necessarily have a maximal element, hence it is not necessarily a lattice,
+\item while the sets~$\linearExtensions(I)$ are always order convex in the weak order by \cref{thm:linearExtensionsPartitionSubwordComplexA}~\eqref{item:convex}, they are not necessarily intervals in the weak order by \cref{rem:linearExtensionsPartitionSubwordComplexA}.
+\end{enumerate}
+To bypass Issue~(i), we could restrict our attention to the situation when the word~$Q$ is sorting by~\cref{thm:linearExtensionsPartitionSubwordComplexB} (we will do that in \cref{conj:latticeQuotientSortingAlternating}).
+Here, we want to be slightly more general, so we will instead consider general words~$Q$, but restrict our attention to the interval~$[e, \omega]$ as follows.
+For a facet~$I$ of~$\subwordComplex(Q, \omega)$, we define~$\strictLinearExtensions(I) \eqdef \linearExtensions(I) \cap [e, \omega]$.
+We say that~$I$ is \defn{strictly acyclic}~$\strictLinearExtensions(I) \ne \varnothing$, and we denote by~$\subwordStrictAcyclicFacets(Q, \omega)$ the set of strictly acyclic facets of~$\subwordComplex(Q, \omega)$.
+Note that by \cref{thm:linearExtensionsPartitionSubwordComplexA}~\eqref{item:partition}, we have
+\[
+[e, \omega] = \bigsqcup_{I\in\subwordStrictAcyclicFacets(Q,\omega)} \strictLinearExtensions(I).
+\]
+We can thus now define the analogue of the pipe dream congruence of \cref{def:pipeDreamCongruence} for subword complexes as follows.
 
@@
 \label{def:pipeDreamCongruenceSubwordComplexes}
-For a non-empty subword complex $\subwordComplex(Q,\omega)$, the \defn{subword complex congruence} is the equivalence relation~$\equiv_{Q,\omega}$ on the set~$\linearExtensions(Q,\omega) \eqdef \sqcup_{I \in \subwordAcyclicFacets(Q, \omega)} \linearExtensions(I)$  whose equivalence classes are the sets~$\linearExtensions(I)$ of linear extensions of the acyclic facets~$I$ of~$\subwordComplex(Q, \omega)$.
+For a non-empty subword complex $\subwordComplex(Q,\omega)$, the \defn{subword complex congruence} is the equivalence relation~$\equiv_{Q,\omega}$ on the interval~$[e, \omega]$  whose equivalence classes are the sets~$\strictLinearExtensions(I)$ of linear extensions of strictly acyclic facets~$I$ of~$\subwordStrictAcyclicFacets(Q, \omega)$.
 In other words, $\pi \equiv_{Q,\omega} \pi'$ if and only if $\pi$ and $\pi'$ are linear extensions of the same facet.  
@@
 
-Note that the subword complex congruence indeed defines an equivalence relation by \cref{coro:linearExtensionsPartitionSubwordComplexes}.
-However, it is in general not a lattice congruence for two obvious reasons:
+Despite its name, this equivalence relation is not always a congruence because of Issue~(ii) above.
+To fix it, we now assume that the word~$Q$ is \defn{alternating}, meaning that all non-commuting pairs $s, t\in S$ alternate within $Q$ (this notion was already considered in \cite{PilaudSantos-brickPolytope, CeballosLabbeStump}).
+This enables us to state our first conjecture, intended to extend~\cref{thm:pipeDreamCongruence}.
+
+\begin{conjecture}
+\label{conj:latticeCongruenceAlternating}
+For a non-empty subword complex $\subwordComplex(Q,\omega)$ where~$Q$ is alternating, the subword complex congruence~$\equiv_{Q,\omega}$ is a lattice congruence of the interval~$[e,\omega]$ of the weak order.
+\end{conjecture}
+
+We now intend to understand the quotient~$[e, \omega]/\equiv_{Q, \omega}$.
+First, its elements correspond to the congruence classes of~$\equiv_{Q, \omega}$, hence to the strictly acyclic facets in~$\subwordStrictAcyclicFacets(Q, \omega)$.
+The cover relations are certain increasing flips between the facets in~$\subwordStrictAcyclicFacets(Q, \omega)$.
+However, in contrast to \cref{thm:pipeDreamQuotient}, not all increasing flips between two facets in~$\subwordStrictAcyclicFacets(Q, \omega)$ yields a cover relation of~$\subwordStrictAcyclicFacets(Q, \omega)$, as illustrated by the following example.
+
+\begin{example}\label{ex_acyclicflip_not_weakorder_related}
+\vincent{work this out}
+    Let $W=S_3$ be the symmetric group generated by simple transpositions $S=\{s_1,s_2\}$ with $s_i=(i, i+1 )$.
+Let $Q=(s_1,s_2,s_1,s_2,s_1,s_2)$ and $\omega=\wo=s_1s_2s_1=s_2s_1s_2$.
+The subword complex $\subwordComplex(Q,\omega)$ has eight facets, six of which are acyclic.
+    All the fibers of $\equiv_{Q,\omega}$ are singletons and the lattice quotient~$[e,\omega]/\equiv_{Q,\omega}$ coincides with the weak order of type $A_2$.
+    On the other hand there are two facets, $I_1=\{1,3,4\}$ and $I_2=\{3,4,6\}$, which are connected by a flip but whose corresponding elements $\pi_1$ and $\pi_2$ are not related in weak order.
+    \cesar{To do: Double check and expand this example in detail. Add figure.}
+\end{example}
+
+We say that a flip between two facets~$I, J \in \subwordStrictAcyclicFacets(Q, \omega)$ with~$I \ssm \{i\} = J \ssm \{j\}$ is \defn{extremal} if the root~$\rootFunction{I}{i}$ is a ray of the root configuration~$\Roots(I)$ (or equivalently, $\rootFunction{J}{j}$ is a ray~$\Roots(J)$).
+This enables us to state our second conjecture, intended to extend~\cref{thm:pipeDreamQuotient}.
+
+\begin{conjecture}
+\label{conj:latticeQuotientAlternating}
+For a non-empty subword complex $\subwordComplex(Q,\omega)$ where~$Q$ is alternating, the Hasse diagram of the lattice quotient~$[e, \omega]/\equiv_{Q, \omega}$ is isomorphic to the graph of extremal increasing flips between strictly acyclic facets of~$\subwordStrictAcyclicFacets(Q, \omega)$.
+\end{conjecture}
+
+\cref{conj:latticeCongruenceAlternating,conj:latticeQuotientAlternating} holds in type~$A_n$: our specific proof of~\cref{thm:pipeDreamCongruence,thm:pipeDreamQuotient} can be extended to arbitrary alternating words in type~$A_n$ as will be shown in~\cite{Cartier}.
+They are also supported by computer experiments: we verified it for all alternating words of length at most~$\ell(\wo)$ in types~$B_2, B_3, D_4$ and~$H_3$.
+\vincent{Noemie check that.}
+
+We now specialize \cref{conj:latticeCongruenceAlternating,conj:latticeQuotientAlternating} to the case of sorting and alternating words.
+In this case, all acyclic facets are strictly acyclic by \cref{thm:linearExtensionsPartitionSubwordComplexB}.
+Note that this is precisely the situation we had in~\cref{sec:latticeAcyclicPipeDreams}.
+
+\begin{conjecture}
+\label{conj:latticeQuotientSortingAlternating}
+For a non-empty subword complex $\subwordComplex(Q,\omega)$ where~$Q$ is sorting and alternating, the Hasse diagram of the lattice quotient~$[e, \omega]/\equiv_{Q, \omega}$ is isomorphic to the graph of extremal increasing flips between acyclic facets of~$\subwordAcyclicFacets(Q, \omega)$.
+\end{conjecture}
+
+Moreover, there is a close connection with the brick polyhedra introduced in~\cite{JahnStump} as generalizations of the brick polytopes of~\cite{PilaudSantos-brickPolytope, PilaudStump-brickPolytope}.
+We refer to the original papers~\cite{PilaudSantos-brickPolytope, PilaudStump-brickPolytope, JahnStump} for a definition of these polyhedra.
+We just need to know here that the brick polyhedron~$\brickPolyhedron(Q, \omega)$~has
 \begin{itemize}
-\item while~$\linearExtensions(Q,\omega)$ is a lower set of the weak order containing~$[e, \omega]$ by \cref{thm:linearExtensionsPartitionSubwordComplexA}, it does not necessarily have a maximal element, hence it is not necessarily a lattice,
-\item while the sets~$\linearExtensions(I)$ are always order convex in the weak order by \cref{thm:linearExtensionsPartitionSubwordComplexA}~\eqref{item:convex}, they are not necessarily intervals in the weak order by \cref{rem:linearExtensionsPartitionSubwordComplexA}.
+\item a vertex for each acyclic facet of~$\subwordAcyclicFacets(Q, \omega)$, and
+\item an edge for each extremal flip between two acyclic facets,
 \end{itemize}
-These two issues can however be bypassed with additional assumptions on the word~$Q$.
-Recall that a word~$Q$ is
-\begin{itemize}
-\item \defn{sorting} if it contains a reduced expression of $\wo$ (see just before \cref{thm:linearExtensionsPartitionSubwordComplexB}),
-\item \defn{alternating} if all non-commuting pairs $s, t\in S$ alternate within $Q$ (see \cite{PilaudSantos-brickPolytope, CeballosLabbeStump}).
-\end{itemize}
-By \cref{thm:linearExtensionsPartitionSubwordComplexB}, $\linearExtensions(Q,\omega) = [e, \omega]$ if $Q$ is sorting.
+and that the graph of extremal increasing flips on acyclic facets is isomorphic to the finite part (meaning forgetting the unbounded rays) of the graph of the brick polyhedron~$\brickPolyhedron(Q, \omega)$ oriented in a suitable direction~$\delta$.
+This can be derived from \cite[Thm.~4.4]{JahnStump}.
+\cref{conj:latticeQuotientSortingAlternating} can thus be translated geometrically as follows.
 
 \begin{conjecture}
-If the word~$Q$ is sorting and alternating, then for any~$\omega \in W$, the subword complex congruence~$\equiv_{Q,\omega}$ is a lattice congruence of the interval~$[e,\omega]$ of the weak order.
+\label{conj:latticeQuotientSortingAlternatingGeometric}
+For a non-empty subword complex $\subwordComplex(Q,\omega)$ where~$Q$ is sorting and alternating, the finite part of the oriented graph of the brick polyhedron~$\brickPolyhedron(Q, \omega)$ is isomorphic to the Hasse diagram of the lattice quotient~$[e, \omega]/\equiv_{Q, \omega}$.
 \end{conjecture}
-
-This conjecture holds in type~$A_n$: our specific proof of~\cref{thm:pipeDreamCongruence} can be extended to arbitrary sorting and alternating words in type~$A_n$ as shown in~\cite{Cartier}.
-It is also supported by extensive computer experiments: we verified it in types...
-\cesarm{Noemie: in which cases did you check this conjecture? Type $A_n$ for n=???, B,C,D,....?}
 
@@
 \label{subsec:sweepingAlgorithmSubwordComplexes}
+\vincent{I have not checked this part yet.}
 
@@
 At position $j\in [m]$ we produce a new set $I^j$ obtained from the previous one $I^{j-1}$ by either adding $j$ or not, according to certain rules.
-We let $Q^j=Q_{[j]\smallsetminus I^j}$ and denote by
-    \[
-    \rootFunction{I^j}{k} = \prod Q_{[k-1]\smallsetminus I^j}(\alpha_{q_k}).
+We let $Q^j=Q_{[j]\ssm I^j}$ and denote by
+    \[
+    \rootFunction{I^j}{k} = \prod Q_{[k-1]\ssm I^j}(\alpha_{q_k}).
     \]
@@
     \begin{enumerate}
-        \item If $Q_{[m]\smallsetminus I^{j-1}\smallsetminus \{j\}}$ contains a reduced expression of $\omega$ with prefix $Q^{j-1}$ then let 
+        \item If $Q_{[m]\ssm I^{j-1}\ssm \{j\}}$ contains a reduced expression of $\omega$ with prefix $Q^{j-1}$ then let 
         \[
@@
 \begin{proof}
-    Let $I^j$ and $Q^j=Q_{[j]\smallsetminus I^j}$ be as defined in the sweeping algorithm for $\pi$. 
+    Let $I^j$ and $Q^j=Q_{[j]\ssm I^j}$ be as defined in the sweeping algorithm for $\pi$. 
     The proposition follows by applying the following claim for $j=m$.
@@
 
-    {\bf Claim}: $Q^j$ is a reduced expression which is the prefix of a reduced expression of $\omega$ in $Q_{[m]\smallsetminus I^j}$.
+    {\bf Claim}: $Q^j$ is a reduced expression which is the prefix of a reduced expression of $\omega$ in $Q_{[m]\ssm I^j}$.
 
@@
     For $j=0$, $Q^0$ is the empty word which is reduced by definition.
-    Furthermore, $Q_{[m]\smallsetminus I^0 }=Q$ contains a reduced expression of $\omega$ because the subword complex is non-empty.
+    Furthermore, $Q_{[m]\ssm I^0 }=Q$ contains a reduced expression of $\omega$ because the subword complex is non-empty.
 The empty word is a prefix of this reduced expression.
@@
     $Q^j=Q^{j-1}$, which is reduced by induction hypothesis.
-    Moreover, it is a prefix of a reduced expression of $\omega$ in $Q_{[m]\smallsetminus I^{j-1}}$.
-    Since $\rootFunction{I^j}{j}\in \Ninv(\omega)$, this reduced expression can not use the letter $q_j$; so, it is a reduced expression of $\omega$ in $Q_{[m]\smallsetminus I^{j}}$ as desired.
+    Moreover, it is a prefix of a reduced expression of $\omega$ in $Q_{[m]\ssm I^{j-1}}$.
+    Since $\rootFunction{I^j}{j}\in \Ninv(\omega)$, this reduced expression can not use the letter $q_j$; so, it is a reduced expression of $\omega$ in $Q_{[m]\ssm I^{j}}$ as desired.
     \item If $\rootFunction{I^j}{j}\in \Inv(\omega) \cap \Inv (\pi)$ then $Q^j= Q^{j-1}\circ (q_j)$, which is a reduced expression because~$Q^{j-1}$ is reduced and $\rootFunction{I^j}{j}\in \Inv(\omega)$.
 
-    Now let $\widetilde Q$ be a subword of $Q_{[m]\smallsetminus I^{j-1}}=Q_{[m]\smallsetminus I^{j}}$ which is a reduced expression of $\omega$ with prefix $Q^{j-1}$, and let $\widetilde I$ be the corresponding facet.
+    Now let $\widetilde Q$ be a subword of $Q_{[m]\ssm I^{j-1}}=Q_{[m]\ssm I^{j}}$ which is a reduced expression of $\omega$ with prefix $Q^{j-1}$, and let $\widetilde I$ be the corresponding facet.
 
@@
 
-    \item[(3)(a)] If $\rootFunction{I^j}{j}\in \Inv(\omega) \cap \Ninv (\pi)$ and $Q_{[m]\smallsetminus I^{j-1}\smallsetminus \{j\}}$ contains a reduced expression of $\omega$ with prefix $Q^{j-1}$, then $Q^j=Q^{j-1}$.
+    \item[(3)(a)] If $\rootFunction{I^j}{j}\in \Inv(\omega) \cap \Ninv (\pi)$ and $Q_{[m]\ssm I^{j-1}\ssm \{j\}}$ contains a reduced expression of $\omega$ with prefix $Q^{j-1}$, then $Q^j=Q^{j-1}$.
     Therefore, $Q^j$ is reduced and it is a prefix of a reduced expression of $\omega$ in 
-    $Q_{[m]\smallsetminus I^{j-1}\smallsetminus \{j\}}=Q_{[m]\smallsetminus I^j}$.
+    $Q_{[m]\ssm I^{j-1}\ssm \{j\}}=Q_{[m]\ssm I^j}$.
 
@@
     \[
-I_2\cap [j] = I_1\cap [j] \smallsetminus \{j\}
+I_2\cap [j] = I_1\cap [j] \ssm \{j\}
     \]
@@
 \begin{enumerate}
-    \item If $\rootFunction{I^j}{j}\in \Ninv(\omega)$ then clearly $j\in I$ is forced. Otherwise $Q_{[m]\smallsetminus I}$ would not be a reduced expression of $\omega$.
+    \item If $\rootFunction{I^j}{j}\in \Ninv(\omega)$ then clearly $j\in I$ is forced. Otherwise $Q_{[m]\ssm I}$ would not be a reduced expression of $\omega$.
     \item If $\rootFunction{I^j}{j}\in \Inv(\omega) \cap \Inv (\pi)$ then $j\notin I$ is forced. 
     Otherwise we would have an inversion of $\pi$ in the root configuration, which contradicts $\pi \in \linearExtensions(I)$.
-    \item[(3)(a)] If $\rootFunction{I^j}{j}\in \Inv(\omega) \cap \Ninv (\pi)$ and $Q_{[m]\smallsetminus I^{j-1}\smallsetminus \{j\}}$ contains a reduced expression of $\omega$ with prefix $Q^{j-1}$ then $j\in I^j$ is forced.
+    \item[(3)(a)] If $\rootFunction{I^j}{j}\in \Inv(\omega) \cap \Ninv (\pi)$ and $Q_{[m]\ssm I^{j-1}\ssm \{j\}}$ contains a reduced expression of $\omega$ with prefix $Q^{j-1}$ then $j\in I^j$ is forced.
 
@@
     But $\beta \in \Ninv(\pi)$. This contradicts $\pi\in \linearExtensions(I)$.
-    \item[(3)(b)]  If $\rootFunction{I^j}{j}\in \Inv(\omega) \cap \Ninv (\pi)$ and $Q_{[m]\smallsetminus I^{j-1}\smallsetminus \{j\}}$ does not contain a reduced expression of $\omega$ with prefix $Q^{j-1}$ then $j\notin I^j$ is forced.
+    \item[(3)(b)]  If $\rootFunction{I^j}{j}\in \Inv(\omega) \cap \Ninv (\pi)$ and $Q_{[m]\ssm I^{j-1}\ssm \{j\}}$ does not contain a reduced expression of $\omega$ with prefix $Q^{j-1}$ then $j\notin I^j$ is forced.
 Otherwise, the complement of $I$ would not be a reduced expression of $\omega$.

### 2023-01-20 acyclicFacets/draft/latticePipeDreams.tex
improve intro + conjectures

@@
 \newcommand{\C}{\mathbb{C}} % set of summands
+\renewcommand{\b}[1]{\boldsymbol{#1}} % bold
 
@@
 \definecolor{darkgreen}{RGB}{57,181,74} % darkgreen color
-\renewcommand{\b}[1]{{\color{blue} #1}} % blue
-\renewcommand{\r}[1]{{\color{red} #1}} % red
-\newcommand{\g}[1]{{\color{darkgreen} #1}} % green
+\newcommand{\blue}[1]{{\color{blue} #1}} % blue
+\newcommand{\red}[1]{{\color{red} #1}} % red
+\newcommand{\green}[1]{{\color{darkgreen} #1}} % green
 \newcommand{\defn}[1]{\textbf{\textsf{\color{PineGreen} #1}}} % emphasis of a definition
@@
 They are grouped according to their exiting permutation, given by the order in which the pipes appear along the horizontal axis.
-The pipes in a pipe dream have some crossings and some contacts, and the contact graph records all contacts of a pipe dream.
-A flip in a pipe dream exchanges a contact between with a crossing between two pipes, and the flip is increasing when the contact is southeast of the crossing involved in the flip.
-The acyclic pipe dreams are the pipe dreams with an acyclic contact graph, and they naturally appear in the study of brick polytopes~\cite{PilaudSantos-brickPolytope}.
+The linear extensions of a pipe dream are the permutations of its pipes such that for each contact the northwest pipe appears before the southeast pipe in the permutation.
+The pipe dreams with at least one linear extension are called acyclic and naturally appear in the study of brick polytopes~\cite{PilaudSantos-brickPolytope}.
+A flip in a pipe dream exchanges a contact with a crossing between two pipes, and the flip is increasing when the contact is southwest of the crossing involved in the flip.
 A brief recollection on pipe dreams is given in \cref{sec:preliminaries}.
@@
 
-Finally, we discuss in \cref{sec:subwordComplexes} a conjectural extension of our results to subword complexes in finite Coxeter groups~\cite{KnutsonMiller-subwordComplex}.
+Finally, we discuss in \cref{sec:subwordComplexes} (partly conjectural) extensions of our results to subword complexes in finite Coxeter groups~\cite{KnutsonMiller-subwordComplex}.
+Given a finite Coxeter group~$W$ with simple reflections~$S$, a word~$Q$ on~$S$ and an element~$\omega$ of~$W$, the subword complex~$\subwordComplex(Q,\omega)$ is a simplicial complex whose facets are the complements of the reduced expressions of~$\omega$ inside the word~$Q$.
+Pipe dreams can be seen as facets of subword complexes for special words~$Q$ on the simple transpositions of the symmetric groups.
+In general, there is again a natural increasing flip graph on the facets of a subword complex, which was studied in particular in~\cite{PilaudStump-ELlabelings}.
+An important tool to understand this flip is the root function introduced in~\cite{CeballosLabbeStump}, which associates a root~$\rootFunction{I}{i}$ to each position~$i$ and each facet~$I$, and the root configuration~$\Roots(I)$ of a facet~$I$, which collects all roots~$\rootFunction{I}{i}$ at positions~$i$ in~$I$.
+A brief recollection on finite Coxeter systems and subword complexes is given in \cref{subsec:finiteCoxeterGroups,subsec:subwordComplexes}.
+
+We consider the set~$\linearExtensions(I)$ of linear extensions of a facet~$I$ of~$\subwordComplex(Q,\omega)$, that is the set of elements~$\pi$ of~$W$ such that~${\Roots(I) \subseteq \pi(\Phi^+)}$.
+We prove the following statement in \cref{subsec:twoTheorems}.
+
+\begin{theorem*}
+For any non-empty subword complex~$\subwordComplex(Q, \omega)$, the sets~$\linearExtensions(I)$ for all facets~$I$ of~$\subwordComplex(Q, \omega)$ are order convex and form a partition of a lower set of the weak order that contains the interval~$[e, \omega]$.
+\end{theorem*}
+
+In contrast to the case of pipe dreams, there are some subword complexes and some facets for which the interval~$[e, \omega]$ does not contain (even sometimes does not intersect) the set of linear extensions~$\linearExtensions(I)$.
+However, there is a large family of subword complexes for which this cannot happen.
+We say that~$Q$ is sorting if it contains a reduced expression for~$\wo$.
+
+\begin{theorem*}
+If~$Q$ is sorting, then the sets~$\linearExtensions(I)$ for all facets~$I$ of~$\subwordComplex(Q, \omega)$ form a partition of the interval~$[e, \omega]$.
+\end{theorem*}
+
+In the case when~$[e, \omega]$ does not contain all sets of linear extensions, it is natural to consider the restriction of this partition to~$[e, \omega]$ by the sets~$[e, \omega] \cap \linearExtensions(\omega)$.
+This defines an equivalence relation~$\equiv_{Q, \omega}$ on~$[e, \omega]$ that we call the subword complex congruence.
+However, as the sets of linear extensions are not always intervals of the weak order, this equivalence relation is not always a lattice congruence.
+This can seems to be fixed by an additional assumption on~$Q$.
+We say that~$Q$ is alternating when all non-commuting pairs $s, t\in S$ alternate within $Q$ (this notion was already considered in \cite{PilaudSantos-brickPolytope, CeballosLabbeStump}).
 
 \begin{conjecture*}
-For any sorting and alternating word~$Q$ and any~$\omega \in W$, the
-
-the subword complex congruence~$\equiv_{Q,\omega}$ is a lattice congruence of the interval~$[e,\omega]$ of the weak order.
+If~$Q$ is alternating, then the subword complex congruence~$\equiv_{Q, \omega}$ is a lattice congruence of the interval~$[e, \omega]$ of the weak order.
 \end{conjecture*}
+
+In contrast to the case of pipe dreams, the Hasse diagram of the quotient~$[e, \omega]/{\equiv_{Q, \omega}}$ is not isomorphic to the increasing flip graph on acyclic facets of~$\subwordComplex(Q, \omega)$ for two reasons:
+\vincent{refer to the examples...}
+\begin{itemize}
+\item First, not all acyclic facets of~$\subwordComplex(Q, \omega)$ appear as vertices of~$[e, \omega]/{\equiv_{Q, \omega}}$.
+We say that a facet is strongly acyclic if~$[e, \omega] \cap \linearExtensions(\omega) \ne \varnothing$.
+\item Second, not all flips between two strongly acyclic facets of~$\subwordComplex(Q, \omega)$ define a cover relation of~$[e, \omega]/{\equiv_{Q, \omega}}$.
+We say that the flip of a position~$i$ in a facet~$I$ is external if the root~$\rootFunction{I}{i}$ directing the flip is a ray of the root configuration~$\Roots(I)$.
+\end{itemize}
+This leads us to the following conjecture.
+
+\begin{conjecture*}
+If~$Q$ is alternating, then the Hasse diagram of the lattice quotient~$[e, \omega]/\equiv_{Q, \omega}$ is isomorphic to the graph of extremal increasing flips between strongly acyclic facets of~$\subwordAcyclicFacets(Q, \omega)$.
+\end{conjecture*}
+
+Combining the sorting and alternating conditions, we thus obtain the following conjecture, which can be seen as the natural extension of our pipe dream result.
+
+\begin{conjecture*}
+If~$Q$ is sorting and alternating, then the Hasse diagram of the lattice quotient~$[e, \omega]/\equiv_{Q, \omega}$ is isomorphic to the graph of extremal increasing flips between acyclic facets of~$\subwordAcyclicFacets(Q, \omega)$.
+\end{conjecture*}
+
+This last conjecture has a close connection to the brick polytopes of~\cite{PilaudSanto-brickPolytope, PilaudStump-brickPolytope} and the brick polyhedra of~\cite{JahnStump}.
+\vincent{todo}
 
@@
 \begin{example}
-\vincent{todo}
-Type A
+\label{exm:typeACoxeterSystem}
+The Coxeter system of type~$A_{n-1}$ is the symmetric group~$W = \fS_n$ with generators~$S = \set{\tau_i}{i \in [n-1]}$, where~$\tau_i$ is the simple transposition~$\tau_i = (i \; i+1)$.
+It naturally acts on~$\R^n$ by permutations of coordinates.
+Denoting by~$(\b{e}_i)_{i \in [n]}$ the canonical basis of~$\R^n$, the type~$A_{n-1}$ roots are all~$\b{r}_{i,j} \eqdef \b{e}_i - \b{e}_j$ for distinct~$i,j \in [n]$, with positive roots~$\b{r}_{i,j}$ for~$1 \le i < j \le n$ and simple roots~$\b{r}_{i,i+1}$ for~$i \in [n-1]$.
+The inversion set of~$\pi \in \fS_n$ is the set of roots~$\b{e}_i - \b{e}_j$ for the inversions~$(i,j)$ of the permutation~$\pi$.
+The longest element is the reversed permutation~$[n, n-1, \dots, 2, 1]$ (written in one line notation), and it admits the reduced expression~$\tau_1 \cdots \tau_{n-1} \tau_1 \cdots \tau_{n-2} \cdots \tau_1 \tau_2 \tau_1$.
 \end{example}
@@
 \begin{example}
-\vincent{todo}
-Connection root configuration --- contact graph.
+\label{exm:typeARootConfiguration}
+Continuing \cref{exm:typeACoxeterSystem}, we consider the type~$A_n$ Coxeter system, the word $Q \eqdef \tau_1 \cdots \tau_{n-1} \tau_1 \cdots \tau_{n-2} \cdots \tau_1 \tau_2 \tau_1$, and a permutation~$\omega \in \fS_n$.
+The word~$Q$ naturally fits on an $n \times n$ triangular grid (place $\tau_k$ in all boxes with row~$i$ and column~$j$ such that~$i+j+k = n+1$) and each facet~$I$ of the subword complex~$\subwordComplex(Q, \omega)$ corresponds to a pipe dreams~$P_I$ of~$\pipeDreams(\omega)$ (replace each position in~$I$ by a contact in~$P_I$, and the other positions by crossings in~$P_I$).
+The root function is given~$\rootFunction{I}{i} = \b{r}_{p,q} \eqdef \b{e}_p - \b{e}_q$ where~$p$ is the pipe arriving from the west and $q$ is the pipe arriving from the south at the box of~$P_I$ corresponding to position~$i$ of~$Q$.
+Hence, the root configuration is the incidence configuration~$\Roots(I) = \bigset{\b{r}_{p,q}}{(p,q) \in P_I\contact}$ of the contact graph of~$P_I$.
+In particular, the acyclic facets of~$\subwordComplex(Q, \omega)$ correspond to the acyclic pipe dreams of~$\acyclicPipeDreams(\omega)$.
 \end{example}
@@
 We now introduce the analogue of \cref{def:linearExtensions} for subword complexes.
-\vincent{Is linear extension a good term? Should we say $W$-extension?}.
+\vincent{Is linear extension a good term? Should we say $W$-extension?}
 
@@
 \begin{example}
-%The concept of linear extensions of acyclic facets of subword complexes are a natural generalization of linear extensions of contact graphs of acyclic pipe dreams that we introduced in \cref{subsec:linearExtensions}.
-Connection linear extensions of contact graphs.
+In the situation of \cref{exm:typeACoxeterSystem,exm:typeARootConfiguration}, the linear extensions of a facet~$I$ of~$\subwordComplex(Q, \omega)$ are precisely the linear extensions of the pipe dream~$P_I$ of~$\pipeDreams(\omega)$.
 \end{example}
@@
 \begin{example}\label{ex_acyclicflip_not_weakorder_related}
+Consider the type~$A_2$ Coxeter system, the word~$Q = \tau_1 \tau_2 \tau_1 \tau_2 \tau_1 \tau_2$ and the longest element~$\wo = \tau_1 \tau_2 \tau_1 = \tau_2 \tau_1 \tau_2$.
+
 \vincent{work this out}

### 2023-01-20 acyclicFacets/draft/latticePipeDreams.tex
improve intro

@@
 
-\title{The lattice of acyclic pipe dreams}
+\title{Lattices of acyclic pipe dreams}
 
@@
 % theorems
-\newtheorem*{theorem*}{Theorem}
 \newtheorem{theorem}{Theorem}[section]
+\newtheorem{theoremA}{Theorem}
+\renewcommand{\thetheoremA}{\Alph{theoremA}}
 \newtheorem{corollary}[theorem]{Corollary}
@@
 \newtheorem{lemma}[theorem]{Lemma}
-\newtheorem*{conjecture*}{Conjecture}
 \newtheorem{conjecture}[theorem]{Conjecture}
+\newtheorem{conjectureA}{Conjecture}
+\renewcommand{\theconjectureA}{\Alph{conjectureA}}
 \crefname{conjecture}{Conjecture}{Conjectures}
@@
 
-\begin{theorem*}
+\begin{theoremA}
 For any permutation~$\omega$, the Hasse diagram of the lattice quotient of the interval~$[e,\omega]$ of the weak order by the pipe dream congruence of~$\omega$ is isomorphic to the increasing flip graph on acyclic pipe dreams with exiting permutation~$\omega$.
-\end{theorem*}
+\end{theoremA}
 
@@
 
-\begin{theorem*}
+\begin{theoremA}
 For any non-empty subword complex~$\subwordComplex(Q, \omega)$, the sets~$\linearExtensions(I)$ for all facets~$I$ of~$\subwordComplex(Q, \omega)$ are order convex and form a partition of a lower set of the weak order that contains the interval~$[e, \omega]$.
-\end{theorem*}
+\end{theoremA}
 
@@
 
-\begin{theorem*}
+\begin{theoremA}
 If~$Q$ is sorting, then the sets~$\linearExtensions(I)$ for all facets~$I$ of~$\subwordComplex(Q, \omega)$ form a partition of the interval~$[e, \omega]$.
-\end{theorem*}
+\end{theoremA}
 
@@
 
-\begin{conjecture*}
+\begin{conjectureA}
 If~$Q$ is alternating, then the subword complex congruence~$\equiv_{Q, \omega}$ is a lattice congruence of the interval~$[e, \omega]$ of the weak order.
-\end{conjecture*}
+\end{conjectureA}
 
 In contrast to the case of pipe dreams, the Hasse diagram of the quotient~$[e, \omega]/{\equiv_{Q, \omega}}$ is not isomorphic to the increasing flip graph on acyclic facets of~$\subwordComplex(Q, \omega)$ for two reasons:
-\vincent{refer to the examples...}
 \begin{itemize}
-\item First, not all acyclic facets of~$\subwordComplex(Q, \omega)$ appear as vertices of~$[e, \omega]/{\equiv_{Q, \omega}}$.
+\item First, not all acyclic facets of~$\subwordComplex(Q, \omega)$ appear as vertices of~$[e, \omega]/{\equiv_{Q, \omega}}$ (see \cref{rem:linearExtensionsPartitionSubwordComplexA}).
 We say that a facet is strongly acyclic if~$[e, \omega] \cap \linearExtensions(\omega) \ne \varnothing$.
-\item Second, not all flips between two strongly acyclic facets of~$\subwordComplex(Q, \omega)$ define a cover relation of~$[e, \omega]/{\equiv_{Q, \omega}}$.
+\item Second, not all flips between two strongly acyclic facets of~$\subwordComplex(Q, \omega)$ define a cover relation of~$[e, \omega]/{\equiv_{Q, \omega}}$ (see \cref{exm:acyclicFlipvsWeakOrder}).
 We say that the flip of a position~$i$ in a facet~$I$ is external if the root~$\rootFunction{I}{i}$ directing the flip is a ray of the root configuration~$\Roots(I)$.
@@
 
-\begin{conjecture*}
-If~$Q$ is alternating, then the Hasse diagram of the lattice quotient~$[e, \omega]/\equiv_{Q, \omega}$ is isomorphic to the graph of extremal increasing flips between strongly acyclic facets of~$\subwordAcyclicFacets(Q, \omega)$.
-\end{conjecture*}
+\begin{conjectureA}
+If~$Q$ is alternating, then the Hasse diagram of the quotient~$[e, \omega]/\equiv_{Q, \omega}$ is isomorphic to the graph of extremal increasing flips between strongly acyclic facets of~$\subwordAcyclicFacets(Q, \omega)$.
+\end{conjectureA}
 
@@
 
-\begin{conjecture*}
-If~$Q$ is sorting and alternating, then the Hasse diagram of the lattice quotient~$[e, \omega]/\equiv_{Q, \omega}$ is isomorphic to the graph of extremal increasing flips between acyclic facets of~$\subwordAcyclicFacets(Q, \omega)$.
-\end{conjecture*}
-
-This last conjecture has a close connection to the brick polytopes of~\cite{PilaudSanto-brickPolytope, PilaudStump-brickPolytope} and the brick polyhedra of~\cite{JahnStump}.
-\vincent{todo}
+\begin{conjectureA}
+If~$Q$ is sorting and alternating, then the Hasse diagram of the quotient~$[e, \omega]/\equiv_{Q, \omega}$ is isomorphic to the graph of extremal increasing flips between acyclic facets of~$\subwordAcyclicFacets(Q, \omega)$.
+\end{conjectureA}
+
+This last conjecture has a strong connection to the geometry of subword complexes given by brick polytopes of~\cite{PilaudSantos-brickPolytope, PilaudStump-brickPolytope} and the brick polyhedra of~\cite{JahnStump}.
+Namely, the extremal increasing flips between acyclic facets of~$\subwordAcyclicFacets(Q, \omega)$ is precisely the bounded part (meaning forgetting the unbounded rays) of the brick polyhedron~$\brickPolyhedron(Q, \omega)$ oriented by a natural linear functional.
+In particular, when~$\omega = \wo$, we obtain the following conjecture, extending results from~\cite{Pilaud-brickAlgebra}.
+
+\begin{conjectureA}
+If~$Q$ is sorting and alternating, the oriented graph of the brick polytope~$\brickPolyhedron(Q, \wo)$ is the Hasse diagram of a lattice quotient of the weak order.
+\end{conjectureA}
 
@@
 
-The \defn{contact graph} of a pipe dream~$P$ is the directed graph~$P\contact$ with one node for each pipe of~$P$ and one arc for each contact of~$P$ connecting the northwest pipe to the southeast pipe of the contact\footnote{We have reversed the usual orientation conventions of \cite{PilaudSantos-brickPolytope, PilaudPocchiola, Pilaud-BrickAlgebra} to suit better our purposes, in particular in \cref{subsec:insertionAlgorithm}.}.
+The \defn{contact graph} of a pipe dream~$P$ is the directed graph~$P\contact$ with one node for each pipe of~$P$ and one arc for each contact of~$P$ connecting the northwest pipe to the southeast pipe of the contact\footnote{We have reversed the usual orientation conventions of \cite{PilaudSantos-brickPolytope, PilaudPocchiola, Pilaud-brickAlgebra} to suit better our purposes, in particular in \cref{subsec:insertionAlgorithm}.}.
 We see equivalently the contact graph~$P\contact$ as a graph on the pipes of~$P$ or on the integers~$[n]$.
@@
 
-Our second algorithm to construct~$\insertion{\pi}{\omega}$ is an \defn{insertion algorithm} inspired from~\cite{Pilaud-BrickAlgebra} and similar to the insertion in binary search trees.
+Our second algorithm to construct~$\insertion{\pi}{\omega}$ is an \defn{insertion algorithm} inspired from~\cite{Pilaud-brickAlgebra} and similar to the insertion in binary search trees.
 
@@
 
-\begin{example}\label{ex_acyclicflip_not_weakorder_related}
+\begin{example}
+\label{exm:acyclicFlipvsWeakOrder}
 Consider the type~$A_2$ Coxeter system, the word~$Q = \tau_1 \tau_2 \tau_1 \tau_2 \tau_1 \tau_2$ and the longest element~$\wo = \tau_1 \tau_2 \tau_1 = \tau_2 \tau_1 \tau_2$.
@@
 In analogy to the case of pipe dreams in \cref{subsec:proofCongruence}, one might expect that the quotient~$[e,\omega]/\equiv_{Q,\omega}$ is isomorphic to the restriction of the increasing flip poset of $\subwordComplex(Q,\omega)$ to the set of acyclic facets.
-But this is not the case as shown in \cref{ex_acyclicflip_not_weakorder_related}.     
+But this is not the case as shown in \cref{exm:acyclicFlipvsWeakOrder}.     
 \end{remark}
 
-\begin{example}\label{ex_acyclicflip_not_weakorder_related}
+\begin{example}\label{exm:acyclicFlipvsWeakOrder}
     Let $W=S_3$ be the symmetric group generated by simple transpositions $S=\{s_1,s_2\}$ with $s_i=(i, i+1 )$.
@@
 As pointed out in \cref{rem_acyclicflipposet_not_latticequotient},  we can not expect~$[e,\omega]/\equiv_{Q,\omega}$ to be isomorphic to the restriction of the increasing flip poset of $\subwordComplex(Q,\omega)$ to the set of acyclic facets.
-\cref{ex_acyclicflip_not_weakorder_related} shows that there are flips between acyclic facets that are not detected by the week order.
+\cref{exm:acyclicFlipvsWeakOrder} shows that there are flips between acyclic facets that are not detected by the week order.
 One could expect that there is a natural restriction to a special class of flips that behave nicer, meaning that all of them are identified by the quotient~$[e,\omega]/\equiv_{Q,\omega}$.
-In our \cref{ex_acyclicflip_not_weakorder_related}, the generalized Chute moves from~\cite{Rubey} do the job, because the flip that is not detected by the week order is exactly the one flip which is not Chute.
+In our \cref{exm:acyclicFlipvsWeakOrder}, the generalized Chute moves from~\cite{Rubey} do the job, because the flip that is not detected by the week order is exactly the one flip which is not Chute.
 The Chute lattice conjecture~\cite[Conjecture~2.8]{Rubey} might be an indication that this is the right direction to look at.

### 2023-01-20 acyclicFacets/draft/latticePipeDreams.tex
wrapping up

@@
 
+\thanks{NC \& VP were partially supported by the French project CHARMS (ANR~19\,CE40\,0017), and by the French\,--\,Austrian project PAGCAP (ANR~21\,CE48\,0020 \& FWF I 5788).}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \newtheorem{conjecture}[theorem]{Conjecture}
+\crefname{conjecture}{Conjecture}{Conjectures}
 \newtheorem{conjectureA}{Conjecture}
 \renewcommand{\theconjectureA}{\Alph{conjectureA}}
-\crefname{conjecture}{Conjecture}{Conjectures}
+\crefname{conjectureA}{Conjecture}{Conjectures}
 
@@
 
-\vspace*{.2cm}
 \maketitle
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\tableofcontents
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Introduction}
+\label{sec:introduction}
 
@@
 They have important connections and applications to various areas related to Schubert calculus and Schubert varieties~\cite{LascouxSchutzenberger-PolynomesSchubert, LascouxSchutzenberger-SchubertLittlewoudRichardson}.
-A pipe dream is an arrangement of pipes in the triangular shape, each entering along the vertical side and exiting along the horizontal side.
+A pipe dream is an arrangement of pipes in the triangular shape, each entering along the vertical side and exiting along the horizontal side (see \cref{fig:pipeDreams}).
 They are grouped according to their exiting permutation, given by the order in which the pipes appear along the horizontal axis.
@@
 The pipe dreams with at least one linear extension are called acyclic and naturally appear in the study of brick polytopes~\cite{PilaudSantos-brickPolytope}.
-A flip in a pipe dream exchanges a contact with a crossing between two pipes, and the flip is increasing when the contact is southwest of the crossing involved in the flip.
+A flip in a pipe dream exchanges a contact with a crossing between two pipes (see \cref{fig:pipeDreams}), and the flip is increasing when the contact is southwest of the crossing involved in the flip.
 A brief recollection on pipe dreams is given in \cref{sec:preliminaries}.
+
+\begin{figure}[t]
+	\centerline{
+		%\input{pipeDreams}
+		\includegraphics[scale=.9]{pipeDreams}
+	}
+	\caption{Two pipe dreams of~$\pipeDreams(1365724)$ connected by an increasing flip (exchanging a contact with the crossing on the two red pipes~$3$ and~$4$).}
+	\label{fig:pipeDreams}
+\end{figure}
 
@@
 \begin{theoremA}
+\label{thm:A}
 For any permutation~$\omega$, the Hasse diagram of the lattice quotient of the interval~$[e,\omega]$ of the weak order by the pipe dream congruence of~$\omega$ is isomorphic to the increasing flip graph on acyclic pipe dreams with exiting permutation~$\omega$.
@@
 
-We then explore in \cref{sec:furtherTopics} some natural further topics.
+We then explore in \cref{sec:furtherTopics} some natural further topics on pipe dreams.
 We describe two algorithms to compute the unique acyclic pipe dream whose linear extensions contain a given permutation generalizing the binary tree insertion map on permutations (\cref{subsec:sweepingAlgorithm,subsec:insertionAlgorithm}), we describe the pipe dream congruence as the transitive closure of a local rewriting rule generalizing that of the sylvester congruence (\cref{subsec:rewritingRule}), and we describe a natural commutative diagram of lattice morphism generalizing the connection between the recoil map and the binary tree insertion map on permutations and the canopy on binary trees (\cref{subsec:canopy}).
@@
 \begin{theoremA}
+\label{thm:B}
 For any non-empty subword complex~$\subwordComplex(Q, \omega)$, the sets~$\linearExtensions(I)$ for all facets~$I$ of~$\subwordComplex(Q, \omega)$ are order convex and form a partition of a lower set of the weak order that contains the interval~$[e, \omega]$.
@@
 \begin{theoremA}
+\label{thm:C}
 If~$Q$ is sorting, then the sets~$\linearExtensions(I)$ for all facets~$I$ of~$\subwordComplex(Q, \omega)$ form a partition of the interval~$[e, \omega]$.
@@
 However, as the sets of linear extensions are not always intervals of the weak order, this equivalence relation is not always a lattice congruence.
-This can seems to be fixed by an additional assumption on~$Q$.
+This seems to be fixed by an additional assumption on~$Q$.
 We say that~$Q$ is alternating when all non-commuting pairs $s, t\in S$ alternate within $Q$ (this notion was already considered in \cite{PilaudSantos-brickPolytope, CeballosLabbeStump}).
@@
 \begin{conjectureA}
+\label{conj:A}
 If~$Q$ is alternating, then the subword complex congruence~$\equiv_{Q, \omega}$ is a lattice congruence of the interval~$[e, \omega]$ of the weak order.
@@
 
-In contrast to the case of pipe dreams, the Hasse diagram of the quotient~$[e, \omega]/{\equiv_{Q, \omega}}$ is not isomorphic to the increasing flip graph on acyclic facets of~$\subwordComplex(Q, \omega)$ for two reasons:
+When~$Q$ is alternating, we can thus consider the quotient~$[e, \omega]/{\equiv_{Q, \omega}}$.
+In contrast to the case of pipe dreams, the Hasse diagram of the quotient~$[e, \omega]/{\equiv_{Q, \omega}}$ is not always isomorphic to the increasing flip graph on acyclic facets of~$\subwordComplex(Q, \omega)$ for two reasons:
 \begin{itemize}
@@
 \begin{conjectureA}
-If~$Q$ is alternating, then the Hasse diagram of the quotient~$[e, \omega]/\equiv_{Q, \omega}$ is isomorphic to the graph of extremal increasing flips between strongly acyclic facets of~$\subwordAcyclicFacets(Q, \omega)$.
+\label{conj:B}
+If~$Q$ is alternating, then the Hasse diagram of the quotient~$[e, \omega]/\equiv_{Q, \omega}$ is isomorphic to the graph of extremal increasing flips between strongly acyclic facets of~$\subwordComplex(Q, \omega)$.
 \end{conjectureA}
 
-Combining the sorting and alternating conditions, we thus obtain the following conjecture, which can be seen as the natural extension of our pipe dream result.
+Combining the sorting and alternating conditions of \cref{thm:B,conj:A,conj:B}, we thus obtain the following conjecture, which can be seen as the natural extension of~\cref{thm:A}.
 
 \begin{conjectureA}
-If~$Q$ is sorting and alternating, then the Hasse diagram of the quotient~$[e, \omega]/\equiv_{Q, \omega}$ is isomorphic to the graph of extremal increasing flips between acyclic facets of~$\subwordAcyclicFacets(Q, \omega)$.
+\label{conj:C}
+If~$Q$ is sorting and alternating, then the Hasse diagram of the quotient~$[e, \omega]/\equiv_{Q, \omega}$ is isomorphic to the graph of extremal increasing flips between acyclic facets of~$\subwordComplex(Q, \omega)$.
 \end{conjectureA}
 
-This last conjecture has a strong connection to the geometry of subword complexes given by brick polytopes of~\cite{PilaudSantos-brickPolytope, PilaudStump-brickPolytope} and the brick polyhedra of~\cite{JahnStump}.
-Namely, the extremal increasing flips between acyclic facets of~$\subwordAcyclicFacets(Q, \omega)$ is precisely the bounded part (meaning forgetting the unbounded rays) of the brick polyhedron~$\brickPolyhedron(Q, \omega)$ oriented by a natural linear functional.
+This last conjecture has a strong connection to the geometry of subword complexes given by brick polytopes~\cite{PilaudSantos-brickPolytope, PilaudStump-brickPolytope} and brick polyhedra~\cite{JahnStump}.
+Namely, the extremal increasing flips between acyclic facets of~$\subwordComplex(Q, \omega)$ is precisely the bounded part (meaning forgetting the unbounded rays) of the brick polyhedron~$\brickPolyhedron(Q, \omega)$ oriented by a natural linear functional.
+\cref{conj:C} thus translates geometrically to the following.
+
+\begin{conjectureA}
+\label{conj:D}
+If~$Q$ is sorting and alternating, then the oriented graph of the brick polyhedron~$\brickPolyhedron(Q, \omega)$ is isomorphic to the Hasse diagram of the lattice quotient~$[e, \omega]/\equiv_{Q, \omega}$.
+\end{conjectureA}
+
 In particular, when~$\omega = \wo$, we obtain the following conjecture, extending results from~\cite{Pilaud-brickAlgebra}.
@@
 \begin{conjectureA}
-If~$Q$ is sorting and alternating, the oriented graph of the brick polytope~$\brickPolyhedron(Q, \wo)$ is the Hasse diagram of a lattice quotient of the weak order.
+\label{conj:E}
+If~$Q$ is sorting and alternating, then the oriented graph of the brick polytope $\brickPolyhedron(Q, \wo)$ is isomorphic to the Hasse diagram of the lattice quotient of the weak order by~$\equiv_{Q, \omega}$.
 \end{conjectureA}
@@
 % We let~$\pipeDreams_n \eqdef \bigsqcup_{\omega \in \fS_n} \pipeDreams(\omega)$ and~$\pipeDreams \eqdef \bigsqcup_{n \in \N} \pipeDreams_n$.
-
-\begin{figure}[ht]
-	\centerline{
-		%\input{pipeDreams}
-		\includegraphics[scale=.9]{pipeDreams}
-	}
-	\caption{Two pipe dreams of~$\pipeDreams(1365724)$ connected by a flip (exchanging a contact with the crossing on the two red pipes~$3$ and~$4$).}
-	\label{fig:pipeDreams}
-\end{figure}
 
@@
 This lattice is defined as the transitive closure of right rotations on binary trees, and is obtained as the quotient of the weak order by the \defn{sylvester congruence}.
-\vincent{Not sure where we want that...}
 An important point here is that all reversing pipe dreams are acyclic, since there contact graphs are (oriented) binary trees.
@@
 
-\section{Further topics}
+\section{Further topics on pipe dreams}
 \label{sec:furtherTopics}
@@
 Our first algorithm to construct~$\insertion{\pi}{\omega}$ is a \defn{sweeping algorithm}, inspired by the algorithm to compute greedy pipe dreams~\cite{PilaudPocchiola, PilaudStump-ELlabelings}.
-Extensions of this algorithm will be discussed in \cref{..}. \vincent{todo. Was this algorithm explicitly somewhere before? We should cite Jahn-Stump later in the paper.}
+An extension of this algorithm to subword complexes will be discussed in \cref{subsec:sweepingAlgorithmSubwordComplexes}, and appeared independently in~\cite{JahnStump}.
 
@@
 %
-\begin{figure}[h]
+\begin{figure}[b]
 	\centerline{\includegraphics[scale=.9]{sweeping}}
@@
 %
-\begin{figure}[t]
+\begin{figure}[b]
 	\centerline{\includegraphics[scale=.9]{insertion}}
@@
 We start with some basic preliminaries on finite Coxeter groups (\cref{subsec:finiteCoxeterGroups}) and subword complexes (\cref{subsec:subwordComplexes}).
-We then define linear extensions of facets of subword complexes (\cref{subsec:linearExtensionsFacets}) and present two theorems (\cref{subsec:twoTheorems}) and two conjectures (\cref{subsec:twoConjectures}) about them.
+We then define linear extensions of facets of subword complexes (\cref{subsec:linearExtensionsFacets}) and present two theorems (\cref{subsec:twoTheorems}) and five conjectures (\cref{subsec:fiveConjectures}) about them.
 To conclude, we present a sweeping algorithm to construct the facet with a given linear extension (\cref{subsec:sweepingAlgorithmSubwordComplexes})
@@
 We now introduce the analogue of \cref{def:linearExtensions} for subword complexes.
-\vincent{Is linear extension a good term? Should we say $W$-extension?}
 
@@
 	\includegraphics[width=0.43\textwidth]{interval_not_contained2}
+	\caption{A facet of a subword complex~$\subwordComplex(Q, \omega)$ whose linear extensions all lie outside the interval~$[e, \omega]$.}
+	\label{fig:outOfInterval}
 \end{figure}
@@
 
-\subsection{Two conjectures on linear extensions of facets}
-\label{subsec:twoConjectures}
+\subsection{Five conjectures on linear extensions of facets}
+\label{subsec:fiveConjectures}
 
@@
 Consider the type~$A_2$ Coxeter system, the word~$Q = \tau_1 \tau_2 \tau_1 \tau_2 \tau_1 \tau_2$ and the longest element~$\wo = \tau_1 \tau_2 \tau_1 = \tau_2 \tau_1 \tau_2$.
-
-\vincent{work this out}
-    Let $W=S_3$ be the symmetric group generated by simple transpositions $S=\{s_1,s_2\}$ with $s_i=(i, i+1 )$.
-Let $Q=(s_1,s_2,s_1,s_2,s_1,s_2)$ and $\omega=\wo=s_1s_2s_1=s_2s_1s_2$.
-The subword complex $\subwordComplex(Q,\omega)$ has eight facets, six of which are acyclic.
-    All the fibers of $\equiv_{Q,\omega}$ are singletons and the lattice quotient~$[e,\omega]/\equiv_{Q,\omega}$ coincides with the weak order of type $A_2$.
-    On the other hand there are two facets, $I_1=\{1,3,4\}$ and $I_2=\{3,4,6\}$, which are connected by a flip but whose corresponding elements $\pi_1$ and $\pi_2$ are not related in weak order.
-    \cesar{To do: Double check and expand this example in detail. Add figure.}
+The subword complex~$\subwordComplex(Q, \wo)$ has eight facets, six of which are acyclic.
+All the fibers of $\equiv_{Q, \wo}$ are singletons and the lattice quotient~$[e, \wo]/\equiv_{Q, \wo}$ coincides with the weak order of type~$A_2$.
+Note that the two acyclic facets~$\{1,3,4\}$ and $\{3,4,6\}$ are connected by a flip but the corresponding classes do not form a cover relation in~$[e, \wo]/\equiv_{Q, \wo}$.
+%
+\begin{figure}[h]
+	\begin{tikzpicture}[xscale=1.5,->]
+	\node (123) at (0,-2.5) {$\{1,2,3\}$};
+	\node (134) at (-1,-1.5) {$\{1,3,4\}$};
+	\node (126) at (0.3,-.5) {$\{1,2,6\}$};
+	\node (236) at (1,-1.5) {$\{2,3,6\}$};
+	\node (145) at (-1,1.5) {$\{1,4,5\}$};
+	\node (156) at (-0.3,.5) {$\{1,5,6\}$};
+	\node (346) at (1,1.5) {$\{3,4,6\}$};
+	\node (456) at (0,2.5) {$\{4,5,6\}$};
+	\draw (123)--(134);
+	\draw (123)--(126);
+	\draw (123)--(236);
+	\draw (134)--(145);
+	\draw (134)--(346);
+	\draw (126)--(156);
+	\draw (126)--(236);
+	\draw (236)--(346);
+	\draw (145)--(456);
+	\draw (145)--(156);
+	\draw (156)--(456);
+	\draw (346)--(456);
+	\end{tikzpicture}
+	\qquad
+	\begin{tikzpicture}[xscale=1.5,->]
+	\node (123) at (0,-2.5) {$\{1,2,3\}$};
+	\node (134) at (-1,-1.5) {$\{1,3,4\}$};
+	\node (236) at (1,-1.5) {$\{2,3,6\}$};
+	\node (145) at (-1,1.5) {$\{1,4,5\}$};
+	\node (346) at (1,1.5) {$\{3,4,6\}$};
+	\node (456) at (0,2.5) {$\{4,5,6\}$};
+	\draw (123)--(134);
+	\draw (123)--(236);
+	\draw (134)--(145);
+	\draw (134)--(346);
+	\draw (236)--(346);
+	\draw (145)--(456);
+	\draw (346)--(456);
+	\end{tikzpicture}
+	\qquad
+	\begin{tikzpicture}[xscale=1.5,->]
+	\node (123) at (0,-2.5) {$\{1,2,3\}$};
+	\node (134) at (-1,-1.5) {$\{1,3,4\}$};
+	\node (236) at (1,-1.5) {$\{2,3,6\}$};
+	\node (145) at (-1,1.5) {$\{1,4,5\}$};
+	\node (346) at (1,1.5) {$\{3,4,6\}$};
+	\node (456) at (0,2.5) {$\{4,5,6\}$};
+	\draw (123)--(134);
+	\draw (123)--(236);
+	\draw (134)--(145);
+	\draw (236)--(346);
+	\draw (145)--(456);
+	\draw (346)--(456);
+	\end{tikzpicture}
+	\caption{The increasing flip graph on~$\subwordComplex(Q, \wo)$ (left), its restriction to acyclic facets (middle) and the Hasse diagram of the quotient~$[e, \wo]/\equiv_{Q, \wo}$ where each class is labeled by its corresponding facet of~$\subwordComplex(Q, \wo)$ (right), for the subword complex~$\subwordComplex(Q, \wo)$ where~$Q = \tau_1 \tau_2 \tau_1 \tau_2 \tau_1 \tau_2$ and~$\wo = \tau_1 \tau_2 \tau_1 = \tau_2 \tau_1 \tau_2$.
+Note that the increasing flip~$\{1,3,4\} \to \{3,4,6\}$ is not a cover relation of~$[e, \wo]/\equiv_{Q, \wo}$.}
+	\label{fig:acyclicFlipvsWeakOrder}
+\end{figure}
 \end{example}
@@
 \label{conj:latticeQuotientSortingAlternating}
-For a non-empty subword complex $\subwordComplex(Q,\omega)$ where~$Q$ is sorting and alternating, the Hasse diagram of the lattice quotient~$[e, \omega]/\equiv_{Q, \omega}$ is isomorphic to the graph of extremal increasing flips between acyclic facets of~$\subwordAcyclicFacets(Q, \omega)$.
+If~$Q$ is sorting and alternating, then the Hasse diagram of the lattice quotient~$[e, \omega]/\equiv_{Q, \omega}$ is isomorphic to the graph of extremal increasing flips between acyclic facets of~$\subwordAcyclicFacets(Q, \omega)$.
 \end{conjecture}
@@
 \begin{conjecture}
-\label{conj:latticeQuotientSortingAlternatingGeometric}
-For a non-empty subword complex $\subwordComplex(Q,\omega)$ where~$Q$ is sorting and alternating, the finite part of the oriented graph of the brick polyhedron~$\brickPolyhedron(Q, \omega)$ is isomorphic to the Hasse diagram of the lattice quotient~$[e, \omega]/\equiv_{Q, \omega}$.
+\label{conj:latticeQuotientSortingAlternatingBrickPolyhedra}
+If~$Q$ is sorting and alternating, then the finite part of the oriented graph of the brick polyhedron~$\brickPolyhedron(Q, \omega)$ is isomorphic to the Hasse diagram of the lattice quotient~$[e, \omega]/\equiv_{Q, \omega}$.
 \end{conjecture}
 
-\vincent{I am working below this line}
-
-\cesarm{To do: meet to discuss about this section? put it in final form...}
-
-cesarm{Do we have more conjectures or questions to be included here?}
-
-\begin{remark}\label{rem_acyclicflipposet_not_latticequotient}
-In analogy to the case of pipe dreams in \cref{subsec:proofCongruence}, one might expect that the quotient~$[e,\omega]/\equiv_{Q,\omega}$ is isomorphic to the restriction of the increasing flip poset of $\subwordComplex(Q,\omega)$ to the set of acyclic facets.
-But this is not the case as shown in \cref{exm:acyclicFlipvsWeakOrder}.     
-\end{remark}
-
-\begin{example}\label{exm:acyclicFlipvsWeakOrder}
-    Let $W=S_3$ be the symmetric group generated by simple transpositions $S=\{s_1,s_2\}$ with $s_i=(i, i+1 )$.
-Let $Q=(s_1,s_2,s_1,s_2,s_1,s_2)$ and $\omega=\wo=s_1s_2s_1=s_2s_1s_2$.
-The subword complex $\subwordComplex(Q,\omega)$ has eight facets, six of which are acyclic.
-    All the fibers of $\equiv_{Q,\omega}$ are singletons and the lattice quotient~$[e,\omega]/\equiv_{Q,\omega}$ coincides with the weak order of type $A_2$.
-    On the other hand there are two facets, $I_1=\{1,3,4\}$ and $I_2=\{3,4,6\}$, which are connected by a flip but whose corresponding elements $\pi_1$ and $\pi_2$ are not related in weak order.
-    \cesar{To do: Double check and expand this example in detail. Add figure.}
-\end{example}
+In particular, specializing this conjecture to the brick polytopes~\cite{PilaudSantos-brickPolytope, PilaudStump-brickPolytope} for which~$\omega = \wo$, we obtain our last conjecture, intended to extend the results of~\cite{Pilaud-brickAlgebra}.
+
+\begin{conjecture}
+\label{conj:latticeQuotientSortingAlternatingBrickPolytopes}
+If~$Q$ is sorting and alternating, then the oriented graph of the brick polytope~$\brickPolyhedron(Q, \wo)$ is isomorphic to the Hasse diagram of a lattice quotient of the weak order.
+\end{conjecture}
+
+\vincent{I want to delete the remaining of this section, but I want to discuss it with Cesar.}
 
@@
 \vincent{I have not checked this part yet.}
+\vincent{Here, we must properly cite \cite{JahnStump} and say that we obtained this algorithm independently.}
 

### 2023-01-28 acyclicFacets/draft/latticePipeDreams.tex
improve

@@
 \newcommand{\linearExtensions}{\mathcal{L}} % linear extensions
-\newcommand{\strictLinearExtensions}{\mathcal{L}^\star} % strict linear extensions
+\newcommand{\strongLinearExtensions}{\mathcal{L}^\star} % strict linear extensions
 \newcommand{\noninversions}[2]{\mathsf{ninv}(#1,#2)} % non-inversions
@@
 \newcommand{\subwordAcyclicFacets}{\mathcal{F}^\bullet} % subword complex
-\newcommand{\subwordStrictAcyclicFacets}{\mathcal{F}^\star} % subword complex
+\newcommand{\subwordStronglyAcyclicFacets}{\mathcal{F}^\star} % subword complex
 \newcommand{\greedyFacet}{I^{\overleftarrow{gr}}} % greedy facet
@@
 The \defn{contact graph} of a pipe dream~$P$ is the directed graph~$P\contact$ with one node for each pipe of~$P$ and one arc for each contact of~$P$ connecting the northwest pipe to the southeast pipe of the contact\footnote{We have reversed the usual orientation conventions of \cite{PilaudSantos-brickPolytope, PilaudPocchiola, Pilaud-brickAlgebra} to suit better our purposes, in particular in \cref{subsec:insertionAlgorithm}.}.
-We see equivalently the contact graph~$P\contact$ as a graph on the pipes of~$P$ or on the integers~$[n]$.
-We say that a pipe dream~$P$ is \defn{acyclic} if its contact graph~$P\contact$ is acyclic (no oriented cycle).
-We then denote by~$\contactLess{P}$ the transitive closure of the contact graph of~$P$.
+We see equivalently the contact graph~$P\contact$ as a (multi)graph on the pipes of~$P$ or on the integers~$[n]$.
+We say that a pipe dream~$P$ is \defn{acyclic} if its contact graph~$P\contact$ has no oriented cycle.
+For an acyclic pipe dream~$P$, we denote by~$\contactLess{P}$ the transitive closure of the contact graph of~$P$.
 For~$\omega \in \fS_n$, we denote by~$\acyclicPipeDreams(\omega)$ the set of acyclic pipe dreams of~$\pipeDreams(\omega)$.
@@
 \cref{fig:bijection} illustrates explicit bijections between reversing pipe dreams of~$\pipeDreams(\rho_n)$, binary trees with $n$ internal nodes, and the triangulations of a convex $(n+2)$-gon.
-More precisely, the map which sends a contact in row~$i$ and column~$j$ of the triangular shape to the diagonal~$[i,n+1-j]$ of the~$(n+2)$-gon provides the following correspondence: \\[.3cm]
+More precisely, the map which sends a contact in row~$i$ and column~$j$ of the triangular shape (indexed from~$0$ to~$n+1$) to the diagonal~$[i,n+1-j]$ of the~$(n+2)$-gon provides the following correspondence: \\[.3cm]
 \centerline{
@@
 
-Two facets $I,J \in \subwordFacets(Q,\omega)$ are connected by a \defn{flip} if they differ one element: $I \ssm \{i\} = J \ssm \{j\}$ for some $i\in I$ and $j\in J$ with $i \ne j$.
+It is known that~$\subwordComplex(Q,\omega)$ is either a ball or a sphere, in particular it is a pseudomanifold (with or without boundary).
+The flip graph of~$\subwordComplex(Q,\omega)$ is the graph whose vertices are the facets of~$\subwordComplex(Q,\omega)$ and whose edges are the ridges of~$\subwordComplex(Q,\omega)$.
+In other words, two facets $I,J \in \subwordFacets(Q,\omega)$ are connected by a \defn{flip} if they differ one element: $I \ssm \{i\} = J \ssm \{j\}$ for some $i\in I$ and $j\in J$ with~$i \ne j$.
 The flip from $I$ to $J$ is called \defn{increasing} if~$i < j$, and \defn{decreasing} otherwise.
@@
 In particular, the acyclic facets of~$\subwordComplex(Q, \omega)$ correspond to the acyclic pipe dreams of~$\acyclicPipeDreams(\omega)$.
+\end{example}
+
+\begin{example}
+For any Coxeter group~$W$ and any Coxeter element~$c \in W$ (a product of all generators of~$S$ in a given arbitrary order), let~$\wo(c)$ denote the $c$-sorting word of~$\wo$ (the lexicographically minimal reduced expression for~$\wo$ in~$c^\infty$, see \cite{Reading-CambrianLattices} for details).
+Extending the observation of \cref{exm:Tamari1}, it was shown in~\cite{CeballosLabbeStump} that the subword complex~$\subwordComplex(c\wo(c), \wo)$ is isomorphic to the cluster complex of type~$W$.
+In particular, the increasing flip graph is the Hasse diagram of the $c$-Cambrian lattice of~\cite{Reading-CambrianLattices}.
+\end{example}
+
+\begin{example}
+\label{exm:counterExampleLattice}
+In contrast to the previous example, consider the word~$Q = \tau_1 \tau_2 \tau_3 \tau_2 \tau_1 \tau_2 \tau_3 \tau_2 \tau_1$ on the simple generators of the symmetric group~$\fS_4$ and the subword complex~$\subwordComplex(Q,\wo)$.
+Note that all facets in this subword complex are acyclic.
+It is shown in~\cite[Rem.~5.12]{PilaudStump-brickPolytope} that its increasing flip poset is not a lattice.
+This shows that neither the increasing flip poset, nor the acyclic increasing flip poset are lattices in general, even in type~$A$. \vincent{clean that}
 \end{example}
@@
 
-In this section, we present two conjectural generalizations of the results of \cref{subsec:pipeDreamCongruence,subsec:pipeDreamQuotient}.
+In this section, we present conjectural generalizations of the results of \cref{subsec:pipeDreamCongruence,subsec:pipeDreamQuotient}.
 By \cref{coro:linearExtensionsPartitionSubwordComplexes}, we have
@@
 Here, we want to be slightly more general, so we will instead consider general words~$Q$, but restrict our attention to the interval~$[e, \omega]$ as follows.
-For a facet~$I$ of~$\subwordComplex(Q, \omega)$, we define~$\strictLinearExtensions(I) \eqdef \linearExtensions(I) \cap [e, \omega]$.
-We say that~$I$ is \defn{strictly acyclic}~$\strictLinearExtensions(I) \ne \varnothing$, and we denote by~$\subwordStrictAcyclicFacets(Q, \omega)$ the set of strictly acyclic facets of~$\subwordComplex(Q, \omega)$.
+For a facet~$I$ of~$\subwordComplex(Q, \omega)$, we define~$\strongLinearExtensions(I) \eqdef \linearExtensions(I) \cap [e, \omega]$.
+We say that~$I$ is \defn{strongly acyclic}~$\strongLinearExtensions(I) \ne \varnothing$, and we denote by~$\subwordStronglyAcyclicFacets(Q, \omega)$ the set of strongly acyclic facets of~$\subwordComplex(Q, \omega)$.
 Note that by \cref{thm:linearExtensionsPartitionSubwordComplexA}~\eqref{item:partition}, we have
 \[
-[e, \omega] = \bigsqcup_{I\in\subwordStrictAcyclicFacets(Q,\omega)} \strictLinearExtensions(I).
+[e, \omega] = \bigsqcup_{I\in\subwordStronglyAcyclicFacets(Q,\omega)} \strongLinearExtensions(I).
 \]
@@
 \label{def:pipeDreamCongruenceSubwordComplexes}
-For a non-empty subword complex $\subwordComplex(Q,\omega)$, the \defn{subword complex congruence} is the equivalence relation~$\equiv_{Q,\omega}$ on the interval~$[e, \omega]$  whose equivalence classes are the sets~$\strictLinearExtensions(I)$ of linear extensions of strictly acyclic facets~$I$ of~$\subwordStrictAcyclicFacets(Q, \omega)$.
+For a non-empty subword complex $\subwordComplex(Q,\omega)$, the \defn{subword complex congruence} is the equivalence relation~$\equiv_{Q,\omega}$ on the interval~$[e, \omega]$  whose equivalence classes are the sets~$\strongLinearExtensions(I)$ of linear extensions of strongly acyclic facets~$I$ of~$\subwordStronglyAcyclicFacets(Q, \omega)$.
 In other words, $\pi \equiv_{Q,\omega} \pi'$ if and only if $\pi$ and $\pi'$ are linear extensions of the same facet.  
@@
 We now intend to understand the quotient~$[e, \omega]/\equiv_{Q, \omega}$.
-First, its elements correspond to the congruence classes of~$\equiv_{Q, \omega}$, hence to the strictly acyclic facets in~$\subwordStrictAcyclicFacets(Q, \omega)$.
-The cover relations are certain increasing flips between the facets in~$\subwordStrictAcyclicFacets(Q, \omega)$.
-However, in contrast to \cref{thm:pipeDreamQuotient}, not all increasing flips between two facets in~$\subwordStrictAcyclicFacets(Q, \omega)$ yields a cover relation of~$\subwordStrictAcyclicFacets(Q, \omega)$, as illustrated by the following example.
+First, its elements correspond to the congruence classes of~$\equiv_{Q, \omega}$, hence to the strongly acyclic facets in~$\subwordStronglyAcyclicFacets(Q, \omega)$.
+The cover relations are certain increasing flips between the facets in~$\subwordStronglyAcyclicFacets(Q, \omega)$.
+However, in contrast to \cref{thm:pipeDreamQuotient}, not all increasing flips between two facets in~$\subwordStronglyAcyclicFacets(Q, \omega)$ yields a cover relation of~$\subwordStronglyAcyclicFacets(Q, \omega)$, as illustrated by the following example.
 
@@
 	\draw (126)--(156);
-	\draw (126)--(236);
+	\draw (236)--(126);
 	\draw (236)--(346);
 	\draw (145)--(456);
-	\draw (145)--(156);
+	\draw (156)--(145);
 	\draw (156)--(456);
@@
 
-We say that a flip between two facets~$I, J \in \subwordStrictAcyclicFacets(Q, \omega)$ with~$I \ssm \{i\} = J \ssm \{j\}$ is \defn{extremal} if the root~$\rootFunction{I}{i}$ is a ray of the root configuration~$\Roots(I)$ (or equivalently, $\rootFunction{J}{j}$ is a ray~$\Roots(J)$).
+We say that a flip between two facets~$I, J \in \subwordStronglyAcyclicFacets(Q, \omega)$ with~$I \ssm \{i\} = J \ssm \{j\}$ is \defn{extremal} if the root~$\rootFunction{I}{i}$ is a ray of the root configuration~$\Roots(I)$ (or equivalently, $\rootFunction{J}{j}$ is a ray~$\Roots(J)$).
 This enables us to state our second conjecture, intended to extend~\cref{thm:pipeDreamQuotient}.
@@
 \label{conj:latticeQuotientAlternating}
-For a non-empty subword complex $\subwordComplex(Q,\omega)$ where~$Q$ is alternating, the Hasse diagram of the lattice quotient~$[e, \omega]/\equiv_{Q, \omega}$ is isomorphic to the graph of extremal increasing flips between strictly acyclic facets of~$\subwordStrictAcyclicFacets(Q, \omega)$.
+For a non-empty subword complex $\subwordComplex(Q,\omega)$ where~$Q$ is alternating, the Hasse diagram of the lattice quotient~$[e, \omega]/\equiv_{Q, \omega}$ is isomorphic to the graph of extremal increasing flips between strongly acyclic facets of~$\subwordStronglyAcyclicFacets(Q, \omega)$.
 \end{conjecture}
 
-\cref{conj:latticeCongruenceAlternating,conj:latticeQuotientAlternating} holds in type~$A_n$: our specific proof of~\cref{thm:pipeDreamCongruence,thm:pipeDreamQuotient} can be extended to arbitrary alternating words in type~$A_n$ as will be shown in~\cite{Cartier}.
-They are also supported by computer experiments: we verified it for all alternating words of length at most~$\ell(\wo)$ in types~$B_2, B_3, D_4$ and~$H_3$.
-\vincent{Noemie check that.}
-
 We now specialize \cref{conj:latticeCongruenceAlternating,conj:latticeQuotientAlternating} to the case of sorting and alternating words.
-In this case, all acyclic facets are strictly acyclic by \cref{thm:linearExtensionsPartitionSubwordComplexB}.
+In this case, all acyclic facets are strongly acyclic by \cref{thm:linearExtensionsPartitionSubwordComplexB}.
 Note that this is precisely the situation we had in~\cref{sec:latticeAcyclicPipeDreams}.
@@
 \end{conjecture}
+
+\begin{remark}
+\cref{conj:latticeCongruenceAlternating,conj:latticeQuotientAlternating,conj:latticeQuotientSortingAlternating,conj:latticeQuotientSortingAlternatingBrickPolyhedra,conj:latticeQuotientSortingAlternatingBrickPolytopes} holds in type~$A_n$: our specific proof of~\cref{thm:pipeDreamCongruence,thm:pipeDreamQuotient} can be extended to arbitrary alternating words in type~$A_n$ as will be shown in~\cite{Cartier}.
+They are also supported by computer experiments: we verified \cref{conj:latticeCongruenceAlternating,conj:latticeQuotientAlternating} for all alternating words of length at most~$\ell(\wo)$ (hence \cref{conj:latticeQuotientSortingAlternating,conj:latticeQuotientSortingAlternatingBrickPolyhedra,conj:latticeQuotientSortingAlternatingBrickPolytopes} for all alternating reduced expressions of~$\wo$) in types~$B_2, B_3, D_4$ and~$H_3$.
+\end{remark}
 

### 2023-01-31 acyclicFacets/draft/latticePipeDreams.tex
Nantel: small typo in Fig 1

@@
 	}
-	\caption{Two pipe dreams of~$\pipeDreams(1365724)$ connected by an increasing flip (exchanging a contact with the crossing on the two red pipes~$3$ and~$4$).}
+	\caption{Two pipe dreams of~$\pipeDreams(1365724)$ connected by an increasing flip (exchanging a contact with the crossing on the two red pipes~$4$ and~$5$).}
 	\label{fig:pipeDreams}

### 2023-03-08 acyclicFacets/draft/latticePipeDreams.tex
sweeping algorithm

--- 2023-01-28 acyclicFacets/draft/latticePipeDreams.tex
@@
 We refer to~\cite{BjornerBrenti, Humphreys} for detailed references on Coxeter groups. 
-We consider a \defn{finite root system} $\Phi$ with \defn{positive roots}~$\Phi^+$, \defn{negative roots}~$\Phi^+-$, and \defn{simple roots} $\Delta \subseteq \Phi^+$.
+We consider a \defn{finite root system} $\Phi$ with \defn{positive roots}~$\Phi^+$, \defn{negative roots}~$\Phi^-$, and \defn{simple roots} $\Delta \subseteq \Phi^+$.
 The reflections along the hyperplanes orthogonal to the roots in $\Phi$ generate a \defn{finite Coxeter group} $W$.
@@
 These two special facets are called the \defn{greedy facet} $\greedyFacet$ and the \defn{antigreedy facet} $\antiGreedyFacet$.
-They are the lexicographically smallest and largest facets of $\subwordComplex(Q,\pi)$, respectively.
+They are the lexicographically smallest and largest facets of $\subwordComplex(Q,\pi)$.
 The \defn{increasing flip poset} is the transitive closure of the increasing flip graph.
@@
 Continuing \cref{exm:typeACoxeterSystem}, we consider the type~$A_n$ Coxeter system, the word $Q \eqdef \tau_1 \cdots \tau_{n-1} \tau_1 \cdots \tau_{n-2} \cdots \tau_1 \tau_2 \tau_1$, and a permutation~$\omega \in \fS_n$.
-The word~$Q$ naturally fits on an $n \times n$ triangular grid (place $\tau_k$ in all boxes with row~$i$ and column~$j$ such that~$i+j+k = n+1$) and each facet~$I$ of the subword complex~$\subwordComplex(Q, \omega)$ corresponds to a pipe dreams~$P_I$ of~$\pipeDreams(\omega)$ (replace each position in~$I$ by a contact in~$P_I$, and the other positions by crossings in~$P_I$).
+The word~$Q$ naturally fits on an $n \times n$ triangular grid (place $\tau_k$ in all boxes with row~$i$ and column~$j$ such that~$i+j+k = n+1$) and each facet~$I$ of the subword complex~$\subwordComplex(Q, \omega)$ corresponds to a pipe dream~$P_I$ of~$\pipeDreams(\omega)$ (replace each position in~$I$ by a contact in~$P_I$, and the other positions by crossings in~$P_I$).
 The root function is given~$\rootFunction{I}{i} = \b{r}_{p,q} \eqdef \b{e}_p - \b{e}_q$ where~$p$ is the pipe arriving from the west and $q$ is the pipe arriving from the south at the box of~$P_I$ corresponding to position~$i$ of~$Q$.
@@
 It is shown in~\cite[Rem.~5.12]{PilaudStump-brickPolytope} that its increasing flip poset is not a lattice.
-This shows that neither the increasing flip poset, nor the acyclic increasing flip poset are lattices in general, even in type~$A$. \vincent{clean that}
+This shows that neither the increasing flip poset, nor the acyclic increasing flip poset are lattices in general, even in type~$A$.
 \end{example}
@@
 
+\begin{example}
+In the situation of \cref{exm:typeACoxeterSystem,exm:typeARootConfiguration}, the linear extensions of a facet~$I$ of~$\subwordComplex(Q, \omega)$ are precisely the linear extensions of the pipe dream~$P_I$ of~$\pipeDreams(\omega)$.
+\end{example}
+
 \begin{lemma}
@@
 \[
-\begin{array}{rcl}
+\begin{array}[b]{rcl}
 I \text{ is acyclic}  & \longleftrightarrow  &  \cone \Roots(I) \text{ is pointed} \\
@@
 & \longleftrightarrow  &  \linearExtensions(I) \neq \varnothing 
+\end{array}
 \qedhere
-\end{array}
 \]
@@
 
-\begin{example}
-In the situation of \cref{exm:typeACoxeterSystem,exm:typeARootConfiguration}, the linear extensions of a facet~$I$ of~$\subwordComplex(Q, \omega)$ are precisely the linear extensions of the pipe dream~$P_I$ of~$\pipeDreams(\omega)$.
-\end{example}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \item a \defn{lower set} if $\sigma < \tau$ and $\tau \in \fR$ implies~$\sigma \in \fR$,
-\item \defn{order convex} if $\sigma < \tau < \rho$ and~$\sigma, \rho \in \fR$ implies~$\tau \in \R$.
+\item \defn{order convex} if $\sigma < \tau < \rho$ and~$\sigma, \rho \in \fR$ implies~$\tau \in \fR$.
 \end{itemize}
@@
 So, our restricted list corresponding to $I$ looks like
-\begin{equation}
+\[
 \begin{array}{ccc}
@@
 \end{array}
-\end{equation}
+\]
 By  \cref{lem:rootFunctionFlips}~\eqref{lem:rootFunctionFlips3}, we obtain that flipping $j$ to $i$ creates the new facet $I' = I \ssm \{j\} \cap \{i\}$ whose corresponding restricted list looks like
-\begin{equation}
+\[
 \begin{array}{ccc}
@@
 \end{array}    
-\end{equation}
+\]
 
@@
 For a facet~$I$ of~$\subwordComplex(Q, \omega)$, we define~$\strongLinearExtensions(I) \eqdef \linearExtensions(I) \cap [e, \omega]$.
-We say that~$I$ is \defn{strongly acyclic}~$\strongLinearExtensions(I) \ne \varnothing$, and we denote by~$\subwordStronglyAcyclicFacets(Q, \omega)$ the set of strongly acyclic facets of~$\subwordComplex(Q, \omega)$.
+We say that~$I$ is \defn{strongly acyclic} if~$\strongLinearExtensions(I) \ne \varnothing$, and we denote by~$\subwordStronglyAcyclicFacets(Q, \omega)$ the set of strongly acyclic facets of~$\subwordComplex(Q, \omega)$.
 Note that by \cref{thm:linearExtensionsPartitionSubwordComplexA}~\eqref{item:partition}, we have
@@
 \label{subsec:sweepingAlgorithmSubwordComplexes}
-\vincent{I have not checked this part yet.}
-\vincent{Here, we must properly cite \cite{JahnStump} and say that we obtained this algorithm independently.}
-
-Given a linear extension $\pi \in \linearExtensions(Q,\omega)$, one natural question is whether we can recover the unique acyclic facet $I$ such that $\pi \in \linearExtensions(I)$.
-We can recover this facet via a sweeping algorithm which we now introduce.
-The algorithm outcomes a facet for every element~$\pi \in W$, and this will be the desired facet for each $\pi \in \linearExtensions(Q,\omega)$.
-
-\[
-\begin{tabular}{cccc}
-$\sweepingAlgorithm$ : & $W$  &$\longrightarrow$ &$\subwordFacets(Q,\omega)$\\
+
+We now extend the sweeping algorithm of \cref{subsec:sweepingAlgorithm} to construct, from a linear extension $\pi \in \linearExtensions(Q,\omega)$, the unique acyclic facet~$I$ such that $\pi \in \linearExtensions(I)$.
+We note that this algorithm was independently described in~\cite{JahnStump}.
+
+We start from a subword complex~$\subwordComplex(Q, \omega)$ and any element~$\pi \in W$.
+The sweeping algorithm outcomes a facet for every element~$\pi \in W$, and this will be the desired facet for each $\pi \in \linearExtensions(Q,\omega)$.
+In other words, we define a function
+\[
+\begin{tabular}{cccl}
+$\sweepingAlgorithm$ : & $W$ & $\longrightarrow$ & $\subwordFacets(Q,\omega)$\\
 & $\pi$ & $\longrightarrow$ & $\sweepingAlgorithm(Q,\omega,\pi)$
@@
 \]
-
-We start by setting $I^0=\varnothing$ to be the empty set.
-Then we scan the word $Q=(q_1,\dots ,q_m)$ from left to right.
-At position $j\in [m]$ we produce a new set $I^j$ obtained from the previous one $I^{j-1}$ by either adding $j$ or not, according to certain rules.
-We let $Q^j=Q_{[j]\ssm I^j}$ and denote by
+\vincent{delete that}
+
+It starts by setting $I^0=\varnothing$ to be the empty set.
+It then scans the word $Q=(q_1,\dots ,q_m)$ from left to right.
+At position $j\in [m]$ it produces a new set $I^j$ obtained from the previous one $I^{j-1}$ by either adding $j$ or not, according to certain rules.
+Roughly speaking, the goal of the algorithm is to insert a reduced expression of $\omega$ in $Q$ by sweeping the word from left to right, while deciding whether we use a letter or not by looking at the root $\beta=\rootFunction{I^j}{j}$ that it produces.
+If $\beta \in \Ninv(\omega)$ then it can not be used (Case~\ref{sweeping_case1}), otherwise we would not have a reduced expression for $\omega$.
+If $\beta \in \Inv(\omega)$ then it takes it when $\beta \in \Inv(\pi)$ (Case~\ref{sweeping_case2}), or delays it as much as possible when $\beta \in \Ninv(\pi)$ (Case~\ref{sweeping_case3}).
+If $\beta \in -\Inv(\omega)$ it can simply not take it (Case~\ref{sweeping_case4}).
+
+More precisely, let $Q^j=Q_{[j]\ssm I^j}$ and denote by
 \[
@@
 
-\begin{enumerate}
-    \item If $\rootFunction{I^j}{j}\in \Ninv(\omega)$ then let 
-    \[
+\begin{enumerate}[{Case} 1:]
+    \item If $\rootFunction{I^j}{j}\in \Ninv(\omega)$ then 
+    \(
     I^j=I^{j-1}\cup\{j\}.
-    \] 
+    \) 
     \label{sweeping_case1}
-    \item If $\rootFunction{I^j}{j}\in \Inv(\omega) \cap \Inv (\pi)$ then let 
-    \[
+    \item If $\rootFunction{I^j}{j}\in \Inv(\omega) \cap \Inv(\pi)$ then 
+    \(
     I^j=I^{j-1}.
-    \]
+    \)
     \label{sweeping_case2}
-    \item If $\rootFunction{I^j}{j}\in \Inv(\omega) \cap \Ninv (\pi)$ then we consider two cases: 
+    \item If $\rootFunction{I^j}{j}\in \Inv(\omega) \cap \Ninv(\pi)$ then we consider two cases: 
     \label{sweeping_case3} 
-    \begin{enumerate}
-        \item If $Q_{[m]\ssm I^{j-1}\ssm \{j\}}$ contains a reduced expression of $\omega$ with prefix $Q^{j-1}$ then let 
-        \[
-        I^j=I^{j-1}\cup \{j\}.
-        \]        
+    \begin{enumerate}[\hspace{-1cm} (a)]
+        \item If $Q_{[m]\ssm I^{j-1}\ssm \{j\}}$ contains a reduced expression of $\omega$ with prefix $Q^{j-1}$ then 
+        \(
+        {I^j=I^{j-1}\cup \{j\}}.
+        \)~
         \label{sweeping_case3a}
-        \item If not let 
-        \[
+        \item Otherwise
+        \(
         I^j=I^{j-1}.
-        \]
+        \)
         \label{sweeping_case3b}
     \end{enumerate}
-    \item If $\rootFunction{I^j}{j}\in -\Inv(\omega)$ then let
-    \[
+    \item If $\rootFunction{I^j}{j}\in -\Inv(\omega)$ then
+    \(
     I^j=I^{j-1}\cup \{j\}.
-    \]
+    \)
     \label{sweeping_case4}
@@
 
-We denote by \defn{$\sweepingAlgorithm(Q,\omega,\pi)$} the resulting set $I^m$ obtained at the last step of the algorithm.
-
-Roughly speaking, the goal of the algorithm is to insert a reduced expression of $\omega$ in $Q$ by sweeping the word from left to right, while deciding whether we use a letter or not by looking at the root $\beta=\rootFunction{I^j}{j}$ that it produces.
-If $\beta \in \Ninv(\omega)$ then it can not be used (Case~\eqref{sweeping_case1}), otherwise we would not have a reduced expression for $\omega$.
-If $\beta \in \Inv(\omega)$ then we take it when $\beta \in \Inv(\pi)$ (Case~\eqref{sweeping_case2}), or delay it as much as possible when $\beta \in \Ninv(\pi)$ (Case~\eqref{sweeping_case3}).
-If $\beta \in -\Inv(\omega)$ we can simply not take it (Case~\eqref{sweeping_case4}).
+We denote by $\sweepingAlgorithm(Q,\omega,\pi)$ the resulting set $I^m$ obtained at the last step of the algorithm.
+The objective of this section is the following statement.
 
 \begin{proposition}
-\label{prop_sweeping1}
-    Let $\subwordComplex(Q,\omega)$ be a non-empty subword complex.
-    For every $\pi \in W$, the set $\sweepingAlgorithm(Q,\omega,\pi)$ is a facet of $\subwordComplex(Q,\omega)$.
+\label{prop:sweeping}
+Let $\subwordComplex(Q,\omega)$ be a non-empty subword complex. Then, for every $\pi \in W$, 
+\begin{enumerate}
+\item the set $\sweepingAlgorithm(Q,\omega,\pi)$ is a facet of $\subwordComplex(Q,\omega)$, \label{item:sweeping1}
+\item if $\pi\in \linearExtensions(I)$ for some facet $I\in \subwordComplex(Q,\omega)$, then $\sweepingAlgorithm(Q,\omega,\pi) = I$. \label{item:sweeping2}
+\end{enumerate}
 \end{proposition}
 
-\begin{proof}
-    Let $I^j$ and $Q^j=Q_{[j]\ssm I^j}$ be as defined in the sweeping algorithm for $\pi$. 
-    The proposition follows by applying the following claim for $j=m$.
-    \smallskip
-
-    {\bf Claim}: $Q^j$ is a reduced expression which is the prefix of a reduced expression of $\omega$ in $Q_{[m]\ssm I^j}$.
-
-    \smallskip
-    We prove the claim by induction on $j$.
+We first need to argue that the algorithm terminates, that is, that any position $j$ falls into one of the four cases above.
+
+\begin{lemma}
+\label{lem:sweeping1}
+At step $j$ of the sweeping algorithm, the root~$\rootFunction{I^j}{j}$ belongs to exactly one of~the~sets
+\[
+\Ninv(\omega),
+\qquad
+\Inv(\omega) \cap \Inv(\pi),
+\qquad
+\Inv(\omega) \cap \Ninv(\pi)
+\qquad\text{or}\qquad
+-\Inv(\omega).
+\]
+\end{lemma}
+
+\begin{proof}
+The root $\rootFunction{I^j}{j}$ belongs to~$\Phi^+ \sqcup \Phi^-$ and we know that
+\[
+\Phi^+ = \Inv(\omega) \sqcup \Ninv(\omega) \qquad \qquad
+\Phi^- = -\Inv(\omega) \sqcup -\Ninv(\omega)  
+\]
+%The positive roots are covered by the cases (1),(2), and (3).
+%The negative roots in $-\Inv(\omega)$ are covered in case (4).
+Since we are inserting a reduced expression of $\omega$ in $Q$, the case $-\Ninv(\omega)$ never occurs.
+\end{proof}
+
+We now observe the main invariant of the sweeping algorithm.
+
+\begin{lemma}
+\label{lem:sweeping2}
+At any step~$j$ of the algorithm, $Q^j$ is a reduced expression which is the prefix of a reduced expression of $\omega$ in $Q_{[m]\ssm I^j}$.
+\end{lemma}
+
+\begin{proof}
+The proof works by induction on $j$.
 
@@
 
-    Now assume that the claim holds for $j-1$ and prove it for $j$.
+We assume now that the claim holds for $j-1$ and we prove it for $j$.
 Note that 
-    \begin{equation}
+\[
 Q^j = 
 \begin{cases}
-    Q^{j-1}, & \text{if } I^j=I^{j-1}\cup \{j\} \\
-    Q^{j-1}\circ (q_j), & \text{if } I^j=I^{j-1}
+Q^{j-1}, & \text{if } I^j=I^{j-1}\cup \{j\} ,\\
+Q^{j-1} q_j, & \text{if } I^j=I^{j-1}.
 \end{cases}
-    \end{equation}    
+\]
 We analyze the different cases of the sweeping algorithm.
@@
     Since $\rootFunction{I^j}{j}\in \Ninv(\omega)$, this reduced expression can not use the letter $q_j$; so, it is a reduced expression of $\omega$ in $Q_{[m]\ssm I^{j}}$ as desired.
-    \item If $\rootFunction{I^j}{j}\in \Inv(\omega) \cap \Inv (\pi)$ then $Q^j= Q^{j-1}\circ (q_j)$, which is a reduced expression because~$Q^{j-1}$ is reduced and $\rootFunction{I^j}{j}\in \Inv(\omega)$.
+    \item If $\rootFunction{I^j}{j}\in \Inv(\omega) \cap \Inv(\pi)$ then $Q^j= Q^{j-1}\circ (q_j)$, which is a reduced expression because~$Q^{j-1}$ is reduced and $\rootFunction{I^j}{j}\in \Inv(\omega)$.
 
@@
 
-    \item[(3)(a)] If $\rootFunction{I^j}{j}\in \Inv(\omega) \cap \Ninv (\pi)$ and $Q_{[m]\ssm I^{j-1}\ssm \{j\}}$ contains a reduced expression of $\omega$ with prefix $Q^{j-1}$, then $Q^j=Q^{j-1}$.
+    \item[(3)(a)] If $\rootFunction{I^j}{j}\in \Inv(\omega) \cap \Ninv(\pi)$ and $Q_{[m]\ssm I^{j-1}\ssm \{j\}}$ contains a reduced expression of $\omega$ with prefix $Q^{j-1}$, then $Q^j=Q^{j-1}$.
     Therefore, $Q^j$ is reduced and it is a prefix of a reduced expression of $\omega$ in 
@@
 
-    \item[(3)(b)] In this case, $\rootFunction{I^j}{j}\in \Inv(\omega) \cap \Ninv (\pi)$ but $Q^j= Q^{j-1}\circ (q_j)$. The proof is similar to the proof of (2).
-
-    \item[(4)] If $\rootFunction{I^j}{j}\in -\Inv(\omega)$ then $Q^j=Q^{j-1}$. The argument is similar to that of part (1).
+    \item[(3)(b)] In this case, $\rootFunction{I^j}{j}\in \Inv(\omega) \cap \Ninv(\pi)$ but $Q^j= Q^{j-1}\circ (q_j)$. The proof is similar to the proof of (2).
+
+    \item[(4)] If $\rootFunction{I^j}{j}\in -\Inv(\omega)$ then $Q^j=Q^{j-1}$. The argument is similar to that of Case~(1).
+    \qedhere
     \end{enumerate}
-
-Finally, we need to argue that any position $j$ falls into one of these cases.
-The root $\rootFunction{I^j}{j}\in \Phi^+ \sqcup \Phi^-$ and we know that
-\[
-\Phi^+ = \Inv(\omega) \sqcup \Ninv(\omega) \qquad \qquad
-\Phi^- = -\Inv(\omega) \sqcup -\Ninv(\omega)  
-\]
-The positive roots are covered by the cases (1),(2), and (3).
-The negative roots in $-\Inv(\omega)$ are covered in case (4).
-Since we are inserting a reduced expression of $\omega$ in $Q$, the case $-\Ninv(\omega)$ never occurs. 
-\end{proof}
-
-The following proposition shows that for every linear extension $\pi \in \linearExtensions(Q,\omega)$, the sweeping algorithm recovers the unique acyclic facet $I$ such that $\pi \in \linearExtensions(I)$.
-
-\begin{proposition}
-\label{prop_sweeping2}
-    If $\pi\in \linearExtensions(I)$ for some facet $I\in \subwordComplex(Q,\omega)$, then 
-    \[
-I = \sweepingAlgorithm(Q,\omega,\pi).
-    \]
-\end{proposition}
-
-Our proof is based on the following lemma.
-
-\begin{lemma}\label{lem_negativeroot}
+\end{proof}
+
+Finally, we need the following technical statement.
+
+\begin{lemma}
+\label{lem:sweeping3}
 Let $I_1,I_2\in \subwordComplex(Q,\omega)$ be two different facets, and $j\in [m]$ be the first position where they differ.
@@
 
-\begin{proof}[Proof of \cref{prop_sweeping2}]
-Assume $\pi \in \linearExtensions(I)$ and let $I^j=I\cap [j]$.
-We will show that the partial root function $\rootFunction{I^j}{\cdot}$ agrees with the decisions taken in the sweeping algorithm.
+\begin{proof}[Proof of \cref{prop:sweeping}]
+Since the sweeping algorithm terminates by \cref{lem:sweeping1}, Point~\eqref{item:sweeping1} follows directly from the invariant of the sweeping algorithm of \cref{lem:sweeping2} applied when~$j = m$.
+
+For Point~\eqref{item:sweeping2}, assume $\pi \in \linearExtensions(I)$ and let $I^j=I\cap [j]$.
+We will show that the partial root function~$\rootFunction{I^j}{\cdot}$ agrees with the decisions taken in the sweeping algorithm.
 Indeed, we will see that those decisions are forced.
@@
 Recall that 
-
 \begin{center}
@@
     \item If $\rootFunction{I^j}{j}\in \Ninv(\omega)$ then clearly $j\in I$ is forced. Otherwise $Q_{[m]\ssm I}$ would not be a reduced expression of $\omega$.
-    \item If $\rootFunction{I^j}{j}\in \Inv(\omega) \cap \Inv (\pi)$ then $j\notin I$ is forced. 
+    \item If $\rootFunction{I^j}{j}\in \Inv(\omega) \cap \Inv(\pi)$ then $j\notin I$ is forced. 
     Otherwise we would have an inversion of $\pi$ in the root configuration, which contradicts $\pi \in \linearExtensions(I)$.
-    \item[(3)(a)] If $\rootFunction{I^j}{j}\in \Inv(\omega) \cap \Ninv (\pi)$ and $Q_{[m]\ssm I^{j-1}\ssm \{j\}}$ contains a reduced expression of $\omega$ with prefix $Q^{j-1}$ then $j\in I^j$ is forced.
+    \item[(3)(a)] If $\rootFunction{I^j}{j}\in \Inv(\omega) \cap \Ninv(\pi)$ and $Q_{[m]\ssm I^{j-1}\ssm \{j\}}$ contains a reduced expression of $\omega$ with prefix $Q^{j-1}$ then $j\in I^j$ is forced.
 
@@
 Let $I_1=\sweepingAlgorithm(Q,\omega,\pi)$ and $I_2=I$.
-Applying \cref{lem_negativeroot}, we deduce that $\beta=\rootFunction{I^j}{j}=\rootFunction{I}{j}$ satisfies
+Applying \cref{lem:sweeping3}, we deduce that $\beta=\rootFunction{I^j}{j}=\rootFunction{I}{j}$ satisfies
     \[
@@
     But $\beta \in \Ninv(\pi)$. This contradicts $\pi\in \linearExtensions(I)$.
-    \item[(3)(b)]  If $\rootFunction{I^j}{j}\in \Inv(\omega) \cap \Ninv (\pi)$ and $Q_{[m]\ssm I^{j-1}\ssm \{j\}}$ does not contain a reduced expression of $\omega$ with prefix $Q^{j-1}$ then $j\notin I^j$ is forced.
+    \item[(3)(b)]  If $\rootFunction{I^j}{j}\in \Inv(\omega) \cap \Ninv(\pi)$ and $Q_{[m]\ssm I^{j-1}\ssm \{j\}}$ does not contain a reduced expression of $\omega$ with prefix $Q^{j-1}$ then $j\notin I^j$ is forced.
 Otherwise, the complement of $I$ would not be a reduced expression of $\omega$.
     \item[(4)] If $\rootFunction{I^j}{j}\in -\Inv(\omega)$ then $j\in I^j$ is clearly forced. Otherwise, the complement of $I$ would not be a reduced expression.
+    \qedhere
 \end{enumerate}
@@
 \begin{remark}
-    Although the sweeping algorithm produces a facet $I=\sweepingAlgorithm(Q,\omega,\pi)$ for every~$\omega\in W$, in some cases we have $\pi \notin \linearExtensions(I)$. 
+    Although the sweeping algorithm produces a facet $I=\sweepingAlgorithm(Q,\omega,\pi)$ for every~${\omega\in W}$, in some cases we have $\pi \notin \linearExtensions(I)$. 
     This happens because of Case~\eqref{sweeping_case1}, when a non-inversion~$\beta\in \Ninv(\omega)$ of $\omega$ is added to the root configuration $\Roots(I)$, such that~$\beta \notin \Ninv(\pi)$.

### 2023-03-08 acyclicFacets/draft/latticePipeDreams.tex
adding picture

@@
 \end{itemize}
-In summary, we obtain the following statement.
+In summary, we obtain the following statement, illustrated in \cref{fig:latticeAcyclicPipeDreams}.
 
@@
 This section goes straight to the proof of this property, and leaves alternative perspectives on this quotient to \cref{sec:furtherTopics}.
+\vincent{add picture}
 
@@
 
-In this section, we prove the following structural property of~$\linearExtensions(P)$.
+In this section, we prove the following structural property of~$\linearExtensions(P)$, illustrated in \cref{fig:latticeAcyclicPipeDreams}.
 
@@
 
+\begin{figure}
+	\centerline{\includegraphics[scale=1]{latticeAcyclicPipeDreams}}
+	\caption{The pipe dream congruence on the weak order interval~$[12345, 31542]$ (left) and the increasing flip graph on acyclic pipe dreams (right).
+The blue bubbles represent the classes of the pipe dream congruence.
+The acyclic pipe dreams are represented with their contact graphs.}
+	\label{fig:latticeAcyclicPipeDreams}
+\end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-We now focus on the following congruence.
+We now focus on the following congruence, illustrated in \cref{fig:latticeAcyclicPipeDreams}.
 
@@
 \end{itemize}
-In this section, we aim at the following statement.
+In this section, we aim at the following statement, illustrated in \cref{fig:latticeAcyclicPipeDreams}.
 
@@
 \[
-\set{ik}{i < j \text{ and } j-i \le \#\set{k \in [i]}{\omega^{-1}(k) < \omega^{-1}(j)}}.
+\set{ij}{i < j \text{ and } j-i \le \#\set{k \in [i]}{\omega^{-1}(k) < \omega^{-1}(j)}}.
 \]
@@
 \label{rem:linearExtensionsPartitionSubwordComplexA}
-Before proving this theorem, we would like to make the following remarks about items~\eqref{item:cover} and~\eqref{item:convex}.
+Before proving this theorem, we would like to make the following remarks about items~\eqref{item:convex} and~\eqref{item:cover}.
 \begin{enumerate}
-\setcounter{enumi}{1}
+\setcounter{enumi}{0}
 \item There are cases where $[e,\omega] \ne \linearExtensions(Q,\omega)$. \cesarm{add discussion}
@@
 %
-\setcounter{enumi}{3}
+\setcounter{enumi}{2}
 \item $\linearExtensions(I)$ is not an interval in general. See for instance the example~\cite[Figure~9]{PilaudStump-brickPolytope}. 
@@
 The sweeping algorithm outcomes a facet for every element~$\pi \in W$, and this will be the desired facet for each $\pi \in \linearExtensions(Q,\omega)$.
-In other words, we define a function
-\[
-\begin{tabular}{cccl}
-$\sweepingAlgorithm$ : & $W$ & $\longrightarrow$ & $\subwordFacets(Q,\omega)$\\
-& $\pi$ & $\longrightarrow$ & $\sweepingAlgorithm(Q,\omega,\pi)$
-\end{tabular}
-\]
-\vincent{delete that}
+%In other words, we define a function
+%\[
+%\begin{tabular}{cccl}
+%$\sweepingAlgorithm$ : & $W$ & $\longrightarrow$ & $\subwordFacets(Q,\omega)$\\
+%& $\pi$ & $\longrightarrow$ & $\sweepingAlgorithm(Q,\omega,\pi)$
+%\end{tabular}
+%\]
 

### 2023-03-09 acyclicFacets/draft/latticePipeDreams.tex
Proof lemma 5.27

--- 2023-03-08 acyclicFacets/draft/latticePipeDreams.tex
@@
 I do not remember the details at the moment, but the proof is based on the paper of Jahn--Stump that we discussed during your visit in Graz.}
+
+For the purpose of this proof, let us write~$\leqslant_B$ the strong Bruhat order, defined by~$x \leqslant_B y$ if and only if a reduced expression of~$y$ has a reduced expression of~$x$ as a subword, and~$x \prec_B y$ the covers of this order.
+We note that for any word~$Q$ and any~$x\in W$, we can find a reduced expression of~$x$ as a subword of~$Q$ if and only if~$x \leqslant_B Dem(Q)$ the demazure product of~$Q$.
+
+We will use \cite[Proposition 3.14]{JahnStump}, reformulated as follows:
+
+\begin{proposition}[\cite{JahnStump}]\label{prop:JSDemazureCone}
+Let~$\subwordComplex(Q,w)$ be a non-empty subword complex.
+Then for any facet~$I \in \subwordComplex(Q,w)$ and for any simple root~$\alpha$ such that~$w \prec_B s_\alpha w \leqslant_B Dem(Q)$, we have~$\alpha \in \Roots(I)$.
+\end{proposition}
+
+Let us write~$w = uv$ with~$u$ the prefix of~$w$ defined by~$I_1$ and~$I_2$ on~$Q$ until index~$j-1$ and~$v$ the suffix of~$w$ defined by the same facets from index~$j$ and onward.
+Let us also write~$s$ the~$j^{\text{th}}$ letter of~$Q$ and~$\alpha$ the simple root associated with~$s$.
+We note that~$\beta = \rootFunction{I_1}{j} = u(\alpha)$, and that since~$j \notin I_2$, we know that~$sv \prec_B v$ (this is also a cover of the left weak order).
+
+Let us call~$Q'$ the suffix of~$Q$ starting at index~$j+1$, and~$I'_1,I'_2$ the restrictions of~$I_1$ and~$I_2$ to~$Q'$.
+The subwords induced by~$I'_1$ and~$I'_2$ on~$Q'$ are suffixes of reduced subwords of~$Q$, so they are also reduced.
+Moreover, since~$j \in I_1$, we know that~$I'_1$ is a facet of~$\subwordComplex(Q',v)$; this means that this subword complex is not empty and that~$v \leqslant_B Dem(Q')$.
+Similarly, since~$j \notin I_2$, we know that~$I'_2$ is a facet of~$\subwordComplex(Q',sv)$.
+By combining the previous statements, we know that~$sv \prec_B v \leqslant_B Dem(Q')$ (or equivalently and with~$v' = sv$, that~$v' \prec_B sv' \leqslant_B Dem(Q')$).
+We can thus apply \cref{prop:JSDemazureCone} to obtain that~$\alpha \in \Roots(I'_2)$.
+
+Going back to our facets on~$Q$, we know that the prefix of~$w$ written by~$I_2$ on~$Q \cap [j]$ is~$us$, and thus~$us(\Roots(I'_2)) \subseteq \Roots(I_2)$.
+Therefore, we have~$us(\alpha) = u(-\alpha) = -u(\alpha) = -\beta \in \Roots(I_2)$, thus concluding the proof.
 \end{proof}

### 2023-03-09 acyclicFacets/draft/latticePipeDreams.tex
missing pictures

--- 2023-03-08 acyclicFacets/draft/latticePipeDreams.tex
@@
 This section goes straight to the proof of this property, and leaves alternative perspectives on this quotient to \cref{sec:furtherTopics}.
-\vincent{add picture}
 
@@
 \begin{figure}[ht]
-	\centerline{\includegraphics[scale=1.3]{counterExampleRestrictionIncreasingFlipPoset}}
+	\centerline{\includegraphics[scale=1.2]{counterExampleRestrictionIncreasingFlipPoset}}
 	\caption{Two acyclic pipe dreams~$\acyclicPipeDreams(126543)$ connected by a sequence of increasing flips in~$\pipeDreams(126543)$ but by no sequence of increasing flips in~$\acyclicPipeDreams(126543)$.}
@@
 \label{rem:linearExtensionsPartitionSubwordComplexA}
-Before proving this theorem, we would like to make the following remarks about items~\eqref{item:convex} and~\eqref{item:cover}.
+Before proving this theorem, we would like to make the following remarks about items~\eqref{item:convex} and~\eqref{item:cover}:
 \begin{enumerate}
 \setcounter{enumi}{0}
-\item There are cases where $[e,\omega] \ne \linearExtensions(Q,\omega)$. \cesarm{add discussion}
+\item There are cases where $[e,\omega] \ne \linearExtensions(Q,\omega)$.
+Namely, some of the sets~$\linearExtensions(I)$ may not be included in~$[e,\omega]$, and may even not meet~$[e,\omega]$.
+See \cref{fig:counterExample1}.
 %
-\begin{figure}[h]
-	\includegraphics[width=0.52\textwidth]{interval_not_contained1} \quad
-	\includegraphics[width=0.43\textwidth]{interval_not_contained2}
-	\caption{A facet of a subword complex~$\subwordComplex(Q, \omega)$ whose linear extensions all lie outside the interval~$[e, \omega]$.}
-	\label{fig:outOfInterval}
+%\begin{figure}[h]
+%	\includegraphics[width=0.52\textwidth]{interval_not_contained1} \quad
+%	\includegraphics[width=0.43\textwidth]{interval_not_contained2}
+%	\caption{A facet of a subword complex~$\subwordComplex(Q, \omega)$ whose linear extensions all lie outside the interval~$[e, \omega]$.}
+%	\label{fig:outOfInterval}
+%\end{figure}
+%
+\begin{figure}[p]
+	\centerline{\includegraphics[scale=.8]{counterExample1}}
+	\caption{The sets~$\linearExtensions(I)$ (blue bubbles) are not always subsets of, and may even not meet~$[e,\omega]$ (green bubble).}
+	\label{fig:counterExample1}
 \end{figure}
+
+\setcounter{enumi}{2}
+\item Some of the sets~$\linearExtensions(I)$ may not be intervals.
+See \cref{fig:counterExample2}.
+Another example with~$\omega = \omega_\circ$ can be found in~\cite[Figure~9]{PilaudStump-brickPolytope}.
 %
-\setcounter{enumi}{2}
-\item $\linearExtensions(I)$ is not an interval in general. See for instance the example~\cite[Figure~9]{PilaudStump-brickPolytope}. 
-In that figure, the elements of the week order $\mathfrak{S}_4$ that are linear extensions of the same acyclic facet of a given subword complex are grouped together.
-Some of the groups in the figure are not intervals.
-\\
+\begin{figure}[p]
+	\centerline{\includegraphics[scale=.8]{counterExample2}}
+	\caption{The sets~$\linearExtensions(I)$ (blue bulles) are not always intervals.}
+	\label{fig:counterExample2}
+\end{figure}
 \end{enumerate}
+\cref{fig:counterExample1,fig:counterExample2} represent type~$A$ subword complexes.
+As in~\cite{PilaudPocchiola, PilaudSantos-brickPolytope, PilaudStump-brickPolytope}, we thus use pseudoline arrangements on sorting networks to represent their facets (and we have represented their contact graphs together).
 \end{remark}

### 2023-03-09 acyclicFacets/draft/latticePipeDreams.tex
improve Remark 5.11

@@
 \label{rem:linearExtensionsPartitionSubwordComplexA}
-Before proving this theorem, we would like to make the following remarks about items~\eqref{item:convex} and~\eqref{item:cover}:
+Before proving it, we would like to make the following remarks about theorem.
 \begin{enumerate}
-\setcounter{enumi}{0}
-\item There are cases where $[e,\omega] \ne \linearExtensions(Q,\omega)$.
-Namely, some of the sets~$\linearExtensions(I)$ may not be included in~$[e,\omega]$, and may even not meet~$[e,\omega]$.
-See \cref{fig:counterExample1}.
+\item While the sets~$\linearExtensions(I)$ are order convex, they may not be intervals.
+See \cref{fig:counterExample2}.
+Another example with~$\omega = \omega_\circ$ can be found in~\cite[Figure~9]{PilaudStump-brickPolytope}.
+%
+\begin{figure}[p]
+	\centerline{\includegraphics[scale=.8]{counterExample2}}
+	\caption{The sets~$\linearExtensions(I)$ (blue bulles) are not always intervals.}
+	\label{fig:counterExample2}
+\end{figure}
+
+\item The lower set~$\linearExtensions(Q,\omega)$ may have more than one maximal element, and~$\omega$ is not necessarily maximal in~$\linearExtensions(Q,\omega)$. See \cref{fig:counterExample1}.
+
+\item Some of the sets~$\linearExtensions(I)$ may not be included in, nor even meet~$[e,\omega]$. See \cref{fig:counterExample1}.
 %
@@
 \end{figure}
-
-\setcounter{enumi}{2}
-\item Some of the sets~$\linearExtensions(I)$ may not be intervals.
-See \cref{fig:counterExample2}.
-Another example with~$\omega = \omega_\circ$ can be found in~\cite[Figure~9]{PilaudStump-brickPolytope}.
-%
-\begin{figure}[p]
-	\centerline{\includegraphics[scale=.8]{counterExample2}}
-	\caption{The sets~$\linearExtensions(I)$ (blue bulles) are not always intervals.}
-	\label{fig:counterExample2}
-\end{figure}
 \end{enumerate}
-\cref{fig:counterExample1,fig:counterExample2} represent type~$A$ subword complexes.
+Note that \cref{fig:counterExample1,fig:counterExample2} represent type~$A$ subword complexes.
 As in~\cite{PilaudPocchiola, PilaudSantos-brickPolytope, PilaudStump-brickPolytope}, we thus use pseudoline arrangements on sorting networks to represent their facets (and we have represented their contact graphs together).

### 2023-03-09 acyclicFacets/draft/latticePipeDreams.tex
get Proposition 5.18 out of the proof of Lemma 5.27

@@
 
-\begin{proof}
-    ~\cesar{Noemie: can you please write the proof of this Lemma?
-I do not remember the details at the moment, but the proof is based on the paper of Jahn--Stump that we discussed during your visit in Graz.}
-
-For the purpose of this proof, let us write~$\leqslant_B$ the strong Bruhat order, defined by~$x \leqslant_B y$ if and only if a reduced expression of~$y$ has a reduced expression of~$x$ as a subword, and~$x \prec_B y$ the covers of this order.
-We note that for any word~$Q$ and any~$x\in W$, we can find a reduced expression of~$x$ as a subword of~$Q$ if and only if~$x \leqslant_B Dem(Q)$ the demazure product of~$Q$.
-
-We will use \cite[Proposition 3.14]{JahnStump}, reformulated as follows:
+In the proof of \cref{lem:sweeping3}, let us write~$\leqslant_B$ the strong Bruhat order, defined by~$x \leqslant_B y$ if and only if a reduced expression of~$y$ has a reduced expression of~$x$ as a subword, and~$x \prec_B y$ the covers of this order.
+We note that for any word~$Q$ and any~$x\in W$, we can find a reduced expression of~$x$ as a subword of~$Q$ if and only if~$x \leqslant_B \DemazureProduct(Q)$ the Demazure product of~$Q$.
+We will use \cite[Proposition 3.14]{JahnStump}, reformulated as follows.
 
@@
 Let~$\subwordComplex(Q,w)$ be a non-empty subword complex.
-Then for any facet~$I \in \subwordComplex(Q,w)$ and for any simple root~$\alpha$ such that~$w \prec_B s_\alpha w \leqslant_B Dem(Q)$, we have~$\alpha \in \Roots(I)$.
+Then for any facet~$I \in \subwordComplex(Q,w)$ and for any simple root~$\alpha$ such that~$w \prec_B s_\alpha w \leqslant_B \DemazureProduct(Q)$, we have~$\alpha \in \Roots(I)$.
 \end{proposition}
 
+\begin{proof}[Proof of \cref{lem:sweeping3}]
 Let us write~$w = uv$ with~$u$ the prefix of~$w$ defined by~$I_1$ and~$I_2$ on~$Q$ until index~$j-1$ and~$v$ the suffix of~$w$ defined by the same facets from index~$j$ and onward.
@@
 The subwords induced by~$I'_1$ and~$I'_2$ on~$Q'$ are suffixes of reduced subwords of~$Q$, so they are also reduced.
-Moreover, since~$j \in I_1$, we know that~$I'_1$ is a facet of~$\subwordComplex(Q',v)$; this means that this subword complex is not empty and that~$v \leqslant_B Dem(Q')$.
+Moreover, since~$j \in I_1$, we know that~$I'_1$ is a facet of~$\subwordComplex(Q',v)$; this means that this subword complex is not empty and that~$v \leqslant_B \DemazureProduct(Q')$.
 Similarly, since~$j \notin I_2$, we know that~$I'_2$ is a facet of~$\subwordComplex(Q',sv)$.
-By combining the previous statements, we know that~$sv \prec_B v \leqslant_B Dem(Q')$ (or equivalently and with~$v' = sv$, that~$v' \prec_B sv' \leqslant_B Dem(Q')$).
+By combining the previous statements, we know that~$sv \prec_B v \leqslant_B \DemazureProduct(Q')$ (or equivalently and with~$v' = sv$, that~$v' \prec_B sv' \leqslant_B \DemazureProduct(Q')$).
 We can thus apply \cref{prop:JSDemazureCone} to obtain that~$\alpha \in \Roots(I'_2)$.

### 2023-03-09 acyclicFacets/draft/latticePipeDreams.tex
adding quesiton
My reading comments and little fix.

--- 2023-03-09 acyclicFacets/draft/latticePipeDreams.tex
@@
 \begin{figure}[ht]
-	\centerline{\includegraphics[scale=1.2]{counterExampleRestrictionIncreasingFlipPoset}}
+	\centerline{\includegraphics[scale=1.3]{counterExampleRestrictionIncreasingFlipPoset}}
 	\caption{Two acyclic pipe dreams~$\acyclicPipeDreams(126543)$ connected by a sequence of increasing flips in~$\pipeDreams(126543)$ but by no sequence of increasing flips in~$\acyclicPipeDreams(126543)$.}
@@
 
-The \defn{weak order} on $W$ is the partial order $\le$ defined by $\sigma \leq \omega$ if there exists $\tau \in W$ such that $\sigma\tau = \omega$ and $\ell(\sigma) + \ell(\tau) = \ell(\omega)$.
+The \defn{weak order} on $W$ is the partial order $\le$ defined by $\sigma \leq \omega$ if there exists $\tau \in S$  such that $\sigma\tau = \omega$ and $\ell(\sigma) + \ell(\tau) = \ell(\omega)$.
 In other words, the element $\omega$ has a reduced expression with a prefix which is a reduced expression of $\sigma$.
@@
 \label{rem:linearExtensionsPartitionSubwordComplexA}
-Before proving this theorem, we would like to make the following remarks about items~\eqref{item:convex} and~\eqref{item:cover}:
+Before proving this theorem, we would like to make the following remarks about items~\eqref{item:convex} and~\eqref{item:cover}.
 \begin{enumerate}
 \setcounter{enumi}{0}
-\item There are cases where $[e,\omega] \ne \linearExtensions(Q,\omega)$.
-Namely, some of the sets~$\linearExtensions(I)$ may not be included in~$[e,\omega]$, and may even not meet~$[e,\omega]$.
-See \cref{fig:counterExample1}.
+\item There are cases where $[e,\omega] \ne \linearExtensions(Q,\omega)$. \cesarm{add discussion}
 %
-%\begin{figure}[h]
-%	\includegraphics[width=0.52\textwidth]{interval_not_contained1} \quad
-%	\includegraphics[width=0.43\textwidth]{interval_not_contained2}
-%	\caption{A facet of a subword complex~$\subwordComplex(Q, \omega)$ whose linear extensions all lie outside the interval~$[e, \omega]$.}
-%	\label{fig:outOfInterval}
-%\end{figure}
+\begin{figure}[h]
+	\includegraphics[width=0.52\textwidth]{interval_not_contained1} \quad
+	\includegraphics[width=0.43\textwidth]{interval_not_contained2}
+	\caption{A facet of a subword complex~$\subwordComplex(Q, \omega)$ whose linear extensions all lie outside the interval~$[e, \omega]$.}
+	\label{fig:outOfInterval}
+\end{figure}
 %
-\begin{figure}[p]
-	\centerline{\includegraphics[scale=.8]{counterExample1}}
-	\caption{The sets~$\linearExtensions(I)$ (blue bubbles) are not always subsets of, and may even not meet~$[e,\omega]$ (green bubble).}
-	\label{fig:counterExample1}
-\end{figure}
-
 \setcounter{enumi}{2}
-\item Some of the sets~$\linearExtensions(I)$ may not be intervals.
-See \cref{fig:counterExample2}.
-Another example with~$\omega = \omega_\circ$ can be found in~\cite[Figure~9]{PilaudStump-brickPolytope}.
-%
-\begin{figure}[p]
-	\centerline{\includegraphics[scale=.8]{counterExample2}}
-	\caption{The sets~$\linearExtensions(I)$ (blue bulles) are not always intervals.}
-	\label{fig:counterExample2}
-\end{figure}
+\item $\linearExtensions(I)$ is not an interval in general. See for instance the example~\cite[Figure~9]{PilaudStump-brickPolytope}. 
+In that figure, the elements of the week order $\mathfrak{S}_4$ that are linear extensions of the same acyclic facet of a given subword complex are grouped together.
+Some of the groups in the figure are not intervals.
+\\
 \end{enumerate}
-\cref{fig:counterExample1,fig:counterExample2} represent type~$A$ subword complexes.
-As in~\cite{PilaudPocchiola, PilaudSantos-brickPolytope, PilaudStump-brickPolytope}, we thus use pseudoline arrangements on sorting networks to represent their facets (and we have represented their contact graphs together).
 \end{remark}
@@
 \end{definition}
+
+\nantel{it is bad to name this ``congruence". Call it equivalence, and state it is a concruence in the conjecture.}
 
@@
 
+\nantel{to be honest, I find that the paper ends well here, the rest should be part of a paper by No\'emie alone?}
+
 As we have seen in \cref{cor_acyclicpipedreams_lattice}, the increasing flip poset of acyclic pipe dreams of any permutation $\omega$ is a lattice, because it is isomorphic to the lattice quotient~$[e,\omega]/\equiv_\omega$.
@@
 
-For the purpose of this proof, let us write~$\leqslant_B$ the strong Bruhat order, defined by~$x \leqslant_B y$ if and only if a reduced expression of~$y$ has a reduced expression of~$x$ as a subword, and~$x \prec_B y$ the covers of this order.
+For the purpose of this proof, let us write~$\leqslant_B$ the strong Bruhat order, defined by~$x \leqslant_B y \iff$ a reduced expression of~$y$ has a reduced expression of~$x$ as a subword, and~$x \less_B y$ the covers of this order.
 We note that for any word~$Q$ and any~$x\in W$, we can find a reduced expression of~$x$ as a subword of~$Q$ if and only if~$x \leqslant_B Dem(Q)$ the demazure product of~$Q$.
-
-We will use \cite[Proposition 3.14]{JahnStump}, reformulated as follows:
-
-\begin{proposition}[\cite{JahnStump}]\label{prop:JSDemazureCone}
-Let~$\subwordComplex(Q,w)$ be a non-empty subword complex.
-Then for any facet~$I \in \subwordComplex(Q,w)$ and for any simple root~$\alpha$ such that~$w \prec_B s_\alpha w \leqslant_B Dem(Q)$, we have~$\alpha \in \Roots(I)$.
-\end{proposition}
 
@@
 Let us also write~$s$ the~$j^{\text{th}}$ letter of~$Q$ and~$\alpha$ the simple root associated with~$s$.
-We note that~$\beta = \rootFunction{I_1}{j} = u(\alpha)$, and that since~$j \notin I_2$, we know that~$sv \prec_B v$ (this is also a cover of the left weak order).
-
-Let us call~$Q'$ the suffix of~$Q$ starting at index~$j+1$, and~$I'_1,I'_2$ the restrictions of~$I_1$ and~$I_2$ to~$Q'$.
-The subwords induced by~$I'_1$ and~$I'_2$ on~$Q'$ are suffixes of reduced subwords of~$Q$, so they are also reduced.
-Moreover, since~$j \in I_1$, we know that~$I'_1$ is a facet of~$\subwordComplex(Q',v)$; this means that this subword complex is not empty and that~$v \leqslant_B Dem(Q')$.
-Similarly, since~$j \notin I_2$, we know that~$I'_2$ is a facet of~$\subwordComplex(Q',sv)$.
-By combining the previous statements, we know that~$sv \prec_B v \leqslant_B Dem(Q')$ (or equivalently and with~$v' = sv$, that~$v' \prec_B sv' \leqslant_B Dem(Q')$).
-We can thus apply \cref{prop:JSDemazureCone} to obtain that~$\alpha \in \Roots(I'_2)$.
-
-Going back to our facets on~$Q$, we know that the prefix of~$w$ written by~$I_2$ on~$Q \cap [j]$ is~$us$, and thus~$us(\Roots(I'_2)) \subseteq \Roots(I_2)$.
-Therefore, we have~$us(\alpha) = u(-\alpha) = -u(\alpha) = -\beta \in \Roots(I_2)$, thus concluding the proof.
+We note that~$\beta = \rootFunction{I_1}{j} = u(\alpha)$.
+
+Let us call~$Q'$ the suffix of~$Q$ starting at index~$j+1$.
+Since~$j \notin I_2$, we note that~$sv \less_B v$ and the restriction of~$I_2$ to~$Q'$ is a facet of~$\subwordComplex(Q', sv)$.
+However, since~$j \in I_1$, the restriction of~$I_1$ to~$Q'$ is a facet of~$\subwordComplex(Q', v)$.
+Therefore, we know that~$v \leqslant_B Dem(Q')$.
+
+We can now apply \cite[proposition 3.14]{JahnStump} to~$I'_2$ the restriction of~$I_2$ to~$Q'$, which tells us that~$\mathcal{E}^+(sv, Dem(Q)) \subseteq \cone \Roots(I'_2)$.
+Since~$sv \less_B v \leqslant Dem(Q)$, then~$\alpha \in \mathcal{E}^+(sv, Dem(Q))$ and so~$\alpha \in \cone \Roots(I'_2)$.
+
+Going back to~$I_2$, we know that~$us(\Roots(I'_2)) \subseteq \Roots(I_2)$ and so~$us(\alpha) = -u(\alpha) = -\beta \in \cone \Roots(I_2)$.
 \end{proof}

### 2023-03-09 acyclicFacets/draft/latticePipeDreams.tex

--- 2023-03-09 acyclicFacets/draft/latticePipeDreams.tex
@@
 \end{figure}
+\vincent{Do we want to redo this picture using sorting networks?}
 \end{example}
@@
 \vincent{I want to delete the remaining of this section, but I want to discuss it with Cesar.}
+
+\nantel{to be honest, I find that the paper ends well here, the rest should be part of a paper by No\'emie alone?}
 

### 2023-03-15 acyclicFacets/draft/latticePipeDreams.tex
add figures sweeping and insertion algorithms

--- 2023-03-09 acyclicFacets/draft/latticePipeDreams.tex
@@
 It is clearly a directed acyclic graph, and it has a unique source and a unique sink \cite{PilaudPocchiola}, called the \defn{greedy} and \defn{antigreedy} pipe dreams, and denoted~$\greedyPipeDream$ and~$\antiGreedyPipeDream$.
-\vincent{In \cite{PilaudStump-ELlabelings}, these are called positive and negative greedy facets. Also the notations are different...}
 The \defn{increasing flip poset} is the reflexive and transitive closure of the increasing flip graph on~$\pipeDreams(\omega)$.
@@
 An extension of this algorithm to subword complexes will be discussed in \cref{subsec:sweepingAlgorithmSubwordComplexes}, and appeared independently in~\cite{JahnStump}.
+We say that an order on the boxes of the triangular shape is \defn{northeast compatible} if each box~$b$ is before all boxes which are located weakly northeast of~$b$.
 
@@
 \label{prop:sweepingAlgorithm}
-For any permutations~$\pi,\omega \in \fS_n$ such that~$\pi < \omega$ in weak order, the unique pipe dream~$P \in \acyclicPipeDreams(\omega)$ such that~$\pi \in \linearExtensions(P)$ can be constructed by sweeping the triangular shape in any perturbation of the northwest direction and placing a crossing when sweeping a vertex~$v$ of the grid where pipe~$i$ arrives horizontally and pipe~$j$ arrives vertically if and only if
+For any permutations~$\pi,\omega \in \fS_n$ such that~$\pi < \omega$ in weak order, the unique pipe dream~$P \in \acyclicPipeDreams(\omega)$ such that~$\pi \in \linearExtensions(P)$ can be constructed by sweeping the triangular shape in any northeast compatible order and placing a crossing when sweeping a vertex~$v$ of the grid where pipe~$i$ arrives horizontally and pipe~$j$ arrives vertically if and only if
 \begin{itemize}
@@
 \end{itemize}
-See \cref{fig:sweepingAlgorithm}.
+See \cref{fig:sweepingAlgorithm1,fig:sweepingAlgorithm2}.
 \end{proposition}
@@
 \label{exm:sweepingAlgorithm}
-\cref{fig:sweepingAlgorithm} illustrates the sweeping algorithm for the permutations~${\pi = 513264}$ and~${\omega = 561324}$.
+\cref{fig:sweepingAlgorithm1,fig:sweepingAlgorithm2} illustrate the sweeping algorithm for the exiting permutation ${\omega = 561324}$ and the input permutations~${\pi = 513264}$ and~${\pi = 512364}$ respectively.
 The algorithm has 15 steps, but we have grouped together steps $2$ to $9$ (second arrow) and steps $12$ to $13$ (fifth arrow) as they have the same justification.
-We place contacts in steps $1$, $10$, $12$, $13$ and~$15$ since~$\omega^{-1}(i) < \omega^{-1}(j)$, and in step~$14$ since~$i > j$.
-We place crossings in steps $2$ to $9$ since~$i < j$, $\omega^{-1}(i) > \omega^{-1}(j)$ and we are in the column~$\omega^{-1}(j)$, and in step $11$ since~$i < j$, $\omega^{-1}(i) > \omega^{-1}(j)$ and~$\pi^{-1}(i) > \pi^{-1}(j)$.
+For~${\pi = 513264}$ in \cref{fig:sweepingAlgorithm1}, we place 
+\begin{itemize}
+\item contacts at steps $1$, $10$, $12$, $13$ and~$15$ since~$\omega^{-1}(i) < \omega^{-1}(j)$, and at step~$14$ since~$i > j$,
+\item crossings at steps $2$ to $9$ since~$i < j$, $\omega^{-1}(i) > \omega^{-1}(j)$ and we are in the column~$\omega^{-1}(j)$, and at step $11$ since~$i < j$, $\omega^{-1}(i) > \omega^{-1}(j)$ and~$\pi^{-1}(i) > \pi^{-1}(j)$.
+\end{itemize}
+For~${\pi = 512364}$ in \cref{fig:sweepingAlgorithm2}, we make the same choices, except that we place 
+\begin{itemize}
+\item a contact at step~$11$ since~$\pi^{-1}(i) < \pi^{-1}(j)$ and we are not in column~$\omega^{-1}(j)$, 
+\item a crossing at step~$14$ since~$i < j$, $\omega^{-1}(i) > \omega^{-1}(j)$ and we are in the column~$\omega^{-1}(j)$.
+\end{itemize}
 %
 \begin{figure}[b]
-	\centerline{\includegraphics[scale=.9]{sweeping}}
+	\centerline{\includegraphics[scale=.9]{sweeping1}}
 	\caption{Sweeping algorithm for the permutations~$\pi = 513264$ and~$\omega = 561324$.} % See details in \cref{exm:sweepingAlgorithm}.}
-	\label{fig:sweepingAlgorithm}
+	\label{fig:sweepingAlgorithm1}
+\end{figure}
+%
+\begin{figure}[b]
+	\centerline{\includegraphics[scale=.9]{sweeping2}}
+	\caption{Sweeping algorithm for the permutations~$\pi = 512364$ and~$\omega = 561324$.} % See details in \cref{exm:sweepingAlgorithm}.}
+	\label{fig:sweepingAlgorithm2}
 \end{figure}
@@
 %More precisely, at step~$t$, we consider the set~$X_t$ of free southeast elbows in the rectangle~$[\pi(t)] \times [\omega^{-1}(\pi(t))]$, and we insert a pipe starting at row~$\pi(t)$, ending at column~$\omega^{-1}(\pi(t))$, and whose northeast elbows are precisely covering the elbows of~$X_t$, and adding a new free southeast elbow in between any two consecutive elbows of~$X_t$
-See \cref{fig:insertionAlgorithm}.
+See \cref{fig:insertionAlgorithm1,fig:insertionAlgorithm2}.
 \end{proposition}
@@
 \label{exm:insertionAlgorithm}
-\cref{fig:insertionAlgorithm} illustrates the insertion algorithm for the permutations~${\pi = 513264}$ and~${\omega = 561324}$.
+\cref{fig:insertionAlgorithm1,fig:insertionAlgorithm2} illustrate the insertion algorithm for the exiting permutation ${\omega = 561324}$ and the input permutations~${\pi = 513264}$ and~${\pi = 512364}$ respectively.
 For instance, when inserting the (green) pipe~$4$ in the last step, the currently free southeast elbows are the first southeast elbow of the (blue) pipe~$3$ and the two southeast elbows of the (purple) pipe~$2$.
@@
 \begin{figure}[b]
-	\centerline{\includegraphics[scale=.9]{insertion}}
+	\centerline{\includegraphics[scale=.9]{insertion1}}
 	\caption{Insertion algorithm for the permutations~$\pi = 513264$ and~$\omega = 561324$.}
-	\label{fig:insertionAlgorithm}
+	\label{fig:insertionAlgorithm1}
+\end{figure}
+%
+\begin{figure}[b]
+	\centerline{\includegraphics[scale=.9]{insertion2}}
+	\caption{Insertion algorithm for the permutations~$\pi = 512364$ and~$\omega = 561324$.}
+	\label{fig:insertionAlgorithm2}
 \end{figure}

### 2023-03-16 acyclicFacets/draft/latticePipeDreams.tex
many pictures

@@
 
-\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap, a4wide, pdflscape, multido, xargs, colortbl, multicol, multirow, calc, shuffle}
+\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap, a4wide, pdflscape, multido, xargs, colortbl, multicol, multirow, calc, shuffle, hvfloat}
 \hypersetup{colorlinks=true, citecolor=PineGreen, linkcolor=PineGreen}
@@
 \usepackage[noabbrev,capitalise]{cleveref}
+\setlength{\abovecaptionskip}{10pt}
+\setlength{\belowcaptionskip}{5pt}
 
@@
 
-Note that we recover the connection between the weak order and the Tamari lattice by the sylvester congruence for a well-chosen exiting permutation~$\omega$.
+We recover the connection between the weak order and the Tamari lattice by the sylvester congruence for a well-chosen exiting permutation~$\omega$.
+Note that \cref{thm:A} is the correct generalization of the Tamari lattice, as neither the increasing flip poset on all pipe dreams, nor its subposet induced by acyclic pipe dreams, are lattices in general (see \cref{rem:increasingFlipPosetNotLattice,rem:acyclicIncreasingFlipPosetNotLattice}).
 
@@
 In the case when~$[e, \omega]$ does not contain all sets of linear extensions, it is natural to consider the restriction of this partition to~$[e, \omega]$ by the sets~$[e, \omega] \cap \linearExtensions(\omega)$.
-This defines an equivalence relation~$\equiv_{Q, \omega}$ on~$[e, \omega]$ that we call the subword complex congruence.
-However, as the sets of linear extensions are not always intervals of the weak order, this equivalence relation is not always a lattice congruence.
+This defines an equivalence relation~$\equiv_{Q, \omega}$ on~$[e, \omega]$ that we call the subword complex equivalence.
+As the sets of linear extensions are not always intervals of the weak order, this equivalence relation is not always a lattice congruence.
 This seems to be fixed by an additional assumption on~$Q$.
@@
 \label{conj:D}
-If~$Q$ is sorting and alternating, then the oriented graph of the brick polyhedron~$\brickPolyhedron(Q, \omega)$ is isomorphic to the Hasse diagram of the lattice quotient~$[e, \omega]/\equiv_{Q, \omega}$.
+If~$Q$ is sorting and alternating, then the bounded oriented graph of the brick polyhedron~$\brickPolyhedron(Q, \omega)$ is isomorphic to the Hasse diagram of the lattice quotient~$[e, \omega]/\equiv_{Q, \omega}$.
 \end{conjectureA}
@@
 %
-As a consequence, this map sends the increasing flip poset on reversing pipe dreams to the \defn{Tamari lattice} on binary trees.
+Hence, this map sends the increasing flip poset on reversing pipe dreams to the \defn{Tamari lattice} on binary trees.
 This lattice is defined as the transitive closure of right rotations on binary trees, and is obtained as the quotient of the weak order by the \defn{sylvester congruence}.
-An important point here is that all reversing pipe dreams are acyclic, since there contact graphs are (oriented) binary trees.
+An important point here is that all reversing pipe dreams are acyclic, since their contact graphs are (oriented)~binary~trees.
 \end{example}
+
+\begin{remark}
+\label{rem:increasingFlipPosetNotLattice}
+In contrast to \cref{exm:Tamari1}, the increasing flip poset on all pipe dreams of~$\pipeDreams(\omega)$ is not always a lattice.
+The first counter-example happens for the exiting permutation~${\omega = 1243}$.
+\end{remark}
 
@@
 
+\enlargethispage{.6cm}
 We now gather some elementary properties of crossings and contacts in pipe dreams that will be needed later to construct pipe dreams from permutations.
@@
 The Hasse diagram of the lattice quotient~$[e,\omega]/{\equiv_\omega}$ is isomorphic to the increasing flip graph on~$\acyclicPipeDreams(\omega)$.
+%Hence, the transitive closure of the increasing flip graph on~$\acyclicPipeDreams(\omega)$ is a lattice.
 \end{theorem}
@@
 \begin{remark}
-\label{rem:pipeDreamQuotient}
+\label{rem:acyclicIncreasingFlipPosetNotLattice}
 The increasing flip poset on~$\pipeDreams(\omega)$ is the transitive closure of the increasing flip graph on~$\pipeDreams(\omega)$.
@@
 \cref{fig:counterExampleRestrictionIncreasingFlipPoset} illustrates two acyclic pipe dreams of~$\acyclicPipeDreams(126543)$ connected by a sequence of increasing flips in~$\pipeDreams(126543)$ but by no sequence of increasing flips in~$\acyclicPipeDreams(126543)$.
+In fact, the subposet of the increasing flip poset induced by~$\acyclicPipeDreams(126543)$ is not even a lattice.
 This example is minimal.
@@
 \begin{example}
-For any Coxeter group~$W$ and any Coxeter element~$c \in W$ (a product of all generators of~$S$ in a given arbitrary order), let~$\wo(c)$ denote the $c$-sorting word of~$\wo$ (the lexicographically minimal reduced expression for~$\wo$ in~$c^\infty$, see \cite{Reading-CambrianLattices} for details).
+\vincent{todo: Introduce here quickly pseudoline arrangements on sorting networks and their contact graphs.}
+\end{example}
+
+\begin{example}
+For any finite Coxeter group~$W$ and any Coxeter element~$c \in W$ (a product of all generators of~$S$ in a given arbitrary order), let~$\wo(c)$ denote the $c$-sorting word of~$\wo$ (the lexicographically minimal reduced expression for~$\wo$ in~$c^\infty$, see \cite{Reading-CambrianLattices} for details).
 Extending the observation of \cref{exm:Tamari1}, it was shown in~\cite{CeballosLabbeStump} that the subword complex~$\subwordComplex(c\wo(c), \wo)$ is isomorphic to the cluster complex of type~$W$.
 In particular, the increasing flip graph is the Hasse diagram of the $c$-Cambrian lattice of~\cite{Reading-CambrianLattices}.
+See \cref{fig:increasingFlipPosets}\,(left) for an example with~$c = \tau_2\tau_1\tau_3$ in type~$A_3$.
+See also \cref{fig:subwordComplex1}.
 \end{example}
@@
 \label{exm:counterExampleLattice}
-In contrast to the previous example, consider the word~$Q = \tau_1 \tau_2 \tau_3 \tau_2 \tau_1 \tau_2 \tau_3 \tau_2 \tau_1$ on the simple generators of the symmetric group~$\fS_4$ and the subword complex~$\subwordComplex(Q,\wo)$.
-Note that all facets in this subword complex are acyclic.
-It is shown in~\cite[Rem.~5.12]{PilaudStump-brickPolytope} that its increasing flip poset is not a lattice.
-This shows that neither the increasing flip poset, nor the acyclic increasing flip poset are lattices in general, even in type~$A$.
+In contrast to the previous example, we have already seen in \cref{rem:increasingFlipPosetNotLattice,rem:acyclicIncreasingFlipPosetNotLattice} that neither the increasing flip poset on all facets, nor its subposet induced by the acyclic facets, are lattices in general, even in type~$A$ and even for pipe dreams.
+Here is another example in type~$A$, but in a case where all facets are actually acyclic.
+Consider the word~$Q = \tau_1 \tau_2 \tau_3 \tau_2 \tau_1 \tau_2 \tau_3 \tau_2 \tau_1$ on the simple generators of the symmetric group~$\fS_4$ and the subword complex~$\subwordComplex(Q,\wo)$.
+The increasing flip lattice of this subword complex is represented in \cref{fig:increasingFlipPosets}, and the highlighted facets in blue and red show that it is not a lattice (this was observed in~\cite[Rem.~5.12]{PilaudStump-brickPolytope}).
+See also \cref{fig:subwordComplex3}.
+%
+\begin{figure}[t]
+	\centerline{
+	\begin{tikzpicture}[xscale=1.7,yscale=1.25,->]
+	\node (123) at (0,-3) {$\{1,2,3\}$};
+	\node (139) at (-2,-2) {$\{1,3,9\}$};
+	\node (234) at (0,-2) {$\{2,3,4\}$};
+	\node (128) at (1.5,-2) {$\{1,2,8\}$};
+	\node (345) at (-1,-1) {$\{3,4,5\}$};
+	\node (246) at (1,-1) {$\{2,4,6\}$};
+	\node (359) at (-2.4,0) {$\{3,5,9\}$};
+	\node (189) at (-1.2,0) {$\{1,8,9\}$};
+	\node (456) at (0,0) {$\{4,5,6\}$};
+	\node (268) at (2,0) {$\{2,6,8\}$};
+	\node (567) at (0,1) {$\{5,6,7\}$};
+	\node (579) at (-1,2) {$\{5,7,9\}$};
+	\node (678) at (1,2) {$\{6,7,8\}$};
+	\node (789) at (0,3) {$\{7,8,9\}$};
+	\draw (123)--(139);
+	\draw (123)--(234);
+	\draw (123)--(128);
+	\draw (139)--(359);
+	\draw (139)--(189);
+	\draw (234)--(345);
+	\draw (234)--(246);
+	\draw (128)--(189);
+	\draw (128)--(268);
+	\draw (345)--(359);
+	\draw (345)--(456);
+	\draw (246)--(456);
+	\draw (246)--(268);
+	\draw (359)--(579);
+	\draw (189)--(789);
+	\draw (456)--(567);
+	\draw (268)--(678);
+	\draw (567)--(579);
+	\draw (567)--(678);
+	\draw (579)--(789);
+	\draw (678)--(789);
+	\end{tikzpicture}
+	\quad
+	\begin{tikzpicture}[xscale=2,yscale=1.5,->]
+	\node (123) at (0,-2.5) {$\{1,2,3\}$};
+	\node (236) at (-1,-1.5) {$\{2,3,6\}$};
+	\node (134) at (0,-1.5) {$\blue{\{1,3,4\}}$};
+	\node (129) at (1.2,-1.5) {$\blue{\{1,2,9\}}$};
+	\node (346) at (-1.8,-.5) {$\{3,4,6\}$};
+	\node (148) at (-.3,-.5) {$\{1,4,8\}$};
+	\node (269) at (.7,-.5) {$\{2,6,9\}$};
+	\node (467) at (-1.8,.5) {$\{4,6,7\}$};
+	\node (189) at (1.5,.5) {$\red{\{1,8,9\}}$};
+	\node (478) at (-1,1.5) {$\{4,7,8\}$};
+	\node (679) at (0,1.5) {$\red{\{6,7,9\}}$};
+	\node (789) at (0,2.5) {$\{7,8,9\}$};
+	\draw (123)--(236);
+	\draw (123)--(134);
+	\draw (123)--(129);
+	\draw (236)--(346);
+	\draw (134)--(346);
+	\draw (134)--(148);
+	\draw (236)--(269);
+	\draw (129)--(269);
+	\draw (346)--(467);
+	\draw (148)--(189);
+	\draw (129)--(189);
+	\draw (148)--(478);
+	\draw (467)--(478);
+	\draw (269)--(679);
+	\draw (467)--(679);
+	\draw (189)--(789);
+	\draw (478)--(789);
+	\draw (679)--(789);
+	\end{tikzpicture}
+	}
+	\caption{The increasing flip graph on~$\subwordComplex(Q, \wo)$ where~$Q = \tau_2 \tau_1 \tau_3 \tau_2 \tau_1 \tau_3 \tau_2 \tau_1 \tau_3$ (left) and~$Q = \tau_1 \tau_2 \tau_3 \tau_2 \tau_1 \tau_2 \tau_3 \tau_2 \tau_1$ (right).
+The left one is the $\tau_2 \tau_1 \tau_3$-Cambrian lattice, while the right one is not a lattice (the two facets highlighted in blue have no join while the two facets highlighted in red have no meet).
+In both examples, all facets are acyclic.}
+	\label{fig:increasingFlipPosets}
+\end{figure}
 \end{example}
@@
 
+\begin{example}
+We have represented $5$ examples in \cref{fig:subwordComplex1,fig:subwordComplex2,fig:subwordComplex3,fig:subwordComplex4,fig:subwordComplex5}.
+The first $3$ use~$\omega = \wo$ and are spherical subword complexes (their brick polytopes are represented in \cref{fig:brickPolytope1,fig:brickPolytope2,fig:brickPolytope3}), while the last $2$ do not.
+%
+\hvFloat[floatPos=p, capWidth=h, capPos=r, capAngle=90, objectAngle=90, capVPos=c, objectPos=c]{figure}
+{\includegraphics[scale=.6]{subwordComplex1}}
+{For~$Q = \tau_2 \tau_1 \tau_3 \tau_2 \tau_1 \tau_3 \tau_2 \tau_1 \tau_3$ and~$\omega = \wo$, the subword complex equivalence is a lattice congruence (left) so that the increasing flip poset is a lattice (right).
+It is actually the $\tau_2\tau_1\tau_3$-Cambrian lattice.
+The blue bubbles represent the classes of the pipe dream congruence.
+For each facet of the subword complex, we have represented the corresponding pseudoline arrangement on the sorting network, and the corresponding contact graph.
+Note that all facets are acyclic in this case.}
+{fig:subwordComplex1}
+%
+\hvFloat[floatPos=p, capWidth=h, capPos=r, capAngle=90, objectAngle=90, capVPos=c, objectPos=c]{figure}
+{\includegraphics[scale=.7]{subwordComplex2}}
+{For~$Q = \tau_2 \tau_3 \tau_1 \tau_3 \tau_2 \tau_1 \tau_2 \tau_3 \tau_1$ and~$\omega = \wo$, the subword complex equivalence is not a lattice congruence (left) but the increasing flip poset is a lattice (right).
+The blue bubbles represent the classes of the pipe dream congruence.
+For each facet of the subword complex, we have represented the corresponding pseudoline arrangement on the sorting network, and the corresponding contact graph.
+Note that all facets are acyclic in this case.}
+{fig:subwordComplex2}
+%
+\hvFloat[floatPos=p, capWidth=h, capPos=r, capAngle=90, objectAngle=90, capVPos=c, objectPos=c]{figure}
+{\includegraphics[scale=.7]{subwordComplex3}}
+{For~$Q = \tau_1 \tau_2 \tau_3 \tau_2 \tau_1 \tau_2 \tau_3 \tau_2 \tau_1$ and~$\omega = \wo$, the subword complex equivalence is not a lattice congruence (left) and the increasing flip poset is not a lattice (right).
+The blue bubbles represent the classes of the pipe dream congruence.
+For each facet of the subword complex, we have represented the corresponding pseudoline arrangement on the sorting network, and the corresponding contact graph.
+Note that all facets are acyclic in this case.}
+{fig:subwordComplex3}
+\end{example}
+
 \begin{remark}
@@
 \item While the sets~$\linearExtensions(I)$ are order convex, they may not be intervals.
-See \cref{fig:counterExample2}.
-Another example with~$\omega = \omega_\circ$ can be found in~\cite[Figure~9]{PilaudStump-brickPolytope}.
+See \cref{fig:subwordComplex2,fig:subwordComplex4} (the example of \cref{fig:subwordComplex2} is borrowed from~\cite[Figure~9]{PilaudStump-brickPolytope}).
 %
 \begin{figure}[p]
-	\centerline{\includegraphics[scale=.8]{counterExample2}}
+	\centerline{\includegraphics[scale=.8]{subwordComplex4}}
 	\caption{The sets~$\linearExtensions(I)$ (blue bulles) are not always intervals.}
-	\label{fig:counterExample2}
+	\label{fig:subwordComplex4}
 \end{figure}
 
-\item The lower set~$\linearExtensions(Q,\omega)$ may have more than one maximal element, and~$\omega$ is not necessarily maximal in~$\linearExtensions(Q,\omega)$. See \cref{fig:counterExample1}.
-
-\item Some of the sets~$\linearExtensions(I)$ may not be included in, nor even meet~$[e,\omega]$. See \cref{fig:counterExample1}.
+\item The lower set~$\linearExtensions(Q,\omega)$ may have more than one maximal element, and~$\omega$ is not necessarily maximal in~$\linearExtensions(Q,\omega)$. See \cref{fig:subwordComplex5}.
+
+\item Some of the sets~$\linearExtensions(I)$ may not be included in, nor even meet~$[e,\omega]$. See \cref{fig:subwordComplex5}.
 %
@@
 \begin{figure}[p]
-	\centerline{\includegraphics[scale=.8]{counterExample1}}
+	\centerline{\includegraphics[scale=.8]{subwordComplex5}}
 	\caption{The sets~$\linearExtensions(I)$ (blue bubbles) are not always subsets of, and may even not meet~$[e,\omega]$ (green bubble).}
-	\label{fig:counterExample1}
+	\label{fig:subwordComplex5}
 \end{figure}
 \end{enumerate}
-Note that \cref{fig:counterExample1,fig:counterExample2} represent type~$A$ subword complexes.
+Note that \cref{fig:subwordComplex4,fig:subwordComplex5} represent type~$A$ subword complexes.
 As in~\cite{PilaudPocchiola, PilaudSantos-brickPolytope, PilaudStump-brickPolytope}, we thus use pseudoline arrangements on sorting networks to represent their facets (and we have represented their contact graphs together).
@@
 
+\begin{example}
+Observe for instance that:
+\begin{itemize}
+\item the subword complex equivalence is a lattice congruence of the weak order in \cref{fig:subwordComplex1} but not in \cref{fig:subwordComplex2,fig:subwordComplex3},
+\item the increasing flip poset is a lattice in \cref{fig:subwordComplex1,fig:subwordComplex2} but not in \cref{fig:subwordComplex3}.
+\end{itemize}
+\end{example}
+
 Despite its name, this equivalence relation is not always a congruence because of Issue~(ii) above.
@@
 	\begin{tikzpicture}[xscale=1.5,->]
-	\node (123) at (0,-2.5) {$\{1,2,3\}$};
-	\node (134) at (-1,-1.5) {$\{1,3,4\}$};
-	\node (126) at (0.3,-.5) {$\{1,2,6\}$};
-	\node (236) at (1,-1.5) {$\{2,3,6\}$};
-	\node (145) at (-1,1.5) {$\{1,4,5\}$};
-	\node (156) at (-0.3,.5) {$\{1,5,6\}$};
-	\node (346) at (1,1.5) {$\{3,4,6\}$};
-	\node (456) at (0,2.5) {$\{4,5,6\}$};
+	\node (123) at (0,-2) {$\{1,2,3\}$};
+	\node (134) at (-1,-1) {$\{1,3,4\}$};
+	\node (126) at (0,-.8) {$\{1,2,6\}$};
+	\node (236) at (1,0) {$\{2,3,6\}$};
+	\node (145) at (-1,0) {$\{1,4,5\}$};
+	\node (156) at (0,.8) {$\{1,5,6\}$};
+	\node (346) at (1,1) {$\{3,4,6\}$};
+	\node (456) at (0,2) {$\{4,5,6\}$};
 	\draw (123)--(134);
@@
 	\draw (126)--(156);
-	\draw (236)--(126);
+	\draw (126)--(236);
 	\draw (236)--(346);
 	\draw (145)--(456);
-	\draw (156)--(145);
+	\draw (145)--(156);
 	\draw (156)--(456);
@@
 	\begin{tikzpicture}[xscale=1.5,->]
-	\node (123) at (0,-2.5) {$\{1,2,3\}$};
-	\node (134) at (-1,-1.5) {$\{1,3,4\}$};
-	\node (236) at (1,-1.5) {$\{2,3,6\}$};
-	\node (145) at (-1,1.5) {$\{1,4,5\}$};
-	\node (346) at (1,1.5) {$\{3,4,6\}$};
-	\node (456) at (0,2.5) {$\{4,5,6\}$};
+	\node (123) at (0,-2) {$\{1,2,3\}$};
+	\node (134) at (-1,-1) {$\{1,3,4\}$};
+	\node (236) at (1,0) {$\{2,3,6\}$};
+	\node (145) at (-1,0) {$\{1,4,5\}$};
+	\node (346) at (1,1) {$\{3,4,6\}$};
+	\node (456) at (0,2) {$\{4,5,6\}$};
 	\draw (123)--(134);
@@
 \end{figure}
-\vincent{Do we want to redo this picture using sorting networks?}
 \end{example}
@@
 \end{remark}
+
+\begin{example}
+\vincent{todo: explain}
+\begin{figure}[p]
+	\centerline{\input{figures/brickPolytope1}}
+	\caption{The brick polytope of the subword complexe...}
+	\label{fig:brickPolytope1}
+\end{figure}
+%
+\begin{figure}[p]
+	\centerline{\input{figures/brickPolytope2}}
+	\caption{The brick polytope of the subword complexe...}
+	\label{fig:brickPolytope2}
+\end{figure}
+%
+\begin{figure}[p]
+	\centerline{\input{figures/brickPolytope3}}
+	\caption{The brick polytope of the subword complexe...}
+	\label{fig:brickPolytope3}
+\end{figure}
+\end{example}
 

### 2023-03-16 acyclicFacets/draft/latticePipeDreams.tex
change congruence to equivalence

@@
 \label{conj:A}
-If~$Q$ is alternating, then the subword complex congruence~$\equiv_{Q, \omega}$ is a lattice congruence of the interval~$[e, \omega]$ of the weak order.
+If~$Q$ is alternating, then the subword complex equivalence~$\equiv_{Q, \omega}$ is a lattice congruence of the interval~$[e, \omega]$ of the weak order.
 \end{conjectureA}
@@
 \label{def:pipeDreamCongruenceSubwordComplexes}
-For a non-empty subword complex $\subwordComplex(Q,\omega)$, the \defn{subword complex congruence} is the equivalence relation~$\equiv_{Q,\omega}$ on the interval~$[e, \omega]$  whose equivalence classes are the sets~$\strongLinearExtensions(I)$ of linear extensions of strongly acyclic facets~$I$ of~$\subwordStronglyAcyclicFacets(Q, \omega)$.
+For a non-empty subword complex $\subwordComplex(Q,\omega)$, the \defn{subword complex equivalence} is the equivalence relation~$\equiv_{Q,\omega}$ on the interval~$[e, \omega]$  whose equivalence classes are the sets~$\strongLinearExtensions(I)$ of linear extensions of strongly acyclic facets~$I$ of~$\subwordStronglyAcyclicFacets(Q, \omega)$.
 In other words, $\pi \equiv_{Q,\omega} \pi'$ if and only if $\pi$ and $\pi'$ are linear extensions of the same facet.  
 \end{definition}
-
-\nantel{it is bad to name this ``congruence". Call it equivalence, and state it is a concruence in the conjecture.}
 
@@
 
-Despite its name, this equivalence relation is not always a congruence because of Issue~(ii) above.
+The subword complex equivalence is not always a congruence because of Issue~(ii) above.
 To fix it, we now assume that the word~$Q$ is \defn{alternating}, meaning that all non-commuting pairs $s, t\in S$ alternate within $Q$ (this notion was already considered in \cite{PilaudSantos-brickPolytope, CeballosLabbeStump}).
@@
 \label{conj:latticeCongruenceAlternating}
-For a non-empty subword complex $\subwordComplex(Q,\omega)$ where~$Q$ is alternating, the subword complex congruence~$\equiv_{Q,\omega}$ is a lattice congruence of the interval~$[e,\omega]$ of the weak order.
+For a non-empty subword complex $\subwordComplex(Q,\omega)$ where~$Q$ is alternating, the subword complex equivalence~$\equiv_{Q,\omega}$ is a lattice congruence of the interval~$[e,\omega]$ of the weak order.
 \end{conjecture}

### 2023-03-16 acyclicFacets/draft/latticePipeDreams.tex
last changes

@@
 \renewcommand{\b}[1]{\boldsymbol{#1}} % bold
+\newcommand{\cal}[1]{\mathcal{#1}} % cal
 
@@
 \begin{example}
-\vincent{todo: Introduce here quickly pseudoline arrangements on sorting networks and their contact graphs.}
+More generally, for the type~$A_n$ Coxeter system, the word~$Q$ can be represented by a sorting network~$\cal{N}$, a facet~$I$ of the subword complex~$\subwordComplex(Q,w)$ can be represented by a pseudoline arrangement~$P_I$ on the network~$\cal{N}$, and the root configuration~$\Roots(I)$ is again the incidence configuration of the contact graph of~$P_I$.
+We refer to~\cite{PilaudPocchiola, PilaudSantos-brickPolytope, PilaudStump-brickPolytope} for details of this representation and use it in \cref{fig:subwordComplex1,fig:subwordComplex2,fig:subwordComplex3,fig:subwordComplex4,fig:subwordComplex5}.
 \end{example}
@@
 In particular, the increasing flip graph is the Hasse diagram of the $c$-Cambrian lattice of~\cite{Reading-CambrianLattices}.
-See \cref{fig:increasingFlipPosets}\,(left) for an example with~$c = \tau_2\tau_1\tau_3$ in type~$A_3$.
-See also \cref{fig:subwordComplex1}.
+See \cref{fig:increasingFlipPosets}\,(left) and \cref{fig:subwordComplex1} for an example with~$c = \tau_2\tau_1\tau_3$ in type~$A_3$.
 \end{example}
@@
 Consider the word~$Q = \tau_1 \tau_2 \tau_3 \tau_2 \tau_1 \tau_2 \tau_3 \tau_2 \tau_1$ on the simple generators of the symmetric group~$\fS_4$ and the subword complex~$\subwordComplex(Q,\wo)$.
-The increasing flip lattice of this subword complex is represented in \cref{fig:increasingFlipPosets}, and the highlighted facets in blue and red show that it is not a lattice (this was observed in~\cite[Rem.~5.12]{PilaudStump-brickPolytope}).
-See also \cref{fig:subwordComplex3}.
+The increasing flip lattice of this subword complex is represented in \cref{fig:increasingFlipPosets}\,(right) and \cref{fig:subwordComplex3}.
+In \cref{fig:increasingFlipPosets}\,(right), we have highlighted two blue facets which have no join and two red facets which have no meet, proving that it is not a lattice (this was observed in~\cite[Rem.~5.12]{PilaudStump-brickPolytope}).
 %
@@
 	}
-	\caption{The increasing flip graph on~$\subwordComplex(Q, \wo)$ where~$Q = \tau_2 \tau_1 \tau_3 \tau_2 \tau_1 \tau_3 \tau_2 \tau_1 \tau_3$ (left) and~$Q = \tau_1 \tau_2 \tau_3 \tau_2 \tau_1 \tau_2 \tau_3 \tau_2 \tau_1$ (right).
+	\caption{The increasing flip graph on~$\subwordComplex(Q, \wo)$ where~$Q = \tau_2 \tau_1 \tau_3 \tau_2 \tau_1 \tau_3 \tau_2 \tau_1 \tau_3$ (left) and~$Q = \tau_1 \tau_2 \tau_3 \tau_2 \tau_1 \tau_2 \tau_3 \tau_2 \tau_1$ (right) in type~$A_3$.
 The left one is the $\tau_2 \tau_1 \tau_3$-Cambrian lattice, while the right one is not a lattice (the two facets highlighted in blue have no join while the two facets highlighted in red have no meet).
@@
 We have represented $5$ examples in \cref{fig:subwordComplex1,fig:subwordComplex2,fig:subwordComplex3,fig:subwordComplex4,fig:subwordComplex5}.
-The first $3$ use~$\omega = \wo$ and are spherical subword complexes (their brick polytopes are represented in \cref{fig:brickPolytope1,fig:brickPolytope2,fig:brickPolytope3}), while the last $2$ do not.
+The last $3$ use~$\omega = \wo$ and are spherical subword complexes (their brick polytopes are represented in \cref{fig:brickPolytope1,fig:brickPolytope2,fig:brickPolytope3}), while the first $2$ do not.
+%
+\begin{figure}[p]
+	\centerline{\includegraphics[scale=.7]{subwordComplex4}}
+	\caption{The subword complex equivalence (left) and the acyclic increasing flip graph (right) for~$Q = \tau_2 \tau_3 \tau_1 \tau_3 \tau_2 \tau_1 \tau_2 \tau_3 \tau_1$ and~$w = \tau_2 \tau_3 \tau_1 \tau_2 \tau_3 = 3421$ in type~$A_3$.
+Note that the sets~$\linearExtensions(I)$ (blue bulles) are not always intervals.}
+	\label{fig:subwordComplex4}
+\end{figure}
+%
+\begin{figure}[p]
+	\centerline{\includegraphics[scale=.7]{subwordComplex5}}
+	\caption{The subword complex equivalence (left) and the acyclic increasing flip graph (right) for~$Q = \tau_3 \tau_4 \tau_1 \tau_3 \tau_2 \tau_4 \tau_1 \tau_2$ and~$w = \tau_3 \tau_4 \tau_1 \tau_2 = 24153$ in type~$A_4$.
+Note that the sets~$\linearExtensions(I)$ (blue bubbles) are not always subsets of, and may even not meet~$[e,\omega]$ (green bubble).}
+	\label{fig:subwordComplex5}
+\end{figure}
 %
@@
 {\includegraphics[scale=.6]{subwordComplex1}}
-{For~$Q = \tau_2 \tau_1 \tau_3 \tau_2 \tau_1 \tau_3 \tau_2 \tau_1 \tau_3$ and~$\omega = \wo$, the subword complex equivalence is a lattice congruence (left) so that the increasing flip poset is a lattice (right).
-It is actually the $\tau_2\tau_1\tau_3$-Cambrian lattice.
+{For~$Q = \tau_2 \tau_1 \tau_3 \tau_2 \tau_1 \tau_3 \tau_2 \tau_1 \tau_3$ and~$\omega = \wo = 4321$ in type~$A_3$, the subword complex equivalence is a lattice congruence (left) so that the increasing flip poset is a lattice (right).
+See also~\cref{fig:increasingFlipPosets}\,(left) It is actually the $\tau_2\tau_1\tau_3$-Cambrian lattice in type~$A_3$.
 The blue bubbles represent the classes of the pipe dream congruence.
@@
 {\includegraphics[scale=.7]{subwordComplex2}}
-{For~$Q = \tau_2 \tau_3 \tau_1 \tau_3 \tau_2 \tau_1 \tau_2 \tau_3 \tau_1$ and~$\omega = \wo$, the subword complex equivalence is not a lattice congruence (left) but the increasing flip poset is a lattice (right).
+{For~$Q = \tau_2 \tau_3 \tau_1 \tau_3 \tau_2 \tau_1 \tau_2 \tau_3 \tau_1$ and~$\omega = \wo = 4321$ in type~$A_3$, the subword complex equivalence is not a lattice congruence (left) but the increasing flip poset is a lattice (right).
 The blue bubbles represent the classes of the pipe dream congruence.
@@
 {\includegraphics[scale=.7]{subwordComplex3}}
-{For~$Q = \tau_1 \tau_2 \tau_3 \tau_2 \tau_1 \tau_2 \tau_3 \tau_2 \tau_1$ and~$\omega = \wo$, the subword complex equivalence is not a lattice congruence (left) and the increasing flip poset is not a lattice (right).
+{For~$Q = \tau_1 \tau_2 \tau_3 \tau_2 \tau_1 \tau_2 \tau_3 \tau_2 \tau_1$ and~$\omega = \wo = 4321$ in type~$A_3$, the subword complex equivalence is not a lattice congruence (left) and the increasing flip poset is not a lattice (right).
+See also~\cref{fig:increasingFlipPosets}\,(right).
 The blue bubbles represent the classes of the pipe dream congruence.
@@
 See \cref{fig:subwordComplex2,fig:subwordComplex4} (the example of \cref{fig:subwordComplex2} is borrowed from~\cite[Figure~9]{PilaudStump-brickPolytope}).
-%
-\begin{figure}[p]
-	\centerline{\includegraphics[scale=.8]{subwordComplex4}}
-	\caption{The sets~$\linearExtensions(I)$ (blue bulles) are not always intervals.}
-	\label{fig:subwordComplex4}
-\end{figure}
-
 \item The lower set~$\linearExtensions(Q,\omega)$ may have more than one maximal element, and~$\omega$ is not necessarily maximal in~$\linearExtensions(Q,\omega)$. See \cref{fig:subwordComplex5}.
-
 \item Some of the sets~$\linearExtensions(I)$ may not be included in, nor even meet~$[e,\omega]$. See \cref{fig:subwordComplex5}.
-%
-%\begin{figure}[h]
-%	\includegraphics[width=0.52\textwidth]{interval_not_contained1} \quad
-%	\includegraphics[width=0.43\textwidth]{interval_not_contained2}
-%	\caption{A facet of a subword complex~$\subwordComplex(Q, \omega)$ whose linear extensions all lie outside the interval~$[e, \omega]$.}
-%	\label{fig:outOfInterval}
-%\end{figure}
-%
-\begin{figure}[p]
-	\centerline{\includegraphics[scale=.8]{subwordComplex5}}
-	\caption{The sets~$\linearExtensions(I)$ (blue bubbles) are not always subsets of, and may even not meet~$[e,\omega]$ (green bubble).}
-	\label{fig:subwordComplex5}
-\end{figure}
 \end{enumerate}
@@
 It is enough to show this when $\pi = \pi's$ for some descent~$s$ of~$\pi$ (\ie some $s\in S$ such that $\ell(\pi') < \ell(\pi)$).
+Define~$\beta=\pi'(\alpha_s)$ and observe that~$s_\beta$ preserves the set~$\pi'(\Phi^+) \ssm \{\beta\} = \pi(\Phi^+) \ssm \{-\beta\} = \pi(\Phi^+) \cap \pi'(\Phi^+)$.
+
+%Now,
+%\[
+%\pi(\Phi^+)= -\Inv(\pi)\sqcup \Ninv(\pi)
+%\]
+%and 
+%\[
+%\Inv(\pi') =\Inv(\pi) \ssm \{\beta\}
+%\qquad\text{and}\qquad
+%\Ninv(\pi') = \Ninv(\pi) \cup \{\beta\}
+%\]
+%for $\beta=\pi'(\alpha_s)$.
+%Therefore,
+%\begin{align*}
+%\pi'(\Phi^+) = \pi(\Phi^+) \ssm \{-\beta\} \cup \{\beta\}.
+%\end{align*}
+%%
+%%\begin{center}
+%%\begin{tikzpicture}
+%%\coordinate (a) at (0,0);
+%%\coordinate (b) at (0:2);
+%%\coordinate (c) at (60:2);
+%%\coordinate (d) at (120:2);
+%%\coordinate (e) at (180:2);
+%%\draw (b) node[right] {$\beta$};
+%%\draw (e) node[left] {$-\beta$};
+%%%
+%%\path[fill=green!20] (0,0) --  (60:2) arc(60:180:2) -- cycle;
+%%%
+%%\draw[-stealth,dashed] (a) -- (b);
+%%\draw[-stealth] (a) -- (c);
+%%% \draw[-stealth] (a) -- (d);
+%%\draw[-stealth] (a) -- (e);
+%%\node at (120:1) {$\pi(\Phi^+)$};
+%%\end{tikzpicture} 
+%%%
+%%\qquad
+%%%
+%%\begin{tikzpicture}
+%%\coordinate (a) at (0,0);
+%%\coordinate (b) at (0:2);
+%%\coordinate (c) at (60:2);
+%%\coordinate (d) at (120:2);
+%%\coordinate (e) at (180:2);
+%%\draw (b) node[right] {$\beta$};
+%%\draw (e) node[left] {$-\beta$};
+%%%
+%%\path[fill=green!20] (0,0) -- (0:2) arc(0:120:2)  -- cycle;
+%%%
+%%\draw[-stealth] (a) -- (b);
+%%% \draw[-stealth] (a) -- (c);
+%%\draw[-stealth] (a) -- (d);
+%%\draw[-stealth,dashed] (a) -- (e);
+%%\node at (60:1) {$\pi'(\Phi^+)$};
+%%\end{tikzpicture} 
+%%\end{center}
+%%%
+%Note that the reflection $s_\beta=\pi's\pi'^{-1}$ orthogonal to the root $\beta$ transforms $\pi(\Phi^+)$ and $\pi'(\Phi^+)$ into each other:
+%\[
+%s_\beta(\pi(\Phi^+))=\pi'(\Phi^+).
+%\]
+%Since $s_\beta(\beta)= -\beta$, then $s_\beta$ preserves the set 
+%\[
+%\pi(\Phi^+) \ssm \{-\beta\} = \pi'(\Phi^+) \ssm \{\beta\} = \pi(\Phi^+) \cap \pi'(\Phi^+).
+%\]
+%This observation will be useful to prove the statement in the second of the following two cases.
 
 By definition, $\pi \in \linearExtensions(I)$ if and only if $\Roots(I) \subseteq \pi(\Phi^+)$.
-Now,
-\[
-\pi(\Phi^+)= -\Inv(\pi)\sqcup \Ninv(\pi)
-\]
-and 
-\[
-\Inv(\pi') =\Inv(\pi) \ssm \{\beta\}
-\qquad\text{and}\qquad
-\Ninv(\pi') = \Ninv(\pi) \cup \{\beta\}
-\]
-for $\beta=\pi'(\alpha_s)$.
-Therefore,
-\begin{align*}
-\pi'(\Phi^+) = \pi(\Phi^+) \ssm \{-\beta\} \cup \{\beta\}.
-\end{align*}
-
-\begin{center}
-\begin{tikzpicture}
-\coordinate (a) at (0,0);
-\coordinate (b) at (0:2);
-\coordinate (c) at (60:2);
-\coordinate (d) at (120:2);
-\coordinate (e) at (180:2);
-\draw (b) node[right] {$\beta$};
-\draw (e) node[left] {$-\beta$};
-%
-\path[fill=green!20] (0,0) --  (60:2) arc(60:180:2) -- cycle;
-%
-\draw[-stealth,dashed] (a) -- (b);
-\draw[-stealth] (a) -- (c);
-% \draw[-stealth] (a) -- (d);
-\draw[-stealth] (a) -- (e);
-\node at (120:1) {$\pi(\Phi^+)$};
-\end{tikzpicture} 
-%
-\qquad
-%
-\begin{tikzpicture}
-\coordinate (a) at (0,0);
-\coordinate (b) at (0:2);
-\coordinate (c) at (60:2);
-\coordinate (d) at (120:2);
-\coordinate (e) at (180:2);
-\draw (b) node[right] {$\beta$};
-\draw (e) node[left] {$-\beta$};
-%
-\path[fill=green!20] (0,0) -- (0:2) arc(0:120:2)  -- cycle;
-%
-\draw[-stealth] (a) -- (b);
-% \draw[-stealth] (a) -- (c);
-\draw[-stealth] (a) -- (d);
-\draw[-stealth,dashed] (a) -- (e);
-\node at (60:1) {$\pi'(\Phi^+)$};
-\end{tikzpicture} 
-\end{center}
-%
-Note that the reflection $s_\beta=\pi's\pi'^{-1}$ orthogonal to the root $\beta$ transforms $\pi(\Phi^+)$ and $\pi'(\Phi^+)$ into each other:
-\[
-s_\beta(\pi(\Phi^+))=\pi'(\Phi^+).
-\]
-Since $s_\beta(\beta)= -\beta$, then $s_\beta$ preserves the set 
-\[
-\pi(\Phi^+) \ssm \{-\beta\} = \pi'(\Phi^+) \ssm \{\beta\} = \pi(\Phi^+) \cap \pi'(\Phi^+).
-\]
-This observation will be useful to prove the statement in the second of the following two cases.
-\vincent{I believe we could shorten all this discussion. Also the picture is not really useful.}
+We now define a new facet $I'$ such that $\pi' \in \linearExtensions(I')$.
+We distinguish two cases, depending on whether or not~$-\beta \in \Roots(I)$.
 
@@
 \label{def:pipeDreamCongruenceSubwordComplexes}
-For a non-empty subword complex $\subwordComplex(Q,\omega)$, the \defn{subword complex equivalence} is the equivalence relation~$\equiv_{Q,\omega}$ on the interval~$[e, \omega]$  whose equivalence classes are the sets~$\strongLinearExtensions(I)$ of linear extensions of strongly acyclic facets~$I$ of~$\subwordStronglyAcyclicFacets(Q, \omega)$.
+For a non-empty subword complex $\subwordComplex(Q,\omega)$, the \defn{subword complex equivalence} is the equivalence relation~$\equiv_{Q,\omega}$ on the interval~$[e, \omega]$  whose equivalence classes are the sets~$\strongLinearExtensions(I)$ for all strongly acyclic facets~$I$ of~$\subwordStronglyAcyclicFacets(Q, \omega)$.
 In other words, $\pi \equiv_{Q,\omega} \pi'$ if and only if $\pi$ and $\pi'$ are linear extensions of the same facet.  
@@
 \end{itemize}
-and that the graph of extremal increasing flips on acyclic facets is isomorphic to the finite part (meaning forgetting the unbounded rays) of the graph of the brick polyhedron~$\brickPolyhedron(Q, \omega)$ oriented in a suitable direction~$\delta$.
+and that the graph of extremal increasing flips on acyclic facets is isomorphic to the bounded graph (meaning forgetting the unbounded rays) of the brick polyhedron~$\brickPolyhedron(Q, \omega)$ oriented in a suitable direction~$\delta$.
 This can be derived from \cite[Thm.~4.4]{JahnStump}.
@@
 \label{conj:latticeQuotientSortingAlternatingBrickPolyhedra}
-If~$Q$ is sorting and alternating, then the finite part of the oriented graph of the brick polyhedron~$\brickPolyhedron(Q, \omega)$ is isomorphic to the Hasse diagram of the lattice quotient~$[e, \omega]/\equiv_{Q, \omega}$.
+If~$Q$ is sorting and alternating, then the bounded oriented graph of the brick polyhedron~$\brickPolyhedron(Q, \omega)$ is isomorphic to the Hasse diagram of the lattice quotient~$[e, \omega]/\equiv_{Q, \omega}$.
 \end{conjecture}
@@
 \begin{example}
-\vincent{todo: explain}
+We have illustrated in \cref{fig:brickPolytope1,fig:brickPolytope2,fig:brickPolytope3} the brick polytopes of the subword complexes represented in \cref{fig:subwordComplex1,fig:subwordComplex2,fig:subwordComplex3}.
+Note that the oriented graph (from bottom to top) defines a lattice in \cref{fig:brickPolytope1,fig:brickPolytope2} but not in \cref{fig:brickPolytope3}.
+%
 \begin{figure}[p]
 	\centerline{\input{figures/brickPolytope1}}
-	\caption{The brick polytope of the subword complexe...}
+	\caption{The brick polytope of~$\subwordComplex(Q,\wo)$ where~$Q = \tau_2 \tau_1 \tau_3 \tau_2 \tau_1 \tau_3 \tau_2 \tau_1 \tau_3$ in type~$A_3$.
+Its graph, oriented from bottom to top is the lattice of \cref{fig:increasingFlipPosets}\,(left) and \cref{fig:subwordComplex1}.
+This is actually the $c$-associahedron and the $c$-Cambrian lattice for the Coxeter element~$c = \tau_2\tau_1\tau_3$ of type~$A_3$.}
 	\label{fig:brickPolytope1}
@@
 	\centerline{\input{figures/brickPolytope2}}
-	\caption{The brick polytope of the subword complexe...}
+	\caption{The brick polytope of~$\subwordComplex(Q,\wo)$ where~$Q = \tau_2 \tau_3 \tau_1 \tau_3 \tau_2 \tau_1 \tau_2 \tau_3 \tau_1$ in type~$A_3$.
+Its graph, oriented from bottom to top is the lattice of \cref{fig:subwordComplex2}, but it is not obtained as a lattice quotient of the weak order.}
 	\label{fig:brickPolytope2}
@@
 	\centerline{\input{figures/brickPolytope3}}
-	\caption{The brick polytope of the subword complexe...}
+	\caption{The brick polytope of~$\subwordComplex(Q,\wo)$ where~$Q = \tau_1 \tau_2 \tau_3 \tau_2 \tau_1 \tau_2 \tau_3 \tau_2 \tau_1$ in type~$A_3$.
+Its graph, oriented from bottom to top is the poset of \cref{fig:increasingFlipPosets}\,(right) and \cref{fig:subwordComplex3}, which is not a lattice.}
 	\label{fig:brickPolytope3}
@@
 
-\vincent{I want to delete the remaining of this section, but I want to discuss it with Cesar.}
-
-\nantel{to be honest, I find that the paper ends well here, the rest should be part of a paper by No\'emie alone?}
-
-As we have seen in \cref{cor_acyclicpipedreams_lattice}, the increasing flip poset of acyclic pipe dreams of any permutation $\omega$ is a lattice, because it is isomorphic to the lattice quotient~$[e,\omega]/\equiv_\omega$.
-This motivates the following open question for subword complexes.
-
-\begin{question}
-Let $\subwordComplex(Q,\omega)$ be a non-empty subword complex.
-Is the restriction of the increasing flip poset of $\subwordComplex(Q,\omega)$ to the set of acyclic facets a lattice?    
-\end{question}
-
-As pointed out in \cref{rem_acyclicflipposet_not_latticequotient},  we can not expect~$[e,\omega]/\equiv_{Q,\omega}$ to be isomorphic to the restriction of the increasing flip poset of $\subwordComplex(Q,\omega)$ to the set of acyclic facets.
-\cref{exm:acyclicFlipvsWeakOrder} shows that there are flips between acyclic facets that are not detected by the week order.
-One could expect that there is a natural restriction to a special class of flips that behave nicer, meaning that all of them are identified by the quotient~$[e,\omega]/\equiv_{Q,\omega}$.
-In our \cref{exm:acyclicFlipvsWeakOrder}, the generalized Chute moves from~\cite{Rubey} do the job, because the flip that is not detected by the week order is exactly the one flip which is not Chute.
-The Chute lattice conjecture~\cite[Conjecture~2.8]{Rubey} might be an indication that this is the right direction to look at.
+%As pointed out in \cref{rem_acyclicflipposet_not_latticequotient},  we can not expect~$[e,\omega]/\equiv_{Q,\omega}$ to be isomorphic to the restriction of the increasing flip poset of $\subwordComplex(Q,\omega)$ to the set of acyclic facets.
+%\cref{exm:acyclicFlipvsWeakOrder} shows that there are flips between acyclic facets that are not detected by the week order.
+%One could expect that there is a natural restriction to a special class of flips that behave nicer, meaning that all of them are identified by the quotient~$[e,\omega]/\equiv_{Q,\omega}$.
+%In our \cref{exm:acyclicFlipvsWeakOrder}, the generalized Chute moves from~\cite{Rubey} do the job, because the flip that is not detected by the week order is exactly the one flip which is not Chute.
+%The Chute lattice conjecture~\cite[Conjecture~2.8]{Rubey} might be an indication that this is the right direction to look at.
 

### 2023-03-16 acyclicFacets/draft/latticePipeDreams.tex
minor last changes

@@
 In contrast to \cref{exm:Tamari1}, the increasing flip poset on all pipe dreams of~$\pipeDreams(\omega)$ is not always a lattice.
-The first counter-example happens for the exiting permutation~${\omega = 1243}$.
+The first counter-example happens for the exiting permutation~${\omega = 12543}$.
 \end{remark}
@@
 \begin{example}
+\label{exm:sortingNetworks}
 More generally, for the type~$A_n$ Coxeter system, the word~$Q$ can be represented by a sorting network~$\cal{N}$, a facet~$I$ of the subword complex~$\subwordComplex(Q,w)$ can be represented by a pseudoline arrangement~$P_I$ on the network~$\cal{N}$, and the root configuration~$\Roots(I)$ is again the incidence configuration of the contact graph of~$P_I$.
@@
 The last $3$ use~$\omega = \wo$ and are spherical subword complexes (their brick polytopes are represented in \cref{fig:brickPolytope1,fig:brickPolytope2,fig:brickPolytope3}), while the first $2$ do not.
+We use the representation of the facets as pseudoline arrangements on sorting networks, see \cref{exm:sortingNetworks}.
 %
@@
 \end{enumerate}
-Note that \cref{fig:subwordComplex4,fig:subwordComplex5} represent type~$A$ subword complexes.
-As in~\cite{PilaudPocchiola, PilaudSantos-brickPolytope, PilaudStump-brickPolytope}, we thus use pseudoline arrangements on sorting networks to represent their facets (and we have represented their contact graphs together).
+%Note that \cref{fig:subwordComplex4,fig:subwordComplex5} represent type~$A$ subword complexes.
+%As in~\cite{PilaudPocchiola, PilaudSantos-brickPolytope, PilaudStump-brickPolytope}, we thus use pseudoline arrangements on sorting networks to represent their facets (and we have represented their contact graphs together).
 \end{remark}

### 2023-03-16 acyclicFacets/draft/latticePipeDreams.tex
numbers

@@
 \begin{example}
-We have represented $5$ examples in \cref{fig:subwordComplex1,fig:subwordComplex2,fig:subwordComplex3,fig:subwordComplex4,fig:subwordComplex5}.
-The last $3$ use~$\omega = \wo$ and are spherical subword complexes (their brick polytopes are represented in \cref{fig:brickPolytope1,fig:brickPolytope2,fig:brickPolytope3}), while the first $2$ do not.
+We have represented five examples in \cref{fig:subwordComplex1,fig:subwordComplex2,fig:subwordComplex3,fig:subwordComplex4,fig:subwordComplex5}.
+The last three use~$\omega = \wo$ and are spherical subword complexes (their brick polytopes are represented in \cref{fig:brickPolytope1,fig:brickPolytope2,fig:brickPolytope3}), while the first two do not.
 We use the representation of the facets as pseudoline arrangements on sorting networks, see \cref{exm:sortingNetworks}.

### 2023-03-16 acyclicFacets/draft/latticePipeDreams.tex
title subsection

@@
 \hvFloat[floatPos=p, capWidth=h, capPos=r, capAngle=90, objectAngle=90, capVPos=c, objectPos=c]{figure}
-{\includegraphics[scale=.6]{subwordComplex1}}
+{\includegraphics[scale=.55]{subwordComplex1}}
 {For~$Q = \tau_2 \tau_1 \tau_3 \tau_2 \tau_1 \tau_3 \tau_2 \tau_1 \tau_3$ and~$\omega = \wo = 4321$ in type~$A_3$, the subword complex equivalence is a lattice congruence (left) so that the increasing flip poset is a lattice (right).
@@
 \hvFloat[floatPos=p, capWidth=h, capPos=r, capAngle=90, objectAngle=90, capVPos=c, objectPos=c]{figure}
-{\includegraphics[scale=.7]{subwordComplex2}}
+{\includegraphics[scale=.65]{subwordComplex2}}
 {For~$Q = \tau_2 \tau_3 \tau_1 \tau_3 \tau_2 \tau_1 \tau_2 \tau_3 \tau_1$ and~$\omega = \wo = 4321$ in type~$A_3$, the subword complex equivalence is not a lattice congruence (left) but the increasing flip poset is a lattice (right).
@@
 \hvFloat[floatPos=p, capWidth=h, capPos=r, capAngle=90, objectAngle=90, capVPos=c, objectPos=c]{figure}
-{\includegraphics[scale=.7]{subwordComplex3}}
+{\includegraphics[scale=.65]{subwordComplex3}}
 {For~$Q = \tau_1 \tau_2 \tau_3 \tau_2 \tau_1 \tau_2 \tau_3 \tau_2 \tau_1$ and~$\omega = \wo = 4321$ in type~$A_3$, the subword complex equivalence is not a lattice congruence (left) and the increasing flip poset is not a lattice (right).
@@
 	\caption{The brick polytope of~$\subwordComplex(Q,\wo)$ where~$Q = \tau_2 \tau_1 \tau_3 \tau_2 \tau_1 \tau_3 \tau_2 \tau_1 \tau_3$ in type~$A_3$.
-Its graph, oriented from bottom to top is the lattice of \cref{fig:increasingFlipPosets}\,(left) and \cref{fig:subwordComplex1}.
+Its graph, oriented from bottom to top is the Hasse diagram of the lattice of \cref{fig:increasingFlipPosets}\,(left) and \cref{fig:subwordComplex1}.
 This is actually the $c$-associahedron and the $c$-Cambrian lattice for the Coxeter element~$c = \tau_2\tau_1\tau_3$ of type~$A_3$.}
@@
 	\caption{The brick polytope of~$\subwordComplex(Q,\wo)$ where~$Q = \tau_2 \tau_3 \tau_1 \tau_3 \tau_2 \tau_1 \tau_2 \tau_3 \tau_1$ in type~$A_3$.
-Its graph, oriented from bottom to top is the lattice of \cref{fig:subwordComplex2}, but it is not obtained as a lattice quotient of the weak order.}
+Its graph, oriented from bottom to top is the Hasse diagram of the lattice of \cref{fig:subwordComplex2}, but it is not obtained as a lattice quotient of the weak order.}
 	\label{fig:brickPolytope2}
@@
 	\caption{The brick polytope of~$\subwordComplex(Q,\wo)$ where~$Q = \tau_1 \tau_2 \tau_3 \tau_2 \tau_1 \tau_2 \tau_3 \tau_2 \tau_1$ in type~$A_3$.
-Its graph, oriented from bottom to top is the poset of \cref{fig:increasingFlipPosets}\,(right) and \cref{fig:subwordComplex3}, which is not a lattice.}
+Its graph, oriented from bottom to top is the Hasse diagram of the poset of \cref{fig:increasingFlipPosets}\,(right) and \cref{fig:subwordComplex3}, which is not a lattice.}
 	\label{fig:brickPolytope3}
@@
 
-\subsection{The sweeping algorithm}
+\subsection{Sweeping algorithm}
 \label{subsec:sweepingAlgorithmSubwordComplexes}

### 2023-03-17 acyclicFacets/draft/latticePipeDreams.tex
some changes plus remark about Thm 5.11

@@
 
-\thanks{NC \& VP were partially supported by the French project CHARMS (ANR~19\,CE40\,0017), and by the French\,--\,Austrian project PAGCAP (ANR~21\,CE48\,0020 \& FWF I 5788).}
+\thanks{
+CC was supported by the Austrian Science Fund FWF (Project P 33278).
+NC \& VP were partially supported by the French project CHARMS (ANR~19\,CE40\,0017).
+CC, NC \& VP were also supported by the Austrian\,--\,French project PAGCAP (ANR~21\,CE48\,0020 \& FWF I 5788).
+}
 
@@
 We then explore in \cref{sec:furtherTopics} some natural further topics on pipe dreams.
-We describe two algorithms to compute the unique acyclic pipe dream whose linear extensions contain a given permutation generalizing the binary tree insertion map on permutations (\cref{subsec:sweepingAlgorithm,subsec:insertionAlgorithm}), we describe the pipe dream congruence as the transitive closure of a local rewriting rule generalizing that of the sylvester congruence (\cref{subsec:rewritingRule}), and we describe a natural commutative diagram of lattice morphism generalizing the connection between the recoil map and the binary tree insertion map on permutations and the canopy on binary trees (\cref{subsec:canopy}).
+We describe two algorithms to compute the unique acyclic pipe dream whose linear extensions contain a given permutation generalizing the binary tree insertion map on permutations (\cref{subsec:sweepingAlgorithm,subsec:insertionAlgorithm}), we describe the pipe dream congruence as the transitive closure of a local rewriting rule generalizing that of the sylvester congruence (\cref{subsec:rewritingRule}), and we describe a natural commutative diagram of lattice morphisms generalizing the connection between the recoil map and the binary tree insertion map on permutations and the canopy on binary trees (\cref{subsec:canopy}).
 
@@
 \begin{itemize}
-\item First, not all acyclic facets of~$\subwordComplex(Q, \omega)$ appear as vertices of~$[e, \omega]/{\equiv_{Q, \omega}}$ (see \cref{rem:linearExtensionsPartitionSubwordComplexA}).
+\item First, not all acyclic facets of~$\subwordComplex(Q, \omega)$ appear as elements of~$[e, \omega]/{\equiv_{Q, \omega}}$ (see \cref{rem:linearExtensionsPartitionSubwordComplexA}).
 We say that a facet is strongly acyclic if~$[e, \omega] \cap \linearExtensions(\omega) \ne \varnothing$.
@@
 This last conjecture has a strong connection to the geometry of subword complexes given by brick polytopes~\cite{PilaudSantos-brickPolytope, PilaudStump-brickPolytope} and brick polyhedra~\cite{JahnStump}.
-Namely, the extremal increasing flips between acyclic facets of~$\subwordComplex(Q, \omega)$ is precisely the bounded part (meaning forgetting the unbounded rays) of the brick polyhedron~$\brickPolyhedron(Q, \omega)$ oriented by a natural linear functional.
+Namely, the extremal increasing flips between acyclic facets of~$\subwordComplex(Q, \omega)$ are precisely the edges of the bounded part (meaning forgetting the unbounded rays) of the brick polyhedron~$\brickPolyhedron(Q, \omega)$ oriented by a natural linear functional.
 \cref{conj:C} thus translates geometrically to the following.
@@
 \label{exm:Tamari2}
-Following \cref{exm:Tamari1}, observe that the permutations of~$\{0, 1, \dots, n, n+1\}$ below $\rho_n$ are precisely the permutations of the form~$[0, \pi, n+1]$ for some~$\pi \in \fS_n$.
+Following \cref{exm:Tamari1}, observe that the permutations of~$\{0, 1, \dots, n, n+1\}$ below~$\rho_n$ are precisely the permutations of the form~$[0, \pi, n+1]$ for some~$\pi \in \fS_n$.
 It is well-known that any permutation~$\pi \in \fS_n$ is a linear extension of a unique binary tree.
@@
 \begin{proof}[Proof of \cref{thm:partitionPipeDreams}]
-Direct consequence of \cref{lem:partition,lem:interval}.
+This is a direct consequence of \cref{lem:partition,lem:interval}.
 \end{proof}
@@
 \item $X \le Y$ in~$L/{\equiv}$ if and only if there exist representatives~$x \in X$ and~$y \in Y$ such that~$x \le y$ in~$L$, or equivalently $\min(X) \le \min(Y)$, or equivalently $\max(X) \le \max(Y)$,
-\item $X \meet Y$ (resp.~$X \join Y$) is the congruence classe of~$x \meet y$ (resp.~of~$x \join y$) for arbitrary representatives~$x \in X$ and~$y \in Y$.
+\item $X \meet Y$ (resp.~$X \join Y$) is the congruence class of~$x \meet y$ (resp.~of~$x \join y$) for arbitrary representatives~$x \in X$ and~$y \in Y$.
 \end{itemize}
@@
 The Hasse diagram of the lattice quotient~$[e,\omega]/{\equiv_\omega}$ is isomorphic to the increasing flip graph on~$\acyclicPipeDreams(\omega)$.
-%Hence, the transitive closure of the increasing flip graph on~$\acyclicPipeDreams(\omega)$ is a lattice.
+Hence, the transitive closure of the increasing flip graph on~$\acyclicPipeDreams(\omega)$ is a lattice.
 \end{theorem}
@@
 	\centerline{\includegraphics[scale=1.2]{counterExampleRestrictionIncreasingFlipPoset}}
-	\caption{Two acyclic pipe dreams~$\acyclicPipeDreams(126543)$ connected by a sequence of increasing flips in~$\pipeDreams(126543)$ but by no sequence of increasing flips in~$\acyclicPipeDreams(126543)$.}
+	\caption{Two acyclic pipe dreams in~$\acyclicPipeDreams(126543)$ connected by a sequence of increasing flips in~$\pipeDreams(126543)$ but by no sequence of increasing flips in~$\acyclicPipeDreams(126543)$.
+	The restriction of the increasing flip poset on~$\pipeDreams(126543)$ to the set of acyclic facets~$\acyclicPipeDreams(126543)$ is not a lattice.
+But, the poset induced by increasing flips between acyclic facets in~$\acyclicPipeDreams(126543)$ is a lattice (Theorem~\ref{thm:pipeDreamQuotient}).}
 	\label{fig:counterExampleRestrictionIncreasingFlipPoset}
@@
 
-Let us conclude by providing more equivalent characterizations of the increasing flip lattice lattice on~$\acyclicPipeDreams(\omega)$.
+Let us conclude by providing more equivalent characterizations of the increasing flip lattice on~$\acyclicPipeDreams(\omega)$.
 
@@
 Our first algorithm to construct~$\insertion{\pi}{\omega}$ is a \defn{sweeping algorithm}, inspired by the algorithm to compute greedy pipe dreams~\cite{PilaudPocchiola, PilaudStump-ELlabelings}.
-An extension of this algorithm to subword complexes will be discussed in \cref{subsec:sweepingAlgorithmSubwordComplexes}, and appeared independently in~\cite{JahnStump}.
+An extension of this algorithm to subword complexes will be discussed in \cref{subsec:sweepingAlgorithmSubwordComplexes}, and a related algorithm appeared independently in~\cite{JahnStump}.
+We say that a box~$b'$ is located \defn{weakly northeast} of a box~$b$, if the vector connecting the center of $b$ to the center of $b'$ is a vector in $\mathbb{R}^2_{\geq 0}$ (with non-negative real entries).
 We say that an order on the boxes of the triangular shape is \defn{northeast compatible} if each box~$b$ is before all boxes which are located weakly northeast of~$b$.
@@
 	}
-	\caption{The increasing flip graph on~$\subwordComplex(Q, \wo)$ where~$Q = \tau_2 \tau_1 \tau_3 \tau_2 \tau_1 \tau_3 \tau_2 \tau_1 \tau_3$ (left) and~$Q = \tau_1 \tau_2 \tau_3 \tau_2 \tau_1 \tau_2 \tau_3 \tau_2 \tau_1$ (right) in type~$A_3$.
+	\caption{The increasing flip poset on~$\subwordComplex(Q, \wo)$ where~$Q = \tau_2 \tau_1 \tau_3 \tau_2 \tau_1 \tau_3 \tau_2 \tau_1 \tau_3$ (left) and~$Q = \tau_1 \tau_2 \tau_3 \tau_2 \tau_1 \tau_2 \tau_3 \tau_2 \tau_1$ (right) in type~$A_3$.
 The left one is the $\tau_2 \tau_1 \tau_3$-Cambrian lattice, while the right one is not a lattice (the two facets highlighted in blue have no join while the two facets highlighted in red have no meet).
@@
 %As in~\cite{PilaudPocchiola, PilaudSantos-brickPolytope, PilaudStump-brickPolytope}, we thus use pseudoline arrangements on sorting networks to represent their facets (and we have represented their contact graphs together).
+\end{remark}
+
+\begin{remark}
+We remark that the set~$\linearExtensions(Q,\omega)$ of linear extensions has been considered independently in the work on brick polyhedra by Jahn and Stump in~\cite{JahnStump}.
+In particular,~$\linearExtensions(Q,\omega)$ is completely characterized using Bruhat cones in~\cite[Proposition~4.12]{JahnStump}, and the convex property~\eqref{item:convex} is equivalent to~\cite[Lemma~4.13]{JahnStump}.
+The other three properties also follow from their characterization, see~\cite[Section~4.2]{JahnStump}.
+Since we found these results independently, and the techniques we use to prove them are rather different, we believe that it is relevant to keep our contributions here.
+Moreover, this leads to further perspectives and conjectures in connection to brick polyhedra which we present in Section~\ref{subsec:fiveConjectures}.
 \end{remark}

### 2023-03-17 acyclicFacets/draft/latticePipeDreams.tex
added Remark 5.29 about connection between our sweeping algorithm and the algorithm of Jahn-Stump

@@
 We now extend the sweeping algorithm of \cref{subsec:sweepingAlgorithm} to construct, from a linear extension $\pi \in \linearExtensions(Q,\omega)$, the unique acyclic facet~$I$ such that $\pi \in \linearExtensions(I)$.
-We note that this algorithm was independently described in~\cite{JahnStump}.
+We note that this algorithm is related to an algorithm that was independently described in~\cite{JahnStump}, see Remark~\ref{rem_sweepJahnStump}.
 
@@
 
-We first need to argue that the algorithm terminates, that is, that any position $j$ falls into one of the four cases above.
+\begin{remark}\label{rem_sweepJahnStump}
+In~\cite[Section~3.3]{JahnStump}, Jahn and Stump describe an algorithm to compute the $f$-antigreedy facet of a subword complex $\subwordComplex(Q,\omega)$ associated to a linear functional $f$.  
+The output of our algorithm coincides with the output of Jahn-Stump's algorithm whenever $f$ is positive on~$\pi(\Phi^+)$ and negative on $\pi(\Phi^-)$, see~\cite[Proposition~4.12]{JahnStump}.
+Also, compare Proposition~\ref{prop:sweeping}~\eqref{item:sweeping1} with~\cite[Theorem~3.17 (a)]{JahnStump},
+and Proposition~\ref{prop:sweeping}~\eqref{item:sweeping2} with the second part of~\cite[Proposition~4.12]{JahnStump}.
+
+Although the algorithm presented in~\cite{JahnStump} is more general, our sweeping algorithm is more direct when computing the output for the input $\pi$, since we skip the step of translating the conditions on the sign of $f(\rootFunction{I^j}{j})$ in Jahn-Stump's algorithm.
+We remark that these two algorithms were developed independently, while approaching different problems.
+This highlights the relevance of the sweeping algorithm.
+\end{remark}
+
+In order to prove Proposition~\ref{prop:sweeping}, we first need to argue that the algorithm terminates, that is, that any position $j$ falls into one of the four cases above.
 

### 2023-03-17 acyclicFacets/draft/latticePipeDreams.tex
added Remark 5.29 about connection between our sweeping algorithm and the algorithm of Jahn-Stump

@@
 
-Although the algorithm presented in~\cite{JahnStump} is more general, our sweeping algorithm is more direct when computing the output for the input $\pi$, since we skip the step of translating the conditions on the sign of $f(\rootFunction{I^j}{j})$ in Jahn-Stump's algorithm.
+Although the algorithm presented in~\cite{JahnStump} is more general, we highlight that our sweeping algorithm is conceptually simpler, since we skip the step of translating the conditions on the sign of $f(\rootFunction{I^j}{j})$ in Jahn-Stump's algorithm.
 We remark that these two algorithms were developed independently, while approaching different problems.
-This highlights the relevance of the sweeping algorithm.
+This shows that the sweeping algorithm has a significant importance in the combinatorial and geometric understanding of subword complexes.
 \end{remark}

### 2023-03-17 acyclicFacets/draft/latticePipeDreams.tex
another minor change

@@
 
-Since $\linearExtensions(I)\neq \varnothing$ if and only if $I$ is acyclic by \cref{lem:linearExtensionsAcyclic}, and~$\linearExtensions(I) \ne \linearExtensions(J)$ for~$I \ne J$ by \cref{thm:linearExtensionsPartitionSubwordComplexA}~\eqref{item:partition}, we have the following straight forward corollary.
+Since $\linearExtensions(I)\neq \varnothing$ if and only if $I\in \subwordAcyclicFacets(Q,\omega)$ (i.e.
+$I$ is an acyclic facet) by \cref{lem:linearExtensionsAcyclic}, and also~$\linearExtensions(I) \ne \linearExtensions(J)$ for~$I \ne J$ by \cref{thm:linearExtensionsPartitionSubwordComplexA}~\eqref{item:partition}, we have the following straight forward corollary.
 

### 2023-03-17 acyclicFacets/draft/latticePipeDreams.tex
minor changes

@@
 This last conjecture has a strong connection to the geometry of subword complexes given by brick polytopes~\cite{PilaudSantos-brickPolytope, PilaudStump-brickPolytope} and brick polyhedra~\cite{JahnStump}.
-Namely, the extremal increasing flips between acyclic facets of~$\subwordComplex(Q, \omega)$ are precisely the edges of the bounded part (meaning forgetting the unbounded rays) of the brick polyhedron~$\brickPolyhedron(Q, \omega)$ oriented by a natural linear functional.
+Namely, the extremal increasing flips between acyclic facets of~$\subwordComplex(Q, \omega)$ are precisely the bounded edges (meaning forgetting the unbounded rays) of the brick polyhedron~$\brickPolyhedron(Q, \omega)$ oriented by a natural linear functional.
 \cref{conj:C} thus translates geometrically to the following.
@@
 	The restriction of the increasing flip poset on~$\pipeDreams(126543)$ to the set of acyclic facets~$\acyclicPipeDreams(126543)$ is not a lattice.
-But, the poset induced by increasing flips between acyclic facets in~$\acyclicPipeDreams(126543)$ is a lattice (Theorem~\ref{thm:pipeDreamQuotient}).}
+But, the poset induced by increasing flips between acyclic facets in~$\acyclicPipeDreams(126543)$ is a lattice (\cref{thm:pipeDreamQuotient}).}
 	\label{fig:counterExampleRestrictionIncreasingFlipPoset}
@@
 An extension of this algorithm to subword complexes will be discussed in \cref{subsec:sweepingAlgorithmSubwordComplexes}, and a related algorithm appeared independently in~\cite{JahnStump}.
-We say that a box~$b'$ is located \defn{weakly northeast} of a box~$b$, if the vector connecting the center of $b$ to the center of $b'$ is a vector in $\mathbb{R}^2_{\geq 0}$ (with non-negative real entries).
+%We say that a box~$b'$ is located \defn{weakly northeast} of a box~$b$, if the vector connecting the center of $b$ to the center of $b'$ is a vector in $\mathbb{R}^2_{\geq 0}$ (with non-negative real entries).
 We say that an order on the boxes of the triangular shape is \defn{northeast compatible} if each box~$b$ is before all boxes which are located weakly northeast of~$b$.
@@
 \begin{remark}
-We remark that the set~$\linearExtensions(Q,\omega)$ of linear extensions has been considered independently in the work on brick polyhedra by Jahn and Stump in~\cite{JahnStump}.
-In particular,~$\linearExtensions(Q,\omega)$ is completely characterized using Bruhat cones in~\cite[Proposition~4.12]{JahnStump}, and the convex property~\eqref{item:convex} is equivalent to~\cite[Lemma~4.13]{JahnStump}.
-The other three properties also follow from their characterization, see~\cite[Section~4.2]{JahnStump}.
+We note that the set~$\linearExtensions(Q,\omega)$ of linear extensions has been considered independently in the work on brick polyhedra by D.~Jahn and C.~Stump in~\cite{JahnStump}.
+In particular,~$\linearExtensions(Q,\omega)$ is completely characterized using Bruhat cones in~\cite[Prop.~4.12]{JahnStump}, and the convex property~\eqref{item:convex} is equivalent to~\cite[Lem.~4.13]{JahnStump}.
+The other three properties also follow from their characterization, see~\cite[Sect.~4.2]{JahnStump}.
 Since we found these results independently, and the techniques we use to prove them are rather different, we believe that it is relevant to keep our contributions here.
-Moreover, this leads to further perspectives and conjectures in connection to brick polyhedra which we present in Section~\ref{subsec:fiveConjectures}.
+Moreover, this leads to further perspectives and conjectures in connection to brick polyhedra which we present in~\cref{subsec:fiveConjectures}.
 \end{remark}
@@
 We now extend the sweeping algorithm of \cref{subsec:sweepingAlgorithm} to construct, from a linear extension $\pi \in \linearExtensions(Q,\omega)$, the unique acyclic facet~$I$ such that $\pi \in \linearExtensions(I)$.
-We note that this algorithm is related to an algorithm that was independently described in~\cite{JahnStump}, see Remark~\ref{rem_sweepJahnStump}.
+We note that this algorithm is related to an algorithm that was independently described in~\cite{JahnStump}, see~\cref{rem:sweepJahnStump}.
 
@@
 
-\begin{remark}\label{rem_sweepJahnStump}
-In~\cite[Section~3.3]{JahnStump}, Jahn and Stump describe an algorithm to compute the $f$-antigreedy facet of a subword complex $\subwordComplex(Q,\omega)$ associated to a linear functional $f$.  
-The output of our algorithm coincides with the output of Jahn-Stump's algorithm whenever $f$ is positive on~$\pi(\Phi^+)$ and negative on $\pi(\Phi^-)$, see~\cite[Proposition~4.12]{JahnStump}.
-Also, compare Proposition~\ref{prop:sweeping}~\eqref{item:sweeping1} with~\cite[Theorem~3.17 (a)]{JahnStump},
-and Proposition~\ref{prop:sweeping}~\eqref{item:sweeping2} with the second part of~\cite[Proposition~4.12]{JahnStump}.
-
-Although the algorithm presented in~\cite{JahnStump} is more general, we highlight that our sweeping algorithm is conceptually simpler, since we skip the step of translating the conditions on the sign of $f(\rootFunction{I^j}{j})$ in Jahn-Stump's algorithm.
+\begin{remark}
+\label{rem:sweepJahnStump}
+In~\cite[Sect.~3.3]{JahnStump}, D.~Jahn and C.~Stump describe an algorithm to compute the $f$-antigreedy facet of a subword complex $\subwordComplex(Q,\omega)$ associated to a linear functional $f$.  
+The output of our algorithm coincides with the output of their algorithm whenever $f$ is positive on~$\pi(\Phi^+)$ and negative on $\pi(\Phi^-)$, see~\cite[Prop.~4.12]{JahnStump}.
+Also, compare \cref{prop:sweeping}~\eqref{item:sweeping1} with~\cite[Thm.~3.17 (a)]{JahnStump}, and \cref{prop:sweeping}~\eqref{item:sweeping2} with the second part of~\cite[Prop.~4.12]{JahnStump}.
+
+Although the algorithm presented in~\cite{JahnStump} is more general, we highlight that our sweeping algorithm is conceptually simpler, since we skip the step of translating the conditions on the sign of $f(\rootFunction{I^j}{j})$ in the algorithm of~\cite{JahnStump}.
 We remark that these two algorithms were developed independently, while approaching different problems.
@@
 
-In order to prove Proposition~\ref{prop:sweeping}, we first need to argue that the algorithm terminates, that is, that any position $j$ falls into one of the four cases above.
+In order to prove \cref{prop:sweeping}, we first need to argue that the algorithm terminates, that is, that any position $j$ falls into one of the four cases above.
 

### 2023-03-17 acyclicFacets/draft/latticePipeDreams.tex
minor changes

@@
 	\caption{Two acyclic pipe dreams in~$\acyclicPipeDreams(126543)$ connected by a sequence of increasing flips in~$\pipeDreams(126543)$ but by no sequence of increasing flips in~$\acyclicPipeDreams(126543)$.
-	The restriction of the increasing flip poset on~$\pipeDreams(126543)$ to the set of acyclic facets~$\acyclicPipeDreams(126543)$ is not a lattice.
-But, the poset induced by increasing flips between acyclic facets in~$\acyclicPipeDreams(126543)$ is a lattice (\cref{thm:pipeDreamQuotient}).}
+The subposet of the increasing flip poset on~$\pipeDreams(126543)$ induced by the set~$\acyclicPipeDreams(126543)$ of acyclic facets is not a lattice, but the transitive closure of the increasing flip graph between the acyclic facets of~$\acyclicPipeDreams(126543)$ is a lattice (\cref{thm:pipeDreamQuotient}).}
 	\label{fig:counterExampleRestrictionIncreasingFlipPoset}
@@
 
-Since $\linearExtensions(I)\neq \varnothing$ if and only if $I\in \subwordAcyclicFacets(Q,\omega)$ (i.e.
-$I$ is an acyclic facet) by \cref{lem:linearExtensionsAcyclic}, and also~$\linearExtensions(I) \ne \linearExtensions(J)$ for~$I \ne J$ by \cref{thm:linearExtensionsPartitionSubwordComplexA}~\eqref{item:partition}, we have the following straight forward corollary.
+Since $\linearExtensions(I)\neq \varnothing$ if and only if $I\in \subwordAcyclicFacets(Q,\omega)$ (\ie $I$ is an acyclic facet) by \cref{lem:linearExtensionsAcyclic}, and also~$\linearExtensions(I) \ne \linearExtensions(J)$ for~$I \ne J$ by \cref{thm:linearExtensionsPartitionSubwordComplexA}~\eqref{item:partition}, we have the following straightforward corollary.
 

### 2023-03-17 acyclicFacets/draft/latticePipeDreams.tex
adding red and blue dots in brick polytope picture

@@
 	\caption{The brick polytope of~$\subwordComplex(Q,\wo)$ where~$Q = \tau_1 \tau_2 \tau_3 \tau_2 \tau_1 \tau_2 \tau_3 \tau_2 \tau_1$ in type~$A_3$.
-Its graph, oriented from bottom to top is the Hasse diagram of the poset of \cref{fig:increasingFlipPosets}\,(right) and \cref{fig:subwordComplex3}, which is not a lattice.}
+Its graph, oriented from bottom to top is the Hasse diagram of the poset of \cref{fig:increasingFlipPosets}\,(right) and \cref{fig:subwordComplex3}, which is not a lattice (the two blue vertices have no join while the two red vertices have no meet).}
 	\label{fig:brickPolytope3}

### 2023-03-17 acyclicFacets/draft/latticePipeDreams.tex
add picture

@@
 Namely, the transitive closure of the subgraph of the increasing flip graph induced by~$\acyclicPipeDreams(\omega)$ may have strictly less relations than the subposet of the increasing flip poset induced by~$\acyclicPipeDreams(\omega)$.
-\cref{fig:counterExampleRestrictionIncreasingFlipPoset} illustrates two acyclic pipe dreams of~$\acyclicPipeDreams(126543)$ connected by a sequence of increasing flips in~$\pipeDreams(126543)$ but by no sequence of increasing flips in~$\acyclicPipeDreams(126543)$.
-In fact, the subposet of the increasing flip poset induced by~$\acyclicPipeDreams(126543)$ is not even a lattice.
+\cref{fig:counterExampleRestrictionIncreasingFlipPoset1} illustrates two acyclic pipe dreams of~$\acyclicPipeDreams(126543)$ connected by a sequence of increasing flips in~$\pipeDreams(126543)$ but by no sequence of increasing flips in~$\acyclicPipeDreams(126543)$.
+In fact, the subposet of the increasing flip poset induced by~$\acyclicPipeDreams(126543)$ is not even a lattice, as illustrated in \cref{counterExampleRestrictionIncreasingFlipPoset2}.
 This example is minimal.
+%
 %	* type A5,
@@
 %	(3, 4, 5, 7, 8, 10, 11, 12, 14)
-
+%
 \begin{figure}[ht]
-	\centerline{\includegraphics[scale=1.2]{counterExampleRestrictionIncreasingFlipPoset}}
-	\caption{Two acyclic pipe dreams in~$\acyclicPipeDreams(126543)$ connected by a sequence of increasing flips in~$\pipeDreams(126543)$ but by no sequence of increasing flips in~$\acyclicPipeDreams(126543)$.
-The subposet of the increasing flip poset on~$\pipeDreams(126543)$ induced by the set~$\acyclicPipeDreams(126543)$ of acyclic facets is not a lattice, but the transitive closure of the increasing flip graph between the acyclic facets of~$\acyclicPipeDreams(126543)$ is a lattice (\cref{thm:pipeDreamQuotient}).}
-	\label{fig:counterExampleRestrictionIncreasingFlipPoset}
+	\centerline{\includegraphics[scale=1.2]{counterExampleRestrictionIncreasingFlipPoset1}}
+	\caption{Two acyclic pipe dreams in~$\acyclicPipeDreams(126543)$ connected by a sequence of increasing flips in~$\pipeDreams(126543)$ but by no sequence of increasing flips in~$\acyclicPipeDreams(126543)$.}
+	\label{fig:counterExampleRestrictionIncreasingFlipPoset1}
+\end{figure}
+%
+\begin{figure}[ht]
+	\centerline{\includegraphics[scale=1.2]{counterExampleRestrictionIncreasingFlipPoset2}}
+	\caption{Some acyclic pipe dreams of~$\acyclicPipeDreams(126543)$, connected by some strong arrows representing increasing flips, and by a dotted arrow representing the relation of \cref{fig:counterExampleRestrictionIncreasingFlipPoset1}.
+The subposet of the increasing flip poset on~$\pipeDreams(126543)$ induced by~$\acyclicPipeDreams(126543)$ contains the dotted arrow and is thus not a lattice (the two bottom elements of the picture have no join while the two top elements of the picture have no meet).
+In contrast, the transitive closure of the increasing flip graph on~$\acyclicPipeDreams(126543)$ does not contain the dotted arrow and is a lattice (\cref{thm:pipeDreamQuotient}).}
+	\label{fig:counterExampleRestrictionIncreasingFlipPoset2}
 \end{figure}
@@
 %
-\begin{figure}[b]
+\begin{figure}[t]
 	\centerline{\includegraphics[scale=.9]{sweeping1}}
@@
 %
-\begin{figure}[b]
+\begin{figure}[t]
 	\centerline{\includegraphics[scale=.9]{sweeping2}}
@@
 %
-\begin{figure}[b]
+\begin{figure}[t]
 	\centerline{\includegraphics[scale=.9]{insertion1}}
@@
 %
-\begin{figure}[b]
+\begin{figure}[t]
 	\centerline{\includegraphics[scale=.9]{insertion2}}

### 2023-03-20 acyclicFacets/draft/latticePipeDreams.tex
Added my grant.
fig sizes
replace Nantel grant
cleaning tex file for submission

@@
 \thanks{
+NB was supported by NSERC and York Research Chair in Applied Algebra.
 CC was supported by the Austrian Science Fund FWF (Project P 33278).
@@
 
-% Let $\fS_n$ denote the set of permutations of~$[n] \eqdef \{1,2,\ldots,n\}$, and let~$\fS \eqdef \bigsqcup_{n \ge 0} \fS_n$.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 For a fixed permutation~$\omega \in \fS_n$, we denote by~$\pipeDreams(\omega)$ the set of reduced pipe dreams~$P$ such that~$\omega_P = \omega$.
-% We let~$\pipeDreams_n \eqdef \bigsqcup_{\omega \in \fS_n} \pipeDreams(\omega)$ and~$\pipeDreams \eqdef \bigsqcup_{n \in \N} \pipeDreams_n$.
-
-%Two pipe dreams are related by a \defn{flip} if they only differ by the position of a crossing and a contact (in particular, they define the same permutation).
+
 A contact~$c$ is \defn{flippable} if the two pipes passing through contact~$c$ have a crossing~$x$.
 The \defn{flip} exchanges the contact~$c$ with the crossing~$x$.
-%See \cref{fig:pipeDreams}.
 The flip is \defn{increasing} if the contact~$c$ is weakly southwest of the crossing~$x$.
@@
 For~$\omega \in \fS_n$, we denote by~$\acyclicPipeDreams(\omega)$ the set of acyclic pipe dreams of~$\pipeDreams(\omega)$.
-% We let~$\acyclicPipeDreams_n \eqdef \bigsqcup_{\omega \in \fS_n} \acyclicPipeDreams(\omega)$ and~$\acyclicPipeDreams \eqdef \bigsqcup_{n \in \N} \acyclicPipeDreams_n$.
-%\vincent{Add contact graphs to \cref{fig:pipeDreams}.}
 
@@
 In this case, it is natural to label the pipes from~$0$ to~$n+1$, so that the permutation of the pipes is~$\rho_n \eqdef [0, n, n-1, \dots, 2, 1, n+1]$.
-% We denote by~$\reversingPipeDreams_n$ the reversing pipe dreams of~$\pipeDreams_n$.
 As observed in~\cite{Woo, PilaudPocchiola, Pilaud-these, Stump}, the family of reversing pipe dreams belong to the Catalan families, meaning that it is counted by the famous Catalan numbers.
@@
 contact flips in~$P$ & diagonal flips in~$P\duality$. \\
-%increasing flip poset & Tamari lattice.
 \end{tabular}} \\[.3cm]
 %
-\begin{figure}
-	\centerline{\includegraphics[scale=1.3]{dualiteTriangulation}}
+\begin{figure}[h]
+	\centerline{\includegraphics[scale=1.23]{dualiteTriangulation}}
 	\caption{The bijection between reversing pipe dreams (left), binary trees (middle) and triangulations (right).}
@@
 \end{figure}
-%
+
 Hence, this map sends the increasing flip poset on reversing pipe dreams to the \defn{Tamari lattice} on binary trees.
@@
 
-%Recall that a \defn{linear extension} of a binary relation~$\less$ on~$[n]$ is a permutation~$\pi \in \fS_n$ such that~$i \less j$ implies $\pi^{-1}(i) < \pi^{-1}(j)$.
-%We denote by~$\linearExtensions(\less)$ the set of linear extensions of~$\less$.
-%Consider an acyclic pipe dream~$P$, and recall that we denote by~$\contactLess{P}$ the transitive closure of the contact graph~$P\contact$ of~$P$.
-%We denote by~$\linearExtensions(P)$ the set of linear extensions of~$\contactLess{P}$, and we say abusively that the permutations of~$\linearExtensions(P)$ are linear extensions of~$P$.
-%In other words, $\pi \in \linearExtensions(P)$ if and only if~$\pi^{-1}(i) < \pi^{-1}(j)$ for all arcs~$i \to j$ in~$P\contact$.
-
 \begin{definition}
@@
 We denote by~$\linearExtensions(P)$ the set of linear extensions of~$P$.
-%For a pipe dream~$P \in \pipeDreams(\omega)$, we denote by~$\linearExtensions(P)$ the set of \defn{linear extensions} of~$P$, \ie the permutations~$\pi$ of~$[n]$ such that~$\pi^{-1}(i) < \pi^{-1}(j)$ for every arc~$i \to j$ in~$P\contact$.
 \end{definition}
@@
 \begin{figure}[ht]
-	\centerline{\includegraphics[scale=1.2]{counterExampleRestrictionIncreasingFlipPoset1}}
+	\centerline{\includegraphics[scale=1.1]{counterExampleRestrictionIncreasingFlipPoset1}}
 	\caption{Two acyclic pipe dreams in~$\acyclicPipeDreams(126543)$ connected by a sequence of increasing flips in~$\pipeDreams(126543)$ but by no sequence of increasing flips in~$\acyclicPipeDreams(126543)$.}
@@
 \begin{figure}[ht]
-	\centerline{\includegraphics[scale=1.2]{counterExampleRestrictionIncreasingFlipPoset2}}
+	\centerline{\includegraphics[scale=1.1]{counterExampleRestrictionIncreasingFlipPoset2}}
 	\caption{Some acyclic pipe dreams of~$\acyclicPipeDreams(126543)$, connected by some strong arrows representing increasing flips, and by a dotted arrow representing the relation of \cref{fig:counterExampleRestrictionIncreasingFlipPoset1}.
@@
 
-%To sum up, there are three equivalent ways to partition the interval~$[e,\omega]$ of the weak order:
-%\begin{itemize}
-%\item by the sets of linear extensions~$\linearExtensions(P)$ of all pipe dreams of~$\acyclicPipeDreams(\omega)$,
-%\item by the fibers of the sweeping algorithm, \vincent{choose notation}
-%\item by the fibers of the insertion map~$\insertion{\cdot}{\omega}$,
-%\item by the classes of the pipe dream congruence~$\equiv_\omega$.
-%\end{itemize}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 An extension of this algorithm to subword complexes will be discussed in \cref{subsec:sweepingAlgorithmSubwordComplexes}, and a related algorithm appeared independently in~\cite{JahnStump}.
-%We say that a box~$b'$ is located \defn{weakly northeast} of a box~$b$, if the vector connecting the center of $b$ to the center of $b'$ is a vector in $\mathbb{R}^2_{\geq 0}$ (with non-negative real entries).
 We say that an order on the boxes of the triangular shape is \defn{northeast compatible} if each box~$b$ is before all boxes which are located weakly northeast of~$b$.
@@
 	\centerline{\includegraphics[scale=.9]{sweeping1}}
-	\caption{Sweeping algorithm for the permutations~$\pi = 513264$ and~$\omega = 561324$.} % See details in \cref{exm:sweepingAlgorithm}.}
+	\caption{Sweeping algorithm for the permutations~$\pi = 513264$ and~$\omega = 561324$.}
 	\label{fig:sweepingAlgorithm1}
@@
 	\centerline{\includegraphics[scale=.9]{sweeping2}}
-	\caption{Sweeping algorithm for the permutations~$\pi = 512364$ and~$\omega = 561324$.} % See details in \cref{exm:sweepingAlgorithm}.}
+	\caption{Sweeping algorithm for the permutations~$\pi = 512364$ and~$\omega = 561324$.}
 	\label{fig:sweepingAlgorithm2}
@@
 More precisely, at step~$t$, we insert a pipe starting at row~$\pi(t)$, ending at column~$\omega^{-1}(\pi(t))$, and whose northeast elbows are precisely covering the staircase of currently free southeast elbows in the rectangle~$[\pi(t)] \times [\omega^{-1}(\pi(t))]$.
-%More precisely, at step~$t$, we consider the set~$X_t$ of free southeast elbows in the rectangle~$[\pi(t)] \times [\omega^{-1}(\pi(t))]$, and we insert a pipe starting at row~$\pi(t)$, ending at column~$\omega^{-1}(\pi(t))$, and whose northeast elbows are precisely covering the elbows of~$X_t$, and adding a new free southeast elbow in between any two consecutive elbows of~$X_t$
 See \cref{fig:insertionAlgorithm1,fig:insertionAlgorithm2}.
@@
 Since the northwest and southeast elbows alternate along pipe~$\pi(t)$, this follows from the fact that the pipe~$\pi(t)$ enters~$R$ with an horizontal step if~$\pi(t) \le r$ and with a vertical step if~$\pi(s) > r$, and exits~$R$ with a vertical step if~$\omega^{-1}(\pi(t)) \le c$ and with an horizontal step if~$\omega^{-1}(\pi(s)) > c$.
-%setting~$i \eqdef \pi(t)$ and~$j \eqdef \pi(s)$, we have~${i < j}$ and~$\pi^{-1}(i) > \pi^{-1}(j)$ while~$\omega^{-1}(i) < \omega^{-1}(j)$, which contradicts our assumption that~$\pi < \omega$.
-\qedhere
 \end{proof}
@@
 \begin{proof}
-%Let $\Phi = \Phi^+ \sqcup \Phi^-$ be the root system associated to $W$.
 A classical result for finite root systems states that for any generic linear halfspace~$H^+$ the intersection~$\Phi \cap H^+$ is of the form $\pi(\Phi^+)$ for some $\pi \in W$.
@@
 Define~$\beta=\pi'(\alpha_s)$ and observe that~$s_\beta$ preserves the set~$\pi'(\Phi^+) \ssm \{\beta\} = \pi(\Phi^+) \ssm \{-\beta\} = \pi(\Phi^+) \cap \pi'(\Phi^+)$.
-
-%Now,
-%\[
-%\pi(\Phi^+)= -\Inv(\pi)\sqcup \Ninv(\pi)
-%\]
-%and 
-%\[
-%\Inv(\pi') =\Inv(\pi) \ssm \{\beta\}
-%\qquad\text{and}\qquad
-%\Ninv(\pi') = \Ninv(\pi) \cup \{\beta\}
-%\]
-%for $\beta=\pi'(\alpha_s)$.
-%Therefore,
-%\begin{align*}
-%\pi'(\Phi^+) = \pi(\Phi^+) \ssm \{-\beta\} \cup \{\beta\}.
-%\end{align*}
-%%
-%%\begin{center}
-%%\begin{tikzpicture}
-%%\coordinate (a) at (0,0);
-%%\coordinate (b) at (0:2);
-%%\coordinate (c) at (60:2);
-%%\coordinate (d) at (120:2);
-%%\coordinate (e) at (180:2);
-%%\draw (b) node[right] {$\beta$};
-%%\draw (e) node[left] {$-\beta$};
-%%%
-%%\path[fill=green!20] (0,0) --  (60:2) arc(60:180:2) -- cycle;
-%%%
-%%\draw[-stealth,dashed] (a) -- (b);
-%%\draw[-stealth] (a) -- (c);
-%%% \draw[-stealth] (a) -- (d);
-%%\draw[-stealth] (a) -- (e);
-%%\node at (120:1) {$\pi(\Phi^+)$};
-%%\end{tikzpicture} 
-%%%
-%%\qquad
-%%%
-%%\begin{tikzpicture}
-%%\coordinate (a) at (0,0);
-%%\coordinate (b) at (0:2);
-%%\coordinate (c) at (60:2);
-%%\coordinate (d) at (120:2);
-%%\coordinate (e) at (180:2);
-%%\draw (b) node[right] {$\beta$};
-%%\draw (e) node[left] {$-\beta$};
-%%%
-%%\path[fill=green!20] (0,0) -- (0:2) arc(0:120:2)  -- cycle;
-%%%
-%%\draw[-stealth] (a) -- (b);
-%%% \draw[-stealth] (a) -- (c);
-%%\draw[-stealth] (a) -- (d);
-%%\draw[-stealth,dashed] (a) -- (e);
-%%\node at (60:1) {$\pi'(\Phi^+)$};
-%%\end{tikzpicture} 
-%%\end{center}
-%%%
-%Note that the reflection $s_\beta=\pi's\pi'^{-1}$ orthogonal to the root $\beta$ transforms $\pi(\Phi^+)$ and $\pi'(\Phi^+)$ into each other:
-%\[
-%s_\beta(\pi(\Phi^+))=\pi'(\Phi^+).
-%\]
-%Since $s_\beta(\beta)= -\beta$, then $s_\beta$ preserves the set 
-%\[
-%\pi(\Phi^+) \ssm \{-\beta\} = \pi'(\Phi^+) \ssm \{\beta\} = \pi(\Phi^+) \cap \pi'(\Phi^+).
-%\]
-%This observation will be useful to prove the statement in the second of the following two cases.
 
@@
 
-%As pointed out in \cref{rem_acyclicflipposet_not_latticequotient},  we can not expect~$[e,\omega]/\equiv_{Q,\omega}$ to be isomorphic to the restriction of the increasing flip poset of $\subwordComplex(Q,\omega)$ to the set of acyclic facets.
-%\cref{exm:acyclicFlipvsWeakOrder} shows that there are flips between acyclic facets that are not detected by the week order.
-%One could expect that there is a natural restriction to a special class of flips that behave nicer, meaning that all of them are identified by the quotient~$[e,\omega]/\equiv_{Q,\omega}$.
-%In our \cref{exm:acyclicFlipvsWeakOrder}, the generalized Chute moves from~\cite{Rubey} do the job, because the flip that is not detected by the week order is exactly the one flip which is not Chute.
-%The Chute lattice conjecture~\cite[Conjecture~2.8]{Rubey} might be an indication that this is the right direction to look at.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 The sweeping algorithm outcomes a facet for every element~$\pi \in W$, and this will be the desired facet for each $\pi \in \linearExtensions(Q,\omega)$.
-%In other words, we define a function
-%\[
-%\begin{tabular}{cccl}
-%$\sweepingAlgorithm$ : & $W$ & $\longrightarrow$ & $\subwordFacets(Q,\omega)$\\
-%& $\pi$ & $\longrightarrow$ & $\sweepingAlgorithm(Q,\omega,\pi)$
-%\end{tabular}
-%\]
 
@@
 \]
-%The positive roots are covered by the cases (1),(2), and (3).
-%The negative roots in $-\Inv(\omega)$ are covered in case (4).
 Since we are inserting a reduced expression of $\omega$ in $Q$, the case $-\Ninv(\omega)$ never occurs.

### 2023-04-20 acyclicFacets/draft/latticePipeDreams.tex
acknoledgments
Added Section 4.5 about the acyclic property for v-Tamari

@@
 \newtheorem{notation}[theorem]{Notation}
+\newtheorem{openproblem}[theorem]{Open problem}
 
@@
 
+\vspace*{.5cm}
+
 \maketitle
@@
 \end{proof}
+
+\subsection{The acyclic property for $\nu$-Tamari lattices}
+We would like to close this section stating an open problem that relates our results to the $\nu$-Tamari lattices introduced by Préville-Ratelle and Viennot in~\cite{preville_nu_tamari_2017}.
+These posets are indexed by a lattice path $\nu$ consisting of a finite number of north (N) and east (E) steps, and coincide with the classical Tamari lattices when $\nu=(NE)^n$.
+
+In~\cite{ceballos_nu_trees_2020}, it was shown that the $\nu$-Tamari lattice can be obtained as the increasing flip poset on pipe dreams~$\pipeDreams(\omega_\nu)$ for an explicit permutation $\omega_\nu$ associated to $\nu$.
+The permutations of the form~$\omega_\nu$ can be easily characterized as follows.
+We refer to~\cite{ceballos_nu_trees_2020} for details.
+
+A permutation $\omega$ is called \defn{dominant} if its Rothe diagram, \ie the set $$\set{(\omega(j),i)}{i<j,\ \omega(i)>\omega(j)}$$ in matrix notation, is the Ferrer's diagram of a partition located at the top left corner $(1,1)$.
+Equivalently, a permutation~$\omega$ is dominant if and only if it is 132-avoiding.
+
+Given a permutation $u$ of $[m]$ and a permutation $v$ of $[n]$, we denote by $u\oplus v$ the permutation of $[m+n]$ defined by 
+\[
+(u\oplus v)(i)=
+\begin{cases}
+u(i), & \text{for } 1\leq i\leq m \\
+v(i)+m, & \text{for } m<i\leq m+n.
+\end{cases}
+\] 
+The permutations $\omega_\nu$ associated to lattice paths $\nu$ are those of the form~$1\oplus w$ for some dominant permutation $w$, see~\cite{ceballos_nu_trees_2020}.
+
+\begin{openproblem}[The acyclic property for $\nu$-Tamari lattices]
+\label{prob_nu_acyclicproperty}
+Show that if $\omega$ is a dominant permutation then all pipe dreams with permutation $1\oplus \omega$ are acyclic.
+%In particular, the corresponding $\nu$-Tamari lattice is the increasing flip poset on acyclic pipe dreams~$\acyclicPipeDreams(1\oplus \omega)$.
+\end{openproblem}
+
+This property is known to be true when $\omega=n\dots21$ is the reverse permutation.
+In this case, the increasing flip poset is the classical Tamari lattice.
+Removing the vertex 1 from the contact graph of a pipe dream~$P\in \pipeDreams(1\oplus \omega)$ returns the binary tree corresponding to $P$ (with the leaves removed and the internal nodes labeled appropriately with the numbers from 2 to $n+1$).
+The edges of the binary tree are oriented going away from the root of the tree.
+We have also checked this property computationally for all dominant permutations up to $n=8$.
+
+Applying our Theorem~\ref{thm:pipeDreamQuotient}, we get the following consequence.
+
+\begin{proposition}
+If the statement of Open Problem~\ref{prob_nu_acyclicproperty} holds, then the $\nu$-Tamari lattice is a lattice quotient of the interval~$[e,\omega_\nu]$.
+\end{proposition}
+
+%\label{thm:pipeDreamQuotient}
+%The Hasse diagram of the lattice quotient~$[e,\omega]/{\equiv_\omega}$ is isomorphic to the increasing flip graph on~$\acyclicPipeDreams(\omega)$.
+%Hence, the transitive closure of the increasing flip graph on~$\acyclicPipeDreams(\omega)$ is a lattice.
 
@@
 
+\section*{Acknowledgments}
+
+We thank Florent Hivert for various discussions.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \bibliographystyle{alpha}

### 2023-04-20 acyclicFacets/draft/latticePipeDreams.tex
Acknowledgements Rubey

@@
 This property is known to be true when $\omega=n\dots21$ is the reverse permutation.
-In this case, the increasing flip poset is the classical Tamari lattice.
+In this case, the increasing flip poset on~$\pipeDreams(1\oplus \omega)$ is the classical Tamari lattice.
 Removing the vertex 1 from the contact graph of a pipe dream~$P\in \pipeDreams(1\oplus \omega)$ returns the binary tree corresponding to $P$ (with the leaves removed and the internal nodes labeled appropriately with the numbers from 2 to $n+1$).
@@
 
-We thank Florent Hivert for various discussions.
+We are grateful to Florent Hivert for various discussions. We also thank Martin Rubey for his comments which led us to think about Open Problem~\ref{prob_nu_acyclicproperty}.
 

### 2023-04-26 acyclicFacets/draft/latticePipeDreams.tex
minor corrections

--- 2023-03-20 acyclicFacets/draft/latticePipeDreams.tex
@@
 
+\vspace*{.1cm}
+
 \maketitle
@@
 We then explore in \cref{sec:furtherTopics} some natural further topics on pipe dreams.
-We describe two algorithms to compute the unique acyclic pipe dream whose linear extensions contain a given permutation generalizing the binary tree insertion map on permutations (\cref{subsec:sweepingAlgorithm,subsec:insertionAlgorithm}), we describe the pipe dream congruence as the transitive closure of a local rewriting rule generalizing that of the sylvester congruence (\cref{subsec:rewritingRule}), and we describe a natural commutative diagram of lattice morphisms generalizing the connection between the recoil map and the binary tree insertion map on permutations and the canopy on binary trees (\cref{subsec:canopy}).
+We first present two algorithms to compute the unique acyclic pipe dream whose linear extensions contain a given permutation generalizing the binary tree insertion map on permutations (\cref{subsec:sweepingAlgorithm,subsec:insertionAlgorithm}).
+We then describe the pipe dream congruence as the transitive closure of a local rewriting rule generalizing that of the sylvester congruence (\cref{subsec:rewritingRule}).
+We then present a natural commutative diagram of lattice morphisms generalizing the connection between the recoil map and the binary tree insertion map on permutations and the canopy on binary trees (\cref{subsec:canopy}).
+Finally, we discuss a specific family of pipe dreams in connection to the $\nu$-Tamari lattices (\cref{subsec:nuTamari}).
 
@@
 
-In this section, we discuss four further topics on the pipe dream congruence.
-We first describe two algorithms to construct the pipe dream~$\insertion{\pi}{\omega}$ of~$\acyclicPipeDreams(\omega)$ of which a given permutation~$\pi$ is a linear extension (\cref{subsec:sweepingAlgorithm,subsec:insertionAlgorithm}).
+In this section, we discuss five further topics on the pipe dream congruence.
+We first present two algorithms to construct the pipe dream~$\insertion{\pi}{\omega}$ of~$\acyclicPipeDreams(\omega)$ of which a given permutation~$\pi$ is a linear extension (\cref{subsec:sweepingAlgorithm,subsec:insertionAlgorithm}).
 We then describe the pipe dream congruence~$\equiv_\omega$ as the transitive closure of a rewriting rule on permutations of~$[e, \omega]$ (\cref{subsec:rewritingRule}).
-Finally, we describe the natural coarsening of the pipe dream congruence~$\equiv_\omega$ by the recoil congruence~$\cong_\omega$ (\cref{subsec:canopy}).
+We then present the natural coarsening of the pipe dream congruence~$\equiv_\omega$ by the recoil congruence~$\cong_\omega$ (\cref{subsec:canopy}).
+Finally, we discuss a specific family of pipe dreams in connection to the $\nu$-Tamari lattices (\cref{subsec:nuTamari}).
 
@@
 
-To conclude, we generalize the notion of recoils of permutations and of canopy of a binary trees to show a natural commutative diagram of lattice homomorphisms.
+We now generalize the notion of recoils of permutations and of canopy of a binary trees to show a natural commutative diagram of lattice homomorphisms.
 We start with the easy generalization of recoils of a permutation.
@@
 \end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{The acyclic property for $\nu$-Tamari lattices}
+\label{subsec:nuTamari}
+
+We close this section by stating an open problem that relates our results to the $\nu$-Tamari lattices introduced by L.-F.~Préville-Ratelle and X.~Viennot in~\cite{PrevilleRatelleViennot}.
+These posets are indexed by a lattice path $\nu$ consisting of a finite number of north~(N) and east~(E) steps, and coincide with the classical Tamari lattices when $\nu=(NE)^n$.
+
+In~\cite{CeballosPadrolSarmiento}, it was shown that the $\nu$-Tamari lattice can be obtained as the increasing flip poset on pipe dreams~$\pipeDreams(\omega_\nu)$ for an explicit permutation $\omega_\nu$ associated to $\nu$.
+The permutations of the form~$\omega_\nu$ can be easily characterized as follows.
+We refer to~\cite{CeballosPadrolSarmiento} for details.
+
+The \defn{Rothe diagram} of a permutation~$\omega$ is the set $\set{(\omega(j),i)}{i<j,\ \omega(i)>\omega(j)}$ in matrix notation.
+A permutation $\omega$ is called \defn{dominant} if its Rothe diagram is the Ferrer's diagram of a partition located at the top left corner $(1,1)$.
+Equivalently, a permutation~$\omega$ is dominant if and only if it is 132-avoiding.
+For a permutation~$\omega = \omega_1 \dots \omega_n \in \fS_n$, we denote by~$0\omega$ the permutation~$0 \omega_1 \dots \omega_n$ of~$\{0, 1, \dots, n\}$, and we consider here pipe dreams with pipes indexed by~$\{0, 1, \dots, n\}$.
+%For instance, for the reversed permutation~$\omega = n \dots 2 1$, the permutation~$0\omega$ is the permutation~$\rho_n$ considered in \cref{exm:Tamari1}.
+%The permutations $\omega_\nu$ associated to lattice paths $\nu$ are those of the form~$1\oplus w$ for some dominant permutation $w$, see~\cite{CeballosPadrolSarmiento}.
+
+\begin{openproblem}%[The acyclic property for $\nu$-Tamari lattices]
+\label{prob:nuAcyclicProperty}
+Show that if $\omega$ is a dominant permutation then all pipe dreams with permutation $0 \omega$ are acyclic.
+%In particular, the corresponding $\nu$-Tamari lattice is the increasing flip poset on acyclic pipe dreams~$\acyclicPipeDreams(1\oplus \omega)$.
+\end{openproblem}
+
+From \cref{exm:Tamari1}, we know that this property holds when $\omega=n\dots21$ is the reverse permutation. 
+In this case, the increasing flip poset on~$\pipeDreams(0 \omega)$ is the classical Tamari lattice.
+Removing vertex $0$ from the contact graph of a pipe dream~$ P\in \pipeDreams(0 \omega)$ returns the binary tree corresponding to $P$ (with the leaves removed and the internal nodes labeled from $1$ to $n$).
+The edges of the binary tree are oriented going away from the root of the tree.  
+See \cref{fig:bijection}.
+We have also checked this property computationally for all dominant permutations up to $n=8$.
+
+Applying our Theorem~\ref{thm:pipeDreamQuotient}, we get the following consequence.
+
+\begin{proposition}
+If the statement of Open Problem~\ref{prob:nuAcyclicProperty} holds, then the $\nu$-Tamari lattice is a lattice quotient of the interval~$[e,\omega_\nu]$.
+\end{proposition}
 
@@
 
+\section*{Acknowledgments}
+
+We are grateful to Florent Hivert for various discussions. We also thank Martin Rubey for his comments which led us to think about Open Problem~\ref{prob:nuAcyclicProperty}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \bibliographystyle{alpha}

### 2023-05-10 acyclicFacets/draft/latticePipeDreams.tex
I added proof in subsection 4.5

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{The acyclic property for $\nu$-Tamari lattices}
-\label{subsec:nuTamari}
-
-We close this section by stating an open problem that relates our results to the $\nu$-Tamari lattices introduced by L.-F.~Préville-Ratelle and X.~Viennot in~\cite{PrevilleRatelleViennot}.
+\input{nuTamari}
+
+%
+%\subsection{The acyclic property for $\nu$-Tamari lattices}
+%\label{subsec:nuTamari}
+%
+%We close this section by stating an open problem that relates our results to the $\nu$-Tamari lattices introduced by L.-F.~Préville-Ratelle and X.~Viennot in~\cite{PrevilleRatelleViennot}.
 These posets are indexed by a lattice path $\nu$ consisting of a finite number of north~(N) and east~(E) steps, and coincide with the classical Tamari lattices when $\nu=(NE)^n$.
-
-In~\cite{CeballosPadrolSarmiento}, it was shown that the $\nu$-Tamari lattice can be obtained as the increasing flip poset on pipe dreams~$\pipeDreams(\omega_\nu)$ for an explicit permutation $\omega_\nu$ associated to $\nu$.
+%
+%In~\cite{CeballosPadrolSarmiento}, it was shown that the $\nu$-Tamari lattice can be obtained as the increasing flip poset on pipe dreams~$\pipeDreams(\omega_\nu)$ for an explicit permutation $\omega_\nu$ associated to $\nu$.
 The permutations of the form~$\omega_\nu$ can be easily characterized as follows.
 We refer to~\cite{CeballosPadrolSarmiento} for details.
-
-The \defn{Rothe diagram} of a permutation~$\omega$ is the set $\set{(\omega(j),i)}{i<j,\ \omega(i)>\omega(j)}$ in matrix notation.
-A permutation $\omega$ is called \defn{dominant} if its Rothe diagram is the Ferrer's diagram of a partition located at the top left corner $(1,1)$.
+%
+%The \defn{Rothe diagram} of a permutation~$\omega$ is the set $\set{(\omega(j),i)}{i<j,\ \omega(i)>\omega(j)}$ in matrix notation.
+%A permutation $\omega$ is called \defn{dominant} if its Rothe diagram is the Ferrer's diagram of a partition located at the top left corner $(1,1)$.
 Equivalently, a permutation~$\omega$ is dominant if and only if it is 132-avoiding.
-For a permutation~$\omega = \omega_1 \dots \omega_n \in \fS_n$, we denote by~$0\omega$ the permutation~$0 \omega_1 \dots \omega_n$ of~$\{0, 1, \dots, n\}$, and we consider here pipe dreams with pipes indexed by~$\{0, 1, \dots, n\}$.
-%For instance, for the reversed permutation~$\omega = n \dots 2 1$, the permutation~$0\omega$ is the permutation~$\rho_n$ considered in \cref{exm:Tamari1}.
-%The permutations $\omega_\nu$ associated to lattice paths $\nu$ are those of the form~$1\oplus w$ for some dominant permutation $w$, see~\cite{CeballosPadrolSarmiento}.
-
-\begin{openproblem}%[The acyclic property for $\nu$-Tamari lattices]
-\label{prob:nuAcyclicProperty}
-Show that if $\omega$ is a dominant permutation then all pipe dreams with permutation $0 \omega$ are acyclic.
+%For a permutation~$\omega = \omega_1 \dots \omega_n \in \fS_n$, we denote by~$0\omega$ the permutation~$0 \omega_1 \dots \omega_n$ of~$\{0, 1, \dots, n\}$, and we consider here pipe dreams with pipes indexed by~$\{0, 1, \dots, n\}$.
+%%For instance, for the reversed permutation~$\omega = n \dots 2 1$, the permutation~$0\omega$ is the permutation~$\rho_n$ considered in \cref{exm:Tamari1}.
+%%The permutations $\omega_\nu$ associated to lattice paths $\nu$ are those of the form~$1\oplus w$ for some dominant permutation $w$, see~\cite{CeballosPadrolSarmiento}. 
+%
+%\begin{openproblem}%[The acyclic property for $\nu$-Tamari lattices]
+%\label{prob:nuAcyclicProperty}
+%Show that if $\omega$ is a dominant permutation then all pipe dreams with permutation $0 \omega$ are acyclic.
 %In particular, the corresponding $\nu$-Tamari lattice is the increasing flip poset on acyclic pipe dreams~$\acyclicPipeDreams(1\oplus \omega)$.
-\end{openproblem}
-
-From \cref{exm:Tamari1}, we know that this property holds when $\omega=n\dots21$ is the reverse permutation. 
-In this case, the increasing flip poset on~$\pipeDreams(0 \omega)$ is the classical Tamari lattice.
+%\end{openproblem}
+%
+%From \cref{exm:Tamari1}, we know that this property holds when $\omega=n\dots21$ is the reverse permutation. 
+%In this case, the increasing flip poset on~$\pipeDreams(0 \omega)$ is the classical Tamari lattice.
 Removing vertex $0$ from the contact graph of a pipe dream~$ P\in \pipeDreams(0 \omega)$ returns the binary tree corresponding to $P$ (with the leaves removed and the internal nodes labeled from $1$ to $n$).
-The edges of the binary tree are oriented going away from the root of the tree.  
-See \cref{fig:bijection}.
-We have also checked this property computationally for all dominant permutations up to $n=8$.
-
-Applying our Theorem~\ref{thm:pipeDreamQuotient}, we get the following consequence.
-
-\begin{proposition}
-If the statement of Open Problem~\ref{prob:nuAcyclicProperty} holds, then the $\nu$-Tamari lattice is a lattice quotient of the interval~$[e,\omega_\nu]$.
-\end{proposition}
+%The edges of the binary tree are oriented going away from the root of the tree.  
+%See \cref{fig:bijection}.
+%We have also checked this property computationally for all dominant permutations up to $n=8$. 
+%
+%Applying our Theorem~\ref{thm:pipeDreamQuotient}, we get the following consequence.
+%
+%\begin{proposition}
+%If the statement of Open Problem~\ref{prob:nuAcyclicProperty} holds, then the $\nu$-Tamari lattice is a lattice quotient of the interval~$[e,\omega_\nu]$.
+%\end{proposition}
 

### 2023-05-10 acyclicFacets/draft/nuTamari.tex
I added proof in subsection 4.5

\subsection{The acyclic property for $\nu$-Tamari lattices} 
\label{subsec:nuTamari} 
\nantel{I commented out the original section and input the file "nuTamari"}

We close this section with a theorem that relates our results to the $\nu$-Tamari lattices introduced by L.-F.~Préville-Ratelle and X.~Viennot in~\cite{PrevilleRatelleViennot}. These posets are indexed by a lattice path $\nu$ consisting of a finite number of north~(N) and east~(E) steps, and coincide with the classical Tamari lattices when $\nu=(NE)^n$.

In~\cite{CeballosPadrolSarmiento}, it was shown that the $\nu$-Tamari lattice can be obtained as the increasing flip poset on pipe dreams~$\pipeDreams(\omega_\nu)$ for an explicit permutation $\omega_\nu$ associated to $\nu$. The permutations of the form~$\omega_\nu$ can be easily characterized as follows. We refer to~\cite{CeballosPadrolSarmiento} for details.

The \defn{Rothe diagram} of a permutation~$\omega$ is the set $\set{(\omega(j),i)}{i<j,\ \omega(i)>\omega(j)}$ in matrix notation.
A permutation $\omega$ is called \defn{dominant} if its Rothe diagram is the Ferrer's diagram of a partition located at the top left corner $(1,1)$. Equivalently, a permutation~$\omega$ is dominant if and only if it is 132-avoiding. 
For a permutation~$\omega = \omega_1 \dots \omega_n \in \fS_n$, we denote by~$0\omega$ the permutation~$0 \omega_1 \dots \omega_n$ of~$\{0, 1, \dots, n\}$, and we consider here pipe dreams with pipes indexed by~$\{0, 1, \dots, n\}$. The Theorem~\ref{prob:nuAcyclicProperty} below states that all pipe dreams with permutation $0 \omega$ are acyclic if and only if $\omega$ is a dominant permutation.

From \cref{exm:Tamari1}, we know that this property holds when $\omega=n\dots21$ is the reverse permutation. 
In this case, the increasing flip poset on~$\pipeDreams(0 \omega)$ is the classical Tamari lattice. Removing vertex $0$ from the contact graph of a pipe dream~$ P\in \pipeDreams(0 \omega)$ returns the binary tree corresponding to $P$ (with the leaves removed and the internal nodes labeled from $1$ to $n$).
The edges of the binary tree are oriented going away from the root of the tree.  
See \cref{fig:bijection}.

Before we start, we need some definition and notation. Given a pipe dream $P$, we say that a crossing is \defn{horizontally connected} if all positions west of it are crossing,
so that the horizontal pipe of the crossing join the west boundary horizontally, without any elbows. Similarly, a crossing is  \defn{vertically connected} if all position north of it are crossing. A \defn{(general) chute move}
is a special increasing flip from a crossing to a northeast contact such that the rectangle defined by these two positions contains only crossing
except in the southeast, northwest and northeast corners (see~\cite[Figure 13]{CeballosPadrolSarmiento}). The following statement appear
in Remark 38 of~\cite{CeballosPadrolSarmiento}, its proof follows from previous result within the cited paper.

\begin{lemma}[\cite{CeballosPadrolSarmiento}]\label{lem:onlychute} 
If $\omega$ is dominant, then any flip of any pipe dream with permutation $0\omega$ is a (general) chute move.
\end{lemma}

The above lemma is very helpful to show our next result.

\begin{lemma}\label{lem:hv_connected} 
If $\omega$ is dominant, then any crossing of any pipe dream with permutation $0\omega$ must be horizontally or vertically connected.
\end{lemma}

\begin{proof}
We proceed by induction on the increasing flip poset of the pipe dreams with $0\omega$ permutation. 
For the greedy pipe dream, where all the crossing are left adjusted, they are all horizontally connected in this case.
We assume the result is true for any crossing in a pipe dream $P$ and show that it still holds  for any crossing of a pipe dream  $Q$ obtained from $P$ by a single flip.
In light of Lemma~\ref{lem:onlychute}, the difference between $P$ and $Q$ must be a single general chute move. As in the picture of the chute portion in $P$ below, 
let $(c,t)$ be the position (row $t$, column $c$) of the crossing that will flip with the contact in position $(d,s)$.
$$	\centerline{\includegraphics[scale=.2]{chuteofP}}  $$
By assumption, all crossings of  $P$ are either horizontally or vertically connected. Since in position $(c,s)$ there is a contact, any crossing in row $s$ east of column $c$ must
be vertically connected, and by extension all crossing in rows $\le t$ strictly between column $c$ and $d$ are vertically connected.

The pipe dream $Q$ differ from $P$ in only two positions. The crossings of $Q$ are still obviously horizontally or vertically connected is all rows $\ne t$ and all columns $\ne d$.
For row $t$, the remark above shows that in $P$, the crossings strictly between column $c$ and $d$ are vertically connected, so they will still be so in $Q$, resolving all crossings in row $t$
For column $d$, we only need to show that the new crossing in position $(d,s)$ is vertically connected (it cannot be horizontally connected).
We show that we have crossings in column $d$ in all rows $\le s$. Assume for contradiction that there is a contact in row $r<s$ and column $d$.
Let $e$ be the west-most contact east of $d$ in row s. Recall that all crossings in row $s$ strictly between column $d$ and $e$ must be vertically connected (they are east of $c$).

Following Lemma~\ref{lem:horiVertCrossings} and considering $P$, let $i<j$ be the pipes crossing at position $(c,t)$. 
We claim it is not possible to have a crossing in position $(e,r)$, otherwise let $j<k$ be the pipes crossing at position $(e,r)$.
Remark that indeed the pipe $j$ goes through position $(c,t)$ and $(e,r)$, it travel  horizontally west to column d, and south to row s. 
The pipe $k$ at $(e,r)$, going south, cannot be $i$, so it must turn west before row s, travel horizontally and cross $j$ again, a contradiction to $P$ being reduced.
Hence $(e,r)$ must be a contact of $j$ with a pipe $k$.

If the pipe $k=i$, then we have two contacts of $i$ and $j$ in different positions $(d,s)$ and $(e,r)$, this would contradict Lemma~\ref{lem:onlychute}, for the flip of the crossing $(c,t)$
to $(e,r)$ is not a general chute move. If the pipe $k\ne i$, then we remark that, as above, it must cross with $j$ in column $d$ and row $r<r'<s$. We can perform a flip of the crossing
$(d,r')$ with the contact $(e,r)$. This gives us a new pipe dream $P'$ with permutation $0\omega$ similar to $P$ but with an $r'>r$. We repeat the argument in the position $(e,r')$: it cannot be a crossing,
it cannot be a contact with $i$, it must be a contact with a $k'\ne i$. The pipe $k'$ must cross the pipe $j$ in column $d$ and row $r<r'<r''<s$. We can do another flip to get $P''$.
We can only repeat this process finitely many times and after $m<s-r$ steps, we must have a $k^{(m)}=i$ and reach a contradiction. 
Therefor, it is not possible that $P$ has a contact in column $d$ and row $r<s$, and the crossing of $Q$ in position $d,s)$ is vertically connected.
\end{proof}

\begin{theorem}%[The acyclic property for $\nu$-Tamari lattices]
\label{prob:nuAcyclicProperty}
All pipe dreams with permutation $0 \omega$ are acyclic if and only if $\omega$ is a dominant permutation.
\end{theorem}

\begin{proof} For the forward direction, assume that $\omega$ is not dominant. 
Let $P_0$ be the greedy pipe dream of $0\omega$. It has no crossing in row 0, and cannot be a partition starting at row 1.
There must be a row $r>1$ with more crossing than in row $r-1$. 
Considering the rightmost column $c$ of $P$ with a crossing in row $r$,  the pipes $r<k$ are crossing at $(c,r)$, $\omega^{-1}(k)<\omega^{-1}(r)$ and are in contact in position $(c+1,r-1)$.
Let $Q$ be the pipe dream obtained from $P_0$ by the flip of the crossing at $(c,r)$ with the contact at $(c+1,r-1)$.
The contact of $Q$ at $(c,r)$ would gives $r\contactLess{Q} k$. In row $0$ we only have contacts and $\omega^{-1}(k)<\omega^{-1}(r)$, combining this  with Lemma~\ref{lem:rectangle} would give  that 
$k \contactLess{Q} r$, a contradiction, hence $Q$ is not acyclic.

For the reverse direction, assume we have a pipe dream $P$ that is not acyclic. The contact graph must contain a cycle $i_1 \to i_2\to\cdots\to i_m\to i_1$.
This is only possible if some pipe $i_j$ and $i_\ell$ with some contact on both side of the crossing.
Hence that crossing is not horizontally nor vertically connected, therefore Lemma~\ref{lem:hv_connected} gives that $\omega$ is not dominant.
\end{proof}

Applying our Theorem~\ref{thm:pipeDreamQuotient}, we get the following consequence.

\begin{corollary}
If the statement of Open Problem~\ref{prob:nuAcyclicProperty} holds, then the $\nu$-Tamari lattice is a lattice quotient of the interval~$[e,\omega_\nu]$.
\end{corollary}

### 2023-05-10 acyclicFacets/draft/nuTamari.tex
Added a little detail in proof of 4.19

@@
 The Theorem~\ref{prob:nuAcyclicProperty} below states that all pipe dreams with permutation $0 \omega$ are acyclic if and only if $\omega$ is a dominant permutation.
+\nantel{modify intro to reflect this?}
 
@@
 \end{theorem}
+\nantel{add in acknowledgement that : Lucas Gagnon had a proof of converse in different contaxt}
 
-\begin{proof} For the forward direction, assume that $\omega$ is not dominant. 
+\begin{proof} For the forward implication, assume that $\omega$ is not dominant. 
 Let $P_0$ be the greedy pipe dream of $0\omega$. It has no crossing in row 0, and cannot be a partition starting at row 1.
@@
 
-For the reverse direction, assume we have a pipe dream $P$ that is not acyclic. The contact graph must contain a cycle $i_1 \to i_2\to\cdots\to i_m\to i_1$.
-This is only possible if some pipe $i_j$ and $i_\ell$ with some contact on both side of the crossing.
+For the converse, assume we have a pipe dream that is not acyclic. The contact graph must contain a cycle $i_1 \to i_2\to\cdots\to i_m\to i_1$.
+The contact $i_1 \to i_2$ implies that a portion of the pipe $i_2$ is southeast of $i_1$. The same is true for the contact $i_2\to i_3$ and so on.
+In the end, we have that $i_m\to i_1$ gives a portion of the pipe $i_m$ is northwest of $i_1$. 
+This is only possible if some pipe $i_j$ cross $i_1$ with the contact $i_1\to i_2$ on one side of the crossing of $i_1$ and $i_j$, and the contact $i_j \to i_{j+1 \mod m}$ on the other side.
 Hence that crossing is not horizontally nor vertically connected, therefore Lemma~\ref{lem:hv_connected} gives that $\omega$ is not dominant.

### 2023-05-11 acyclicFacets/draft/nuTamari.tex
Needed more details in the last part of the proof.

--- 2023-05-10 acyclicFacets/draft/nuTamari.tex
@@
 
+\nantel{add in acknowledgement that : Lucas Gagnon had a proof of converse in different context}
 \begin{theorem}%[The acyclic property for $\nu$-Tamari lattices]
@@
 
-\begin{proof} For the forward direction, assume that $\omega$ is not dominant. 
+\begin{proof} For the forward implication, assume that $\omega$ is not dominant. 
 Let $P_0$ be the greedy pipe dream of $0\omega$. It has no crossing in row 0, and cannot be a partition starting at row 1.
@@
 
-For the reverse direction, assume we have a pipe dream $P$ that is not acyclic. The contact graph must contain a cycle $i_1 \to i_2\to\cdots\to i_m\to i_1$.
-This is only possible if some pipe $i_j$ and $i_\ell$ with some contact on both side of the crossing.
-Hence that crossing is not horizontally nor vertically connected, therefore Lemma~\ref{lem:hv_connected} gives that $\omega$ is not dominant.
+\nantel{Here, I went a bit fast before. Here is a much more detailed version}
+For the converse, assume we have a pipe dream that is not acyclic. The contact graph must contain a cycle $i_1 \to i_2\to\cdots\to i_m\to i_1$.
+The contact $i_1 \to i_2$ is southeast of $i_1$ and the contact  $i_m\to i_1$ northwest of $i_1$. 
+Let $i_k$ be the first time where $i_{k-1}\to i_k$ is a contact southeast of $i_1$ and $i_k \to i_{k+1}$\footnote{with the convention that$k+1$ is $1$ if $k=m$} is a contact northwest of $i_1$.
+This implies that the pipe $i_k$ cross $i_1$. Consider the case where $i_1<i_k$, hence $i_k$ is the vertical pipe of the crossing. 
+The contact $i_k\to i_{j+1}$ must occur after the crossing of $i_1$ and $i_k$, since it is northwest of $i_1$.
+This implies that the crossing of $i_1$ and $i_k$ cannot be vertically connected. 
+If $k=2$, then the contact of $i_1\to i_2$ is before the crossing, implying that the crossing of $i_1$ and $i_2$ cannot be horizontally connected. 
+The Lemma~\ref{lem:hv_connected} gives that $\omega$ is not dominant in this case.
+Assume $k>2$ and assume that the crossing $i_1$ and $i_k$ is horizontally connected. The contact $i_1\to i_2$ is southeast of $i_k$ and the contact $i_{k-1}\to i_k$ is northwest.
+Therefor there must be a pipe $i_j$ for $1<j<k$, such that the contact $i_{j-1}\to i_j$ is southeast of both $i_1$ and $i_k$, and the contact $i_{j}\to i_{j+1}$ is southeast of $i_1$ but northwest of $i_j$.
+This implies that the pipe $i_j$ and $i_k$ cross southeast of $i_1$ and we must have $i_j<i_k$. The crossing of $i_j$ and $i_k$ cannot be horizontally connected since $i_j$ has a contact west of it.
+It cannot be vertically connected since $i_k$ has a contact north of it. Again, Lemma~\ref{lem:hv_connected} gives that $\omega$ is not dominant in this case.
+
+The case where $i_1>i_k$ is very similar, reflecting all arguments. Hence, in all cases, if a pipe dream is not acyclic, then the permutation $\omega$ is not dominant. 
 \end{proof}

### 2023-05-13 acyclicFacets/draft/nuTamari.tex
Much simplified version of Section 4.5 (a single page proof)

--- 2023-05-10 acyclicFacets/draft/nuTamari.tex
@@
 \label{subsec:nuTamari}
-\nantel{I commented out the original section and input the file "nuTamari"}
 
@@
 For a permutation~$\omega = \omega_1 \dots \omega_n \in \fS_n$, we denote by~$0\omega$ the permutation~$0 \omega_1 \dots \omega_n$ of~$\{0, 1, \dots, n\}$, and we consider here pipe dreams with pipes indexed by~$\{0, 1, \dots, n\}$.
-The Theorem~\ref{prob:nuAcyclicProperty} below states that all pipe dreams with permutation $0 \omega$ are acyclic if and only if $\omega$ is a dominant permutation.
 
-From \cref{exm:Tamari1}, we know that this property holds when $\omega=n\dots21$ is the reverse permutation. 
+From \cref{exm:Tamari1}, we see that this property holds when $\omega=n\dots21$ is the reverse permutation. 
 In this case, the increasing flip poset on~$\pipeDreams(0 \omega)$ is the classical Tamari lattice.
@@
 
-Before we start, we need some definition and notation. Given a pipe dream $P$, we say that a crossing is \defn{horizontally connected} if all positions west of it are crossing,
-so that the horizontal pipe of the crossing join the west boundary horizontally, without any elbows.
-Similarly, a crossing is  \defn{vertically connected} if all position north of it are crossing.
-A \defn{(general) chute move}
-is a special increasing flip from a crossing to a northeast contact such that the rectangle defined by these two positions contains only crossing
-except in the southeast, northwest and northeast corners (see~\cite[Figure 13]{CeballosPadrolSarmiento}). The following statement appear
-in Remark 38 of~\cite{CeballosPadrolSarmiento}, its proof follows from previous result within the cited paper.
+Given a pipe dream $P$, We write $i\to j$ whenever $i$ has a contact with $j$,
+when $P$ has a cycle ${\bf C}=(i_1, i_2, \ldots, i_m)$ where $i_1 \to i_2\to\cdots\to i_m\to i_1$, we can always assume that $i_1=\min\{i_1,\ldots,i_m\}$.
+To describe the location of crossing and contacts (elbows), we use the coordinate $(c,r)$ where $r$ is the row and $c$ is the column.
 
-\begin{lemma}[\cite{CeballosPadrolSarmiento}]\label{lem:onlychute} 
-If $\omega$ is dominant, then any flip of any pipe dream with permutation $0\omega$ is a (general) chute move.
+\begin{lemma}\label{lem:not_dominant}
+For a pipe dream $P$ with permutation $0\omega$ and pipes $i<j$ crossing. If $i$ has an elbow southwest of the crossing and $j$ has an elbow northeast of the crossing, then $\omega$ is not dominant.
 \end{lemma}
 
-The above lemma is very helpful to show our next result.
+\begin{proof} Let $(c,r)$ be the position of the crossing. Since $i$ has an elbow southwest of $(c,r)$ we have $r\le i-1$.
+Since $j$ has an elbow northeast of the crossing, there are at most $i-2$ pipes that cross north of $(c,r)$ in column $c$. 
+Hence, at least $2$ pipes $<i$ reach the Northern border before column $c$.
+Excluding $0$, there is at least a pipe $0<h$ such that $h<i<j$ and $\omega^{-1}(h)< \omega^{-1}(j)<\omega^{-1}(i)$.
+This is a $132$ pattern in $\omega$, therefor $\omega$ is not dominant. \end{proof}
 
-\begin{lemma}\label{lem:hv_connected} 
-If $\omega$ is dominant, then any crossing of any pipe dream with permutation $0\omega$ must be horizontally or vertically connected.
-\end{lemma}
-
-\begin{proof}
-We proceed by induction on the increasing flip poset of the pipe dreams with $0\omega$ permutation. 
-For the greedy pipe dream, where all the crossing are left adjusted, they are all horizontally connected in this case.
-We assume the result is true for any crossing in a pipe dream $P$ and show that it still holds  for any crossing of a pipe dream  $Q$ obtained from $P$ by a single flip.
-In light of Lemma~\ref{lem:onlychute}, the difference between $P$ and $Q$ must be a single general chute move. As in the picture of the chute portion in $P$ below, 
-let $(c,t)$ be the position (row $t$, column $c$) of the crossing that will flip with the contact in position $(d,s)$.
-$$	\centerline{\includegraphics[scale=.2]{chuteofP}}  $$
-By assumption, all crossings of  $P$ are either horizontally or vertically connected. Since in position $(c,s)$ there is a contact, any crossing in row $s$ east of column $c$ must
-be vertically connected, and by extension all crossing in rows $\le t$ strictly between column $c$ and $d$ are vertically connected.
-
-The pipe dream $Q$ differ from $P$ in only two positions. The crossings of $Q$ are still obviously horizontally or vertically connected is all rows $\ne t$ and all columns $\ne d$.
-For row $t$, the remark above shows that in $P$, the crossings strictly between column $c$ and $d$ are vertically connected, so they will still be so in $Q$, resolving all crossings in row $t$
-For column $d$, we only need to show that the new crossing in position $(d,s)$ is vertically connected (it cannot be horizontally connected).
-We show that we have crossings in column $d$ in all rows $\le s$. Assume for contradiction that there is a contact in row $r<s$ and column $d$.
-Let $e$ be the west-most contact east of $d$ in row s. Recall that all crossings in row $s$ strictly between column $d$ and $e$ must be vertically connected (they are east of $c$).
-
-Following Lemma~\ref{lem:horiVertCrossings} and considering $P$, let $i<j$ be the pipes crossing at position $(c,t)$. 
-We claim it is not possible to have a crossing in position $(e,r)$, otherwise let $j<k$ be the pipes crossing at position $(e,r)$.
-Remark that indeed the pipe $j$ goes through position $(c,t)$ and $(e,r)$, it travel  horizontally west to column d, and south to row s. 
-The pipe $k$ at $(e,r)$, going south, cannot be $i$, so it must turn west before row s, travel horizontally and cross $j$ again, a contradiction to $P$ being reduced.
-Hence $(e,r)$ must be a contact of $j$ with a pipe $k$.
-
-If the pipe $k=i$, then we have two contacts of $i$ and $j$ in different positions $(d,s)$ and $(e,r)$, this would contradict Lemma~\ref{lem:onlychute}, for the flip of the crossing $(c,t)$
-to $(e,r)$ is not a general chute move. If the pipe $k\ne i$, then we remark that, as above, it must cross with $j$ in column $d$ and row $r<r'<s$. We can perform a flip of the crossing
-$(d,r')$ with the contact $(e,r)$.
-This gives us a new pipe dream $P'$ with permutation $0\omega$ similar to $P$ but with an $r'>r$.
-We repeat the argument in the position $(e,r')$: it cannot be a crossing,
-it cannot be a contact with $i$, it must be a contact with a $k'\ne i$. The pipe $k'$ must cross the pipe $j$ in column $d$ and row $r<r'<r''<s$. We can do another flip to get $P''$.
-We can only repeat this process finitely many times and after $m<s-r$ steps, we must have a $k^{(m)}=i$ and reach a contradiction. 
-Therefor, it is not possible that $P$ has a contact in column $d$ and row $r<s$, and the crossing of $Q$ in position $d,s)$ is vertically connected.
-\end{proof}
-
-\begin{theorem}%[The acyclic property for $\nu$-Tamari lattices]
+\nantel{modify intro to reflect this and must thanks Lucas Gagnon for helpful suggestions that shorten our proof}
+\begin{theorem}
 \label{prob:nuAcyclicProperty}
-All pipe dreams with permutation $0 \omega$ are acyclic if and only if $\omega$ is a dominant permutation.
+All pipe dreams with $0 \omega$ are acyclic if and only if $\omega$ is a dominant permutation.
 \end{theorem}
 
-\begin{proof} For the forward direction, assume that $\omega$ is not dominant. 
+\begin{proof} For the forward implication, assume that $\omega$ is not dominant. 
 Let $P_0$ be the greedy pipe dream of $0\omega$. It has no crossing in row 0, and cannot be a partition starting at row 1.
@@
 Let $Q$ be the pipe dream obtained from $P_0$ by the flip of the crossing at $(c,r)$ with the contact at $(c+1,r-1)$.
-The contact of $Q$ at $(c,r)$ would gives $r\contactLess{Q} k$. In row $0$ we only have contacts and $\omega^{-1}(k)<\omega^{-1}(r)$, combining this  with Lemma~\ref{lem:rectangle} would give  that 
-$k \contactLess{Q} r$, a contradiction, hence $Q$ is not acyclic.
+The contact of $Q$ at $(c,r)$ gives $r\contactLess{Q} k$. In row $0$ we only have contacts, we have $\omega^{-1}(k)<\omega^{-1}(r)$ and Lemma~\ref{lem:rectangle} gives  that 
+$k \contactLess{Q} r$, hence $Q$ is not acyclic.
 
-For the reverse direction, assume we have a pipe dream $P$ that is not acyclic. The contact graph must contain a cycle $i_1 \to i_2\to\cdots\to i_m\to i_1$.
-This is only possible if some pipe $i_j$ and $i_\ell$ with some contact on both side of the crossing.
-Hence that crossing is not horizontally nor vertically connected, therefore Lemma~\ref{lem:hv_connected} gives that $\omega$ is not dominant.
+For the converse, assume we have a pipe dream $P$ that is not acyclic. The contact graph must contain a cycle ${\bf C}=(i, j_1, \ldots, j_m)$ with $i<j_k$ for all $1\le k\le m$. 
+The contact $i \to j_1$ is southeast of $i$ and the contact  $j_m\to i$ northwest of $i$. 
+Let $j_k$ be the first time where $j_{k-1}\to j_k$ is a contact southeast of $i$ and $j_k \to j_{k+1}$\footnote{with the convention that $j_{m+1}=i$} is a contact northwest of $i$.
+This implies that the pipe $j=j_k$ cross $i$ in some position $(c,r)$. Since $i<j$, the pipe $j$ is the vertical pipe of the crossing. 
+Remark that all contact $j_{k'}\to j_{k'+1}$ are southeast of $i$ for $1\le k' <k$.
+
+Consider first the case $m=1$. The contact $i\to j$ implies there is an elbow  of $i$ southwest of the crossing and  $j\to i$ implies there is an elbow of $j$  northeast of the crossing. 
+Lemma~\ref{lem:not_dominant} implies  $\omega$ is not dominant.
+Assume now that $m>1$. If $i$ has an elbow southwest of the crossing, then Lemma~\ref{lem:not_dominant} implies  $\omega$ is not dominant.
+Thus, we may as well ssume that $i$ has no elbow west of $(c,r)$, and therefor $r=i$. The contact $i\to j_1$ must be southeast of both $i$ and $j$ and the  $j_{k-1}\to j_k=j$ is northwest of $j$.
+Let  $j'=j_{k'}$ for $1\le k' <k$ be the first pipe such that the $j_{k'-1}\to j'$ is southeast of $j$ and $j'\to j_{k'+1}$ is northwest of $j$, and both are southeast of $i$. 
+Hence $j$ and $j'$ are crossing at some position $(c',r')$ and the pipe $j'$ remain southeast of $i$ between these two contacts.
+Remark that now all contacts $j_{k''}\to j_{k''+1}$ are southeast of both pipes  $i$ and $j$ for $1\le k'' <k' < k$.
+
+if $j'<j$, then the contact $j'\to j_{k'+1}$ is southwest of the crossing at $(c',r')$ and  $r'\le j'-1$ and $j$ has a contact north of $(c,r)$ which is north of $(c',r')$.
+We can apply Lemma~\ref{lem:not_dominant} to
+ $j'<j$ and $\omega$ is not dominant. if $j'>j$, and $j$ has no elbow southwest of $(c',r')$, then the pipe $j'$ must cross $i$ in row $i$ due west of $(c,i)$.
+We now repeat the argument above: we have the contact $i\to j_1$ must be southeast of $i$, $j$ and $j'$,
+and the contact $j_{k'-1}\to j_{k'}=j'$ is northwest of $j'$.
+Let  $j''=j_{k''}$ for $1\le k''<k' <k$ be the first pipe such that the $j_{k''-1}\to j''$ is southeast of $j'$ and $j''\to j_{k''+1}$ is northwest of $j'$, and both are southeast of $i$ and $j$. 
+Hence $j'$ and $j''$ are crossing at some position $(c'',r'')$ and the pipe $j''$ remain southeast of $i$ and $j$ between these two contacts.
+Remark that now all contacts $j_{k^{(3)}}\to j_{k^{(3)}+1}$ are southeast of both pipes  $i$, $j$ and $j'$ for $1\le k^{(3)}<k'' <k' < k$.
+
+The process above cannot continue at infinitum since $k-1$ is finite.
+At one point we will find $j^{(\ell)}<j^{(\ell-1)}$ where Lemma~\ref{lem:not_dominant} applies and conclude that $\omega$ is not dominant
+in all cases. 
 \end{proof}

### 2023-05-13 acyclicFacets/draft/latticePipeDreams.tex
Polished the proof (used chatGPT), changed intro and acknoledgement. done

--- 2023-04-26 acyclicFacets/draft/latticePipeDreams.tex
@@
 We then present a natural commutative diagram of lattice morphisms generalizing the connection between the recoil map and the binary tree insertion map on permutations and the canopy on binary trees (\cref{subsec:canopy}).
-Finally, we discuss a specific family of pipe dreams in connection to the $\nu$-Tamari lattices (\cref{subsec:nuTamari}).
+Finally, we show that all pipe dreams of $0\omega$ are acyclic whenever $\omega$ is dominant.
+Therefore, Theorem~\ref{thm:A} implies that the $\nu$-Tamari lattice is a quotient of the interval~$[e,\omega]$ for a well-chosen dominant permutation $\omega$ (\cref{subsec:nuTamari}).
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \subsection{The acyclic property for $\nu$-Tamari lattices} 
@@
 
-We close this section by stating an open problem that relates our results to the $\nu$-Tamari lattices introduced by L.-F.~Préville-Ratelle and X.~Viennot in~\cite{PrevilleRatelleViennot}.
-These posets are indexed by a lattice path $\nu$ consisting of a finite number of north~(N) and east~(E) steps, and coincide with the classical Tamari lattices when $\nu=(NE)^n$.
-
-In~\cite{CeballosPadrolSarmiento}, it was shown that the $\nu$-Tamari lattice can be obtained as the increasing flip poset on pipe dreams~$\pipeDreams(\omega_\nu)$ for an explicit permutation $\omega_\nu$ associated to $\nu$.
+We close this section with a theorem that relates our results to the $\nu$-Tamari lattices introduced by L.-F.~Pr\'eville-Ratelle and X.Viennot in\cite{PrevilleRatelleViennot}.
+These posets are indexed by a lattice path $\nu$ consisting of a finite number of north (N) and east (E) steps, and coincide with the classical Tamari lattices when $\nu=(NE)^n$.
+
+In~\cite{CeballosPadrolSarmiento}, it was shown that the $\nu$-Tamari lattice can be obtained as the increasing flip poset on pipe dreams~$\pipeDreams(\omega_\nu)$ for an explicit permutation $\omega_\nu$ associated with $\nu$.
 The permutations of the form~$\omega_\nu$ can be easily characterized as follows.
@@
 The \defn{Rothe diagram} of a permutation~$\omega$ is the set $\set{(\omega(j),i)}{i<j,\ \omega(i)>\omega(j)}$ in matrix notation.
-A permutation $\omega$ is called \defn{dominant} if its Rothe diagram is the Ferrer's diagram of a partition located at the top left corner $(1,1)$.
+A permutation $\omega$ is called \defn{dominant} if its Rothe diagram is the Ferrers diagram of a partition located at the top left corner $(1,1)$.
 Equivalently, a permutation~$\omega$ is dominant if and only if it is 132-avoiding.
-For a permutation~$\omega = \omega_1 \dots \omega_n \in \fS_n$, we denote by~$0\omega$ the permutation~$0 \omega_1 \dots \omega_n$ of~$\{0, 1, \dots, n\}$, and we consider here pipe dreams with pipes indexed by~$\{0, 1, \dots, n\}$.
-%For instance, for the reversed permutation~$\omega = n \dots 2 1$, the permutation~$0\omega$ is the permutation~$\rho_n$ considered in \cref{exm:Tamari1}.
-%The permutations $\omega_\nu$ associated to lattice paths $\nu$ are those of the form~$1\oplus w$ for some dominant permutation $w$, see~\cite{CeballosPadrolSarmiento}.
-
-\begin{openproblem}%[The acyclic property for $\nu$-Tamari lattices]
-\label{prob:nuAcyclicProperty}
-Show that if $\omega$ is a dominant permutation then all pipe dreams with permutation $0 \omega$ are acyclic.
-%In particular, the corresponding $\nu$-Tamari lattice is the increasing flip poset on acyclic pipe dreams~$\acyclicPipeDreams(1\oplus \omega)$.
-\end{openproblem}
-
-From \cref{exm:Tamari1}, we know that this property holds when $\omega=n\dots21$ is the reverse permutation. 
+For a permutation~$\omega = \omega_1 \dots \omega_n \in \fS_n$, we denote by~$0\omega$ the permutation~$0 \omega_1 \dots \omega_n$ of~${0, 1, \dots, n}$, and we consider here pipe dreams with pipes indexed by~${0, 1, \dots, n}$.
+
+From \cref{exm:Tamari1}, we see that this property holds when $\omega=n\dots21$ is the reverse permutation.
 In this case, the increasing flip poset on~$\pipeDreams(0 \omega)$ is the classical Tamari lattice.
@@
 See \cref{fig:bijection}.
-We have also checked this property computationally for all dominant permutations up to $n=8$.
-
-Applying our Theorem~\ref{thm:pipeDreamQuotient}, we get the following consequence.
-
-\begin{proposition}
-If the statement of Open Problem~\ref{prob:nuAcyclicProperty} holds, then the $\nu$-Tamari lattice is a lattice quotient of the interval~$[e,\omega_\nu]$.
-\end{proposition}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Given a pipe dream $P$, we write $i\to j$ whenever $i$ has a contact with $j$.
+When $P$ has a cycle ${\bf C}=(i_1, i_2, \ldots, i_m)$ where $i_1 \to i_2\to\cdots\to i_m\to i_1$, we can always assume that $i_1=\min\{i_1,\ldots,i_m\}$.
+To describe the location of crossings and contacts (elbows), we use the coordinate $(c,r)$, where $r$ is the row and $c$ is the column.
+
+\begin{lemma}\label{lem:not_dominant}
+For a pipe dream $P$ with permutation $0\omega$ and crossing pipes $i<j$: if $i$ has an elbow southwest of the crossing and $j$ has an elbow northeast of the crossing, then $\omega$ is not dominant.
+\end{lemma}
+
+\begin{proof}
+Let $(c,r)$ be the position of the crossing. Since $i$ has an elbow southwest of $(c,r)$, we have $r\leq i-1$.
+Since $j$ has an elbow northeast of the crossing, there are at most $i-2$ pipes that cross north of $(c,r)$ in column $c$.
+Hence, at least $2$ pipes $<i$ reach the Northern border before column $c$.
+Excluding $0$, there is at least a pipe $0<h$ such that $h<i<j$ and $\omega^{-1}(h)< \omega^{-1}(j)<\omega^{-1}(i)$.
+This is a $132$ pattern in $\omega$, therefore $\omega$ is not dominant.
+\end{proof}
+
+\begin{theorem}
+\label{prob:nuAcyclicProperty}
+All pipe dreams with $0 \omega$ are acyclic if and only if $\omega$ is a dominant permutation.
+\end{theorem}
+
+\begin{proof}
+For the forward implication, assume that $\omega$ is not dominant.
+Let $P_0$ be the greedy pipe dream of $0\omega$.
+It has no crossing in row 0, and cannot be a partition starting at row 1.
+There must be a row $r>1$ with more crossing than in row $r-1$.
+Considering the rightmost column $c$ of $P$ with a crossing in row $r$, the pipes $r<k$ are crossing at $(c,r)$, $\omega^{-1}(k)<\omega^{-1}(r)$ and are in contact in position $(c+1,r-1)$.
+Let $Q$ be the pipe dream obtained from $P_0$ by the flip of the crossing at $(c,r)$ with the contact at $(c+1,r-1)$.
+The contact of $Q$ at $(c,r)$ gives $r\contactLess{Q} k$.
+In row $0$ we only have contacts, we have $\omega^{-1}(k)<\omega^{-1}(r)$ and Lemma~\ref{lem:rectangle} gives that $k \contactLess{Q} r$, hence $Q$ is not acyclic.
+
+For the converse, assume we have a pipe dream $P$ that is not acyclic.
+The contact graph must contain a cycle ${\bf C}=(i, j_1, \ldots, j_m)$ with $i<j_k$ for all $1\le k\le m$.
+The contact $i \to j_1$ is southeast of $i$ and the contact $j_m\to i$ northwest of $i$.
+Let $j_k$ be the first time where $j_{k-1}\to j_k$ is a contact southeast of $i$ and $j_k \to j_{k+1}$ (with the convention that $j_{m+1}=i$) is a contact northwest of $i$.
+This implies that the pipe $j=j_k$ cross $i$ in some position $(c,r)$.
+Since $i<j$, the pipe $j$ is the vertical pipe of the crossing.
+
+Remark that all contacts $j_{k'}\to j_{k'+1}$ are southeast of $i$ for $1\le k' <k$.
+Consider first the case $m=1$.
+The contact $i\to j$ implies there is an elbow of $i$ southwest of the crossing and $j\to i$ implies there is an elbow of $j$ northeast of the crossing.
+Lemma~\ref{lem:not_dominant} implies $\omega$ is not dominant.
+
+Consider now the case $m>1$.
+If $i$ has an elbow southwest of the crossing, then Lemma~\ref{lem:not_dominant} implies $\omega$ is not dominant.
+Thus, we may assume that $i$ has no elbow west of $(c,r)$, and therefore $r=i$.
+The contact $i\to j_1$ must be southeast of both $i$ and $j$, and the $j_{k-1}\to j_k=j$ is northwest of $j$.
+Let $j'=j_{k'}$ for $1\le k' <k$ be the first pipe such that the $j_{k'-1}\to j'$ is southeast of $j$ and $j'\to j_{k'+1}$ is northwest of $j$, and both are southeast of $i$.
+Hence $j$ and $j'$ are crossing at some position $(c',r')$, and the pipe $j'$ remains southeast of $i$ between these two contacts.
+
+Remark that now all contacts $j_{k''}\to j_{k''+1}$ are southeast of both pipes $i$ and $j$ for $1\le k''<k'<k$.
+If $j'<j$, then the contact $j'\to j_{k'+1}$ is southwest of the crossing at $(c',r')$, and $r'\le j'-1$, and $j$ has a contact north of $(c,r)$ which is north of $(c',r')$.
+We can apply Lemma~\ref{lem:not_dominant} to $j'<j$, and $\omega$ is not dominant.
+
+If $j'>j$, and $j$ has no elbow southwest of $(c',r')$, then the pipe $j'$ must cross $i$ in row $i$ due west of $(c,i)$.
+We now repeat the argument above: we have the contact $i\to j_1$ must be southeast of $i$, $j$, and $j'$, and the contact $j_{k'-1}\to j_{k'}=j'$ is northwest of $j'$.
+Let $j''=j_{k''}$ for $1\le k''<k'<k$ be the first pipe such that the $j_{k''-1}\to j''$ is southeast of $j'$ and $j''\to j_{k''+1}$ is northwest of $j'$, and both are southeast of $i$ and $j$.
+Hence $j'$ and $j''$ are crossing at some position $(c'',r'')$, and the pipe $j''$ remains southeast of $i$ and $j$ between these two contacts.
+
+Remark that now all contacts $j_{k^{(3)}}\to j_{k^{(3)}+1}$ are southeast of both pipes  $i$, $j$ and $j'$ for $1\le k^{(3)}<k'' <k' < k$.
+The process above cannot continue at infinitum since $k-1$ is finite.
+At one point we will find $j^{(\ell)}<j^{(\ell-1)}$ where Lemma~\ref{lem:not_dominant} applies and conclude that $\omega$ is not dominant
+in all cases. 
+\end{proof}
+
+Applying our Theorem~\ref{thm:pipeDreamQuotient}, using the Isomorphism $[0e,0\omega_\nu]\cong [e,\omega_\nu]$, we get the following consequence.
+
+\begin{corollary}
+The $\nu$-Tamari lattice is a lattice quotient of the interval~$[e,\omega_\nu]$.
+\end{corollary}
 
@@
 
-We are grateful to Florent Hivert for various discussions. We also thank Martin Rubey for his comments which led us to think about Open Problem~\ref{prob:nuAcyclicProperty}.
+We are grateful to Florent Hivert for various discussions. We also thank Martin Rubey for his comments which led us to think about Theorem~\ref{prob:nuAcyclicProperty}. 
+We are very grateful to Lucas Gagnon who shared with us an independent proof of the forward direction of Theorem~\ref{prob:nuAcyclicProperty}, this allowed us to simplify our argument.
 

### 2023-05-13 acyclicFacets/draft/nuTamari.tex
Polished the proof (used chatGPT), changed intro and acknoledgement. done

@@
 
-We close this section with a theorem that relates our results to the $\nu$-Tamari lattices introduced by L.-F.~Préville-Ratelle and X.~Viennot in~\cite{PrevilleRatelleViennot}.
-These posets are indexed by a lattice path $\nu$ consisting of a finite number of north~(N) and east~(E) steps, and coincide with the classical Tamari lattices when $\nu=(NE)^n$.
+We close this section with a theorem that relates our results to the $\nu$-Tamari lattices introduced by L.-F.~Pr\'eville-Ratelle and X.Viennot in\cite{PrevilleRatelleViennot}.
+These posets are indexed by a lattice path $\nu$ consisting of a finite number of north (N) and east (E) steps, and coincide with the classical Tamari lattices when $\nu=(NE)^n$.
 
-In~\cite{CeballosPadrolSarmiento}, it was shown that the $\nu$-Tamari lattice can be obtained as the increasing flip poset on pipe dreams~$\pipeDreams(\omega_\nu)$ for an explicit permutation $\omega_\nu$ associated to $\nu$.
+In~\cite{CeballosPadrolSarmiento}, it was shown that the $\nu$-Tamari lattice can be obtained as the increasing flip poset on pipe dreams~$\pipeDreams(\omega_\nu)$ for an explicit permutation $\omega_\nu$ associated with $\nu$.
 The permutations of the form~$\omega_\nu$ can be easily characterized as follows.
@@
 The \defn{Rothe diagram} of a permutation~$\omega$ is the set $\set{(\omega(j),i)}{i<j,\ \omega(i)>\omega(j)}$ in matrix notation.
-A permutation $\omega$ is called \defn{dominant} if its Rothe diagram is the Ferrer's diagram of a partition located at the top left corner $(1,1)$.
+A permutation $\omega$ is called \defn{dominant} if its Rothe diagram is the Ferrers diagram of a partition located at the top left corner $(1,1)$.
 Equivalently, a permutation~$\omega$ is dominant if and only if it is 132-avoiding.
-For a permutation~$\omega = \omega_1 \dots \omega_n \in \fS_n$, we denote by~$0\omega$ the permutation~$0 \omega_1 \dots \omega_n$ of~$\{0, 1, \dots, n\}$, and we consider here pipe dreams with pipes indexed by~$\{0, 1, \dots, n\}$.
+For a permutation~$\omega = \omega_1 \dots \omega_n \in \fS_n$, we denote by~$0\omega$ the permutation~$0 \omega_1 \dots \omega_n$ of~${0, 1, \dots, n}$, and we consider here pipe dreams with pipes indexed by~${0, 1, \dots, n}$.
 
@@
 
-Given a pipe dream $P$, We write $i\to j$ whenever $i$ has a contact with $j$,
-when $P$ has a cycle ${\bf C}=(i_1, i_2, \ldots, i_m)$ where $i_1 \to i_2\to\cdots\to i_m\to i_1$, we can always assume that $i_1=\min\{i_1,\ldots,i_m\}$.
-To describe the location of crossing and contacts (elbows), we use the coordinate $(c,r)$ where $r$ is the row and $c$ is the column.
+Given a pipe dream $P$, we write $i\to j$ whenever $i$ has a contact with $j$.
+When $P$ has a cycle ${\bf C}=(i_1, i_2, \ldots, i_m)$ where $i_1 \to i_2\to\cdots\to i_m\to i_1$, we can always assume that $i_1=\min\{i_1,\ldots,i_m\}$.
+To describe the location of crossings and contacts (elbows), we use the coordinate $(c,r)$, where $r$ is the row and $c$ is the column.
 
 \begin{lemma}\label{lem:not_dominant}
-For a pipe dream $P$ with permutation $0\omega$ and pipes $i<j$ crossing. If $i$ has an elbow southwest of the crossing and $j$ has an elbow northeast of the crossing, then $\omega$ is not dominant.
+For a pipe dream $P$ with permutation $0\omega$ and crossing pipes $i<j$: if $i$ has an elbow southwest of the crossing and $j$ has an elbow northeast of the crossing, then $\omega$ is not dominant.
 \end{lemma}
 
-\begin{proof} Let $(c,r)$ be the position of the crossing. Since $i$ has an elbow southwest of $(c,r)$ we have $r\le i-1$.
+\begin{proof}
+Let $(c,r)$ be the position of the crossing. Since $i$ has an elbow southwest of $(c,r)$, we have $r\leq i-1$.
 Since $j$ has an elbow northeast of the crossing, there are at most $i-2$ pipes that cross north of $(c,r)$ in column $c$.
@@
 Excluding $0$, there is at least a pipe $0<h$ such that $h<i<j$ and $\omega^{-1}(h)< \omega^{-1}(j)<\omega^{-1}(i)$.
-This is a $132$ pattern in $\omega$, therefor $\omega$ is not dominant. \end{proof}
+This is a $132$ pattern in $\omega$, therefore $\omega$ is not dominant.
+\end{proof}
 
-\nantel{modify intro to reflect this and must thanks Lucas Gagnon for helpful suggestions that shorten our proof}
 \begin{theorem}
@@
 
-\begin{proof} For the forward implication, assume that $\omega$ is not dominant. 
-Let $P_0$ be the greedy pipe dream of $0\omega$. It has no crossing in row 0, and cannot be a partition starting at row 1.
+\begin{proof}
+For the forward implication, assume that $\omega$ is not dominant.
+Let $P_0$ be the greedy pipe dream of $0\omega$.
+It has no crossing in row 0, and cannot be a partition starting at row 1.
 There must be a row $r>1$ with more crossing than in row $r-1$.
@@
 Let $Q$ be the pipe dream obtained from $P_0$ by the flip of the crossing at $(c,r)$ with the contact at $(c+1,r-1)$.
-The contact of $Q$ at $(c,r)$ gives $r\contactLess{Q} k$. In row $0$ we only have contacts, we have $\omega^{-1}(k)<\omega^{-1}(r)$ and Lemma~\ref{lem:rectangle} gives  that 
-$k \contactLess{Q} r$, hence $Q$ is not acyclic.
+The contact of $Q$ at $(c,r)$ gives $r\contactLess{Q} k$.
+In row $0$ we only have contacts, we have $\omega^{-1}(k)<\omega^{-1}(r)$ and Lemma~\ref{lem:rectangle} gives that $k \contactLess{Q} r$, hence $Q$ is not acyclic.
 
-For the converse, assume we have a pipe dream $P$ that is not acyclic. The contact graph must contain a cycle ${\bf C}=(i, j_1, \ldots, j_m)$ with $i<j_k$ for all $1\le k\le m$. 
+For the converse, assume we have a pipe dream $P$ that is not acyclic.
+The contact graph must contain a cycle ${\bf C}=(i, j_1, \ldots, j_m)$ with $i<j_k$ for all $1\le k\le m$.
 The contact $i \to j_1$ is southeast of $i$ and the contact $j_m\to i$ northwest of $i$.
-Let $j_k$ be the first time where $j_{k-1}\to j_k$ is a contact southeast of $i$ and $j_k \to j_{k+1}$\footnote{with the convention that $j_{m+1}=i$} is a contact northwest of $i$.
-This implies that the pipe $j=j_k$ cross $i$ in some position $(c,r)$. Since $i<j$, the pipe $j$ is the vertical pipe of the crossing. 
-Remark that all contact $j_{k'}\to j_{k'+1}$ are southeast of $i$ for $1\le k' <k$.
+Let $j_k$ be the first time where $j_{k-1}\to j_k$ is a contact southeast of $i$ and $j_k \to j_{k+1}$ (with the convention that $j_{m+1}=i$) is a contact northwest of $i$.
+This implies that the pipe $j=j_k$ cross $i$ in some position $(c,r)$.
+Since $i<j$, the pipe $j$ is the vertical pipe of the crossing.
 
-Consider first the case $m=1$. The contact $i\to j$ implies there is an elbow  of $i$ southwest of the crossing and  $j\to i$ implies there is an elbow of $j$  northeast of the crossing. 
+Remark that all contacts $j_{k'}\to j_{k'+1}$ are southeast of $i$ for $1\le k' <k$.
+Consider first the case $m=1$.
+The contact $i\to j$ implies there is an elbow of $i$ southwest of the crossing and $j\to i$ implies there is an elbow of $j$ northeast of the crossing.
 Lemma~\ref{lem:not_dominant} implies $\omega$ is not dominant.
-Assume now that $m>1$. If $i$ has an elbow southwest of the crossing, then Lemma~\ref{lem:not_dominant} implies  $\omega$ is not dominant.
-Thus, we may as well ssume that $i$ has no elbow west of $(c,r)$, and therefor $r=i$. The contact $i\to j_1$ must be southeast of both $i$ and $j$ and the  $j_{k-1}\to j_k=j$ is northwest of $j$.
+
+Consider now the case $m>1$.
+If $i$ has an elbow southwest of the crossing, then Lemma~\ref{lem:not_dominant} implies $\omega$ is not dominant.
+Thus, we may assume that $i$ has no elbow west of $(c,r)$, and therefore $r=i$.
+The contact $i\to j_1$ must be southeast of both $i$ and $j$, and the $j_{k-1}\to j_k=j$ is northwest of $j$.
 Let $j'=j_{k'}$ for $1\le k' <k$ be the first pipe such that the $j_{k'-1}\to j'$ is southeast of $j$ and $j'\to j_{k'+1}$ is northwest of $j$, and both are southeast of $i$.
-Hence $j$ and $j'$ are crossing at some position $(c',r')$ and the pipe $j'$ remain southeast of $i$ between these two contacts.
-Remark that now all contacts $j_{k''}\to j_{k''+1}$ are southeast of both pipes  $i$ and $j$ for $1\le k'' <k' < k$.
+Hence $j$ and $j'$ are crossing at some position $(c',r')$, and the pipe $j'$ remains southeast of $i$ between these two contacts.
 
-if $j'<j$, then the contact $j'\to j_{k'+1}$ is southwest of the crossing at $(c',r')$ and  $r'\le j'-1$ and $j$ has a contact north of $(c,r)$ which is north of $(c',r')$.
-We can apply Lemma~\ref{lem:not_dominant} to
- $j'<j$ and $\omega$ is not dominant. if $j'>j$, and $j$ has no elbow southwest of $(c',r')$, then the pipe $j'$ must cross $i$ in row $i$ due west of $(c,i)$.
-We now repeat the argument above: we have the contact $i\to j_1$ must be southeast of $i$, $j$ and $j'$,
-and the contact $j_{k'-1}\to j_{k'}=j'$ is northwest of $j'$.
-Let  $j''=j_{k''}$ for $1\le k''<k' <k$ be the first pipe such that the $j_{k''-1}\to j''$ is southeast of $j'$ and $j''\to j_{k''+1}$ is northwest of $j'$, and both are southeast of $i$ and $j$. 
-Hence $j'$ and $j''$ are crossing at some position $(c'',r'')$ and the pipe $j''$ remain southeast of $i$ and $j$ between these two contacts.
+Remark that now all contacts $j_{k''}\to j_{k''+1}$ are southeast of both pipes $i$ and $j$ for $1\le k''<k'<k$.
+If $j'<j$, then the contact $j'\to j_{k'+1}$ is southwest of the crossing at $(c',r')$, and $r'\le j'-1$, and $j$ has a contact north of $(c,r)$ which is north of $(c',r')$.
+We can apply Lemma~\ref{lem:not_dominant} to $j'<j$, and $\omega$ is not dominant.
+
+If $j'>j$, and $j$ has no elbow southwest of $(c',r')$, then the pipe $j'$ must cross $i$ in row $i$ due west of $(c,i)$.
+We now repeat the argument above: we have the contact $i\to j_1$ must be southeast of $i$, $j$, and $j'$, and the contact $j_{k'-1}\to j_{k'}=j'$ is northwest of $j'$.
+Let $j''=j_{k''}$ for $1\le k''<k'<k$ be the first pipe such that the $j_{k''-1}\to j''$ is southeast of $j'$ and $j''\to j_{k''+1}$ is northwest of $j'$, and both are southeast of $i$ and $j$.
+Hence $j'$ and $j''$ are crossing at some position $(c'',r'')$, and the pipe $j''$ remains southeast of $i$ and $j$ between these two contacts.
+
 Remark that now all contacts $j_{k^{(3)}}\to j_{k^{(3)}+1}$ are southeast of both pipes  $i$, $j$ and $j'$ for $1\le k^{(3)}<k'' <k' < k$.
-
 The process above cannot continue at infinitum since $k-1$ is finite.
@@
 
-Applying our Theorem~\ref{thm:pipeDreamQuotient}, we get the following consequence.
+Applying our Theorem~\ref{thm:pipeDreamQuotient}, using the Isomorphism $[0e,0\omega_\nu]\cong [e,\omega_\nu]$, we get the following consequence.
 
 \begin{corollary}
-If the statement of Open Problem~\ref{prob:nuAcyclicProperty} holds, then the $\nu$-Tamari lattice is a lattice quotient of the interval~$[e,\omega_\nu]$.
+The $\nu$-Tamari lattice is a lattice quotient of the interval~$[e,\omega_\nu]$.
 \end{corollary}

### 2023-05-15 acyclicFacets/draft/latticePipeDreams.tex
Borowwing more from Lucas, here is a much better proof.

@@
 
-Given a pipe dream $P$, we write $i\to j$ whenever $i$ has a contact with $j$.
-When $P$ has a cycle ${\bf C}=(i_1, i_2, \ldots, i_m)$ where $i_1 \to i_2\to\cdots\to i_m\to i_1$, we can always assume that $i_1=\min\{i_1,\ldots,i_m\}$.
+Given a pipe dream $P$, we write $i\to j$ whenever $i$ has an elbow weakly northwest of $j$. Lemma~\ref{lem:rectangle} gives us that $i\to j$ implies $i\contactLess{P} j$. 
+When $P$ is not acyclic, we can find a cycle ${\bf C}=(i_1, i_2, \ldots, i_m)$ of the contact graph, where $i_1 \to i_2\to\cdots\to i_m\to i_1$. 
+We say that $\bf{C}$ is a \defn{reduced cycle} if it is not possible to remove any pipe from $\bf C$ and still have a cycle. 
+Given a reduced cycle $\bf C$, we can also assume that $i_1=\min{i_1,\ldots,i_m}$.
+
 To describe the location of crossings and contacts (elbows), we use the coordinate $(c,r)$, where $r$ is the row and $c$ is the column.
@@
 
-For the converse, assume we have a pipe dream $P$ that is not acyclic.
-The contact graph must contain a cycle ${\bf C}=(i, j_1, \ldots, j_m)$ with $i<j_k$ for all $1\le k\le m$.
-The contact $i \to j_1$ is southeast of $i$ and the contact $j_m\to i$ northwest of $i$.
-Let $j_k$ be the first time where $j_{k-1}\to j_k$ is a contact southeast of $i$ and $j_k \to j_{k+1}$ (with the convention that $j_{m+1}=i$) is a contact northwest of $i$.
-This implies that the pipe $j=j_k$ cross $i$ in some position $(c,r)$.
-Since $i<j$, the pipe $j$ is the vertical pipe of the crossing.
-
-Remark that all contacts $j_{k'}\to j_{k'+1}$ are southeast of $i$ for $1\le k' <k$.
-Consider first the case $m=1$.
-The contact $i\to j$ implies there is an elbow of $i$ southwest of the crossing and $j\to i$ implies there is an elbow of $j$ northeast of the crossing.
+For the converse, assume we have a pipe dream $P$ that is not acyclic. The contact graph must contain a reduced cycle ${\bf C}=(i, j_1, \ldots, j_m)$ with $i<j_k$ for all $1\le k\le m$. 
+If $m=1$, then $i$ and $j_1$ must cross , $i\to j_1$ implies there is an elbow of $i$ southwest of the crossing and $j_1\to i$ implies there is an elbow of $j$ northeast of the crossing.
 Lemma~\ref{lem:not_dominant} implies $\omega$ is not dominant.
-
-Consider now the case $m>1$.
-If $i$ has an elbow southwest of the crossing, then Lemma~\ref{lem:not_dominant} implies $\omega$ is not dominant.
-Thus, we may assume that $i$ has no elbow west of $(c,r)$, and therefore $r=i$.
-The contact $i\to j_1$ must be southeast of both $i$ and $j$, and the $j_{k-1}\to j_k=j$ is northwest of $j$.
-Let $j'=j_{k'}$ for $1\le k' <k$ be the first pipe such that the $j_{k'-1}\to j'$ is southeast of $j$ and $j'\to j_{k'+1}$ is northwest of $j$, and both are southeast of $i$.
-Hence $j$ and $j'$ are crossing at some position $(c',r')$, and the pipe $j'$ remains southeast of $i$ between these two contacts.
-
-Remark that now all contacts $j_{k''}\to j_{k''+1}$ are southeast of both pipes $i$ and $j$ for $1\le k''<k'<k$.
-If $j'<j$, then the contact $j'\to j_{k'+1}$ is southwest of the crossing at $(c',r')$, and $r'\le j'-1$, and $j$ has a contact north of $(c,r)$ which is north of $(c',r')$.
-We can apply Lemma~\ref{lem:not_dominant} to $j'<j$, and $\omega$ is not dominant.
-
-If $j'>j$, and $j$ has no elbow southwest of $(c',r')$, then the pipe $j'$ must cross $i$ in row $i$ due west of $(c,i)$.
-We now repeat the argument above: we have the contact $i\to j_1$ must be southeast of $i$, $j$, and $j'$, and the contact $j_{k'-1}\to j_{k'}=j'$ is northwest of $j'$.
-Let $j''=j_{k''}$ for $1\le k''<k'<k$ be the first pipe such that the $j_{k''-1}\to j''$ is southeast of $j'$ and $j''\to j_{k''+1}$ is northwest of $j'$, and both are southeast of $i$ and $j$.
-Hence $j'$ and $j''$ are crossing at some position $(c'',r'')$, and the pipe $j''$ remains southeast of $i$ and $j$ between these two contacts.
-
-Remark that now all contacts $j_{k^{(3)}}\to j_{k^{(3)}+1}$ are southeast of both pipes  $i$, $j$ and $j'$ for $1\le k^{(3)}<k'' <k' < k$.
-The process above cannot continue at infinitum since $k-1$ is finite.
-At one point we will find $j^{(\ell)}<j^{(\ell-1)}$ where Lemma~\ref{lem:not_dominant} applies and conclude that $\omega$ is not dominant
-in all cases. 
+We consider the case where $m>1$.
+For $i\to j_1$, the pipe $i$ must have an  elbows at $(a,b)$ weakly northwest of $(c_1,d_1)$ an elbow of the pipe $j_1$. 
+Similarly $j_m\to i$ must have $(a_m,b_m)$ weakly northwest $(c,d)$ elbows of the pipes $j_m$ and $i$, respectively. 
+Since the cycle $C$ is reduced, we must have that $(a_m,b_m)$ is not northeast $(c_1,d_1)$. That is $c_1<a_m$ or $d_1<b_m$.
+
+For $d_1<b_m$, we must have $a_m<c_1$ since the pipe $i$ is northwest of $(c_1,d_1)$ and southeast of $(a_m,d_m)$.
+The pipe $j_1$ cannot have an elbow southeast of $(a_m,b_m)$; otherwise $j_m\to j_1$ would contradict the fact that $\bf C$ is reduced.
+The pipes $i<j_1$ must cross in the some column $<a_m$ since $j_1$ must remain strictly west of $a_m$ in rows $>b_m$, but the pipe $i$
+must have and elbow southeast of $(a_m,b_m)$. Now, in rows $\le b_m$ the pipe $j_1$ must remain northwest of the pipe $i$. 
+It is them impossible to have an elbow in position $(c_1,d_1)$ southeast of $i$ in a row $d_1<b_1$. This is a contradiction and it exclude this case.
+
+For $c_1<a_m$, similarly to above,  we must now have $b_m<d_1$ and the pipe $j_m$ cannot have an elbow northeast of $(c_1,d_1)$.
+The pipes $i<j_m$ must cross in some column strictly between $c_1$ and $a_m$; the pipe $j_m$ must remain strictly south of $d_1$ in columns $<c_1$, but the pipe $i$
+must have an elbow northwest of $(c_1,d_m)$. Then, $j_m$ has an elbow at $(a_m,b_m)$ northwest of $i$.
+For the crossing of $i$ and $j_m$,
+the pipe $i$ has an elbow at $(a,b)$ southeast of the crossing since $a\le c_1$ and the pipe $j_m$ has an elbow at $(a_m,b_m)$ northeast of the crossing.
+ Lemma~\ref{lem:not_dominant} implies that $\omega$ is not dominant and conclude the proof.
 \end{proof}
@@
 
-We are grateful to Florent Hivert for various discussions. We also thank Martin Rubey for his comments which led us to think about Theorem~\ref{prob:nuAcyclicProperty}. 
-We are very grateful to Lucas Gagnon who shared with us an independent proof of the forward direction of Theorem~\ref{prob:nuAcyclicProperty}, this allowed us to simplify our argument.
+We are grateful to Florent Hivert for various discussions. We also thank Martin Rubey for his comments which led us to think about Theorem~\ref{prob:nuAcyclicProperty} and
+we are very grateful to Lucas Gagnon who shared with us an independent proof of the converse direction of Theorem~\ref{prob:nuAcyclicProperty}, this allowed us to simplify grately our argument.
 

### 2023-05-25 acyclicFacets/draft/latticePipeDreams.tex
minor corrections and comments/questions

@@
 
-\vspace*{.1cm}
+\vspace*{-.8cm}
 
@@
 We then present a natural commutative diagram of lattice morphisms generalizing the connection between the recoil map and the binary tree insertion map on permutations and the canopy on binary trees (\cref{subsec:canopy}).
-Finally, we show that all pipe dreams of $0\omega$ are acyclic whenever $\omega$ is dominant.
-Therefore, Theorem~\ref{thm:A} implies that the $\nu$-Tamari lattice is a quotient of the interval~$[e,\omega]$ for a well-chosen dominant permutation $\omega$ (\cref{subsec:nuTamari}).
+Finally, we show that all pipe dreams with exiting permutation $0\omega$ are acyclic whenever $\omega$ is dominant.
+Therefore, \cref{thm:A} implies that the $\nu$-Tamari lattice is a quotient of the interval~$[e,\omega]$ for a well-chosen dominant permutation $\omega$ (\cref{subsec:nuTamari}).
 
@@
 
-We close this section with a theorem that relates our results to the $\nu$-Tamari lattices introduced by L.-F.~Pr\'eville-Ratelle and X.Viennot in\cite{PrevilleRatelleViennot}.
-These posets are indexed by a lattice path $\nu$ consisting of a finite number of north (N) and east (E) steps, and coincide with the classical Tamari lattices when $\nu=(NE)^n$.
+We close this section with a theorem that relates our results to the $\nu$-Tamari lattices introduced by L.-F.~Pr\'eville-Ratelle and X.~Viennot in~\cite{PrevilleRatelleViennot}.
+These posets are indexed by a lattice path $\nu$ consisting of a finite number of north~(N) and east~(E) steps, and coincide with the classical Tamari lattices when $\nu=(NE)^n$.
 
@@
 
-From \cref{exm:Tamari1}, we see that this property holds when $\omega=n\dots21$ is the reverse permutation.
+The main example is when $\omega=n\dots21$ is the reverse permutation, see \cref{exm:Tamari1}.
 In this case, the increasing flip poset on~$\pipeDreams(0 \omega)$ is the classical Tamari lattice.
-Removing vertex $0$ from the contact graph of a pipe dream~$ P\in \pipeDreams(0 \omega)$ returns the binary tree corresponding to $P$ (with the leaves removed and the internal nodes labeled from $1$ to $n$).
+Removing vertex $0$ from the contact graph of a pipe dream~$ P\in \pipeDreams(0 \omega)$ returns the binary tree corresponding to $P$ (with the leaves removed and the internal nodes labeled in inorder from $1$ to $n$).
 The edges of the binary tree are oriented going away from the root of the tree.
@@
 
-Given a pipe dream $P$, we write $i\to j$ whenever $i$ has an elbow weakly northwest of $j$. Lemma~\ref{lem:rectangle} gives us that $i\to j$ implies $i\contactLess{P} j$. 
+Given a pipe dream $P$, we write $i\to j$ whenever $i$ has an elbow weakly northwest of $j$. \cref{lem:rectangle} gives us that $i\to j$ implies $i\contactLess{P} j$. 
 When $P$ is not acyclic, we can find a cycle ${\bf C}=(i_1, i_2, \ldots, i_m)$ of the contact graph, where $i_1 \to i_2\to\cdots\to i_m\to i_1$. 
 We say that $\bf{C}$ is a \defn{reduced cycle} if it is not possible to remove any pipe from $\bf C$ and still have a cycle. 
-Given a reduced cycle $\bf C$, we can also assume that $i_1=\min{i_1,\ldots,i_m}$.
-
-To describe the location of crossings and contacts (elbows), we use the coordinate $(c,r)$, where $r$ is the row and $c$ is the column.
-
-\begin{lemma}\label{lem:not_dominant}
-For a pipe dream $P$ with permutation $0\omega$ and crossing pipes $i<j$: if $i$ has an elbow southwest of the crossing and $j$ has an elbow northeast of the crossing, then $\omega$ is not dominant.
+Given a reduced cycle $\bf C$, we can also assume that $i_1 = \min\{i_1, \dots, i_m\}$.
+
+To describe the location of crossings and contacts (elbows), we use the coordinate $(c,r)$, where~$r$ is the row and $c$ is the column (ranging from $0$ to~$n$).
+
+\begin{lemma}
+\label{lem:notDominant}
+For a pipe dream $P \in \pipeDreams(0\omega)$ with a crossing~$x$ between two pipes~$i < j$, if $i$ has an elbow southwest of~$x$ and $j$ has an elbow northeast of~$x$, then $\omega$ is not dominant.
 \end{lemma}
@@
 \begin{proof}
-Let $(c,r)$ be the position of the crossing. Since $i$ has an elbow southwest of $(c,r)$, we have $r\leq i-1$.
-Since $j$ has an elbow northeast of the crossing, there are at most $i-2$ pipes that cross north of $(c,r)$ in column $c$.
-Hence, at least $2$ pipes $<i$ reach the Northern border before column $c$.
+Let $(c,r)$ denote the position of the crossing~$x$. Since $i$ has an elbow southwest of $x$, we have $r\leq i-1$.
+Since $j$ has an elbow northeast of~$x$, there are at most $r-1 \le i-2$ pipes that cross north of $(c,r)$ in column~$c$.
+Hence, at least $2$ pipes $<i$ reach the northern border before column~$c$.
 Excluding $0$, there is at least a pipe $0<h$ such that $h<i<j$ and $\omega^{-1}(h)< \omega^{-1}(j)<\omega^{-1}(i)$.
@@
 \label{prob:nuAcyclicProperty}
-All pipe dreams with $0 \omega$ are acyclic if and only if $\omega$ is a dominant permutation.
+All pipe dreams of $\pipeDreams(0\omega)$ are acyclic if and only if $\omega$ is a dominant permutation.
 \end{theorem}
@@
 For the forward implication, assume that $\omega$ is not dominant.
-Let $P_0$ be the greedy pipe dream of $0\omega$.
+Let $\greedyPipeDream$ be the greedy pipe dream of $0\omega$. 
+\vincent{I believe you wanted the antigreedy here?}
 It has no crossing in row 0, and cannot be a partition starting at row 1.
+\vincent{I don't like the way it is written here. I would say explicitly the connection between the crossings of the greedy pipe dream and the Rothe diagram of~$\omega$.}
 There must be a row $r>1$ with more crossing than in row $r-1$.
+\vincent{You mean really inclusionwise on columns?}
 Considering the rightmost column $c$ of $P$ with a crossing in row $r$, the pipes $r<k$ are crossing at $(c,r)$, $\omega^{-1}(k)<\omega^{-1}(r)$ and are in contact in position $(c+1,r-1)$.
-Let $Q$ be the pipe dream obtained from $P_0$ by the flip of the crossing at $(c,r)$ with the contact at $(c+1,r-1)$.
+Let $Q$ be the pipe dream obtained from $\greedyPipeDream$ by the flip of the crossing at $(c,r)$ with the contact at $(c+1,r-1)$.
 The contact of $Q$ at $(c,r)$ gives $r\contactLess{Q} k$.
-In row $0$ we only have contacts, we have $\omega^{-1}(k)<\omega^{-1}(r)$ and Lemma~\ref{lem:rectangle} gives that $k \contactLess{Q} r$, hence $Q$ is not acyclic.
-
-For the converse, assume we have a pipe dream $P$ that is not acyclic. The contact graph must contain a reduced cycle ${\bf C}=(i, j_1, \ldots, j_m)$ with $i<j_k$ for all $1\le k\le m$. 
+In row $0$ we only have contacts, we have $\omega^{-1}(k)<\omega^{-1}(r)$ and \cref{lem:rectangle} gives that $k \contactLess{Q} r$, hence $Q$ is not acyclic.
+
+For the converse, assume we have a pipe dream $P$ that is not acyclic. The contact graph must contain a reduced cycle ${\bf C}=(i, j_1, \ldots, j_m)$ with $i<j_k$ for all $k \in [m]$. 
 If $m=1$, then $i$ and $j_1$ must cross , $i\to j_1$ implies there is an elbow of $i$ southwest of the crossing and $j_1\to i$ implies there is an elbow of $j$ northeast of the crossing.
-Lemma~\ref{lem:not_dominant} implies $\omega$ is not dominant.
+\cref{lem:notDominant} implies $\omega$ is not dominant.
 We consider the case where $m>1$.
-For $i\to j_1$, the pipe $i$ must have an  elbows at $(a,b)$ weakly northwest of $(c_1,d_1)$ an elbow of the pipe $j_1$. 
-Similarly $j_m\to i$ must have $(a_m,b_m)$ weakly northwest $(c,d)$ elbows of the pipes $j_m$ and $i$, respectively. 
-Since the cycle $C$ is reduced, we must have that $(a_m,b_m)$ is not northeast $(c_1,d_1)$. That is $c_1<a_m$ or $d_1<b_m$.
-
-For $d_1<b_m$, we must have $a_m<c_1$ since the pipe $i$ is northwest of $(c_1,d_1)$ and southeast of $(a_m,d_m)$.
-The pipe $j_1$ cannot have an elbow southeast of $(a_m,b_m)$; otherwise $j_m\to j_1$ would contradict the fact that $\bf C$ is reduced.
-The pipes $i<j_1$ must cross in the some column $<a_m$ since $j_1$ must remain strictly west of $a_m$ in rows $>b_m$, but the pipe $i$
-must have and elbow southeast of $(a_m,b_m)$. Now, in rows $\le b_m$ the pipe $j_1$ must remain northwest of the pipe $i$. 
-It is them impossible to have an elbow in position $(c_1,d_1)$ southeast of $i$ in a row $d_1<b_1$. This is a contradiction and it exclude this case.
+For $i\to j_1$, there is an elbow of~$i$ at $(a,b)$ weakly northwest of an elbow of~$j_1$ at $(c_1,d_1)$ an elbow.
+Similarly, for $j_m\to i$, there is an elbow of~$j_m$ at $(a_m,b_m)$ weakly northwest of an elbow of~$i$ at~$(c,d)$.
+Since the cycle $C$ is reduced, we must have that $(a_m,b_m)$ is not northwest $(c_1,d_1)$. That is $c_1<a_m$ or $d_1<b_m$.
+
+For $d_1<b_m$, we must have $a_m<c_1$ since the pipe $i$ passes northwest of $(c_1,d_1)$ and southeast of $(a_m,d_m)$.
+The pipe $j_1$ cannot have an elbow southeast of $(a_m,b_m)$, as otherwise $j_m\to j_1$ would contradict the fact that $\bf C$ is reduced.
+The pipes $i<j_1$ must cross in some column $<a_m$ since $j_1$ must remain strictly west of $a_m$ in rows $>b_m$, but the pipe $i$ must have and elbow southeast of $(a_m,b_m)$.
+Now, in rows $\le b_m$ the pipe $j_1$ must remain northwest of the pipe $i$. 
+It is them impossible to have an elbow in position $(c_1,d_1)$ southeast of $i$ in a row $d_1<b_1$. This is a contradiction and it excludes this case.
 
 For $c_1<a_m$, similarly to above,  we must now have $b_m<d_1$ and the pipe $j_m$ cannot have an elbow northeast of $(c_1,d_1)$.
-The pipes $i<j_m$ must cross in some column strictly between $c_1$ and $a_m$; the pipe $j_m$ must remain strictly south of $d_1$ in columns $<c_1$, but the pipe $i$
-must have an elbow northwest of $(c_1,d_m)$. Then, $j_m$ has an elbow at $(a_m,b_m)$ northwest of $i$.
+The pipes $i<j_m$ must cross in some column strictly between $c_1$ and $a_m$, since the pipe $j_m$ must remain strictly south of $d_1$ in columns $<c_1$, but the pipe $i$ must have an elbow northwest of $(c_1,d_1)$ and the pipe $j_m$ has an elbow at $(a_m,b_m)$ northwest of $i$.
 For the crossing of $i$ and $j_m$,
 the pipe $i$ has an elbow at $(a,b)$ southeast of the crossing since $a\le c_1$ and the pipe $j_m$ has an elbow at $(a_m,b_m)$ northeast of the crossing.
- Lemma~\ref{lem:not_dominant} implies that $\omega$ is not dominant and conclude the proof.
-\end{proof}
-
-Applying our Theorem~\ref{thm:pipeDreamQuotient}, using the Isomorphism $[0e,0\omega_\nu]\cong [e,\omega_\nu]$, we get the following consequence.
+\cref{lem:notDominant} implies that $\omega$ is not dominant and conclude the proof.
+\end{proof}
+
+Applying our \cref{thm:pipeDreamQuotient}, using the Isomorphism $[0e,0\omega_\nu]\cong [e,\omega_\nu]$, we get the following consequence.
 
@@
 \end{corollary}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2023-05-25 acyclicFacets/draft/latticePipeDreams.tex
minor corrections and comments/questions
minor corrections

@@
 Given a reduced cycle $\bf C$, we can also assume that $i_1 = \min\{i_1, \dots, i_m\}$.
+\vincent{Maybe I would put this cycle story inside the proof.}
 
@@
 
-For the converse, assume we have a pipe dream $P$ that is not acyclic. The contact graph must contain a reduced cycle ${\bf C}=(i, j_1, \ldots, j_m)$ with $i<j_k$ for all $k \in [m]$. 
+For the backward direction, assume we have a pipe dream $P$ that is not acyclic. The contact graph must contain a reduced cycle ${\bf C}=(i, j_1, \ldots, j_m)$ with $i<j_k$ for all $k \in [m]$. 
 If $m=1$, then $i$ and $j_1$ must cross , $i\to j_1$ implies there is an elbow of $i$ southwest of the crossing and $j_1\to i$ implies there is an elbow of $j$ northeast of the crossing.
@@
 
-We are grateful to Florent Hivert for various discussions. We also thank Martin Rubey for his comments which led us to think about Theorem~\ref{prob:nuAcyclicProperty} and
-we are very grateful to Lucas Gagnon who shared with us an independent proof of the converse direction of Theorem~\ref{prob:nuAcyclicProperty}, this allowed us to simplify grately our argument.
+We are grateful to Florent Hivert for various discussions. We also thank Martin Rubey for his comments which led us to think about~\cref{prob:nuAcyclicProperty}.
+Finally, we are grateful to Lucas Gagnon who shared with us an independent proof of the backward direction of \cref{prob:nuAcyclicProperty}, allowing us to greatly simplify our argument.
 

### 2023-06-10 acyclicFacets/draft/latticePipeDreams.tex
typo
Adding a drawn picture in the proof (request of Cesar).

@@
 
-For $c_1<a_m$, similarly to above,  we must now have $b_m<d_1$ and the pipe $j_m$ cannot have an elbow northeast of $(c_1,d_1)$.
+\centerline{\includegraphics[scale=.3]{TwoCasesofproof.pdf}}
+
+For $c_1<a_m$, similarly to above,  we must now have $b_m<d_1$ and the pipe $j_m$ cannot have an elbow northwest of $(c_1,d_1)$.
 The pipes $i<j_m$ must cross in some column strictly between $c_1$ and $a_m$, since the pipe $j_m$ must remain strictly south of $d_1$ in columns $<c_1$, but the pipe $i$ must have an elbow northwest of $(c_1,d_1)$ and the pipe $j_m$ has an elbow at $(a_m,b_m)$ northwest of $i$.
@@
 
-Applying our \cref{thm:pipeDreamQuotient}, using the Isomorphism $[0e,0\omega_\nu]\cong [e,\omega_\nu]$, we get the following consequence.
+Applying our \cref{thm:pipeDreamQuotient}, using the isomorphism $[0e,0\omega_\nu]\cong [e,\omega_\nu]$, we get the following consequence.
 

### 2023-06-14 acyclicFacets/draft/latticePipeDreams.tex
Adding my webpage

--- 2023-05-25 acyclicFacets/draft/latticePipeDreams.tex
@@
 \email{noemie.cartier@lri.fr}
+\urladdr{https://www.lisn.upsaclay.fr/~cartier/}
 
@@
 
-\vspace*{-.8cm}
+\vspace*{.1cm}
 
@@
 We then present a natural commutative diagram of lattice morphisms generalizing the connection between the recoil map and the binary tree insertion map on permutations and the canopy on binary trees (\cref{subsec:canopy}).
-Finally, we show that all pipe dreams with exiting permutation $0\omega$ are acyclic whenever $\omega$ is dominant.
-Therefore, \cref{thm:A} implies that the $\nu$-Tamari lattice is a quotient of the interval~$[e,\omega]$ for a well-chosen dominant permutation $\omega$ (\cref{subsec:nuTamari}).
+Finally, we show that all pipe dreams of $0\omega$ are acyclic whenever $\omega$ is dominant.
+Therefore, Theorem~\ref{thm:A} implies that the $\nu$-Tamari lattice is a quotient of the interval~$[e,\omega]$ for a well-chosen dominant permutation $\omega$ (\cref{subsec:nuTamari}).
 
@@
 
-We close this section with a theorem that relates our results to the $\nu$-Tamari lattices introduced by L.-F.~Pr\'eville-Ratelle and X.~Viennot in~\cite{PrevilleRatelleViennot}.
-These posets are indexed by a lattice path $\nu$ consisting of a finite number of north~(N) and east~(E) steps, and coincide with the classical Tamari lattices when $\nu=(NE)^n$.
+We close this section with a theorem that relates our results to the $\nu$-Tamari lattices introduced by L.-F.~Pr\'eville-Ratelle and X.Viennot in\cite{PrevilleRatelleViennot}.
+These posets are indexed by a lattice path $\nu$ consisting of a finite number of north (N) and east (E) steps, and coincide with the classical Tamari lattices when $\nu=(NE)^n$.
 
@@
 
-The main example is when $\omega=n\dots21$ is the reverse permutation, see \cref{exm:Tamari1}.
+From \cref{exm:Tamari1}, we see that this property holds when $\omega=n\dots21$ is the reverse permutation.
 In this case, the increasing flip poset on~$\pipeDreams(0 \omega)$ is the classical Tamari lattice.
-Removing vertex $0$ from the contact graph of a pipe dream~$ P\in \pipeDreams(0 \omega)$ returns the binary tree corresponding to $P$ (with the leaves removed and the internal nodes labeled in inorder from $1$ to $n$).
+Removing vertex $0$ from the contact graph of a pipe dream~$ P\in \pipeDreams(0 \omega)$ returns the binary tree corresponding to $P$ (with the leaves removed and the internal nodes labeled from $1$ to $n$).
 The edges of the binary tree are oriented going away from the root of the tree.
@@
 
-Given a pipe dream $P$, we write $i\to j$ whenever $i$ has an elbow weakly northwest of $j$. \cref{lem:rectangle} gives us that $i\to j$ implies $i\contactLess{P} j$. 
+Given a pipe dream $P$, we write $i\to j$ whenever $i$ has an elbow weakly northwest of $j$. Lemma~\ref{lem:rectangle} gives us that $i\to j$ implies $i\contactLess{P} j$. 
 When $P$ is not acyclic, we can find a cycle ${\bf C}=(i_1, i_2, \ldots, i_m)$ of the contact graph, where $i_1 \to i_2\to\cdots\to i_m\to i_1$. 
 We say that $\bf{C}$ is a \defn{reduced cycle} if it is not possible to remove any pipe from $\bf C$ and still have a cycle. 
-Given a reduced cycle $\bf C$, we can also assume that $i_1 = \min\{i_1, \dots, i_m\}$.
-
-To describe the location of crossings and contacts (elbows), we use the coordinate $(c,r)$, where~$r$ is the row and $c$ is the column (ranging from $0$ to~$n$).
-
-\begin{lemma}
-\label{lem:notDominant}
-For a pipe dream $P \in \pipeDreams(0\omega)$ with a crossing~$x$ between two pipes~$i < j$, if $i$ has an elbow southwest of~$x$ and $j$ has an elbow northeast of~$x$, then $\omega$ is not dominant.
+Given a reduced cycle $\bf C$, we can also assume that $i_1=\min{i_1,\ldots,i_m}$.
+
+To describe the location of crossings and contacts (elbows), we use the coordinate $(c,r)$, where $r$ is the row and $c$ is the column.
+
+\begin{lemma}\label{lem:not_dominant}
+For a pipe dream $P$ with permutation $0\omega$ and crossing pipes $i<j$: if $i$ has an elbow southwest of the crossing and $j$ has an elbow northeast of the crossing, then $\omega$ is not dominant.
 \end{lemma}
@@
 \begin{proof}
-Let $(c,r)$ denote the position of the crossing~$x$. Since $i$ has an elbow southwest of $x$, we have $r\leq i-1$.
-Since $j$ has an elbow northeast of~$x$, there are at most $r-1 \le i-2$ pipes that cross north of $(c,r)$ in column~$c$.
-Hence, at least $2$ pipes $<i$ reach the northern border before column~$c$.
+Let $(c,r)$ be the position of the crossing. Since $i$ has an elbow southwest of $(c,r)$, we have $r\leq i-1$.
+Since $j$ has an elbow northeast of the crossing, there are at most $i-2$ pipes that cross north of $(c,r)$ in column $c$.
+Hence, at least $2$ pipes $<i$ reach the Northern border before column $c$.
 Excluding $0$, there is at least a pipe $0<h$ such that $h<i<j$ and $\omega^{-1}(h)< \omega^{-1}(j)<\omega^{-1}(i)$.
@@
 \label{prob:nuAcyclicProperty}
-All pipe dreams of $\pipeDreams(0\omega)$ are acyclic if and only if $\omega$ is a dominant permutation.
+All pipe dreams with $0 \omega$ are acyclic if and only if $\omega$ is a dominant permutation.
 \end{theorem}
@@
 For the forward implication, assume that $\omega$ is not dominant.
-Let $\greedyPipeDream$ be the greedy pipe dream of $0\omega$. 
-\vincent{I believe you wanted the antigreedy here?}
+Let $P_0$ be the greedy pipe dream of $0\omega$.
 It has no crossing in row 0, and cannot be a partition starting at row 1.
-\vincent{I don't like the way it is written here. I would say explicitly the connection between the crossings of the greedy pipe dream and the Rothe diagram of~$\omega$.}
 There must be a row $r>1$ with more crossing than in row $r-1$.
-\vincent{You mean really inclusionwise on columns?}
 Considering the rightmost column $c$ of $P$ with a crossing in row $r$, the pipes $r<k$ are crossing at $(c,r)$, $\omega^{-1}(k)<\omega^{-1}(r)$ and are in contact in position $(c+1,r-1)$.
-Let $Q$ be the pipe dream obtained from $\greedyPipeDream$ by the flip of the crossing at $(c,r)$ with the contact at $(c+1,r-1)$.
+Let $Q$ be the pipe dream obtained from $P_0$ by the flip of the crossing at $(c,r)$ with the contact at $(c+1,r-1)$.
 The contact of $Q$ at $(c,r)$ gives $r\contactLess{Q} k$.
-In row $0$ we only have contacts, we have $\omega^{-1}(k)<\omega^{-1}(r)$ and \cref{lem:rectangle} gives that $k \contactLess{Q} r$, hence $Q$ is not acyclic.
-
-For the converse, assume we have a pipe dream $P$ that is not acyclic. The contact graph must contain a reduced cycle ${\bf C}=(i, j_1, \ldots, j_m)$ with $i<j_k$ for all $k \in [m]$. 
+In row $0$ we only have contacts, we have $\omega^{-1}(k)<\omega^{-1}(r)$ and Lemma~\ref{lem:rectangle} gives that $k \contactLess{Q} r$, hence $Q$ is not acyclic.
+
+For the converse, assume we have a pipe dream $P$ that is not acyclic. The contact graph must contain a reduced cycle ${\bf C}=(i, j_1, \ldots, j_m)$ with $i<j_k$ for all $1\le k\le m$. 
 If $m=1$, then $i$ and $j_1$ must cross , $i\to j_1$ implies there is an elbow of $i$ southwest of the crossing and $j_1\to i$ implies there is an elbow of $j$ northeast of the crossing.
-\cref{lem:notDominant} implies $\omega$ is not dominant.
+Lemma~\ref{lem:not_dominant} implies $\omega$ is not dominant.
 We consider the case where $m>1$.
-For $i\to j_1$, there is an elbow of~$i$ at $(a,b)$ weakly northwest of an elbow of~$j_1$ at $(c_1,d_1)$ an elbow.
-Similarly, for $j_m\to i$, there is an elbow of~$j_m$ at $(a_m,b_m)$ weakly northwest of an elbow of~$i$ at~$(c,d)$.
-Since the cycle $C$ is reduced, we must have that $(a_m,b_m)$ is not northwest $(c_1,d_1)$. That is $c_1<a_m$ or $d_1<b_m$.
-
-For $d_1<b_m$, we must have $a_m<c_1$ since the pipe $i$ passes northwest of $(c_1,d_1)$ and southeast of $(a_m,d_m)$.
-The pipe $j_1$ cannot have an elbow southeast of $(a_m,b_m)$, as otherwise $j_m\to j_1$ would contradict the fact that $\bf C$ is reduced.
-The pipes $i<j_1$ must cross in some column $<a_m$ since $j_1$ must remain strictly west of $a_m$ in rows $>b_m$, but the pipe $i$ must have and elbow southeast of $(a_m,b_m)$.
-Now, in rows $\le b_m$ the pipe $j_1$ must remain northwest of the pipe $i$. 
-It is them impossible to have an elbow in position $(c_1,d_1)$ southeast of $i$ in a row $d_1<b_1$. This is a contradiction and it excludes this case.
+For $i\to j_1$, the pipe $i$ must have an  elbows at $(a,b)$ weakly northwest of $(c_1,d_1)$ an elbow of the pipe $j_1$. 
+Similarly $j_m\to i$ must have $(a_m,b_m)$ weakly northwest $(c,d)$ elbows of the pipes $j_m$ and $i$, respectively. 
+Since the cycle $C$ is reduced, we must have that $(a_m,b_m)$ is not northeast $(c_1,d_1)$. That is $c_1<a_m$ or $d_1<b_m$.
+
+For $d_1<b_m$, we must have $a_m<c_1$ since the pipe $i$ is northwest of $(c_1,d_1)$ and southeast of $(a_m,d_m)$.
+The pipe $j_1$ cannot have an elbow southeast of $(a_m,b_m)$; otherwise $j_m\to j_1$ would contradict the fact that $\bf C$ is reduced.
+The pipes $i<j_1$ must cross in the some column $<a_m$ since $j_1$ must remain strictly west of $a_m$ in rows $>b_m$, but the pipe $i$
+must have and elbow southeast of $(a_m,b_m)$. Now, in rows $\le b_m$ the pipe $j_1$ must remain northwest of the pipe $i$. 
+It is them impossible to have an elbow in position $(c_1,d_1)$ southeast of $i$ in a row $d_1<b_1$. This is a contradiction and it exclude this case.
 
 For $c_1<a_m$, similarly to above,  we must now have $b_m<d_1$ and the pipe $j_m$ cannot have an elbow northeast of $(c_1,d_1)$.
-The pipes $i<j_m$ must cross in some column strictly between $c_1$ and $a_m$, since the pipe $j_m$ must remain strictly south of $d_1$ in columns $<c_1$, but the pipe $i$ must have an elbow northwest of $(c_1,d_1)$ and the pipe $j_m$ has an elbow at $(a_m,b_m)$ northwest of $i$.
+The pipes $i<j_m$ must cross in some column strictly between $c_1$ and $a_m$; the pipe $j_m$ must remain strictly south of $d_1$ in columns $<c_1$, but the pipe $i$
+must have an elbow northwest of $(c_1,d_m)$. Then, $j_m$ has an elbow at $(a_m,b_m)$ northwest of $i$.
 For the crossing of $i$ and $j_m$,
 the pipe $i$ has an elbow at $(a,b)$ southeast of the crossing since $a\le c_1$ and the pipe $j_m$ has an elbow at $(a_m,b_m)$ northeast of the crossing.
-\cref{lem:notDominant} implies that $\omega$ is not dominant and conclude the proof.
-\end{proof}
-
-Applying our \cref{thm:pipeDreamQuotient}, using the Isomorphism $[0e,0\omega_\nu]\cong [e,\omega_\nu]$, we get the following consequence.
+ Lemma~\ref{lem:not_dominant} implies that $\omega$ is not dominant and conclude the proof.
+\end{proof}
+
+Applying our Theorem~\ref{thm:pipeDreamQuotient}, using the Isomorphism $[0e,0\omega_\nu]\cong [e,\omega_\nu]$, we get the following consequence.
 
@@
 \end{corollary}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2023-07-07 acyclicFacets/draft/latticePipeDreams.tex
small edit relating v-Tamari to increasing flip poset

--- 2023-06-10 acyclicFacets/draft/latticePipeDreams.tex
@@
 
-In~\cite{CeballosPadrolSarmiento}, it was shown that the $\nu$-Tamari lattice can be obtained as the increasing flip poset on pipe dreams~$\pipeDreams(\omega_\nu)$ for an explicit permutation $\omega_\nu$ associated with $\nu$.
+In~\cite{CeballosPadrolSarmiento}, it was shown that the $\nu$-Tamari lattice can be obtained as the increasing flip poset on pipe dreams~$\pipeDreams(0\omega_\nu)$ for an explicit permutation $\omega_\nu$ associated with $\nu$.
 The permutations of the form~$\omega_\nu$ can be easily characterized as follows.
@@
 For a permutation~$\omega = \omega_1 \dots \omega_n \in \fS_n$, we denote by~$0\omega$ the permutation~$0 \omega_1 \dots \omega_n$ of~${0, 1, \dots, n}$, and we consider here pipe dreams with pipes indexed by~${0, 1, \dots, n}$.
+The $\nu$-Tamari lattice is the increasing flip poset on pipe dreams~$\pipeDreams(0\omega_\nu)$ for some dominant permutation $\omega_\nu$ determined by $\nu$, see~\cite{CeballosPadrolSarmiento}.
 

### 2023-09-25 acyclicFacets/draft/latticePipeDreams.tex
new proposition proof

@@
 They are grouped according to their exiting permutation, given by the order in which the pipes appear along the horizontal axis.
-The linear extensions of a pipe dream are the permutations of its pipes such that for each contact the northwest pipe appears before the southeast pipe in the permutation.
+The linear extensions of a pipe dream are the permutations of its pipes such that for each contact, the northwest pipe appears before the southeast pipe in the permutation.
 The pipe dreams with at least one linear extension are called acyclic and naturally appear in the study of brick polytopes~\cite{PilaudSantos-brickPolytope}.
@@
 
-The \defn{Rothe diagram} of a permutation~$\omega$ is the set $\set{(\omega(j),i)}{i<j,\ \omega(i)>\omega(j)}$ in matrix notation.
+The \defn{Rothe diagram} of a permutation~$\omega$ is the set $\set{(\omega(j),i)}{i<j \text{ and } \omega(i)>\omega(j)}$ in matrix notation.
 A permutation $\omega$ is called \defn{dominant} if its Rothe diagram is the Ferrers diagram of a partition located at the top left corner $(1,1)$.
 Equivalently, a permutation~$\omega$ is dominant if and only if it is 132-avoiding.
-For a permutation~$\omega = \omega_1 \dots \omega_n \in \fS_n$, we denote by~$0\omega$ the permutation~$0 \omega_1 \dots \omega_n$ of~${0, 1, \dots, n}$, and we consider here pipe dreams with pipes indexed by~${0, 1, \dots, n}$.
+For a permutation~$\omega = \omega_1 \dots \omega_n \in \fS_n$, we denote by~$0\omega$ the permutation~$0 \omega_1 \dots \omega_n$ of~$\{0, 1, \dots, n\}$, and we consider here pipe dreams with pipes indexed by~${0, 1, \dots, n}$.
 The $\nu$-Tamari lattice is the increasing flip poset on pipe dreams~$\pipeDreams(0\omega_\nu)$ for some dominant permutation $\omega_\nu$ determined by $\nu$, see~\cite{CeballosPadrolSarmiento}.
 
-The main example is when $\omega=n\dots21$ is the reverse permutation, see \cref{exm:Tamari1}.
+The main example is when $\omega \eqdef n \dots 2 1$ is the reverse permutation, see \cref{exm:Tamari1,fig:bijection}.
 In this case, the increasing flip poset on~$\pipeDreams(0 \omega)$ is the classical Tamari lattice.
-Removing vertex $0$ from the contact graph of a pipe dream~$ P\in \pipeDreams(0 \omega)$ returns the binary tree corresponding to $P$ (with the leaves removed and the internal nodes labeled in inorder from $1$ to $n$).
+Removing vertex~$0$ from the contact graph of a pipe dream~$ P\in \pipeDreams(0 \omega)$ returns the binary tree corresponding to $P$ (with the leaves removed and the internal nodes labeled in inorder from $1$ to $n$).
 The edges of the binary tree are oriented going away from the root of the tree.
-See \cref{fig:bijection}.
-
-Given a pipe dream $P$, we write $i\to j$ whenever $i$ has an elbow weakly northwest of $j$. \cref{lem:rectangle} gives us that $i\to j$ implies $i\contactLess{P} j$. 
-When $P$ is not acyclic, we can find a cycle ${\bf C}=(i_1, i_2, \ldots, i_m)$ of the contact graph, where $i_1 \to i_2\to\cdots\to i_m\to i_1$. 
-We say that $\bf{C}$ is a \defn{reduced cycle} if it is not possible to remove any pipe from $\bf C$ and still have a cycle. 
-Given a reduced cycle $\bf C$, we can also assume that $i_1 = \min\{i_1, \dots, i_m\}$.
-\vincent{Maybe I would put this cycle story inside the proof.}
-
-To describe the location of crossings and contacts (elbows), we use the coordinate $(c,r)$, where~$r$ is the row and $c$ is the column (ranging from $0$ to~$n$).
+In particular, all pipe dreams of~$\pipeDreams(0 \omega)$ are acyclic.
+This extends to all dominant permutations as follows.
+
+\begin{theorem}
+\label{prob:nuAcyclicProperty}
+All pipe dreams of $\pipeDreams(0\omega)$ are acyclic if and only if $\omega$ is a dominant permutation.
+\end{theorem}
+
+To prove this result, we will need the following observation.
+Note that throughout the proof, the pipes, rows, and column are all indexed by indices ranging from $0$ to~$n$.
 
@@
 \begin{proof}
-Let $(c,r)$ denote the position of the crossing~$x$. Since $i$ has an elbow southwest of $x$, we have $r\leq i-1$.
+Let~$r$ be the row and $c$ be the column of the crossing~$x$ (careful that all indices range from~$0$ to~$n$).
+Since $i$ has an elbow southwest of $x$, we have $r \le i-1$.
 Since $j$ has an elbow northeast of~$x$, there are at most $r-1 \le i-2$ pipes that cross north of $(c,r)$ in column~$c$.
-Hence, at least $2$ pipes $<i$ reach the northern border before column~$c$.
-Excluding $0$, there is at least a pipe $0<h$ such that $h<i<j$ and $\omega^{-1}(h)< \omega^{-1}(j)<\omega^{-1}(i)$.
-This is a $132$ pattern in $\omega$, therefore $\omega$ is not dominant.
-\end{proof}
-
-\begin{theorem}
-\label{prob:nuAcyclicProperty}
-All pipe dreams of $\pipeDreams(0\omega)$ are acyclic if and only if $\omega$ is a dominant permutation.
-\end{theorem}
-
-\begin{proof}
-For the forward implication, assume that $\omega$ is not dominant.
-Let $\greedyPipeDream$ be the greedy pipe dream of $0\omega$. 
-\vincent{I believe you wanted the antigreedy here?}
-It has no crossing in row 0, and cannot be a partition starting at row 1.
-\vincent{I don't like the way it is written here. I would say explicitly the connection between the crossings of the greedy pipe dream and the Rothe diagram of~$\omega$.}
-There must be a row $r>1$ with more crossing than in row $r-1$.
-\vincent{You mean really inclusionwise on columns?}
-Considering the rightmost column $c$ of $P$ with a crossing in row $r$, the pipes $r<k$ are crossing at $(c,r)$, $\omega^{-1}(k)<\omega^{-1}(r)$ and are in contact in position $(c+1,r-1)$.
-Let $Q$ be the pipe dream obtained from $\greedyPipeDream$ by the flip of the crossing at $(c,r)$ with the contact at $(c+1,r-1)$.
-The contact of $Q$ at $(c,r)$ gives $r\contactLess{Q} k$.
-In row $0$ we only have contacts, we have $\omega^{-1}(k)<\omega^{-1}(r)$ and \cref{lem:rectangle} gives that $k \contactLess{Q} r$, hence $Q$ is not acyclic.
-
-For the backward direction, assume we have a pipe dream $P$ that is not acyclic. The contact graph must contain a reduced cycle ${\bf C}=(i, j_1, \ldots, j_m)$ with $i<j_k$ for all $k \in [m]$. 
-If $m=1$, then $i$ and $j_1$ must cross , $i\to j_1$ implies there is an elbow of $i$ southwest of the crossing and $j_1\to i$ implies there is an elbow of $j$ northeast of the crossing.
-\cref{lem:notDominant} implies $\omega$ is not dominant.
-We consider the case where $m>1$.
-For $i\to j_1$, there is an elbow of~$i$ at $(a,b)$ weakly northwest of an elbow of~$j_1$ at $(c_1,d_1)$ an elbow.
-Similarly, for $j_m\to i$, there is an elbow of~$j_m$ at $(a_m,b_m)$ weakly northwest of an elbow of~$i$ at~$(c,d)$.
-Since the cycle $C$ is reduced, we must have that $(a_m,b_m)$ is not northwest $(c_1,d_1)$. That is $c_1<a_m$ or $d_1<b_m$.
-
-For $d_1<b_m$, we must have $a_m<c_1$ since the pipe $i$ passes northwest of $(c_1,d_1)$ and southeast of $(a_m,d_m)$.
-The pipe $j_1$ cannot have an elbow southeast of $(a_m,b_m)$, as otherwise $j_m\to j_1$ would contradict the fact that $\bf C$ is reduced.
-The pipes $i<j_1$ must cross in some column $<a_m$ since $j_1$ must remain strictly west of $a_m$ in rows $>b_m$, but the pipe $i$ must have and elbow southeast of $(a_m,b_m)$.
-Now, in rows $\le b_m$ the pipe $j_1$ must remain northwest of the pipe $i$. 
-It is them impossible to have an elbow in position $(c_1,d_1)$ southeast of $i$ in a row $d_1<b_1$. This is a contradiction and it excludes this case.
-
-\centerline{\includegraphics[scale=.3]{TwoCasesofproof.pdf}}
-
-For $c_1<a_m$, similarly to above,  we must now have $b_m<d_1$ and the pipe $j_m$ cannot have an elbow northwest of $(c_1,d_1)$.
-The pipes $i<j_m$ must cross in some column strictly between $c_1$ and $a_m$, since the pipe $j_m$ must remain strictly south of $d_1$ in columns $<c_1$, but the pipe $i$ must have an elbow northwest of $(c_1,d_1)$ and the pipe $j_m$ has an elbow at $(a_m,b_m)$ northwest of $i$.
-For the crossing of $i$ and $j_m$,
-the pipe $i$ has an elbow at $(a,b)$ southeast of the crossing since $a\le c_1$ and the pipe $j_m$ has an elbow at $(a_m,b_m)$ northeast of the crossing.
-\cref{lem:notDominant} implies that $\omega$ is not dominant and conclude the proof.
+Hence, at least two pipes smaller than~$i$ reach the northern border before column~$c$.
+Excluding the pipe~$0$, there is at least one pipe $h > 0$ such that $h < i < j$ and $\omega^{-1}(h) < \omega^{-1}(j) < \omega^{-1}(i)$.
+This is a $132$ pattern in the permutation~$\omega$, therefore $\omega$ is not dominant.
+\end{proof}
+
+\begin{proof}[Proof of \cref{prob:nuAcyclicProperty}]
+For the forward implication, assume that $\omega$ is not dominant, and consider~${i,j,k \in [n]}$ such that~$i < j < k$ while~$\omega^{-1}(i) < \omega^{-1}(k) < \omega^{-1}(j)$, and such that~$k$ is maximal for this property.
+Consider any pipe dream~$P \in \pipeDreams(0\omega)$ obtained by capping any pipe dream of~$\pipeDreams(\omega)$ by a top row of contacts.
+Because of this top row of contacts, $\omega^{-1}(u) < \omega^{-1}(v)$ implies~$u \contactLess{P} v$.
+We now consider the eastmost point~$x$ of pipe~$k$ along row~$i$, and let~$\ell$ denote the other pipe at this point.
+We distinguish two cases:
+\begin{enumerate}[(i)]
+\item Assume first that~$k$ and~$\ell$ cross at~$x$.
+Since $\omega^{-1}(k) < \omega^{-1}(\ell)$, we have~$k \contactLess{P} \ell$.
+Moreover, since~$\ell\ne i$, the pipe~$\ell$ must have an elbow west of~$x$ along row~$i$, which implies that~$\ell \contactLess{P} k$.
+Hence, we have both~$k \contactLess{P} \ell$ and~$\ell \contactLess{P} k$, so that~$P$ is cyclic.
+\item Assume now that~$k$ and~$\ell$ touch at~$x$, so that~$k \contactLess{P} \ell$.
+If~$\ell < k$, then~$k$ and~$\ell$ must cross before~$x$, and flipping~$x$ in~$P$ yields a cyclic facet.
+If~$\omega^{-1}(\ell) < \omega^{-1}(k)$, then~$\ell \contactLess{P} k$, so that~$P$ is again cyclic.
+Hence, we can assume that~$k < \ell$ and~$\omega^{-1}(k) < \omega^{-1}(\ell)$.
+By maximality of~$k$, we obtain that~$j$ and~$\ell$ do not cross, and thus that~$j$ passes northwest of~$x$.
+We conclude that~$j \contactLess{P} k$.
+Since~$\omega^{-1}(k) < \omega^{-1}(j)$, we also have~$k \contactLess{P} j$, so that~$P$ is cyclic.
+\end{enumerate}
+
+For the backward implication, we introduce a local notation.
+We write~$i \to j$ if there is an elbow of pipe~$i$ weakly northwest of an elbow of pipe~$j$.
+Note that~$i \to j$ implies~$i \contactLess{P} j$ by \cref{lem:rectangle}.
+The reverse direction does not necessarily holds, but clearly holds for cover relations of~$\contactLess{P}$ (as in this case, there is an elbow of~$i$ in contact with an elbow of~$j$).
+Assume now that there is a cyclic pipe dream~$P \in \pipeDreams(\omega)$.
+We can thus find a cycle~$\b{C}=(i_1, \dots, i_m)$ with~$i_1 \to \dots \to i_m \to i_1$.
+We can moreover assume that~$\b{C}$ is reduced in the sense that no subsequence of~$\b{C}$ forms a cycle for~$\to$.
+
+If~$m = 2$, then the pipes~$i_1$ and~$i_2$ must cross at some point~$x$, and $i_1 \to i_2$ implies that $i_1$ has an elbow southeast of~$x$, while $i_2 \to i_1$ implies that $i_2$ has an elbow northwest of~$x$, so that $\omega$ is not dominant by \cref{lem:notDominant}.
+
+Assume now that~$m \ge 3$.
+Assume moreover that~$i_1 < i_\ell$ for all~$\ell \in [m]$ (if not, rotate the indices).
+Since~$i_m \to i_1$, there is an elbow~$e$ of~$i_m$ weakly northwest of an elbow~$e'$ of~$i_1$.
+Since~$i_1 \to i_2$, there is an elbow~$f$ of~$i_1$ weakly northwest of an elbow~$f'$ of~$i_2$.
+We now distinguish four cases:
+\begin{itemize}
+\item If~$e$ is weakly northwest of~$f$, thus of~$f'$, then~$i_m \to i_2$, contradicting the minimality of~$\b{C}$.
+\item If~$e$ is northeast of~$f$, since~$i_1 < i_m$, the pipe~$i_m$ starts southwest of~$f$ and ends northeast of~$f$, so that it has an elbow either southeast of~$f$ so that~$i_1 \to i_m$, or northwest of~$f$ thus of~$f'$ so that~$i_m \to i_2$.
+In both cases, this contradicts the minimality of~$\b{C}$.
+\item If~$e$ is southwest of~$f$, as~$i_1$ passes trough~$e'$ and~$f$, and $i_2$ starts south of~$i_1$ (since~$i_1 < i_2$) and passes south of~$f$, we obtain that~$i_2$ must pass south of~$e$, so that $i_m \to i_2$, which contradicts the minimality of~$\b{C}$.
+\item If~$e$ is weakly southeast of~$f$, then~$e'$ is southeast of~$f$, which is impossible as $i_1$ has to pass through both~$e'$ and~$f$.
+\qedhere
+\end{itemize}
 \end{proof}
@@
 
+\pagebreak
 \subsection{Linear extensions of facets}
@@
 
+\pagebreak
 \begin{remark}

### 2023-10-06 acyclicFacets/draft/latticePipeDreams.tex
corrections comments Nantel

@@
 To prove this result, we will need the following observation.
-Note that throughout the proof, the pipes, rows, and column are all indexed by indices ranging from $0$ to~$n$.
+Note that throughout the proof, all pipes, rows, and column are indexed by indices ranging from $0$ to~$n$.
 
@@
 \begin{proof}
-Let~$r$ be the row and $c$ be the column of the crossing~$x$ (careful that all indices range from~$0$ to~$n$).
+Let~$r$ be the row and $c$ be the column of the crossing~$x$. % (careful that all indices range from~$0$ to~$n$).
 Since $i$ has an elbow southwest of $x$, we have $r \le i-1$.
@@
 \item Assume first that~$k$ and~$\ell$ cross at~$x$.
-Since $\omega^{-1}(k) < \omega^{-1}(\ell)$, we have~$k \contactLess{P} \ell$.
-Moreover, since~$\ell\ne i$, the pipe~$\ell$ must have an elbow west of~$x$ along row~$i$, which implies that~$\ell \contactLess{P} k$.
+Note that $k$ is vertical while $\ell$ is horizontal at~$x$.
+Hence, $\omega^{-1}(k) < \omega^{-1}(\ell)$,  so that~$k \contactLess{P} \ell$.
+Moreover, $\ell \ne i$ (since~$i$ and~$k$ do not cross), so that~$\ell$ must have an elbow west of~$x$ along row~$i$.
+As $k$ must have an elbow south of~$x$, we obtain that~$\ell \contactLess{P} k$ by~\cref{lem:rectangle}.
 Hence, we have both~$k \contactLess{P} \ell$ and~$\ell \contactLess{P} k$, so that~$P$ is cyclic.
-\item Assume now that~$k$ and~$\ell$ touch at~$x$, so that~$k \contactLess{P} \ell$.
-If~$\ell < k$, then~$k$ and~$\ell$ must cross before~$x$, and flipping~$x$ in~$P$ yields a cyclic facet.
+\item Assume now that~$k$ and~$\ell$ touch at~$x$.
+Hence~$k \contactLess{P} \ell$.
+If~$\ell < k$, then~$k$ and~$\ell$ must cross at~$y$ before~$x$.
+Flipping~$x$ to~$y$, we obtain a facet~$P'$ with~$\ell \contactLess{P'} k$ (because of the contact~$y$) and~$k \contactLess{P'} \ell$ (because of the last row of elbows which is still in~$P'$), so that~$P'$ would be cyclic.
 If~$\omega^{-1}(\ell) < \omega^{-1}(k)$, then~$\ell \contactLess{P} k$, so that~$P$ is again cyclic.
 Hence, we can assume that~$k < \ell$ and~$\omega^{-1}(k) < \omega^{-1}(\ell)$.
-By maximality of~$k$, we obtain that~$j$ and~$\ell$ do not cross, and thus that~$j$ passes northwest of~$x$.
-We conclude that~$j \contactLess{P} k$.
+By maximality of~$k$, we obtain that~$j$ and~$\ell$ do not cross, and thus that~$j$ must have elbow northwest of~$x$.
+Since $x$ contain an elbow for~$k$, \cref{lem:rectangle} yield~$j \contactLess{P} k$.
 Since~$\omega^{-1}(k) < \omega^{-1}(j)$, we also have~$k \contactLess{P} j$, so that~$P$ is cyclic.

### 2023-10-29 acyclicFacets/draft/latticePipeDreams.tex
small edits section v-Tamari

@@
 To prove this result, we will need the following observation.
-Note that throughout the proof, all pipes, rows, and column are indexed by indices ranging from $0$ to~$n$.
+Note that throughout the proof, all pipes, rows, and columns are indexed by indices ranging from $0$ to~$n$.
 
@@
 Let~$r$ be the row and $c$ be the column of the crossing~$x$. % (careful that all indices range from~$0$ to~$n$).
-Since $i$ has an elbow southwest of $x$, we have $r \le i-1$.
+Since $i$ has an elbow southwest of~$x$, we have $r \le i-1$.
 Since $j$ has an elbow northeast of~$x$, there are at most $r-1 \le i-2$ pipes that cross north of $(c,r)$ in column~$c$.
-Hence, at least two pipes smaller than~$i$ reach the northern border before column~$c$.
+Hence, at least two pipes smaller than~$i$ reach the northern border weakly before column~$c$.
 Excluding the pipe~$0$, there is at least one pipe $h > 0$ such that $h < i < j$ and $\omega^{-1}(h) < \omega^{-1}(j) < \omega^{-1}(i)$.
@@
 If~$\ell < k$, then~$k$ and~$\ell$ must cross at~$y$ before~$x$.
-Flipping~$x$ to~$y$, we obtain a facet~$P'$ with~$\ell \contactLess{P'} k$ (because of the contact~$y$) and~$k \contactLess{P'} \ell$ (because of the last row of elbows which is still in~$P'$), so that~$P'$ would be cyclic.
+Flipping~$x$ to~$y$, we obtain a pipe dream~$P'$ with~$\ell \contactLess{P'} k$ (because of the contact~$y$) and~$k \contactLess{P'} \ell$ (because of the last row of elbows which is still in~$P'$), so that~$P'$ would be cyclic.
 If~$\omega^{-1}(\ell) < \omega^{-1}(k)$, then~$\ell \contactLess{P} k$, so that~$P$ is again cyclic.
@@
 By maximality of~$k$, we obtain that~$j$ and~$\ell$ do not cross, and thus that~$j$ must have elbow northwest of~$x$.
-Since $x$ contain an elbow for~$k$, \cref{lem:rectangle} yield~$j \contactLess{P} k$.
+Since $x$ contain an elbow for~$k$, \cref{lem:rectangle} yields~$j \contactLess{P} k$.
 Since~$\omega^{-1}(k) < \omega^{-1}(j)$, we also have~$k \contactLess{P} j$, so that~$P$ is cyclic.
@@
 The reverse direction does not necessarily holds, but clearly holds for cover relations of~$\contactLess{P}$ (as in this case, there is an elbow of~$i$ in contact with an elbow of~$j$).
-Assume now that there is a cyclic pipe dream~$P \in \pipeDreams(\omega)$.
+Assume now that there is a cyclic pipe dream~$P \in \pipeDreams(0\omega)$.
 We can thus find a cycle~$\b{C}=(i_1, \dots, i_m)$ with~$i_1 \to \dots \to i_m \to i_1$.
@@
 
-If~$m = 2$, then the pipes~$i_1$ and~$i_2$ must cross at some point~$x$, and $i_1 \to i_2$ implies that $i_1$ has an elbow southeast of~$x$, while $i_2 \to i_1$ implies that $i_2$ has an elbow northwest of~$x$, so that $\omega$ is not dominant by \cref{lem:notDominant}.
-
-Assume now that~$m \ge 3$.
+If~$m = 2$, then the pipes~$i_1$ and~$i_2$ must cross at some point~$x$.
+Without loss of generality, we can assume $i_1<i_2$. 
+The fact $i_1 \to i_2$ implies that $i_1$ has an elbow southwest of~$x$, while $i_2 \to i_1$ implies that $i_2$ has an elbow northeast of~$x$, so that $\omega$ is not dominant by \cref{lem:notDominant}.
+
+We now show that if~$\b{C}$ is reduced then the case $m\geq 3$ is impossible.
+Assume that~$m \ge 3$.
 Assume moreover that~$i_1 < i_\ell$ for all~$\ell \in [m]$ (if not, rotate the indices).
@@
 We now distinguish four cases:
-\begin{itemize}
+\begin{enumerate}[(i)]
 \item If~$e$ is weakly northwest of~$f$, thus of~$f'$, then~$i_m \to i_2$, contradicting the minimality of~$\b{C}$.
@@
 In both cases, this contradicts the minimality of~$\b{C}$.
-\item If~$e$ is southwest of~$f$, as~$i_1$ passes trough~$e'$ and~$f$, and $i_2$ starts south of~$i_1$ (since~$i_1 < i_2$) and passes south of~$f$, we obtain that~$i_2$ must pass south of~$e$, so that $i_m \to i_2$, which contradicts the minimality of~$\b{C}$.
+\item If~$e$ is southwest of~$f$, as~$i_1$ passes trough~$e'$ and~$f$, and $i_2$ starts south of~$i_1$ (since~$i_1 < i_2$) and passes south of~$f$, we obtain that~$i_2$ must pass south of~$e$ (otherwise $i_2$ would cross $i_1$ twice), so that $i_m \to i_2$, which contradicts the minimality of~$\b{C}$.
 \item If~$e$ is weakly southeast of~$f$, then~$e'$ is southeast of~$f$, which is impossible as $i_1$ has to pass through both~$e'$ and~$f$.
 \qedhere
-\end{itemize}
-\end{proof}
-
-Applying our \cref{thm:pipeDreamQuotient}, using the isomorphism $[0e,0\omega_\nu]\cong [e,\omega_\nu]$, we get the following consequence.
+\end{enumerate}
+\end{proof}
+
+Applying our \cref{thm:pipeDreamQuotient}, and using the isomorphism $[0e,0\omega_\nu]\cong [e,\omega_\nu]$, we get the following consequence.
 

### 2023-10-30 acyclicFacets/draft/latticePipeDreams.tex
last edits before submission

@@
 
-\vspace*{-.8cm}
+\vspace*{-1cm}
 
@@
 \tableofcontents
+
+\vspace*{-.5cm}
 
@@
 Note that \cref{thm:A} is the correct generalization of the Tamari lattice, as neither the increasing flip poset on all pipe dreams, nor its subposet induced by acyclic pipe dreams, are lattices in general (see \cref{rem:increasingFlipPosetNotLattice,rem:acyclicIncreasingFlipPosetNotLattice}).
+Other conjectural lattice structures on pipe dreams are considered in~\cite[Conj.~2.8]{Rubey}.
 
@@
 Since $i$ has an elbow southwest of~$x$, we have $r \le i-1$.
-Since $j$ has an elbow northeast of~$x$, there are at most $r-1 \le i-2$ pipes that cross north of $(c,r)$ in column~$c$.
+Since $j$ has an elbow northeast of~$x$, there are at most $r-1 \le i-2$ pipes that cross north of $x$ in column~$c$.
 Hence, at least two pipes smaller than~$i$ reach the northern border weakly before column~$c$.
@@
 Without loss of generality, we can assume $i_1<i_2$. 
-The fact $i_1 \to i_2$ implies that $i_1$ has an elbow southwest of~$x$, while $i_2 \to i_1$ implies that $i_2$ has an elbow northeast of~$x$, so that $\omega$ is not dominant by \cref{lem:notDominant}.
+The fact $i_1 \to i_2$ implies that $i_1$ has an elbow southwest of~$x$, while the fact that $i_2 \to i_1$ implies that $i_2$ has an elbow northeast of~$x$, so that $\omega$ is not dominant by \cref{lem:notDominant}.
 

### 2023-10-31 acyclicFacets/draft/latticePipeDreams.tex
Some typos

@@
 Then~$x'$ is still weakly northwest of~$y$ and $x',y$ are strictly closer than~$x,y$.
-By induction, there is a directed path from~$k$ to~$\ell$ in~$P\contact$, and thus a path directed form~$i$ to~$j$.
+By induction, there is a directed path from~$k$ to~$\ell$ in~$P\contact$, and thus a path directed from~$i$ to~$j$.
 \end{proof}
@@
 
-We will see in \cref{sec:furtherTopics} insertion algorithms to compute the pipe dream~$P \in \acyclicPipeDreams(\omega)$ such that~$\pi \in \linearExtensions(P)$ for given permutations~$\pi < \omega$.
+We will see in \cref{sec:furtherTopics} insertion algorithms to compute the pipe dream~$P \in \acyclicPipeDreams(\omega)$ such that~$\pi \in \linearExtensions(P)$ for given permutations~$\pi \le \omega$.
 These algorithms are however not needed for the proof of \cref{thm:partitionPipeDreams}, which we break into the following three lemmas.
@@
 Decompose the triangular shape into three regions: the region~$A$ of all points located northeast of the last elbow of the pipe~$j$ of~$P$, the region~$B$ of all points located northwest or southeast of an elbow of the pipe~$j$ of~$P$, and the region~$C$ of all points located southwest of the first elbow of the pipe~$j$ of~$P$.
-Since~$i \contactLess{P} k$, there is a path~$\pi$ form the exiting point of the pipe~$i$ of~$P$ to the entering point of the pipe~$j$ of~$P$ which travels along the pipes of~$P$, possibly jumping from the northwest pipe to the southeast pipe of a contact it encounters.
+Since~$i \contactLess{P} k$, there is a path~$\pi$ from the exiting point of the pipe~$i$ of~$P$ to the entering point of the pipe~$j$ of~$P$ which travels along the pipes of~$P$, possibly jumping from the northwest pipe to the southeast pipe of a contact it encounters.
 Since~$i < j$ and~$\omega^{-1}(j) > \omega^{-1}(k)$, the path~$\pi$ starts in region~$A$ and ends in region~$C$, so that it necessarily passes from region~$A$ to region~$C$.
@@
 \item there exist linear extensions~$\pi$ of~$P$ and~$\pi'$ of~$P'$ such that~$\pi < \pi'$ in weak order,
-\item the minimal (resp.~max) linear extensions~$\pi$ of~$P$ and~$\pi'$ of~$P$ satisfy~$\pi < \pi'$ in weak order.
+\item the minimal (resp.~max) linear extensions~$\pi$ of~$P$ and~$\pi'$ of~$P'$ satisfy~$\pi < \pi'$ in weak order.
 \item there is no~$i < j$ such that~$i \contactMore{P} j$ and~$i \contactLess{P'} j$,
@@
 The equivalence (ii) $\Leftrightarrow$ (iii) is valid for any lattice quotient.
-The equivalences (iii) $\Leftrightarrow$ (iv) $\Leftrightarrow$ (v) $\Leftrightarrow$ (vi) follow from the descriptions of \cref{prop:WOIP} for the inversions of the minimum and the non-inversions of the maximum of a weak order interval.
+The equivalences (iii) $\Leftrightarrow$ (iv) $\Leftrightarrow$ (v) $\Leftrightarrow$ (vi) follow from the descriptions of \cref{prop:WOIP} of the inversions of the minimum and the non-inversions of the maximum of a weak order interval.
 \end{proof}
@@
 \label{prop:sweepingAlgorithm}
-For any permutations~$\pi,\omega \in \fS_n$ such that~$\pi < \omega$ in weak order, the unique pipe dream~$P \in \acyclicPipeDreams(\omega)$ such that~$\pi \in \linearExtensions(P)$ can be constructed by sweeping the triangular shape in any northeast compatible order and placing a crossing when sweeping a vertex~$v$ of the grid where pipe~$i$ arrives horizontally and pipe~$j$ arrives vertically if and only if
+For any permutations~$\pi,\omega \in \fS_n$ such that~$\pi \le \omega$ in weak order, the unique pipe dream~$P \in \acyclicPipeDreams(\omega)$ such that~$\pi \in \linearExtensions(P)$ can be constructed by sweeping the triangular shape in any northeast compatible order and placing a crossing when sweeping a vertex~$v$ of the grid where pipe~$i$ arrives horizontally and pipe~$j$ arrives vertically if and only if
 \begin{itemize}
@@
 \label{prop:insertionAlgorithm}
-For any permutations~$\pi,\omega \in \fS_n$ such that~$\pi < \omega$ in weak order, the unique pipe dream~$P \in \acyclicPipeDreams(\omega)$ such that~$\pi \in \linearExtensions(P)$ can be constructed starting from the empty triangular shape and inserting the pipes~$\pi(1), \dots, \pi(n)$ one by one in the order of the permutation~$\pi$ as northwest as possible.
+For any permutations~$\pi,\omega \in \fS_n$ such that~$\pi \le \omega$ in weak order, the unique pipe dream~$P \in \acyclicPipeDreams(\omega)$ such that~$\pi \in \linearExtensions(P)$ can be constructed starting from the empty triangular shape and inserting the pipes~$\pi(1), \dots, \pi(n)$ one by one in the order of the permutation~$\pi$ as northwest as possible.
 More precisely, at step~$t$, we insert a pipe starting at row~$\pi(t)$, ending at column~$\omega^{-1}(\pi(t))$, and whose northeast elbows are precisely covering the staircase of currently free southeast elbows in the rectangle~$[\pi(t)] \times [\omega^{-1}(\pi(t))]$.
@@
 \begin{proof}
-Observe first that if there if~$r < s$ such that~$\pi(r) > \pi(s)$ and~$\omega^{-1}(\pi(r)) > \omega^{-1}(\pi(s))$, then setting~$i \eqdef \pi(s)$ and~$j \eqdef \pi(r)$, we have~${i < j}$ and~$\pi^{-1}(i) > \pi^{-1}(j)$ while~$\omega^{-1}(i) < \omega^{-1}(j)$, which contradicts our assumption that~$\pi < \omega$.
+Observe first that if there if~$r < s$ such that~$\pi(r) > \pi(s)$ and~$\omega^{-1}(\pi(r)) > \omega^{-1}(\pi(s))$, then setting~$i \eqdef \pi(s)$ and~$j \eqdef \pi(r)$, we have~${i < j}$ and~$\pi^{-1}(i) > \pi^{-1}(j)$ while~$\omega^{-1}(i) < \omega^{-1}(j)$, which contradicts our assumption that~$\pi \le \omega$.
 This implies that
@@
 \label{coro:rectangleInsertionAlgorithm2}
-All pipes of constructed by the insertion algorithm remain in the triangular shape.
+All pipes constructed by the insertion algorithm remain in the triangular shape.
 \end{corollary}
@@
 We now generalize the canopy of a binary tree.
-Recall that the \defn{canopy} of a binary tree~$T$ with~$n$ internal nodes is the sign sequence~${\canopy{T} \in \{{-},{+}\}^{n-1}}$ defined by~$\canopy{T}_i = {-}$ if the $(i+1)$st leaf of~$T$ is a left leaf and~$\canopy{T}_i = {+}$ if the $(i+1)$st leaf of~$T$ is a right leaf.
+Recall that the \defn{canopy} of a binary tree~$T$ with~$n$ internal nodes is the sign sequence~${\canopy{T} \in \{{-},{+}\}^{n-1}}$ defined by~$\canopy{T}_i = {-}$ if the $(i+1)$-th leaf of~$T$ is a left leaf and~$\canopy{T}_i = {+}$ if the $(i+1)$-th leaf of~$T$ is a right leaf.
 Equivalently, $\canopy{T}_i = -$ if the node~$i$ of~$T$ is above the node~$i+1$ of~$T$ and~$\canopy{T}_i = +$ otherwise.
@@
 Hence, we can assume that~$k < \ell$ and~$\omega^{-1}(k) < \omega^{-1}(\ell)$.
-By maximality of~$k$, we obtain that~$j$ and~$\ell$ do not cross, and thus that~$j$ must have elbow northwest of~$x$.
+By maximality of~$k$, we obtain that~$j$ and~$\ell$ do not cross, and thus that~$j$ must have an elbow northwest of~$x$.
 Since $x$ contain an elbow for~$k$, \cref{lem:rectangle} yields~$j \contactLess{P} k$.

### 2023-10-31 acyclicFacets/draft/latticePipeDreams.tex
minor changes arXiv

--- 2023-10-30 acyclicFacets/draft/latticePipeDreams.tex
@@
 \author[N.~Cartier]{No\'emie Cartier} 
-\address[N.~Cartier]{LRI, Université Paris Saclay}
+\address[N.~Cartier]{LISN, Université Paris Saclay}
 \email{noemie.cartier@lri.fr}
@@
 %
-\hvFloat[floatPos=p, capWidth=h, capPos=r, capAngle=90, objectAngle=90, capVPos=c, objectPos=c]{figure}
+\hvFloat[floatPos=p, capWidth=h, capPos=right, capAngle=90, objectAngle=90, capVPos=center, objectPos=center]{figure}
 {\includegraphics[scale=.55]{subwordComplex1}}
@@
 %
-\hvFloat[floatPos=p, capWidth=h, capPos=r, capAngle=90, objectAngle=90, capVPos=c, objectPos=c]{figure}
+\hvFloat[floatPos=p, capWidth=h, capPos=right, capAngle=90, objectAngle=90, capVPos=center, objectPos=center]{figure}
 {\includegraphics[scale=.65]{subwordComplex2}}
@@
 %
-\hvFloat[floatPos=p, capWidth=h, capPos=r, capAngle=90, objectAngle=90, capVPos=c, objectPos=c]{figure}
+\hvFloat[floatPos=p, capWidth=h, capPos=right, capAngle=90, objectAngle=90, capVPos=center, objectPos=center]{figure}
 {\includegraphics[scale=.65]{subwordComplex3}}

### 2023-12-22 acyclicFacets/draft/latticePipeDreams.tex
add reference to FPSAC
change affiliation

@@
 \author[V.~Pilaud]{Vincent Pilaud}
-\address[V.~Pilaud]{CNRS \& LIX, \'Ecole Polytechnique, Palaiseau}
-\email{vincent.pilaud@lix.polytechnique.fr}
-\urladdr{http://www.lix.polytechnique.fr/~pilaud/}
+\address[V.~Pilaud]{Universitat de Barcelona}
+\email{vincent.pilaud@ub.edu}
+\urladdr{https://www.ub.edu/comb/vincentpilaud/}
 
@@
 CC, NC \& VP were also supported by the Austrian\,--\,French project PAGCAP (ANR~21\,CE48\,0020 \& FWF I 5788).
+VP was a CNRS researcher at \'Ecole Polytechnique when this work was done.
+\\
+\hspace*{.5cm} 
+Part of the material of this paper was announced in an extended abstract of the conference FPSAC'23~\cite{Cartier-FPSAC}.
 }
@@
 
-\vspace*{-1cm}
+\vspace*{-1.2cm}
 
@@
 
-\vspace*{-.5cm}
+\vspace*{-.7cm}
 

### 2024-11-15 acyclicFacets/draft/latticePipeDreams.tex
comments mistake

@@
 \]
+\vincent{
+There is a bug here and in the proof. This should be $\max(0, ...)$.
+In the proof, we need to argue that as soon as we use the $\max$ (meaning that a pipe that should contribute to~$-1$ contributes to~$0$), we stay at~$0$ (as we cannot insert pipes that contribute to~$1$, because all non-inversions of~$\omega$ are non-inversions of~$\pi$!!
+Add Nathan Reading to the acknowledgements for a discussion that made me observe this bug.
+}
 \end{lemma}

### 2025-02-18 acyclicFacets/reports/answerReferee.tex
most corrections + answer referee

\documentclass{letter}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{url}
\usepackage{shuffle}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{amsfonts, amsmath, amssymb}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage[a4paper, top=1in, bottom=.8in, left=1in, right=1in]{geometry}
\signature{%
Nantel Bergeron, Noémie Cartier, Cesar Ceballos, and Vincent Pilaud \Letter
}

\address{\bf Nantel Bergeron \\
\small York University, Toronto \\
\small \texttt{bergeron@yorku.ca} \\[.3cm]
\bf Noémie Cartier \\
\small Université Paris Saclay \\[.3cm]
\bf Cesar Ceballos \\
\small Technische Universit\"at Graz \\
\small \texttt{cesar.ceballos@tugraz.at} \\[.3cm]
\bf Vincent Pilaud \Letter \\
\small Universitat de Barcelona \\
\small \texttt{vincent.pilaud@ub.edu}
}

\begin{document}

\begin{letter}{{\bf Editors and Referees} \\ Algebraic Combinatorics}
\opening{Dear Editors, dear Referee,}

We are grateful to the referee for their thorough reading and their constructive suggestions on our manuscript \emph{Lattices of acyclic pipe dreams}. We would like to submit a revised version of this manuscript to the \emph{Algebraic Combinatorics}.

We agreed with most comments and suggestions of the referee and we have revised our submission accordingly. To simplify the second reading, we now answer the comments of the referee and summarize the changes from the last version:

{\bf About pipe dreams and subword complexes.} The referee underlined a major point:

\textsl{\color{gray} 
In the last part of the paper, the authors investigate the subword complexes in finite Coxeter groups, which were studied by Jahn and Stump recently. The results mostly follow from Jahn and Stump's work, the authors use a different approach and technique though. I feel the content in section 5 is loosely connected to the content before and does not have many pipe dreams in it (as the title suggests). I believe this section should be shortened to keep the article focused on its main point.
}

We believe that our results on pipe dreams are the shadow of more general statements on subword complexes that are discussed in Section~5.
These generalizations are non-obvious extensions of our results on pipe dreams, so we really want to state them here as precise conjectures.
In fact, we obtained our results on pipe dreams in 2017 (about 6 years prior to the prepublication of the present submission), but we really struggled to obtain seemingly correct conjectures generalizing these results.
The title of the paper focusses on pipe dreams to reflect the content nature of the results, but we believe that our conjectures on subword complexes are equally important.

{\bf Major comments}

\begin{itemize}
\item \textsl{\color{gray} Page 5 - lemma 2.6: the lemma statement does not specify the types of elbow of pipes i and j; however, the proof seem to assume the elbows involved in the statement are of certain type (southeast or northwest). This lemma is cited multiple times throughout the paper and this issue needs to be clarified.} \\
We are not sure to understand this comment.
We make no assumption on the type of elbows of pipes~$i$ and~$j$ in the proof of Lemma~2.6.
If~$x=y$, then we have an edge from $i$ to $j$ in~$P^\#$ since $i$ is northwest of~$j$ at~$x$ by assumption (we have added ``and $i$ is northwest of~$j$ at this contact by assumption'' to make that clear).
If~$x \ne y$, we were actually careful to define~$k$ and~$\ell$ precisely to avoid making any assumption on the type of elbow of~$i$ and~$j$.
Please, let us know if we misunderstood your concern.

\item \textsl{\color{gray} Page 18 -- example 5.3: this is the only connection to pipe dreams in this section but the description is quite vague. An example with picture would make it much better.} \\
We agree with the referee.
Actually, not only this description was quite vague, but it was actually not completely correct.
The reason is that we have decided in this paper to label the pipes from top to bottom on the left of the pipe dream, which is unusual but much more convenient for our lattice quotient considerations.
We have corrected the description and added a specific example at the end of Example 5.3 referring to the pipe dreams of Figure~1.
We hope it is much easier to follow now.

\item \textsl{\color{gray} Page 27 -- section 5.5: it seems that some of the conjectures have been solved. Worth adding a remark on that.} \\
We are not sure to understand this comment.
As stated in Remark 5.26, all conjectures of Section~5.5 are proved in type~$A$.
Namely, the case of pipe dreams treated in Section 3 settles the specific case of the word described in Example 5.3, and the paper \\[.2cm]
Noémie Cartier, Lattice properties of acyclic Cambrian pipe dreams. \href{http://arxiv.org/abs/2311.10435}{\texttt{arXiv:2311.10435}}, 2023\\[.2cm]
settles the case of all alternating words in type~$A$.
However, we are not aware that any of these conjectures is solved beyond type~$A$.
Please, let us know if we are missing something here.
\end{itemize}

{\bf Minor comments}

\begin{itemize}
\item \textsl{\color{gray} Page 5 - lemma 2.4: the first place non-inversion of a permutation is mentioned is on page 7 in the proof of lemma 3.6. The phrase 'non-inversion' should be mentioned here when its size is defined.} \\
We have added ``is the number of \emph{non-inversions} of~$j$ in~$\omega$'' at the end of the definition of $\mathsf{ninv}(\omega, j)$.

\item \textsl{\color{gray} Page 6 - example 3.3: when the phrase ``below'' is first used, it should be pointed out that this refers to the weak order.} \\
Thank you. We have added the precision ``in weak order''.

\item \textsl{\color{gray} Page 6 -- example 3.3: add reference of the well-known fact.} \\
Thank you. We have added references to Tonks and to Hivert--Novelli--Thibon. We actually added references to Hivert--Novelli--Thibon in several places mentioning the sylvester congruence.

\item \textsl{\color{gray} Page 8 - proposition 3.12: the notations min(I) and max(I) should be clarified what they mean exactly.} \\
We have added ``$I := [\min(I), \max(I)]$'' in the second line of the proposition.

\item \textsl{\color{gray} Page 9 - remark 3.17: reference not showing up correctly.} \\
Thank you. Fixed.

\item \textsl{\color{gray} Page 10 - proof of lemma 3.18: in the last line, the inequality $\omega^{-1}(k_1)> \omega^{-1}(j) > \omega^{-1}(i)$ should be $\omega^{-1}(k_1)< \omega^{-1}(j) < \omega^{-1}(i)$.} \\
Thank you. Fixed.

\item \textsl{\color{gray} Proposition 3.19 -- (v): the relation after ``then'' is the wrong direction.} \\
Thank you. Fixed.

\item \textsl{\color{gray} Page 12 - 3rd line in the second paragraph in section 4.2: since you are constructing a pipe dream, it makes more sense to say ``For $j\in [n]$ such that $j>r_1$ and $c_k<\omega^{-1}(j)$, we can uniquely define a pipe dream which ...''} \\
Thank you. We have modified.

\item \textsl{\color{gray} Page 12 - second to the last line in proposition 4.3: northeast should be southeast.} \\
Thank you for noticing this inconsistency. We have replaced by ``northwest''.

\item \textsl{\color{gray} Page 14 -- line 1: the second ``if'' should be an ``is''.} \\
Thank you. Corrected.

\item \textsl{\color{gray} Page 15 -- cor 4.12: ``patters'' should be ``pattern''.} \\
Thank you. Corrected.

\item \textsl{\color{gray} Page 15 -- section 4.4: this section needs an example.} \\
{\color{red} TODO}

\item \textsl{\color{gray} Page 18 - second paragraph in section 5.2: $J\subseteq [r]$ should be $J\subseteq [m]$.} \\
Thank you. Corrected.

\item \textsl{\color{gray} Page 18 - root function: the product notation $\prod Q_X$ needs to be clarified.} \\
We have added ``where~$\prod Q_{[k-1]\smallsetminus I}$ is the product of the letters~$q_i$ for~$i \in [k-1] \smallsetminus I$ computed in the natural order''.

\item \textsl{\color{gray} Page 19 -- line 4 in example 5.5: the c-sorting word notation looks different from the one in line 2, \LaTeX error?} \\
We are not sure we understood your concern here. In the subword complex, we consider the word~$c\omega_\circ(c)$, obtained by concatenation of~$c$ with the $c$-sorting word~$\omega_\circ(c)$. We have added ``and consider the concatenation~$c\omega_\circ(c)$'' to make this clear.

\end{itemize}

{\bf Additional correction.}
Finally, we have also slightly modified the statement and proof of Lemma 4.7.
{\color{red} TODO + explain why.}

We are really grateful for all these improvements and would like to thank the referee again for the efforts they offered to our work. We hope that we have addressed their comments carefully, but we will be happy to have any further comments on this submission.

%Sincerely,
%
%\vspace{.5cm}
%\hspace{8cm} Asilata Bapat and Vincent Pilaud

\closing{Sincerely yours,}

\end{letter}

\end{document}

### 2025-02-18 acyclicFacets/draft/latticePipeDreams.tex
most corrections + answer referee

@@
 Hence, this map sends the increasing flip poset on reversing pipe dreams to the \defn{Tamari lattice} on binary trees.
-This lattice is defined as the transitive closure of right rotations on binary trees, and is obtained as the quotient of the weak order by the \defn{sylvester congruence}.
+This lattice is defined as the transitive closure of right rotations on binary trees, and is obtained as the quotient of the weak order by the \defn{sylvester congruence}~\cite{Tonks,HivertNovelliThibon-algebraBinarySearchTrees}.
 An important point here is that all reversing pipe dreams are acyclic, since their contact graphs are (oriented)~binary~trees.
@@
 \end{itemize}
-where~$\noninversions{\omega}{j} \eqdef \#\set{i \in [n]}{i < j \text{ and } \omega^{-1}(i) < \omega^{-1}(j)}$.
+where~$\noninversions{\omega}{j} \eqdef \#\set{i \in [n]}{i < j \text{ and } \omega^{-1}(i) < \omega^{-1}(j)}$ is the number of \defn{non-inversions} of~$j$ in~$\omega$.
 \end{lemma}
@@
 We proceed by induction on the grid distance from~$x$ to~$y$.
-If they coincide, then pipes~$i$ and~$j$ share a contact, so that there is an edge from~$i$ to~$j$ in~$P\contact$.
+If they coincide, then pipes~$i$ and~$j$ share a contact, and $i$ is northwest of~$j$ at this contact by assumption, so that there is an edge from~$i$ to~$j$ in~$P\contact$.
 Otherwise, let~$k$ be the pipe of~$P$ with a southeast elbow at~$x$ ($k$ is either the pipe~$i$ itself, or there is an edge from~$i$ to~$k$ in~$P\contact$) and~$\ell$ be the pipe of~$P$ with a northwest elbow at~$y$ ($\ell$ is either the pipe~$j$ itself, or there is an edge from~$\ell$ to~$j$ in~$P\contact$).
@@
 \label{exm:Tamari2}
-Following \cref{exm:Tamari1}, observe that the permutations of~$\{0, 1, \dots, n, n+1\}$ below~$\rho_n$ are precisely the permutations of the form~$[0, \pi, n+1]$ for some~$\pi \in \fS_n$.
-It is well-known that any permutation~$\pi \in \fS_n$ is a linear extension of a unique binary tree.
-This binary tree can be obtained by inserting~$\pi$ from right to left in a binary search tree.
+Following \cref{exm:Tamari1}, observe that the permutations of~$\{0, 1, \dots, n, n+1\}$ below~$\rho_n$ in weak order are precisely the permutations of the form~$[0, \pi, n+1]$ for some~$\pi \in \fS_n$.
+It is well-known that any permutation~$\pi \in \fS_n$ is a linear extension of a unique binary tree~\cite{Tonks}.
+This binary tree can be obtained by inserting~$\pi$ from right to left in a binary search tree~\cite{HivertNovelliThibon-algebraBinarySearchTrees}.
 Hence any permutation of~$\{0, 1, \dots, n, n+1\}$ below~$\rho_n$ is a linear extension of a unique reversing pipe dream on~$n+2$ pipes.
@@
 \label{exm:Tamari3}
-Following \cref{exm:Tamari1,exm:Tamari2}, observe that the congruence~$\equiv_{\rho_n}$ on the permutations of~$\{0, 1, \dots, n, n+1\}$ below~$\rho_n$ corresponds to the sylvester congruence on~$\fS_n$.
+Following \cref{exm:Tamari1,exm:Tamari2}, observe that the congruence~$\equiv_{\rho_n}$ on the permutations of~$\{0, 1, \dots, n, n+1\}$ below~$\rho_n$ corresponds to the sylvester congruence on~$\fS_n$ defined in~\cite{HivertNovelliThibon-algebraBinarySearchTrees}.
 The classes of this congruence are the sets of linear extensions of the binary trees (considered as posets, labeled in inorder, and oriented towards their roots).
@@
 \label{prop:WOIP}
-The set~$\linearExtensions(\less)$ of linear extensions of a poset~$\less$ on~$[n]$ forms an interval~$I$ of the weak order if and only if for every~$i < j < k$,
+The set~$\linearExtensions(\less)$ of linear extensions of a poset~$\less$ on~$[n]$ forms an interval~$I \eqdef [\min(I), \max(I)]$ of the weak order if and only if for every~$i < j < k$,
 \[
@@
 \cref{fig:counterExampleRestrictionIncreasingFlipPoset1} illustrates two acyclic pipe dreams of~$\acyclicPipeDreams(126543)$ connected by a sequence of increasing flips in~$\pipeDreams(126543)$ but by no sequence of increasing flips in~$\acyclicPipeDreams(126543)$.
-In fact, the subposet of the increasing flip poset induced by~$\acyclicPipeDreams(126543)$ is not even a lattice, as illustrated in \cref{counterExampleRestrictionIncreasingFlipPoset2}.
+In fact, the subposet of the increasing flip poset induced by~$\acyclicPipeDreams(126543)$ is not even a lattice, as illustrated in \cref{fig:counterExampleRestrictionIncreasingFlipPoset2}.
 This example is minimal.
@@
 We thus obtain that~$k$ must be straight before it reaches~$R$, and after it leaves~$R$.
-Hence $k_1 < i < j$ and~$\omega^{-1}(k_1) > \omega^{-1}(j) > \omega^{-1}(i)$.
+Hence $k_1 < i < j$ and~$\omega^{-1}(k_1) < \omega^{-1}(j) < \omega^{-1}(i)$.
 By \cref{lem:consequenceRectangle1}, this contradicts~$i \contactLess{P} k_1$~and~$k_1 \contactMore{P'} j$.
@@
 \item there is no~$i < j$ such that~$i \contactMore{P} j$ and~$i \contactLess{P'} j$,
-\item for all~$i < j$, if~$i \contactMore{P} j$, then~$j \contactMore{P'} i$,
-\item for all~$i < j$, if~$i \contactLess{P'} j$, then~$i \contactLess{P} j$,
+\item for all~$i < j$, if~$i \contactMore{P} j$, then~$i \contactMore{P'} j$,
+\item for all~$i < j$, if~$i \contactLess{P'} j$, then~$i \contactLess{P} j$.
 \end{enumerate}
@@
 In other words, $r_1 > \dots > r_k$ and~$c_1 < \dots < c_k$ where~$e_i$ is located in row~$r_i$ and column~$c_i$.
-For~$j \in [n]$ such that~$j > r_1$ and~$c_k < \omega^{-1}(j)$, there is a unique pipe which enters at row~$j$, exits at column~$\omega^{-1}(j)$, and whose northeast elbows are precisely covering the southeast elbows~$e_1, \dots, e_k$.
+For~$j \in [n]$ such that~$j > r_1$ and~$c_k < \omega^{-1}(j)$, we can uniquely define a pipe which enters at row~$j$, exits at column~$\omega^{-1}(j)$, and whose northeast elbows are precisely covering the southeast elbows~$e_1, \dots, e_k$.
 Namely, it has a northeast elbow at row~$r_i$ and column~$c_i$ for each~$i \in [k]$, and a southeast elbow at row~$r_{i-1}$ and column~$c_i$ for each~$i \in [k+1]$, where by convention~$r_0 \eqdef j$ and~$c_{k+1} \eqdef \omega^{-1}(j)$.
@@
 For any permutations~$\pi,\omega \in \fS_n$ such that~$\pi \le \omega$ in weak order, the unique pipe dream~$P \in \acyclicPipeDreams(\omega)$ such that~$\pi \in \linearExtensions(P)$ can be constructed starting from the empty triangular shape and inserting the pipes~$\pi(1), \dots, \pi(n)$ one by one in the order of the permutation~$\pi$ as northwest as possible.
-More precisely, at step~$t$, we insert a pipe starting at row~$\pi(t)$, ending at column~$\omega^{-1}(\pi(t))$, and whose northeast elbows are precisely covering the staircase of currently free southeast elbows in the rectangle~$[\pi(t)] \times [\omega^{-1}(\pi(t))]$.
+More precisely, at step~$t$, we insert a pipe starting at row~$\pi(t)$, ending at column~$\omega^{-1}(\pi(t))$, and whose northwest elbows are precisely covering the staircase of currently free southeast elbows in the rectangle~$[\pi(t)] \times [\omega^{-1}(\pi(t))]$.
 See \cref{fig:insertionAlgorithm1,fig:insertionAlgorithm2}.
@@
 \begin{proof}
-Observe first that if there if~$r < s$ such that~$\pi(r) > \pi(s)$ and~$\omega^{-1}(\pi(r)) > \omega^{-1}(\pi(s))$, then setting~$i \eqdef \pi(s)$ and~$j \eqdef \pi(r)$, we have~${i < j}$ and~$\pi^{-1}(i) > \pi^{-1}(j)$ while~$\omega^{-1}(i) < \omega^{-1}(j)$, which contradicts our assumption that~$\pi \le \omega$.
+Observe first that if there is~$r < s$ such that~$\pi(r) > \pi(s)$ and~$\omega^{-1}(\pi(r)) > \omega^{-1}(\pi(s))$, then setting~$i \eqdef \pi(s)$ and~$j \eqdef \pi(r)$, we have~${i < j}$ and~$\pi^{-1}(i) > \pi^{-1}(j)$ while~$\omega^{-1}(i) < \omega^{-1}(j)$, which contradicts our assumption that~$\pi \le \omega$.
 This implies that
@@
 \label{coro:patternAvoiding}
-A permutation is minimal (resp.~maximal) in its pipe dream congruence class if and only if it avoids the patters~$k_1 - \cdots - k_p - ji$ (resp.~$k_1 - \cdots - k_p - ij$) where~$k_q > i$ and~$\omega^{-1}(k_q) > \omega^{-1}(j)$ for~$q \in [p]$ and~$p = \# \set{k \in [i]}{\omega^{-1}(k) < \omega^{-1}(j)}$.
+A permutation is minimal (resp.~maximal) in its pipe dream congruence class if and only if it avoids the patterns~$k_1 - \cdots - k_p - ji$ (resp.~$k_1 - \cdots - k_p - ij$) where~$k_q > i$ and~$\omega^{-1}(k_q) > \omega^{-1}(j)$ for~$q \in [p]$ and~$p = \# \set{k \in [i]}{\omega^{-1}(k) < \omega^{-1}(j)}$.
 \end{corollary}
@@
 Let $(W,S)$ be a finite Coxeter system, $Q=(q_1,\dots,q_m)$ be a word in the simple reflections $S$, and $\omega \in W$ be an element of the group.
-For $J\subseteq [r]$, we denote by $Q_J$ the subword of~$Q$ consisting of the letters with positions in $J$.
+For $J\subseteq [m]$, we denote by $Q_J$ the subword of~$Q$ consisting of the letters with positions in $J$.
 The \defn{subword complex} $\subwordComplex(Q,\omega)$ is the simplicial complex whose facets are subsets $I\subseteq [m]$ such that $Q_{[m]\setminus I}$ is a reduced expression for $\omega$.
@@
 \[
-\rootFunction{I}{k} \eqdef \prod Q_{[k-1]\ssm I}(\alpha_{q_k}).
-\]
+\rootFunction{I}{k} \eqdef \prod Q_{[k-1]\ssm I}(\alpha_{q_k}),
+\]
+where~$\prod Q_{[k-1]\ssm I}$ is the product of the letters~$q_i$ for~$i \in [k-1] \ssm I$ computed in the natural order.
 The \defn{root configuration} is the set $\Roots(I)=\set{\rootFunction{I}{i}}{i\in I}$.
@@
 \label{exm:typeARootConfiguration}
-Continuing \cref{exm:typeACoxeterSystem}, we consider the type~$A_n$ Coxeter system, the word $Q \eqdef \tau_1 \cdots \tau_{n-1} \tau_1 \cdots \tau_{n-2} \cdots \tau_1 \tau_2 \tau_1$, and a permutation~$\omega \in \fS_n$.
-The word~$Q$ naturally fits on an $n \times n$ triangular grid (place $\tau_k$ in all boxes with row~$i$ and column~$j$ such that~$i+j+k = n+1$) and each facet~$I$ of the subword complex~$\subwordComplex(Q, \omega)$ corresponds to a pipe dream~$P_I$ of~$\pipeDreams(\omega)$ (replace each position in~$I$ by a contact in~$P_I$, and the other positions by crossings in~$P_I$).
-The root function is given~$\rootFunction{I}{i} = \b{r}_{p,q} \eqdef \b{e}_p - \b{e}_q$ where~$p$ is the pipe arriving from the west and $q$ is the pipe arriving from the south at the box of~$P_I$ corresponding to position~$i$ of~$Q$.
+Continuing \cref{exm:typeACoxeterSystem}, we consider the type~$A_{n-1}$ Coxeter system, the word $Q \eqdef \tau_{n-1} \cdots \tau_1 \tau_{n-1} \cdots \tau_2 \cdots \tau_{n-1} \tau_{n-2} \tau_{n-1}$, and a permutation~$\omega \in \fS_n = A_{n-1}$.
+The word~$Q$ naturally fits on an $n \times n$ triangular grid (place $\tau_k$ in all boxes with row~$i$ and column~$j$ such that~$i+j = k+1$). 
+Moreover, each facet~$I$ of the subword complex~$\subwordComplex(Q, \omega)$ corresponds to a pipe dream~$P_I$ of~$\pipeDreams(\omega)$ (replace each position in~$I$ by a contact in~$P_I$, and the other positions by crossings in~$P_I$).
+The root function is given~$\rootFunction{I}{i} = \b{r}_{p,q} \eqdef \b{e}_q - \b{e}_p$ where~$p$ is the pipe arriving from the west and $q$ is the pipe arriving from the south at the box of~$P_I$ corresponding to position~$i$ of~$Q$.
 Hence, the root configuration is the incidence configuration~$\Roots(I) = \bigset{\b{r}_{p,q}}{(p,q) \in P_I\contact}$ of the contact graph of~$P_I$.
 In particular, the acyclic facets of~$\subwordComplex(Q, \omega)$ correspond to the acyclic pipe dreams of~$\acyclicPipeDreams(\omega)$.
+
+For a specific illustration, consider the word~$Q \eqdef \tau_6 \tau_5 \tau_4 \tau_3 \tau_2 \tau_1 \tau_6 \tau_5 \tau_4 \tau_3 \tau_2 \tau_6 \tau_5 \tau_4 \tau_3 \tau_6 \tau_5 \tau_4 \tau_6 \tau_5 \tau_6$ of~${A_6 = \fS_7}$ and the permutation~$\pi \eqdef 1365724$.
+Then~$Q$ fits in the triangle of \cref{fig:pipeDreams}.
+Moreover, the facets~$I \eqdef \{1,2,3,4,5,6,7,8,9,10,12,16,21\}$ and~$I' \eqdef \{1,2,4,5,6,7,8,9,10,12,16,17,21\}$ \linebreak of~$\subwordComplex(Q, \pi)$ give the pipe dreams of \cref{fig:pipeDreams}.
+The roots~$\rootFunction{I}{3} = \alpha_{q_3} = \alpha_4 = \b{e}_5 - \b{e}_4$ and~$\rootFunction{I'}{17} = q_3 q_{11} q_{13} q_{14} q_{15} (\alpha_{q_{17}}) = \tau_4 \tau_2 \tau_5 \tau_4 \tau_3 (\alpha_5) = - \alpha_4 = \b{e}_4 - \b{e}_5$ correspond to the pipes~$4$ and~$5$ at the corresponding crossings.
 \end{example}
@@
 \begin{example}
-For any finite Coxeter group~$W$ and any Coxeter element~$c \in W$ (a product of all generators of~$S$ in a given arbitrary order), let~$\wo(c)$ denote the $c$-sorting word of~$\wo$ (the lexicographically minimal reduced expression for~$\wo$ in~$c^\infty$, see \cite{Reading-CambrianLattices} for details).
+For any finite Coxeter group~$W$ and any Coxeter element~$c \in W$ (a product of all generators of~$S$ in a given arbitrary order), let~$\wo(c)$ denote the $c$-sorting word of~$\wo$ (the lexicographically minimal reduced expression for~$\wo$ in~$c^\infty$, see \cite{Reading-CambrianLattices} for details), and consider the concatenation~$c\wo(c)$.
 Extending the observation of \cref{exm:Tamari1}, it was shown in~\cite{CeballosLabbeStump} that the subword complex~$\subwordComplex(c\wo(c), \wo)$ is isomorphic to the cluster complex of type~$W$.
@@
 \begin{remark}
-\cref{conj:latticeCongruenceAlternating,conj:latticeQuotientAlternating,conj:latticeQuotientSortingAlternating,conj:latticeQuotientSortingAlternatingBrickPolyhedra,conj:latticeQuotientSortingAlternatingBrickPolytopes} holds in type~$A_n$: our specific proof of~\cref{thm:pipeDreamCongruence,thm:pipeDreamQuotient} can be extended to arbitrary alternating words in type~$A_n$ as will be shown in~\cite{Cartier}.
+\cref{conj:latticeCongruenceAlternating,conj:latticeQuotientAlternating,conj:latticeQuotientSortingAlternating,conj:latticeQuotientSortingAlternatingBrickPolyhedra,conj:latticeQuotientSortingAlternatingBrickPolytopes} holds in type~$A_n$: our specific proof of~\cref{thm:pipeDreamCongruence,thm:pipeDreamQuotient} can be extended to arbitrary alternating words in type~$A_n$ as shown in~\cite{Cartier}.
 They are also supported by computer experiments: we verified \cref{conj:latticeCongruenceAlternating,conj:latticeQuotientAlternating} for all alternating words of length at most~$\ell(\wo)$ (hence \cref{conj:latticeQuotientSortingAlternating,conj:latticeQuotientSortingAlternatingBrickPolyhedra,conj:latticeQuotientSortingAlternatingBrickPolytopes} for all alternating reduced expressions of~$\wo$) in types~$B_2, B_3, D_4$ and~$H_3$.

### 2025-02-18 acyclicFacets/draft/latticePipeDreams.tex
canopy picture

@@
 \[
-\# \set{s < t}{\pi(s) \le r \text{ and } \omega^{-1}(\pi(s)) \le c} - \# \set{s < t}{\pi(s) > r \text{ and } \omega^{-1}(\pi(s)) > c}.
-\]
-\vincent{
-There is a bug here and in the proof. This should be $\max(0, ...)$.
-In the proof, we need to argue that as soon as we use the $\max$ (meaning that a pipe that should contribute to~$-1$ contributes to~$0$), we stay at~$0$ (as we cannot insert pipes that contribute to~$1$, because all non-inversions of~$\omega$ are non-inversions of~$\pi$!!
-Add Nathan Reading to the acknowledgements for a discussion that made me observe this bug.
-}
+\max \big( 0, \# \set{s < t}{\pi(s) \le r \text{ and } \omega^{-1}(\pi(s)) \le c} - \# \set{s < t}{\pi(s) > r \text{ and } \omega^{-1}(\pi(s)) > c} \! \big).
+\]
 \end{lemma}
@@
 At step~$t$, we insert a new pipe~$\pi(t)$ which enters at~$\pi(t)$ and exits at~$\omega^{-1}(\pi(t))$.
+
+Assume first that the new pipe~$\pi(t)$ intersects the rectangle~$R$.
 Let~${0 \le i < j \le k+1}$ be such that~$e_{i+1}, \dots, e_{j-1}$ are the northwest elbows of pipe~$\pi(t)$ in~$R$, and let~$e'_1, \dots, e'_\ell$ be the southeast elbows of pipe~$\pi(t)$ in~$R$.
@@
 Since the northwest and southeast elbows alternate along pipe~$\pi(t)$, this follows from the fact that the pipe~$\pi(t)$ enters~$R$ with an horizontal step if~$\pi(t) \le r$ and with a vertical step if~$\pi(s) > r$, and exits~$R$ with a vertical step if~$\omega^{-1}(\pi(t)) \le c$ and with an horizontal step if~$\omega^{-1}(\pi(s)) > c$.
+
+Finally, assume that the new pipe~$\pi(t)$ does not intersect the rectangle~$R$.
+This implies that~$\pi(t) > r$ and~$\omega^{-1}(\pi(t)) > c$, and there are no free southeast elbows in~$R$ just before step~$t$.
+Moreover, there is no~$s > t$ such that~$\pi(s) \le r$ and~$\omega^{-1}(\pi(s)) \le c$ (since any inversion of~$\pi$ is an inversion of~$\omega$), and there are no free southeast elbows in~$R$ at any step after~$t$.
+We conclude that the formula still holds in this case.
 \end{proof}
@@
 We start with the easy generalization of recoils of a permutation.
+See \cref{exm:canopy} for an illustration.
 
@@
 \[
-\set{ij}{i < j \text{ and } j-i \le \#\set{k \in [i]}{\omega^{-1}(k) < \omega^{-1}(j)}}.
+\set{ij}{i < j \text{ and } j-i \le \#\set{k < i}{\omega^{-1}(k) < \omega^{-1}(j)}}.
 \]
@@
 We now define a generalization of the canopy map for pipe dreams in~$\acyclicPipeDreams(\omega)$, using \cref{coro:canopy}.
+See \cref{exm:canopy} for an illustration.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{example}
+\label{exm:canopy}
+
+\end{example}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{The acyclic property for $\nu$-Tamari lattices} 
@@
 
-We are grateful to Florent Hivert for various discussions. We also thank Martin Rubey for his comments which led us to think about~\cref{prob:nuAcyclicProperty}.
-Finally, we are grateful to Lucas Gagnon who shared with us an independent proof of the backward direction of \cref{prob:nuAcyclicProperty}, allowing us to greatly simplify our argument.
+We thank Florent Hivert for various discussions, Martin Rubey for his comments which led us to think about~\cref{prob:nuAcyclicProperty}, Lucas Gagnon for sharing his independent proof of the backward direction of \cref{prob:nuAcyclicProperty}, allowing us to greatly simplify our argument, and Nathan Reading for pointing out a serious mistake in the statement and proof of a previous version of \cref{lem:rectangleInsertionAlgorithm}.
+We are grateful to an anonymous referee for comments and suggestions which greatly improved the presentation of this paper.
 

### 2025-02-18 acyclicFacets/draft/latticePipeDreams.tex
canopy picture

@@
 \[
-\set{ij}{i < j \text{ and } j-i \le \#\set{k < i}{\omega^{-1}(k) < \omega^{-1}(j)}}.
+\set{ij}{i < j \text{ and } j-i, \; \omega^{-1}(i) > \omega^{-1}(j) \le \#\set{k < i}{\omega^{-1}(k) < \omega^{-1}(j)}}.
 \]
@@
 \label{prop:latticeHomomorphisms}
-The maps~$\recoils{\cdot}{\omega}$, $\insertion{\cdot}{\omega}$, and~$\canopy{\cdot}$ define the following commutative diagram of lattice homomorphisms:
+The maps~$\recoils{\cdot}{\omega}$, $\insertion{\cdot}{\omega}$, and~$\canopy{\cdot}$ define the following commutative diagram of surjective poset homomorphisms:
 \[
@@
 
+%
+\begin{figure}
+	\centerline{\includegraphics[scale=1]{canopy}}
+	\caption{The pipe dream congruence (blue bubbles) and the $31542$-recoil congruence (red bubbles) on the weak order interval~$[12345, 31542]$ (left) and the canopy congruence (red bubbles) on the increasing flip graph on acyclic pipe dreams (right).
+Each blue bubble is contained in a red bubble.}
+	\label{fig:canopy}
+\end{figure}
 \end{example}

### 2025-02-18 acyclicFacets/reports/answerReferee.tex
canopy picture
last changes

@@
 \item \textsl{\color{gray} Page 15 -- section 4.4: this section needs an example.} \\
-{\color{red} TODO}
+We have added two examples in Section 4.4.
+In particular, we have added Figure 10 were we have grouped permutations of~$[e,\omega]$ according to their $\omega$-recoils and pipe dreams of $\Sigma(\omega)$ according to their canopy.
+We have also slightly modified the graph~$G(\omega)$ to make these $\omega$-recoil and canopy maps surjective.
 
@@
 Finally, we have also slightly modified the statement and proof of Lemma 4.7.
-{\color{red} TODO + explain why.}
+The statement was missing a $\max(0, \dots)$, and the proof was not considering the case where the new pipe~$\pi(t)$ does not meet the rectangle~$R$.
+This is now rectified.
+This problem was observed in discussions with Nathan Reading.
 

### 2025-02-18 acyclicFacets/draft/latticePipeDreams.tex
last changes

@@
 
-\enlargethispage{.6cm}
 We now gather some elementary properties of crossings and contacts in pipe dreams that will be needed later to construct pipe dreams from permutations.
@@
 We already proved the equivalence (i) $\Leftrightarrow$ (ii) in \cref{thm:pipeDreamQuotient}.
-The equivalence (ii) $\Leftrightarrow$ (iii) is valid for any lattice quotient.
+The equivalence \mbox{(ii) $\Leftrightarrow$ (iii)} is valid for any lattice quotient.
 The equivalences (iii) $\Leftrightarrow$ (iv) $\Leftrightarrow$ (v) $\Leftrightarrow$ (vi) follow from the descriptions of \cref{prop:WOIP} of the inversions of the minimum and the non-inversions of the maximum of a weak order interval.
@@
 Let~$\acyclicOrientations(\omega)$ denote the set of acyclic orientations of~$G(\omega)$.
-The \defn{$\omega$-recoil congruence} is the equivalence relation on the weak order interval~$[e, \omega]$ whose equivalence classes are the sets of linear extensions of the acyclic orientations of~$G(\omega)$.
+%The \defn{$\omega$-recoil congruence} is the equivalence relation on the weak order interval~$[e, \omega]$ whose equivalence classes are the sets of linear extensions of the acyclic orientations of~$G(\omega)$.
 The \defn{$\omega$-recoils} of a permutation~$\pi \in [e,\omega]$ is the acyclic orientation~${\recoils{\pi}{\omega} \in \acyclicOrientations(\omega)}$ such that~$\pi$ is a linear extension of~$\recoils{\pi}{\omega}$.
@@
 \label{prop:latticeHomomorphisms}
-The maps~$\recoils{\cdot}{\omega}$, $\insertion{\cdot}{\omega}$, and~$\canopy{\cdot}$ define the following commutative diagram of surjective poset homomorphisms:
+The maps~$\recoils{\cdot}{\omega}$, $\insertion{\cdot}{\omega}$, and~$\canopy{\cdot}$ define the following commutative diagram of surjective lattice homomorphisms:
 \[
@@
 \begin{example}
+For the permutation~$\omega = 1 n \cdots 2$, the graph~$G(\omega)$ has an isolated vertex~$1$ and a path~$2-3-\dots -n$.
+The orientations of this path can be seen as sign sequences, corresponding to the recoils of permutations or the canopies of binary trees.
+More generally, for the permutation~${\omega = 1 \cdots k n \dots (k+1)}$, the graph~$G(\omega)$ consist of all edges~$ij$ for~$k+1 \le i < j \le n$ such that~$|i-j| \le k$, and the $\omega$-recoil map on permutations and canopy on acyclic pipe dreams were already considered in~\cite{Pilaud-brickAlgebra}.
+\end{example}
+
+\begin{example}
 \label{exm:canopy}
-
+For~$\omega = 31542$, the graph~$G(\omega)$ has a single edge~$4-5$.
+We have grouped the permutations of~$[e,\omega]$ according to their $\omega$-recoils, and the pipe dreams of~$\acyclicPipeDreams(\omega)$ according to their canopy in \cref{fig:canopy}.
 %
@@
 
-\pagebreak
 \subsection{Linear extensions of facets}
@@
 
+\pagebreak
 \begin{lemma}
@@
 
-\pagebreak
 \begin{remark}

### 2025-02-18 acyclicFacets/draft/latticePipeDreams.tex
affiliation and grants

@@
 \author[V.~Pilaud]{Vincent Pilaud}
-\address[V.~Pilaud]{Universitat de Barcelona}
+\address[Vincent Pilaud]{Universitat de Barcelona \& Centre de Recerca Matemàtica, Barcelona, Spain}
 \email{vincent.pilaud@ub.edu}
@@
 CC was supported by the Austrian Science Fund FWF (Project P 33278).
-NC \& VP were partially supported by the French project CHARMS (ANR~19\,CE40\,0017).
-CC, NC \& VP were also supported by the Austrian\,--\,French project PAGCAP (ANR~21\,CE48\,0020 \& FWF I 5788).
+CC, NC \& VP were supported by the Austrian\,--\,French project PAGCAP (ANR~21\,CE48\,0020 \& FWF I 5788).
+NC \& VP were also supported by the French project CHARMS (ANR~19\,CE40\,0017).
+VP was also supported by the Spanish project PID2022-137283NB-C21 of MCIN/AEI/10.13039/501100011033 / FEDER, UE, by the Spanish--German project COMPOTE (AEI PCI2024-155081-2 \& DFG 541393733), by the Severo Ochoa and María de Maeztu Program for Centers and Units of Excellence in R\&D (CEX2020-001084-M), by the Departament de Recerca i Universitats de la Generalitat de Catalunya (2021 SGR 00697).
 VP was a CNRS researcher at \'Ecole Polytechnique when this work was done.
@@
 
-\vspace*{-1.2cm}
+%\vspace*{-1.2cm}
 
@@
 
-\vspace*{-.7cm}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+%\vspace*{-.7cm}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\pagebreak
 \section{Introduction}
@@
 
-\begin{figure}[t]
+\begin{figure}[b]
 	\centerline{
@@
 
+\pagebreak
 Note that the pipe dream congruence indeed defines an equivalence relation by \cref{thm:partitionPipeDreams}.
@@
 
-\pagebreak
 \begin{lemma}
@@
 It then scans the word $Q=(q_1,\dots ,q_m)$ from left to right.
-At position $j\in [m]$ it produces a new set $I^j$ obtained from the previous one $I^{j-1}$ by either adding $j$ or not, according to certain rules.
+At position $j\in [m]$ it produces a new set $I^j$ obtained from the previous one~$I^{j-1}$ by either adding $j$ or not, according to certain rules.
 Roughly speaking, the goal of the algorithm is to insert a reduced expression of $\omega$ in $Q$ by sweeping the word from left to right, while deciding whether we use a letter or not by looking at the root $\beta=\rootFunction{I^j}{j}$ that it produces.
-If $\beta \in \Ninv(\omega)$ then it can not be used (Case~\ref{sweeping_case1}), otherwise we would not have a reduced expression for $\omega$.
-If $\beta \in \Inv(\omega)$ then it takes it when $\beta \in \Inv(\pi)$ (Case~\ref{sweeping_case2}), or delays it as much as possible when $\beta \in \Ninv(\pi)$ (Case~\ref{sweeping_case3}).
+If~$\beta \in \Ninv(\omega)$ then it can not be used (Case~\ref{sweeping_case1}), otherwise we would not have a reduced expression for $\omega$.
+If~$\beta \in \Inv(\omega)$ then it takes it when $\beta \in \Inv(\pi)$ (Case~\ref{sweeping_case2}), or delays it as much as possible when $\beta \in \Ninv(\pi)$ (Case~\ref{sweeping_case3}).
 If $\beta \in -\Inv(\omega)$ it can simply not take it (Case~\ref{sweeping_case4}).
